### 2017-09-11 article/sections/introduction.tex
added the article  folder where the results of this project are being documented

\section{Introduction}

In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.

This paper is organized in the following manner: In \sec{sec:pol-intro} we present a primer on the description of CMB polarization on the sphere and introduce the matrix notation which provides a more concise description of the same. In \sec{sec:real_space_operators} we introduce the necessary tools  and discuss the derivations of the real space operators. In \sec{sec:visualize_operator} we evaluate the real space operators and present visualizations of these functions. Here we discuss the locality of the real space E \& B operators. In \sec{sec:numerical_implementation} we implement these operators to evaluate E \& B  maps from the Stokes parameters Q \& U and compare these maps and their spectra from those derived using Healpix. We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.

\section{E/B description of CMB polarization} \label{sec:pol-intro}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Polarization primer}\label{sec:pol-primer}
The CMB polarization is measured in terms of Stokes Q and U parameters. These measurements can be combined to form the complex spin 2 polarization field as follows,
%
\beqry \label{eq:spin-pol}
_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
\eeqry
%
Since these measured quantities depend on the local coordinate system making it is cumbersome to work with them. To overcome this, one describes the CMB polarization field in terms of a scalar field denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}. These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ through the following relation,
%
\beq \label{eq:ebdef}
\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  +  \eth^2 _{- 2}X(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
\eeq
%
where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively. These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions. The spin raising and lowering operators have the following properties \cite{goldberg67},
%
\beqrys \label{eq:spinopylm} 
\eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
\bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
\eeqrys
%
where $_s Y_{lm}(\hat{n}) $ denote the spin-s spherical harmonics.

Using \eq{eq:ebdef} and the properties of the spin raising and lowering operators given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are defined via the following set of equations,
%
\beq \label{eq:pseudo}
\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
\eeq
%
where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the spin harmonic coefficients of the polarization field through the following equations,
%
\beq\label{eq:x2eb}
a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}X_{\ell m} + _{-2}X_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}X_{\ell m} - _{-2}X_{\ell m} \Big] 
\eeq
%
In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following expressions, 
%
\beq \label{eq:pseudo}
E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
\eeq
%
Note that the two set of fields $\mathcal{E}/\mathcal{B}$ and $E/B$ differ, since their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
\filbreak

### 2017-09-11 article/sections/real_space_operators.tex
added the article  folder where the results of this project are being documented

\subsection{Matrix notation} \label{sec:mat_pol_intro}
In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}. This representation will make transparent the derivation of the real space operators we discuss in the following sections. We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
%
\beq
_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
\eeq
%
where $s$ denotes the spin of the basis functions. For this work we will only be working with cases $s \in [0,2]$. In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere. Note that this matrix is in general not a square matrix. Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).

We now define the different data vectors and their representation in real and harmonic space as follows,
%
\beqrys
\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
\eeqrys
%
The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.

Next we define the operators which govern the transformations between different representations of the polarization field as follows,
%
\beqrys
\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
\eeqrys
%
Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
%
\beqrys \label{eq:pol_data_relns}
\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
\eeqrys
%
Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
%
\beqrys
\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
\eeqrys
%
Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
%
\beqrys\label{eq:eb_har_proj}
\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
 \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
 \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
\eeqrys
%
Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real space operators} \label{sec:real_space_operators}
In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa. We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively. We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.

All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere. Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}. The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
%
\beqrys \label{eq:fn_euler}
\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
\eeqrys
%
where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems. While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$. It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator. 
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U. To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields. Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.  
We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
%
\beqrys
\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
&=&  \bar O *\bar{P} \,.
\eeqrys
%
The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure of contracting over the operators is explicitly worked out in the following set of equations,
%
\beqrys
\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
\eeqrys
%
where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$. Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
%
\beq
 \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
 \eeq
 %
 where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
%
\beqrys
\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
\eeqrys
%
where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}. Here we first note that this function does not depend on the Euler angle $\gamma$. This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.  except the factor of 2 which arises because the polarization field is a spin-2 field. The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function. $f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel. The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.

Finally the real space operator can be cast in this simple form,
%
\beq\label{eq:op_qu2eb}
\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
\eeq
%
where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere. \revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}

The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
%
\beq \label{eq:qu2eb_convolution}
\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
\eeq
%
where we have used the Einstein summation convention: repeated indices are summed over. The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization. \revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions. One can now think of constructing alternate basis functions which have different radial fall off.}
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
%
\beqry
\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
&=&  \bar O^{-1} *\bar{S}
\eeqry
%
We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
%
\beq
{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
\eeq
%
where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
%
\beq
\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
\eeq
%
where again the Einstein summation convention is implied and all the symbols have their usual meaning.

\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections. The E \& B modes are orthogonal to each other. It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization. We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.  In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}. Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved. Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators. It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
%
\beqry
\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
&=&  \bar O_{B}*\bar{P} \,. \nonumber
\eeqry
%
We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
%
\beq
\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
\eeq
where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
\beqry
\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
\eeqry
%
These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}. Specifically it can be shown that these functions reduce to the following mathematical forms,
%
\beqrys \label{eq:fn_i}
\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
\eeqrys
%
%
\beqrys \label{eq:fn_d}
\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
\eeqrys
%
where the functions,
%
\beq
{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
\eeq
%
can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
 %
 \beqry
 _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\ 
&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
 \eeqry
 %
Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
 %
\beqry
\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
\eeqry
%
where all the symbols have their usual meaning.

\section{Visualizing the real space operators} \label{sec:visualize_operator}
We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $. Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels. These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$. The resultant functions are depicted in \fig{fig:beta_kernel}. Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$). 
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}. These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$. The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
\label{fig:beta_kernel}
\end{figure}
%
We recall that the fields E \& B are scalar and hence immune to coordinate definitions. The locally defined Stokes parameters however necessarily depend on the coordinate definition. Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars. The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B. Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.

In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}. We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere. For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048. We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}. 
 %
\begin{figure}[!h] \label{fig:mixing_kernel}
\centering
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}. These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal. The size of each panel is approximately $26^{\circ} \times 26^{\circ}$. The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole. The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
\label{fig:vis_kernel}
 \end{figure}
%
\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel. The only contrasting locations are the poles (i.e. $|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$. It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}. On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel. It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}. This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.  The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles. \revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}. Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }. All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.

\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels. To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$. The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}. All the function have been normalized such that their global maxima is set to unity. Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel. 
%
\begin{figure}[!t]
\centering
\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$. The curves for each of these functions have been normalized such that the maximum of the curve is set to unity. The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum. The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions. While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%
We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$. We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.

The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off. A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range. This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).

\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}

\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
\section{Numerical implementation} \label{sec:numerical_implementation}

As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}). For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel. This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel. The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.

We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters. To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$. Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels. $f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}. ${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}. As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}. We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}. Given these  inputs we evaluate the convolution kernel as simple Reimann sums. We repeat this procedure for each pixel on the Healpix map.

For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise. \revisit{We use the CMB spectra for some fiducial cosmology. This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.  Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$. We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs. We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise. Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e. $\beta_o=\pi$).  We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}

%
\begin{figure}[!h] 
\centering
\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix. {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$. {\textit Right:} Difference between the maps shown in the left and middle columns. Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
\label{fig:eb-maps-compare}
\end{figure}
%
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:eq-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Extracting Equ and Bqu maps}
%
\begin{figure}[!h] 
\centering
\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}

\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
\caption{}
\label{fig:equ-bqu-maps-compare}
\end{figure}
%

%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
\caption{}
\label{fig:equ-bqu-spectra_rad_cutoff}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Scaling and future prospects}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$. The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
\label{fig:disc_rad_healpix_numpix}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Application of Planck 353 Ghz polarization maps}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
\caption{}
\label{fig:353ghz-eb-maps}
\end{figure}
%
\section{Discussion}\label{sec:discussion}
\begin{itemize}
\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa. We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.

\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.

\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment. Motivation for defining radially compact kernels. We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.

\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.

\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.

\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking. For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.

\end{itemize}
%
%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization. One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask. Mask apodization techniques should fail at low Nside. The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.

### 2017-09-11 article/article.tex
added the folder article which documents the results of this project

%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers,twocolumn]{revtex4}%showpacs,superscriptaddress
%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers]{revtex4}%showpacs,superscriptaddress
\documentclass[a4paper,11pt]{article}
\usepackage{jcappub}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\hypersetup{colorlinks=True,citecolor=blue}
\usepackage{amssymb}
\usepackage{graphicx,multirow}
\usepackage{subfigure}
\renewcommand*{\thesubfigure}{}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

%\usepackage{caption}
%\usepackage{subfigure}
%\usepackage{float}
%\usepackage{bm}
%\usepackage{latexsym}
%\usepackage{epsfig}
%\usepackage{graphicx,color}
\usepackage{bbold}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqry}{\begin{eqnarray}}
\newcommand{\eeqry}{\end{eqnarray}}
\newcommand{\beqrys}{\begin{subequations}\begin{eqnarray}}
\newcommand{\eeqrys}{\end{eqnarray}\end{subequations}}
\newcommand{\fqu}{\begin{bmatrix} Q \\ U \end{bmatrix}}
\newcommand{\xpm}{\begin{bmatrix} _{+2}X \\ _{-2}X \end{bmatrix}}
\newcommand{\equ}{\begin{bmatrix} Q \\ U \end{bmatrix}_{E}}
\newcommand{\bqu}{\begin{bmatrix} Q \\ U \end{bmatrix}_{B}}
\newcommand{\eblm}{\begin{bmatrix} a^E \\ a^{B} \end{bmatrix}}
\newcommand{\qutox}{\begin{bmatrix} \mathbb{1} & i\mathbb{1}  \\  \mathbb{1} & -i\mathbb{1}   \end{bmatrix}}
\newcommand{\qutoxd}{\begin{bmatrix} \mathbb{1} & \mathbb{1}  \\  -i\mathbb{1} & i\mathbb{1}   \end{bmatrix}}
\newcommand{\ymat}{\begin{bmatrix} _{+2}Y & 0  \\  0 & _{-2}Y  \end{bmatrix}}
\newcommand{\ymatc}{\begin{bmatrix} _{+2}Y^* & 0  \\  0 & _{-2}Y^*  \end{bmatrix}}
\newcommand{\yzmat}{\begin{bmatrix} _{0}Y & 0  \\  0 & _{0}Y  \end{bmatrix}}
\newcommand{\yzmatc}{\begin{bmatrix} _{0}Y^* & 0  \\  0 & _{0}Y^*  \end{bmatrix}}
\newcommand{\ope}{\hat{O}_{E}}
\newcommand{\opb}{\hat{O}_{B}}
\newcommand{\bmat}{\begin{bmatrix}}
\newcommand{\emat}{\end{bmatrix}}

\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{red}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
\newcommand{\rfedit}{\textcolor{magenta}  }
\newcommand{\soothe}{\textcolor{BlueViolet}  }

\def\eq#1{{Eq.~(\ref{#1})}}
\def\sec#1{{Sec.~\ref{#1}}}
\def\fig#1{{Fig.~\ref{#1}}}
\def\app#1{{Appendix~\ref{#1}}}
\def\ymat#1{\begin{bmatrix} _{+2}Y_{#1} & 0  \\  0 & _{-2}Y_{#1}  \end{bmatrix}}
\def\ymatc#1{\begin{bmatrix} _{+2}Y^{T*}_{#1} & 0  \\  0 & _{-2}Y^{T*}_{#1}  \end{bmatrix}}
\def\yzmat#1{\begin{bmatrix} _{0}Y_{#1} & 0  \\  0 & _{0}Y_{#1}  \end{bmatrix}}
\def\yzmatc#1{\begin{bmatrix} _{0}Y^*_{#1} & 0  \\  0 & _{0}Y^*_{#1}  \end{bmatrix}}

\graphicspath{ {"./figures/"} }

\begin{document}

\title{Local real space operators for translating Stokes Q/U to E/B maps on the sphere }
\author[]{Aditya Rotti and}
\author[]{Kevin Huffenberger}
\affiliation[]{Department of Physics, Florida State University, Keen Physics Building, 77 Chieftan Way, Tallahassee, Florida, U.S.A.}
\emailAdd{adityarotti@gmail.com}
\emailAdd{khuffenberger@fsu.edu}

\abstract{
\noindent We derive real space operators to translate Stokes Q/U to coordinate independent even and odd parity E/B fields on the sphere and demonstrate their numerical equivalence to the harmonic space methods. In process we also derive real space operators which allow direct decomposition of measured Q/U into Q/U fields corresponding to E-modes and B-modes respectively. These operators are derived on the sphere and account for the curvature effects. The analytical derivations reveal a functional form for the radial kernel, which quantifies the non-local nature of the E and B fields. 
%and their dependence on the band limit of the measurement. 
These real space operators allow the computation of E and B field in each pixel by integrating in a small region around it, and hence it can be easily parallelized and is not memory intensive. A major drawback of these real space operators is that they cannot reliably construct modes on large angular scales $\ell<50$ with ease. Finally, this study motivates the construction of more locally defined E and B maps, by making desired alterations to the radial filter. We demonstrate that these altered E mode and B mode constructions do not significantly distort spectral information on small angular scales. %Such locally constructed E and B maps may help mitigate the foreground leakage issue across the two modes.
}

\maketitle

\include{./sections/introduction}
\include{./sections/real_space_operators}
\include{./sections/discussion.tex}
\include{./sections/appendix}

\bibliographystyle{JHEP}
\bibliography{ref}

\end{document}

### 2017-09-11 article/sections/appendix.tex
added the folder article which documents the results of this project

\section{Appendix}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{ Mathematical properties of spin spherical harmonics}\label{sec:ylm_mathprop}
The sum over $m$ index of product of two spherical harmonic functions of spin $s_1$ and $s_2$ respectively, is given by the following expression \cite{varshalovich},
\beq \label{eq:sum_spin_shf}
 \sum_{m}{_{s_1}Y^*_{\ell m}}(\hat{n}_i){_{s_2}Y_{\ell m}}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} _{s_2}Y^{-s_1}_{\ell}(\beta,\alpha) e^{- i s_2 \gamma} \,,
\eeq
where $\alpha, ~\beta ~\&~ \gamma$ correspond to the Euler angles that specify the rotation matrix which transforms the local cartesian coordinates defined at $\hat{n}_i$ such that it aligns with the local cartesian coordinate system at $\hat{n}_j$.

The spin spherical harmonics satisfy the following orthogonality relations,
%
\beq
\int  {_sY_{\ell m}}(\hat{n}){_sY^*_{\ell' m'}}(\hat{n}) d\Omega = \delta_{\ell \ell'} \delta_{\rm m m'} \,, \label{eq:ylmortho1}
\eeq
%
where $s$ denotes the spin of the spherical harmonic coefficients. The numerical validity of \eq{eq:ylmortho1} is only limited by the rate at which these functions are sampled on the sphere and hence this identity can be made arbitrarily accurate by choosing a sufficiently high sampling rate.
%While working with CMB polarization one is often dealing with spin-2 spherical harmonics. Here we derive some relation which we use while evaluating the real space projection operators,
%\beq
%\sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) = 
%\eeq

The spin spherical harmonic functions satisfy the following completeness relation,
%
\beq
\sum_{\ell m}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) = \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,,
\eeq
%
Note that the numerical validity of \eq{eq:ylmortho2} is strictly true only when the sums over the indices $(\ell, m)$ run to infinity. This is never true in practice, since the measured data invariable are band limited owing to the finite resolution of the experiments. Hence this relation is only approximately true and in more realistic scenario takes up the following function form,
%
\beqry
\sum_{\ell=\ell_{\rm min}, m}^{\ell_{\rm max}}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) &\approx& \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,, \\
&=& \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} {}_{s}Y^{-s}_{\ell}(\beta,\alpha) e^{-i s \gamma} \,, \nonumber
\eeqry
%
where $\alpha, \beta ~\&~ \gamma$ are the Euler angles relating the two directions $\hat{n}_i$ and $\hat{n}_j$. A specific case of this function with $(s=2, \ell_{\rm min}=2, \ell_{\rm max}=96)$ is depicted in the last two columns of \fig{fig:vis_kernel}.

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Asymptotic forms for the functions ${}_{\pm 2}f_{\ell}(\beta)$}\label{sec:asymptotic_f}
The functions ${}_{\pm}f_{\ell}(\beta)$ need to be evaluated close to $\beta= 0$ and $\beta=\pi$. Close to these values we cannot evaluate these functions using the relation given in  \eq{eq:rad_ker_quequbqu}, owing to the inverse $\sin(\beta)$ dependence of a number of terms. To overcome this issue, we use the asymptotic form of the Legendre polynomials as $\beta \rightarrow 0$,
%
\beq
P_{\ell}^2(\cos{\beta})=\sin^2(\beta) \frac{(\ell+2)!}{8(\ell-2)!} \,.
\eeq
%
Using the above limiting form, the functions ${}_{\pm}f_{\ell}(\beta)$ reduce to the following equations,
%
\beqry
\lim_{\beta \to 0}{}_{\pm}f_{\ell}(\beta)&=&\frac{1}{4} \sqrt{\frac{2 \ell+1}{4 \pi}} \Bigg\lbrace -\left[  (\ell-4) + \frac{1}{2} \ell(\ell-1)\sin^2(\beta) \pm 2 (\ell-1) \cos(\beta) \right] \nonumber \\ &+& \left[ (\ell-2) \cos(\beta) \pm 2(\ell-2) \right] \Bigg\rbrace \,.
\eeqry
%
Using the parity property of the associate Legendre polynomials: $P_{\ell}^m(-x)=(-1)^{\ell+m}P_{\ell}^{m}(x)$, the asymptotic form for the functions ${}_{\pm}f_{\ell}(\beta)$ in the limit $\beta \rightarrow \pi$ are given by the following equations,
%
\beqry
\lim_{\beta \to \pi}{}_{\pm}f_{\ell}(\beta)&=&\frac{1}{4} \sqrt{\frac{2 \ell+1}{4 \pi}} \Bigg\lbrace -\left[ (\ell-4) + \frac{1}{2} \ell(\ell-1)\sin^2(\beta) \pm 2 (\ell-1) \cos(\beta) \right] (-1)^{\ell} \nonumber \\ &+& \left[(\ell-2) \cos(\beta) \pm 2(\ell-2)\right] (-1)^{\ell-1} \Bigg\rbrace \,.
\eeqry
%
We use these asymptotic forms for ${}_{\pm}f_{\ell}(\beta)$ to evaluate the radial kernel close to the poles.
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Convolution error}\label{sec:convolution_err}
Here we assess  error in the simple integeration scheme used in our python script. To estimate the error, we use the Healpix integration scheme as the reference. The spatially local convolutions suggested in this work can be carried out using Healpix via the following algorithm: (i) Generate a disc mask of radius $r_{\rm cutoff}$ around a pixel with index ``i". (ii) Apply the mask on the Stokes Q \& U maps and evaluate the E \& B maps using standard Healpix functions. (iii) Store the E \& B field values evaluated at the pixel with index ``i" (the center of the disc mask), while rejecting the fields constructed at other pixels in the mask. (iv) Repeat this process at all pixels to generate a map of the scalar fields E \&  B.  This scheme is mathematical identical to our implementation of carrying out the convolution integrals over spatially local regions. In the above proposed algorithm the locality is enforced by the disc mask. However note that evaluating this scheme using Healpix is extremely inefficient since it effectively involves translating Npix Stokes Q \& U maps to scalar E \& B maps. The computational cost of carrying out this operation using Healpix grows quickly with the resolution parameter $\rm Nside$. For the results presented here we work with Healpix maps simulated at a resolution of Nside=64.

We evaluate the E \& B maps using three different methods,  using our simple Python implementation of the local convolutions, the equivalent scheme using Healpix as described above and the full sky Healpix evaluation (which we use to evaluate the reference spectra). The relative percentage differences between the spectra derived from maps using the local methods and the reference spectra are depicted in \fig{fig:convolution-err}. Note that the error on the E mode spectrum derived from maps constructed using the two different local convolution methods nearly match each other. However for the B-mode spectrum, the error on the spectrum derived from our python implementation is significantly larger as compared to the error on the spectrum derived from the local Healpix convolution method. This indicated the fact that Healpix convolution has a better accuracy as compared our implementation. More important to note here is the fact that the error on the spectra from locally evaluated E and B mode maps are nearly equal to each other, as can be seen by comparing the green curves in the left and and right panels of \fig{fig:convolution-err}.
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{complementary/convolution-err-ee-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{complementary/convolution-err-bb-spectrum-radial-cutoff.pdf}}
\caption{The figure on the left and right depict the relative percentage difference between spectra derived from local convolution estimates of E \& B map and the reference spectra derived from full sky Healpix evaluations. The green curves depict the results from local E \& B maps evaluated using local Healpix operations while the red curve shows the same for the scalar maps derived using our python script. The gray band indicates the scatter expected due to cosmic variance, the lighter shade corresponding to $1\sigma$ and the darker shade to $0.5 \sigma$. \revisit{The cosmic variance band does not account for the non-guassian distribution, which is particularly relevant at the low multipoles.}}
\label{fig:convolution-err}
\end{figure}
%

### 2017-09-11 article/sections/application_353ghz.tex
restructured and made more modular the sections of the article for ease of parallel editing

--- 2017-09-11 article/sections/real_space_operators.tex
@@
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
-This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
-We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
-%
-\beq
-_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
-\eeq
-%
-where $s$ denotes the spin of the basis functions.
-For this work we will only be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere.
-Note that this matrix is in general not a square matrix.
-Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).
-
-We now define the different data vectors and their representation in real and harmonic space as follows,
-%
-\beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
-\eeqrys
-%
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.
-
-Next we define the operators which govern the transformations between different representations of the polarization field as follows,
-%
-\beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
-\eeqrys
-%
-Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
-%
-\beqrys \label{eq:pol_data_relns}
-\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
-\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
-%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-\eeqrys
-%
-Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
-%
-\beqrys
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
-\eeqrys
-%
-Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
-%
-\beqrys\label{eq:eb_har_proj}
-\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
- \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqrys
-%
-Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa.
-We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively.
-We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.
-
-All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
-%
-\beqrys \label{eq:fn_euler}
-\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
-\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
-\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
-\eeqrys
-%
-where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems.
-While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
-It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
-To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
-%
-\beqrys
-\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,.
-\eeqrys
-%
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.
-This procedure of contracting over the operators is explicitly worked out in the following set of equations,
-%
-\beqrys
-\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
-\eeqrys
-%
-where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
-%
-\beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
- \eeq
- %
- where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
-%
-\beqrys
-\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqrys
-%
-where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Here we first note that this function does not depend on the Euler angle $\gamma$.
-This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.
-except the factor of 2 which arises because the polarization field is a spin-2 field.
-The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function.
-$f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel.
-The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
-
-Finally the real space operator can be cast in this simple form,
-%
-\beq\label{eq:op_qu2eb}
-\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}
-
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
-%
-\beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
-\eeq
-%
-where we have used the Einstein summation convention: repeated indices are summed over.
-The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.}
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
-The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
-%
-\beqry
-\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
-&=&  \bar O^{-1} *\bar{S}
-\eeqry
-%
-We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section.
-The inverse operator is given by the following expression,
-%
-\beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
-We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
-%
-\beq
-\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
-\eeq
-%
-where again the Einstein summation convention is implied and all the symbols have their usual meaning.
-
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
-The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other.
-It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization.
-We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}.
-Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved.
-Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators.
-It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
-%
-\beqry
-\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
-\eeqry
-%
-We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
-%
-\beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
-\eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
-\beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
-\eeqry
-%
-These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
-%
-\beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-%
-\beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-where the functions,
-%
-\beq
-{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
-\eeq
-%
-can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
- %
- \beqry
- _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
-&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
- \eeqry
- %
-Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
- %
-\beqry
-\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
-\eeqry
-%
-where all the symbols have their usual meaning.
-
-\section{Visualizing the real space operators} \label{sec:visualize_operator}
-We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
-Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
-Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
-These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
-\label{fig:beta_kernel}
-\end{figure}
-%
-We recall that the fields E \& B are scalar and hence immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars.
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.
-
-In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}.
-We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere.
-For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048.
-We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}.
- %
-\begin{figure}[!h] \label{fig:mixing_kernel}
-\centering
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
-\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal.
-The size of each panel is approximately $26^{\circ} \times 26^{\circ}$.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-\label{fig:vis_kernel}
- \end{figure}
-%
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
-The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.
-It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}.
-On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
-It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.
-The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}.
-Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }.
-All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
-
-\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel.
-%
-\begin{figure}[!t]
-\centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
-The curves for each of these functions have been normalized such that the maximum of the curve is set to unity.
-The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
-The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
-\label{fig:rad_ker_decay}
-\end{figure}
-%
-We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
-
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off.
-A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range.
-This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).
-
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}
-
-\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
-\section{Numerical implementation} \label{sec:numerical_implementation}
-
-As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}).
-For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel.
-This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel.
-The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.
-
-We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
-To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$.
-Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels.
-$f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}.
-As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
-We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
-Given these  inputs we evaluate the convolution kernel as simple Reimann sums.
-We repeat this procedure for each pixel on the Healpix map.
-
-For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-\revisit{We use the CMB spectra for some fiducial cosmology.
-This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
-Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
-We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e.
-$\beta_o=\pi$).
-We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
-\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
-{\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$.
-{\textit Right:} Difference between the maps shown in the left and middle columns.
-Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
-\label{fig:eb-maps-compare}
-\end{figure}
-%
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:eq-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Extracting Equ and Bqu maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}
-
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
-\caption{}
-\label{fig:equ-bqu-maps-compare}
-\end{figure}
-%
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:equ-bqu-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Scaling and future prospects}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
-\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
-The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
-\label{fig:disc_rad_healpix_numpix}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
 \subsection{Application of Planck 353 Ghz polarization maps}
@@
 %
-\section{Discussion}\label{sec:discussion}
-\begin{itemize}
-\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
-We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.
-
-\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.
-
-\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment.
-Motivation for defining radially compact kernels.
-We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.
-
-\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.
-
-\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
-
-\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking.
-For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.
-
-\end{itemize}
-%
-%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization.
-One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask.
-Mask apodization techniques should fail at low Nside.
-The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.

### 2017-09-11 article/sections/discussion.tex
restructured and made more modular the sections of the article for ease of parallel editing

--- 2017-09-11 article/sections/real_space_operators.tex
@@
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
-This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
-We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
-%
-\beq
-_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
-\eeq
-%
-where $s$ denotes the spin of the basis functions.
-For this work we will only be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere.
-Note that this matrix is in general not a square matrix.
-Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).
-
-We now define the different data vectors and their representation in real and harmonic space as follows,
-%
-\beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
-\eeqrys
-%
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.
-
-Next we define the operators which govern the transformations between different representations of the polarization field as follows,
-%
-\beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
-\eeqrys
-%
-Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
-%
-\beqrys \label{eq:pol_data_relns}
-\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
-\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
-%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-\eeqrys
-%
-Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
-%
-\beqrys
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
-\eeqrys
-%
-Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
-%
-\beqrys\label{eq:eb_har_proj}
-\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
- \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqrys
-%
-Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa.
-We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively.
-We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.
-
-All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
-%
-\beqrys \label{eq:fn_euler}
-\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
-\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
-\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
-\eeqrys
-%
-where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems.
-While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
-It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
-To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
-%
-\beqrys
-\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,.
-\eeqrys
-%
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.
-This procedure of contracting over the operators is explicitly worked out in the following set of equations,
-%
-\beqrys
-\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
-\eeqrys
-%
-where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
-%
-\beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
- \eeq
- %
- where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
-%
-\beqrys
-\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqrys
-%
-where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Here we first note that this function does not depend on the Euler angle $\gamma$.
-This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.
-except the factor of 2 which arises because the polarization field is a spin-2 field.
-The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function.
-$f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel.
-The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
-
-Finally the real space operator can be cast in this simple form,
-%
-\beq\label{eq:op_qu2eb}
-\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}
-
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
-%
-\beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
-\eeq
-%
-where we have used the Einstein summation convention: repeated indices are summed over.
-The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.}
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
-The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
-%
-\beqry
-\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
-&=&  \bar O^{-1} *\bar{S}
-\eeqry
-%
-We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section.
-The inverse operator is given by the following expression,
-%
-\beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
-We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
-%
-\beq
-\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
-\eeq
-%
-where again the Einstein summation convention is implied and all the symbols have their usual meaning.
-
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
-The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other.
-It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization.
-We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}.
-Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved.
-Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators.
-It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
-%
-\beqry
-\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
-\eeqry
-%
-We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
-%
-\beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
-\eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
-\beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
-\eeqry
-%
-These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
-%
-\beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-%
-\beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-where the functions,
-%
-\beq
-{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
-\eeq
-%
-can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
- %
- \beqry
- _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
-&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
- \eeqry
- %
-Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
- %
-\beqry
-\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
-\eeqry
-%
-where all the symbols have their usual meaning.
-
-\section{Visualizing the real space operators} \label{sec:visualize_operator}
-We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
-Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
-Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
-These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
-\label{fig:beta_kernel}
-\end{figure}
-%
-We recall that the fields E \& B are scalar and hence immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars.
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.
-
-In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}.
-We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere.
-For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048.
-We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}.
- %
-\begin{figure}[!h] \label{fig:mixing_kernel}
-\centering
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
-\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal.
-The size of each panel is approximately $26^{\circ} \times 26^{\circ}$.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-\label{fig:vis_kernel}
- \end{figure}
-%
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
-The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.
-It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}.
-On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
-It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.
-The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}.
-Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }.
-All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
-
-\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel.
-%
-\begin{figure}[!t]
-\centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
-The curves for each of these functions have been normalized such that the maximum of the curve is set to unity.
-The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
-The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
-\label{fig:rad_ker_decay}
-\end{figure}
-%
-We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
-
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off.
-A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range.
-This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).
-
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}
-
-\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
-\section{Numerical implementation} \label{sec:numerical_implementation}
-
-As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}).
-For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel.
-This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel.
-The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.
-
-We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
-To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$.
-Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels.
-$f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}.
-As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
-We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
-Given these  inputs we evaluate the convolution kernel as simple Reimann sums.
-We repeat this procedure for each pixel on the Healpix map.
-
-For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-\revisit{We use the CMB spectra for some fiducial cosmology.
-This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
-Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
-We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e.
-$\beta_o=\pi$).
-We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
-\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
-{\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$.
-{\textit Right:} Difference between the maps shown in the left and middle columns.
-Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
-\label{fig:eb-maps-compare}
-\end{figure}
-%
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:eq-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Extracting Equ and Bqu maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}
-
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
-\caption{}
-\label{fig:equ-bqu-maps-compare}
-\end{figure}
-%
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:equ-bqu-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Scaling and future prospects}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
-\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
-The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
-\label{fig:disc_rad_healpix_numpix}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Application of Planck 353 Ghz polarization maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
-\caption{}
-\label{fig:353ghz-eb-maps}
-\end{figure}
-%
 \section{Discussion}\label{sec:discussion}

### 2017-09-11 article/sections/kernel_discussion.tex
restructured and made more modular the sections of the article for ease of parallel editing

--- 2017-09-11 article/sections/real_space_operators.tex
@@
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
-This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
-We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
-%
-\beq
-_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
-\eeq
-%
-where $s$ denotes the spin of the basis functions.
-For this work we will only be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere.
-Note that this matrix is in general not a square matrix.
-Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).
-
-We now define the different data vectors and their representation in real and harmonic space as follows,
-%
-\beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
-\eeqrys
-%
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.
-
-Next we define the operators which govern the transformations between different representations of the polarization field as follows,
-%
-\beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
-\eeqrys
-%
-Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
-%
-\beqrys \label{eq:pol_data_relns}
-\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
-\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
-%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-\eeqrys
-%
-Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
-%
-\beqrys
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
-\eeqrys
-%
-Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
-%
-\beqrys\label{eq:eb_har_proj}
-\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
- \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqrys
-%
-Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa.
-We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively.
-We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.
-
-All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
-%
-\beqrys \label{eq:fn_euler}
-\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
-\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
-\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
-\eeqrys
-%
-where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems.
-While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
-It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
-To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
-%
-\beqrys
-\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,.
-\eeqrys
-%
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.
-This procedure of contracting over the operators is explicitly worked out in the following set of equations,
-%
-\beqrys
-\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
-\eeqrys
-%
-where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
-%
-\beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
- \eeq
- %
- where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
-%
-\beqrys
-\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqrys
-%
-where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Here we first note that this function does not depend on the Euler angle $\gamma$.
-This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.
-except the factor of 2 which arises because the polarization field is a spin-2 field.
-The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function.
-$f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel.
-The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
-
-Finally the real space operator can be cast in this simple form,
-%
-\beq\label{eq:op_qu2eb}
-\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}
-
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
-%
-\beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
-\eeq
-%
-where we have used the Einstein summation convention: repeated indices are summed over.
-The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.}
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
-The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
-%
-\beqry
-\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
-&=&  \bar O^{-1} *\bar{S}
-\eeqry
-%
-We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section.
-The inverse operator is given by the following expression,
-%
-\beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
-We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
-%
-\beq
-\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
-\eeq
-%
-where again the Einstein summation convention is implied and all the symbols have their usual meaning.
-
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
-The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other.
-It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization.
-We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}.
-Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved.
-Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators.
-It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
-%
-\beqry
-\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
-\eeqry
-%
-We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
-%
-\beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
-\eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
-\beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
-\eeqry
-%
-These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
-%
-\beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-%
-\beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-where the functions,
-%
-\beq
-{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
-\eeq
-%
-can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
- %
- \beqry
- _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
-&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
- \eeqry
- %
-Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
- %
-\beqry
-\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
-\eeqry
-%
-where all the symbols have their usual meaning.
-
 \section{Visualizing the real space operators} \label{sec:visualize_operator}
@@
 \comment{Do you want to comment on the telescoping behavior of these radial functions ? }
-\section{Numerical implementation} \label{sec:numerical_implementation}
-
-As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}).
-For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel.
-This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel.
-The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.
-
-We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
-To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$.
-Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels.
-$f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}.
-As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
-We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
-Given these  inputs we evaluate the convolution kernel as simple Reimann sums.
-We repeat this procedure for each pixel on the Healpix map.
-
-For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-\revisit{We use the CMB spectra for some fiducial cosmology.
-This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
-Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
-We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e.
-$\beta_o=\pi$).
-We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
-\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
-{\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$.
-{\textit Right:} Difference between the maps shown in the left and middle columns.
-Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
-\label{fig:eb-maps-compare}
-\end{figure}
-%
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:eq-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Extracting Equ and Bqu maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}
-
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
-\caption{}
-\label{fig:equ-bqu-maps-compare}
-\end{figure}
-%
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:equ-bqu-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Scaling and future prospects}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
-\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
-The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
-\label{fig:disc_rad_healpix_numpix}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Application of Planck 353 Ghz polarization maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
-\caption{}
-\label{fig:353ghz-eb-maps}
-\end{figure}
-%
-\section{Discussion}\label{sec:discussion}
-\begin{itemize}
-\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
-We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.
-
-\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.
-
-\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment.
-Motivation for defining radially compact kernels.
-We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.
-
-\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.
-
-\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
-
-\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking.
-For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.
-
-\end{itemize}
-%
-%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization.
-One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask.
-Mask apodization techniques should fail at low Nside.
-The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.

### 2017-09-11 article/sections/numerical_implementation.tex
restructured and made more modular the sections of the article for ease of parallel editing

--- 2017-09-11 article/sections/real_space_operators.tex
@@
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
-This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
-We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
-%
-\beq
-_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
-\eeq
-%
-where $s$ denotes the spin of the basis functions.
-For this work we will only be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere.
-Note that this matrix is in general not a square matrix.
-Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).
-
-We now define the different data vectors and their representation in real and harmonic space as follows,
-%
-\beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
-\eeqrys
-%
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.
-
-Next we define the operators which govern the transformations between different representations of the polarization field as follows,
-%
-\beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
-\eeqrys
-%
-Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
-%
-\beqrys \label{eq:pol_data_relns}
-\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
-\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
-%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-\eeqrys
-%
-Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
-%
-\beqrys
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
-\eeqrys
-%
-Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
-%
-\beqrys\label{eq:eb_har_proj}
-\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
- \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqrys
-%
-Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa.
-We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively.
-We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.
-
-All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
-%
-\beqrys \label{eq:fn_euler}
-\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
-\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
-\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
-\eeqrys
-%
-where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems.
-While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
-It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
-To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
-%
-\beqrys
-\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,.
-\eeqrys
-%
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.
-This procedure of contracting over the operators is explicitly worked out in the following set of equations,
-%
-\beqrys
-\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
-\eeqrys
-%
-where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
-%
-\beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
- \eeq
- %
- where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
-%
-\beqrys
-\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqrys
-%
-where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Here we first note that this function does not depend on the Euler angle $\gamma$.
-This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.
-except the factor of 2 which arises because the polarization field is a spin-2 field.
-The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function.
-$f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel.
-The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
-
-Finally the real space operator can be cast in this simple form,
-%
-\beq\label{eq:op_qu2eb}
-\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}
-
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
-%
-\beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
-\eeq
-%
-where we have used the Einstein summation convention: repeated indices are summed over.
-The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.}
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
-The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
-%
-\beqry
-\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
-&=&  \bar O^{-1} *\bar{S}
-\eeqry
-%
-We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section.
-The inverse operator is given by the following expression,
-%
-\beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
-\eeq
-%
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
-We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
-%
-\beq
-\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
-\eeq
-%
-where again the Einstein summation convention is implied and all the symbols have their usual meaning.
-
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
-The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other.
-It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization.
-We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}.
-Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved.
-Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators.
-It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
-%
-\beqry
-\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
-\eeqry
-%
-We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
-%
-\beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
-\eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
-\beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
-\eeqry
-%
-These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
-%
-\beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-%
-\beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-where the functions,
-%
-\beq
-{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
-\eeq
-%
-can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
- %
- \beqry
- _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
-&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
- \eeqry
- %
-Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
- %
-\beqry
-\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
-\eeqry
-%
-where all the symbols have their usual meaning.
-
-\section{Visualizing the real space operators} \label{sec:visualize_operator}
-We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
-Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
-Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
-These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
-\label{fig:beta_kernel}
-\end{figure}
-%
-We recall that the fields E \& B are scalar and hence immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars.
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.
-
-In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}.
-We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere.
-For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048.
-We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}.
- %
-\begin{figure}[!h] \label{fig:mixing_kernel}
-\centering
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
-\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal.
-The size of each panel is approximately $26^{\circ} \times 26^{\circ}$.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-\label{fig:vis_kernel}
- \end{figure}
-%
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
-The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.
-It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}.
-On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
-It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.
-The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}.
-Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }.
-All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
-
-\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel.
-%
-\begin{figure}[!t]
-\centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
-The curves for each of these functions have been normalized such that the maximum of the curve is set to unity.
-The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
-The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
-\label{fig:rad_ker_decay}
-\end{figure}
-%
-We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
-
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off.
-A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range.
-This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).
-
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}
-
-\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
 \section{Numerical implementation} \label{sec:numerical_implementation}
@@
 %--------------------------------------------------------
-\subsection{Application of Planck 353 Ghz polarization maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
-\caption{}
-\label{fig:353ghz-eb-maps}
-\end{figure}
-%
-\section{Discussion}\label{sec:discussion}
-\begin{itemize}
-\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
-We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.
-
-\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.
-
-\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment.
-Motivation for defining radially compact kernels.
-We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.
-
-\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.
-
-\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
-
-\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking.
-For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.
-
-\end{itemize}
-%
-%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization.
-One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask.
-Mask apodization techniques should fail at low Nside.
-The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.

### 2017-09-11 article/sections/real_space_formalism.tex
restructured and made more modular the sections of the article for ease of parallel editing

--- 2017-09-11 article/sections/real_space_operators.tex
@@
 where all the symbols have their usual meaning.
-
-\section{Visualizing the real space operators} \label{sec:visualize_operator}
-We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
-Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
-Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
-These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
-\label{fig:beta_kernel}
-\end{figure}
-%
-We recall that the fields E \& B are scalar and hence immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars.
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.
-
-In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}.
-We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere.
-For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048.
-We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}.
- %
-\begin{figure}[!h] \label{fig:mixing_kernel}
-\centering
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
-\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal.
-The size of each panel is approximately $26^{\circ} \times 26^{\circ}$.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-\label{fig:vis_kernel}
- \end{figure}
-%
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
-The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.
-It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}.
-On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
-It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.
-The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}.
-Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }.
-All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
-
-\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel.
-%
-\begin{figure}[!t]
-\centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
-The curves for each of these functions have been normalized such that the maximum of the curve is set to unity.
-The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
-The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
-\label{fig:rad_ker_decay}
-\end{figure}
-%
-We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
-
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off.
-A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range.
-This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).
-
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}
-
-\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
-\section{Numerical implementation} \label{sec:numerical_implementation}
-
-As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}).
-For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel.
-This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel.
-The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.
-
-We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
-To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$.
-Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels.
-$f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}.
-As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
-We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
-Given these  inputs we evaluate the convolution kernel as simple Reimann sums.
-We repeat this procedure for each pixel on the Healpix map.
-
-For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-\revisit{We use the CMB spectra for some fiducial cosmology.
-This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
-Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
-We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e.
-$\beta_o=\pi$).
-We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
-\caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
-{\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$.
-{\textit Right:} Difference between the maps shown in the left and middle columns.
-Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
-\label{fig:eb-maps-compare}
-\end{figure}
-%
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:eq-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Extracting Equ and Bqu maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}
-
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
-\caption{}
-\label{fig:equ-bqu-maps-compare}
-\end{figure}
-%
-
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:equ-bqu-spectra_rad_cutoff}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Scaling and future prospects}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
-\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
-The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
-\label{fig:disc_rad_healpix_numpix}
-\end{figure}
-%
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Application of Planck 353 Ghz polarization maps}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
-\caption{}
-\label{fig:353ghz-eb-maps}
-\end{figure}
-%
-\section{Discussion}\label{sec:discussion}
-\begin{itemize}
-\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
-We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.
-
-\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.
-
-\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment.
-Motivation for defining radially compact kernels.
-We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.
-
-\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.
-
-\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
-
-\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking.
-For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.
-
-\end{itemize}
-%
-%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization.
-One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask.
-Mask apodization techniques should fail at low Nside.
-The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.

### 2017-09-14 article/sections/appendix.tex
updated path to figures in latex files

@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{complementary/convolution-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{complementary/convolution-err-bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/convolution-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/convolution-err-bb-spectrum-radial-cutoff.pdf}}
 \caption{The figure on the left and right depict the relative percentage difference between spectra derived from local convolution estimates of E \& B map and the reference spectra derived from full sky Healpix evaluations.

### 2017-09-14 article/sections/application_353ghz.tex
updated path to figures in latex files

@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz-b-mode-real-space-disc8apo3.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-real-space-disc8apo3.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-real-space-disc8apo3.pdf}}
 \caption{}

### 2017-09-14 article/sections/kernel_discussion.tex
updated path to figures in latex files

@@
 \centering
-\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
+\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
 \caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
@@
 \centering
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{I_ker_i_lat0_lon90.pdf}}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat90_lon0.pdf}}\\[-2ex]
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon0.pdf}}\\[-2ex]
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon30.pdf}}\\[-2ex]
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat80_lon30.pdf}}\\[-2ex]
+\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat0_lon90.pdf}}
 \caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
@@
 \centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{fm2_rad_ker_fn_of_ellmax.pdf}}
+\subfigure[]{\includegraphics[width=1.0\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
+\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
+\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
 \caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.

### 2017-09-14 article/sections/numerical_implementation.tex
updated path to figures in latex files

@@
 \centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{bmap-diff.pdf}}
+\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/emap-healpix.pdf}}
+\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/emap-2beta.pdf}}
+\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/emap-diff.pdf}}
+\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-healpix.pdf}}
+\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-2beta.pdf}}
+\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-diff.pdf}}
 \caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bb-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
 \caption{}
@@
 \centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{e-umap-diff.pdf}}
+\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
+\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
+\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
+\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
+\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
+\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}
 
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{b-umap-diff.pdf}}
+\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-healpix.pdf}}
+\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-2beta.pdf}}
+\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-diff.pdf}}
+\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-healpix.pdf}}
+\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-2beta.pdf}}
+\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-diff.pdf}}
 \caption{}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{bqu-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/equ-spectra-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
 \caption{}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{number_of_disc_pixels.pdf}}
+\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
 \caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.

### 2017-09-14 article/sections/discussion.tex
updated to conclusions and numerical implementation section

@@
 
-\item Small field experiments like BICEP, implicitly implement such radial cut offs due to limited survey area.
+\item Small field experiments like BICEP implement such radial cut offs due to limited survey area.
 
 \item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
+
+\item \textit{Total convolution methods:} Since the convolution kernels can be thought of as effective beams for polarization maps, it may be possible to use total convolution methods to construct E and B mode maps.
+
+\item{Separate Q and U maps for E and B:} We have presented kernels which allow for decomposition of the total Stokes Q and U parameters to those corresponding to E and B modes.
+This could be potentially interesting, since one can now work with E and B modes foregrounds and their separations separately.
+\comment{But is there an issue with doing this in the standard method which involves going through the process of generating E and B modes ?}
 

### 2017-09-14 article/sections/numerical_implementation.tex
updated to conclusions and numerical implementation section

@@
 
-As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}).
-For a sufficiently high maximum multipole $\ell_{\rm max}$, the lowest multipole being fixed at $\ell_{\rm min}=2$, the maximum the radial kernel reaches near the vicity of the diametrically opposite end can be significantly smaller than global maxima of the radial kernel.
-This suggests that for sufficiently high resolution CMB maps (${\rm NSIDE} >32$), having high multipole information, it may suffice to restrict the convolution over the Stoke parameters Q \& U (to deduce either the scalar E \& B maps or pure Stokes Q \& U corresponding to either of the two scalar modes) to a local region around the central pixel.
-The locality of the region is quantified by the non-locality parameter $\beta_o$, which is a function of the maximum multipole accessible in the Stokes maps.
+As discussed in \sec{sec:radial_locality}, the radial kernels decay ($\propto ~ \beta^{-1.5}$) as the distance from the central pixel increases, but they begin to increase on approaching the diametrically opposite position ($\beta \rightarrow \pi$)  as seen in \fig{fig:rad_ker_decay}.
+For a map containing sufficiently high multipole $\ell_{\rm max}$ information,  the local maxima the radial kernel attains in the vicinity of the diametrically opposite end is significantly smaller than global maxima.
+This suggests that for sufficiently high resolution CMB maps, it may suffice to restrict the convolution over the Stoke parameters Q \& U to a local region around the central pixel.
+The size of this local region is determined by the non-locality parameter $\beta_o$.
+\revisit{It is important to note that this claim is valid only while working with maps that are fairly homogeneous.
+In the case of foregrounds for example, though the radial kernel falls off, a strong foreground very far from the central pixel may still make significant contribution to the local definition of E and B modes.}
 
+In this section we study the effects of localizing the convolution kernels on the inferred E and B mode maps and their power spectra.
 We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
@@
 $f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$ as discussed in \app{sec:asymptotic_f}.
+${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$, given in \app{sec:asymptotic_f}.
 As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
 We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
-Given these  inputs we evaluate the convolution kernel as simple Reimann sums.
+Given these  inputs we evaluate the convolutions as simple Reimann sums.
 We repeat this procedure for each pixel on the Healpix map.
 
-For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-\revisit{We use the CMB spectra for some fiducial cosmology.
-This work  only deals with lensing B-mode spectra.} To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
+\revisit{We use the CMB spectra for the fiducial cosmology.
+Specifically we restrict our analysis on lensing generated B-mode spectra.}  For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
+To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
 Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
@@
 We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are in principle equivalent to carrying out the convolution over the full sphere (i.e.
+Note that the Healpix evaluations are equivalent to carrying out the convolution over the full sphere (i.e.
 $\beta_o=\pi$).

### 2017-09-15 article/sections/application_353ghz.tex
updated the introductory discussion in the numerical implementation section

@@
-\subsection{Application of Planck 353 Ghz polarization maps}
+%--------------------------------------------------------
+%--------------------------------------------------------
+\subsection{Application to Planck 353 Ghz polarization maps}
 %
@@
 %
+%--------------------------------------------------------
+%--------------------------------------------------------
+
+%--------------------------------------------------------
+%--------------------------------------------------------
+\subsection{Scaling and future prospects}
+%
+\begin{figure}[!h] 
+\centering
+\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
+\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
+The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
+\label{fig:disc_rad_healpix_numpix}
+\end{figure}
+%
+%--------------------------------------------------------
+%--------------------------------------------------------

### 2017-09-15 article/sections/kernel_discussion.tex
updated the introductory discussion in the numerical implementation section

@@
-\section{Visualizing the real space operators} \label{sec:visualize_operator}
+\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
 We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
@@
 
-\section{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
+\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
 It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
@@
 We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm max}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
+We find that the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
 

### 2017-09-15 article/sections/numerical_implementation.tex
updated the introductory discussion in the numerical implementation section

@@
 In this section we study the effects of localizing the convolution kernels on the inferred E and B mode maps and their power spectra.
-We have developed a Python script to evaluate these local convolution over Stokes Q \& U parameters.
-To evaluate the convolution kernel (\eq{eq:qu2eb_convolution}), we precompute the radial part of the kernel ( $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$.
-Specifically, we use the python routine {\textit scipy.special.lpmn} to evaluate the associated Legendre polynomial functions, which are needed to evaluate the radial kernels.
-$f(\beta)$ is simply evaluated by calculating the multipole sum in \eq{eq:rad_ker_queb}.
-${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta))$ are estimated by evaluating the sum in \eq{eq:f2_rad_ker}, where we take care to use the limiting forms of the functions ${}_{\pm 2}f_{\ell}(\beta)$ in the vicinity of $\beta=0,\pi$, given in \app{sec:asymptotic_f}.
+We have developed a Python script to compute these local convolution over Stokes Q \& U parameters.
+To carry out this numerical exercise, we pre-compute the radial part of the kernels, namely the function: $f(\beta), {}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta)$.
+We use the python routine {\textit scipy.special.lpmn} for the numerical evaluation of the associated Legendre polynomial functions required to compute the respective radial kernels following equations \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker}.
+Specifically while computing the functions ${}_{+2}f(\beta) ~\&~ {}_{-2}f(\beta)$ in the vicinity of $\beta=0~\&~\pi$, we use the limiting forms of the respective functions given in \app{sec:asymptotic_f}.
 As the next step, for each pixel on the Healpix map we get the pixel numbers of all the neighboring pixels lying within radius of $r_{\rm cutoff}$ from the central pixel using the Healpix routine {\textit query\_disc}.
-We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are then used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
+We then use the {\textit pix2ang} function of Healpix to get the angular coordinates of the central $(\theta_o,\phi_o)$ and its surrounding pixels $(\theta_i,\phi_i)$, which are used to calculate the corresponding Euler angles using \eq{eq:fn_euler}.
 Given these inputs we evaluate the convolutions as simple Reimann sums.
-We repeat this procedure for each pixel on the Healpix map.
+We repeat this procedure for each pixel on the Healpix map to yielding the resultant maps (E ,B, Q, U).
 
-\revisit{We use the CMB spectra for the fiducial cosmology.
-Specifically we restrict our analysis on lensing generated B-mode spectra.}  For the results presented in the following sub-sections we work with CMB maps at Healpix resolution of ${\rm NSIDE}=64$, unless specified otherwise.
-To understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
-Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=30^{\circ}$.
-We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
-Note that the Healpix evaluations are equivalent to carrying out the convolution over the full sphere (i.e.
+\revisit{We use the CMB spectra for a fiducial cosmology and restrict our analysis on lensing induced B-mode spectra.}  For the results presented in the following sections we carry out our analysis on CMB maps at Healpix resolution of ${\rm NSIDE}=64$.
+In order to understand the effects of restricting the convolution to a local neighbourhood, we evaluate these convolutions on discs with progressively smaller radii surrounding the central pixel.
+Specifically the non-locality parameter for a NSIDE=64 map is $\beta_o=22.5^{\circ}$.
+\revisit{We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
+}We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
+Note that the Healpix evaluations are equivalent to carrying out the convolutions over the full sphere (i.e.
 $\beta_o=\pi$).
-We compare the spectra derived from all these maps to those derived from the reference maps to quantify the effect of the imposed radial cutoff on the convolution integrals.
+We compare these maps to the reference maps and their respective spectra, to quantitatively understand the effect of the imposed radial cutoff on the convolutions.
 
@@
 %--------------------------------------------------------
-\subsection{Constructing E \& B maps from local convolutions on Stokes Q \& U maps}
+\subsection{Constructing E \& B maps using local convolutions}
 
@@
 %--------------------------------------------------------
-\subsection{Extracting Equ and Bqu maps}
+\subsection{Separating Stokes Q \& U maps corresponding to E \& B modes of polarization}
 %
@@
 %--------------------------------------------------------
-\subsection{Scaling and future prospects}
-%
-\begin{figure}[!h] 
-\centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
-\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$.
-The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
-\label{fig:disc_rad_healpix_numpix}
-\end{figure}
-%
+\subsection{Multipole filtering using spatial convolutions}
 %--------------------------------------------------------

### 2017-09-18 article/sections/numerical_implementation.tex
First update to numerical implementation section of the paper : 18Sep2017

@@
 \revisit{We impose radial cutoffs of $r_{\rm cutoff}=[2\beta_0,\beta_o,0.5\beta_o,0.25\beta_o]$ with an apodization of 3 degrees having a cosine squared profiles on the edges of the discs.
-}We also evaluate the corresponding maps using standard Healpix routines and use these as reference maps for this exercise.
+}We also evaluate the corresponding maps using standard full sky Healpix routines and use these as reference maps for this exercise.
 Note that the Healpix evaluations are equivalent to carrying out the convolutions over the full sphere (i.e.
@@
 \subsection{Constructing E \& B maps using local convolutions}
-
+Here we present the results of evaluating the local convolution given in \eq{eq:op_qu2eb}, to derive E \& B mode maps given maps of Stokes Q \& U.
+The resultant maps are depicted in \fig{fig:eb-maps-compare}.
+Specifically the left column depicts the reference E \& B maps derived using Healpix, the middle column depicts the E \& B mode maps derived from local convolutions restricted to $2\beta_o$ and difference between these maps is depicted in the right column.
+The differences between these maps are observed to be large near the polar caps, however they are significantly smaller in the band around the equator.
+Further note that the differences seen around the equator are dominated by large scale modes, in contrast to the polar caps where one even observes small scale fluctuations.
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 {\textit Middle:} E \& B mode maps derived using $r_{\rm cutoff}=2\beta_o$.
-{\textit Right:} Difference between the maps shown in the left and middle columns.
-Note that the differences maps are primarily due to differences in the recovery of large scale modes.}
+The color scale is saturated to that of the respective reference maps.
+{\textit Right:} Difference between the maps shown in the left and middle columns.}
 \label{fig:eb-maps-compare}
@@
 %
+
+Next we compute the power spectra of these local E \& B maps and compare them to the spectra derived from the reference maps.
+The results of this exercise are summarized in \fig{fig:eb-spectra_rad_cutoff}.
+We note that when the radial cutoff is set much below the non-locality parameter as in $r_{\rm cutoff}=0.25 \beta_o$, the spectra differ from the reference spectra by more the cosmic variance.
+However on increasing the radial cutoff to only $0.5\beta_o$, the differences at most multipoles reduce to being comparable to the cosmic variance.
+On further increasing the radial cutoff to $\beta_o$ and $2 \beta_o$, the difference at most multipoles further reduce to levels of 0.5 cosmic variance or in absolute terms the differences are at the level of 2\%.
+Also note that the improvement while transitioning from $r_{\rm cutoff}=\beta_o$ to $r_{\rm cutoff}=2 \beta_o$ are not as significant
+as seen while increasing the $r_{\rm cutoff}$ to $\beta_o$. This is can be understood as a consequence of the rapidly decaying nature of the radial kernels we discussed in \sec{sec:radial_locality}.
+
+At first glance, the above remarks seem to hold true only for the E mode spectra, since the errors in the B mode spectra seem to be significantly larger as seen in the middle row of \fig{fig:eb-spectra_rad_cutoff}.
+We understand that the higher error in the B mode spectra is primarily a combined effect of the low amplitude of the B mode spectrum as compared to the E mode spectrum and limited numerical accuracy of our simple convolution algorithm.
+We ran a number of tests to confirm these as reasons for the observed discrepant behaviour.
+We exchanged the E and B mode spectra, \revisit{(taking care to set $C_{\ell}^{TE}=0$)} and noted that the trends observed in the error plots are reversed, clearly indicating a dependence on the amplitude of the spectrum.
+We noted that the polar caps were particularly error prone, as seen in \fig{fig:eb-maps-compare}.
+We excised these error prone regions, specifically masking portions of the maps with $|b|>30^{\circ}$ to find that the errors on the B mode spectra revert to having very similar structure as that of the E mode spectra, as seen in the bottom row of \fig{fig:eb-spectra_rad_cutoff}.
+Finally we modified the
 %
@@
 \centering
+%\vspace{-5cm}
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
-\caption{}
-\label{fig:eq-spectra_rad_cutoff}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
+\caption{\textit{Top:} The figures on left and right depict the E mode spectra and the B mode spectra respectively.
+\textit{Middle:} These figures depict the relative percentage difference between the spectra derived from full sky, locally evaluated E \& B  maps and the reference spectra.
+\textit{Bottom:} These figures depict the same results as shown in the middle row, except that the regions with $|b|>30^\circ$ of the maps have been masked for this analysis.
+The colors indicate the spectra derived from imposing different radial cutoff as indicated by the legends.
+The gray bands indicate the cosmic variance scatter around the fiducial spectra.
+The dashed horizontal black lines mark the 2\% error.}
+\label{fig:eb-spectra_rad_cutoff}
 \end{figure}

### 2017-09-19 article/sections/introduction.tex
reorganized the introduction sections ; completed section on numerical implementation qu2eb

@@
 We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.
-
-\section{E/B description of CMB polarization} \label{sec:pol-intro}
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-\subsection{Polarization primer}\label{sec:pol-primer}
-The CMB polarization is measured in terms of Stokes Q and U parameters. These measurements can be combined to form the complex spin 2 polarization field as follows,
-%
-\beqry \label{eq:spin-pol}
-_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
-\eeqry
-%
-Since these measured quantities depend on the local coordinate system making it is cumbersome to work with them.
-To overcome this, one describes the CMB polarization field in terms of a scalar field denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
-These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ through the following relation,
-%
-\beq \label{eq:ebdef}
-\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  +  \eth^2 _{- 2}X(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
-\eeq
-%
-where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively.
-These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions.
-The spin raising and lowering operators have the following properties \cite{goldberg67},
-%
-\beqrys \label{eq:spinopylm} 
-\eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
-\bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
-\eeqrys
-%
-where $_s Y_{lm}(\hat{n}) $ denote the spin-s spherical harmonics.
-
-Using \eq{eq:ebdef} and the properties of the spin raising and lowering operators given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are defined via the following set of equations,
-%
-\beq \label{eq:pseudo}
-\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
-\eeq
-%
-where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the spin harmonic coefficients of the polarization field through the following equations,
-%
-\beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}X_{\ell m} + _{-2}X_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}X_{\ell m} - _{-2}X_{\ell m} \Big] 
-\eeq
-%
-In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following expressions, 
-%
-\beq \label{eq:pseudo}
-E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
-\eeq
-%
-Note that the two set of fields $\mathcal{E}/\mathcal{B}$ and $E/B$ differ, since their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
-\filbreak

### 2017-09-19 article/sections/numerical_implementation.tex
reorganized the introduction sections ; completed section on numerical implementation qu2eb

@@
 We ran a number of tests to confirm these as reasons for the observed discrepant behaviour.
-We exchanged the E and B mode spectra, \revisit{(taking care to set $C_{\ell}^{TE}=0$)} and noted that the trends observed in the error plots are reversed, clearly indicating a dependence on the amplitude of the spectrum.
-We noted that the polar caps were particularly error prone, as seen in \fig{fig:eb-maps-compare}.
-We excised these error prone regions, specifically masking portions of the maps with $|b|>30^{\circ}$ to find that the errors on the B mode spectra revert to having very similar structure as that of the E mode spectra, as seen in the bottom row of \fig{fig:eb-spectra_rad_cutoff}.
-Finally we modified the
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}} \\[-2ex]
 \caption{\textit{Top:} The figures on left and right depict the E mode spectra and the B mode spectra respectively.
@@
 %
+We exchanged the E and B mode spectra, \revisit{(taking care to set $C_{\ell}^{TE}=0$)} and noted that the trends observed in the error plots are reversed, clearly indicating a dependence on the amplitude of the spectrum.
+We noted that the polar caps were particularly error prone, as seen in \fig{fig:eb-maps-compare}.
+We excised these error prone regions, specifically masking portions of the maps with $|b|>30^{\circ}$ to find that the errors on the B mode spectra revert to having very similar structure as that of the E mode spectra, as seen in the bottom row of \fig{fig:eb-spectra_rad_cutoff}.
+Finally we modify the use of standard Healpix routines to mimic the local convolution E \& B construction (see \app{sec:convolution_err} for details).
+The results from this exercise also concur with our understanding of the discrepant behaviour for the B-mode spectrum.
 %--------------------------------------------------------
@@
 \centering
-\subfigure[E-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
-\subfigure[E-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
-\subfigure[E-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
-\subfigure[E-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
-\subfigure[E-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
-\subfigure[E-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}
+\subfigure[E Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
+\subfigure[E Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
+\subfigure[E Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
+\subfigure[E U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
+\subfigure[E U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
+\subfigure[E U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}
 
-\subfigure[B-Q map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-healpix.pdf}}
-\subfigure[B-Q map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-2beta.pdf}}
-\subfigure[B-Q map difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-diff.pdf}}
-\subfigure[B-U map Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-healpix.pdf}}
-\subfigure[B-U map local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-2beta.pdf}}
-\subfigure[B-U map difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-diff.pdf}}
-\caption{}
+\subfigure[B Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-healpix.pdf}}
+\subfigure[B Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-2beta.pdf}}
+\subfigure[B Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-diff.pdf}}
+\subfigure[B U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-healpix.pdf}}
+\subfigure[B U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-2beta.pdf}}
+\subfigure[B U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-diff.pdf}}
+\caption{The top two rows depict the Stokes Q \& U maps  respectively corresponding to E mode of polarization while the bottom two rows depict  the Stokes Q \& U maps  respectively corresponding to the  B modes of polarization.
+\textit{Left:} Stokes Maps derived using Healpix.
+\textit{Middle}: Stokes maps derived using local convolution with $r_{\rm cutoff} = 2 \beta_o$.
+\textit{Right:} Difference between the maps derived using the two different methods.}
 \label{fig:equ-bqu-maps-compare}
@@
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}\\[-5ex]
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}

### 2017-09-19 article/sections/real_space_formalism.tex
reorganized the introduction sections ; completed section on numerical implementation qu2eb

@@
+%--------------------------------------------------------
+%--------------------------------------------------------
+\section{E/B description of CMB polarization} \label{sec:pol-intro}
+%--------------------------------------------------------
+\subsection{Polarization primer}\label{sec:pol-primer}
+The CMB polarization is measured in terms of Stokes Q and U parameters. These measurements can be combined to form the complex spin 2 polarization field as follows,
+%
+\beqry \label{eq:spin-pol}
+_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
+\eeqry
+%
+Since these measured quantities depend on the local coordinate system making it is cumbersome to work with them.
+To overcome this, one describes the CMB polarization field in terms of a scalar field denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
+These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ through the following relation,
+%
+\beq \label{eq:ebdef}
+\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  +  \eth^2 _{- 2}X(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
+\eeq
+%
+where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively.
+These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions.
+The spin raising and lowering operators have the following properties \cite{goldberg67},
+%
+\beqrys \label{eq:spinopylm} 
+\eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
+\bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
+\eeqrys
+%
+where $_s Y_{lm}(\hat{n}) $ denote the spin-s spherical harmonics.
+
+Using \eq{eq:ebdef} and the properties of the spin raising and lowering operators given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are defined via the following set of equations,
+%
+\beq \label{eq:pseudo}
+\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
+\eeq
+%
+where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the spin harmonic coefficients of the polarization field through the following equations,
+%
+\beq\label{eq:x2eb}
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}X_{\ell m} + _{-2}X_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}X_{\ell m} - _{-2}X_{\ell m} \Big] 
+\eeq
+%
+In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following expressions, 
+%
+\beq \label{eq:pseudo}
+E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
+\eeq
+%
+Note that the two set of fields $\mathcal{E}/\mathcal{B}$ and $E/B$ differ, since their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+
+%--------------------------------------------------------
+%--------------------------------------------------------
 \subsection{Matrix notation} \label{sec:mat_pol_intro}

### 2017-09-19 article/sections/appendix.tex
updated the path to the figure files which was necessary after figure reorganization

@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/convolution-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/convolution-err-bb-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/healpix_local/convolution-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{supplementary/healpix_local/convolution-err-bb-spectrum-radial-cutoff.pdf}}
 \caption{The figure on the left and right depict the relative percentage difference between spectra derived from local convolution estimates of E \& B map and the reference spectra derived from full sky Healpix evaluations.

### 2017-09-19 article/sections/numerical_implementation.tex
updated the path to the figure files which was necessary after figure reorganization

@@
 \centering
-\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/emap-healpix.pdf}}
-\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/emap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/emap-diff.pdf}}
-\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-healpix.pdf}}
-\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-2beta.pdf}}
-\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/bmap-diff.pdf}}
+\subfigure[E-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-healpix.pdf}}
+\subfigure[E-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-2beta.pdf}}
+\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/emap-diff.pdf}}
+\subfigure[B-mode Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-healpix.pdf}}
+\subfigure[B-mode local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-2beta.pdf}}
+\subfigure[Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2eb/bmap-diff.pdf}}
 \caption{{\textit Left:} Reference E \& B mode maps derived using Healpix.
@@
 %\vspace{-5cm}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/eqmask/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}} \\[-2ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}}\\[-6ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/eqmask/relative-percentage-err-ee-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2eb/eqmask/relative-percentage-err-bb-spectrum-radial-cutoff.pdf}} \\[-2ex]
 \caption{\textit{Top:} The figures on left and right depict the E mode spectra and the B mode spectra respectively.
@@
 \subsection{Separating Stokes Q \& U maps corresponding to E \& B modes of polarization}
+Here 
 %
@@
 \centering
-\subfigure[E Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-healpix.pdf}}
-\subfigure[E Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-2beta.pdf}}
-\subfigure[E Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-qmap-diff.pdf}}
-\subfigure[E U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-healpix.pdf}}
-\subfigure[E U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-2beta.pdf}}
-\subfigure[E U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/e-umap-diff.pdf}}
+\subfigure[E Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-qmap-healpix.pdf}}
+\subfigure[E Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-qmap-2beta.pdf}}
+\subfigure[E Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-qmap-diff.pdf}}
+\subfigure[E U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-umap-healpix.pdf}}
+\subfigure[E U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-umap-2beta.pdf}}
+\subfigure[E U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-umap-diff.pdf}}
 
-\subfigure[B Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-healpix.pdf}}
-\subfigure[B Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-2beta.pdf}}
-\subfigure[B Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-qmap-diff.pdf}}
-\subfigure[B U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-healpix.pdf}}
-\subfigure[B U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-2beta.pdf}}
-\subfigure[B U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/b-umap-diff.pdf}}
+\subfigure[B Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-qmap-healpix.pdf}}
+\subfigure[B Q-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-qmap-2beta.pdf}}
+\subfigure[B Q-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-qmap-diff.pdf}}
+\subfigure[B U-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-umap-healpix.pdf}}
+\subfigure[B U-map: Local convolution]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-umap-2beta.pdf}}
+\subfigure[B U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-umap-diff.pdf}}
 \caption{The top two rows depict the Stokes Q \& U maps  respectively corresponding to E mode of polarization while the bottom two rows depict  the Stokes Q \& U maps  respectively corresponding to the  B modes of polarization.
@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/equ-spectra-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/bqu-spectra-radial-cutoff.pdf}}\\[-5ex]
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/equ-spectra-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/bqu-spectra-radial-cutoff.pdf}}\\[-5ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-equ-e-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
 \caption{}

### 2017-09-19 codes/modules/local_eb_kernel_masked.py
Included high res analysis ; modified module to work on small portions of the sky ; added python notebook to use this modified module to work with high res maps

@@ -1,0 +1,389 @@
+import numpy as np
+from scipy.special import lpmn as lpmn
+from scipy.interpolate import interp1d
+import healpy as h
+
+class real_space_queb_kernels(object):
+
+	def __init__(self,nside,tmin=0.,tmax=30.,maxlmax=1024,sampling=1024):
+		self.nside=nside
+		self.tmin=tmin
+		self.tmax=tmax
+		self.maxlmax=maxlmax
+		self.sampling=sampling		
+
+		self.npix=h.nside2npix(self.nside)
+		self.omega=4.*np.pi/self.npix
+
+		self.theta=np.linspace(tmin*np.pi/180.,tmax*np.pi/180.,self.sampling)
+		self.pl2=np.zeros((self.maxlmax+1,np.size(self.theta)),float)
+		self.taper=np.ones(self.theta.size,float)
+
+
+		for i in range(self.theta.size):
+			y,temp=lpmn(2,self.maxlmax,np.cos(self.theta[i]))
+			for l in range(self.maxlmax+1):
+				self.pl2[l,i]=y[2,l]
+
+#	-----------------------------------------------------------------------------------------------------------------------------------------
+#	Function called by other internal functions.
+	def gauss(self,x,sigma=180.):
+	    y=np.exp(-x**2./(2.*sigma*sigma))#/sqrt(2.*pi*sigma*sigma)
+	    return y
+
+	def return_euler_angles(self,nside,cpixel,discsize=180.,nest=False):
+		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
+
+		v=h.pix2vec(nside,cpixel,nest=nest)
+		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=True,fact=4,nest=nest)
+		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
+
+		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
+		beta=np.arccos(temp_beta)
+
+		n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
+    		da = np.cos(theta1)*np.cos(beta) - np.cos(theta2)
[…]

### 2017-09-20 article/sections/numerical_implementation.tex
updates to the notebook evaluating the high res analysis, added latitude position of the mask as a input variable

@@
 \subsection{Separating Stokes Q \& U maps corresponding to E \& B modes of polarization}
-Here 
+In this section we present the results of evaluating the local convolution given in \eq{eq:op_qu2equbqu}, to decompose the total Stokes Q and U parameters into those correspond to the E modes and B modes of polarization respectively.
+We reiterate that this procedure only relies on real space operation on the total Stokes Q and U maps and do not go through the process of constructing the E and B modes as is usually the case.
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
+\caption{\textit{Top:} The thick lines in the figure on left depicts the E mode spectra derived from pure E Stokes Q and U parameters derived for different radial cutoffs on the convolution, the thin lines depict the B mode spectra for the residual B modes.}
 \label{fig:equ-bqu-spectra_rad_cutoff}

### 2017-09-20 article/sections/discussion.tex
updates to the section qu2equbqu section in numerical miplementation ; added a set of new figures of the spectra derived from stokes maps for E and B derived from differencing the total from local Stokes Q U estimates corresponding to E and B

@@
 
+\item{The difference between the spectra derived from the local convolution maps and the reference spectra follow a definite pattern and maybe it possible to model this difference and correct for it.
+For this purpose one will have to model the two point correlation function for the E and B fields in terms of the Stokes Q and U maps.}
+
+\item{We have not addressed the E to B leakage issue in this work.}
+
 \end{itemize}

### 2017-09-20 article/sections/numerical_implementation.tex
updates to the section qu2equbqu section in numerical miplementation ; added a set of new figures of the spectra derived from stokes maps for E and B derived from differencing the total from local Stokes Q U estimates corresponding to E and B

--- 2017-09-19 article/sections/numerical_implementation.tex
@@
 \subsection{Separating Stokes Q \& U maps corresponding to E \& B modes of polarization}
-Here 
+In this section we present the results of evaluating the local convolution given in \eq{eq:op_qu2equbqu}, to decompose the total Stokes Q and U parameters into those correspond to the E modes and B modes of polarization respectively.
+We reiterate that this procedure uses real space operation on the total Stokes Q and U maps and does not go through the process of constructing the E and B modes as is usually the case.
+The resultant Stokes Q and U maps corresponding to the E mode are depicted in the first two rows while those corresponding to B modes are shown in the final two rows of \fig{fig:equ-bqu-maps-compare}.
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 %
+The local convolution maps depicted in this figure are computed using a radial cutoff of $r_{\rm cutoff }=2\beta_o$.
+Note that similar to observations of the previous section, the maps derived via local real space convolutions, suffer from having relatively higher error in the polar caps, while the differences in the  band around the equator are smaller and dominated by large scale modes.
 
+Next we compute the E and B mode spectra from the set of Stokes maps constructed using local convolutions with different $r_{\rm cutoff}$.
+Note that for this exercise we use the standard Healpix routines for computing the spectra from the Stokes maps.
+The spectra derived from these local convolution maps and their difference with respect to the reference spectra are depicted in \fig{fig:equ-bqu-spectra_rad_cutoff}.
+The observations are similar to that made in the previous section: the difference with respect to the reference spectra reduce on increasing the radial cutoff and reach 2\% levels at most multipoles for the maximum radial $r_{\rm cutoff} =2 \beta_o$ used in this analysis.
 %
-\begin{figure}[!h] 
+\begin{figure}[!t] 
 \centering
@@
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-b-spectrum-radial-cutoff.pdf}}
-\caption{}
+\caption{\textit{Top:} The thick lines in the figure on left depicts the E mode spectra derived from pure E Stokes Q and U maps derived using different radial cutoffs, while the thin lines depict the residual B mode power.
+The figure on the right depict the same except that the thick lines now depict the B mode spectra while the thin lines show the residual E mode power.
+\textit{Bottom:} The figure on the left and right depict the difference between the reference spectra and those derived from local convolution maps for different $r_{\rm cutoff}$ imposed on the convolution.
+In all the panels the color of the lines indicate the radial cutoff as indicated by the legend and the gray band marks the cosmic variance around the fiducial spectra.}
 \label{fig:equ-bqu-spectra_rad_cutoff}
@@
 %
+In particular here we note that the B-mode residue in the Stokes Q \& U maps corresponding to E-modes is much smaller as compared to the E-mode residue in the Stokes Q \& U maps  computed for the B-modes of polarization.
+At all multipoles the B-mode residual power is below the lensing B-modes.
+The E-mode residual power at low multipoles is almost fully intact.
+
+Motivated by these observations we also compute the Stokes Q \& U maps corresponding to B-modes of polarization by simply subtracting the Stokes Q \& U maps corresponding to E-mode from the total Stoker Q \& U maps.
+For completeness we also compute the Stokes Q \& U maps corresponding to E-mode in an analogous manner.
+We carry out a spectral study on these Stokes Q \& U maps corresponding to E \& B modes, computed using this alternate method.
+The results of the spectral analysis are summarized in \fig{fig:dbqu-spectra_rad_cutoff}.
+%
+\begin{figure}[!t] 
+\centering
+%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dequ-spectra-radial-cutoff.pdf}}
+%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dbqu-spectra-radial-cutoff.pdf}} \\[-5ex]
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-equ-de-spectrum-radial-cutoff.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-db-spectrum-radial-cutoff.pdf}}
+\caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}.
+The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\equ=\fqu-\fqu_{Local}^B$, $\bqu=\fqu-\fqu_{Local}^{E}$.}
+\label{fig:dbqu-spectra_rad_cutoff}
+\end{figure}
+%
+We observe that the the low multipole spectral behavior is not affected by this alternate construction of pure Stokes Q \& U maps.
+The high multipole behavior is significantly altered as can be seen by comparing \fig{fig:dbqu-spectra_rad_cutoff} with lower panels of \fig{fig:equ-bqu-spectra_rad_cutoff}.
+The relative percentage difference with respect to the reference spectra is seen to lie well within 2\% error for sufficiently high multipoles for all radial cutoff $r_{\rm cutoff}$.
 %--------------------------------------------------------

### 2017-09-20 article/sections/numerical_implementation.tex
added preliminary text/motication to multipole filtering section and some points to the discussions

@@
 \caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}.
-The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\equ=\fqu-\fqu_{Local}^B$, $\bqu=\fqu-\fqu_{Local}^{E}$.}
+The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\fqu_{E}=\fqu-\fqu_{Local}^B$, $\fqu_{B}=\fqu-\fqu_{Local}^{E}$.}
 \label{fig:dbqu-spectra_rad_cutoff}
@@
 \subsection{Multipole filtering using spatial convolutions}
+As we have seen in the previous section that recovering large scale modes using local convolutions is not possible.
+The small angular scales however are reliably recovered.
+However the local convolution methods can be used to recover competent spectra.
+Many CMB experiments cannot access the large angle modes due to limited sky coverage.
+Often the large angle analysis is deal with in pixel space owing to the non-Gaussianity of the likelihood functions.
+With all these as motivations we study how the radial filters are modified by removing the large scale modes.
+We try to understand how removing large scale modes effects the locality of the E and B map estimators.
+We demonstrate that it is possible to get filtered maps by using the modifying the radial filter.
 %--------------------------------------------------------

### 2017-09-21 article/sections/numerical_implementation.tex
added new figures to 353Ghz application ; minor edits to article

@@
 We reiterate that this procedure uses real space operation on the total Stokes Q and U maps and does not go through the process of constructing the E and B modes as is usually the case.
-The resultant Stokes Q and U maps corresponding to the E mode are depicted in the first two rows while those corresponding to B modes are shown in the final two rows of \fig{fig:equ-bqu-maps-compare}.
 %
@@
 \subfigure[E U-map: Difference]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/e-umap-diff.pdf}}
-
 \subfigure[B Q-map: Healpix]{\includegraphics[width=0.31\columnwidth]{simulated/qu2equbqu/b-qmap-healpix.pdf}}
@@
 %
+The resultant Stokes Q and U maps corresponding to the E mode are depicted in the first two rows while those corresponding to B modes are shown in the final two rows of \fig{fig:equ-bqu-maps-compare}.
 The local convolution maps depicted in this figure are computed using a radial cutoff of $r_{\rm cutoff }=2\beta_o$.
 Note that similar to observations of the previous section, the maps derived via local real space convolutions, suffer from having relatively higher error in the polar caps, while the differences in the  band around the equator are smaller and dominated by large scale modes.
-
-Next we compute the E and B mode spectra from the set of Stokes maps constructed using local convolutions with different $r_{\rm cutoff}$.
-Note that for this exercise we use the standard Healpix routines for computing the spectra from the Stokes maps.
-The spectra derived from these local convolution maps and their difference with respect to the reference spectra are depicted in \fig{fig:equ-bqu-spectra_rad_cutoff}.
-The observations are similar to that made in the previous section: the difference with respect to the reference spectra reduce on increasing the radial cutoff and reach 2\% levels at most multipoles for the maximum radial $r_{\rm cutoff} =2 \beta_o$ used in this analysis.
 %
@@
 %
+Next we compute the E and B mode spectra from the set of Stokes maps constructed using local convolutions with different $r_{\rm cutoff}$.
+Note that for this exercise we use the standard Healpix routines for computing the spectra from the Stokes maps.
+The spectra derived from these local convolution maps and their difference with respect to the reference spectra are depicted in \fig{fig:equ-bqu-spectra_rad_cutoff}.
+The observations are similar to that made in the previous section: the difference with respect to the reference spectra reduce on increasing the radial cutoff and reach 2\% levels at most multipoles for the maximum radial $r_{\rm cutoff} =2 \beta_o$ used in this analysis.
 In particular here we note that the B-mode residue in the Stokes Q \& U maps corresponding to E-modes is much smaller as compared to the E-mode residue in the Stokes Q \& U maps  computed for the B-modes of polarization.
@@
 \caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}.
-The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\fqu_{E}=\fqu-\fqu_{Local}^B$, $\fqu_{B}=\fqu-\fqu_{Local}^{E}$.}
+The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations:  $[Q,U]_{E}=[Q,U]-[Q,U]_{Local}^B$ ; $[Q,U]_{B}=[Q,U]-[Q,U]_{Local}^{E}$.}
 \label{fig:dbqu-spectra_rad_cutoff}

### 2017-09-22 article/sections/application_353ghz.tex
updates for 21sep2017

@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-real-space-disc8apo3.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-real-space-disc8apo3.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix_filter_lmin50_lmax256_nside128.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix_filter_lmin50_lmax256_nside128.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-realspace_disc15d_apo4d_lmin50_lmax256_nside128.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-realspace_disc15d_apo4d_lmin50_lmax256_nside128.pdf}}
 \caption{}

### 2017-09-22 article/sections/discussion.tex
added preliminary text/motication to multipole filtering section and some points to the discussions
updates for 21sep2017

@@
 \begin{itemize}
+
+\item Many CMB experiments cannot access the large angle modes due to limited sky coverage.
+Often the large angle analysis is deal with in pixel space owing to the non-Gaussianity of the likelihood functions.
+With all these as motivations we study how the radial filters are modified by removing the large scale modes.
+We try to understand how removing large scale modes effects the locality of the E and B map estimators.
+We demonstrate that it is possible to get filtered maps by using the modifying the radial filter.
+
 \item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
@@
 
+\item{Poor sensitivity to large scale modes as the local estimated maps do no carry information from pixel which are further away than the radial cutoff.
+This should cause a compromise on spectral estimates of low multipoles, which correspond to large angular scales, much larger than radial cutoff.}
+
 \item{We have not addressed the E to B leakage issue in this work.}

### 2017-09-22 article/sections/numerical_implementation.tex
updates for 21sep2017

--- 2017-09-20 article/sections/numerical_implementation.tex
@@
 \caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}.
-The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\equ=\fqu-\fqu_{Local}^B$, $\bqu=\fqu-\fqu_{Local}^{E}$.}
+The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations:  $[Q,U]_{E}=[Q,U]-[Q,U]_{Local}^B$ ; $[Q,U]_{B}=[Q,U]-[Q,U]_{Local}^{E}$.}
 \label{fig:dbqu-spectra_rad_cutoff}
@@
 \subsection{Multipole filtering using spatial convolutions}
+As seen in the previous sections using local convolution methods to separate E and B modes does not allow the recovery of large scale modes.
+However we demonstrated that these local convolution methods can be used to recover competent spectra on small angular scales.
+In this section we demonstrate the construction of radial kernels which achieve the desired multipole filtering.
+The radial filters for the desired multipole filtering can be constructed by simply controlling the $\ell_{\rm min}$ \& $\ell_{\rm max}$ arguments of the functions $f(\beta,\ell_{\rm min},\ell_{\rm max})$ and ${}_{\pm 2}f(\beta,\ell_{\rm min},\ell_{\rm max})$.
+
+Altering $\ell_{\rm max}$ would necessitate updating $\beta_o$, hence we avoid doing that.
+In order to ensure that we are changing only one parameter, we focus on high pass filtering, which we achieve by altering $\ell_{\rm min}$.
+%
+\begin{figure}[!t]
+\centering
+\subfigure[]{\includegraphics[width=1.\columnwidth]{simulated/multipole_filter/f_rad_ker_fn_vary_lmin.pdf}}\\
+\subfigure[]{\includegraphics[width=0.48\columnwidth]{simulated/multipole_filter/fp2_rad_ker_fn_vary_lmin.pdf}}
+\subfigure[]{\includegraphics[width=0.48\columnwidth]{simulated/multipole_filter/fm2_rad_ker_fn_vary_lmin.pdf}}
+\caption{}
+\label{}
+\end{figure}
+%
+
+%
+\begin{figure}[!t]
+\centering
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/multipole_filter/eqmask/ee-spectrum-rteb-2beta_multipole_filtering.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/multipole_filter/eqmask/bb-spectrum-rteb-2beta_multipole_filtering.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/multipole_filter/eqmask/ee-spectrum-requ-2beta_multipole_filtering.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/multipole_filter/eqmask/bb-spectrum-rbqu-2beta_multipole_filtering.pdf}}
+\caption{}
+\label{}
+\end{figure}
+%
+
 %--------------------------------------------------------

### 2017-09-27 article/sections/numerical_implementation.tex
completed first pass at the multupole filtering section

@@
 \subsection{Multipole filtering using spatial convolutions}
-As seen in the previous sections using local convolution methods to separate E and B modes does not allow the recovery of large scale modes.
-However we demonstrated that these local convolution methods can be used to recover competent spectra on small angular scales.
-In this section we demonstrate the construction of radial kernels which achieve the desired multipole filtering.
-The radial filters for the desired multipole filtering can be constructed by simply controlling the $\ell_{\rm min}$ \& $\ell_{\rm max}$ arguments of the functions $f(\beta,\ell_{\rm min},\ell_{\rm max})$ and ${}_{\pm 2}f(\beta,\ell_{\rm min},\ell_{\rm max})$.
-
-Altering $\ell_{\rm max}$ would necessitate updating $\beta_o$, hence we avoid doing that.
-In order to ensure that we are changing only one parameter, we focus on high pass filtering, which we achieve by altering $\ell_{\rm min}$.
+ In this section we construct radial kernels which result in the desired multipole filtering, which can be achieved by simply controlling the $\ell_{\rm min}$ \& $\ell_{\rm max}$ arguments of the functions $f(\beta,\ell_{\rm min},\ell_{\rm max})$ and ${}_{\pm 2}f(\beta,\ell_{\rm min},\ell_{\rm max})$.
+\revisit{We reiterate that only the radial part of the convolution kernel encodes the multipole information, while the azimuthal part of the kernel is independent of multipoles.
+As seen in the previous sections, using local convolution methods to separate E and B modes does not allow the recovery of large scale modes.
  %
@@
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{simulated/multipole_filter/fm2_rad_ker_fn_vary_lmin.pdf}}
-\caption{}
-\label{}
+\caption{This figure depicts the all the radial kernels evaluated for different multipole filters.
+In the filtered kernels presented here, only $\ell_{\rm min}$ has been altered while the maximum multipole is held fixed at $\ell_{\rm max}=192$.
+The kernels have been multiplied by a factor of the argument $\beta$ to highlight the differences in the kernel at large angular separations $\beta$.}
+\label{fig:rad_ker_multipole_filter}
 \end{figure}
 %
-
+This can be understood as occurring due to the following reason: localizing the convolution kernel by introducing a radial cut off, progressively reduces the overlap of the kernels for pixels on increasing the separation between them.
+The overlap begins to significantly drop when angular distances are larger than $r_{\rm cutoff}$ and reaches a null at a separation of  $2 r_{\rm cutoff}$.
+Owing to this overlap reduction, the pixels at large separation in the constructed maps have a reduced correlation, specifically $C(\theta > 2 r_{\rm cutoff})=0$.}  This motivates the construction of high pass filters especially while working with local convolution maps.
+\comment{This should results in systematically lower power on large angular scales.
+This is observed for E mode spectra, but not quiet for B.
+Why is that ?}.
 %
@@
 \subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/multipole_filter/eqmask/bb-spectrum-rbqu-2beta_multipole_filtering.pdf}}
-\caption{}
-\label{}
+\caption{The top left and right panels depict the spectra  for E and B modes respectively, where each panel shows the spectra derived from filtered E \& B maps computed using local convolutions.
+The bottom left and right panels depict the same for spectra derived from $[Q,U]_E$ and $[Q,U]_B$ maps computed using local convolutions.
+The thin dashed lines in the bottom panels depict the residual power in the orthogonal modes.
+The vertical gray lines mark the low multipole cut off corresponding to $\ell_{min}=64$ and $\ell_{min}=128$.
+All local convolution have been performed with $r_{\rm cutoff} =2 \beta_o$.}
+\label{fig:filtered_spectra}
 \end{figure}
 %
+We construct radial filters with three different low multipole cut-offs: $\ell_{\rm min} =2,64 ~ \& ~ 128$ which are depicted in \fig{fig:rad_ker_multipole_filter}.
+The kernels have been purposefully multiplied by a factor of the angular distance $\beta$ to highlight the differences in the radial kernels for different multipole cut-offs.
+
+We use these different radial kernels to perform local convolutions on the simulated polarization maps.
+We use the same radial cut off: $r_{\rm cutoff}=2\beta_o$ for all the different filters, where $\beta_o=22.5^{\circ}$.
+The spectra from the filtered maps so constructed are depicted in \fig{fig:filtered_spectra}.
+Through these results we demonstrate how we can alter the radial part of the convolution kernels to get maps with the desired multipole filtering.
+\comment{What do you have to say about the jump in power for the B mode spectra at the low multipole cutoff, derived from filtered B maps ?}
 

### 2017-10-07 codes/modules/local_eb_kernel.py
added a new, more stable, euler angle routine to the modules local_eb_kernel.py.

@@ -51,6 +51,44 @@ class real_space_queb_kernels(object):
     		gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
 
 		return alpha,beta,gamma,spixel
+
+	def return_euler_angles_new(self,nside,cpixel,discsize=180.,nest=False):
+		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
+
+		v=h.pix2vec(nside,cpixel,nest=nest)
+		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=True,fact=4,nest=nest)
+		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
+
+		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
+		beta=np.arccos(temp_beta)
+
+		na = np.sin(theta2)*np.sin(phi2-phi1)
+		da = np.sin(theta1)*np.cos(theta2) - np.sin(theta2)*np.cos(theta1)*np.cos(phi2-phi1)
+    		alpha=np.arctan2(na,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+		ng = np.sin(theta1)*np.sin(phi2-phi1)
+		dg = -np.sin(theta2)*np.cos(theta1) + np.sin(theta1)*np.cos(theta2)*np.cos(phi2-phi1)
+    		gamma=np.arctan2(ng,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
+		return alpha,beta,gamma,spixel
+
+
+	def return_euler_ang(self,theta1,phi1,theta2,phi2):
+
+		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+		#temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
+		beta=np.arccos(temp_beta)
+
+		na = np.sin(theta2)*np.sin(phi2-phi1)
[…]

### 2017-10-08 codes/modules/return_rotated_kernel_healpix.py
added a module which computes the kernel by rotating the harmonic coefficients of the kernels specified at the poles

@@ -1,0 +1,108 @@
+import healpy as h
+import numpy as np
+
+def return_kernel_qu2eb(nside,lmax,pixi,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
+    
+    if sample_nside==-1:
+        sample_nside=nside
+
+    if norm=="Int":
+        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
+    else:
+        norm=1.
+
+    if use_coord:
+        pixi=h.ang2pix(nside,thetai,phii)
+        thetai,phii=h.pix2ang(nside,pixi)
+    else:
+        thetai,phii=h.pix2ang(nside,pixi)
+
+    almsize=h.Alm.getsize(lmax=lmax,mmax=lmax)
+    almr0=np.zeros(almsize,complex)
+    almi0=np.zeros(almsize,complex)
+
+    for i in range(almsize):
+        l,m=h.Alm.getlm(lmax,i)
+        if l>1 and m==2:
+            almr0[i]=complex(1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))*norm
+            almi0[i]=complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))*norm
+
+    h.rotate_alm(almr0,0.0,thetai,phii)
+    h.rotate_alm(almi0,0.0,thetai,phii)
+
+    mr=h.alm2map(almr0,sample_nside,lmax=lmax,mmax=lmax,verbose=False)
+    mi=h.alm2map(almi0,sample_nside,lmax=lmax,mmax=lmax,verbose=False)
+
+    return mr,mi
+    
+
+def return_kernel_I(nside,lmax,pixi=-1,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
+    '''
+    If pixi=-1 then the alms correspond to the kernel exactly at the pole. Else the alms are rotated to 
+    allign with the specified coordinate or the coordinate of the pixel.
+    '''
+    if sample_nside==-1:
+        sample_nside=nside
+
+    if norm=="Int":
+        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
+    else:
+        norm=1.
+
+    if use_coord:
+        pixi=h.ang2pix(nside,thetai,phii)
+        thetai,phii=h.pix2ang(nside,pixi)
+    else:
[…]

### 2017-10-09 article/sections/appendix.tex
completed first pass at the multupole filtering section
made some refinements to Sections 1 and 2 of the paper

@@
 %
+
+\subsection{Local convolution kernels using standing Healpix routines}\label{sec:rot_ker_healpix}
+Healpix uses Euler angles given in the z-y-z convention in contrast to the Euler angle definitions given in \sec{sec:euler} which are in z-y1-z2 convention.
+The two set of Euler angles are related by the following relations $(\alpha,\beta,\gamma)_{\rm z-y-z} = (\gamma,\beta,\alpha)_{\rm z-y1-z2}$ \cite{varshalovich}.
+We know the exact form of the harmonic coefficients for the kernels when they are centered around the north pole.
+Therefore the kernels centered around any arbitrary Healpix pixel $\hat{n}_i$ can be calculated by simply rotating these harmonic coefficients by the Euler angles $(0,\theta_i,\phi_i)_{\rm z-y-z}$ and synthesizing the kernel by evaluating the harmonic sum.
+\subsection{The correlation function and radial cut offs.}\label{sec:corrfn_rad_cutoff}

### 2017-10-09 article/sections/real_space_formalism.tex
updates to the notebook evaluating the high res analysis, added latitude position of the mask as a input variable
made some refinements to Sections 1 and 2 of the paper

@@
 %
-Since these measured quantities depend on the local coordinate system making it is cumbersome to work with them.
+Since these measured quantities depend on the local coordinate system, it is cumbersome to work with them.
 To overcome this, one describes the CMB polarization field in terms of a scalar field denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
-These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ through the following relation,
+These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ via the following relations,
 %
@@
 where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively.
-These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions.
+These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions (except that the B-modes have an odd parity, meaning that they change sign under reflection $\hat{n} \rightarrow -\hat{n}$.).
 The spin raising and lowering operators have the following properties \cite{goldberg67},
@@
 %
-where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the spin harmonic coefficients of the polarization field through the following equations,
+where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
 %
@@
 %
-Note that the two set of fields $\mathcal{E}/\mathcal{B}$ and $E/B$ differ, since their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
-
+Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
 %--------------------------------------------------------
@@
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of Healpix pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
+In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
 This representation will make transparent the derivation of the real space operators we discuss in the following sections.
@@
 \beq
-_sB= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
+{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
 \eeq
@@
 Note that this matrix is in general not a square matrix.
-Generally the number of columns is determined by the scheme used to discretely represent the sphere and the number of rows is set by the number of basis functions of interest (often determined the band limit).
+The number of rows is determined by the scheme used to discretely represent the sphere and the number of columns is set by the number of basis functions of interest (often determined by the band limit).
 
-We now define the different data vectors and their representation in real and harmonic space as follows,
+We now define the different polarization data vectors and their representation in real and harmonic space as follows,
 %
@@
 %
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed to avoid clutter in notation.
+The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed if favor of cleaner notation.
 
@@
 \bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,. 
+\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
 \eeqrys
 %
-Using the data vectors and the all the operators defined in this section we now write down, in compact notation, the forward and inverse relations between different representations of the polarization field as follows,
+where we have chosen the sign conventions so as to match those used in Healpix.
+Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
 %
@@
 \bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {_2B} * \tilde X  ~~;~~ \tilde X ={_2B}^{\dagger} * \bar X  \,, \\
+\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
 \tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {_0B} * \tilde S ~~;~~  \tilde S =  {_0B}^{\dagger} * \bar S \,.
-%\tilde X &=&  {_2B}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {_0B}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
+\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
+%\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
+%\bar{S} &=& {{}_0\mathcal{Y}}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
 %\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
@@
 \tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,.
+\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,
 \eeqrys
@@
 %
-Here it is important to note that these relations are exact in harmonic space.  \revisit{In the following sections our aim is to derive real space analogues of these harmonic space operators. }
+Note that the above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues of these harmonic space operators.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_i \equiv (\theta_i,\phi_i)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_j \equiv (\theta_j,\phi_j)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_i \equiv (\theta_i , \phi_i)$ and $\hat{n}_j \equiv (\theta_j, \phi_j)$,
+Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
+The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_0 \equiv (\theta_0 , \phi_0)$ and $\hat{n}_i \equiv (\theta_i, \phi_i)$,
 %
 \beqrys \label{eq:fn_euler}
-\cos(\beta) &=& \sin(\theta_i)\sin(\theta_j) \cos(\phi_i -\phi_j) + \cos(\theta_i)\cos(\theta_j) \,,\\
-\tan(\alpha) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_i) \cos(\beta) - \cos(\theta_j)} \,, \\
-\tan(\gamma) &=& \frac{\sin(\phi_i - \phi_j) \sin(\theta_i) \sin(\theta_j)}{\cos(\theta_j) \cos(\beta) - \cos(\theta_i)}\,,
+\tan{\alpha} &=& \frac{\sin{(\phi_i - \phi_0)} \sin{\theta_i}}{\sin{\theta_i}\cos{\theta_0} \cos{(\phi_i - \phi_0)} - \sin{\theta_0} \cos{\theta_i} } \,, \\
+\cos{\beta} &=& \sin{\theta_i}\sin{\theta_0} \cos{(\phi_i -\phi_0)} + \cos{\theta_i}\cos{\theta_0} \,,\\
+\tan{\gamma} &=& \frac{ - \sin{(\phi_i - \phi_0)} \sin{\theta_0}}{\sin{\theta_0}\cos{\theta_i} \cos{(\phi_i - \phi_0)} - \sin{\theta_i} \cos{\theta_0} } \,,
 \eeqrys
 %
-where $\beta$ denotes the angular distance between the two points $\hat{n}_i$ \& $\hat{n}_j$ on the sphere, while the angles $\alpha$ \& $\gamma$ define rotations which co-align the coordinate axes of the two local coordinate systems.
+where $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
+These angles can be understood in more physical terms as follows: the rotation $\alpha$ is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
+The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, the z-axes of the two coordinate systems are now parallel to each other.
+Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
+The simplest case is when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
+In this case it is easy to check by substituting these coordinate values in  \eq{eq:fn_euler} that the Euler angles are: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$.
 While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
 It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
+\revisit{While in following section we present results in terms of these Euler angles, the local kernels surrounding any pixel can be simply evaluated using standard Healpix functions.
+We give the details of this procedure in \app{sec:rot_ker_healpix}}.
 %--------------------------------------------------------
@@
 \beqrys
-\bar{S} &=& {_0B} *\tilde T^{-1}* {_2B^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {_0B} *\tilde T^{\dagger} {_2B^{\dagger}} *\bar T *\bar{P}   \,, \\
+\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
 &=&  \bar O *\bar{P} \,.
@@
 \beqrys
-\bar{O} &=& \frac{1}{2} {_0B} *\tilde T^{\dagger} *{_2B^{\dagger}} *\bar T \,, \\
+\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
 &=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
@@
 The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
+\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.} \eq{eq:qu2eb_convolution} can be written more concisely as follows,
+%
+\beqry
+[E + iB](\hat{n}_0) &=& \left[ \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} (\hat{n}_0, \hat{n}_i) \right]  \circ [Q+iU](\hat{n}_i) \\
+&=& 
+\eeqry
+%
 \rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
@@
 \beqry
-\bar{P} &=& \bar{T}^{-1} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{_2B} *\tilde T *{_0B^{\dagger}}\bar{S}   \\
+\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S}   \\
 &=&  \bar O^{-1} *\bar{S}
@@
 \beqry
-\bar{P}_E &=&  [\bar T^{-1} * {_2B} *\tilde T * \tilde O_E* \tilde T^{-1}* {_2B^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {_2B^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
+\bar{P}_E &=&  [\bar T^{-1} * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {{}_2\mathcal{Y}^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
 &=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {_2B}* \tilde T* \tilde O_B* \tilde T^{-1}* {_2B^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {_2B} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{_2B^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
+\bar{P}_B &=&  [\bar T^{-1}* {{}_2\mathcal{Y}}* \tilde T* \tilde O_B* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}* \bar T]*\bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
 &=&  \bar O_{B}*\bar{P} \,. \nonumber
@@
  %
-\beqry
+\beqry \label{eq:op_qu2equbqu}
 \bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber

### 2017-10-09 article/sections/introduction.tex
made some refinements to Sections 1 and 2 of the paper
made refinements to discussion on: Euler angles, the derivations of QU to EB operator and the derivations of EB to QU operator

@@
 In \sec{sec:visualize_operator} we evaluate the real space operators and present visualizations of these functions.
-Here we discuss the locality of the real space E \& B operators.
+Here we also discuss the locality of the real space E \& B operators.
 In \sec{sec:numerical_implementation} we implement these operators to evaluate E \& B  maps from the Stokes parameters Q \& U and compare these maps and their spectra from those derived using Healpix.
-We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.
+We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.\\ \\ \\
+
+\textbf{Some comments, questions and ideas that occurred to me while writing the draft:}
+\begin{enumerate}
+\item Using these local convolution can one now understand the E to B leakage occurring due to masking ?
+
+\item Healpix has rings at constant latitude.
+So the real space convolution is only perfect for pixels near the pole ?
+What happens when you consider pixels around any arbitrary pixel on a Healpix map, they are probably not arranged in rings.
+Maybe for this reason working with upgraded map works and finer pixels allow for a better approximation of rings around arbitrary pixels ??
+\end{enumerate}

### 2017-10-09 article/sections/real_space_formalism.tex
made refinements to discussion on: Euler angles, the derivations of QU to EB operator and the derivations of EB to QU operator

@@
 Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+We make this choice since the CMB spectra are more closely related to the fields E \& B.
 %--------------------------------------------------------
@@
 %
-\beqrys \label{eq:pol_data_relns}
+\begin{subequations} \label{eq:pol_data_relns}
+\beqry 
 \bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
@@
 %\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-\eeqrys
+\eeqry
+\end{subequations}
 %
@@
 \section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes parameters Q \& U to E \& B fields and vice versa.
-We also derive real space operators for directly(without first evaluating the E \& B field themselves) decomposing the Stokes  parameters Q \& U in to Stokes parameters that correspond to the E \& B fields respectively.
-We extensively make use of the matrix notation introduces in \sec{sec:mat_pol_intro} for these derivations.
+In this section we derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
+We also derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{\rm E} that correspond to E-modes and another vector \vp{\rm B} that corresponds to the B-modes of polarization, such that \vp{} = \vp{\rm E} + \vp{\rm B} (without ever evaluating the E \& B fields or their spherical harmonics).
+For carrying out these derivations we extensively use the matrix notation introduced in \sec{sec:mat_pol_intro}.
 
-All the results are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Generically, the Euler angles define the rotations that transforms the local cartesian coordinate system defined at the sphere position $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
-The Euler angles can be evaluated as the following functions of the angular coordinates of the points $\hat{n}_0 \equiv (\theta_0 , \phi_0)$ and $\hat{n}_i \equiv (\theta_i, \phi_i)$,
+\textit{Euler angles:} All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
+Owing to this fact we begin by briefly describing the Euler angles and present a way to think about them.
+The local cartesian coordinate system at any point on the sphere is defined such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east.
+The Euler angles define rotations that transforms the local cartesian coordinate system defined at the location $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
+The Euler angles can be evaluated using the following functions of the angular coordinates of the two locations $\hat{n}_0 \equiv (\theta_0 , \phi_0)$ and $\hat{n}_i \equiv (\theta_i, \phi_i)$,
 %
@@
 where $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-These angles can be understood in more physical terms as follows: the rotation $\alpha$ is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
-The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, the z-axes of the two coordinate systems are now parallel to each other.
+In more physical terms, these angles can be understood as follow: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
+The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, such that the z-axes of the two coordinate systems are parallel to each other.
 Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
@@
 \subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we discussed how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
+In \sec{sec:pol-primer} we described how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
 To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
 Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \revisit{\eq{eq:pol_data_relns}}, to write down an equation relating the real space vector of scalars $\bar{S}^{\dagger}=[E, B]$ to the polarization vector $\bar{P}^{\dagger}=[Q, U]$ as given below,
+We use the relations given in \eq{eq:pol_data_relns}, to write down an equation relating the real space vector of scalars \vs to the polarization vector \vp{} as given below,
 %
@@
 %
-where the symbol ${}_{0}Y_i$ is used to denote the matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
+where the symbol ${}_{0}Y_i$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
 Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
@@
  where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operators  are completely specified in terms of the complex function,
+Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
 %
@@
 where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Here we first note that this function does not depend on the Euler angle $\gamma$.
-This function has a part which depends only on the Euler angle $\alpha$ and this part of the function has no multipole dependence.
-except the factor of 2 which arises because the polarization field is a spin-2 field.
-The other part of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ depends only on the Euler angle $\beta$ and completely incorporates the multipole dependence of the function.
-$f(\beta,\ell_{\rm min},\ell_{\rm max})$ will be often be referred to as the radial kernel.
-The radial kernel is what determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
+Note that this kernel does not depend on the Euler angle $\gamma$.
+This local convolution kernel has a part which depends only on the Euler angle $\alpha$ which has no multipole dependence,  except the factor of 2 which arises because the polarization field is a spin-2 field.
+The remaining part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ which depends only on the Euler angle $\beta$ and completely incorporates any multipole $\ell$ dependence of the kernel.
+We will refer to $f(\beta,\ell_{\rm min},\ell_{\rm max})$ as the radial part of the kernel since it only depends on the distance from the location at which the scalar fields are being evaluated.
+The radial part of the kernel completely determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
 
-Finally the real space operator can be cast in this simple form,
+On simplifying \eq{eq:qu2eb_ker_1}, the local convolution kernel can be cast in this simple form,
 %
@@
 where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results are derived for the flat sky case and do not explicitly derive the radial kernel.} \comment{Maybe a discussion on this should be in the conclusions.}
+\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
 
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following expression,
+The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following convolution,
 %
 \beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
+\bmat E_i \\ B_i  \emat= \sum_{j=1}^{N_{\rm pix}}-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
 \eeq
 %
-where we have used the Einstein summation convention: repeated indices are summed over.
-The factor $\Delta \Omega$ accounts for the finite pixel size and is important for proper normalization.
-\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.} \eq{eq:qu2eb_convolution} can be written more concisely as follows,
+where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
+%\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
+The above equation can be expressed more concisely as follows,
 %
-\beqry
-[E + iB](\hat{n}_0) &=& \left[ \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} (\hat{n}_0, \hat{n}_i) \right]  \circ [Q+iU](\hat{n}_i) \\
-&=& 
-\eeqry
+\beq \label{eq:qu2eb_simple}
+[E + iB](\hat{n}_0) = \left( \left[ -\sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ [Q+iU] \right)(\hat{n}_0)\,, 
+\eeq
 %
+where $\circ$ denotes a convolution and the spherical harmonic function are to be evaluated at the $(\theta,\phi)=(\beta,\alpha)$.
+\revisit{Note that since the kernel does not depend on the Euler angle $\gamma$, the evaluation of the E and B maps is not critically dependent on the exact alignment of the rotated x and y axis with the local x and y axis, only the z-axis needs to be exactly aligned with the local z-axis.}
+
 \rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.}
+One can now think of constructing alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels.
+So shift this line to the section where we explore different radial functions.}
 %--------------------------------------------------------
@@
 \beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
+{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
 \eeq
 %
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
+%where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
 Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
@@
 \beq
-\bmat Q_i \\ U_i  \emat=-f(\beta_{ij})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
+\bmat Q_i \\ U_i  \emat=\sum_{j=1}^{N_{\rm pix}}-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
 \eeq
 %
-where again the Einstein summation convention is implied and all the symbols have their usual meaning.
+where all the symbols have their usual meaning. The above equation can again be expressed more concisely as follows,
+%
+\beq
+[Q + iU](\hat{n}_0) = \left( \left[ -\sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)(\hat{n}_0)\,,
+\eeq
+%
+which is to be interpreted in the same manner as \eq{eq:qu2eb_simple}.
+Note that the only change in the convolution kernel as compared to that in \eq{eq:qu2eb_simple} is that the spherical harmonic function $Y_{\ell 2}$ is not conjugated.
 
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? }
+\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}
 %--------------------------------------------------------

### 2017-10-16 article/sections/appendix.tex
Updates to the real space derivation sections of the paper

@@
 \beqry
-\sum_{\ell=\ell_{\rm min}, m}^{\ell_{\rm max}}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) &\approx& \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,, \\
-&=& \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} {}_{s}Y^{-s}_{\ell}(\beta,\alpha) e^{-i s \gamma} \,, \nonumber
+\sum_{\ell=\ell_{\rm min}, m}^{\ell_{\rm max}}{_{s_1}Y^*_{\ell m}}(\hat{n}_i){_{s_2}Y_{\ell m}}(\hat{n}_j) &\approx& \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,, \\
+&=& \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} {}_{s_2}Y^{-s_1}_{\ell}(\beta,\alpha) e^{-i s_2 \gamma} \,, \nonumber
 \eeqry

### 2017-10-16 article/sections/kernel_discussion.tex
updates to the notebook evaluating the high res analysis, added latitude position of the mask as a input variable
added new figures to 353Ghz application ; minor edits to article
Updates to the real space derivation sections of the paper

@@
 Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
+These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
 The resultant functions are depicted in \fig{fig:beta_kernel}.
@@
 These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
+The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.
+\comment{Update to Nside=64 ?}}
 \label{fig:beta_kernel}
@@
 \centering
+%\captionsetup[subfigure]{labelformat=empty}
 \subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}

### 2017-10-16 article/sections/real_space_formalism.tex
Updates to the real space derivation sections of the paper

@@
 %
-\beqrys
+\begin{subequations} \label{eq:har_eb_op}
+\beqry
 \tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
 \tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,
-\eeqrys
+\eeqry
+\end{subequations}
 %
@@
 %
-\beqrys\label{eq:eb_har_proj}
+\begin{subequations} \label{eq:har_op_prop}
+\beqry
 \tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \\
+ \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
  \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqrys
+\eeqry
+\end{subequations}
 %
@@
 \beqrys
-\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
+\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
 &=&  \bar O *\bar{P} \,.
@@
 \mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) {{_2}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}^*_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) - i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
+&=&\sum_{\ell m} {{_0}Y}^*_{\ell m}(\hat n_i) {{_2}Y}_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
+&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
+&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
 \eeqrys
@@
 where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
-Note that this kernel does not depend on the Euler angle $\gamma$.
-This local convolution kernel has a part which depends only on the Euler angle $\alpha$ which has no multipole dependence,  except the factor of 2 which arises because the polarization field is a spin-2 field.
-The remaining part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ which depends only on the Euler angle $\beta$ and completely incorporates any multipole $\ell$ dependence of the kernel.
-We will refer to $f(\beta,\ell_{\rm min},\ell_{\rm max})$ as the radial part of the kernel since it only depends on the distance from the location at which the scalar fields are being evaluated.
-The radial part of the kernel completely determines the locality of the operator which translates the Stokes parameters Q \& U to the scalars E \& B.
-
 On simplifying \eq{eq:qu2eb_ker_1}, the local convolution kernel can be cast in this simple form,
@@
 \beq\label{eq:op_qu2eb}
-\bar O =\bmat  -\mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & -\mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
+\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
 \eeq
 %
-where i,j indices map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
+where indices i,j map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
 \revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
@@
 \beq \label{eq:qu2eb_convolution}
-\bmat E_i \\ B_i  \emat= \sum_{j=1}^{N_{\rm pix}}-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Delta \Omega\,,
+\bmat E_i \\ B_i  \emat= -\Delta \Omega \sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \,,
 \eeq
@@
 %
-\beq \label{eq:qu2eb_simple}
-[E + iB](\hat{n}_0) = \left( \left[ -\sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ [Q+iU] \right)(\hat{n}_0)\,, 
-\eeq
+\begin{subequations} \label{eq:qu2eb_simple}
+\beqry 
+[E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
+&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right)\,, \label{eq:qu2eb_convolution} 
+\eeqry
+\end{subequations}
 %
-where $\circ$ denotes a convolution and the spherical harmonic function are to be evaluated at the $(\theta,\phi)=(\beta,\alpha)$.
-\revisit{Note that since the kernel does not depend on the Euler angle $\gamma$, the evaluation of the E and B maps is not critically dependent on the exact alignment of the rotated x and y axis with the local x and y axis, only the z-axis needs to be exactly aligned with the local z-axis.}
+where $\circ$ denotes a convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_0$ and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
+We know that the spin of product of functions with different spins is given by: ${}_{s_1}f {}_{s_2}g = {}_{s_1 +s_2}h$.
+Since $[Q + iU]$ is a field with spin +2 and the function $\exp(-i2\alpha)$ is a field with spin -2, the resultant field formed by the product of these two function has spin-0.
+This makes intuitive, the construction of the spin-0 E and B modes of polarization.
+Note that the coordinate dependence of the Stokes parameters cannot be integrated out at the location $\hat{n}_0$ where the scalar fields are to be evaluated since the azimuthal angle becomes ill-defined.
+This issue is averted by the fact that the radial function is formed by taking weighted linear combinations of $P_{\ell}^2$ Legendre polynomials which have vanishing contribution $(P_{\ell}^2(\beta) \propto \sin^2{\beta})$ as $\beta \rightarrow 0 ,\pi$.
+\revisit{Also note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
 
-\rfedit{While the azimuthal operations do not depend on the choice of basis functions, the radial kernel is completely determined by the choice of the basis functions.
-One can now think of constructing alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels.
+Note that this kernel does not depend on the Euler angle $\gamma$ \comment{Why is that and how do you understand this ?
+}.
+This local convolution kernel has a part which depends only on the Euler angle $\alpha$ which has no multipole dependence.
+The remaining part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ which depends only on the Euler angle $\beta$ and completely incorporates the multipole $\ell$ dependence of the kernel.
+We will refer to $f(\beta,\ell_{\rm min},\ell_{\rm max})$ as the radial part of the kernel since it only depends on the angular distance between different locations.
+Its the radial part of the kernel that completely determines the locality of this operator.
+
+\rfedit{The azimuthal operations do not depend on the choice of basis functions, and can be argued as a requirement for constructing spin-0 fields by operating on spin-2 fields.
+The radial kernel however is determined by the choice of the basis functions.
+Motivated by this observation, one can now think of working with alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels.
 So shift this line to the section where we explore different radial functions.}
@@
 %
-We do not provide the explicit calculations here, since the real space inverse operator can be derived by contracting over all the matrix operators using a procedure nearly identical to that discussed in the previous section.
-The inverse operator is given by the following expression,
+We do not provide the explicit calculations here, since the derivation is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
 %
 \beq
-{\bar O}^{-1}=\bmat - \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & - \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
+{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
 \eeq
@@
 \beq
-\bmat Q_i \\ U_i  \emat=\sum_{j=1}^{N_{\rm pix}}-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \Delta\Omega \,,
+\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
 \eeq
@@
 %
-\beq
-[Q + iU](\hat{n}_0) = \left( \left[ -\sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)(\hat{n}_0)\,,
-\eeq
+\begin{subequations} \label{eq:eb2qu_simple}
+\beqry 
+[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
+{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)\,, 
+\eeqry
+\end{subequations}
 %
 which is to be interpreted in the same manner as \eq{eq:qu2eb_simple}.
-Note that the only change in the convolution kernel as compared to that in \eq{eq:qu2eb_simple} is that the spherical harmonic function $Y_{\ell 2}$ is not conjugated.
+Note that the only change in the convolution kernel as compared to that in \eq{eq:op_qu2eb} is that the signs of the off-diagonal block matrices are reversed.
+Alternatively, the $Y_{\ell 2}$ functions are not conjugated.
+This can again be simply understood as constructing a spin-2 field by taking a product of a spin-0 field: $[E +iB]$ with a spin $+2$ field: $\exp(+i2\alpha)$.
+The radial dependence of the operator ${\bar O}^{-1}$  is identical to the that of ${\bar O}$ as one may have expected.
+In this case all the coordinate dependence in encoded in the function $\exp(+i2\alpha)$, which is ill-defined at the poles ($\beta \rightarrow 0,\pi$) and hence the radial functions have to vanish at these locations, which is the case for the same reasons discussed previously.
 
@@
 The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other.
-It is possible to decompose the Stokes Q \& U parameters into those that purely contribute to E modes and those that purely contribute to the B mode of polarization.
-We can only measure the total Stokes parameters which is a sum of the Stokes Q \& U corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly decompose the total measured Stokes Q \& U parameters to Stokes parameters corresponding to the scalar fields E \& B respectively, \textit{without ever having to evaluate the E \& B modes explicitly}.
-Again the procedure is analogous to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved.
-Here we use the harmonic space E/B projection operators $\tilde O_{E/B}$, defined in \eq{eq:eb_har_proj}, to derive the respective real space operators.
-It can be shown that the Stokes parameters corresponding to each scalar mode are given by the following expressions,
+The E \& B modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
+It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to E modes and another \vp{\rm B} that purely contribute to the B modes of polarization.
+We can only measure the total Stokes vector which is a sum of the Stokes vectors corresponding to the respective scalar modes.
+In this section we derive the real space operators which directly perform this decomposition, without ever having to evaluate the E \& B modes.
+The derivation is similar to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved in this case.
+Here we use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
+The Stokes parameters corresponding to each scalar mode are given by the following expressions,
 %
@@
 %
-We contract over all the matrix operators to arrive at the the real space operators. On simplification it can be shows that the real space operator takes up the following form,
+We contract over all the matrix operators to arrive at the the real space operators. On working through the algebra it can be shown that the real space operators have the following form,
 %
 \beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} \pm \mathcal{D}_{r} & -\mathcal{I}_{i} \pm \mathcal{D}_{i} \\  -\mathcal{I}_{i} \pm \mathcal{D}_{i}  & \mathcal{I}_{r} \mp \mathcal{D}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} \,,\\
+\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \,,\\
 \eeq
@@
 \beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_2Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
+\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
 \mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
@@
 \beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell -2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) - i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
+\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell +2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
+\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
 \mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
@@
  %
-Finally, the Stokes parameters corresponding to the respective scalar fields can be derived by evaluating the following expression, 
+Finally, the Stokes parameters corresponding to the respective scalar fields are given by evaluating the following expressions, 
  %
 \beqry \label{eq:op_qu2equbqu}
-\bmat Q_i \\ U_i  \emat_{E/B} &=&0.5 \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  \sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat   \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) & - \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace \Delta\Omega \,,\nonumber
+\bmat Q_i \\ U_i  \emat_{E/B} &=& \sum_{j=1}^{N_{\rm pix}} \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat  \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) &  \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  \sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
 \eeqry
 %
-where all the symbols have their usual meaning.
+where all the symbols have their usual meaning. The above expression can be cast in the following simplified form,
+%
+\begin{subequations}
+\beqry
+{}_{+2}X_{E/B} &=&0.5 \Delta \Omega\sum_{j=1}^{N_{\rm pix}}  {}_{-2}f(\beta_{ij}) e^{-i2 (\alpha_{ij} + \gamma_{ij})} {}_{+2}X_j \pm {}_{+2}f(\beta_{ij}) e^{i2 (\alpha_{ij} - \gamma_{ij})} {}_{+2}X_j^*\,, \label{eq:qu2equbqu_explicit_convolution} \\
+&=& 0.5 \Bigg\lbrace I^* \circ {}_{+2}X\pm D \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
+\eeqry
+\end{subequations}
+%
+where in \eq{eq:qu2equbqu_explicit_convolution} we have suppressed the explicit multipole dependence of functions $_{\pm 2}f$ for brevity and in \eq{eq:qu2equbqu_convolution} $\circ$ denotes a convolution.
+
+It is easy to show that the operator $D$ is a complex but symmetric matrix and that the operator $I$ is Hermitian.
+The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} I = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix.
+Though its non-local ($I \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $I$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $I*I=I$ ; (ii) $D*I=D$.
+Also $D^*$ is the inverse of $D$ in this band limited sense: $D^**D=I$.
+Using these properties of the operators $I$ and $D$, one can verify that the real space operators satisfy the following identities,
+%
+\begin{subequations}
+\beqry
+\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
+\bar O_E*\bar O_B &=& 0 \,,\\
+\bar O_E + \bar O_B &=& I \,,
+\eeqry
+\end{subequations}
+%
+which are the real space analogues of \eq{eq:har_op_prop}.
+While testing the above stated identities one encounters terms like $D*I^*,I^**I \textrm{ and }  I*I^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other.
+\revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix.
+\comment{Isn't it possible to do some real space operations which don't care for the band limit but still give me the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit.
+If one forces the sum of the operators to be exactly an identity operator, then one compromises on the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators.}

### 2017-10-17 article/sections/kernel_discussion.tex
deleted some kernel figure files

@@
 \subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
-We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $.
-Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels.
-These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$.
+As seen in the previous sections, all the kernels separate into a part which depends only on the angular distance between pixels and another part that depends on the azimuthal orientation around the central pixel.
+The radial part of the kernels determines the non-locality of the operator.
+We numerically compute the radial kernels: $f, _{+2}f ~\&~ _{-2}f $ by evaluating the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [=2,192]$.
 The resultant functions are depicted in \fig{fig:beta_kernel}.
-Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
 %
@@
 \includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}.
-These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$.
-The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.
-\comment{Update to Nside=64 ?}}
+\caption{The figure depicts the radial part of the convolution kernels.
+These radial function have been evaluated with the band limit fixed at $\ell \in [2,192]$.
+The vertical dashed line marks the approximate size of a NSIDE=64 Healpix pixel.}
 \label{fig:beta_kernel}
@@
 %
-We recall that the fields E \& B are scalar and hence immune to coordinate definitions.
+Note that the function $f(\beta)$, which forms the radial part of the real space convolution kernel that translates the Stokes parameters Q \& U to scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
+Recall that the fields E \& B are scalar and hence expected to be immune to coordinate definitions.
 The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars.
+Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being coordinate independent.
+
 The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.
+$_{-2}f(\beta)$ form the radial part of the band limited delta function $I$ and hence it contributes the most at the location of the central pixel.
+$_{+2}f(\beta)$ again has a vanishing contribution near the central pixel and it dominantly contributes in the neighbouring regions which are approximately at least 1 pixel distance away from the central pixel.
 
-In addition to the angular distance $\beta$ from the central pixel, the convolution kernels also depend on the other Euler angles $\alpha ~\&~ \gamma$ as seen from \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d}.
-We plot the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ at different positions on the sphere.
-For illustration the functions have been sampled at a very high Healpix resolution parameter of NSIDE=2048.
-We evaluate parts of the convolution kernels at different locations on the sphere and the results are depicted in \fig{fig:vis_kernel}.
+The azimuthal dependencies of the convolution kernels, are specified as functions of the Euler angles $\alpha ~\&~ \gamma$.
+We evaluate the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ by calculating the Euler angles for all the pixels surrounding the central pixel and using them in \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d} respectively.
  %
-\begin{figure}[!h] \label{fig:mixing_kernel}
+\begin{figure}[t] \label{fig:mixing_kernel}
 \centering
 %\captionsetup[subfigure]{labelformat=empty}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat90_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat90_lon0.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon0.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon0.pdf}}\\[-2ex]
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat90_lon45.pdf}}\\[-2ex]
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon45.pdf}}\\[-2ex]
 \subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
@@
 \caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit fixed at $\ell_{\rm max}=96$, however the functions have been sampled at an NSIDE=2048 resolution for visual appeal.
-The size of each panel is approximately $26^{\circ} \times 26^{\circ}$.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated and the black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
+These kernels have been evaluated with the band limit: $\ell \in [2,192]$.
+The functions have been sampled at an NSIDE=2048 resolution for visual appeal.
+The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations.
+The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated.
+The black star marks the location of the north galactic pole.
+The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.
+}
+%from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
 \label{fig:vis_kernel}
@@
 %
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernel at different locations on the sphere, to give a sense of how these kernels vary across the sphere.}
-The function $\mathcal{M}$ is nearly identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.
-It is also important to note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first four rows of \fig{fig:vis_kernel}.
-On the contrary, the function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
+\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernels at different locations, to give a sense of how these kernels vary across the sphere.} For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
+All the plots have been rotated such that the pixel around which the kernels are evaluated lies in the centre marked by the back circle.
+The results are depicted in \fig{fig:vis_kernel}.
+
+The function $\mathcal{M}$ is identical irrespective of changes in the galactic latitude and longitude of the central pixel.
+\st{The only contrasting locations are the poles (i.e.
+$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.} Also note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
+Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
+\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
+Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
+
+The function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
 It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This transformation arises from the distortions induced in this function as parts of its domain passes the galactic poles.
-The function $\mathcal{I}$ shows similar behavior, varying with latitude and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the ideal case of no band limit would reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), \revisit{hints of which can be seen by comparing the amplitudes of the real and imaginary parts of this function in the last two columns of \fig{fig:vis_kernel}, especially close to the equator}.
-Since we invariably work with a specific band limit, both the real and imaginary parts of this functions make important finite non-zero contributions }.
-All the function are seen to be invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second (evaluated at $[b,\ell]=[87^{\circ},0^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
+This change in behavior is primarily due to the  dependence on the Euler angle $\gamma$.
+When the central pixel is nearly at the pole, $\gamma$ vanishes, and the azimuthal part of the function $D$ is identical to that of $\mathcal{M}$ and hence the two function look very similar as seen in the first row of \fig{fig:vis_kernel}.
+Also note that this function is distorted as parts of its domain pass the galactic poles.
+
+The function $\mathcal{I}$ shows similar behavior, varying with latitude, having an identical azimuthal behavior near the poles and being distorted in parts that overlap with the galactic poles.
+\revisit{This function, in the case of an infinite band limit reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), as discussed previously.
+Hints of this behavior can be seen by comparing the amplitudes of the real and imaginary parts of this function near the equator, depicted in the fifth row of the last two columns of \fig{fig:vis_kernel}.
+However note that this function significantly deviates from this behavior at higher galactic latitudes.
+The real and imaginary parts of this function contribute nearly equally near the vicinity of the poles.}  We invariably work with a specific band limit, hence both the real and imaginary parts of this functions make important non-zero contributions.
+
+We reiterate that all the function are invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second row (evaluated at $[b,\ell]=[87^{\circ},45^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
 
 \subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-It is clear that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the resolution of the experiment, we evaluate only the radial part of the convolution kernel for different values of the maximum multipole $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
+It is clear from previous discussions that that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
+To quantify this non-locality as a function of the maximum multipole accessible for analysis, we evaluate the radial part of the convolution kernel for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
 The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
 All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels fall appear to shift left, becoming insignificant relative  to their global maxima at progressively small angular distance $\beta$ from the central pixel.
+Note that on increasing $\ell_{\rm max}$ the radial kernels shift to the left, attaining fractions of  their global maxima at progressively small angular distances $\beta$ from the central pixel.
 %
@@
 
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$. What do you want to say about these functions?}
-
-\comment{Do you want to comment on the telescoping behavior of these radial functions ? }
+\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$.}
+\comment{Comment on the telescoping behavior of these radial functions ? }

### 2017-10-17 article/sections/real_space_formalism.tex
deleted some kernel figure files

@@
 \revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix.
-\comment{Isn't it possible to do some real space operations which don't care for the band limit but still give me the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit.
+\comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit.
 If one forces the sum of the operators to be exactly an identity operator, then one compromises on the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators.}

### 2017-10-17 article/sections/kernel_discussion.tex
updates to discussion on locality of E and B mode kernels

@@
 To quantify this non-locality as a function of the maximum multipole accessible for analysis, we evaluate the radial part of the convolution kernel for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels shift to the left, attaining fractions of  their global maxima at progressively small angular distances $\beta$ from the central pixel.
 %
-\begin{figure}[!t]
+\begin{figure}[t]
 \centering
-\subfigure[]{\includegraphics[width=1.0\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.96\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
 \caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
@@
 %
+The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
+All the function have been normalized such that their global maxima is set to unity.
+Note that on increasing $\ell_{\rm max}$ the radial kernels shift to the left, attaining fractions of  their global maxima at progressively small angular distances $\beta$ from the central pixel.
+
+We have observed that the radial functions derived by evaluating the multipole sums to different maximum multipoles are self similar.
+Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx [\frac{\ell_{\rm max}}{\ell'_{\rm max}}]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
+Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.
+The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity.
+The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.
+
+We are primarily interested in the non-local dependence of the scalar modes E \& B on the Stokes parameters Q \& U.
 We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-We find that the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ can predict quite accurately the value of the non-locality parameter for a given maximum multipole $\ell_{\rm max}$ and fixed $\ell_{\rm min}=2$.
+For a $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$, since the radial function never falls monotonously below 1\% of the global maxima of the function.
+Using the self similar  property of the radial function discussed above, we define the following: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ as the non-locality parameter, given the maximum multipole $\ell_{\rm max}$.
+\revisit{$\beta_0$ is not very sensitive to $\ell_{\rm min}$, though it can be important on making drastic changes to $\ell_{\rm min}$.
+} \comment{Quantify how changing $\ell_{\rm min}$ changes $\beta_0$}
 
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a linear relation to the angular distance $\beta$ in log space as seen in \fig{fig:rad_ker_decay}, indicating a power law fall off.
-A fit by eye indicates that the envelope of the function is well represented by a fuction proportional to $\beta^{-1.5}$ in intermediate angular distance range.
-This is not valid in regions $\beta << \beta_o$ and $\beta >> \beta_o$, where the envelope of the function can be clearly seen to deviate from power law behavior (see \fig{fig:rad_ker_decay}).
-
+The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a power law relation to the angular distance $\beta$ as seen in \fig{fig:rad_ker_decay}.
+At small values of $\beta$, which corresponds to the flat sky limit,  the radial function is proportional to $\beta^2$.
+In the intermediate range,  a fit by eye indicates that the envelope of the function is well represented by the power law $\beta^{-1.5}$.
 \comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$.}
-\comment{Comment on the telescoping behavior of these radial functions ? }

### 2017-10-19 article/sections/ebclcorrection.tex
added a notebook which computes the oscillations seen in the spectra of eb maps evaluated from localized convolution kernels. Added a discussion to the draft on constructing convolution kernels with different radial profiles

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Explaining the oscillations in spectra and recovering the true spectra}

The radial part of the convolution kernel which translates Stokes parameters Q \& U to scalar E \& B is given by the following expression,
%
\beq
R_{QU \leftrightarrow EB}(\beta) = R(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:native_rad}
\eeq
%
where $P_{\ell}^{2}$ are the associated Legendre polynomials. Note that the form of the radial kernel remains unchanged for the forward $\bar{O}$ and the inverse operators $\bar{O}^{-1}$.

While translating from Stokes Q \& U parameters which form a spin-2 field to spin-0 scalars E \& B, the azimuthal part of the convolution is restricted to have the form $e^{-i2\phi}$. The only freedom is to choose the radial part of the convolution kernel.  It is possible to generalize the form of the radial kernel by introducing the following redefinition,
%
\beq
G_{QU \rightarrow EB}(\beta) = G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_forward}
\eeq
%
where $b_{\ell}$ encodes the desired changes to the radial function. This radial function now defines the modified forward operator $\bar{O}'$. Since we require the following property: $\bar{O}' \bar{O}'^{-1} = I$ to hold true, the inverse operator cannot have the same form for the radial function. Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the radial part of the inverse operator has to take up the following form,
%
\beq
G_{EB \rightarrow QU}(\beta) = G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}^{-1}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
\eeq
%
where $b_{\ell}$ is the same multipole function introduced in \eq{eq:mod_rad_forward}. Therefore for the forward and backward operators to be well behaved we are restricted in choosing multipole functions $b_{\ell}$ such that its inverse is well defined. If this constraint is overlooked, the ability to transform back and forth between the Stokes parameters and the scalar representation of the CMB polarization field is compromised. Given this general definition for the radial function $G(\beta)$, note that the radial function $R(\beta)$ is just a special case formed by making the choice $b_{\ell}=1$. Note that for this choice the inverse of the multipole function is itself $b_{\ell}^{-1} = b_{\ell}$ and therefore $G^{-1}(\beta) = G(\beta)$.

While modifying the radial function, it makes more sense to make a choice on the real space function $G(\beta)$ instead of choosing the multipole function $b_{\ell}$. We use the orthogonality property of associated Legendre polynomials to express the multipole function $b_{\ell}$ as,
%
\beq
b_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl}
\eeq
%
where we have used the orthonormality property of the associated Legendre polynomials to arrive at the above equation. Note that once the choice of $G(\beta)$ is made, the inverse function $G^{-1}(\beta)$ is automatically defined by the forward relation given in \eq{eq:mod_rad_inverse}.

In \sec{sec:local_conv_eb} we constructed localized convolution kernels by multiplying $R(\beta)$ with an apodized version of the step function $\theta_{\rm apo}(r_{\rm cutoff})$. The oscillation seen in the spectra in \fig{fig:eb-spectra_rad_cutoff} can be explained to be due to this effective beam characterized by $b_{\ell}^2$ operating on the power spectra. The effective beam can be evaluated by computing the multipole function $b_{\ell}$ as follows,
%
\beq
b_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{r_{\rm cutoff}} R(\beta) \theta_{\rm apo}(r_{\rm cutoff})  P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl} \,,
\eeq
%
where the upper limit of the integration is set to $r_{\rm cutoff}$ since the function $\theta_{\rm apo}(r_{\rm cutoff})$ vanishes for $\beta>r_{\rm cutoff}$. The function $b^2_{\ell}-1$ matches the oscillation seen in \fig{fig:eb-spectra_rad_cutoff} as  seen in \fig{fig:match_cl_oscillations} where the two results have been over plotted.
%
\begin{figure}[!t] 
\centering
\subfigure[]{\includegraphics[width=0.98\columnwidth]{analytical_cl_oscillations_vs_data.pdf}}
\caption{The thin lines depicts the same spectral differences as those seen in \fig{fig:eb-spectra_rad_cutoff}, while the thick lines of the corresponding color depict the function $b_{\ell}^2 -1$ as derived from evaluating \eq{eq:gb2bl} for different $r_{\rm cutoff}$}.
\label{fig:match_cl_oscillations}
\end{figure}
%
The apodized step function in this case transition from 1 at $\beta < r_{\rm cutoff} -w$ to 0 at $r_{\rm cutoff}$ over a width $w= 3^{\circ}$ with a cosine squared profile .

%--------------------------------------------------------
%--------------------------------------------------------

### 2017-10-19 article/sections/kernel_discussion.tex
added a notebook which computes the oscillations seen in the spectra of eb maps evaluated from localized convolution kernels. Added a discussion to the draft on constructing convolution kernels with different radial profiles

@@
 We have observed that the radial functions derived by evaluating the multipole sums to different maximum multipoles are self similar.
-Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx [\frac{\ell_{\rm max}}{\ell'_{\rm max}}]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
 We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.

### 2017-10-19 codes/modules/local_eb_kernel.py

@@ -52,7 +52,10 @@ class real_space_queb_kernels(object):
 
 		return alpha,beta,gamma,spixel
 
+		#This a equivalent way of getting the Euler angles.
+ 		#This method returns the beta and alpha as theta and phi when one of the pixels coincides with the north pole. 
 	def return_euler_angles_new(self,nside,cpixel,discsize=180.,nest=False):
+		'''Returns the pixel numbers and the respective Euler angles within a circle of radius discsize from the central pixel: cpixel'''
 		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
 
 		v=h.pix2vec(nside,cpixel,nest=nest)
@@ -75,7 +78,7 @@ class real_space_queb_kernels(object):
 
 
 	def return_euler_ang(self,theta1,phi1,theta2,phi2):
-
+		'''Returns the Euler angles for a pair of spherical coordinates'''
 		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
 		#temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
 		beta=np.arccos(temp_beta)

### 2017-10-21 articles/draft/sections/application_353ghz.tex
added a new section on generalized operators

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Application to Planck 353 Ghz polarization maps}
In this section we apply the local convolution estimator for E and B mode maps on Planck 353 GHz polarization data. To work with out local convolution method, we reduce the resolution of the map to $Nside=128$ using the Healpix \textit {ud\_grade} function. We use a high pass filters which retains modes in the multipole range $\ell=[50,256]$. The non-locality parameter given $\ell_{\rm max}=256$ is $\beta_o=17^{\circ}$. We estimate the local E and B mode maps by performing local convolutions for a set of radial cut-offs: $r_{\rm cutoff} = \beta_o, 0.5\beta_o, 0.25\beta_o$. We do not use any mask while carrying out this analysis. The resultant E and B mode maps are depicted in \fig{fig:353ghz-eb-maps}.
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-healpix_filter_lmin30_lmax256_nside128.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-healpix_filter_lmin30_lmax256_nside128.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-realspace_disc7d_apo0d_lmin30_lmax256_nside128.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-realspace_disc7d_apo0d_lmin30_lmax256_nside128.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-e-mode-realspace_disc7d_apo0d_lmin50_lmax256_nside128.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{353ghz/353ghz-b-mode-realspace_disc7d_apo0d_lmin50_lmax256_nside128.pdf}}
\caption{}
\label{fig:353ghz-eb-maps}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Scaling and future prospects}
%
\begin{figure}[!h] 
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{supplementary/number_of_disc_pixels.pdf}}
\caption{The red dashed curve depicts the how $\beta_o$ changes as a function of the Healpix resolution parameter Nside assuming that the maximum multipole accessible in the map is given by $\ell_{\rm max} = 3 * Nside$. The blue solid curve depicts the number of surrounding pixel that will need to be accessed to carry out the convolution on Stokes Q \& U maps to infer the value of the scalar fields E \& B at the central pixel.}
\label{fig:disc_rad_healpix_numpix}
\end{figure}
%
%--------------------------------------------------------
%--------------------------------------------------------

### 2017-10-21 articles/draft/sections/generalizedeb.tex
added a new section on generalized operators

--- 2017-10-19 article/sections/ebclcorrection.tex
@@
 %--------------------------------------------------------
-\subsection{Explaining the oscillations in spectra and recovering the true spectra}
+\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}
+\section{Generalized operators}
+The azimuthal dependence of the convolution kernels which translate the Stokes parameters Q \& U to the scalar E \& B is determined by the spin properties of the field being operated upon and the spin of the resultant fields.
+Hence there is no freedom in the choice of function for the azimuthal dependence of the convolution kernels.
+The radial part of the function however is determined by the choice of the basis functions.
+It is possible to generalize these convolution kernels by choosing alternate forms for the radial functions.
+
+We can characterize different forms of the radial kernel by introducing the following harmonic space operator,
+%
+\beq
+\tilde{\mathcal{G}} = {\begin{bmatrix} b_{\ell}^E & 0  \\  0 & b_{\ell}^B \end{bmatrix}} \,,
+\eeq
+%
+where the functions $b^E_{\ell}$ and $b^B_{\ell}$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for E and B modes.
+To simplify the discussion and without loosing this generality we proceed with the assumption $b_{\ell}^E = b_{\ell}^B= b_{\ell}$.
+We can chose this function to be any arbitrary function and it will allow us to define some convolution operator which either translates Stokes Q \& U parameters to scalars E \& B or vice verse.
+Given $\tilde{\mathcal{G}}$ the modified forward and inverse convolution kernels are given by the following expressions,
+%
+\begin{subequations} \label{eq:gen_qu2eb}
+\beqry
+{\bar O}' &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
+{\bar O}'^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
+\eeqry
+\end{subequations}
+%
+where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
+Note that for an arbitrary choice of $\tilde{\mathcal{G}}$ only one of the operators in \eq{eq:gen_qu2eb} is well defined, since $\tilde{\mathcal{G}}^{-1}$ may be ill defined.
+If we require both the forward and inverse hold true, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that its inverse is well defined.
 
@@
 Since we require the following property: $\bar{O}' \bar{O}'^{-1} = I$ to hold true, the inverse operator cannot have the same form for the radial function.
-Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the radial part of the inverse operator has to take up the following form,
+Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the modified operator and its inverse is given by the following equations,
+%
+\begin{subequations}
+\beqry
+{\bar O} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
+{\bar O}^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
+\eeqry
+\end{subequations}
+%
+where it can be shown that the radial part of the inverse operator has to take up the following form,
 %
@@
 
+%
+\begin{figure}[!t] 
+\centering
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{example_gbeta.pdf}}
+\subfigure[]{\includegraphics[width=0.49\columnwidth]{example_eff_bl.pdf}}
+\caption{}
+\label{fig:example_gbeta}
+\end{figure}
+%
 %--------------------------------------------------------

### 2017-10-21 articles/draft/sections/numerical_implementation.tex
added a new section on generalized operators

--- 2017-09-27 article/sections/numerical_implementation.tex
@@
 %--------------------------------------------------------
-\subsection{Constructing E \& B maps using local convolutions}
+\subsection{Constructing E \& B maps using local convolutions} \label{sec:local_conv_eb}
 Here we present the results of evaluating the local convolution given in \eq{eq:op_qu2eb}, to derive E \& B mode maps given maps of Stokes Q \& U.

### 2017-10-21 articles/draft/sections/real_space_formalism.tex
added a new section on generalized operators

--- 2017-10-17 article/sections/real_space_formalism.tex
@@
 %
-\beq \label{eq:pseudo}
+\beq \label{eq:realeb}
 E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
@@
 %
-\beq \label{eq:qu2eb_convolution}
+\beq \label{eq:qu2eb_convolution_explicit}
 \bmat E_i \\ B_i  \emat= -\Delta \Omega \sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \,,
@@
 In this case all the coordinate dependence in encoded in the function $\exp(+i2\alpha)$, which is ill-defined at the poles ($\beta \rightarrow 0,\pi$) and hence the radial functions have to vanish at these locations, which is the case for the same reasons discussed previously.
-
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}
 %--------------------------------------------------------
@@
 {}_{+2}X_{E/B} &=&0.5 \Delta \Omega\sum_{j=1}^{N_{\rm pix}}  {}_{-2}f(\beta_{ij}) e^{-i2 (\alpha_{ij} + \gamma_{ij})} {}_{+2}X_j \pm {}_{+2}f(\beta_{ij}) e^{i2 (\alpha_{ij} - \gamma_{ij})} {}_{+2}X_j^*\,, \label{eq:qu2equbqu_explicit_convolution} \\
-&=& 0.5 \Bigg\lbrace I^* \circ {}_{+2}X\pm D \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
+&=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
 \eeqry
@@
 
-It is easy to show that the operator $D$ is a complex but symmetric matrix and that the operator $I$ is Hermitian.
-The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} I = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix.
-Though its non-local ($I \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $I$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $I*I=I$ ; (ii) $D*I=D$.
-Also $D^*$ is the inverse of $D$ in this band limited sense: $D^**D=I$.
-Using these properties of the operators $I$ and $D$, one can verify that the real space operators satisfy the following identities,
+It is easy to show that the operator $\mathcal{D}$ is a complex but symmetric matrix and that the operator $\mathcal{I}$ is Hermitian.
+The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix.
+Though its non-local ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $\mathcal{I}$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
+Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=I$.
+Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
 %
@@
 \bar O_E*\bar O_B &=& 0 \,,\\
-\bar O_E + \bar O_B &=& I \,,
+\bar O_E + \bar O_B &=& \mathcal{I} \,,
 \eeqry
@@
 which are the real space analogues of \eq{eq:har_op_prop}.
-While testing the above stated identities one encounters terms like $D*I^*,I^**I \textrm{ and }  I*I^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other.
+While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other.
 \revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix.

### 2017-10-22 articles/draft/sections/generalizedeb.tex
updates to draft, section on generalized operators. revised figuresdepicting the pixel scaling as a function of maximum multipole

@@
 \beq
-\tilde{\mathcal{G}} = {\begin{bmatrix} b_{\ell}^E & 0  \\  0 & b_{\ell}^B \end{bmatrix}} \,,
+\tilde{\mathcal{G}} = {\begin{bmatrix} g_{\ell}^E & 0  \\  0 & g_{\ell}^B \end{bmatrix}} \,,
 \eeq
 %
-where the functions $b^E_{\ell}$ and $b^B_{\ell}$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for E and B modes.
-To simplify the discussion and without loosing this generality we proceed with the assumption $b_{\ell}^E = b_{\ell}^B= b_{\ell}$.
+where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for E and B modes.
+To simplify the discussion and without loosing this generality we proceed with the assumption $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
 We can chose this function to be any arbitrary function and it will allow us to define some convolution operator which either translates Stokes Q \& U parameters to scalars E \& B or vice verse.
@@
 
-The radial part of the convolution kernel which translates Stokes parameters Q \& U to scalar E \& B is given by the following expression,
-%
-\beq
-R_{QU \leftrightarrow EB}(\beta) = R(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:native_rad}
-\eeq
-%
-where $P_{\ell}^{2}$ are the associated Legendre polynomials. Note that the form of the radial kernel remains unchanged for the forward $\bar{O}$ and the inverse operators $\bar{O}^{-1}$.
-
-While translating from Stokes Q \& U parameters which form a spin-2 field to spin-0 scalars E \& B, the azimuthal part of the convolution is restricted to have the form $e^{-i2\phi}$.
-The only freedom is to choose the radial part of the convolution kernel.
-It is possible to generalize the form of the radial kernel by introducing the following redefinition,
-%
-\beq
-G_{QU \rightarrow EB}(\beta) = G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_forward}
-\eeq
-%
-where $b_{\ell}$ encodes the desired changes to the radial function.
-This radial function now defines the modified forward operator $\bar{O}'$.
-Since we require the following property: $\bar{O}' \bar{O}'^{-1} = I$ to hold true, the inverse operator cannot have the same form for the radial function.
-Demanding $\bar{O}' \bar{O}'^{-1} = I$ to hold true it can be shown that the modified operator and its inverse is given by the following equations,
+The radial part of these generalized convolution kernels is now given by the following expressions,
 %
@@
 \beqry
-{\bar O} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
-{\bar O}^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
+G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \\
+G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
 \eeqry
@@
 %
-where it can be shown that the radial part of the inverse operator has to take up the following form,
+where $g_{\ell}$ are the same multipole function as those appearing in $\tilde{\mathcal{G}}$.
+If one chooses different forms of $g_{\ell}$ for E and B modes then the radial function are defined accordingly.
+Given this general definition for the radial function $G(\beta)$, note that the default radial function $f(\beta)$ is just a special case resulting from the choice $\tilde{\mathcal{G}}=\tilde{\mathcal{I}}$ ($g_{\ell}=1$).
+Note that for this choice of $\tilde{\mathcal{G}}$ the inverse is trivial $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)$.
+
+While defining these alternate operators by modifying the radial part of the kernels, it seems more natural to make a choice on the real space function $G(\beta)$ as compared to choosing the multipole function $g_{\ell}$.
+Using the orthogonality property of associated Legendre polynomials it can be shown that the multipole function $g_{\ell}$ is given by the following integral once the radial function $G(\beta)$ is specified,
 %
 \beq
-G_{EB \rightarrow QU}(\beta) = G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} b_{\ell}^{-1}\sqrt{\frac{2 \ell+1}{4 \pi} \frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
+g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,. \label{eq:gb2bl}
 \eeq
 %
-where $b_{\ell}$ is the same multipole function introduced in \eq{eq:mod_rad_forward}.
-Therefore for the forward and backward operators to be well behaved we are restricted in choosing multipole functions $b_{\ell}$ such that its inverse is well defined.
-If this constraint is overlooked, the ability to transform back and forth between the Stokes parameters and the scalar representation of the CMB polarization field is compromised.
-Given this general definition for the radial function $G(\beta)$, note that the radial function $R(\beta)$ is just a special case formed by making the choice $b_{\ell}=1$.
-Note that for this choice the inverse of the multipole function is itself $b_{\ell}^{-1} = b_{\ell}$ and therefore $G^{-1}(\beta) = G(\beta)$.
+Here it is important to note that the radial function has to be chosen such that $G(\beta)$ has to be such that it vanishes at $\beta=0$ and $\beta=\pi$.
+One way to understand this is that the associated Legendre polynomials $P_{\ell}^2$ vanish at these values of the abscissa and hence cannot be used to describe function which don't have this property.
+Another way to understand this requirements is that at these locations the coordinate dependence of the Stokes parameters cannot be integrated out, since the azimuthal angle is ill defined and hence the convolution kernel needs to have vanishing contribution from these locations.
+\revisit{The normalization of these functions is not important, since that just defines a convention.
+One just needs to ensure to be consistent with the convention once a choice has been made.} \comment{find a better location for this}
 
-While modifying the radial function, it makes more sense to make a choice on the real space function $G(\beta)$ instead of choosing the multipole function $b_{\ell}$.
-We use the orthogonality property of associated Legendre polynomials to express the multipole function $b_{\ell}$ as,
-%
-\beq
-b_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl}
-\eeq
-%
-where we have used the orthonormality property of the associated Legendre polynomials to arrive at the above equation.
-Note that once the choice of $G(\beta)$ is made, the inverse function $G^{-1}(\beta)$ is automatically defined by the forward relation given in \eq{eq:mod_rad_inverse}.
+In contrast,  the beam convolution function $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$ and a circularly symmetric beam's harmonic representation $b_{\ell}$ are the coefficients of expansion of $B(\beta)$ in the Legendre polynomial $P_{\ell}^0$ basis.
+\comment{Distinguishing E/B localization characterized by $g_{\ell}$ from E/B smoothing characterized by $b_{\ell}$.}
 
-In \sec{sec:local_conv_eb} we constructed localized convolution kernels by multiplying $R(\beta)$ with an apodized version of the step function $\theta_{\rm apo}(r_{\rm cutoff})$.
-The oscillation seen in the spectra in \fig{fig:eb-spectra_rad_cutoff} can be explained to be due to this effective beam characterized by $b_{\ell}^2$ operating on the power spectra.
-The effective beam can be evaluated by computing the multipole function $b_{\ell}$ as follows,
-%
-\beq
-b_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{r_{\rm cutoff}} R(\beta) \theta_{\rm apo}(r_{\rm cutoff})  P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl} \,,
-\eeq
-%
-where the upper limit of the integration is set to $r_{\rm cutoff}$ since the function $\theta_{\rm apo}(r_{\rm cutoff})$ vanishes for $\beta>r_{\rm cutoff}$.
-The function $b^2_{\ell}-1$ matches the oscillation seen in \fig{fig:eb-spectra_rad_cutoff} as  seen in \fig{fig:match_cl_oscillations} where the two results have been over plotted.
-%
-\begin{figure}[!t] 
-\centering
-\subfigure[]{\includegraphics[width=0.98\columnwidth]{analytical_cl_oscillations_vs_data.pdf}}
-\caption{The thin lines depicts the same spectral differences as those seen in \fig{fig:eb-spectra_rad_cutoff}, while the thick lines of the corresponding color depict the function $b_{\ell}^2 -1$ as derived from evaluating \eq{eq:gb2bl} for different $r_{\rm cutoff}$}.
-\label{fig:match_cl_oscillations}
-\end{figure}
-%
-The apodized step function in this case transition from 1 at $\beta < r_{\rm cutoff} -w$ to 0 at $r_{\rm cutoff}$ over a width $w= 3^{\circ}$ with a cosine squared profile .
-
+The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
+To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
+In such a case these two method of evaluating the relevant fields is not identical.
+An example of this claim is depicted in \fig{fig:example_gbeta}.
 %
@@
 %
+
+Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
+For instance evaluating the E and B fields in the vicinity of the poles is are prone to receiving significant contributions from strong foregrounds near the equator.
+Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
+On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.
+
+%In \sec{sec:local_conv_eb} we constructed localized convolution kernels by multiplying $R(\beta)$ with an apodized version of the step function $\theta_{\rm apo}(r_{\rm cutoff})$.
+The oscillation seen in the spectra in \fig{fig:eb-spectra_rad_cutoff} can be explained to be due to this effective beam characterized by $g_{\ell}^2$ operating on the power spectra.
+The effective beam can be evaluated by computing the multipole function $g_{\ell}$ as follows,
+%%
+%\beq
+%g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{r_{\rm cutoff}} R(\beta) \theta_{\rm apo}(r_{\rm cutoff})  P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl} \,,
+%\eeq
+%%
+%where the upper limit of the integration is set to $r_{\rm cutoff}$ since the function $\theta_{\rm apo}(r_{\rm cutoff})$ vanishes for $\beta>r_{\rm cutoff}$.
+The function $b^2_{\ell}-1$ matches the oscillation seen in \fig{fig:eb-spectra_rad_cutoff} as  seen in \fig{fig:match_cl_oscillations} where the two results have been over plotted.
+%%
+%\begin{figure}[!t] 
+%\centering
+%\subfigure[]{\includegraphics[width=0.98\columnwidth]{analytical_cl_oscillations_vs_data.pdf}}
+%\caption{The thin lines depicts the same spectral differences as those seen in \fig{fig:eb-spectra_rad_cutoff}, while the thick lines of the corresponding color depict the function $g_{\ell}^2 -1$ as derived from evaluating \eq{eq:gb2bl} for different $r_{\rm cutoff}$}.
+%\label{fig:match_cl_oscillations}
+%\end{figure}
+%%
+%The apodized step function in this case transition from 1 at $\beta < r_{\rm cutoff} -w$ to 0 at $r_{\rm cutoff}$ over a width $w= 3^{\circ}$ with a cosine squared profile .
+
+\subsection{Recovering the default E and B mode spectra}
+The convolution kernels defined using these modified radial functions returns some E' and B' mode maps,
+%
+\beq
+\bar{S}' = \bar{O}' * \bar{P}
+\eeq
+%
+ which are not the standard $E$ and $B$ modes maps.
+We would now like to relate the spectra of these modified $E'$ and $B'$ mode maps to the standard spectra.
+Even though the $G(\beta)$ maybe such that it doesn't have an accurate band limited  description, the spectra are always evaluated to a definite band limit.
+Therefore the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be used to appropriately normalize the spectra so as to match the standard E and B mode spectra.
+ Specifically it can be shown that the spectra of $E'$ and $B'$ field is related to the spectra of the spectra of the standard E and B fields via the following simple relation,
+ %
+ \beq
+ C_{\ell}^{E',B'} =  C_{\ell}^{E,B} g_{\ell}^2\,,
+ \eeq
+ %
 %--------------------------------------------------------

### 2017-10-22 articles/draft/sections/real_space_formalism.tex
updates to draft, section on generalized operators. revised figuresdepicting the pixel scaling as a function of maximum multipole

@@
 \beqry 
-[E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
+[E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
 &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right)\,, \label{eq:qu2eb_convolution} 
@@
 \beqry 
-[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
+[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}  P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
 {}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)\,, 

### 2017-10-25 codes/modules/mod_rad_cl_correction.py
Updates to section discussing the generalized operators. added new figures depicting the radial kernel corresponding to some Gaussian beams and the effective beams corresponding to some modified radial functions. Added a module named :mod_rad_cl_correction.py which computed the radial function and its harmonic transform. Added a notebook: analysis >> Modified radial kernel cl corrections which uses this module and generates the plots seen in fig 4 of the draft

@@ -1,0 +1,111 @@
+import numpy as np
+from scipy.special import lpmn as lpmn
+from scipy.interpolate import interp1d
+import numpy.polynomial.legendre as lgdr
+import scipy.integrate as intg
+import healpy as h
+import time
+
+def mod_gbeta(x,shift=15.,width=5.,slope=2.,expslope=2.):
+	shift=shift*np.pi/180. ; width=width*np.pi/180.
+	return (x**slope)*np.exp(-((x-shift)/(np.sqrt(2.)*width))**expslope)
+
+def get_mod_gbeta_root(shift=15.,width=5.,slope=2.):
+	return max(0.5*(shift + np.sqrt(shift**2. + 4.*slope*width*width)),0.5*(shift - np.sqrt(shift**2. + 4.*slope*width*width)))*np.pi/180.
+
+def return_beta0(lmax):
+	return min(180.,180.*24./lmax)*np.pi/180.
+
+def pl2norm(l):
+	return 2.*np.pi/(((l+2)*(l+1)*l*(l-1))**0.5)
+
+def fn_step_apo(theta,beta0,frac_beta0=3.,frac_apow=0.1):
+	'''
+	Returns a step function with a cosine squared apodization profile
+	Input variables:
+	frac_beta0 = Takes the factor of beta0 as the radial cutoff.
+	apow = Takes fraction of radial cutoff as in put.
+	example: frac_beta0=3. implies the rcutoff=3*beta0.
+		 apow=0.1. implies 10% of rcutoff is the apodization width.
+	'''
+	theta0=frac_beta0*beta0 ; apow=frac_apow*theta0
+	xp=(theta-(theta0-apow))*np.pi/(2.*apow)
+	stepfn=np.zeros(theta.size,float)
+	stepfn=np.cos(xp)**2.
+	stepfn[theta<=theta0-apow]=1.
+	stepfn[theta>theta0]=0.
+	return stepfn
+
+def har_high_pass_filter(ell,ell0,deltaell):
+    fl=np.ones(ell.size,float)
+    ellp=(ell-(ell0+deltaell))*pi/(2.*deltaell)
+    fl=cos(ellp)**2.
+    fl[ell<ell0]=0.
+    fl[ell>ell0+deltaell]=1.
+    return fl
+
[…]

### 2017-10-26 articles/formalism/article.tex
made a few folder in articles named formalism. Updated abstract. Monor modifications to notebook making the modified radial kernel plots

--- 2017-09-11 article/article.tex
@@
 \usepackage{subfigure}
-\renewcommand*{\thesubfigure}{}
+%\usepackage{soul}
+\usepackage[normalem]{ulem}
+
+\renewcommand*{\thesubfigure}{(\roman{subfigure})}
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
@@
 %\usepackage{caption}
-%\usepackage{subfigure}
 %\usepackage{float}
@@
 \usepackage{bbold}
+%\usepackage{caption}
+%\usepackage{subcaption}
 
@@
 \newcommand{\eeqrys}{\end{eqnarray}\end{subequations}}
+
 \newcommand{\fqu}{\begin{bmatrix} Q \\ U \end{bmatrix}}
@@
 
+\def\vp#1{$\bar{P}_{#1}$ }
+\def\vs{$\bar{S}~$}
+
 \newcommand{\st}{\sout}
@@
 
-\graphicspath{ {"./figures/"} }
+\graphicspath{ {"../../figures/"//} }
 
@@
 
-\title{Local real space operators for translating Stokes Q/U to E/B maps on the sphere }
+\title{Quantifying the locality of operators that translate Stokes $Q$ \& $U$ to scalars $E$ \& $B$}
+\title{Real space operators for Stokes $Q$ \& $U$ to scalars $E$ \& $B$ translation}
 \author[]{Aditya Rotti and}
@@
 \abstract{
-\noindent We derive real space operators to translate Stokes Q/U to coordinate independent even and odd parity E/B fields on the sphere and demonstrate their numerical equivalence to the harmonic space methods.
-In process we also derive real space operators which allow direct decomposition of measured Q/U into Q/U fields corresponding to E-modes and B-modes respectively.
-These operators are derived on the sphere and account for the curvature effects.
-The analytical derivations reveal a functional form for the radial kernel, which quantifies the non-local nature of the E and B fields.
-%and their dependence on the band limit of the measurement. 
-These real space operators allow the computation of E and B field in each pixel by integrating in a small region around it, and hence it can be easily parallelized and is not memory intensive.
-A major drawback of these real space operators is that they cannot reliably construct modes on large angular scales $\ell<50$ with ease.
-Finally, this study motivates the construction of more locally defined E and B maps, by making desired alterations to the radial filter.
-We demonstrate that these altered E mode and B mode constructions do not significantly distort spectral information on small angular scales.
-%Such locally constructed E and B maps may help mitigate the foreground leakage issue across the two modes.
-}
+\noindent  We derive fully sky real space operators to translate Stokes Q \& U parameters to scalars $E$ \& $B$ and vice versa.
+We explicitly show that these local real space operator are fully characterized by the spin-0 $Y_{\ell 2}$ spherical harmonic functions.
+These real space operators make transparent the association of radial and tangential patterns of polarization with the E modes and that of  the clockwise and anti-clockwise pinwheel patterns of polarization with B-modes.
+We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidate these derivations.
+Using this new notation also allows us to derive real space operators which decompose the measured Stokes parameters into those corresponding to E-modes and B-modes respectively, without ever evaluating the scalar fields themselves.
+We use these analytical derivations us to quantify the non-local nature of the relation between the two representations of the polarization field.
+We present a prescription for generalizing these operators, which allow the non-local behavior of these operators to be a tunable parameter.
+We derive constraints on these generalized operators to ensure reliable recovery of the standard $E$ and $B$ fields and the corresponding power spectra.
+This is part 1 of a series of papers where we explore these operators.}
 
@@
 \include{./sections/introduction}
-\include{./sections/real_space_operators}
-\include{./sections/discussion.tex}
+\include{./sections/real_space_formalism}
+\include{./sections/kernel_discussion}
+\include{./sections/generalizedeb}
+\include{./sections/discussion}
 \include{./sections/appendix}

### 2017-10-26 articles/formalism/sections/generalizedeb.tex
made a few folder in articles named formalism. Updated abstract. Monor modifications to notebook making the modified radial kernel plots

--- 2017-10-22 articles/draft/sections/generalizedeb.tex
@@
 \beqry
-G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \\
-G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=\ell_{\rm min}} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
+G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \\
+G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
 \eeqry
@@
 While defining these alternate operators by modifying the radial part of the kernels, it seems more natural to make a choice on the real space function $G(\beta)$ as compared to choosing the multipole function $g_{\ell}$.
-Using the orthogonality property of associated Legendre polynomials it can be shown that the multipole function $g_{\ell}$ is given by the following integral once the radial function $G(\beta)$ is specified,
+Using the orthogonality property of associated Legendre polynomials it can be shown that the multipole function $g_{\ell}$ is given by the following integral over the radial function $G(\beta)$,
 %
@@
 %
-Here it is important to note that the radial function has to be chosen such that $G(\beta)$ has to be such that it vanishes at $\beta=0$ and $\beta=\pi$.
-One way to understand this is that the associated Legendre polynomials $P_{\ell}^2$ vanish at these values of the abscissa and hence cannot be used to describe function which don't have this property.
+Here it is important to note that the radial function $G(\beta)$ has to be chosen such that it vanishes at $\beta=0$ and $\beta=\pi$.
+One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
 Another way to understand this requirements is that at these locations the coordinate dependence of the Stokes parameters cannot be integrated out, since the azimuthal angle is ill defined and hence the convolution kernel needs to have vanishing contribution from these locations.
-\revisit{The normalization of these functions is not important, since that just defines a convention.
-One just needs to ensure to be consistent with the convention once a choice has been made.} \comment{find a better location for this}
+\revisit{The normalization of these functions is not critically important, since any choice defines a convention.
+It is important to ensure consistency with the convention once a choice has been made.} \comment{find a better location for this}
 
-In contrast,  the beam convolution function $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$ and a circularly symmetric beam's harmonic representation $b_{\ell}$ are the coefficients of expansion of $B(\beta)$ in the Legendre polynomial $P_{\ell}^0$ basis.
+In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+A circularly symmetric beam is represented in harmonic space by the multipole function $b_{\ell}$ which can be derived by evaluating the coefficients of expansion of the function $B(\beta)$ defined at the pole in the Legendre polynomial $P_{\ell}^0$ basis.
+The effective instrument beam is \revisit{almost} always identical for $E$ and $B$ modes.
 \comment{Distinguishing E/B localization characterized by $g_{\ell}$ from E/B smoothing characterized by $b_{\ell}$.}
-
-The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
-To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
-In such a case these two method of evaluating the relevant fields is not identical.
-An example of this claim is depicted in \fig{fig:example_gbeta}.
+%
+\beq
+B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} b_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
+\eeq
+%
+\comment{A co-polarized beam which measures the Stokes parameters is not the same as a smoothing beam measuring a scalar field. Is it important to discuss the polarization beam details here ?}
 %
@@
 \centering
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{example_gbeta.pdf}}
-\subfigure[]{\includegraphics[width=0.49\columnwidth]{example_eff_bl.pdf}}
-\caption{}
+\subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.32\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
+\subfigure[]{\includegraphics[width=0.32\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
+\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.32\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
+\caption{\textit{Left:} The vertical dashed gray line depicts the approximate pixel size $\Delta_{\rm pix} = \sqrt{\frac{4 \pi}{N_{\rm pix}}}$ of a Nside=512 Healpix map.
+The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}.
+The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arcminutes respectively.
+The red curve depicts an example modified radial function: $G(\beta)=\mathcal{N} \beta^n \exp{\left[ -\left( \frac{\beta-\beta0}{\sqrt{2} \sigma} \right)^s \right]}$ with parameters set to the following values $[n=1;\, \beta_0=0 ;\, \sigma = 2\Delta_{\rm pix} ;\, s=1.5]$.
+The black dashed curve depicts the band limited reconstruction of the modified radial function $G(\beta)$.
+We intentionally have plotted $\beta G(\beta)$ to clearly depict the high $\beta$ behavior of these functions.
+\textit{Middle: } This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
+The dashed curves of the corresponding color depict the inverse of the harmonic functions.
+\textit{Right:} This figure depicts the beam function $B(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an instrument beam.}
 \label{fig:example_gbeta}
@@
 %
+Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has important differences, in harmonic space they play identical roles.
+Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
+The modified radial kernel resulting from a few example Gaussian beams are depicted in \fig{fig:bl_gbeta}.
+it is possible to interpret the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ as those corresponding to some circularly symmetric instrument beam function.
+The beam function corresponding to the default radial kernel and the modified radial kernel $G(\beta)$ are depicted in \fig{fig:gl_bbeta}.
 
+\comment{Move the following two paragraphs to final discuss}
+\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
+To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
+In such a case these two method of evaluating the relevant fields is not identical.
+An example of this claim is depicted in \fig{fig:example_gbeta}.\\
 Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
@@
 Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
-On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.
+On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}
 
@@
 \subsection{Recovering the default E and B mode spectra}
-The convolution kernels defined using these modified radial functions returns some E' and B' mode maps,
+The convolution kernels defined using a modified radial function $G(\beta)$ returns some scalar $E'$ and $B'$ mode maps,
 %
@@
 which are not the standard $E$ and $B$ modes maps.
-We would now like to relate the spectra of these modified $E'$ and $B'$ mode maps to the standard spectra.
+Since the the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some beam,  the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the spectra of the standard $E$ and $B$ fields via the following relation,
+ %
+ \begin{subequations}
+ \beqry
+C_{\ell}^{EE,BB,EB} &= &C_{\ell}^{E'E',B'B',E'B'} /   g_{\ell}^2\,.\\
+C_{\ell}^{TE,TB}  &=&  C_{\ell}^{TE',TB'} / g_{\ell}\,.
+ \eeqry
+ \end{subequations}
+ %
+The auto and cross spectra with the standard $E$ and $B$ fields can be recovered from the modified fields $E'$ and $B'$.
+Their accurate recovery only relies on the inverse of the harmonic functions $1/g_{\ell}$ being well behaved, which can be ensured by smartly choosing the radial function $G(\beta)$.
+
+Unlike the instrument beam, the radial function $G(\beta)$ is an analysis choice.
+functions are perfectly known.
+Since the radial kernel is perfectly known it is in principle possible to perfectly deconvolve the same.
+In contrast the beam function $B{\beta}$ has to be inferred from measurement of point source and hence is not known exactly and therefore the deconvolution is only approximate.
 Even though the $G(\beta)$ maybe such that it doesn't have an accurate band limited  description, the spectra are always evaluated to a definite band limit.  
-Therefore the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be used to appropriately normalize the spectra so as to match the standard E and B mode spectra.
- Specifically it can be shown that the spectra of $E'$ and $B'$ field is related to the spectra of the spectra of the standard E and B fields via the following simple relation,
- %
- \beq
- C_{\ell}^{E',B'} =  C_{\ell}^{E,B} g_{\ell}^2\,,
- \eeq
- %
 %--------------------------------------------------------

### 2017-10-26 articles/formalism/sections/introduction.tex
made a few folder in articles named formalism. Updated abstract. Monor modifications to notebook making the modified radial kernel plots

--- 2017-10-09 article/sections/introduction.tex
@@
+\textbf{Some comments, questions and ideas that occurred to me while writing the draft:}
+\begin{enumerate}
+\item Using these local convolution can one now understand the E to B leakage occurring due to masking ?
+
+\item Healpix has rings at constant latitude.
+So the real space convolution is only perfect for pixels near the pole ?
+What happens when you consider pixels around any arbitrary pixel on a Healpix map, they are probably not arranged in rings.
+Maybe for this reason working with upgraded map works and finer pixels allow for a better approximation of rings around arbitrary pixels ??
+
+\item The Zaldariagga radial function $1/\theta^2$ cannot be correct, since it does not vanish at $\beta=\pi$, while it is defined to be zero at $\beta=0$.
+I guess since its in the flat sky limit, the $\beta=\pi$ issue is not relevant.
+\end{enumerate}
+
+\textbf{To do list:}
+\begin{enumerate}
+\item Check whether the local Healpix works for primordial B-mode spectrum.
+\item Check the generation of local kernels by using a an effective beam in harmonic space. pl2 transformed
+\item How do the  coefficients of expansion for some radially compact kernel, derived from pl2 transforms differ from that of a pl0 transform ? 
+\end{enumerate}
+
+\newpage
 \section{Introduction}
@@
 We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.\\ \\ \\
-
-\textbf{Some comments, questions and ideas that occurred to me while writing the draft:}
-\begin{enumerate}
-\item Using these local convolution can one now understand the E to B leakage occurring due to masking ?
-
-\item Healpix has rings at constant latitude.
-So the real space convolution is only perfect for pixels near the pole ?
-What happens when you consider pixels around any arbitrary pixel on a Healpix map, they are probably not arranged in rings.
-Maybe for this reason working with upgraded map works and finer pixels allow for a better approximation of rings around arbitrary pixels ??
-\end{enumerate}

### 2017-10-27 articles/formalism/sections/kernel_discussion.tex
made a few folder in articles named formalism. Updated abstract. Monor modifications to notebook making the modified radial kernel plots
updates to sections in the formalism draft. Added the healpix rotation method to the section on visulaizing the local operators

--- 2017-10-19 article/sections/kernel_discussion.tex
@@
 \subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
-As seen in the previous sections, all the kernels separate into a part which depends only on the angular distance between pixels and another part that depends on the azimuthal orientation around the central pixel.
-The radial part of the kernels determines the non-locality of the operator.
-We numerically compute the radial kernels: $f, _{+2}f ~\&~ _{-2}f $ by evaluating the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [=2,192]$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
+
+\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
+In this case the Euler angles in the $z-y1-z2$ convention are simply given by: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$, where $(\theta_i,\phi_i)$ denote the coordinates of the location $\hat{n}_i$.} Since the Euler angle $\gamma=0$ when rotations are defined with respect to the pole, the respective kernels simplify to the following forms,
 %
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
-\caption{The figure depicts the radial part of the convolution kernels.
-These radial function have been evaluated with the band limit fixed at $\ell \in [2,192]$.
-The vertical dashed line marks the approximate size of a NSIDE=64 Healpix pixel.}
-\label{fig:beta_kernel}
-\end{figure}
+\begin{subequations} \label{eq:kernel_at_pole}
+\beqry
+\mathcal{M}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\theta_i,\phi_i) \,,\\
+\mathcal{I}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}{{}_{-2}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\theta_i,\phi_i) \,, \\
+\mathcal{D}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}{{}_{2}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\theta_i,\phi_i) \,.
+\eeqry
+\end{subequations}
 %
-Note that the function $f(\beta)$, which forms the radial part of the real space convolution kernel that translates the Stokes parameters Q \& U to scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-Recall that the fields E \& B are scalar and hence expected to be immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being coordinate independent.
+The kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums using the rotated harmonic coefficients given by,
+%
+\beq
+{}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2} \,,
+\eeq
+%
+where $D^{\ell}_{2 m}$ are the Wigner-D functions and ${{}_s}a_{\ell 2} = \sqrt{\frac{2\ell+1}{4 \pi}}$.
+These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
 
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-$_{-2}f(\beta)$ form the radial part of the band limited delta function $I$ and hence it contributes the most at the location of the central pixel.
-$_{+2}f(\beta)$ again has a vanishing contribution near the central pixel and it dominantly contributes in the neighbouring regions which are approximately at least 1 pixel distance away from the central pixel.
-
-The azimuthal dependencies of the convolution kernels, are specified as functions of the Euler angles $\alpha ~\&~ \gamma$.
-We evaluate the real and imaginary parts of the functions $\mathcal{M}, \mathcal{D}~\&~\mathcal{I}$ by calculating the Euler angles for all the pixels surrounding the central pixel and using them in \eq{eq:op_qu2eb}, \eq{eq:fn_i} and \eq{eq:fn_d} respectively.
+We compute the local convolution kernels using the procedure outlined in the discussion above.
+Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel we depict the kernels at different locations in \fig{fig:vis_kernel}, to give a sense of how these kernels vary across the sphere.
 %
@@
 %
-\revisit{Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel, we evaluate and depict the kernels at different locations, to give a sense of how these kernels vary across the sphere.} For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
-All the plots have been rotated such that the pixel around which the kernels are evaluated lies in the centre marked by the back circle.
-The results are depicted in \fig{fig:vis_kernel}.
+For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
+All the plots have been rotated such that the central location $\hat{n}_j$ around which the kernels are computed lies in the centre marked by the back circle.
 
-The function $\mathcal{M}$ is identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-\st{The only contrasting locations are the poles (i.e.
-$|b|=90^{\circ}$), where the functions $\mathcal{M}_r$ \& $\mathcal{M}_i$ are rotated by $45^{\circ}$  as compared to the respective functions evaluated at locations where $|b|\neq 90^{\circ}$.} Also note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
+The real and imaginary part of the kernel $\mathcal{M}$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
+Note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
 Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
-\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
+%\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
 Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
@@
 \subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
+
+As seen in the previous sections, all the kernels separate into a part which depends only on the angular distance between pixels and another part that depends on the azimuthal orientation around the central pixel.
+The radial part of the kernels determines the non-locality of the operator.
+We numerically compute the radial kernels: $f, _{+2}f ~\&~ _{-2}f $ by evaluating the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [=2,192]$.
+The resultant functions are depicted in \fig{fig:beta_kernel}.
+%
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
+\caption{The figure depicts the radial part of the convolution kernels.
+These radial function have been evaluated with the band limit fixed at $\ell \in [2,192]$.
+The vertical dashed line marks the approximate size of a NSIDE=64 Healpix pixel.}
+\label{fig:beta_kernel}
+\end{figure}
+%
+Note that the function $f(\beta)$, which forms the radial part of the real space convolution kernel that translates the Stokes parameters Q \& U to scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
+Recall that the fields E \& B are scalar and hence expected to be immune to coordinate definitions.
+The locally defined Stokes parameters however necessarily depend on the coordinate definition.
+Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being coordinate independent.
+
+The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
+$_{-2}f(\beta)$ form the radial part of the band limited delta function $I$ and hence it contributes the most at the location of the central pixel.
+$_{+2}f(\beta)$ again has a vanishing contribution near the central pixel and it dominantly contributes in the neighbouring regions which are approximately at least 1 pixel distance away from the central pixel.
+
 It is clear from previous discussions that that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.

### 2017-10-27 articles/formalism/sections/real_space_formalism.tex
updates to sections in the formalism draft. Added the healpix rotation method to the section on visulaizing the local operators

--- 2017-10-22 articles/draft/sections/real_space_formalism.tex
@@
 \beqry \label{eq:spin-pol}
-_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
+_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  \, {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
 \eeqry
@@
 \beq \label{eq:ebdef}
-\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  +  \eth^2 _{- 2}X(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
+\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}\bar{X}(\hat{n})  +  \eth^2 _{- 2}\bar{X}(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
 \eeq
@@
 \beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}X_{\ell m} + _{-2}X_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}X_{\ell m} - _{-2}X_{\ell m} \Big] 
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + _{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - _{-2}\tilde{X}_{\ell m} \Big] 
 \eeq
@@
 Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
-We make this choice since the CMB spectra are more closely related to the fields E \& B.
+%We make this choice since the CMB spectra are more closely related to the fields E \& B.
 %--------------------------------------------------------
@@
 
-\textit{Euler angles:} All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Owing to this fact we begin by briefly describing the Euler angles and present a way to think about them.
-The local cartesian coordinate system at any point on the sphere is defined such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east.
-The Euler angles define rotations that transforms the local cartesian coordinate system defined at the location $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
-The Euler angles can be evaluated using the following functions of the angular coordinates of the two locations $\hat{n}_0 \equiv (\theta_0 , \phi_0)$ and $\hat{n}_i \equiv (\theta_i, \phi_i)$,
-%
-\beqrys \label{eq:fn_euler}
-\tan{\alpha} &=& \frac{\sin{(\phi_i - \phi_0)} \sin{\theta_i}}{\sin{\theta_i}\cos{\theta_0} \cos{(\phi_i - \phi_0)} - \sin{\theta_0} \cos{\theta_i} } \,, \\
-\cos{\beta} &=& \sin{\theta_i}\sin{\theta_0} \cos{(\phi_i -\phi_0)} + \cos{\theta_i}\cos{\theta_0} \,,\\
-\tan{\gamma} &=& \frac{ - \sin{(\phi_i - \phi_0)} \sin{\theta_0}}{\sin{\theta_0}\cos{\theta_i} \cos{(\phi_i - \phi_0)} - \sin{\theta_i} \cos{\theta_0} } \,,
-\eeqrys
-%
-where $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-In more physical terms, these angles can be understood as follow: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
-The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, such that the z-axes of the two coordinate systems are parallel to each other.
-Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
-The simplest case is when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
-In this case it is easy to check by substituting these coordinate values in  \eq{eq:fn_euler} that the Euler angles are: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$.
-While evaluating the above functions we follow the convention that $\beta$ lies in the domain $[0, \pi]$ and that the angles $\alpha ~\&~ \gamma$ lie in the domain $[-\pi,\pi]$.
-It is important to assign the proper signs to $\alpha ~\&~ \gamma$ by duly accounting for the signs of the term in the numerator and the denominator.
-\revisit{While in following section we present results in terms of these Euler angles, the local kernels surrounding any pixel can be simply evaluated using standard Healpix functions.
-We give the details of this procedure in \app{sec:rot_ker_healpix}}.
-%--------------------------------------------------------
 %--------------------------------------------------------
@@
 %
-\beqrys
+\begin{subequations}\label{eq:qu2eb_gen_kernel}
+\beqry
 \mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
@@
 &=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqrys
+\eeqry
+\end{subequations}
 %
@@
 [E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right)\,, \label{eq:qu2eb_convolution} 
+&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right) = - \Bigg\lbrace \mathcal{M}^* \circ {}_{+2}X \Bigg\rbrace(\hat{n}_0)\,, \label{eq:qu2eb_convolution}
 \eeqry
@@
 [Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}  P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
-{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)\,, 
+{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)= - \Bigg\lbrace \mathcal{M} \circ [E + iB] \Bigg\rbrace(\hat{n}_0)\,,
 \eeqry

### 2017-10-28 articles/formalism/sections/real_space_formalism.tex
Revised sections 3.1 and 3.2

@@
 %--------------------------------------------------------
-\section{E/B description of CMB polarization} \label{sec:pol-intro}
+\section{The spin-0 description of CMB polarization} \label{sec:pol-intro}
 %--------------------------------------------------------
@@
 \section{Real space operators} \label{sec:real_space_operators}
-In this section we derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
-We also derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{\rm E} that correspond to E-modes and another vector \vp{\rm B} that corresponds to the B-modes of polarization, such that \vp{} = \vp{\rm E} + \vp{\rm B} (without ever evaluating the E \& B fields or their spherical harmonics).
-For carrying out these derivations we extensively use the matrix notation introduced in \sec{sec:mat_pol_intro}.
-
+The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization.
+In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
+This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics.
 %--------------------------------------------------------
-\subsection{Evaluating E \& B fields from measured Stokes parameters Q \& U}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we described how the scalar fields E \& B are derived from the Stokes parameters Q \& U.
-To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 field $({}_{\pm2} \bar X)$, taking linear combinations of the resultant coefficients of expansion $({}_{\pm 2} \tilde X_{\ell m})$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar E \& B fields on the sphere.
-We use the relations given in \eq{eq:pol_data_relns}, to write down an equation relating the real space vector of scalars \vs to the polarization vector \vp{} as given below,
+\subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
+In \sec{sec:pol-primer} we described the standard procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
+%To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
+Here we derive the real space convolution kernels on the sphere, which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
+We use the relations given in \eq{eq:pol_data_relns}, to write down an equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
 %
@@
 &=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i {}_{2}Y^{T*}_j - {}_{0}Y_i {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i {}_{2}Y^{T*}_j + {}_{0}Y_i {}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
+&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i ~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i ~ {}_{2}Y^{T*}_j - {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j + {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
 \eeqrys
@@
  where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
+The $m$ sum over the product of two spherical harmonic functions with spins $s_1$ and $s_2$ respectively, is given by the following identity \cite{varshalovich},
+%
+\beq \label{eq:sum_spin_shf}
+ \sum_{m}{{}_{s_1}}Y^*_{\ell m}(\hat{n}_i){{}_{s_2}}Y_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta,\alpha) e^{- i s_2 \gamma} \,,
+\eeq
+%
+where $\alpha, ~\beta ~\&~ \gamma$ denote the Euler angles. Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
 %
@@
 \mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}^*_{\ell m}(\hat n_i) {{_2}Y}_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
+&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) \, {{_{-2}}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
 &=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
@@
 %
-where we have used the property of summation over spin spherical harmonics (see \eq{eq:sum_spin_shf}) listed in Appendix \ref{sec:ylm_mathprop}.
+where we have used the identity given in \eq{eq:sum_spin_shf} to simplify the product of the spherical harmonic functions.
 On simplifying \eq{eq:qu2eb_ker_1}, the local convolution kernel can be cast in this simple form,
@@
 where indices i,j map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space E \& B operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
+\revisit{A similar equation for real space $E$ \& $B$ operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
 
-The scalar fields E \& B can now be directly derived from the measured Stokes Q \& U parameters by evaluating the following convolution,
+The scalar fields $E$ \& $B$ can now be directly derived from the measured Stokes $Q$ \& $U$ parameters by evaluating the following convolution,
 %
@@
 [E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right) = - \Bigg\lbrace \mathcal{M}^* \circ {}_{+2}X \Bigg\rbrace(\hat{n}_0)\,, \label{eq:qu2eb_convolution}
+&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right) \,, \\
+&=& - \Bigg\lbrace \mathcal{M}^* \circ {}_{+2}X \Bigg\rbrace(\hat{n}_0)\,, \label{eq:qu2eb_convolution} 
 \eeqry
@@
 where $\circ$ denotes a convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_0$ and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
-We know that the spin of product of functions with different spins is given by: ${}_{s_1}f {}_{s_2}g = {}_{s_1 +s_2}h$.
-Since $[Q + iU]$ is a field with spin +2 and the function $\exp(-i2\alpha)$ is a field with spin -2, the resultant field formed by the product of these two function has spin-0.
-This makes intuitive, the construction of the spin-0 E and B modes of polarization.
-Note that the coordinate dependence of the Stokes parameters cannot be integrated out at the location $\hat{n}_0$ where the scalar fields are to be evaluated since the azimuthal angle becomes ill-defined.
-This issue is averted by the fact that the radial function is formed by taking weighted linear combinations of $P_{\ell}^2$ Legendre polynomials which have vanishing contribution $(P_{\ell}^2(\beta) \propto \sin^2{\beta})$ as $\beta \rightarrow 0 ,\pi$.
-\revisit{Also note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
 
+The convolution kernel has a azimuthal part which depends only on the Euler angle $\alpha$ and has no multipole dependence and this is the primary operation which translates between the two different spin representation of CMB polarization.
+The radial part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, it depends only on the angular separation given by the Euler angle $\beta$ and it completely incorporates the multipole $\ell$ dependence of the kernel.
+It is the radial part of the kernel that completely determines the locality of this operator.
 Note that this kernel does not depend on the Euler angle $\gamma$ \comment{Why is that and how do you understand this ?
 }.
-This local convolution kernel has a part which depends only on the Euler angle $\alpha$ which has no multipole dependence.
-The remaining part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ which depends only on the Euler angle $\beta$ and completely incorporates the multipole $\ell$ dependence of the kernel.
-We will refer to $f(\beta,\ell_{\rm min},\ell_{\rm max})$ as the radial part of the kernel since it only depends on the angular distance between different locations.
-Its the radial part of the kernel that completely determines the locality of this operator.
 
-\rfedit{The azimuthal operations do not depend on the choice of basis functions, and can be argued as a requirement for constructing spin-0 fields by operating on spin-2 fields.
-The radial kernel however is determined by the choice of the basis functions.
-Motivated by this observation, one can now think of working with alternate basis functions which have different radial fall off.} \comment{This is generally true for all the local kernels.
+We know that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$.
+Since $[Q + iU]$ is a field with spin +2 and the field $\exp(-i2\alpha)$ has spin -2, the resultant field formed by the product of these two function has spin-0.
+This makes intuitive, the construction of the spin-0 E and B modes of polarization.
+Note that the coordinate dependence of the Stokes parameters cannot be integrated out at the location $\hat{n}_0$ where the scalar fields are to be evaluated and at the diametrically opposite location, since the azimuthal angle $\alpha$ becomes ill-defined at these points.
+The convolution kernel has vanishing contribution from these points, since the radial part of the kernel is given by a weighted linear combination of $P_{\ell}^2$ Legendre polynomials which $P_{\ell}^2(\beta) \propto \sin^2{\beta} \rightarrow 0 $ as $\beta \rightarrow 0 ,\pi$.
+\revisit{It is also interesting to note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
+
+\rfedit{The azimuthal operations do not depend on the choice of basis functions, and could have been been argued to have the form $e^{-i2 \alpha}$ by requiring to construct a spin-0 field given some spin-2 fields.
+The radial part of the kernel however is determined by the choice of the basis functions.
+Motivated by this observation, we can think of constructing convolution kernels with different radial dependences, hence allowing control over the non-locality of the convolution kernels.} \comment{This is generally true for all the local kernels.
 So shift this line to the section where we explore different radial functions.}
@@
 %--------------------------------------------------------
-\subsection{Evaluating Stokes parameters Q \& U fields from E \& B fields}\label{sec:eb2qu}
-The real space operator which translates E \& B fields to Stokes parameters Q \& U is derived using a similar procedure. The inverse operator is given by the following expression,
+\subsection{Evaluating Stokes parameters $Q$ \& $U$ from scalar fields $E$ \& $B$}\label{sec:eb2qu}
+The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure. The inverse operator is given by the following expression,
 %
+\begin{subequations}
 \beqry
-\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S}   \\
-&=&  \bar O^{-1} *\bar{S}
+\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} \,,  \\
+&=&  \bar O^{-1} *\bar{S}\,.
 \eeqry
+\end{subequations}
 %
-We do not provide the explicit calculations here, since the derivation is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
+We do not provide the explicit derivation here, since the procedure is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
 %
@@
 Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
-We can evaluate the Stokes Q \& U parameters from the scalar E \& B  fields by evaluating the following expression,
+We can evaluate the Stokes parameters  $Q$ \& $U$ from the scalar fields $E$ \& $B$ by evaluating the following expression,
 %
@@
 \beqry 
-[Q + iU](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}  P_{\ell}^{2}(\beta_{0j}) \right)  \mathbf{\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
-{}_{+2}X(\hat{n}_0) &=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB] \right)= - \Bigg\lbrace \mathcal{M} \circ [E + iB] \Bigg\rbrace(\hat{n}_0)\,,
+{}_{+2}\bar{X}(\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}  P_{\ell}^{2}(\beta_{0j}) \right)  {\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
+&=& - \Bigg\lbrace \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB]  \Bigg\rbrace (\hat{n}_0) \,, \\
+&=& - \Bigg\lbrace \mathcal{M} \circ [E + iB] \Bigg\rbrace(\hat{n}_0)\,, 
 \eeqry
@@
 %
-which is to be interpreted in the same manner as \eq{eq:qu2eb_simple}.
-Note that the only change in the convolution kernel as compared to that in \eq{eq:op_qu2eb} is that the signs of the off-diagonal block matrices are reversed.
-Alternatively, the $Y_{\ell 2}$ functions are not conjugated.
-This can again be simply understood as constructing a spin-2 field by taking a product of a spin-0 field: $[E +iB]$ with a spin $+2$ field: $\exp(+i2\alpha)$.
+which $\circ$ is to be interpreted as a convolution.
+The only change in the convolution kernel as compared to that in \eq{eq:qu2eb_simple} is that the $Y_{\ell 2}$ functions are not conjugated.
+This can again be simply understood as the construction of a spin-2 field by taking a product of a spin-0 field $[E +iB]$ with a spin $+2$ field $e^{+i2\alpha}$.
 The radial dependence of the operator ${\bar O}^{-1}$  is identical to the that of ${\bar O}$ as one may have expected.
-In this case all the coordinate dependence in encoded in the function $\exp(+i2\alpha)$, which is ill-defined at the poles ($\beta \rightarrow 0,\pi$) and hence the radial functions have to vanish at these locations, which is the case for the same reasons discussed previously.
+From the perspective of the scalar field $[E + iB]$, all the coordinate dependence of the Stokes parameters is encoded in the function $e^{+i2\alpha}$.
+The radial functions again have to vanish at $\beta \rightarrow 0,\pi$ for the same reasons that the function $e^{+i2\alpha}$ is ill defined at these locations.
 %--------------------------------------------------------
 %--------------------------------------------------------
-\subsection{Decomposing Q \& U Stokes parameters into those corresponding to E \& B modes respectively}
+\subsection{Decomposing Stokes parameters $Q$ \& $U$  into those corresponding to $E$ \& $B$ modes respectively}
 The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.

### 2017-10-31 articles/formalism/sections/kernel_discussion.tex
updated the discussion surrounding the visulization of the convolution kernels

@@
 \subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
-
-\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
-In this case the Euler angles in the $z-y1-z2$ convention are simply given by: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$, where $(\theta_i,\phi_i)$ denote the coordinates of the location $\hat{n}_i$.} Since the Euler angle $\gamma=0$ when rotations are defined with respect to the pole, the respective kernels simplify to the following forms,
-%
-\begin{subequations} \label{eq:kernel_at_pole}
-\beqry
-\mathcal{M}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\theta_i,\phi_i) \,,\\
-\mathcal{I}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}{{}_{-2}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\theta_i,\phi_i) \,, \\
-\mathcal{D}(\hat{n}_0,\hat{n}_i) &=& \sum_{\ell} \sqrt{\frac{2 \ell+1}{4 \pi}}{{}_{2}}Y_{\ell 2}(\theta_i,\phi_i) = \sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\theta_i,\phi_i) \,.
-\eeqry
-\end{subequations}
-%
-The kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums using the rotated harmonic coefficients given by,
-%
-\beq
-{}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2} \,,
-\eeq
-%
-where $D^{\ell}_{2 m}$ are the Wigner-D functions and ${{}_s}a_{\ell 2} = \sqrt{\frac{2\ell+1}{4 \pi}}$.
-These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
-
-We compute the local convolution kernels using the procedure outlined in the discussion above.
-Since its not easy to imagine how the Euler angles vary as a function of position of the central pixel we depict the kernels at different locations in \fig{fig:vis_kernel}, to give a sense of how these kernels vary across the sphere.
 %
@@
 \subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon45.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon30.pdf}}\\[-2ex]
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon30.pdf}}\\[-2ex]
 \subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
@@
 The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.
-}
+\comment{Whats the normalization?} }
 %from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
@@
 %
+
+\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole $\hat{z}=(0,0)$ (this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$).
+In this case the Euler angles in the $z-y1-z2$ convention are simply given by: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$, where $(\theta_i,\phi_i)$ denote the coordinates of the location $\hat{n}_i$.} Since the Euler angle $\gamma=0$ when rotations are defined with respect to the pole, the respective kernels simplify to the following forms,
+%
+\begin{subequations}
+\beqry 
+\mathcal{M}(\hat{z},\hat{n}_i) &=&  \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\hat{n}_i) \,;\\
+\mathcal{I}(\hat{z},\hat{n}_i) &=& \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\hat{n}_i) ~~\,;~~
+\mathcal{D}(\hat{z},\hat{n}_i) =\sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\hat{n}_i) \,,
+\eeqry
+\end{subequations}
+%
+where ${}_{s}a_{\ell 2} = \sqrt{\frac{2 \ell+1}{ 4 \pi}} ~~\forall ~~ s \in [0,-2,+2]$.
+The convolution kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums: $\sum_{\ell m} {}_{s}a_{\ell m}\,{}_{s}Y_{\ell m}(\hat{n}_i)$ using the rotated harmonic coefficients given by: ${}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2}$, where $D^{\ell}_{2 m}$ are the Wigner-D functions.
+These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
+\comment{Make parallels with instrument beam analysis here ? Or is it trivial since its obvious that all convolution problems can be cast in this form.}
+
+We compute the local convolution kernels using the procedure described above.
+To given an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the kernels at a few different locations.
 For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
-All the plots have been rotated such that the central location $\hat{n}_j$ around which the kernels are computed lies in the centre marked by the back circle.
+All the plots have been rotated such that the central location $\hat{n}_j$ marked by the black circle are in the centre of the figure.
+The horizontal and vertical lines that pass through the central black circle mark the local latitude and longitude respectively.
 
@@
 Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
+From \eq{eq:qu2eb_convolution_explicit} and \eq{eq:eb2qu_convolution_explicit} it is clear that $\mathcal{M}_r$ and $\mathcal{M}_i$ can be interpreted in the following ways,
 %\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
 Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
-
-The function $\mathcal{D}$ varies significantly as a function of galactic latitude of the central pixel.
-It varies from having a two fold symmetry at the poles to having a four fold symmetry at the equator as seen in the middle two columns of \fig{fig:vis_kernel}.
-This change in behavior is primarily due to the  dependence on the Euler angle $\gamma$.
-When the central pixel is nearly at the pole, $\gamma$ vanishes, and the azimuthal part of the function $D$ is identical to that of $\mathcal{M}$ and hence the two function look very similar as seen in the first row of \fig{fig:vis_kernel}.
-Also note that this function is distorted as parts of its domain pass the galactic poles.
-
-The function $\mathcal{I}$ shows similar behavior, varying with latitude, having an identical azimuthal behavior near the poles and being distorted in parts that overlap with the galactic poles.
-\revisit{This function, in the case of an infinite band limit reduces to a delta function at the position of the central pixel ($\lim_{\ell_{\rm max} \to \infty}: \mathcal{I}_r \rightarrow \delta(\hat{n}_0 - \hat{n}'),~ \mathcal{I}_i \rightarrow 0$), as discussed previously.
-Hints of this behavior can be seen by comparing the amplitudes of the real and imaginary parts of this function near the equator, depicted in the fifth row of the last two columns of \fig{fig:vis_kernel}.
-However note that this function significantly deviates from this behavior at higher galactic latitudes.
-The real and imaginary parts of this function contribute nearly equally near the vicinity of the poles.}  We invariably work with a specific band limit, hence both the real and imaginary parts of this functions make important non-zero contributions.
-
-We reiterate that all the function are invariant under changes in longitude of the central pixel, the latitude being held fixed as can be seen by comparing the figures in the second row (evaluated at $[b,\ell]=[87^{\circ},45^{\circ}]$) and third row (evaluated at $[b,\ell]=[87^{\circ},30^{\circ}]$) of \fig{fig:vis_kernel}, as one may have expected.
+%
+\begin{subequations}
+\beqry
+\bmat E= -\mathcal{M}_r \\ B =+\mathcal{M}_i  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_j)\\ U=0 \emat ~~;~~ \bmat E= -\mathcal{M}_i \\ B = - \mathcal{M}_r  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_j) \emat \,,  \\
+\bmat Q= -\mathcal{M}_r \\ U = -\mathcal{M}_i  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_j)\\ B=0 \emat ~~;~~ \bmat Q= +\mathcal{M}_i \\ U = - \mathcal{M}_r  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_j) \emat \,.
+\eeqry
+\end{subequations}
+%
+The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in the last four columns of \fig{fig:vis_kernel}.
+These kernels show a two fold symmetry in the vicinity of the poles and this arises due to Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
+Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is similar to $\mathcal{M}_r$ and $\mathcal{M}_i$ respectively.
+This also explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
+On moving to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
+This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{i2(\alpha + \gamma)} =1 + i0$.
+Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel} which depict the kernels evaluated at the equator while the middle two row depict the kernels evaluated at a latitudes of $b=87^{\circ}~\&~ 80^{\circ}$ serve to indicate the rate of this transition.
+These kernels are invariant under changes in longitude of the central pixel, the latitude being held fixed as one may have expected.
 

### 2017-10-31 articles/formalism/sections/real_space_formalism.tex
updated the discussion surrounding the visulization of the convolution kernels

@@
 \beq \label{eq:sum_spin_shf}
- \sum_{m}{{}_{s_1}}Y^*_{\ell m}(\hat{n}_i){{}_{s_2}}Y_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta,\alpha) e^{- i s_2 \gamma} \,,
+ \sum_{m}{{}_{s_1}Y}^*_{\ell m}(\hat{n}_i)\,{{}_{s_2}Y}_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta,\alpha) e^{- i s_2 \gamma} \,,
 \eeq
@@
 %
-\beq
+\beq \label{eq:eb2qu_convolution_explicit}
 \bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
@@
 \subsection{Decomposing Stokes parameters $Q$ \& $U$  into those corresponding to $E$ \& $B$ modes respectively}
-The Stokes Q \& U parameters can be decomposed into the scalar modes E \& B and vice verse, as seen in the previous sections.
-The E \& B modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
-It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to E modes and another \vp{\rm B} that purely contribute to the B modes of polarization.
 We can only measure the total Stokes vector which is a sum of the Stokes vectors corresponding to the respective scalar modes.
-In this section we derive the real space operators which directly perform this decomposition, without ever having to evaluate the E \& B modes.
-The derivation is similar to that discussed in \sec{sec:qu2eb}, though the algebra is a little more involved in this case.
-Here we use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
+The $E$ \& $B$ modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
+It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
+In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes.
+Though the algebra is a little more involved, the derivation is similar to that discussed in \sec{sec:qu2eb}, hence we refrain from presenting the detailed calculations here, but outline the key points.
+We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
 The Stokes parameters corresponding to each scalar mode are given by the following expressions,
@@
 where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
+%
+\begin{subequations}
 \beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,, \nonumber \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.\nonumber
+\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,, \\
+\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.
 \eeqry
+\end{subequations}
 %
-These functions can be further simplified using the properties of spin spherical harmonics listed in Appendix~\ref{sec:ylm_mathprop}.
+These functions can be further simplified using the identity of spin spherical harmonics given in \eq{eq:sum_spin_shf}.
 Specifically it can be shown that these functions reduce to the following mathematical forms,
@@
 \mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   _{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   {{}_{-2}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   _{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   {{}_{+2}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
 %
-where the functions,
+where the radial functions are given by,
 %
 \beq
-{}_{\pm2}f(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} _{ \pm 2}{f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
+{{}_{\pm2}f}(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} {{}_{ \pm 2}f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
 \eeq
 %
-can be expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
+where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
  %
@@
  %
-Finally, the Stokes parameters corresponding to the respective scalar fields are given by evaluating the following expressions, 
+Finally the Stokes parameters corresponding to the respective scalar fields can be computed by evaluating the following expressions, 
  %
@@
 %
-where all the symbols have their usual meaning. The above expression can be cast in the following simplified form,
+where all the symbols have their usual meaning. The above expression can be cast in the further simplified form,
 %
@@
 
-It is easy to show that the operator $\mathcal{D}$ is a complex but symmetric matrix and that the operator $\mathcal{I}$ is Hermitian.
-The function $I$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$), when interpreted as a matrix operator forms a band limited version of the identity matrix.
-Though its non-local ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes the operator $\mathcal{I}$ acts like an identity operator as is confirmed by the following identities it satisfies: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
-Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=I$.
+\comment{Recheck the math described below}
+The function $\mathcal{I}$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$).
+When interpreted as a matrix it is a band limited version of the identity matrix.
+Though it has non vanishing off diagonal elements ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
+Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
+It is useful to note that the operator $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{I}$ is an Hermitian operator.
 Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
@@
 While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other.
-\revisit{Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix.
-\comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} This indicates the loss of information occurred from the original data due to making this transformations with some assumed band limit.
-If one forces the sum of the operators to be exactly an identity operator, then one compromises on the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators.}
+
+Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix. 
+%\comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} 
+This non-exactness is representative of the loss of information resulting from making this transformation on the measured data with some imposed band limit.
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators, which is exact.

### 2017-10-31 articles/formalism/sections/kernel_discussion.tex
updated the caption of figure depicting the kernels at different locations

@@
 \caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit: $\ell \in [2,192]$.
-The functions have been sampled at an NSIDE=2048 resolution for visual appeal.
+These kernels have been evaluated with the band limit: $\ell \in [2,192]$ but sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal.
 The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated.
-The black star marks the location of the north galactic pole.
-The five rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.
-\comment{Whats the normalization?} }
+The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated while the black star marks the location of the north galactic pole.
+The four rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.}
 %from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}

### 2017-10-31 articles/formalism/sections/introduction.tex
resolved the clearpage issue which was occuring with the use of include command. Completed another pass at the non-locality of the E and B kernels

--- 2017-09-19 article/sections/introduction.tex
@@
 \section{Introduction}
-
 In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.
@@
 In \sec{sec:visualize_operator} we evaluate the real space operators and present visualizations of these functions.
-Here we discuss the locality of the real space E \& B operators.
+Here we also discuss the locality of the real space E \& B operators.
 In \sec{sec:numerical_implementation} we implement these operators to evaluate E \& B  maps from the Stokes parameters Q \& U and compare these maps and their spectra from those derived using Healpix.

### 2017-10-31 articles/formalism/sections/kernel_discussion.tex
resolved the clearpage issue which was occuring with the use of include command. Completed another pass at the non-locality of the E and B kernels

@@
 On moving to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
-This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{i2(\alpha + \gamma)} =1 + i0$.
-Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel} which depict the kernels evaluated at the equator while the middle two row depict the kernels evaluated at a latitudes of $b=87^{\circ}~\&~ 80^{\circ}$ serve to indicate the rate of this transition.
-These kernels are invariant under changes in longitude of the central pixel, the latitude being held fixed as one may have expected.
+This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} =1 + i0$.
+Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel} which depict the kernels evaluated at the equator $b=0^{\circ}$.
+The middle two row depict the kernels evaluated at a latitudes of $b=87^{\circ}~\&~ 80^{\circ}$ and serve to indicate the rate of this transition.
+These kernels are invariant under changes in longitude of the central pixel, the latitude being held fixed, as one may have expected.
 
 \subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
-
-As seen in the previous sections, all the kernels separate into a part which depends only on the angular distance between pixels and another part that depends on the azimuthal orientation around the central pixel.
-The radial part of the kernels determines the non-locality of the operator.
-We numerically compute the radial kernels: $f, _{+2}f ~\&~ _{-2}f $ by evaluating the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [=2,192]$.
-The resultant functions are depicted in \fig{fig:beta_kernel}.
 %
@@
 These radial function have been evaluated with the band limit fixed at $\ell \in [2,192]$.
-The vertical dashed line marks the approximate size of a NSIDE=64 Healpix pixel.}
+The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=64, which is the lowest resolution that allows access to $\ell_{\rm max}=192$.}
 \label{fig:beta_kernel}
@@
 %
-Note that the function $f(\beta)$, which forms the radial part of the real space convolution kernel that translates the Stokes parameters Q \& U to scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$).
-Recall that the fields E \& B are scalar and hence expected to be immune to coordinate definitions.
-The locally defined Stokes parameters however necessarily depend on the coordinate definition.
-Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being coordinate independent.
+\fig{fig:mixing_kernel} and the surrounding discussion provides a quantative understanding of the  azimuthal dependence of various kernels, however it is difficult to assess the radial nature of these kernels from these figures.
+The radial part determines the non-locality of the respective operators and encodes all the multipole dependence.
+We compute the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ by evaluating the respective multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.
 
-The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B.
-$_{-2}f(\beta)$ form the radial part of the band limited delta function $I$ and hence it contributes the most at the location of the central pixel.
-$_{+2}f(\beta)$ again has a vanishing contribution near the central pixel and it dominantly contributes in the neighbouring regions which are approximately at least 1 pixel distance away from the central pixel.
+Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa.
+Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$.
+The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars.
+Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in.
+${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}.
+${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.
 
-It is clear from previous discussions that that the non-locality of the E and B modes is determined by the radial part of the convolution kernels.
-To quantify this non-locality as a function of the maximum multipole accessible for analysis, we evaluate the radial part of the convolution kernel for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
+\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions.
+We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis.
+To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
 %
@@
 \subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel shows a plot of the radial kernels $f(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{+2}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{-2}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by the legends and fixed $\ell_{\rm min}=2$.
-The curves for each of these functions have been normalized such that the maximum of the curve is set to unity.
+\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by their legends and fixed $\ell_{\rm min}=2$.
+All the curves have been normalized such that the maximum of the curve is set to unity.
 The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
 The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function $f(\beta)~\&~ {}_{-2}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{-2}f(\beta)$ is seen to have a slightly steeper fall off $\propto \beta^{-1.65}$.}
+While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
 \label{fig:rad_ker_decay}
@@
 %
-The set of radial kernels so derived are plotted in \fig{fig:rad_ker_decay}.
-All the function have been normalized such that their global maxima is set to unity.
-Note that on increasing $\ell_{\rm max}$ the radial kernels shift to the left, attaining fractions of  their global maxima at progressively small angular distances $\beta$ from the central pixel.
-
-We have observed that the radial functions derived by evaluating the multipole sums to different maximum multipoles are self similar.
-Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
-We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
+The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity.
+We note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distance from the central pixel.
+The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$.
+At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$, the details of this fit can be seen in \fig{fig:rad_ker_decay}.
+We observe that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow an interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+%We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
 Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.
@@
 
-We are primarily interested in the non-local dependence of the scalar modes E \& B on the Stokes parameters Q \& U.
-We define the value of the abscissa at which the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-For a $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$, since the radial function never falls monotonously below 1\% of the global maxima of the function.
-Using the self similar  property of the radial function discussed above, we define the following: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ as the non-locality parameter, given the maximum multipole $\ell_{\rm max}$.
-\revisit{$\beta_0$ is not very sensitive to $\ell_{\rm min}$, though it can be important on making drastic changes to $\ell_{\rm min}$.
-} \comment{Quantify how changing $\ell_{\rm min}$ changes $\beta_0$}
-
-The envelope of the radial kernel $f(\beta,\ell_{\rm min},\ell_{\rm max})$ is observed to have a power law relation to the angular distance $\beta$ as seen in \fig{fig:rad_ker_decay}.
-At small values of $\beta$, which corresponds to the flat sky limit,  the radial function is proportional to $\beta^2$.
-In the intermediate range,  a fit by eye indicates that the envelope of the function is well represented by the power law $\beta^{-1.5}$.
-\comment{There isn't too much of a discussion surrounding the function ${}_{\pm}f(\beta)$.}
+It is useful to define a characteristic radius of the region from which the scalar fields evaluated at a point get most of their contribution from.
+Since the primarily interest is in the non-locality of the scalar modes $E$ \& $B$ we define the abscissa at which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
+For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima.
+Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.

### 2017-10-31 articles/formalism/sections/real_space_formalism.tex
resolved the clearpage issue which was occuring with the use of include command. Completed another pass at the non-locality of the E and B kernels

@@
 %--------------------------------------------------------
-\section{The spin-0 description of CMB polarization} \label{sec:pol-intro}
+%\section{The spin-0 description of CMB polarization} \label{sec:pol-intro}
 %--------------------------------------------------------
-\subsection{Polarization primer}\label{sec:pol-primer}
+\section{Polarization primer}\label{sec:pol-primer}
 The CMB polarization is measured in terms of Stokes Q and U parameters. These measurements can be combined to form the complex spin 2 polarization field as follows,
@@
 &=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big] f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
+&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big] {{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
 \eeqry
@@
 \beq\label{eq:op_qu2eb}
-\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
+\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
 \eeq
@@
 \beq \label{eq:qu2eb_convolution_explicit}
-\bmat E_i \\ B_i  \emat= -\Delta \Omega \sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \,,
+\bmat E_i \\ B_i  \emat= -\Delta \Omega \sum_{j=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \,,
 \eeq
@@
 \beq
-{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
+{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
 \eeq
@@
 \beq \label{eq:eb2qu_convolution_explicit}
-\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
+\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}} {{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
 \eeq
@@
 \mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   {{}_{-2}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   {{}_{\mi}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   {{}_{+2}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   {{}_{\md}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \beq
-{{}_{\pm2}f}(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} {{}_{ \pm 2}f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
+{{}_{\mdi}f}(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} {{}_{ \mdi}f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
 \eeq
@@
  \beqry
- _{\pm 2}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
+ _{\mdi}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
 &+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
@@
 \beqry \label{eq:op_qu2equbqu}
-\bmat Q_i \\ U_i  \emat_{E/B} &=& \sum_{j=1}^{N_{\rm pix}} \Bigg\lbrace {}_{-2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat  \\ &\pm& {}_{+2}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) &  \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  \sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
+\bmat Q_i \\ U_i  \emat_{E/B} &=& \sum_{j=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat  \\ &\pm& {}_{\md}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) &  \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  \sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
 \eeqry
@@
 \beqry
-{}_{+2}X_{E/B} &=&0.5 \Delta \Omega\sum_{j=1}^{N_{\rm pix}}  {}_{-2}f(\beta_{ij}) e^{-i2 (\alpha_{ij} + \gamma_{ij})} {}_{+2}X_j \pm {}_{+2}f(\beta_{ij}) e^{i2 (\alpha_{ij} - \gamma_{ij})} {}_{+2}X_j^*\,, \label{eq:qu2equbqu_explicit_convolution} \\
+{}_{+2}X_{E/B} &=&0.5 \Delta \Omega\sum_{j=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{ij}) e^{-i2 (\alpha_{ij} + \gamma_{ij})} {}_{+2}X_j \pm {{}_{\md}f}(\beta_{ij}) e^{i2 (\alpha_{ij} - \gamma_{ij})} {}_{+2}X_j^*\,, \label{eq:qu2equbqu_explicit_convolution} \\
 &=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
@@
 where in \eq{eq:qu2equbqu_explicit_convolution} we have suppressed the explicit multipole dependence of functions $_{\pm 2}f$ for brevity and in \eq{eq:qu2equbqu_convolution} $\circ$ denotes a convolution.
+\comment{Here it will be nice to interpret $e^{i2\gamma}[E-iB]$.
+We don't understand this as of now.}
 

### 2017-10-31 articles/formalism/sections/discussion.tex
Refined the discussion on generalized kernels and recovery of standard spectra

--- 2017-09-22 article/sections/discussion.tex
@@
 This should cause a compromise on spectral estimates of low multipoles, which correspond to large angular scales, much larger than radial cutoff.}
+\item{Cluster polarization will be measurable with future CMB experiments. These local estimators can be used to evaluate the local scalar modes of polarization.}
 
@@
 \end{itemize}
+
+\comment{Move the following two paragraphs to final discuss}
+\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
+To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
+In such a case these two method of evaluating the relevant fields is not identical.
+An example of this claim is depicted in \fig{fig:example_gbeta}.\\
+Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
+For instance evaluating the E and B fields in the vicinity of the poles is are prone to receiving significant contributions from strong foregrounds near the equator.
+Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
+On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}
+
 %

### 2017-10-31 articles/formalism/sections/generalizedeb.tex
resolved the clearpage issue which was occuring with the use of include command. Completed another pass at the non-locality of the E and B kernels
Refined the discussion on generalized kernels and recovery of standard spectra

@@
 %--------------------------------------------------------
-\comment{How does the radial kernel reduce to unity on evaluating the the operator on to its inverse ? This will be important to understand how to define alternate radial functions.}
 \section{Generalized operators}
-The azimuthal dependence of the convolution kernels which translate the Stokes parameters Q \& U to the scalar E \& B is determined by the spin properties of the field being operated upon and the spin of the resultant fields.
-Hence there is no freedom in the choice of function for the azimuthal dependence of the convolution kernels.
-The radial part of the function however is determined by the choice of the basis functions.
-It is possible to generalize these convolution kernels by choosing alternate forms for the radial functions.
+The azimuthal of the convolution kernel $\mathcal{M}$ could have been been argued to have the form $e^{-i2 \alpha}$ by requiring to construct a spin-0 field given some spin-2 fields.
+In this sense there is no freedom in the choice of the azimuthal dependence of the convolution kernels.
+The radial part of this kernel however is determined by the basis functions.
+It is possible to generalize these convolution kernels by choosing alternate forms for the radial functions, without affecting the parity properties of the scalar fields $E$ \& $B$.
 
@@
 %
-where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for E and B modes.
-To simplify the discussion and without loosing this generality we proceed with the assumption $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
-We can chose this function to be any arbitrary function and it will allow us to define some convolution operator which either translates Stokes Q \& U parameters to scalars E \& B or vice verse.
-Given $\tilde{\mathcal{G}}$ the modified forward and inverse convolution kernels are given by the following expressions,
+where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for $E$ and $B$ modes.
+To simplify the discussion and without loosing generality we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
+Once we have made a choice for these harmonic functions, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
 %
@@
 Note that for an arbitrary choice of $\tilde{\mathcal{G}}$ only one of the operators in \eq{eq:gen_qu2eb} is well defined, since $\tilde{\mathcal{G}}^{-1}$ may be ill defined.
-If we require both the forward and inverse hold true, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that its inverse is well defined.
-
-The radial part of these generalized convolution kernels is now given by the following expressions,
+If we require both the forward and inverse operators to be well defined, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that it has a valid  inverse.
+The radial part of these generalized convolution kernels is given by the following expressions,
 %
@@
 where $g_{\ell}$ are the same multipole function as those appearing in $\tilde{\mathcal{G}}$.
-If one chooses different forms of $g_{\ell}$ for E and B modes then the radial function are defined accordingly.
-Given this general definition for the radial function $G(\beta)$, note that the default radial function $f(\beta)$ is just a special case resulting from the choice $\tilde{\mathcal{G}}=\tilde{\mathcal{I}}$ ($g_{\ell}=1$).
+Given this general definition for the radial function $G(\beta)$, note that the default radial function ${{}_{\mm}f}$ is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$).
 Note that for this choice of $\tilde{\mathcal{G}}$ the inverse is trivial $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)$.
 
-While defining these alternate operators by modifying the radial part of the kernels, it seems more natural to make a choice on the real space function $G(\beta)$ as compared to choosing the multipole function $g_{\ell}$.
-Using the orthogonality property of associated Legendre polynomials it can be shown that the multipole function $g_{\ell}$ is given by the following integral over the radial function $G(\beta)$,
+While defining these generalized operators, it seems more natural to choose the real space function $G(\beta)$ as compared to choosing the multipole function $g_{\ell}$.
+Using the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the following integral over the radial function $G(\beta)$,
 %
@@
 Here it is important to note that the radial function $G(\beta)$ has to be chosen such that it vanishes at $\beta=0$ and $\beta=\pi$. 
-One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
+%One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
 Another way to understand this requirements is that at these locations the coordinate dependence of the Stokes parameters cannot be integrated out, since the azimuthal angle is ill defined and hence the convolution kernel needs to have vanishing contribution from these locations.
@@
 It is important to ensure consistency with the convention once a choice has been made.} \comment{find a better location for this}
-
-In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-A circularly symmetric beam is represented in harmonic space by the multipole function $b_{\ell}$ which can be derived by evaluating the coefficients of expansion of the function $B(\beta)$ defined at the pole in the Legendre polynomial $P_{\ell}^0$ basis.
-The effective instrument beam is \revisit{almost} always identical for $E$ and $B$ modes.
-\comment{Distinguishing E/B localization characterized by $g_{\ell}$ from E/B smoothing characterized by $b_{\ell}$.}
+Note that in contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+We clarify that the $B(\beta)$ refers to the effective beam acting to smooth the scalar $E$ \& $B$ mode maps.
+A circularly symmetric beam $B(\beta)$ defined at the pole can be expressed in the Legendre polynomial $P_{\ell}^0$ basis as follows,
 %
@@
 %
-\comment{A co-polarized beam which measures the Stokes parameters is not the same as a smoothing beam measuring a scalar field. Is it important to discuss the polarization beam details here ?}
+where $b_{\ell}$ denote the coefficients of expansion.
 %
@@
 \subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.32\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
-\subfigure[]{\includegraphics[width=0.32\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
+\subfigure[\label{fig:glbl}]{\includegraphics[width=0.32\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
 \subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.32\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
@@
 %
+
 Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has important differences, in harmonic space they play identical roles.
 Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
-The modified radial kernel resulting from a few example Gaussian beams are depicted in \fig{fig:bl_gbeta}.
-it is possible to interpret the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ as those corresponding to some circularly symmetric instrument beam function.
-The beam function corresponding to the default radial kernel and the modified radial kernel $G(\beta)$ are depicted in \fig{fig:gl_bbeta}.
-
-\comment{Move the following two paragraphs to final discuss}
-\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
-To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
-In such a case these two method of evaluating the relevant fields is not identical.
-An example of this claim is depicted in \fig{fig:example_gbeta}.\\
-Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
-For instance evaluating the E and B fields in the vicinity of the poles is are prone to receiving significant contributions from strong foregrounds near the equator.
-Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
-On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}
+\fig{fig:glbl} depicts the harmonic functions $g_{\ell} (b_{\ell})$ for the respective radial kernel and beams.
+The modified radial kernel resulting from Gaussian beams with ${\rm fwhm} =15' \,\&\, 12'$ are depicted in \fig{fig:bl_gbeta} as blue and orange curves respectively.
+Note that instruments  beams tend to increase the non-locality parameter $\beta_0$, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
+The red curve depicts a modified radial kernel which by construction has a very small $\beta_0$.
+Similarly it is possible to interpret the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ as those corresponding to some instrument beam function.
+The beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of the delta function depicted by the green curve \fig{fig:gl_bbeta}, while the red curve depicts the same for the modified radial kernel.
 
@@
 
-\subsection{Recovering the default E and B mode spectra}
-The convolution kernels defined using a modified radial function $G(\beta)$ returns some scalar $E'$ and $B'$ mode maps,
+\subsection{Recovering the default $E$ and $B$ mode spectra}
+The generalized convolution kernels defined in the previous section, when operated on the Stokes vector returns some scalar $E'$ and $B'$ mode maps,
 %
@@
 which are not the standard $E$ and $B$ modes maps.
-Since the the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some beam,  the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the spectra of the standard $E$ and $B$ fields via the following relation,
+Since the the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some beam,  the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %
@@
  \beqry
-C_{\ell}^{EE,BB,EB} &= &C_{\ell}^{E'E',B'B',E'B'} /   g_{\ell}^2\,.\\
-C_{\ell}^{TE,TB}  &=&  C_{\ell}^{TE',TB'} / g_{\ell}\,.
+C_{\ell}^{EE,BB,EB} &= &C_{\ell}^{E'E',B'B',E'B'} /   g_{\ell}^2\,,\\
+C_{\ell}^{TE,TB}  &=&  C_{\ell}^{TE',TB'} / g_{\ell}\,,
  \eeqry
@@
  %
-The auto and cross spectra with the standard $E$ and $B$ fields can be recovered from the modified fields $E'$ and $B'$.
-Their accurate recovery only relies on the inverse of the harmonic functions $1/g_{\ell}$ being well behaved, which can be ensured by smartly choosing the radial function $G(\beta)$.
-
-Unlike the instrument beam, the radial function $G(\beta)$ is an analysis choice.
-functions are perfectly known.
-Since the radial kernel is perfectly known it is in principle possible to perfectly deconvolve the same.
-In contrast the beam function $B{\beta}$ has to be inferred from measurement of point source and hence is not known exactly and therefore the deconvolution is only approximate.
-Even though the $G(\beta)$ maybe such that it doesn't have an accurate band limited  description, the spectra are always evaluated to a definite band limit.  
+ where $C_{\ell}$ denotes the angular power spectra and $T$ refers to the temperature anisotropy map.
+Therefore the standard $E$ and $B$ mode spectra can be recovered from the modified fields $E'$ and $B'$ and their accurate recovery only relies on the inverse of the harmonic functions $1/g_{\ell}$ being well behaved, which can be ensured by making a suitable choice for the radial function $G(\beta)$.
+%One direct application of this freedom in choosing the radial kernel is that one can mitigate the issue of leakage of power from $E$ to $B$.
+By constructing a radial function which tapers to zero at sufficiently small radii one can clearly discard pixels which are affected by masking.
 %--------------------------------------------------------

### 2017-10-31 articles/formalism/sections/real_space_formalism.tex
Refined the discussion on generalized kernels and recovery of standard spectra

@@
 \revisit{It is also interesting to note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
-
-\rfedit{The azimuthal operations do not depend on the choice of basis functions, and could have been been argued to have the form $e^{-i2 \alpha}$ by requiring to construct a spin-0 field given some spin-2 fields.
-The radial part of the kernel however is determined by the choice of the basis functions.
-Motivated by this observation, we can think of constructing convolution kernels with different radial dependences, hence allowing control over the non-locality of the convolution kernels.} \comment{This is generally true for all the local kernels.
-So shift this line to the section where we explore different radial functions.}
 %--------------------------------------------------------

### 2017-11-01 articles/formalism/sections/kernel_discussion.tex
updated figure depicting the radial kernels on linear scale

@@
 \caption{The figure depicts the radial part of the convolution kernels.
-These radial function have been evaluated with the band limit fixed at $\ell \in [2,192]$.
-The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=64, which is the lowest resolution that allows access to $\ell_{\rm max}=192$.}
+These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$.
+The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
 \label{fig:beta_kernel}

### 2017-11-01 articles/formalism/sections/real_space_formalism.tex
updated figure depicting the radial kernels on linear scale

@@
 %
-Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor of $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relation introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
+In this section we cast the relations introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
 This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.\\
+We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.
+
 We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
@@
 where $s$ denotes the spin of the basis functions.
-For this work we will only be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices:$(\ell,m)$ and each row maps to a specific position on the sphere.
+For this work we will be working with cases $s \in [0,2]$.
+In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices: $(\ell,m)$ and each row maps to a specific position on the sphere.
 Note that this matrix is in general not a square matrix.

### 2017-11-01 articles/formalism/article.tex
updates to sections in the formalism draft. Added the healpix rotation method to the section on visulaizing the local operators
Revised sections 3.1 and 3.2
updated the discussion surrounding the visulization of the convolution kernels
resolved the clearpage issue which was occuring with the use of include command. Completed another pass at the non-locality of the E and B kernels
Refined the discussion on generalized kernels and recovery of standard spectra
minor updates to figures. A first pass at the section on discussions

@@
-%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers,twocolumn]{revtex4}%showpacs,superscriptaddress
-%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers]{revtex4}%showpacs,superscriptaddress
 \documentclass[a4paper,11pt]{article}
@@
 \usepackage[latin1]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{hyperref}
+\usepackage{amsmath, amsfonts, amssymb, hyperref, graphicx, multirow, subfigure, bbold}
 \hypersetup{colorlinks=True,citecolor=blue}
-\usepackage{amssymb}
-\usepackage{graphicx,multirow}
-\usepackage{subfigure}
-%\usepackage{soul}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 \usepackage[normalem]{ulem}
-
-\renewcommand*{\thesubfigure}{(\roman{subfigure})}
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-
-%\usepackage{caption}
-%\usepackage{float}
-%\usepackage{bm}
-%\usepackage{latexsym}
-%\usepackage{epsfig}
-%\usepackage{graphicx,color}
-\usepackage{bbold}
-%\usepackage{caption}
-%\usepackage{subcaption}
+\renewcommand{\thesubfigure}{(\roman{subfigure})}
+%\renewcommand{\thesubfigure}{}
 
@@
 \newcommand{\eeqrys}{\end{eqnarray}\end{subequations}}
-
 \newcommand{\fqu}{\begin{bmatrix} Q \\ U \end{bmatrix}}
@@
 \newcommand{\emat}{\end{bmatrix}}
-
+\newcommand{\mdi}{\mathcal{D}/\mathcal{I}}
+\newcommand{\mm}{\mathcal{M}}
+\newcommand{\md}{\mathcal{D}}
+\newcommand{\mi}{\mathcal{I}}
 \def\vp#1{$\bar{P}_{#1}$ }
 \def\vs{$\bar{S}~$}
-
-\newcommand{\st}{\sout}
-\newcommand{\revisit}{\textcolor{red}}
-\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
-\newcommand{\rfedit}{\textcolor{magenta}  }
-\newcommand{\soothe}{\textcolor{BlueViolet}  }
-
 \def\eq#1{{Eq.~(\ref{#1})}}
@@
 
+% Text comments and highlights
+\newcommand{\st}{\sout}
+\newcommand{\revisit}{\textcolor{red}}
+\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
+\newcommand{\rfedit}{\textcolor{magenta}  }
+\newcommand{\soothe}{\textcolor{BlueViolet}  }
+
 \graphicspath{ {"../../figures/"//} }
@@
 \begin{document}
-
 \title{Quantifying the locality of operators that translate Stokes $Q$ \& $U$ to scalars $E$ \& $B$}
@@
 We derive constraints on these generalized operators to ensure reliable recovery of the standard $E$ and $B$ fields and the corresponding power spectra.
-This is part 1 of a series of papers where we explore these operators.}
+\revisit{This is part 1 of a series of papers where we have derived the real space operators.
+In the following papers we will explore some of their applications.} \comment{Needs better blending.}}
 
 \maketitle
-
+\begingroup
+\let\clearpage\relax
 \include{./sections/introduction}
@@
 \include{./sections/discussion}
-\include{./sections/appendix}
+\endgroup
 

### 2017-11-01 articles/formalism/sections/discussion.tex
minor updates to figures. A first pass at the section on discussions

--- 2017-09-20 article/sections/discussion.tex
@@
 \section{Discussion}\label{sec:discussion}
-\begin{itemize}
-\item We have derived the real space kernels for translating Stokes parameters Q \& U to scalars E \& B and vice versa.
-We have also derived real space kernels which allow for direct separation of Stokes Q \& U parameters without having to first evaluate the scalar field E \& B.
 
-\item These kernels quantify the non-locality of the E and B fields. We have introduced the non-locatity parameter $\beta_0$ which provides a quantitative measure of the non-locality of these fields.
+In this article we have cast the standard CMB polarization analysis operations in a vector matrix notation.
+Using this concise notation we derive the real space operators that translate the Stokes vector \vp{} to  the vector of scalars \vs and vice versa.
+We explicitly demonstrated that this real space operation can be simply interpreted as a convolution over the complex field $[Q - i U]$ (or $[E + iB]$) with an effective complex beam which is fully expressed in terms of the $Y_{\ell 2}$ spherical harmonic functions.
+We also use this vector matrix notation to derive real space operators which allow the direct decomposition of the full Stokes vector \vp{} into the vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
 
-\item Studying these real space kernels reveals that its the radial part of the kernel which knows about the band limit of the experiment.
-Motivation for defining radially compact kernels.
-We have demonstrated that using the radially compact kernels does not bias the spectral information on intermediate angular scales.
+Given the effective beam interpretation of these real space operators we derive the harmonic coefficients of these effective beams at the north galactic pole.
+Using these harmonic coefficients we provide a prescription for computing the convolution kernels at any position on the sphere using the standard Healpix built in functions.
+The procedure is equivalent to parallel transporting the beam at the north pole to any desired location on the sphere.
+We implement the prescription to compute the  kernel at different location on the sphere and provide simple explanations in terms of Euler angles for the observed variations.
 
-\item Small field experiments like BICEP implement such radial cut offs due to limited survey area.
+These real space convolution kernels provide a spatially intuitive way of understanding the construction of the scalar modes.
+We explicitly show that the kernels separates into an band limit independent azimuthal operation around any given direction which is primarily responsible for requisite decomposition, while the band limit dependent radial weights can be interpreted as some isotropic smoothing operation.
+These radial weights primarily determine the non-local dependence of the construction of the respective fields at any location on the Stoke field.
+We define the parameter $\beta_0$ as a means to characterize the non-locality and show that $\beta_0$ scales $\propto \ell_{\rm max}^{-1}$.
+We show that this non-locality parameter also characterized the non-locality of the $\bar{O}_{E/B}$ operators.
 
-\item Using in conjunction with FEBECOP \cite{febecop} like schemes to directly infer E and B mode maps from raw maps.
-
-\item \textit{Total convolution methods:} Since the convolution kernels can be thought of as effective beams for polarization maps, it may be possible to use total convolution methods to construct E and B mode maps.
-
-\item{Separate Q and U maps for E and B:} We have presented kernels which allow for decomposition of the total Stokes Q and U parameters to those corresponding to E and B modes.
-This could be potentially interesting, since one can now work with E and B modes foregrounds and their separations separately.
-\comment{But is there an issue with doing this in the standard method which involves going through the process of generating E and B modes ?}
-
-\item \textit{Mask leakages} can be understood as arising from improper sine quadrupole and cosine quadrupole transforms on rings with holes in them due to masking.
-For the global mask (no point sources), by using a radially compact kernel with some $\beta_0$, the pixels which are at a angular distance $\beta_0$ from the edges of the mask have unbiased estimates of the scalar fields E and B.
-
-\item{The difference between the spectra derived from the local convolution maps and the reference spectra follow a definite pattern and maybe it possible to model this difference and correct for it.
-For this purpose one will have to model the two point correlation function for the E and B fields in terms of the Stokes Q and U maps.}
-
-\item{We have not addressed the E to B leakage issue in this work.}
-
-\end{itemize}
-%
-%The width of the $\beta$ kernel can be used as an indicator of the width of mask apodization.
-One may also use the width of the $\beta$ kernel to throw away the regions of the sky close to the edges of the mask.
-Mask apodization techniques should fail at low Nside.
-The width of the $\beta$ kernel makes transparent why the E to B leakage issues are only relevant close to the edges of the mask.
+Finally we present the generalized real space operators $\bar{O}'$, which are derived by allowing the radial function to vary from its default form.
+We derive constraints on the modifications to these radial function by demanding the inverse operator to be well defined.
+We argue that these modifications to the radial kernel can be be interpreted as a some smoothing smoothing operation on the scalar fields with a circularly symmetric instrument beam.
+We also show that as long as these radial function are invertible, the standard spectra can always be recovered from these modified $E'$ \& $B'$ maps.
+The main advantage of modifying these radial function is the ability to generate more locally defined $E$ and $B$ mode maps.
+This could potentially be useful in reducing foreground contamination on large angular scales in a full sky $E/B$ analysis.
+Also defining more locally constructed scalar fields $E$ \& $B$ can be used to circumvent the power leakage nuisance.
+We explore and demonstrate the working of these ideas in the next paper in this series.
+%\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
+To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
+In such a case these two method of evaluating the relevant fields is not identical.
+An example of this claim is depicted in \fig{fig:example_gbeta}.\\
+%Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
+For instance evaluating the E and B fields in the vicinity of the poles is are prone to receiving significant contributions from strong foregrounds near the equator.
+Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
+On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}

### 2017-11-01 articles/formalism/sections/kernel_discussion.tex
minor updates to figures. A first pass at the section on discussions

@@
 \subfigure{\includegraphics[width=0.96\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
 \subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for different $\ell_{\rm max}$ as indicated by their legends and fixed $\ell_{\rm min}=2$.
+\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and different $\ell_{\rm max}$ as indicated by their legends.
 All the curves have been normalized such that the maximum of the curve is set to unity.

### 2017-11-02 articles/formalism/article.tex
Heavy edit of abstract

@@
 \begin{document}
-\title{Quantifying the locality of operators that translate Stokes $Q$ \& $U$ to scalars $E$ \& $B$}
-\title{Real space operators for Stokes $Q$ \& $U$ to scalars $E$ \& $B$ translation}
+%\title{Quantifying the locality of operators that translate Stokes $Q$ \& $U$ to scalars $E$ \& $B$}
+%\title{Real space operators for Stokes $Q$ \& $U$ to scalars $E$ \& $B$ translation}
+\title{Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels}
 \author[]{Aditya Rotti and}
@@
 \abstract{
-\noindent  We derive fully sky real space operators to translate Stokes Q \& U parameters to scalars $E$ \& $B$ and vice versa.
+  \noindent 
+  \revisit{  We derive full-sky, real-space operators that convert between polarization Stokes $Q$/$U$ parameters to the coordinate-independent, scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background and cosmic shear analysis.
+The covolution kernels split naturally into angular and radial parts, and we show explicitly how the spatial extent of the convolution kernel depends on the targeted band-limit.
+We show that a arbitrary radial dependence can produce $E$/$B$-like maps and that these are simply filtered versions of the standard $E$/$B$ maps.
+This allows us to compute $E$/$B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
+We can compute power spectra using standard techniques, and recover the power spectrum of the sky with a simple window function.
+    %
+     We cast the standard CMB polarization analysis operators in a matrix-vector notation which facilitates the derivations and shows that the kernels relate directly to spin-0 $Y_{\ell 2}$ spherical harmonic functions.
+This new notation also allows us to derive real space operators which decompose the measured Stokes parameters into their even and odd-parity parts, without ever evaluating the scalar $E$/$B$ fields themselves.
+This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.
+  } 
+  \\
+  \\
+%  We derive fully sky real space operators to translate Stokes Q \& U parameters to scalars $E$ \& $B$ and vice versa.
 We explicitly show that these local real space operator are fully characterized by the spin-0 $Y_{\ell 2}$ spherical harmonic functions.
@@
 \revisit{This is part 1 of a series of papers where we have derived the real space operators.
-In the following papers we will explore some of their applications.} \comment{Needs better blending.}}
+In the following papers we will explore some of their applications.} \comment{Needs better blending.}
+}
 

### 2017-11-02 articles/formalism/sections/introduction.tex
brainstorming in the intro

@@
 \section{Introduction}
+The Cosmic Mircowave Background is 10 percent polarized, but the polarization contains independent cosmological information.
+
+Standard technique is to convert Stokes parameters into scalar and pseudo-scalar modes, which are easier to compare to theory.
+
+The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations
+
+primordial tensor perturbations
+
+lensing of $E$-modes
+
+systematics checks
+
+exotic phenemena like cosmic birefringence
+
+The spin-0 $E$/$B$ modes relate to the spin-2 Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.
+However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.
+In other words, the $E$/$B$ modes at a point can get contributions from all over the sky.
+
+(stuff about foregrounds, masking, ambiguous modes with references)
+
+Zaldarriaga explored the spatial real-space kernels in the flat-sky approximation \citep{}.
+
 In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.

### 2017-11-02 articles/formalism/sections/generalizedeb.tex
updated color scheme for line plots

@@
 \centering
-\subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.32\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
-\subfigure[\label{fig:glbl}]{\includegraphics[width=0.32\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
-\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.32\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
+\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}\\
+\subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
+\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
 \caption{\textit{Left:} The vertical dashed gray line depicts the approximate pixel size $\Delta_{\rm pix} = \sqrt{\frac{4 \pi}{N_{\rm pix}}}$ of a Nside=512 Healpix map.

### 2017-11-02 codes/modules/local_healpix_qu2eb_masked.py

@@ -1,0 +1,55 @@
+import healpy as h
+import numpy as np
+
+def return_disc_mask(discsize,apow,nside,cpix):
+    mask=np.zeros(h.nside2npix(nside),float)
+    # The coordinate of the pixel center updated to that in the mask resolution
+    theta0=h.pix2ang(nside,cpix)[0] ; phi0=h.pix2ang(nside,cpix)[1]
+
+    pixnum=np.arange(h.nside2npix(nside))
+    theta=h.pix2ang(nside,pixnum)[0] ; phi=h.pix2ang(nside,pixnum)[1]
+    dotprod=np.sin(theta)*np.sin(theta0)*np.cos(phi-phi0)+np.cos(theta)*np.cos(theta0)
+    dtheta=np.arccos(dotprod)*180./np.pi
+
+    for i in range(h.nside2npix(nside)):
+        if dtheta[i] <= (discsize-apow):
+            mask[i]=1.
+        elif dtheta[i] > (discsize-apow) and dtheta[i] <= discsize:
+            mask[i]=np.cos((dtheta[i]-(discsize-apow))*np.pi/(2.*apow))**2.
+            
+    return mask
+
+def return_local_eb(tqu,discsize,nside,lmax,lmin=2.,apow=2.,pindex=[],return_equ_bqu=False):
+	
+	npix=h.nside2npix(nside)
+	rteb=[np.zeros(npix,float),np.zeros(npix,float)]
+
+	# Setting the pixel index
+	if np.size(pindex)==0:
+		print "Computing on all pixels"
+		pindex=np.arange(h.nside2npix(nside))
+
+
+	if return_equ_bqu:
+		requ=[np.zeros(npix,float),np.zeros(npix,float)]
+		rbqu=[np.zeros(npix,float),np.zeros(npix,float)]
+	
+		for i in pindex:
+			mask=return_disc_mask(discsize,apow,nside,i)
+			temp_alm=h.map2alm(tqu*mask,lmax=lmax,pol=True)
+			temp_teb=h.alm2map(temp_alm,nside,pol=False,verbose=False)
+			temp_equ=h.alm2map([temp_alm[0],temp_alm[1],temp_alm[2]*0.],nside,pol=True,verbose=False)
[…]

### 2017-11-21 codes/modules/aliasing_correction.py
added a module to compute the aliasing correction

@@ -1,0 +1,61 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''
+	This Euler angles function works for the qu2_equ_bqu function.
+	The set of function here, match Healpix results to numerical accuracy.
+	'''
+	theta1,phi1=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	theta2,phi2=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
+	beta=np.arccos(cosbeta)
+
+	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
+    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
+    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
+    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
+	return beta,alpha,gamma,spix
+
+def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	hq=np.zeros(npix,"double")
+	hu=np.zeros(npix,"double")
+	
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+		
+	for i in pix_list:
[…]

### 2017-11-22 articles/formalism/sections/real_space_formalism.tex
added explanation for the alpha and gamma as being the radiating and the convolution kernels, still sharpening the explanation

@@
 \bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{i} \qutoxd \ymatc{j} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_i ~{}_{2}Y^{T*}_j  +  {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & {\rm i}  \sum ({}_{0}Y_i ~ {}_{2}Y^{T*}_j - {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \\  - {\rm i} \sum  ({}_{0}Y_i ~ {}_{2}Y^{T*}_j - {}_{0}Y_i~ {}_{-2}Y^{T*}_j) & \sum ({}_{0}Y_i~ {}_{2}Y^{T*}_j + {}_{0}Y_i ~{}_{-2}Y^{T*}_j)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
+&=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
+&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{T*}_q  +  {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{T*}_q + {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
 \eeqrys
 %
-where the symbol ${}_{0}Y_i$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_i \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_i)$, the symbol ${}_{\pm 2}Y^{T*}_j$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_j} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_j)$ and the summation is over the multipole indices $\ell,m$.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
+where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
+\revisit{We have purposefully used the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
 %
 \beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{+2}Y^*_{\ell m}(\hat{n}_j)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_i){}_{-2}Y^*_{\ell m}(\hat{n}_j) \,.
+ \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,.
  \eeq
@@
 \beq \label{eq:sum_spin_shf}
- \sum_{m}{{}_{s_1}Y}^*_{\ell m}(\hat{n}_i)\,{{}_{s_2}Y}_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta,\alpha) e^{- i s_2 \gamma} \,,
+ \sum_{m}{{}_{s_1}Y}^*_{\ell m}(\hat{n}_i)\,{{}_{s_2}Y}_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta_{ij},\alpha_{ij}) e^{- i s_2 \gamma_{ij}} \,,
 \eeq
 %
-where $\alpha, ~\beta ~\&~ \gamma$ denote the Euler angles. Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
+where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles.
+Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
 %
@@
 \beqry
-\mathcal{M}( \hat{n}_i, \hat{n}_j)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_i) \, {{_{-2}}Y}^*_{\ell m}(\hat n_j) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{ij},\alpha_{ij})\,,\\
-&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{ij}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{ij}) + i \sin(2 \alpha_{ij} ) \Big] {{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,, 
+\mathcal{M}( \hat{n}_e, \hat{n}_q)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
+&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_e) \, {{_{-2}}Y}^*_{\ell m}(\hat n_q) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{qe},\alpha_{qe})\,,\\
+&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{qe}) \,, \label{eq:rad_ker_queb} \\
+&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
 \eeqry
@@
 \beq\label{eq:op_qu2eb}
-\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,,
+\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,.
 \eeq
 %
-where indices i,j map to the location $\hat{n}_i$ and $\hat{n}_j$ on the sphere.
-\revisit{A similar equation for real space $E$ \& $B$ operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
+Specifically note that $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at the location $\hat{n}_q$ where the Stokes field is measured to the cartesian system at the location $\hat{n}_e$ where the scalar fields are evaluated: $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
+The Euler angles for the inverse rotation are given by the Euler angles $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$\cite{varshalovich}.
+Since the real space kernels will only depend on the cosine of the Euler angle $\beta$, they are immune to its change of sign.
+However the ordering of indices  on the Euler angle $\alpha$ and $\gamma$  is important and leads to two different interpretations of the real space kernels.
 
-The scalar fields $E$ \& $B$ can now be directly derived from the measured Stokes $Q$ \& $U$ parameters by evaluating the following convolution,
+\textit{Convolution:} Now working from the position of the pixel ``e'' where the scalar modes need to be evaluated, the Euler angles to the surrounding pixels are: $\alpha_{eq}, \beta_{eq},\gamma_{eq}$.
+One can now think of the value of scalar fields $E$ \& $B$ at the central pixel ``e" as resulting from the convolution over the measured Stokes $Q$ \& $U$ parameters in the surrounding pixels ``q''.
+This convolution is defined in terms of the Euler angle $\gamma_{eq}$ and is given by the following equation,
 %
 \beq \label{eq:qu2eb_convolution_explicit}
-\bmat E_i \\ B_i  \emat= -\Delta \Omega \sum_{j=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & \sin(2\alpha_{ij})\\  -\sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat Q_j \\ U_j  \emat \,,
+\bmat E_e \\ B_e  \emat =- \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega\,,
 \eeq
@@
 \beqry 
-[E + iB](\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{0j}) \right) {\Bigg( e^{-i2 \alpha_{0j}}   {}_{+2}X (\hat{n}_j) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2} \right]  \circ {}_{+2}X \right) \,, \\
+[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
+&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta,\gamma) \right]  \circ {}_{+2}X \right) \,, \\
 &=& - \Bigg\lbrace \mathcal{M}^* \circ {}_{+2}X \Bigg\rbrace(\hat{n}_0)\,, \label{eq:qu2eb_convolution} 
@@
 %
-where $\circ$ denotes a convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_0$ and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
+where $\circ$ denotes a convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_e$.
+%and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
+
+\textit{Radiating:} Working from the position ``q'' where the Stokes parameters are known, the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.
+The E \& B mode maps resulting from the Stokes Q \& U parameters specified at location $\hat{n}_q$ is given by the following expression,
+%
+\beq \label{eq:qu2eb_radiation_explicit}
+\bmat E_e \\ B_e  \emat_q =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega \,,
+\eeq
+%
+and the total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
+%$\bmat E_e \\ B_e  \emat = \sum_{q=1}^{N_{\rm pix}} \bmat E_e \\ B_e  \emat_q$.
 

### 2017-11-22 codes/modules/convert_qu2eb.py

@@ -6,7 +6,7 @@ from scipy.interpolate import interp1d
 # Integrating method to generate E and B mode maps.
 def convert_qu2eb_integrate(q,u,theta_cutoff,theta,rad_ker):
 	'''
-	   This function uses Q and U maps in reggions defined by the radial cutoff, irrespective of the mask.\n
+	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
 	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
 	'''
 	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
@@ -41,7 +41,7 @@ def convert_qu2eb_integrate_masked(q,u,theta_cutoff,theta,rad_ker,mask=[]):
 		cosbeta,cos2gamma,sin2gamma,spix=euler.fn_s2euler_gamma(nside,i,theta_cutoff,inclusive=False,fact=4)
 		gbeta=fn_rad_ker(cosbeta)
 		cgfb=cos2gamma*gbeta ; sgfb=sin2gamma*gbeta
-		e[i] = (np.dot(-cgfb,q[spix]) + np.dot(sgfb,u[spix]))*domega
+		e[i] = (np.dot(-cgfb,q[spix]) + np.dot( sgfb,u[spix]))*domega
 		b[i] = (np.dot(-sgfb,q[spix]) + np.dot(-cgfb,u[spix]))*domega
 	return [np.zeros(npix),e,b]
 
@@ -58,8 +58,8 @@ def convert_qu2eb_radiate(q,u,theta_cutoff,theta,rad_ker):
 		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
 		gbeta=fn_rad_ker(cosbeta)
 		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
-		e[spix] = e[spix] + (-cafb*q[i] - safb*u[i])*domega
-		b[spix] = b[spix] + ( safb*q[i] - cafb*u[i])*domega
+		e[spix] = e[spix] + (-cafb*q[i] + safb*u[i])*domega
+		b[spix] = b[spix] + (-safb*q[i] - cafb*u[i])*domega
 	return [np.zeros(npix),e,b]
 
 

### 2017-11-22 codes/modules/euler.py

@@ -57,10 +57,10 @@ def fn_s2euler_alpha_gamma(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
 	
 	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1)
 
-	sinalpha=np.where(abs(cosbeta)<1.,np.sin(theta1)*np.sin(phi0-phi1)/np.sqrt(1.-cosbeta*cosbeta),0.)
+	sinalpha=np.where(abs(cosbeta)<1.,-np.sin(theta1)*np.sin(phi0-phi1)/np.sqrt(1.-cosbeta*cosbeta),0.)
 	cosalpha=np.where(abs(cosbeta)<1.,(np.cos(theta1) - np.cos(theta0)*cosbeta)/(np.sin(theta0)*np.sqrt(1.-cosbeta*cosbeta)),0)
 	singamma=np.where(abs(cosbeta)<1.,-np.sin(theta0)*np.sin(phi0-phi1)/np.sqrt(1.-cosbeta*cosbeta),0.)
-	cosgamma=np.where(abs(cosbeta)<1.,-(np.cos(theta0) - np.cos(theta1)*cosbeta)/(np.sin(theta1)*np.sqrt(1.-cosbeta*cosbeta)),0)
+	cosgamma=np.where(abs(cosbeta)<1.,(np.cos(theta0) - np.cos(theta1)*cosbeta)/(np.sin(theta1)*np.sqrt(1.-cosbeta*cosbeta)),0)
 
 	s2a=2.*sinalpha*cosalpha
 	c2a=cosalpha*cosalpha - sinalpha*sinalpha
@@ -84,7 +84,7 @@ def fn_s2euler_alpha(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
 	theta1,phi1=h.pix2ang(nside,spix)
 	
 	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1)
-	sinalpha=np.where(abs(cosbeta)<1.,np.sin(theta1)*np.sin(phi0-phi1)/np.sqrt(1.-cosbeta*cosbeta),0.)
[…]

### 2017-11-23 articles/formalism/sections/real_space_formalism.tex
revised discussion in sec 3.1 and 3.2, yet to complete

@@
 Specifically note that $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at the location $\hat{n}_q$ where the Stokes field is measured to the cartesian system at the location $\hat{n}_e$ where the scalar fields are evaluated: $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
-The Euler angles for the inverse rotation are given by the Euler angles $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$\cite{varshalovich}.
-Since the real space kernels will only depend on the cosine of the Euler angle $\beta$, they are immune to its change of sign.
-However the ordering of indices  on the Euler angle $\alpha$ and $\gamma$  is important and leads to two different interpretations of the real space kernels.
+The Euler angles for the inverse rotations are given by the Euler angles $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$\cite{varshalovich}.
+Since the kernels only depend on the cosine of the Euler angle $\beta$, they are immune to the change in its sign.
+More importantly, the ordering of indices  on the Euler angle $\alpha$ and $\gamma$  is important and leads to two different interpretations of the real space kernels.
 
-\textit{Convolution:} Now working from the position of the pixel ``e'' where the scalar modes need to be evaluated, the Euler angles to the surrounding pixels are: $\alpha_{eq}, \beta_{eq},\gamma_{eq}$.
-One can now think of the value of scalar fields $E$ \& $B$ at the central pixel ``e" as resulting from the convolution over the measured Stokes $Q$ \& $U$ parameters in the surrounding pixels ``q''.
-This convolution is defined in terms of the Euler angle $\gamma_{eq}$ and is given by the following equation,
+\textit{Convolution:} Working from the frame of the pixel ``e'' where the scalar modes need to be evaluated, the Euler angles to the surrounding pixels are: $\alpha_{eq}, \beta_{eq},\gamma_{eq}$.
+In terms of these Euler angles, the value of scalar fields $E$ \& $B$ at the central pixel ``e" can be evaluated by convolving over the measured Stokes $Q$ \& $U$ parameters in the surrounding pixels marked by indices ``q''.
+Specifically, the convolution is fully defined in terms of the Euler angles $\beta_{eq}~ \& ~\gamma_{eq}$ and is given by the following equation,
 %
@@
 %\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-The above equation can be expressed more concisely as follows,
+When written in terms of the complex spin-0 field $[E + iB]$ and the spin-2 field ${}_{+2}X$, the above equation can be expressed more concisely as follows,
 %
-\begin{subequations} \label{eq:qu2eb_simple}
+\begin{subequations} \label{q:qu2eb_convolution_concise}
 \beqry 
-[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& - \left( \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta,\gamma) \right]  \circ {}_{+2}X \right) \,, \\
-&=& - \Bigg\lbrace \mathcal{M}^* \circ {}_{+2}X \Bigg\rbrace(\hat{n}_0)\,, \label{eq:qu2eb_convolution} 
+%[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
+[E + iB](\hat{n}_e) &=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
+&=& \Bigg\lbrace \mathcal{M}_{Beam} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e)\,, \label{eq:qu2eb_convolution} 
 \eeqry
@@
 %
-where $\circ$ denotes a convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_e$.
+where $\circ$ denotes the convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_e$.
 %and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
 
-\textit{Radiating:} Working from the position ``q'' where the Stokes parameters are known, the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.
+\textit{Radiating:} On the contrary, while working from the frame of the pixel ``q'', the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.
 The E \& B mode maps resulting from the Stokes Q \& U parameters specified at location $\hat{n}_q$ is given by the following expression,
@@
 \beq  \label{eq:qu2eb_radiation_explicit}
-\bmat E_e \\ B_e  \emat_q =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega \,,
+\bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
 \eeq
 %
-and the total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
-%$\bmat E_e \\ B_e  \emat = \sum_{q=1}^{N_{\rm pix}} \bmat E_e \\ B_e  \emat_q$.
+The total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
+The above expression can again be cast in a more concise form as follows,
+%
+\begin{subequations} \label{eq:qu2eb_radiation_concise}
+\beqry 
+\left[E + iB\right] &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
+&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
+&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{Green}(\hat{n}_{q}) \,,
+\eeqry
+\end{subequations}
+%
+where ``$\cdot$'' denotes a simple scalar multiplication.
+\revisit{$\mathcal{M}_{Green}(\hat{n}_{q})$ is response of the real space operator $\bar{O}$ when operated on a Stokes field: $\delta(\hat{n}-\hat{n}_q) + i \delta(\hat{n}-\hat{n}_q)$, it can be thought of as the Green's function of the real space operator.} \comment{Is this interpretation correct ?
+Is the complex delta function a spin 2 function ?}
 
@@
 %
-We do not provide the explicit derivation here, since the procedure is nearly identical to that discussed in the previous section. The inverse operator is given by the following expression,
+We do not provide the explicit derivation here, since the procedure is identical to that discussed in the previous section. The inverse operator is given by the following expression,
 %
 \beq
-{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat \,.
+{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{eq}) & -\sin(2\alpha_{eq})\\  \sin(2 \alpha_{eq})  & \cos(2 \alpha_{eq}) \emat \,.
 \eeq
 %
-%where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel is different by a mere change in sign on the off-diagonals of the block matrix as compared to \eq{eq:op_qu2eb}.
+where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
+Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb} by a change in sign on the off-diagonals of the block matrix and the pixel indexing is reversed $ e \leftrightarrow q$.
 We can evaluate the Stokes parameters  $Q$ \& $U$ from the scalar fields $E$ \& $B$ by evaluating the following expression,

### 2017-11-23 articles/formalism/sections/real_space_formalism.tex
Sec 3.1 is now more more complete and satisfactory at some level. Still needs refining, but the core ideas are now in place.

@@
 where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-\revisit{We have purposefully used the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
+\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
 %
@@
 \beqry 
-%[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-[E + iB](\hat{n}_e) &=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
+[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
+&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
 &=& \Bigg\lbrace \mathcal{M}_{Beam} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e)\,, \label{eq:qu2eb_convolution} 
@@
 where ``$\cdot$'' denotes a simple scalar multiplication.
-\revisit{$\mathcal{M}_{Green}(\hat{n}_{q})$ is response of the real space operator $\bar{O}$ when operated on a Stokes field: $\delta(\hat{n}-\hat{n}_q) + i \delta(\hat{n}-\hat{n}_q)$, it can be thought of as the Green's function of the real space operator.} \comment{Is this interpretation correct ?
+\revisit{$\mathcal{M}_{Green}(\hat{n}_{q})$ is response of the real space operator $\bar{O}$ when operated on a Stokes field: $\delta(\hat{n}-\hat{n}_q) + i \delta(\hat{n}-\hat{n}_q)$, hence it can be thought of as the Green's function of the real space operator.} \comment{Is this interpretation correct ?
 Is the complex delta function a spin 2 function ?}
 
-The convolution kernel has a azimuthal part which depends only on the Euler angle $\alpha$ and has no multipole dependence and this is the primary operation which translates between the two different spin representation of CMB polarization.
-The radial part of the kernel is specified by the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, it depends only on the angular separation given by the Euler angle $\beta$ and it completely incorporates the multipole $\ell$ dependence of the kernel.
-It is the radial part of the kernel that completely determines the locality of this operator.
-Note that this kernel does not depend on the Euler angle $\gamma$ \comment{Why is that and how do you understand this ?
+Recall that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$ \comment{The following argument is that of the product of a number with a field, so is this relevant ?
 }.
+If one rotates by an angle $\phi$ about the local $\hat{z}_q$ axis, the local Stokes parameters transform as: ${}_{+2}X(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{i2\phi} $.
+Since this angle $\phi$ can be thought of as the phase angle $\gamma$ in the $z-y_1-z_2$ convention of Euler angles, one can see that: $e^{-i2\alpha_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{-i2\phi}$.
+The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
+Given these transformation properties one can now note that the product ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence must form a spin-0 field.
+This argument makes intuitive, the construction of the spin-0 E and B modes of polarization from the measured Stokes parameters.
+\revisit{Here it is also interesting to note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
 
-We know that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$.
-Since $[Q + iU]$ is a field with spin +2 and the field $\exp(-i2\alpha)$ has spin -2, the resultant field formed by the product of these two function has spin-0.
-This makes intuitive, the construction of the spin-0 E and B modes of polarization.
-Note that the coordinate dependence of the Stokes parameters cannot be integrated out at the location $\hat{n}_0$ where the scalar fields are to be evaluated and at the diametrically opposite location, since the azimuthal angle $\alpha$ becomes ill-defined at these points.
-The convolution kernel has vanishing contribution from these points, since the radial part of the kernel is given by a weighted linear combination of $P_{\ell}^2$ Legendre polynomials which $P_{\ell}^2(\beta) \propto \sin^2{\beta} \rightarrow 0 $ as $\beta \rightarrow 0 ,\pi$.
-\revisit{It is also interesting to note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
+Using \eq{eq:qu2eb_radiation_explicit} one can see that when $q=e$: $E_q=-{{}_{\mm}f}(\beta_{qq})Q_q$ and $B_q = -{{}_{\mm}f}(\beta_{qq})U_q$ which does not transform as a spin-0 field under local rotations unless ${{}_{\mm}f}(\beta_{qq}=0)=0$.
+One can make a similar argument when pixels ``q'' and ``e'' are diametrically opposite.
+Therefore the radial kernels have to satisfy the constraint that they vanish at $\beta = 0, \pi$.
+The radial kernel ${{}_{\mm}f}(\beta)$ is constructed by forming a weighted linear combination of $P_{\ell}^2$ Legendre polynomials which have the following limiting form: $P_{\ell}^2(\beta) \propto \sin^2{\beta} \rightarrow 0 $ as $\beta \rightarrow 0 ,\pi$ and therefore satisfy this necessary constraint.
+
+The real space operator has a azimuthal part which depends only on the Euler angle $\alpha_{qe} (\gamma_{eq})$, has no multipole $\ell$ dependence and is the crucial operation which translates between the two different spin representation of CMB polarization.
+The radial part of the kernel is specified by the function ${}_{\mm}f(\beta,\ell_{\rm min},\ell_{\rm max})$, it depends only on the angular separation $|\beta_{eq}|$ between pixels and completely incorporates the multipole $\ell$ dependence of the kernel.
+It's the radial part of the kernel that determines the locality of the real space operator.
 %--------------------------------------------------------

### 2017-11-23 articles/formalism/sections/real_space_formalism.tex
reintroduced the discussion on Euler angles in the formalism draft, with significant edits to the discussion given in the old draft.

@@
 This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics.
+All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
+Owing to this, we begin with a brief discussion on Euler angles and present visual method to think about them.
+
+\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east.
+The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
+
+Specifically $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
+In more physical terms, these angles can be understood as follow: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
+The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, such that the z-axes of the two coordinate systems are parallel to each other.
+Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
+
+The simplest case is when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
+In this case it is easy to visualize and infer that the rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$ in the $z-y1-z2$ sense, will align the local cartesian system at the pole with that defined at position $\hat{n}_i$.
+The Euler angles in the $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$.
 %--------------------------------------------------------

### 2017-11-24 articles/formalism/sections/real_space_formalism.tex
The spatial argument of spin-0 construction in section 3.1 is now more solid. I am satisfied with this explanation now. Still not happy with the explanation for convolution and radiating interpretations of the real space kernels.

@@
 \beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + _{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - _{-2}\tilde{X}_{\ell m} \Big] 
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] 
 \eeq
@@
 where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true,
+\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true, \comment{These constructions are dyadics}
 %
@@
 \textit{Radiating:} On the contrary, while working from the frame of the pixel ``q'', the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.
-The E \& B mode maps resulting from the Stokes Q \& U parameters specified at location $\hat{n}_q$ is given by the following expression,
+The E \& B mode maps resulting from the Stokes Q \& U parameters specified at the location $\hat{n}_q$ is given by the following expression,
 %
@@
 
-Recall that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$ \comment{The following argument is that of the product of a number with a field, so is this relevant ?
-}.
-If one rotates by an angle $\phi$ about the local $\hat{z}_q$ axis, the local Stokes parameters transform as: ${}_{+2}X(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{i2\phi} $.
-Since this angle $\phi$ can be thought of as the phase angle $\gamma$ in the $z-y_1-z_2$ convention of Euler angles, one can see that: $e^{-i2\alpha_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{-i2\phi}$.
-The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
+Recall that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$ \comment{The following argument is that of the product of a number with a field, so is this relevant ?}.
+If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new rotated frame are given by: ${}_{+2}X(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
+\revisit{Recall that the Euler angle $\alpha_{qe}$ in the $z-y_1-z_2$ sense of rotations is such that it aligns the local $\hat{x}_q$-axis along the geodesic in the direction of $\hat{n}_e$.
+Now if the local planar axes are already rotated by an angle $\phi$ then $\alpha_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.} The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
 Given these transformation properties one can now note that the product ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence must form a spin-0 field.
@@
 
-Using \eq{eq:qu2eb_radiation_explicit} one can see that when $q=e$: $E_q=-{{}_{\mm}f}(\beta_{qq})Q_q$ and $B_q = -{{}_{\mm}f}(\beta_{qq})U_q$ which does not transform as a spin-0 field under local rotations unless ${{}_{\mm}f}(\beta_{qq}=0)=0$.
+Using \eq{eq:qu2eb_radiation_explicit} one can see that when $q=e ~(\beta_{qq}=0\,,\, \alpha_{qq}=0,2\pi,4\pi,...)$: $E_q=-{{}_{\mm}f}(\beta_{qq})Q_q$ and $B_q = -{{}_{\mm}f}(\beta_{qq})U_q$ which does not transform as a spin-0 field under local rotations unless ${{}_{\mm}f}(\beta_{qq}=0)=0$.
 One can make a similar argument when pixels ``q'' and ``e'' are diametrically opposite.
@@
 %
-We do not provide the explicit derivation here, since the procedure is identical to that discussed in the previous section. The inverse operator is given by the following expression,
+Providing the explicit derivation here will be redundant with that described in the previous sections and hence we avoid that.
+The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
+%
+\beq
+\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
+\eeq
+%
+
+ The inverse operator is given by the following expression,
 %

### 2017-11-25 codes/make_eb_gen_movie/gen_gif_animate.py
added a code to make a plot of the e and b mode at various stages of construction, especially using the radiating form of the kernels

@@ -1,0 +1,3 @@
+convert -quality 99 -density 200 -delay 40 -loop 0 egen_*.pdf egen_animate.gif
+convert -quality 99 -density 200 -delay 40 -loop 0 bgen_*.pdf bgen_animate.gif
+

### 2017-11-27 codes/make_eb_gen_movie/eb_gen/gen_gif_animate.py
Added scripts to make movie of e-mode generation, euler angle explanation and the radiating and convolving interpretations of stokes qu to eb translation.

@@ -1,0 +1,2 @@
+convert -quality 99 -density 150 -delay 30 -loop 0 ./figures/egen_*.pdf egen_animate.gif
+convert -quality 99 -density 150 -delay 30 -loop 0 ./figures/bgen_*.pdf bgen_animate.gif

### 2017-11-27 codes/make_eb_gen_movie/gen_gif_animate.py

@@ -1,3 +1,0 @@
-convert -quality 99 -density 200 -delay 40 -loop 0 egen_*.pdf egen_animate.gif
-convert -quality 99 -density 200 -delay 40 -loop 0 bgen_*.pdf bgen_animate.gif
-

### 2017-11-27 codes/modules/convert_qu2eb.py

@@ -80,8 +80,8 @@ def convert_qu2eb_radiate_masked(q,u,theta_cutoff,theta,rad_ker,mask=[]):
 		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
 		gbeta=fn_rad_ker(cosbeta)
 		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
-		e[spix] = e[spix] + (-q[i]*cafb - u[i]*safb)*domega
-		b[spix] = b[spix] + ( q[i]*safb - u[i]*cafb)*domega
+		e[spix] = e[spix] + (-q[i]*cafb + u[i]*safb)*domega
+		b[spix] = b[spix] + (-q[i]*safb - u[i]*cafb)*domega
 	return [np.zeros(npix),e,b]
 
 ###########################################################################################

### 2017-11-28 articles/formalism/sections/real_space_formalism.tex
Added new plot generation scripts: 1. euler angles plots and movie, 2. plot elucidating the radiation and convolution. | Tested the existing codes for conversion to qu2eb and eb2qu and qu2equ&bqu

@@
 Owing to this, we begin with a brief discussion on Euler angles and present visual method to think about them.
-
+%
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.5\columnwidth]{euler.pdf}
+\caption{}
+\label{fig:euler_angles}
+\end{figure}
+%
 \textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east.
@@
 %and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
-
+%
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
+\caption{}
+\label{fig:euler_angles}
+\end{figure}
+%
 \textit{Radiating:} On the contrary, while working from the frame of the pixel ``q'', the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.

### 2017-11-28 codes/make_eb_gen_movie/eb_gen/gen_gif_animate.py

@@ -1,2 +1,0 @@
-convert -quality 99 -density 150 -delay 30 -loop 0 ./figures/egen_*.pdf egen_animate.gif
-convert -quality 99 -density 150 -delay 30 -loop 0 ./figures/bgen_*.pdf bgen_animate.gif

### 2017-11-28 codes/modules/convert_eb2qu.py

@@ -17,8 +17,8 @@ def convert_eb2qu_integrate(e,b,theta_cutoff,theta,rad_ker):
 		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
 		gbeta=fn_rad_ker(cosbeta)
 		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
-		q[i] = (np.dot(-cafb,e[spix]) + np.dot( safb,b[spix]))*domega
-		u[i] = (np.dot(-safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
+		q[i] = (np.dot(-cafb,e[spix]) + np.dot(-safb,b[spix]))*domega
+		u[i] = (np.dot( safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
 	return [np.zeros(npix),q,u]
 
 
@@ -41,8 +41,8 @@ def convert_eb2qu_integrate_masked(e,b,theta_cutoff,theta,rad_ker,mask=[]):
 		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
 		gbeta=fn_rad_ker(cosbeta)
 		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
-		q[i] = (np.dot(-cafb,e[spix]) + np.dot( safb,b[spix]))*domega
-		u[i] = (np.dot(-safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
+		q[i] = (np.dot(-cafb,e[spix]) + np.dot(-safb,b[spix]))*domega
+		u[i] = (np.dot( safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
 	return [np.zeros(npix),q,u]
 
 

### 2017-12-05 articles/formalism/sections/real_space_formalism.tex
Minor edits to Euler angles plot/movie. Added appendix in formalism paper deriving the important identity on product of spin spherical harmonics and the radiating and convolution interpretations of the kernel.

@@
 \includegraphics[width=0.5\columnwidth]{euler.pdf}
-\caption{}
+\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
+The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
 \label{fig:euler_angles}
@@
 %
-\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east.
+
+\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east as shown in \fig{fig:euler_angles}.
 The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
 
-Specifically $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-In more physical terms, these angles can be understood as follow: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
+For this work, we believe it is convenient to work in the z-y1-z2 convention, therefore all future references to Euler angles are to be assumed to be given in this convention.
+\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}
+In the z-y1-z2 convention, $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
+In more \revisit{physical terms}, these angles can be understood as follows: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
 The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, such that the z-axes of the two coordinate systems are parallel to each other.
 Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
+The different Euler angles and the corresponding rotations are depicted in \fig{fig:euler_angles}.
 
-The simplest case is when one of the coordinates coincides with the north pole (more formally this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), say $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$.
-In this case it is easy to visualize and infer that the rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$ in the $z-y1-z2$ sense, will align the local cartesian system at the pole with that defined at position $\hat{n}_i$.
-The Euler angles in the $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$.
+The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$ will align the cartesian system at $\hat{n}_0$ with that defined at position $\hat{n}_i$.
 %--------------------------------------------------------
@@
 where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are measured and the index ``q'' to denote the location where the Stokes parameters are measured.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true, \comment{These constructions are dyadics}
+\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true, \comment{These constructions are dyadics}
 %
@@
  where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
+Note that each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by some linear combination of a complex number and its conjugate.
 The $m$ sum over the product of two spherical harmonic functions with spins $s_1$ and $s_2$ respectively, is given by the following identity \cite{varshalovich},
@@
 \includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{}
+\caption{The local cartesian coordinate are only drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
+The coordinates are not drawn on the blue circle representing the fact that the value of the scalar field does not depend of the coordinate definition.
+The value of the scalar field at the specific location `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle (sphere).
+The convolutions are performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
+Alternatively, if centered on `q' then one can compute the contribution from the Stokes parameter at this specific location to all the point on the blue circle(sphere).
+The contribution across the sky from the Stokes parameter at the location `q'  is given by a function of the Euler angle $\alpha_{eq}$.
+In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
 \label{fig:euler_angles}

### 2017-12-05 codes/modules/aliasing_correction.py

@@ -49,13 +49,45 @@ def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
 		hu[i]=(np.dot(-Ii,q[spix]) + np.dot(Ir,u[spix]))*domega
 
 	return hq,hu
-			
 
-def correct_aliasing(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
+def correct_aliasing_convolve(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
 	npix=np.size(tq)
 	cq=np.zeros(npix,"double") ; cu=np.zeros(npix,"double")	
 	for i in range(iter):
 		hq,hu=delta_convolve(tq-cq,tu-cu,theta_cutoff,theta,rad_ker_i,mask)
+		cq=cq + (hq-tq) ; cu=cu + (hu-tu)
+
+	return [np.zeros(npix),tq-cq,tu-cu]
+
+def delta_radiate(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	hq=np.zeros(npix,"double")
+	hu=np.zeros(npix,"double")
+	
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+		
+	for i in pix_list:
+		beta,alpha,gamma,spix=return_euler_angles(nside,i,theta_cutoff,inclusive=True,fact=4)
+		Ir=np.cos(2.*(alpha+gamma))*fn_rad_ker_i(beta)
+		Ii=np.sin(2.*(alpha+gamma))*fn_rad_ker_i(beta)
+
+		hq[spix]=hq[spix] + (q[i]*Ir - u[i]*Ii)*domega
+		hu[spix]=hu[spix] + (q[i]*Ii + u[i]*Ir)*domega
+
+	return hq,hu
+			
+
+def correct_aliasing_radiate(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
+	npix=np.size(tq)
[…]

### 2017-12-05 codes/modules/backup_working_codes/convert_eb2qu.py
This is a working version of the codes. However the notation is untidy, since there are extra negative signs floating around in the calculation of the Euler angles. In the clean version, this is being tidied up so that the code resembles the equations in the paper

@@ -1,0 +1,102 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Integrating method to generate E and B mode maps.
+def convert_eb2qu_integrate(e,b,theta_cutoff,theta,rad_ker):
+	'''
+	   This function uses E and B maps in regions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+	q=np.zeros(npix,"double")
+	u=np.zeros(npix,"double")
+	for i in range(npix):
+		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(cosbeta)
+		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
+		q[i] = (np.dot(-cafb,e[spix]) + np.dot(-safb,b[spix]))*domega
+		u[i] = (np.dot( safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
+	return [np.zeros(npix),q,u]
+
+
+def convert_eb2qu_integrate_masked(e,b,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses E and B maps in reggions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
[…]

### 2017-12-05 codes/modules/backup_working_codes/convert_qu2_equ_bqu_old.py

@@ -1,0 +1,53 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''
+	This Euler angles function works for the qu2_equ_bqu function.
+	The set of function here, match Healpix results to numerical accuracy.
+	'''
+	theta1,phi1=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	theta2,phi2=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
+	beta=np.arccos(cosbeta)
+
+	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
+    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
+    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
+    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
+	return beta,alpha,gamma,spix
+
+def convert_qu2_equ_bqu(q,u,theta_cutoff,theta,rad_ker_i,rad_ker_d):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	fn_rad_ker_d=interp1d(theta,rad_ker_d,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	equ=[np.zeros(npix,"double"),np.zeros(npix,"double")]
[…]

### 2017-12-05 codes/modules/backup_working_codes/rs_rad_ker.py

@@ -1,0 +1,127 @@
+from scipy.special import lpmn as lpmn
+import numpy.polynomial.legendre as lgdr
+from scipy.interpolate import interp1d
+import scipy.integrate as intg
+import numpy as np
+import sys
+
+def mod_rad_ker(theta,shift=0.2,width=0.5,amp=1.,slope=2.,expslope=2.):
+	rad_ker=((amp*theta)**slope)*np.exp(-((theta-shift)/(np.sqrt(2.)*width))**expslope)
+	return rad_ker
+
+def fn_apodization(theta,theta_cutoff=np.pi/6.,apow_frac=0.2):
+	fnapo=np.zeros(theta.size,"double")
+	apow=apow_frac*theta_cutoff
+	# Cosine squared apodization.
+	x=(theta-(theta_cutoff-apow))*np.pi/(2.*apow)
+	fnapo=np.cos(x)**2.
+	fnapo[theta<=theta_cutoff-apow]=1.
+	fnapo[theta>theta_cutoff]=0.
+	return fnapo
+
+def get_plm0(lmax,sampling,theta_min=0.,theta_max=np.pi,m0=2,theta=np.zeros(0,"double")):
+	'''This is written to get the associated Legendre polynomials at a fixed m0. The default m0=2
+	When the array costheta is provided, the sampling parameter is ignored.
+	'''
+	if np.size(theta)==0:
+		theta=np.linspace(theta_min,theta_max,sampling)
+
+	csth=np.cos(theta)
+	pl2=np.zeros((lmax+1,np.size(csth)),"double")
+	for i in range(np.size(csth)):
+		plm,dplm=lpmn(m0,lmax,csth[i])
+		for l in range(lmax+1):
+			pl2[l,i]=plm[m0,l]
+	return theta,pl2
+
+# This is the default radial kernel.
+def calc_qu2eb_rad_ker(lmax,theta,pl2,lmin=2):
+	if lmax>np.size(pl2[:,0])-1:
+		#print "lmax given:",lmax
+		#print "Maximum multipole of Legendre polynomials:", np.size(pl2[:,0])-1
[…]

### 2017-12-05 codes/modules/convert_qu2_equ_bqu.py

@@ -27,27 +27,73 @@ def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
 
 	return beta,alpha,gamma,spix
 
-def convert_qu2_equ_bqu(q,u,theta_cutoff,theta,rad_ker_i,rad_ker_d):
-	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+def convert_qu2_equ_bqu_integrate(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
+	'''Pass alias corrected TQU map to this routine.'''
+	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
+	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
+	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
 	fn_rad_ker_d=interp1d(theta,rad_ker_d,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
 	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
 
-	equ=[np.zeros(npix,"double"),np.zeros(npix,"double")]
-	bqu=[np.zeros(npix,"double"),np.zeros(npix,"double")]
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+
+	dqu=[np.zeros(npix,"double"),np.zeros(npix,"double")]
 	
-	for i in range(npix):
-		beta,alpha,gamma,spix=return_euler_angles(nside,i,theta_cutoff,inclusive=True,fact=4)
-		Ir=np.cos(2.*(alpha+gamma))*fn_rad_ker_i(beta)
-		Ii=np.sin(2.*(alpha+gamma))*fn_rad_ker_i(beta)
-		Dr=np.cos(2.*(alpha-gamma))*fn_rad_ker_d(beta)
[…]

### 2018-03-30 articles/formalism/sections/generalizedeb.tex
updates to the polarization primer section of the formalism paper

@@
 If we require both the forward and inverse operators to be well defined, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that it has a valid  inverse.
+As we will see this will be an important criteria to recover the standard CMB spectra.
 The radial part of these generalized convolution kernels is given by the following expressions,
@@
 %
-Here it is important to note that the radial function $G(\beta)$ has to be chosen such that it vanishes at $\beta=0$ and $\beta=\pi$. 
+To ensure that the resultant field is a spin-0 field, it is important to note that the radial function $G(\beta)$ has to be necessarily chosen such that it vanishes at $\beta=0$ and $\beta=\pi$. 
 %One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
@@
 It is important to ensure consistency with the convention once a choice has been made.} \comment{find a better location for this}
+
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B mode fields being convolved with some circularly symmetric instrument beam. 
 Note that in contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
@@
 where $b_{\ell}$ denote the coefficients of expansion.
+\comment{Note that one can directly get E and B mode maps resulting from convolution with a non-circular beam by chosing the function $g_{\ell}$ to have some m dependence.}
 %
@@
 \centering
-\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}\\
 \subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
+\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
 \subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
@@
 %
-which are not the standard $E$ and $B$ modes maps.
-Since the the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some beam,  the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
+which as we show are mere filtered version of he standard $E$ and $B$ modes maps.
+The harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam $B(\beta) = \sum_{\ell} \frac{2 \ell+1}{4 \pi} g_{\ell} P^0_{\ell}(\cos{\beta})$.
+The spectra of the scalar fields $E'$ and $B'$ derived using the real space operators constructed using an arbitrary radial function $G(\beta)$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %
@@
 Therefore the standard $E$ and $B$ mode spectra can be recovered from the modified fields $E'$ and $B'$ and their accurate recovery only relies on the inverse of the harmonic functions $1/g_{\ell}$ being well behaved, which can be ensured by making a suitable choice for the radial function $G(\beta)$.
+Examples of various forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
 %One direct application of this freedom in choosing the radial kernel is that one can mitigate the issue of leakage of power from $E$ to $B$.

### 2018-03-30 articles/formalism/sections/real_space_formalism.tex
updates to the polarization primer section of the formalism paper

@@
 \section{Polarization primer}\label{sec:pol-primer}
-The CMB polarization is measured in terms of Stokes Q and U parameters. These measurements can be combined to form the complex spin 2 polarization field as follows,
+The CMB polarization is measured in terms of Stokes Q and U parameters.
+The Stokes Q is defined as the linear polarization measured along local cartesian axes ($+$ along the x-axis and $-$ along the y-axis) while Stokes U is defined as the linear polarization measured along the cartesian axes rotated by $45^{\circ}$ ($+$ along x-axis and $-$ along the y-axis in the counter-clockwise rotated system).
+Clearly the definitions of Stokes parameters depend on the choice of the coordinate system and it can be shown that the measurement made in two different coordinate systems rotated by an angle $\phi$ are related by the following equation,
 %
-\beqry \label{eq:spin-pol}
-_{\pm 2}\bar{X}(\hat{n}) &=& Q(\hat{n}) \pm i U (\hat{n}) \nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  \, {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
-\eeqry
+\beq \label{eq:qu-rot}
+\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,,
+\eeq
 %
-Since these measured quantities depend on the local coordinate system, it is cumbersome to work with them.
-To overcome this, one describes the CMB polarization field in terms of a scalar field denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
-These scalar fields are related to the spin-2 polarization field $_{\pm 2}X(\hat{n})$ via the following relations,
+which one can simply checked by verifying that $Q' \rightarrow U$ and $U' \rightarrow -Q$ when the coordinate systems are rotated by $45^\circ$ in the counter-clockwise sense.
+
+Following the notation of \cite{Zaldarriaga1997}, fields which transform as,
+%
+\beq
+{}_{s}f' = e^{-is\psi} {}_{s}f \,,
+\eeq
+%
+under right handed rotations of the local coordinate system are termed spin-s fields. The Stokes parameters can be combined to define the complex fields,
+%
+\beq \label{eq:spin-pol}
+_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n}) \,, %\nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  \, {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
+\eeq
+%
+which under rotation of the local tangent plane coordinate system by an angle $\psi$ at any point on the sphere transform as: $_{\pm 2}X' = e^{\mp i2\psi} {_{\pm 2}X}$, which follows directly from \eq{eq:qu-rot}.
+Hence the quantities $_{\pm2}X$ behave as spin${\pm2}$ respectively.
+
+The Stokes parameters being coordinate dependent quantities, it is cumbersome to work with them.
+It is possible to define spin raising ($\eth$) and spin lowering $(\bar{\eth})$ operators on the sphere \cite{goldberg67}.
+These operators are such that when the spin raising operator acts on a spin-s field $_{s}f$ results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$ and similarly when a spin lowering operator acts on the field results in a field with spin-$(s-1)$: $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
+This challenge is overcome by describing the CMB polarization field in terms of coordinate independent scalar fields denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
+These scalar fields are constructed from the spin-2 polarization fields $_{\pm 2}X(\hat{n})$ via the following mathematical operations,
 %
@@
 where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively.
-These $E$ and $B$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions (except that the B-modes have an odd parity, meaning that they change sign under reflection $\hat{n} \rightarrow -\hat{n}$.).
+These $\mathcal{E}$ and $\mathcal{B}$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions (except that the B-modes have an odd parity, meaning that they change sign under reflection $\hat{n} \rightarrow -\hat{n}$.).
 The spin raising and lowering operators have the following properties \cite{goldberg67},
@@
 
-For this work, we believe it is convenient to work in the z-y1-z2 convention, therefore all future references to Euler angles are to be assumed to be given in this convention.
+For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention.
 \footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}
@@
 %--------------------------------------------------------
+\subsection{A heuristic argument for constructing spin-0 $E$ and $B$ fields}\label{sec:qu2eb_heuristic}
+
+%--------------------------------------------------------
+
 \subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
@@
  where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Note that each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by some linear combination of a complex number and its conjugate.
+Note that each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by some linear combination of a complex number and its conjugate and is hence real.
 The $m$ sum over the product of two spherical harmonic functions with spins $s_1$ and $s_2$ respectively, is given by the following identity \cite{varshalovich},
@@
 The Euler angles for the inverse rotations are given by the Euler angles $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$\cite{varshalovich}.
-Since the kernels only depend on the cosine of the Euler angle $\beta$, they are immune to the change in its sign.
+Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
 More importantly, the ordering of indices  on the Euler angle $\alpha$ and $\gamma$  is important and leads to two different interpretations of the real space kernels.
@@
 \beq  \label{eq:qu2eb_radiation_explicit}
-\bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
+\bar{S}_q = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
 \eeq

### 2018-04-04 articles/formalism/sections/real_space_formalism.tex
updates to section 2 and 3.0

@@
 which under rotation of the local tangent plane coordinate system by an angle $\psi$ at any point on the sphere transform as: $_{\pm 2}X' = e^{\mp i2\psi} {_{\pm 2}X}$, which follows directly from \eq{eq:qu-rot}.
-Hence the quantities $_{\pm2}X$ behave as spin${\pm2}$ respectively.
+Therefore the quantities $_{\pm2}X$ are spin${\pm2}$ fields respectively.
 
-The Stokes parameters being coordinate dependent quantities, it is cumbersome to work with them.
-It is possible to define spin raising ($\eth$) and spin lowering $(\bar{\eth})$ operators on the sphere \cite{goldberg67}.
-These operators are such that when the spin raising operator acts on a spin-s field $_{s}f$ results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$ and similarly when a spin lowering operator acts on the field results in a field with spin-$(s-1)$: $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
-This challenge is overcome by describing the CMB polarization field in terms of coordinate independent scalar fields denoted by $E(\hat{n}) $ and a pseudo scalar field $B(\hat{n}) $ \cite{Kamionkowski1997}.
-These scalar fields are constructed from the spin-2 polarization fields $_{\pm 2}X(\hat{n})$ via the following mathematical operations,
+The Stokes parameters being coordinate dependent quantities it is inconvenient to work with them.
+It is possible to define spin raising ($\eth$) operator on the sphere which when operated on a field of spin-s $_{s}f$ results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$ and similarly one can define a spin lowering $(\bar{\eth})$ operators such that $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$\cite{goldberg67}.
+One can now construct a complex spin-0 scalar by applying the spin raising and lowering operators on the spin-2 fields ${_{\pm 2}X}$ as follows,
 %
-\beq \label{eq:ebdef}
-\mathcal{E}(\hat{n}) = -\frac{1}{2} \big[ \bar{\eth}^2 _{+ 2}\bar{X}(\hat{n})  +  \eth^2 _{- 2}\bar{X}(\hat{n}) \big] ~\,;~\mathcal{B}(\hat{n}) = -\frac{1}{2i} \big[ \bar{\eth}^2 _{+ 2}X(\hat{n})  -  \eth^2 _{- 2}X(\hat{n}) \big] \,,
-\eeq
+\begin{subequations}\label{eq:ebdef}
+\beqry
+\mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\\
+\mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,,
+\eeqry
+\end{subequations}
 %
-where $\eth$ and $\bar{\eth}$ denote the spin raising and lowering operators respectively.
-These $\mathcal{E}$ and $\mathcal{B}$ fields are spin-0 fields similar to the temperature anisotropies and hence their value are independent of the coordinate system definitions (except that the B-modes have an odd parity, meaning that they change sign under reflection $\hat{n} \rightarrow -\hat{n}$.).
-The spin raising and lowering operators have the following properties \cite{goldberg67},
+which by the virtue of being scalars are independent of coordinate definitions.
+%The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
+
+The complex field $_{\pm 2}X$ defined on the sphere can be decomposed in spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities\cite{goldberg67},
 %
-\beqrys \label{eq:spinopylm} 
+\begin{subequations}\label{eq:spinopylm} 
+\beqry
 \eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
 \bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
-\eeqrys
+\eeqry
+\end{subequations}
 %
@@
 
-Using \eq{eq:ebdef} and the properties of the spin raising and lowering operators given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are defined via the following set of equations,
+Using \eq{eq:ebdef}, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
 %
@@
 %
-where the harmonic coefficients of  $\mathcal{E}/\mathcal{B}$ fields are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
+where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
 %
 \beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] 
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
 \eeq
 %
-In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following expressions, 
+In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
 %
@@
 %
-Note that the $[E,B]$ fields are merely filtered versions of the fields $[\mathcal{E},\mathcal{B}]$, as their spherical harmonic coefficients of expansion differ by the factor $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 %
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed if favor of cleaner notation.
+The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed in favor of cleaner notation.
 
@@
 %
-Next we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
+Finally we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
 %
@@
 All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Owing to this, we begin with a brief discussion on Euler angles and present visual method to think about them.
+Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
 %
@@
 \textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east as shown in \fig{fig:euler_angles}.
-The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_0 \equiv (\theta_0,\phi_0)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_i \equiv (\theta_i,\phi_i)$ \cite{varshalovich}.
+The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_q \equiv (\theta_q,\phi_q)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_e \equiv (\theta_e,\phi_e)$ \cite{varshalovich}.
 
-For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention.
-\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}
+For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}.
 In the z-y1-z2 convention, $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-In more \revisit{physical terms}, these angles can be understood as follows: The rotation by $\alpha$ about the z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_0$ along the great circle in the direction of $\hat{n}_i$.
-The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_0$ to location $\hat{n}_i$, such that the z-axes of the two coordinate systems are parallel to each other.
-Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_i$.
-The different Euler angles and the corresponding rotations are depicted in \fig{fig:euler_angles}.
+These angles can be understood as follows: The rotation by $\alpha$ about the original z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_q$ along the great circle in the direction \revisit{of shortest arc length} towards $\hat{n}_e$.
+The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_q$ to location $\hat{n}_e$, such that the z-axes of the two coordinate systems are parallel to each other.
+Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_e$.
+The different Euler angles and the corresponding rotations are schematically represented in \fig{fig:euler_angles}.
 
-The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_0=(\theta_0,\phi_0)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$ will align the cartesian system at $\hat{n}_0$ with that defined at position $\hat{n}_i$.
+The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_q=(\theta_q,\phi_q)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_e,\theta_e,0)$ will align the cartesian system at $\hat{n}_q$ with that defined at position $\hat{n}_e$.
 %--------------------------------------------------------
-\subsection{A heuristic argument for constructing spin-0 $E$ and $B$ fields}\label{sec:qu2eb_heuristic}
 
 %--------------------------------------------------------
-
 \subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
@@
 In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
-\label{fig:euler_angles}
+\label{fig:planar_euler_angles}
 \end{figure}

### 2018-04-05 articles/formalism/sections/real_space_formalism.tex
Added a section presenting a heuristic argument for constructing E/B modes on the sphere

@@
 %--------------------------------------------------------
+\subsection{A heuristic argument for constructing  $E/B$ modes from Stokes parameters $Q/U$ on the sphere} \label{sec:qu2eb_heuristic}
+The primary aim here is to make intuitive the construction of the spin-0 $E/B$ modes of polarization from the Stokes parameters.
+We present heuristic arguments which allows us to derive the important features of the real space kernels\footnote{These heuristic arguments were developed in hindsight but are very instructive.}.
+
+If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes charge in the new coordinate system is related to the Stokes charge in the original coordinate system as: ${}_{+2}X'(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
+Similarly if the local planar axes are rotated by an angle $\phi$ then the Euler angle $\alpha_{qe}$ (recall that this Euler angle aligns the x-axis at $\hat{n}_q$ in the direction of the shortest path along the geodesic to the location $\hat{n}_e$) for the new coordinate system is given by: $\alpha'_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.
+The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
+Given these transformation properties note that: ${}_{+2}X'(\hat{n}_q)e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence by definition must form a spin-0 field.
+Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
+Therefore we can make the association: $E'+iB' \propto {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$
+
+Now note that when the two locations coincide $\hat{n}_q = \hat{n}_e$ then  $\alpha_{qe}=0,2\pi,4\pi,\cdots$ implying $E + iB \propto Q+iU$, which is a fallacy as we know that $Q+iU$ does not transform as a spin-0 field under local rotations.
+One runs into a similar fallacy when the two locations are diametrically opposite.
+Therefore to have a consistent definition of a spin-0 field constructed from a spin-2 field we require the kernel to have the form: $E'+iB' = {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}$, where the function $f(\beta_{qe})$ is such that it vanishes when the two locations are coincident$(\beta_{qe}=0)$ or diametrically opposite$(\beta_{qe}=\pi)$.
+Hence the $E/B$ fields are necessarily non-local.
+Note that this construction can be generalized to transform fields of arbitrary spin to a field of any other spin, one obvious case being constructing the Stokes field given the $E/B$ maps (i.e.
+deriving spin-2 fields from spin-0 fields.)
+
+The azimuthal part which depends only on the Euler angle $\alpha_{qe}$, has no multipole $\ell$ dependence and is the crucial operation which translates between the different spin representation of CMB polarization.
+Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation $|\beta_{qe}|$ between different locations on the sphere and hence must completely incorporate the multipole $\ell$ dependence of the kernel.
+These heuristic arguments cannot take us any further and we now shift to presenting a mathematically rigorous derivation of the real space operators in the following sections.
+%--------------------------------------------------------
+
+%--------------------------------------------------------
 \subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we described the standard procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
+In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
 %To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-Here we derive the real space convolution kernels on the sphere, which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
-We use the relations given in \eq{eq:pol_data_relns}, to write down an equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
+In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
+We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
 %
@@
 \bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,.
+&=&  \bar O *\bar{P} \,. \label{eq:qu2eb_op}
 \eeqrys
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.
-This procedure of contracting over the operators is explicitly worked out in the following set of equations,
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations,
 %
@@
 %
-where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-\revisit{We purposefully use the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed.} Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following relation holds true, \comment{These constructions are dyadics}
+where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
+Note that here we purposefully introduce the notation of the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed.
+Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
 %
 \beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,.
+ \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,,
  \eeq
@@
 where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Note that each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by some linear combination of a complex number and its conjugate and is hence real.
-The $m$ sum over the product of two spherical harmonic functions with spins $s_1$ and $s_2$ respectively, is given by the following identity \cite{varshalovich},
+Note that the operator $\bar{O}$ is real as one expects, since each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by summing a complex number and its conjugate.
+
+\noindent \eq{eq:qu2eb_ker_1} already presents a real space operator, but it is not in a form which can be practically implemented.
+To arrive at a real space operator which is practially usable, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles\cite{varshalovich},
 %
@@
 %
-where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles.
-Therefore the different parts of the real space operator $\bar{O}$  are completely specified in terms of the complex function,
+where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ so as to allign the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
+The different parts of the real space operator $\bar{O}$  are completely specified by the complex function,
 %
@@
 %
-where we have used the identity given in \eq{eq:sum_spin_shf} to simplify the product of the spherical harmonic functions.
-On simplifying \eq{eq:qu2eb_ker_1}, the local convolution kernel can be cast in this simple form,
+where we have used the identity in \eq{eq:sum_spin_shf} to simplify the product of the spherical harmonic functions.
+Note that the function on the right depends only on two out of the three Euler angles.
+Employing \eq{eq:qu2eb_gen_kernel} to simplify the product of spherical harmonic functions in \eq{eq:qu2eb_ker_1}, the real space operator $\bar{O}$ can now be cast in this more useful form,
 %
-\beq\label{eq:op_qu2eb}
-\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,.
+\beq\label{eq:op_qu2eb_rad}
+\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
 \eeq
 %
-Specifically note that $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at the location $\hat{n}_q$ where the Stokes field is measured to the cartesian system at the location $\hat{n}_e$ where the scalar fields are evaluated: $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
-The Euler angles for the inverse rotations are given by the Euler angles $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$\cite{varshalovich}.
+where, we reiterate, $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
+
+\textit{Radiating kernel:} Using \eq{eq:op_qu2eb_rad} in \eq{eq:qu2eb_op} one can see that the $E$/$B$ contribution of the Stokes parameters at some location $\hat{n}_q$ is given by the following expression,
+%
+\beq  \label{eq:qu2eb_radiation_explicit}
+\bar{S}_q = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
+\eeq
+%
+The total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
+This operation can be cast in a concise form as follows,
+%
+\begin{subequations} \label{eq:qu2eb_radiation_concise}
+\beqry 
+\left[E + iB\right] &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
+&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
+&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{Green}[\hat{n}_q] \,,
+\eeqry
+\end{subequations}
+%
+where ``$\cdot$'' denotes a simple scalar multiplication and $\mathcal{M}_{Green}$ is a function that spans the sphere and sourced at $\hat{n}_q$.
+In fact $\mathcal{M}_{Green}$ can be thought of as the Green's function of the operator since $[E +iB] = \mathcal{M}_{Green}$ generated from the Stokes charge $[Q+iU] = [\delta(\hat{n}-\hat{n}_q) + i 0]$.
+
+We denote the kernel expressed in terms of the Euler angle $\alpha$ as the radiating kernel, since it allows us to evaluate the $E/B$ field contribution across the sphere due to a single Stoke (charge) parameter at a fixed location on the sphere.
+The total $E/B$ maps can then be thought of as just superposed radiation emerging from Stokes charges across the sphere.
+In this formulation, one is in effect in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field across the sphere.
+%
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
+\caption{The local cartesian coordinate are only drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
+The value of the scalar field at location `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle (sphere).
+The convolutions are performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
+Alternatively, one can compute the contribution from the Stokes parameter at location `q' to all the point on the blue circle(sphere) and this is a function of the Euler angle $\alpha_{eq}$.
+In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
+\label{fig:planar_euler_angles}
+\end{figure}
+%
+
+\textit{Convolution kernel:} We can also formulate the real space operator to be a function of Euler angles corresponding to the inverse rotation.
+The Euler angles for the inverse rotations (i.e.
+to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$) are related to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
 Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
-More importantly, the ordering of indices  on the Euler angle $\alpha$ and $\gamma$  is important and leads to two different interpretations of the real space kernels.
-
-\textit{Convolution:} Working from the frame of the pixel ``e'' where the scalar modes need to be evaluated, the Euler angles to the surrounding pixels are: $\alpha_{eq}, \beta_{eq},\gamma_{eq}$.
-In terms of these Euler angles, the value of scalar fields $E$ \& $B$ at the central pixel ``e" can be evaluated by convolving over the measured Stokes $Q$ \& $U$ parameters in the surrounding pixels marked by indices ``q''.
-Specifically, the convolution is fully defined in terms of the Euler angles $\beta_{eq}~ \& ~\gamma_{eq}$ and is given by the following equation,
+The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows,
 %
@@
 %
-where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
-%\revisit{This has an elegant interpretation: to derive the E and/or B field at any given position we need to find the cosine quadrupole transform and the sine quadrupole transform of the Stokes Q \& U parameters on circles around this position, weigh the transform by the value of the function $f(\beta,\ell_{\rm min},\ell_{\rm max})$, $\beta$ being the radius of the circle and sum up the results with appropriate signs, to construct the respective scalar fields.}
-When written in terms of the complex spin-0 field $[E + iB]$ and the spin-2 field ${}_{+2}X$, the above equation can be expressed more concisely as follows,
+%where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
+\revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere.
+This operation can be expressed more concisely as follows,
 %
@@
 %
-where $\circ$ denotes the convolution and the spherical harmonic functions denote the rotated functions such that the pole of the function coincides with the direction $\hat{n}_e$.
-%and the reference zero for the azimuthal angle is the local longitude $\phi_0$.
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{The local cartesian coordinate are only drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
-The coordinates are not drawn on the blue circle representing the fact that the value of the scalar field does not depend of the coordinate definition.
-The value of the scalar field at the specific location `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle (sphere).
-The convolutions are performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-Alternatively, if centered on `q' then one can compute the contribution from the Stokes parameter at this specific location to all the point on the blue circle(sphere).
-The contribution across the sky from the Stokes parameter at the location `q'  is given by a function of the Euler angle $\alpha_{eq}$.
-In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
-\label{fig:planar_euler_angles}
-\end{figure}
-%
-\textit{Radiating:} On the contrary, while working from the frame of the pixel ``q'', the Euler angles to the surrounding pixels are: $\alpha_{qe}, \beta_{qe},\gamma_{qe}$.
-The E \& B mode maps resulting from the Stokes Q \& U parameters specified at the location $\hat{n}_q$ is given by the following expression,
-%
-\beq  \label{eq:qu2eb_radiation_explicit}
-\bar{S}_q = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
-\eeq
-%
-The total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
-The above expression can again be cast in a more concise form as follows,
-%
-\begin{subequations} \label{eq:qu2eb_radiation_concise}
-\beqry 
-\left[E + iB\right] &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
-&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{Green}(\hat{n}_{q}) \,,
-\eeqry
-\end{subequations}
-%
-where ``$\cdot$'' denotes a simple scalar multiplication.
-\revisit{$\mathcal{M}_{Green}(\hat{n}_{q})$ is response of the real space operator $\bar{O}$ when operated on a Stokes field: $\delta(\hat{n}-\hat{n}_q) + i \delta(\hat{n}-\hat{n}_q)$, hence it can be thought of as the Green's function of the real space operator.} \comment{Is this interpretation correct ?
-Is the complex delta function a spin 2 function ?}
+where $\circ$ denotes a convolution and $\mathcal{M}_{Beam}$ can be interpreted as some effective instrument beam pointing to the direction $\hat{n}_e$. 
+%--------------------------------------------------------
 
-Recall that the product of two functions with spins $s_1$ and $s_2$ results in a function with spin $s_1 + s_2$: ${}_{s_1 +s_2}f = {}_{s_1}g \,{}_{s_2}h$ \comment{The following argument is that of the product of a number with a field, so is this relevant ?}.
-If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new rotated frame are given by: ${}_{+2}X(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
-\revisit{Recall that the Euler angle $\alpha_{qe}$ in the $z-y_1-z_2$ sense of rotations is such that it aligns the local $\hat{x}_q$-axis along the geodesic in the direction of $\hat{n}_e$.
-Now if the local planar axes are already rotated by an angle $\phi$ then $\alpha_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.} The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
-Given these transformation properties one can now note that the product ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence must form a spin-0 field.
-This argument makes intuitive, the construction of the spin-0 E and B modes of polarization from the measured Stokes parameters.
-\revisit{Here it is also interesting to note that the E-modes are constructed by product of functions $(U\sin{2 \alpha}, Q\cos{2\alpha})$ which have the same parity and hence have even parity while the B-modes are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence have an odd parity.}
-
-Using \eq{eq:qu2eb_radiation_explicit} one can see that when $q=e ~(\beta_{qq}=0\,,\, \alpha_{qq}=0,2\pi,4\pi,...)$: $E_q=-{{}_{\mm}f}(\beta_{qq})Q_q$ and $B_q = -{{}_{\mm}f}(\beta_{qq})U_q$ which does not transform as a spin-0 field under local rotations unless ${{}_{\mm}f}(\beta_{qq}=0)=0$.
-One can make a similar argument when pixels ``q'' and ``e'' are diametrically opposite.
-Therefore the radial kernels have to satisfy the constraint that they vanish at $\beta = 0, \pi$.
-The radial kernel ${{}_{\mm}f}(\beta)$ is constructed by forming a weighted linear combination of $P_{\ell}^2$ Legendre polynomials which have the following limiting form: $P_{\ell}^2(\beta) \propto \sin^2{\beta} \rightarrow 0 $ as $\beta \rightarrow 0 ,\pi$ and therefore satisfy this necessary constraint.
-
-The real space operator has a azimuthal part which depends only on the Euler angle $\alpha_{qe} (\gamma_{eq})$, has no multipole $\ell$ dependence and is the crucial operation which translates between the two different spin representation of CMB polarization.
-The radial part of the kernel is specified by the function ${}_{\mm}f(\beta,\ell_{\rm min},\ell_{\rm max})$, it depends only on the angular separation $|\beta_{eq}|$ between pixels and completely incorporates the multipole $\ell$ dependence of the kernel.
-It's the radial part of the kernel that determines the locality of the real space operator.
-%--------------------------------------------------------
 %--------------------------------------------------------

### 2018-04-05 articles/formalism/sections/real_space_formalism.tex
updated to sections 3.2 and 3.3

@@
 \beqry 
-\left[E + iB\right] &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
+\left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
 &=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{Green}[\hat{n}_q] \,,
+&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{G}[\hat{n}_q] \,,
 \eeqry
@@
 %
-where ``$\cdot$'' denotes a simple scalar multiplication and $\mathcal{M}_{Green}$ is a function that spans the sphere and sourced at $\hat{n}_q$.
-In fact $\mathcal{M}_{Green}$ can be thought of as the Green's function of the operator since $[E +iB] = \mathcal{M}_{Green}$ generated from the Stokes charge $[Q+iU] = [\delta(\hat{n}-\hat{n}_q) + i 0]$.
+where ``$\cdot$'' denotes a simple scalar multiplication.
+$\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it can be thought of as the Green's function of the operator, since $[E +iB] = \mathcal{M}_{G}$ is the spin-0 scalar field generated from the Stokes charge $[Q+iU] = [\delta(\hat{n}-\hat{n}_q) + i 0]$.
 
@@
 The total $E/B$ maps can then be thought of as just superposed radiation emerging from Stokes charges across the sphere.
-In this formulation, one is in effect in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field across the sphere.
+In this formulation, one is effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field across the sphere.
 %
@@
 &=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
-&=& \Bigg\lbrace \mathcal{M}_{Beam} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e)\,, \label{eq:qu2eb_convolution} 
+&=& \Bigg\lbrace \mathcal{M}_{B} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
 \eeqry
@@
 %
-where $\circ$ denotes a convolution and $\mathcal{M}_{Beam}$ can be interpreted as some effective instrument beam pointing to the direction $\hat{n}_e$. 
+where $\circ$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
 %--------------------------------------------------------
@@
 \subsection{Evaluating Stokes parameters $Q$ \& $U$ from scalar fields $E$ \& $B$}\label{sec:eb2qu}
-The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure. The inverse operator is given by the following expression,
+The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure.
+Expressed in the matrix-vector notation, inverse operator is given by,
 %
@@
 %
-Providing the explicit derivation here will be redundant with that described in the previous sections and hence we avoid that.
-The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
+%The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
+%%
+%\beq
+%\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
+%\eeq
+%%
+The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation,
 %
 \beq
-\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
-\eeq
-%
-
- The inverse operator is given by the following expression,
-%
-\beq
-{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{eq}) & -\sin(2\alpha_{eq})\\  \sin(2 \alpha_{eq})  & \cos(2 \alpha_{eq}) \emat \,.
+{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
 \eeq
@@
 where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb} by a change in sign on the off-diagonals of the block matrix and the pixel indexing is reversed $ e \leftrightarrow q$.
-We can evaluate the Stokes parameters  $Q$ \& $U$ from the scalar fields $E$ \& $B$ by evaluating the following expression,
+Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb_rad} by a change in sign on the off-diagonals of the block matrix.
+When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by,
 %
-\beq \label{eq:eb2qu_convolution_explicit}
-\bmat Q_i \\ U_i  \emat=-\Delta \Omega\sum_{j=1}^{N_{\rm pix}} {{}_{\mm}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{ij}) & -\sin(2\alpha_{ij})\\  \sin(2 \alpha_{ij})  & \cos(2 \alpha_{ij}) \emat  \bmat E_j \\ B_j  \emat \,,
-\eeq
+\beqry
+{}_{+2}X(\hat{n}_q) &=& \Bigg\lbrace \mathcal{M}^*_{G} \circ [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} \textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}\\
+{}_{+2}X(\hat{n}_q) &=&  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e}) \cdot  \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} \textrm{\emph{Radiation kernel}}\,,
+\eeqry
 %
-where all the symbols have their usual meaning. The above equation can again be expressed more concisely as follows,
-%
-\begin{subequations} \label{eq:eb2qu_simple}
-\beqry 
-{}_{+2}\bar{X}(\hat{n}_0) &=& - \Delta \Omega \sum_{j=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}  P_{\ell}^{2}(\beta_{0j}) \right)  {\Bigg( e^{i2 \alpha_{0j}}   [E+iB](\hat{n}_j) \Bigg)} \,, \label{eq:eb2qu_physical}\\
-&=& - \Bigg\lbrace \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2} \right]  \circ [E+iB]  \Bigg\rbrace (\hat{n}_0) \,, \\
-&=& - \Bigg\lbrace \mathcal{M} \circ [E + iB] \Bigg\rbrace(\hat{n}_0)\,, 
-\eeqry
-\end{subequations}
-%
-which $\circ$ is to be interpreted as a convolution.
-The only change in the convolution kernel as compared to that in \eq{eq:qu2eb_simple} is that the $Y_{\ell 2}$ functions are not conjugated.
-This can again be simply understood as the construction of a spin-2 field by taking a product of a spin-0 field $[E +iB]$ with a spin $+2$ field $e^{+i2\alpha}$.
-The radial dependence of the operator ${\bar O}^{-1}$  is identical to the that of ${\bar O}$ as one may have expected.
-From the perspective of the scalar field $[E + iB]$, all the coordinate dependence of the Stokes parameters is encoded in the function $e^{+i2\alpha}$.
-The radial functions again have to vanish at $\beta \rightarrow 0,\pi$ for the same reasons that the function $e^{+i2\alpha}$ is ill defined at these locations.
+where all the symbols have the same meaning as defined in \sec{sec:qu2eb}.
+Note that the conjugated forms of the Green's function and the effective beam for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
 %--------------------------------------------------------
+
 %--------------------------------------------------------

### 2018-04-05 articles/formalism/sections/real_space_formalism.tex
Edits to sec3.4 still has some holes and needs some refining

@@
 \beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \,,\\
+\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm 0.5 \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \,,\\
 \eeq
@@
 \beqry
-\mathcal{I} &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,, \\
-\mathcal{D}  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_i) {_{-2}Y}^*_{\ell m}(\hat n_j) \,.
+\mathcal{I} (\hat{n}_e,\hat{n}_q) &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_e) {_{-2}Y}^*_{\ell m}(\hat n_q) \,, \\
+\mathcal{D}(\hat{n}_e,\hat{n}_q)  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_e) {_{-2}Y}^*_{\ell m}(\hat n_q) \,.
 \eeqry
@@
 \beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{i2 \gamma_{ij}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{ij} +  2\gamma_{ij}) + i \sin(2 \alpha_{ij} +  2 \gamma_{ij}) \Big]   {{}_{\mi}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{I}(\hat{n}_e, \hat{n}_q) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{qe}, \alpha_{qe}) ~ \rm{e}^{i2 \gamma_{qe}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
+\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{qe} +  2\gamma_{qe}) + i \sin(2 \alpha_{qe} +  2 \gamma_{qe}) \Big]   {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_i, \hat{n}_j) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{ij}, \alpha_{ij}) ~ \rm{e}^{- i2 \gamma_{ij}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{ij} - 2\gamma_{ij}) + i \sin(2 \alpha_{ij} -  2 \gamma_{ij}) \Big]   {{}_{\md}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \,,
+\mathcal{D}(\hat{n}_q, \hat{n}_e) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{qe}, \alpha_{qe}) ~ \rm{e}^{- i2 \gamma_{qe}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
+\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{qe} - 2\gamma_{qe}) + i \sin(2 \alpha_{qe} -  2 \gamma_{qe}) \Big]   {{}_{\md}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,,
 \eeqrys
@@
 \beqry \label{eq:op_qu2equbqu}
-\bmat Q_i \\ U_i  \emat_{E/B} &=& \sum_{j=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} + 2\gamma_{ij}) & \sin(2\alpha_{ij} +2 \gamma_{ij}) \\  -\sin(2\alpha_{ij} +2 \gamma_{ij})  & \cos(2 \alpha_{ij} + 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat  \\ &\pm& {}_{\md}f(\beta_{ij},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{ij} - 2\gamma_{ij}) &  \sin(2\alpha_{ij} - 2 \gamma_{ij}) \\  \sin(2\alpha_{ij} - 2 \gamma_{ij})  & - \cos(2 \alpha_{ij} - 2 \gamma_{ij}) \emat  \bmat Q_j \\ U_j  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
+\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
 \eeqry
@@
 %
-\begin{subequations}
 \beqry
-{}_{+2}X_{E/B} &=&0.5 \Delta \Omega\sum_{j=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{ij}) e^{-i2 (\alpha_{ij} + \gamma_{ij})} {}_{+2}X_j \pm {{}_{\md}f}(\beta_{ij}) e^{i2 (\alpha_{ij} - \gamma_{ij})} {}_{+2}X_j^*\,, \label{eq:qu2equbqu_explicit_convolution} \\
+{}_{+2}X_{E/B}(\hat{n}_e) &=&0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q) \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
 &=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
 \eeqry
-\end{subequations}
 %
-where in \eq{eq:qu2equbqu_explicit_convolution} we have suppressed the explicit multipole dependence of functions $_{\pm 2}f$ for brevity and in \eq{eq:qu2equbqu_convolution} $\circ$ denotes a convolution.
-\comment{Here it will be nice to interpret $e^{i2\gamma}[E-iB]$.
-We don't understand this as of now.}
+where we have suppressed the explicit multipole dependence of functions ${}_{\mdi}f$ for brevity. \revisit{Comment on the radiating and convolution form of the operators.}
 
 \comment{Recheck the math described below}
-The function $\mathcal{I}$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$).
+The operator $\mathcal{I}$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$) for spin-2 fields.
 When interpreted as a matrix it is a band limited version of the identity matrix.
-Though it has non vanishing off diagonal elements ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
+Though it has non-vanishing off diagonal elements ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
 Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
@@
 which are the real space analogues of \eq{eq:har_op_prop}.
-While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly canceling each other.
+While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly cancel each other.
 

### 2018-04-06 articles/formalism/sections/generalizedeb.tex
added a section relating the spin raising/lowering operators to real space operators

@@
 \section{Generalized operators}
-The azimuthal of the convolution kernel $\mathcal{M}$ could have been been argued to have the form $e^{-i2 \alpha}$ by requiring to construct a spin-0 field given some spin-2 fields.
-In this sense there is no freedom in the choice of the azimuthal dependence of the convolution kernels.
-The radial part of this kernel however is determined by the basis functions.
-It is possible to generalize these convolution kernels by choosing alternate forms for the radial functions, without affecting the parity properties of the scalar fields $E$ \& $B$.
+In this section we present a systematic method to generalize the real space operators that translate been $Q/U$ and $E/B$ description of CMB polarization.
+The azimuthal part of the real space kernels is constrained to be of the form $e^{-i2 \alpha}$.
+The shape of the radial part of the operator is determined by the basis functions and varies as a function of the multipoles included in the summation.
+It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
 
-We can characterize different forms of the radial kernel by introducing the following harmonic space operator,
+We can systematically generalize the real space operator by introducing the following harmonic space operator,
 %
@@
 To simplify the discussion and without loosing generality we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
-Once we have made a choice for these harmonic functions, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
+Once we have made a choice for this harmonic function, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
 %
@@
 where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
-Note that for an arbitrary choice of $\tilde{\mathcal{G}}$ only one of the operators in \eq{eq:gen_qu2eb} is well defined, since $\tilde{\mathcal{G}}^{-1}$ may be ill defined.
 If we require both the forward and inverse operators to be well defined, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that it has a valid  inverse.
 As we will see this will be an important criteria to recover the standard CMB spectra.
-The radial part of these generalized convolution kernels is given by the following expressions,
+The radial parts of this generalized operator and its inverse are given by the following expressions,
 %
@@
 %
-where $g_{\ell}$ are the same multipole function as those appearing in $\tilde{\mathcal{G}}$.
+where $g_{\ell}$ is the harmonic space function used in defining $\tilde{\mathcal{G}}$.
 Given this general definition for the radial function $G(\beta)$, note that the default radial function ${{}_{\mm}f}$ is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$).
@@
 %
-To ensure that the resultant field is a spin-0 field, it is important to note that the radial function $G(\beta)$ has to be necessarily chosen such that it vanishes at $\beta=0$ and $\beta=\pi$. 
+Here it is important to note that the radial function $G(\beta)$ has to be necessarily chosen such that it vanishes at $\beta=0$ and $\beta=\pi$ in order to ensure that the resultant field has the required spin properties.
 %One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
@@
 
-An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B mode fields being convolved with some circularly symmetric instrument beam. 
-Note that in contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-We clarify that the $B(\beta)$ refers to the effective beam acting to smooth the scalar $E$ \& $B$ mode maps.
-A circularly symmetric beam $B(\beta)$ defined at the pole can be expressed in the Legendre polynomial $P_{\ell}^0$ basis as follows,
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B mode fields being convolved with some effective circularly symmetric instrument beam.
+The radial profile of this effective beam is given by,
 %
 \beq
-B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} b_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
+B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,.
 \eeq
 %
-where $b_{\ell}$ denote the coefficients of expansion.
-\comment{Note that one can directly get E and B mode maps resulting from convolution with a non-circular beam by chosing the function $g_{\ell}$ to have some m dependence.}
+Note that in contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has important differences, in harmonic space they play identical roles.
 %
@@
 
-Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has important differences, in harmonic space they play identical roles.
  Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
@@
 
+\subsection{Relation to the spin raising$(\eth^2)$/lowering$(\bar{\eth}^2)$ operations}
+Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of the E/B mode maps as in \eq{eq:ebdef}.
+Now note that we can construct similarly filtered $E/B$ mode maps by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+It can be shown that real space operator takes the following form,
+%
+\beq
+[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
+\eeq
+%
+Therefore the band limited version of the spin lowering operations is given by,
+%
+\beq
+\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}
+\eeq
+%
+The band limited version of the spin raising operations is given by merely by the conjugate $(\bar{\eth}^2)^*$.
 \subsection{Recovering the default $E$ and $B$ mode spectra}

### 2018-04-07 articles/formalism/sections/real_space_formalism.tex
Kevin revisions in section 2

@@
 \section{Polarization primer}\label{sec:pol-primer}
-The CMB polarization is measured in terms of Stokes Q and U parameters.
-The Stokes Q is defined as the linear polarization measured along local cartesian axes ($+$ along the x-axis and $-$ along the y-axis) while Stokes U is defined as the linear polarization measured along the cartesian axes rotated by $45^{\circ}$ ($+$ along x-axis and $-$ along the y-axis in the counter-clockwise rotated system).
-Clearly the definitions of Stokes parameters depend on the choice of the coordinate system and it can be shown that the measurement made in two different coordinate systems rotated by an angle $\phi$ are related by the following equation,
+The CMB polarization is measured in terms of Stokes $Q$ and $U$ parameters.
+Stokes $Q$ is defined as the linear polarization measured along local cartesian axes ($+$ along the $x$-axis and $-$ along the $y$-axis) while Stokes $U$ is defined as the linear polarization measured along the cartesian axes rotated by $45^{\circ}$ ($+$ along x-axis and $-$ along the y-axis in the counter-clockwise rotated system).
+The Stokes parameters depend on the choice of the coordinate system and two different coordinate systems rotated by an angle $\psi$ relate as
 %
 \beq \label{eq:qu-rot}
-\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,,
+\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,.
 \eeq
 %
-which one can simply checked by verifying that $Q' \rightarrow U$ and $U' \rightarrow -Q$ when the coordinate systems are rotated by $45^\circ$ in the counter-clockwise sense.
+%which one can simply checked by verifying that $Q' \rightarrow U$ and $U' \rightarrow -Q$ when the coordinate systems are rotated by $45^\circ$ in the counter-clockwise sense.
 
-Following the notation of \cite{Zaldarriaga1997}, fields which transform as,
+Following the notation of \cite{Zaldarriaga1997}, fields which transform as
 %
-\beq
-{}_{s}f' = e^{-is\psi} {}_{s}f \,,
-\eeq
+%\beq
+${}_{s}f' = e^{-is\psi} {}_{s}f $
+%\eeq
 %
-under right handed rotations of the local coordinate system are termed spin-s fields. The Stokes parameters can be combined to define the complex fields,
+under right handed rotations of the local coordinate system are termed spin-$s$ fields. The Stokes parameters can be combined to define the complex fields,
 %
@@
 which under rotation of the local tangent plane coordinate system by an angle $\psi$ at any point on the sphere transform as: $_{\pm 2}X' = e^{\mp i2\psi} {_{\pm 2}X}$, which follows directly from \eq{eq:qu-rot}.
-Therefore the quantities $_{\pm2}X$ are spin${\pm2}$ fields respectively.
+Therefore the quantities $_{\pm2}X$ are spin ${\pm2}$ fields respectively.
 
-The Stokes parameters being coordinate dependent quantities it is inconvenient to work with them.
-It is possible to define spin raising ($\eth$) operator on the sphere which when operated on a field of spin-s $_{s}f$ results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$ and similarly one can define a spin lowering $(\bar{\eth})$ operators such that $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$\cite{goldberg67}.
-One can now construct a complex spin-0 scalar by applying the spin raising and lowering operators on the spin-2 fields ${_{\pm 2}X}$ as follows,
+The coordinate dependence of Stokes parameters make them inconvenient to work with.
+With operations that raise (or lower) the spin of the field, we can produce a spin-0 scalar that is coordinate independent.
+The spin-raising operator ($\eth$), when operated on a field of spin-s $_{s}f$, results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
+The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
 %
@@
 \mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\\
-\mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,,
+\mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,.
 \eeqry
@@
 %
-which by the virtue of being scalars are independent of coordinate definitions.
+%which by the virtue of being scalars are independent of coordinate definitions.
 %The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
@@
 The complex field $_{\pm 2}X$ defined on the sphere can be decomposed in spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
-On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities\cite{goldberg67},
+On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67},
 %
@@
 
-Using \eq{eq:ebdef}, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
+Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
 %
@@
 %
-Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $\sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
+Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
-In this section we cast the relations introduced in Sec.~\ref{sec:pol-primer} in matrix notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
-This representation will make transparent the derivation of the real space operators we discuss in the following sections.
-We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.
 
-We begin by introducing the matrices encoding the spin spherical harmonic basis vectors,
+Our derivation of real space operators is more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
+We introduce a matrix that encodes spin spherical harmonic basis vectors,
 %
 \beq
-{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,,
+{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,%,
 \eeq
 %
-where $s$ denotes the spin of the basis functions.
-For this work we will be working with cases $s \in [0,2]$.
-In this notation, each column can be mapped to a specific harmonic basis function marked by the pair of indices: $(\ell,m)$ and each row maps to a specific position on the sphere.
-Note that this matrix is in general not a square matrix.
-The number of rows is determined by the scheme used to discretely represent the sphere and the number of columns is set by the number of basis functions of interest (often determined by the band limit).
+%where $s$ denotes the spin of the basis functions.
+We will be working with cases $s \in [0,2]$.
+Each column maps to a specific harmonic basis function (i.e.
+indexed by $\ell m$) and each row maps to a pixel on the sphere.
+This matrix is not square in general: the number of rows is determined by the pixelization and the number of columns is set by the number of basis functions (e.g.
+determined by the band limit).
 
-We now define the different polarization data vectors and their representation in real and harmonic space as follows,
+We now define the different polarization data vectors and their representation in real  space as and harmonic as follows,\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}
 %
@@
 %
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript $_{\ell m}$ for the spherical harmonic coefficients of expansion is suppressed in favor of cleaner notation.
+The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript ${\ell m}$ for the spherical harmonic coefficients is suppressed for cleaner notation.
 
-Next we define the operators which govern the transformations between different representations of the polarization field as follows,
+We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$):
 %
@@
 %
-where we have chosen the sign conventions so as to match those used in Healpix.
+The sign conventions we have chosen match HEALPix.
 Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
@@
 \begin{subequations} \label{eq:pol_data_relns}
+  %Kevin's version
   \beqry
-\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
-\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
+  \bar{X} &= \bar T  \bar{P}; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} ; \\
+  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
+  \eeqry
+  Meanwhile the spherical harmonic transforms are written as:
+  \beqry
+  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\dagger}  \bar X  ; \\
+  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} \bar S \,.
+  \eeqry
+% Aditya's version
+%\beqry
+%\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
+%\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
+%\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
+%\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
 %\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
@@
 %\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
+%\eeqry
+\end{subequations}
+%
+Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace,
+%
+\begin{subequations} \label{eq:har_eb_op}
+\beqry
+\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E  \tilde S ,\\
+\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B  \tilde S .
 \eeqry
@@
 %
-Finally we introduce the harmonic space operators, which project the harmonic space data vector to E or B subspace,
+Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
 %
-\begin{subequations} \label{eq:har_eb_op}
-\beqry
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E* \tilde S \,,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B *\tilde S \,
-\eeqry
-\end{subequations}
+%\begin{subequations} \label{eq:har_op_prop}
+%\beqry
+%\tilde O_E  \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B  \tilde O_B= \tilde O_B \,,\\
+% \tilde O_E  \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
+% \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
+%\eeqry
+%\end{subequations}
 %
-Note that these harmonic space matrices are idempotent, orthogonal to each other and their sum is an identity matrix as can be explicitly seen via the following relations, 
-%
-\begin{subequations} \label{eq:har_op_prop}
-\beqry
-\tilde O_E * \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B * \tilde O_B= \tilde O_B \,,\\
- \tilde O_E * \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
- \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-\eeqry
-\end{subequations}
-%
-Note that the above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues of these harmonic space operators.
+The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-04-11 articles/formalism/sections/real_space_formalism.tex
moved the matrix notation later.

@@
 %--------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Real space operators} \label{sec:real_space_operators}
+The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization.
+In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
+This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics.
+All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
+Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
+%
+\begin{figure}[!hbt]
+\centering
+\includegraphics[width=0.5\columnwidth]{euler.pdf}
+\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
+The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
+\label{fig:euler_angles}
+\end{figure}
+%
+
+\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east as shown in \fig{fig:euler_angles}.
+The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_q \equiv (\theta_q,\phi_q)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_e \equiv (\theta_e,\phi_e)$ \cite{varshalovich}.
+
+For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}.
+In the z-y1-z2 convention, $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
+These angles can be understood as follows: The rotation by $\alpha$ about the original z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_q$ along the great circle in the direction \revisit{of shortest arc length} towards $\hat{n}_e$.
+The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_q$ to location $\hat{n}_e$, such that the z-axes of the two coordinate systems are parallel to each other.
+Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_e$.
+The different Euler angles and the corresponding rotations are schematically represented in \fig{fig:euler_angles}.
+
+The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_q=(\theta_q,\phi_q)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_e,\theta_e,0)$ will align the cartesian system at $\hat{n}_q$ with that defined at position $\hat{n}_e$.
+%--------------------------------------------------------
+
+%--------------------------------------------------------
+\subsection{A heuristic argument for constructing  $E/B$ modes from Stokes parameters $Q/U$ on the sphere} \label{sec:qu2eb_heuristic}
+The primary aim here is to make intuitive the construction of the spin-0 $E/B$ modes of polarization from the Stokes parameters.
+We present heuristic arguments which allows us to derive the important features of the real space kernels\footnote{These heuristic arguments were developed in hindsight but are very instructive.}.
+
+If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes charge in the new coordinate system is related to the Stokes charge in the original coordinate system as: ${}_{+2}X'(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
+Similarly if the local planar axes are rotated by an angle $\phi$ then the Euler angle $\alpha_{qe}$ (recall that this Euler angle aligns the x-axis at $\hat{n}_q$ in the direction of the shortest path along the geodesic to the location $\hat{n}_e$) for the new coordinate system is given by: $\alpha'_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.
+The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
+Given these transformation properties note that: ${}_{+2}X'(\hat{n}_q)e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence by definition must form a spin-0 field.
+Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
+Therefore we can make the association: $E'+iB' \propto {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$
+
+Now note that when the two locations coincide $\hat{n}_q = \hat{n}_e$ then  $\alpha_{qe}=0,2\pi,4\pi,\cdots$ implying $E + iB \propto Q+iU$, which is a fallacy as we know that $Q+iU$ does not transform as a spin-0 field under local rotations.
+One runs into a similar fallacy when the two locations are diametrically opposite.
+Therefore to have a consistent definition of a spin-0 field constructed from a spin-2 field we require the kernel to have the form: $E'+iB' = {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}$, where the function $f(\beta_{qe})$ is such that it vanishes when the two locations are coincident$(\beta_{qe}=0)$ or diametrically opposite$(\beta_{qe}=\pi)$.
+Hence the $E/B$ fields are necessarily non-local.
+Note that this construction can be generalized to transform fields of arbitrary spin to a field of any other spin, one obvious case being constructing the Stokes field given the $E/B$ maps (i.e.
+deriving spin-2 fields from spin-0 fields.)
+
+The azimuthal part which depends only on the Euler angle $\alpha_{qe}$, has no multipole $\ell$ dependence and is the crucial operation which translates between the different spin representation of CMB polarization.
+Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation $|\beta_{qe}|$ between different locations on the sphere and hence must completely incorporate the multipole $\ell$ dependence of the kernel.
+These heuristic arguments cannot take us any further and we now shift to presenting a mathematically rigorous derivation of the real space operators in the following sections.
+%--------------------------------------------------------
+
+%--------------------------------------------------------
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
@@
 The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization.
-In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
-This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics.
-All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.5\columnwidth]{euler.pdf}
-\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
-The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
-The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
-\label{fig:euler_angles}
-\end{figure}
-%
 
-\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east as shown in \fig{fig:euler_angles}.
-The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_q \equiv (\theta_q,\phi_q)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_e \equiv (\theta_e,\phi_e)$ \cite{varshalovich}.
-
-For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}.
-In the z-y1-z2 convention, $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-These angles can be understood as follows: The rotation by $\alpha$ about the original z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_q$ along the great circle in the direction \revisit{of shortest arc length} towards $\hat{n}_e$.
-The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_q$ to location $\hat{n}_e$, such that the z-axes of the two coordinate systems are parallel to each other.
-Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_e$.
-The different Euler angles and the corresponding rotations are schematically represented in \fig{fig:euler_angles}.
-
-The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_q=(\theta_q,\phi_q)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_e,\theta_e,0)$ will align the cartesian system at $\hat{n}_q$ with that defined at position $\hat{n}_e$.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{A heuristic argument for constructing  $E/B$ modes from Stokes parameters $Q/U$ on the sphere} \label{sec:qu2eb_heuristic}
-The primary aim here is to make intuitive the construction of the spin-0 $E/B$ modes of polarization from the Stokes parameters.
-We present heuristic arguments which allows us to derive the important features of the real space kernels\footnote{These heuristic arguments were developed in hindsight but are very instructive.}.
-
-If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes charge in the new coordinate system is related to the Stokes charge in the original coordinate system as: ${}_{+2}X'(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
-Similarly if the local planar axes are rotated by an angle $\phi$ then the Euler angle $\alpha_{qe}$ (recall that this Euler angle aligns the x-axis at $\hat{n}_q$ in the direction of the shortest path along the geodesic to the location $\hat{n}_e$) for the new coordinate system is given by: $\alpha'_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.
-The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
-Given these transformation properties note that: ${}_{+2}X'(\hat{n}_q)e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence by definition must form a spin-0 field.
-Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
-Therefore we can make the association: $E'+iB' \propto {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$
-
-Now note that when the two locations coincide $\hat{n}_q = \hat{n}_e$ then  $\alpha_{qe}=0,2\pi,4\pi,\cdots$ implying $E + iB \propto Q+iU$, which is a fallacy as we know that $Q+iU$ does not transform as a spin-0 field under local rotations.
-One runs into a similar fallacy when the two locations are diametrically opposite.
-Therefore to have a consistent definition of a spin-0 field constructed from a spin-2 field we require the kernel to have the form: $E'+iB' = {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}$, where the function $f(\beta_{qe})$ is such that it vanishes when the two locations are coincident$(\beta_{qe}=0)$ or diametrically opposite$(\beta_{qe}=\pi)$.
-Hence the $E/B$ fields are necessarily non-local.
-Note that this construction can be generalized to transform fields of arbitrary spin to a field of any other spin, one obvious case being constructing the Stokes field given the $E/B$ maps (i.e.
-deriving spin-2 fields from spin-0 fields.)
-
-The azimuthal part which depends only on the Euler angle $\alpha_{qe}$, has no multipole $\ell$ dependence and is the crucial operation which translates between the different spin representation of CMB polarization.
-Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation $|\beta_{qe}|$ between different locations on the sphere and hence must completely incorporate the multipole $\ell$ dependence of the kernel.
-These heuristic arguments cannot take us any further and we now shift to presenting a mathematically rigorous derivation of the real space operators in the following sections.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
 \subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}

### 2018-04-11 articles/formalism/sections/real_space_formalism.tex
Drafted alternative section for bringing heuristic argument earlier.

@@
+\section{Real space polarization operators}
+\textit{Alternative for bringing the heuristic argument earlier.}
+
+ CMB polarization is measured in terms of Stokes parameters, averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.
+(Throughout we use the conventions of HEALPix \cite{healpix_primer}.) Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system and a rotation by an angle $\psi$ around the line of sight transforms them as
+%
+\beq \label{eq:qu-rot}
+\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,.
+\eeq
+Because the combination $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$, the Stokes parameters are components of a spin-2 field \cite{Zaldarriaga1997}.
+
+The standard construction of $E/B$ fields arise from the desire to have a coordinate independent description of the polarization and follow from operations that raise (or lower) the spin of the $X$ field to construct scalar fields.
+But from the transform properties of the Stokes parameters, we can already make a heuristic argument for what these operations must look like in real space.
+
+We consider the contribution from the polarization field (evaluated at $\hat n_q$) to a scalar field (evaluated at $\hat n_e$).
+Figure \ref{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$, and a rotation around $\hat n_q$ by $-\gamma$.
+This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}.
+%
+\begin{figure}%[!hbt]
+\centering
+\includegraphics[width=0.5\columnwidth]{euler.pdf}
+\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
+The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
+\label{fig:euler_angles}
+\end{figure}
+%
+
+Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
+$\mathcal{R}_{\hat{z}_q}(\phi)[{}_{+2}X(\hat{n}_q)] =  {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
+This same rotation by $\phi$ alters the Euler angle $\alpha_{qe}$ (that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$): $\mathcal{R}_{\hat{z}_q}(\phi)[\alpha_{qe}] = \alpha_{qe} - \phi$.
+Therefore one can see that $\mathcal{R}_{\hat{z}_q}(\phi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\phi}$.
+
+Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}$ is invariant under rotations and must by definition be spin-0:
+\beq
+\mathcal{R}_{\hat{z}_q}(\phi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}
+\eeq
+Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
+Therefore we can make the association that contributions to  $(E+iB)(\hat n_e)$ must be proportional to $ {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$.
+
+The same rotation $\mathcal{R}_{\hat{z}_q}(\phi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
+Thus we can conclude that the form of the real-space operation must be like:
+\beq
+(E+iB)(\hat n_e) = \int d\hat n_q \  {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}
+\eeq
+Note that when the two locations coincide ($\beta_{qe}=0$) then  $\alpha_{qe}=0,2\pi,4\pi,\dots$, implying $E + iB \propto Q+iU$.
+This cannot be because $Q+iU$ does not transform as a spin-0 field under local rotations.
+A similar fallacy arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$.
+Therefore we must have function $f(\beta_{qe} = 0 ) = f(\beta_{qe} = \pi ) = 0$.
+Hence the $E/B$ fields are necessarily non-local.
+Any such function $f$ will give us $E/B$-like scalar fields.
+Below we derive the particular one that gives rise to our familiar $E/B$ modes.
+
+The kernel's azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so it's harmonic transform has no multipole $\ell$ dependence.
+The azimuthal part is the crucial operation that translates between different spin representation of CMB polarization.
+Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation between locations and hence must completely incorporate the multipole $\ell$ dependence.
+
+Note that this type of construction can be generalized to transform fields of arbitrary spin to a field of any other spin, and so we can use it in the opposite sense to transform $E/B$ maps back to the Stokes parameters (i.e.
+transforming spin-0 fields to spin-2.)
+
+The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
+The spin-raising operator ($\eth$), when operated on a field of spin-s $_{s}f$, results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
+The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
+%
+\begin{subequations}\label{eq:ebdef}
+\beqry
+\mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\\
+\mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,.
+\eeqry
+\end{subequations}
+%
+%which by the virtue of being scalars are independent of coordinate definitions.
+%The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
+
+The complex field $_{\pm 2}X$ defined on the sphere can be decomposed in spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67},
+%
+\begin{subequations}\label{eq:spinopylm} 
+\beqry
+\eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
+\bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
+\eeqry
+\end{subequations}
+%
+where $_s Y_{lm}(\hat{n}) $ denote the spin-s spherical harmonics.
+
+Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
+%
+\beq \label{eq:pseudo}
+\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
+\eeq
+%
+where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
+%
+\beq\label{eq:x2eb}
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
+\eeq
+%
+In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
+%
+\beq \label{eq:realeb}
+E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
+\eeq
+%
+Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$.
+%We make this choice since the CMB spectra are more closely related to the fields E \& B.
+
 %--------------------------------------------------------

### 2018-04-27 articles/formalism/sections/kernel_discussion.tex
added a section relating the spin raising/lowering operators to real space operators
generated a proper sign version of the codes, generated the convolution kernel plots and added them to the pape. the kernel plots are updated to have the proper sign.

@@
 \centering
-%\captionsetup[subfigure]{labelformat=empty}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat90_lon45.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon45.pdf}}\\[-2ex]
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat87_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat87_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat87_lon30.pdf}}\\[-2ex]
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat80_lon30.pdf}}\\[-2ex]
-\subfigure[$\mathcal{M}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{M}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2eb_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{D}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/qu2ebqu_ker_i_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_r$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_r_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\mathcal{I}_i$]{\includegraphics[width=0.16\columnwidth]{kernel/I_ker_i_lat0_lon90.pdf}}
+\captionsetup[subfigure]{labelformat=empty}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf}}\hspace{-2mm}
+
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf}}\hspace{-2mm}
+
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf}}\hspace{-2mm}
+\subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Img} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Img} \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Img} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Img} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
 \caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
@@
 %
-\begin{figure}[!hbt]
+\begin{figure}[t]
 \centering
@@
 We compute the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ by evaluating the respective multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.
-
-Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa.
-Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$.
-The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars.
-Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in.
-${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}.
-${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.
-
-\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions.
-We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis.
-To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
 %
@@
 %
+Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa.
+Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$.
+The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars.
+Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in.
+${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}.
+${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.
+
+\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions.
+We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis.
+To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
+
 The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity.

### 2018-04-27 codes/modules/aliasing_correction.py

@@ -1,73 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Convolution method to convolve with a band limited delta function
-def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
-	fn_rad_ker_i=interp1d(np.cos(theta)[::-1],rad_ker_i[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	hq=np.zeros(npix,"double")
-	hu=np.zeros(npix,"double")
-	
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
-
-		
-	for i in pix_list:
-		cosbeta,c2apg,s2apg,spix=euler.fn_euler_trig2_alpha_plus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
-		gbeta=fn_rad_ker_i(cosbeta)
-		Ir=c2apg*gbeta
-		Ii=s2apg*gbeta
-
-		hq[i]=(np.dot(Ir,q[spix]) + np.dot(-Ii,u[spix]))*domega
-		hu[i]=(np.dot(Ii,q[spix]) + np.dot( Ir,u[spix]))*domega
-
-	return hq,hu
-
-def correct_aliasing_convolve(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
-	npix=np.size(tq)
-	cq=np.zeros(npix,"double") ; cu=np.zeros(npix,"double")	
-	for i in range(iter):
-		hq,hu=delta_convolve(tq-cq,tu-cu,theta_cutoff,theta,rad_ker_i,mask)
-		cq=cq + (hq-tq) ; cu=cu + (hu-tu)
-
-	return [np.zeros(npix),tq-cq,tu-cu]
-
-# Radiation method to convolve with a band limited delta function
-def delta_radiate(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
[…]

### 2018-04-27 codes/modules/backup_working_codes/aliasing_correction.py

@@ -1,93 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
-	'''
-	This Euler angles function works for the qu2_equ_bqu function.
-	The set of function here, match Healpix results to numerical accuracy.
-	'''
-	theta1,phi1=h.pix2ang(nside,cpix)
-	v=h.pix2vec(nside,cpix)
-	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
-	theta2,phi2=h.pix2ang(nside,spix)
-
-	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
-	beta=np.arccos(cosbeta)
-
-	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-
-    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
-    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
-
-	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
-    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
-
-	return beta,alpha,gamma,spix
-
-def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
-	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	hq=np.zeros(npix,"double")
-	hu=np.zeros(npix,"double")
-	
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
-
-		
-	for i in pix_list:
[…]

### 2018-04-27 codes/modules/backup_working_codes/calc_spinylm.py

@@ -1,52 +1,0 @@
-import numpy as np
-from scipy.special import lpmn as lpmn
-import healpy as h
-
-from sympy.physics.quantum.spin import Rotation
-from sympy import N
-
-def wigd_sylm(l,m,theta,phi,s=2):
-    '''Uses the Wigner D implementation in sympy.physics.quantum.spin to compute the spin spherical harmonic functions. Its very slow and is meant to be used only for testing purposes.'''
-    f=Rotation.D(l,-m,s,phi,theta,0.)
-    res=N(f.doit()*np.sqrt((2.*l+1.)/(4.*np.pi))*((-1.)**m))
-    return res
-
-def calc_factorial_log(x):
-    '''Uses the Stirling approximation to calculate the natural log of the factorial'''
-    if x==0.:
-        logxf=0.
-    else:
-        logxf=x*np.log(x)-x + 0.5*np.log(2.*np.pi*x) + np.log(1. +  (1./(12.*x)) + (1./(288.*x*x)) - (139./(51840.*x*x*x)) - (571./(2488320.*x*x*x*x)))
-    return logxf
-
-def spin0_nlm(l,m):
-    '''Returns sqrt((2l+1)/(4*pi))*sqrt((l-m)!/(l+m)!)'''
-    y=0.5*(calc_factorial_log(l-m) - calc_factorial_log(l+m))
-    return np.sqrt((2.*l+1.)/(4.*np.pi))*np.exp(y)
-
-def spin2_nlm(l,m):
-    '''Returns 2*sqrt((2l+1)/(4*pi))*sqrt(((l-m)!/(l+m)!)*((l-2)!/(l+2)!))'''
-    y=0.5*(calc_factorial_log(l-m) - calc_factorial_log(l+m) + calc_factorial_log(l-2) - calc_factorial_log(l+2))
-    return 2.*np.sqrt((2.*l+1.)/(4.*np.pi))*np.exp(y)
-
-def return_plm(lmax,mmax,csth):	
-	plm,dplm=lpmn(mmax,lmax,csth)
-	return plm
-
-def return_ylm(l,m,csth,phi,plm):
-	ylm=spin0_nlm(l,m)*plm[m,l]*complex(np.cos(m*phi),np.sin(m*phi))
-	return ylm
-
-def return_p2ylm(l,m,csth,phi,plm):
[…]

### 2018-04-27 codes/modules/backup_working_codes/convert_eb2qu.py

@@ -1,102 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Integrating method to generate E and B mode maps.
-def convert_eb2qu_integrate(e,b,theta_cutoff,theta,rad_ker):
-	'''
-	   This function uses E and B maps in regions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-	q=np.zeros(npix,"double")
-	u=np.zeros(npix,"double")
-	for i in range(npix):
-		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_s2euler_alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
-		gbeta=fn_rad_ker(cosbeta)
-		cafb=cos2alpha*gbeta ; safb=sin2alpha*gbeta
-		q[i] = (np.dot(-cafb,e[spix]) + np.dot(-safb,b[spix]))*domega
-		u[i] = (np.dot( safb,e[spix]) + np.dot(-cafb,b[spix]))*domega
-	return [np.zeros(npix),q,u]
-
-
-def convert_eb2qu_integrate_masked(e,b,theta_cutoff,theta,rad_ker,mask=[]):
-	'''
-	   This function uses E and B maps in reggions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
[…]

### 2018-04-27 codes/modules/backup_working_codes/convert_qu2_equ_bqu_new.py

@@ -1,99 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
-	'''
-	This Euler angles function works for the qu2_equ_bqu function.
-	The set of function here, match Healpix results to numerical accuracy.
-	'''
-	theta1,phi1=h.pix2ang(nside,cpix)
-	v=h.pix2vec(nside,cpix)
-	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
-	theta2,phi2=h.pix2ang(nside,spix)
-
-	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
-	beta=np.arccos(cosbeta)
-
-	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-
-    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
-    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
-
-	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
-    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
-
-	return beta,alpha,gamma,spix
-
-def convert_qu2_equ_bqu_integrate(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
-	'''Pass alias corrected TQU map to this routine.'''
-	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
-	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
-	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
[…]

### 2018-04-27 codes/modules/backup_working_codes/convert_qu2_equ_bqu_old.py

@@ -1,53 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
-	'''
-	This Euler angles function works for the qu2_equ_bqu function.
-	The set of function here, match Healpix results to numerical accuracy.
-	'''
-	theta1,phi1=h.pix2ang(nside,cpix)
-	v=h.pix2vec(nside,cpix)
-	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
-	theta2,phi2=h.pix2ang(nside,spix)
-
-	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
-	beta=np.arccos(cosbeta)
-
-	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-
-    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
-    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
-
-	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
-    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
-
-	return beta,alpha,gamma,spix
-
-def convert_qu2_equ_bqu(q,u,theta_cutoff,theta,rad_ker_i,rad_ker_d):
-	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	fn_rad_ker_d=interp1d(theta,rad_ker_d,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	equ=[np.zeros(npix,"double"),np.zeros(npix,"double")]
[…]

### 2018-04-27 codes/modules/backup_working_codes/convert_qu2eb.py

@@ -1,102 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Integrating method to generate E and B mode maps.
-def convert_qu2eb_integrate(q,u,theta_cutoff,theta,rad_ker):
-	'''
-	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-	e=np.zeros(npix,"double")
-	b=np.zeros(npix,"double")
-	for i in range(npix):
-		cosbeta,cos2gamma,sin2gamma,spix=euler.fn_s2euler_gamma(nside,i,theta_cutoff,inclusive=False,fact=4)
-		gbeta=fn_rad_ker(cosbeta)
-		cgfb=cos2gamma*gbeta ; sgfb=sin2gamma*gbeta
-		e[i] = (np.dot(-cgfb,q[spix]) + np.dot( sgfb,u[spix]))*domega
-		b[i] = (np.dot(-sgfb,q[spix]) + np.dot(-cgfb,u[spix]))*domega
-	return [np.zeros(npix),e,b]
-
-
-def convert_qu2eb_integrate_masked(q,u,theta_cutoff,theta,rad_ker,mask=[]):
-	'''
-	   This function uses Q and U maps in reggions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
[…]

### 2018-04-27 codes/modules/backup_working_codes/euler.py

@@ -1,134 +1,0 @@
-import numpy as np
-import healpy as h
-
-def return_euler_angles(theta1,phi1,theta2,phi2):
-	'''Returns the Euler angles for a pair of spherical coordinates'''
-	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-	beta=np.arccos(cosbeta)
-
-	na = np.sin(theta2)*np.sin(phi2-phi1)
-	da = -np.sin(theta1)*np.cos(theta2) + np.sin(theta2)*np.cos(theta1)*np.cos(phi2-phi1)
-    	alpha=np.arctan2(na,da)
-
-	ng = np.sin(theta1)*np.sin(phi2-phi1)
-	dg = np.sin(theta2)*np.cos(theta1) - np.sin(theta1)*np.cos(theta2)*np.cos(phi2-phi1)
-    	gamma=np.arctan2(ng,dg)
-
-	return alpha,beta,gamma
-
-
-def return_spix_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
-	'''Returns the pixel numbers and the respective Euler angles within a circle of radius discsize from the central pixel: cpix'''
-	theta0,phi0=h.pix2ang(nside,cpix)
-	v=h.pix2vec(nside,cpix)
-	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
-	spix=np.delete(spix,np.where(spix==cpix)[0][0])
-	theta1,phi1=h.pix2ang(nside,spix)
-
-	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1) 
-	beta=np.arccos(cosbeta)
-
-	n = np.sin(theta0)*np.sin(theta1)*np.sin(phi0-phi1)
-
-    	da = np.cos(theta0)*np.cos(beta) - np.cos(theta1)
-    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
-
-	dg = np.cos(theta1)*np.cos(beta) - np.cos(theta0)
-    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
-
[…]

### 2018-04-27 codes/modules/backup_working_codes/rs_rad_ker.py

@@ -1,127 +1,0 @@
-from scipy.special import lpmn as lpmn
-import numpy.polynomial.legendre as lgdr
-from scipy.interpolate import interp1d
-import scipy.integrate as intg
-import numpy as np
-import sys
-
-def mod_rad_ker(theta,shift=0.2,width=0.5,amp=1.,slope=2.,expslope=2.):
-	rad_ker=((amp*theta)**slope)*np.exp(-((theta-shift)/(np.sqrt(2.)*width))**expslope)
-	return rad_ker
-
-def fn_apodization(theta,theta_cutoff=np.pi/6.,apow_frac=0.2):
-	fnapo=np.zeros(theta.size,"double")
-	apow=apow_frac*theta_cutoff
-	# Cosine squared apodization.
-	x=(theta-(theta_cutoff-apow))*np.pi/(2.*apow)
-	fnapo=np.cos(x)**2.
-	fnapo[theta<=theta_cutoff-apow]=1.
-	fnapo[theta>theta_cutoff]=0.
-	return fnapo
-
-def get_plm0(lmax,sampling,theta_min=0.,theta_max=np.pi,m0=2,theta=np.zeros(0,"double")):
-	'''This is written to get the associated Legendre polynomials at a fixed m0. The default m0=2
-	When the array costheta is provided, the sampling parameter is ignored.
-	'''
-	if np.size(theta)==0:
-		theta=np.linspace(theta_min,theta_max,sampling)
-
-	csth=np.cos(theta)
-	pl2=np.zeros((lmax+1,np.size(csth)),"double")
-	for i in range(np.size(csth)):
-		plm,dplm=lpmn(m0,lmax,csth[i])
-		for l in range(lmax+1):
-			pl2[l,i]=plm[m0,l]
-	return theta,pl2
-
-# This is the default radial kernel.
-def calc_qu2eb_rad_ker(lmax,theta,pl2,lmin=2):
-	if lmax>np.size(pl2[:,0])-1:
-		#print "lmax given:",lmax
-		#print "Maximum multipole of Legendre polynomials:", np.size(pl2[:,0])-1
[…]

### 2018-04-27 codes/modules/convert_eb2qu.py

@@ -1,54 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Convolution method to generate E and B mode maps.
-def convert_eb2qu_integrate(e,b,theta_cutoff,theta,rad_ker,mask=[]):
-	'''
-	   This function uses E and B maps in reggions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
-
-	q=np.zeros(npix,"double")
-	u=np.zeros(npix,"double")
-	for i in pix_list:
-		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_euler_trig2alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
-		gbeta=fn_rad_ker(cosbeta)
-		c2afb=cos2alpha*gbeta ; s2afb=sin2alpha*gbeta
-		q[i] = (np.dot(-c2afb,e[spix]) + np.dot( s2afb,b[spix]))*domega
-		u[i] = (np.dot(-s2afb,e[spix]) + np.dot(-c2afb,b[spix]))*domega
-
-	return [np.zeros(npix),q,u]
-
-
-
-# Radiating method to generate Q and U mode maps.
-def convert_eb2qu_radiate(e,b,theta_cutoff,theta,rad_ker,mask=[]):
-	'''This function only uses E and B maps inside the mask provided. It computes Q and U maps in regions defined by the radial cutoff'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
[…]

### 2018-04-27 codes/modules/convert_qu2_equ_bqu.py

@@ -1,77 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Convolution method to separate Q U into Stokes parameters corresponding to E and B modes respectively
-def convert_qu2_equ_bqu_convolve(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
-	'''Pass alias corrected TQU map to this routine.'''
-	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
-	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
-	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
-	fn_rad_ker_d=interp1d(np.cos(theta)[::-1],rad_ker_d[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
-
-
-	dqu=[np.zeros(npix,"double"),np.zeros(npix,"double")]
-	
-	if np.size(cq)!=0 and np.size(cu)!=0:
-		for i in pix_list:
-			cosbeta,c2amg,s2amg,spix=euler.fn_euler_trig2_alpha_minus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
-			gbeta=fn_rad_ker_d(cosbeta)
-			Dr=c2amg*gbeta ; Di=s2amg*gbeta
-
-			dqu[0][i]=(np.dot(Dr,cq[spix]) + np.dot( Di,cu[spix]))*domega
-			dqu[1][i]=(np.dot(Di,cq[spix]) + np.dot(-Dr,cu[spix]))*domega
-	else:
-		for i in pix_list:
-			cosbeta,c2amg,s2amg,spix=euler.fn_euler_trig2_alpha_minus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
-			gbeta=fn_rad_ker_d(cosbeta)
[…]

### 2018-04-27 codes/modules/convert_qu2eb.py

@@ -1,53 +1,0 @@
-import healpy as h
-import numpy as np
-import euler as euler
-from scipy.interpolate import interp1d
-
-# Convolution method to generate E and B mode maps.
-def convert_qu2eb_convolve(q,u,theta_cutoff,theta,rad_ker,mask=[]):
-	'''
-	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
-	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
-	'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
-	if np.size(mask)==0:
-		pix_list=np.arange(npix)
-	else:
-		pix_list=np.nonzero(mask)[0]
-
-	e=np.zeros(npix,"double")
-	b=np.zeros(npix,"double")
-	for i in pix_list:
-		cosbeta,cos2gamma,sin2gamma,spix=euler.fn_euler_trig2gamma(nside,i,theta_cutoff,inclusive=False,fact=4)
-		gbeta=fn_rad_ker(cosbeta)
-		c2gfb=cos2gamma*gbeta ; s2gfb=sin2gamma*gbeta
-		e[i] = (np.dot(-c2gfb,q[spix]) + np.dot( s2gfb,u[spix]))*domega
-		b[i] = (np.dot(-s2gfb,q[spix]) + np.dot(-c2gfb,u[spix]))*domega
-	return [np.zeros(npix),e,b]
-
-
-
-# Radiating method to generate E and B mode maps.
-def convert_qu2eb_radiate(q,u,theta_cutoff,theta,rad_ker,mask=[]):
-	'''This function only uses Q and U maps inside the mask provided. It computes E and B maps in regions defined by the radial cutoff'''
-	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-
[…]

### 2018-04-27 codes/modules/euler.py

@@ -1,99 +1,0 @@
-import numpy as np
-import healpy as h
-
-def return_euler_angles(theta0,phi0,theta1,phi1):
-	'''Returns the Euler angles for a pair of spherical coordinates'''
-	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1) 
-	beta=np.arccos(cosbeta)
-
-	na = np.sin(theta0)*np.sin(theta1)*np.sin(phi1-phi0)
-	da = np.cos(theta0)*cosbeta - np.cos(theta1)
-    	alpha=np.arctan2(na,da)
-
-	ng = na
-	dg = np.cos(theta1)*cosbeta - np.cos(theta0)
-    	gamma=np.arctan2(ng,dg)
-
-	return alpha,beta,gamma
-
-def fn_euler_trig2alpha(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
-	'''Returns the pixel numbers and the respective functions of Euler angles within a circle of radius discsize from the central pixel: cpix'''
-	theta0,phi0=h.pix2ang(nside,cpix)
-	v=h.pix2vec(nside,cpix)
-	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
-	# Removing the central pixel from the list of surrounding pixels.
-	#spix=np.delete(spix,np.where(spix==cpix)[0][0]) 
-	theta1,phi1=h.pix2ang(nside,spix)
-	
-	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1)
-	sinalpha=np.where(abs(cosbeta)<1.,np.sin(theta1)*np.sin(phi1-phi0)/np.sqrt(1.-cosbeta*cosbeta),0.)
-	cosalpha=np.where(abs(cosbeta)<1.,(np.cos(theta0)*cosbeta - np.cos(theta1))/(np.sin(theta0)*np.sqrt(1.-cosbeta*cosbeta)),0)
-	
-	sin2alpha=2.*sinalpha*cosalpha
-	cos2alpha=cosalpha*cosalpha - sinalpha*sinalpha
-	
-	return cosbeta,cos2alpha,sin2alpha,spix
-
[…]

### 2018-04-27 codes/modules/return_kernel.py

@@ -1,141 +1,0 @@
-import healpy as h
-import numpy as np
-
-class return_kernel(object):
-
-    def __init__(self,nsidein,nsideout,lmin,lmax,wnorm="Int"):
-        self.nside=nsidein
-        self.upnside=nsideout
-        self.lmin=lmin
-        self.lmax=lmax
-
-        self.wnorm=wnorm
-        if self.wnorm=="Int":
-            self.normr=4.*np.pi/h.nside2npix(self.nside)
-            self.normg=1.
-        else:
-            self.normr=1.
-            self.normg=h.nside2npix(self.nside)/(4.*np.pi)
-
-        self.almsize=h.Alm.getsize(lmax=lmax,mmax=lmax)
-        self.almr0=np.zeros(almsize,complex)
-        self.almi0=np.zeros(almsize,complex)
-        self.almI=[np.zeros(almsize,complex),np.zeros(almsize,complex),np.zeros(almsize,complex)]
-        self.almJ=[np.zeros(almsize,complex),np.zeros(almsize,complex),np.zeros(almsize,complex)]
-        
-        for i in range(self.almsize):
-        l,m=h.Alm.getlm(self.lmax,i)
-        if l>=self.lmin and l<=self.lmax and m==2:
-            almr0[i]=0.5*complex(1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            almi0[i]=0.5*complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            almI[1][i]=0.25*complex(-1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            almI[2][i]=0.25*complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            almJ[1][i]=0.25*complex(-1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            almJ[2][i]=0.25*complex(0.0,1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
-            
-
-    def return_kernel_qu2eb(lmax,pixi,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
-    
-    if sample_nside==-1:
-        sample_nside=nside
-
-    if norm=="Int":
-        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
[…]

### 2018-04-27 codes/modules_old/local_eb_kernel.py

@@ -1,466 +1,0 @@
-import numpy as np
-from scipy.special import lpmn as lpmn
-from scipy.interpolate import interp1d
-import healpy as h
-
-class real_space_queb_kernels(object):
-
-	def __init__(self,nside,tmin=0.,tmax=30.,maxlmax=1024,sampling=1024):
-		self.nside=nside
-		self.tmin=tmin
-		self.tmax=tmax
-		self.maxlmax=maxlmax
-		self.sampling=sampling		
-
-		self.npix=h.nside2npix(self.nside)
-		self.omega=4.*np.pi/self.npix
-
-		self.theta=np.linspace(tmin*np.pi/180.,tmax*np.pi/180.,self.sampling)
-		self.pl2=np.zeros((self.maxlmax+1,np.size(self.theta)),float)
-		self.taper=np.ones(self.theta.size,float)
-
-
-		for i in range(self.theta.size):
-			y,temp=lpmn(2,self.maxlmax,np.cos(self.theta[i]))
-			for l in range(self.maxlmax+1):
-				self.pl2[l,i]=y[2,l]
-
-#	-----------------------------------------------------------------------------------------------------------------------------------------
-#	Function called by other internal functions.
-	def gauss(self,x,sigma=180.):
-	    y=np.exp(-x**2./(2.*sigma*sigma))#/sqrt(2.*pi*sigma*sigma)
-	    return y
-
-	def return_euler_angles(self,nside,cpixel,discsize=180.,nest=False):
-		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
-
-		v=h.pix2vec(nside,cpixel,nest=nest)
-		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=True,fact=4,nest=nest)
-		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
-
-		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
-		beta=np.arccos(temp_beta)
-
-		n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-
[…]

### 2018-04-27 codes/modules_old/local_eb_kernel_masked.py

@@ -1,478 +1,0 @@
-import numpy as np
-from scipy.special import lpmn as lpmn
-from scipy.interpolate import interp1d
-import healpy as h
-
-class real_space_queb_kernels(object):
-
-	def __init__(self,nside,tmin=0.,tmax=30.,maxlmax=1024,sampling=1024):
-		self.nside=nside
-		self.tmin=tmin
-		self.tmax=tmax
-		self.maxlmax=maxlmax
-		self.sampling=sampling		
-
-		self.npix=h.nside2npix(self.nside)
-		self.omega=4.*np.pi/self.npix
-
-		self.theta=np.linspace(tmin*np.pi/180.,tmax*np.pi/180.,self.sampling)
-		self.pl2=np.zeros((self.maxlmax+1,np.size(self.theta)),float)
-		self.taper=np.ones(self.theta.size,float)
-
-
-		for i in range(self.theta.size):
-			y,temp=lpmn(2,self.maxlmax,np.cos(self.theta[i]))
-			for l in range(self.maxlmax+1):
-				self.pl2[l,i]=y[2,l]
-
-#	-----------------------------------------------------------------------------------------------------------------------------------------
-#	Function called by other internal functions.
-	def gauss(self,x,sigma=180.):
-	    y=np.exp(-x**2./(2.*sigma*sigma))#/sqrt(2.*pi*sigma*sigma)
-	    return y
-
-	def return_euler_angles(self,nside,cpixel,discsize=180.,nest=False):
-		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
-
-		v=h.pix2vec(nside,cpixel,nest=nest)
-		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=False,fact=4,nest=nest)
-		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
-
-		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
-		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
-		beta=np.arccos(temp_beta)
-
-		n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-
[…]

### 2018-04-27 codes/modules_old/local_healpix_qu2eb.py

@@ -1,49 +1,0 @@
-import healpy as h
-import numpy as np
-
-def return_disc_mask(discsize,apow,nside,cpix):
-    mask=np.zeros(h.nside2npix(nside),float)
-    # The coordinate of the pixel center updated to that in the mask resolution
-    theta0=h.pix2ang(nside,cpix)[0] ; phi0=h.pix2ang(nside,cpix)[1]
-
-    pixnum=np.arange(h.nside2npix(nside))
-    theta=h.pix2ang(nside,pixnum)[0] ; phi=h.pix2ang(nside,pixnum)[1]
-    dotprod=np.sin(theta)*np.sin(theta0)*np.cos(phi-phi0)+np.cos(theta)*np.cos(theta0)
-    dtheta=np.arccos(dotprod)*180./np.pi
-
-    for i in range(h.nside2npix(nside)):
-        if dtheta[i] <= (discsize-apow):
-            mask[i]=1.
-        elif dtheta[i] > (discsize-apow) and dtheta[i] <= discsize:
-            mask[i]=np.cos((dtheta[i]-(discsize-apow))*np.pi/(2.*apow))**2.
-            
-    return mask
-
-def return_local_eb(tqu,discsize,nside,lmax,lmin=2.,apow=2.,return_equ_bqu=False):
-	
-	npix=h.nside2npix(nside)
-	rteb=[np.zeros(npix,float),np.zeros(npix,float)]
-
-	if return_equ_bqu:
-		requ=[np.zeros(npix,float),np.zeros(npix,float)]
-		rbqu=[np.zeros(npix,float),np.zeros(npix,float)]
-	
-		for i in range(npix):
-			mask=return_disc_mask(discsize,apow,nside,i)
-			temp_alm=h.map2alm(tqu*mask,lmax=lmax,pol=True)
-			temp_teb=h.alm2map(temp_alm,nside,pol=False,verbose=False)
-			temp_equ=h.alm2map([temp_alm[0],temp_alm[1],temp_alm[2]*0.],nside,pol=True,verbose=False)
-			temp_bqu=h.alm2map([temp_alm[0],temp_alm[1]*0.,temp_alm[2]],nside,pol=True,verbose=False)
-			rteb[0][i]=temp_teb[1][i] ; rteb[1][i]=temp_teb[2][i]
[…]

### 2018-04-27 codes/modules_old/local_healpix_qu2eb_masked.py

@@ -1,55 +1,0 @@
-import healpy as h
-import numpy as np
-
-def return_disc_mask(discsize,apow,nside,cpix):
-    mask=np.zeros(h.nside2npix(nside),float)
-    # The coordinate of the pixel center updated to that in the mask resolution
-    theta0=h.pix2ang(nside,cpix)[0] ; phi0=h.pix2ang(nside,cpix)[1]
-
-    pixnum=np.arange(h.nside2npix(nside))
-    theta=h.pix2ang(nside,pixnum)[0] ; phi=h.pix2ang(nside,pixnum)[1]
-    dotprod=np.sin(theta)*np.sin(theta0)*np.cos(phi-phi0)+np.cos(theta)*np.cos(theta0)
-    dtheta=np.arccos(dotprod)*180./np.pi
-
-    for i in range(h.nside2npix(nside)):
-        if dtheta[i] <= (discsize-apow):
-            mask[i]=1.
-        elif dtheta[i] > (discsize-apow) and dtheta[i] <= discsize:
-            mask[i]=np.cos((dtheta[i]-(discsize-apow))*np.pi/(2.*apow))**2.
-            
-    return mask
-
-def return_local_eb(tqu,discsize,nside,lmax,lmin=2.,apow=2.,pindex=[],return_equ_bqu=False):
-	
-	npix=h.nside2npix(nside)
-	rteb=[np.zeros(npix,float),np.zeros(npix,float)]
-
-	# Setting the pixel index
-	if np.size(pindex)==0:
-		print "Computing on all pixels"
-		pindex=np.arange(h.nside2npix(nside))
-
-
-	if return_equ_bqu:
-		requ=[np.zeros(npix,float),np.zeros(npix,float)]
-		rbqu=[np.zeros(npix,float),np.zeros(npix,float)]
-	
-		for i in pindex:
-			mask=return_disc_mask(discsize,apow,nside,i)
-			temp_alm=h.map2alm(tqu*mask,lmax=lmax,pol=True)
-			temp_teb=h.alm2map(temp_alm,nside,pol=False,verbose=False)
-			temp_equ=h.alm2map([temp_alm[0],temp_alm[1],temp_alm[2]*0.],nside,pol=True,verbose=False)
[…]

### 2018-04-27 codes/modules_old/mod_rad_cl_correction.py

@@ -1,111 +1,0 @@
-import numpy as np
-from scipy.special import lpmn as lpmn
-from scipy.interpolate import interp1d
-import numpy.polynomial.legendre as lgdr
-import scipy.integrate as intg
-import healpy as h
-import time
-
-def mod_gbeta(x,shift=15.,width=5.,slope=2.,expslope=2.):
-	shift=shift*np.pi/180. ; width=width*np.pi/180.
-	return (x**slope)*np.exp(-((x-shift)/(np.sqrt(2.)*width))**expslope)
-
-def get_mod_gbeta_root(shift=15.,width=5.,slope=2.):
-	return max(0.5*(shift + np.sqrt(shift**2. + 4.*slope*width*width)),0.5*(shift - np.sqrt(shift**2. + 4.*slope*width*width)))*np.pi/180.
-
-def return_beta0(lmax):
-	return min(180.,180.*24./lmax)*np.pi/180.
-
-def pl2norm(l):
-	return 2.*np.pi/(((l+2)*(l+1)*l*(l-1))**0.5)
-
-def fn_step_apo(theta,beta0,frac_beta0=3.,frac_apow=0.1):
-	'''
-	Returns a step function with a cosine squared apodization profile
-	Input variables:
-	frac_beta0 = Takes the factor of beta0 as the radial cutoff.
-	apow = Takes fraction of radial cutoff as in put.
-	example: frac_beta0=3. implies the rcutoff=3*beta0.
-		 apow=0.1. implies 10% of rcutoff is the apodization width.
-	'''
-	theta0=frac_beta0*beta0 ; apow=frac_apow*theta0
-	xp=(theta-(theta0-apow))*np.pi/(2.*apow)
-	stepfn=np.zeros(theta.size,float)
-	stepfn=np.cos(xp)**2.
-	stepfn[theta<=theta0-apow]=1.
-	stepfn[theta>theta0]=0.
-	return stepfn
-
-def har_high_pass_filter(ell,ell0,deltaell):
-    fl=np.ones(ell.size,float)
-    ellp=(ell-(ell0+deltaell))*pi/(2.*deltaell)
-    fl=cos(ellp)**2.
-    fl[ell<ell0]=0.
-    fl[ell>ell0+deltaell]=1.
-    return fl
-
[…]

### 2018-04-27 codes/modules_old/return_euler.py

@@ -1,136 +1,0 @@
-import numpy as np
-
-def return_euler(theta1,phi1,theta2,phi2):
-
-	n = np.sin(theta1)*np.sin(theta2)*np.cos(phi1-phi2) + np.cos(theta1)*np.cos(theta2)
-	beta = np.arccos(n)
-	
-	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
-	da = np.cos(theta1)*np.cos(beta) - np.cos(theta2)
-	dg = np.cos(theta2)*np.cos(beta) - np.cos(theta1)
-
-
-        if n>=0 and da>=0 :
-		alpha=np.arctan(n/da)
-	elif n>=0 and da<0:
-        	alpha=np.pi-np.arctan(n/abs(da))
-	elif n<0 and da<0:
-        	alpha=np.arctan(abs(n)/abs(da))-np.pi
-        elif n<0 and da>0:
-                alpha=2.*np.pi-np.arctan(abs(n)/da)
-
-	if n==0:
-		alpha=0.0
-	alpha=np.arctan2(n,da)
-
-
-        if n>=0 and dg>=0 :
-		gamma=np.arctan(n/dg)
-	elif n>=0 and dg<0:
-        	gamma=np.pi-np.arctan(n/abs(dg))
-	elif n<0 and dg<0:
-        	gamma=np.pi+np.arctan(abs(n)/abs(dg))
-        elif n<0 and dg>0:
-                gamma=2.*np.pi-np.arctan(abs(n)/dg)	
-
-	if n==0:
-		gamma=0.0
-
-	#gamma=2.*np.pi-gamma
-	gamma=np.arctan2(n,dg)
-
-	return alpha,beta,gamma,n,da,dg	
-
-def return_euler_tan_old(theta1,phi1,theta2,phi2):
-
-	n = np.sin(theta1)*np.sin(theta2)*np.cos(phi1-phi2) + np.cos(theta1)*np.cos(theta2)
-	beta = np.arccos(n)
-	
-	n = np.sin(theta2)*np.sin(phi1-phi2)
-	d = np.sin(theta2)*np.cos(theta1)*np.cos(phi1-phi2) - np.sin(theta1)*np.cos(theta2)
-
-        if n>=0 and d>=0 :
-		alpha=np.arctan(n/d)
-	elif n>=0 and d<0:
[…]

### 2018-04-27 codes/modules_old/return_rotated_kernel_healpix.py

@@ -1,108 +1,0 @@
-import healpy as h
-import numpy as np
-
-def return_kernel_qu2eb(nside,lmax,pixi,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
-    
-    if sample_nside==-1:
-        sample_nside=nside
-
-    if norm=="Int":
-        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
-    else:
-        norm=1.
-
-    if use_coord:
-        pixi=h.ang2pix(nside,thetai,phii)
-        thetai,phii=h.pix2ang(nside,pixi)
-    else:
-        thetai,phii=h.pix2ang(nside,pixi)
-
-    almsize=h.Alm.getsize(lmax=lmax,mmax=lmax)
-    almr0=np.zeros(almsize,complex)
-    almi0=np.zeros(almsize,complex)
-
-    for i in range(almsize):
-        l,m=h.Alm.getlm(lmax,i)
-        if l>1 and m==2:
-            almr0[i]=complex(1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))*norm
-            almi0[i]=complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))*norm
-
-    h.rotate_alm(almr0,0.0,thetai,phii)
-    h.rotate_alm(almi0,0.0,thetai,phii)
-
-    mr=h.alm2map(almr0,sample_nside,lmax=lmax,mmax=lmax,verbose=False)
-    mi=h.alm2map(almi0,sample_nside,lmax=lmax,mmax=lmax,verbose=False)
-
-    return mr,mi
-    
-
-def return_kernel_I(nside,lmax,pixi=-1,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
-    '''
-    If pixi=-1 then the alms correspond to the kernel exactly at the pole. Else the alms are rotated to 
-    allign with the specified coordinate or the coordinate of the pixel.
-    '''
-    if sample_nside==-1:
-        sample_nside=nside
-
-    if norm=="Int":
-        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
-    else:
-        norm=1.
-
-    if use_coord:
-        pixi=h.ang2pix(nside,thetai,phii)
-        thetai,phii=h.pix2ang(nside,pixi)
-    else:
[…]

### 2018-04-27 codes/modules_v0/local_eb_kernel.py

@@ -1,0 +1,466 @@
+import numpy as np
+from scipy.special import lpmn as lpmn
+from scipy.interpolate import interp1d
+import healpy as h
+
+class real_space_queb_kernels(object):
+
+	def __init__(self,nside,tmin=0.,tmax=30.,maxlmax=1024,sampling=1024):
+		self.nside=nside
+		self.tmin=tmin
+		self.tmax=tmax
+		self.maxlmax=maxlmax
+		self.sampling=sampling		
+
+		self.npix=h.nside2npix(self.nside)
+		self.omega=4.*np.pi/self.npix
+
+		self.theta=np.linspace(tmin*np.pi/180.,tmax*np.pi/180.,self.sampling)
+		self.pl2=np.zeros((self.maxlmax+1,np.size(self.theta)),float)
+		self.taper=np.ones(self.theta.size,float)
+
+
+		for i in range(self.theta.size):
+			y,temp=lpmn(2,self.maxlmax,np.cos(self.theta[i]))
+			for l in range(self.maxlmax+1):
+				self.pl2[l,i]=y[2,l]
+
+#	-----------------------------------------------------------------------------------------------------------------------------------------
+#	Function called by other internal functions.
+	def gauss(self,x,sigma=180.):
+	    y=np.exp(-x**2./(2.*sigma*sigma))#/sqrt(2.*pi*sigma*sigma)
+	    return y
+
+	def return_euler_angles(self,nside,cpixel,discsize=180.,nest=False):
+		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
+
+		v=h.pix2vec(nside,cpixel,nest=nest)
+		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=True,fact=4,nest=nest)
+		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
+
+		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
+		beta=np.arccos(temp_beta)
+
+		n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
[…]

### 2018-04-27 codes/modules_v0/local_eb_kernel_masked.py

@@ -1,0 +1,478 @@
+import numpy as np
+from scipy.special import lpmn as lpmn
+from scipy.interpolate import interp1d
+import healpy as h
+
+class real_space_queb_kernels(object):
+
+	def __init__(self,nside,tmin=0.,tmax=30.,maxlmax=1024,sampling=1024):
+		self.nside=nside
+		self.tmin=tmin
+		self.tmax=tmax
+		self.maxlmax=maxlmax
+		self.sampling=sampling		
+
+		self.npix=h.nside2npix(self.nside)
+		self.omega=4.*np.pi/self.npix
+
+		self.theta=np.linspace(tmin*np.pi/180.,tmax*np.pi/180.,self.sampling)
+		self.pl2=np.zeros((self.maxlmax+1,np.size(self.theta)),float)
+		self.taper=np.ones(self.theta.size,float)
+
+
+		for i in range(self.theta.size):
+			y,temp=lpmn(2,self.maxlmax,np.cos(self.theta[i]))
+			for l in range(self.maxlmax+1):
+				self.pl2[l,i]=y[2,l]
+
+#	-----------------------------------------------------------------------------------------------------------------------------------------
+#	Function called by other internal functions.
+	def gauss(self,x,sigma=180.):
+	    y=np.exp(-x**2./(2.*sigma*sigma))#/sqrt(2.*pi*sigma*sigma)
+	    return y
+
+	def return_euler_angles(self,nside,cpixel,discsize=180.,nest=False):
+		theta1,phi1=h.pix2ang(nside,cpixel,nest=nest)
+
+		v=h.pix2vec(nside,cpixel,nest=nest)
+		spixel=h.query_disc(nside,v,discsize*np.pi/180.,inclusive=False,fact=4,nest=nest)
+		theta2,phi2=h.pix2ang(nside,spixel,nest=nest)
+
+		temp_beta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+		temp_beta[temp_beta>1.]=1. ; temp_beta[temp_beta<-1.]=-1.
+		beta=np.arccos(temp_beta)
+
+		n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
[…]

### 2018-04-27 codes/modules_v0/local_healpix_qu2eb.py

@@ -1,0 +1,49 @@
+import healpy as h
+import numpy as np
+
+def return_disc_mask(discsize,apow,nside,cpix):
+    mask=np.zeros(h.nside2npix(nside),float)
+    # The coordinate of the pixel center updated to that in the mask resolution
+    theta0=h.pix2ang(nside,cpix)[0] ; phi0=h.pix2ang(nside,cpix)[1]
+
+    pixnum=np.arange(h.nside2npix(nside))
+    theta=h.pix2ang(nside,pixnum)[0] ; phi=h.pix2ang(nside,pixnum)[1]
+    dotprod=np.sin(theta)*np.sin(theta0)*np.cos(phi-phi0)+np.cos(theta)*np.cos(theta0)
+    dtheta=np.arccos(dotprod)*180./np.pi
+
+    for i in range(h.nside2npix(nside)):
+        if dtheta[i] <= (discsize-apow):
+            mask[i]=1.
+        elif dtheta[i] > (discsize-apow) and dtheta[i] <= discsize:
+            mask[i]=np.cos((dtheta[i]-(discsize-apow))*np.pi/(2.*apow))**2.
+            
+    return mask
+
+def return_local_eb(tqu,discsize,nside,lmax,lmin=2.,apow=2.,return_equ_bqu=False):
+	
+	npix=h.nside2npix(nside)
+	rteb=[np.zeros(npix,float),np.zeros(npix,float)]
+
+	if return_equ_bqu:
+		requ=[np.zeros(npix,float),np.zeros(npix,float)]
+		rbqu=[np.zeros(npix,float),np.zeros(npix,float)]
+	
+		for i in range(npix):
+			mask=return_disc_mask(discsize,apow,nside,i)
+			temp_alm=h.map2alm(tqu*mask,lmax=lmax,pol=True)
+			temp_teb=h.alm2map(temp_alm,nside,pol=False,verbose=False)
+			temp_equ=h.alm2map([temp_alm[0],temp_alm[1],temp_alm[2]*0.],nside,pol=True,verbose=False)
+			temp_bqu=h.alm2map([temp_alm[0],temp_alm[1]*0.,temp_alm[2]],nside,pol=True,verbose=False)
+			rteb[0][i]=temp_teb[1][i] ; rteb[1][i]=temp_teb[2][i]
[…]

### 2018-04-27 codes/modules_v0/mod_rad_cl_correction.py

@@ -1,0 +1,111 @@
+import numpy as np
+from scipy.special import lpmn as lpmn
+from scipy.interpolate import interp1d
+import numpy.polynomial.legendre as lgdr
+import scipy.integrate as intg
+import healpy as h
+import time
+
+def mod_gbeta(x,shift=15.,width=5.,slope=2.,expslope=2.):
+	shift=shift*np.pi/180. ; width=width*np.pi/180.
+	return (x**slope)*np.exp(-((x-shift)/(np.sqrt(2.)*width))**expslope)
+
+def get_mod_gbeta_root(shift=15.,width=5.,slope=2.):
+	return max(0.5*(shift + np.sqrt(shift**2. + 4.*slope*width*width)),0.5*(shift - np.sqrt(shift**2. + 4.*slope*width*width)))*np.pi/180.
+
+def return_beta0(lmax):
+	return min(180.,180.*24./lmax)*np.pi/180.
+
+def pl2norm(l):
+	return 2.*np.pi/(((l+2)*(l+1)*l*(l-1))**0.5)
+
+def fn_step_apo(theta,beta0,frac_beta0=3.,frac_apow=0.1):
+	'''
+	Returns a step function with a cosine squared apodization profile
+	Input variables:
+	frac_beta0 = Takes the factor of beta0 as the radial cutoff.
+	apow = Takes fraction of radial cutoff as in put.
+	example: frac_beta0=3. implies the rcutoff=3*beta0.
+		 apow=0.1. implies 10% of rcutoff is the apodization width.
+	'''
+	theta0=frac_beta0*beta0 ; apow=frac_apow*theta0
+	xp=(theta-(theta0-apow))*np.pi/(2.*apow)
+	stepfn=np.zeros(theta.size,float)
+	stepfn=np.cos(xp)**2.
+	stepfn[theta<=theta0-apow]=1.
+	stepfn[theta>theta0]=0.
+	return stepfn
+
+def har_high_pass_filter(ell,ell0,deltaell):
+    fl=np.ones(ell.size,float)
+    ellp=(ell-(ell0+deltaell))*pi/(2.*deltaell)
+    fl=cos(ellp)**2.
+    fl[ell<ell0]=0.
+    fl[ell>ell0+deltaell]=1.
+    return fl
+
[…]

### 2018-04-27 codes/modules_v1/aliasing_correction.py

@@ -1,0 +1,93 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''
+	This Euler angles function works for the qu2_equ_bqu function.
+	The set of function here, match Healpix results to numerical accuracy.
+	'''
+	theta1,phi1=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	theta2,phi2=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
+	beta=np.arccos(cosbeta)
+
+	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
+    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
+    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
+    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
+	return beta,alpha,gamma,spix
+
+def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	hq=np.zeros(npix,"double")
+	hu=np.zeros(npix,"double")
+	
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+		
+	for i in pix_list:
[…]

### 2018-04-27 codes/modules_v1/convert_qu2_equ_bqu_new.py

@@ -1,0 +1,99 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''
+	This Euler angles function works for the qu2_equ_bqu function.
+	The set of function here, match Healpix results to numerical accuracy.
+	'''
+	theta1,phi1=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	theta2,phi2=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+	cosbeta[cosbeta>1.]=1. ; cosbeta[cosbeta<-1.]=-1.
+	beta=np.arccos(cosbeta)
+
+	n = np.sin(theta1)*np.sin(theta2)*np.sin(phi1-phi2)
+
+    	da = np.cos(theta1)*cosbeta - np.cos(theta2)
+    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+	dg = np.cos(theta2)*cosbeta - np.cos(theta1)
+    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
+	return beta,alpha,gamma,spix
+
+def convert_qu2_equ_bqu_integrate(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
+	'''Pass alias corrected TQU map to this routine.'''
+	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
+	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
+	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
[…]

### 2018-04-27 codes/modules_v1/convert_qu2eb.py

@@ -1,0 +1,102 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Integrating method to generate E and B mode maps.
+def convert_qu2eb_integrate(q,u,theta_cutoff,theta,rad_ker):
+	'''
+	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+	e=np.zeros(npix,"double")
+	b=np.zeros(npix,"double")
+	for i in range(npix):
+		cosbeta,cos2gamma,sin2gamma,spix=euler.fn_s2euler_gamma(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(cosbeta)
+		cgfb=cos2gamma*gbeta ; sgfb=sin2gamma*gbeta
+		e[i] = (np.dot(-cgfb,q[spix]) + np.dot( sgfb,u[spix]))*domega
+		b[i] = (np.dot(-sgfb,q[spix]) + np.dot(-cgfb,u[spix]))*domega
+	return [np.zeros(npix),e,b]
+
+
+def convert_qu2eb_integrate_masked(q,u,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses Q and U maps in reggions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
[…]

### 2018-04-27 codes/modules_v1/euler.py

@@ -1,0 +1,134 @@
+import numpy as np
+import healpy as h
+
+def return_euler_angles(theta1,phi1,theta2,phi2):
+	'''Returns the Euler angles for a pair of spherical coordinates'''
+	cosbeta=np.sin(theta1)*np.sin(theta2)*np.cos(phi2-phi1)+np.cos(theta1)*np.cos(theta2) 
+	beta=np.arccos(cosbeta)
+
+	na = np.sin(theta2)*np.sin(phi2-phi1)
+	da = -np.sin(theta1)*np.cos(theta2) + np.sin(theta2)*np.cos(theta1)*np.cos(phi2-phi1)
+    	alpha=np.arctan2(na,da)
+
+	ng = np.sin(theta1)*np.sin(phi2-phi1)
+	dg = np.sin(theta2)*np.cos(theta1) - np.sin(theta1)*np.cos(theta2)*np.cos(phi2-phi1)
+    	gamma=np.arctan2(ng,dg)
+
+	return alpha,beta,gamma
+
+
+def return_spix_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''Returns the pixel numbers and the respective Euler angles within a circle of radius discsize from the central pixel: cpix'''
+	theta0,phi0=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	spix=np.delete(spix,np.where(spix==cpix)[0][0])
+	theta1,phi1=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1) 
+	beta=np.arccos(cosbeta)
+
+	n = np.sin(theta0)*np.sin(theta1)*np.sin(phi0-phi1)
+
+    	da = np.cos(theta0)*np.cos(beta) - np.cos(theta1)
+    	alpha=np.arctan2(n,da) ; alpha[beta==0]=0. ; alpha[abs(beta-np.pi)<1e-5]=0.
+
+	dg = np.cos(theta1)*np.cos(beta) - np.cos(theta0)
+    	gamma=np.arctan2(n,dg) ; gamma[beta==0]=0. ; gamma[abs(beta-np.pi)<1e-5]=0.
+
[…]

### 2018-04-27 codes/modules_v2/aliasing_correction.py

@@ -1,0 +1,75 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to convolve with a band limited delta function
+def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	hq=np.zeros(npix,"double")
+	hu=np.zeros(npix,"double")
+	
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	# The pixel i is where EQU and BQU are being evaluated.	
+	for i in pix_list:
+		beta,alpha,gamma,spix=euler.return_euler_angles(nside,i,theta_cutoff,inclusive=True,fact=4)
+		gbeta=fn_rad_ker_i(beta)
+		Ir=np.cos(2.*(alpha+gamma))*gbeta
+		Ii=np.sin(2.*(alpha+gamma))*gbeta
+
+		hq[i]=(np.dot(Ir,q[spix]) + np.dot(-Ii,u[spix]))*domega
+		hu[i]=(np.dot(Ii,q[spix]) + np.dot( Ir,u[spix]))*domega
+
+	return hq,hu
+
+def correct_aliasing_convolve(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
+	npix=np.size(tq)
+	cq=np.zeros(npix,"double") ; cu=np.zeros(npix,"double")	
+	for i in range(iter+1):
+		hq,hu=delta_convolve(tq-cq,tu-cu,theta_cutoff,theta,rad_ker_i,mask)
+		cq=cq + (hq-tq) ; cu=cu + (hu-tu)
+
+	return [np.zeros(npix),tq-cq,tu-cu]
+
+# Radiation method to convolve with a band limited delta function
+def delta_radiate(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
[…]

### 2018-04-27 codes/modules_v2/buggy/aliasing_correction_buggy.py

@@ -1,0 +1,75 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to convolve with a band limited delta function
+def delta_convolve(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
+	fn_rad_ker_i=interp1d(np.cos(theta)[::-1],rad_ker_i[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	hq=np.zeros(npix,"double")
+	hu=np.zeros(npix,"double")
+	
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	# The pixel i is where EQU and BQU are being evaluated.	
+	for i in pix_list:
+		cosbeta,c2apg,s2apg,spix=euler.fn_euler_trig2_alpha_plus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
+		gbeta=fn_rad_ker_i(cosbeta)
+		Ir=c2apg*gbeta
+		Ii=s2apg*gbeta
+
+		hq[i]=(np.dot(Ir,q[spix]) + np.dot(-Ii,u[spix]))*domega
+		hu[i]=(np.dot(Ii,q[spix]) + np.dot( Ir,u[spix]))*domega
+
+	return hq,hu
+
+def correct_aliasing_convolve(tq,tu,theta_cutoff,theta,rad_ker_i,iter=3,mask=[]):
+	npix=np.size(tq)
+	cq=np.zeros(npix,"double") ; cu=np.zeros(npix,"double")	
+	for i in range(iter):
+		hq,hu=delta_convolve(tq-cq,tu-cu,theta_cutoff,theta,rad_ker_i,mask)
+		cq=cq + (hq-tq) ; cu=cu + (hu-tu)
+
+	return [np.zeros(npix),tq-cq,tu-cu]
+
+# Radiation method to convolve with a band limited delta function
+def delta_radiate(q,u,theta_cutoff,theta,rad_ker_i,mask=[]):
[…]

### 2018-04-27 codes/modules_v2/buggy/convert_eb2qu.py

@@ -1,0 +1,54 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to generate E and B mode maps.
+def convert_eb2qu_convolve(e,b,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses E and B maps in reggions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	q=np.zeros(npix,"double")
+	u=np.zeros(npix,"double")
+	for i in pix_list:
+		cosbeta,cos2alpha,sin2alpha,spix=euler.fn_euler_trig2alpha(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(cosbeta)
+		c2afb=cos2alpha*gbeta ; s2afb=sin2alpha*gbeta
+		q[i] = (np.dot(-c2afb,e[spix]) + np.dot( s2afb,b[spix]))*domega
+		u[i] = (np.dot(-s2afb,e[spix]) + np.dot(-c2afb,b[spix]))*domega
+
+	return [np.zeros(npix),q,u]
+
+
+
+# Radiating method to generate Q and U mode maps.
+def convert_eb2qu_radiate(e,b,theta_cutoff,theta,rad_ker,mask=[]):
+	'''This function only uses E and B maps inside the mask provided. It computes Q and U maps in regions defined by the radial cutoff'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
[…]

### 2018-04-27 codes/modules_v2/buggy/convert_qu2_equ_bqu.py

@@ -1,0 +1,77 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to separate Q U into Stokes parameters corresponding to E and B modes respectively
+def convert_qu2_equ_bqu_convolve(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
+	'''Pass alias corrected TQU map to this routine.'''
+	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
+	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
+	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
+	fn_rad_ker_d=interp1d(np.cos(theta)[::-1],rad_ker_d[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+
+	dqu=[np.zeros(npix,"double"),np.zeros(npix,"double")]
+	
+	if np.size(cq)!=0 and np.size(cu)!=0:
+		for i in pix_list:
+			cosbeta,c2amg,s2amg,spix=euler.fn_euler_trig2_alpha_minus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
+			gbeta=fn_rad_ker_d(cosbeta)
+			Dr=c2amg*gbeta ; Di=s2amg*gbeta
+
+			dqu[0][i]=(np.dot(Dr,cq[spix]) + np.dot( Di,cu[spix]))*domega
+			dqu[1][i]=(np.dot(Di,cq[spix]) + np.dot(-Dr,cu[spix]))*domega
+	else:
+		for i in pix_list:
+			cosbeta,c2amg,s2amg,spix=euler.fn_euler_trig2_alpha_minus_gamma(nside,i,theta_cutoff,inclusive=True,fact=4)
+			gbeta=fn_rad_ker_d(cosbeta)
[…]

### 2018-04-27 codes/modules_v2/buggy/convert_qu2eb.py

@@ -1,0 +1,54 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to generate E and B mode maps.
+def convert_qu2eb_convolve(q,u,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	e=np.zeros(npix,"double")
+	b=np.zeros(npix,"double")
+	for i in pix_list:
+		cosbeta,cos2gamma,sin2gamma,spix=euler.fn_euler_trig2gamma(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(cosbeta)
+		c2gfb=cos2gamma*gbeta ; s2gfb=sin2gamma*gbeta
+		e[i] = (np.dot(-c2gfb,q[spix]) + np.dot( s2gfb,u[spix]))*domega
+		b[i] = (np.dot(-s2gfb,q[spix]) + np.dot(-c2gfb,u[spix]))*domega
+	return [np.zeros(npix),e,b]
+
+
+
+# Radiating method to generate E and B mode maps.
+def convert_qu2eb_radiate(q,u,theta_cutoff,theta,rad_ker,mask=[]):
+	'''This function only uses Q and U maps inside the mask provided. It computes E and B maps in regions defined by the radial cutoff'''
+	fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
[…]

### 2018-04-27 codes/modules_v2/buggy/euler.py

@@ -1,0 +1,103 @@
+import numpy as np
+import healpy as h
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''Returns the Euler angles for a pair of spherical coordinates'''
+	theta0,phi0=h.pix2ang(nside,cpix)
+        v=h.pix2vec(nside,cpix)
+        spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+        theta1,phi1=h.pix2ang(nside,spix)
+	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1) 
+	beta=np.arccos(cosbeta)
+
+	na = np.sin(theta0)*np.sin(theta1)*np.sin(phi1-phi0)
+	da = np.cos(theta0)*cosbeta - np.cos(theta1)
+    	alpha=np.arctan2(na,da)
+
+	ng = na
+	dg = np.cos(theta1)*cosbeta - np.cos(theta0)
+    	gamma=np.arctan2(ng,dg)
+
+	return beta,alpha,gamma,spix
+
+def fn_euler_trig2alpha(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''Returns the pixel numbers and the respective functions of Euler angles within a circle of radius discsize from the central pixel: cpix'''
+	theta0,phi0=h.pix2ang(nside,cpix)
+	v=h.pix2vec(nside,cpix)
+	spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+	# Removing the central pixel from the list of surrounding pixels.
+	#spix=np.delete(spix,np.where(spix==cpix)[0][0]) 
+	theta1,phi1=h.pix2ang(nside,spix)
+	
+	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1)
+	sinalpha=np.where(abs(cosbeta)<1.,np.sin(theta1)*np.sin(phi1-phi0)/np.sqrt(1.-cosbeta*cosbeta),0.)
[…]

### 2018-04-27 codes/modules_v2/buggy/return_kernel.py

@@ -1,0 +1,141 @@
+import healpy as h
+import numpy as np
+
+class return_kernel(object):
+
+    def __init__(self,nsidein,nsideout,lmin,lmax,wnorm="Int"):
+        self.nside=nsidein
+        self.upnside=nsideout
+        self.lmin=lmin
+        self.lmax=lmax
+
+        self.wnorm=wnorm
+        if self.wnorm=="Int":
+            self.normr=4.*np.pi/h.nside2npix(self.nside)
+            self.normg=1.
+        else:
+            self.normr=1.
+            self.normg=h.nside2npix(self.nside)/(4.*np.pi)
+
+        self.almsize=h.Alm.getsize(lmax=lmax,mmax=lmax)
+        self.almr0=np.zeros(almsize,complex)
+        self.almi0=np.zeros(almsize,complex)
+        self.almI=[np.zeros(almsize,complex),np.zeros(almsize,complex),np.zeros(almsize,complex)]
+        self.almJ=[np.zeros(almsize,complex),np.zeros(almsize,complex),np.zeros(almsize,complex)]
+        
+        for i in range(self.almsize):
+        l,m=h.Alm.getlm(self.lmax,i)
+        if l>=self.lmin and l<=self.lmax and m==2:
+            almr0[i]=0.5*complex(1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            almi0[i]=0.5*complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            almI[1][i]=0.25*complex(-1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            almI[2][i]=0.25*complex(0.0,-1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            almJ[1][i]=0.25*complex(-1.0,0.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            almJ[2][i]=0.25*complex(0.0,1.0)*np.sqrt((2.*l+1.)/(4.*np.pi))
+            
+
+    def return_kernel_qu2eb(lmax,pixi,thetai=0,phii=0,use_coord=False,norm="Int",sample_nside=-1):
+    
+    if sample_nside==-1:
+        sample_nside=nside
+
+    if norm=="Int":
+        norm=0.5*(4.*np.pi)/h.nside2npix(nside)
[…]

### 2018-04-27 codes/modules_v2/buggy/return_kernels.py

@@ -1,0 +1,50 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_qu2eb_kernel_convolve(nside,lon,lat,theta_cutoff,theta,rad_ker):
+    fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+    cpix=h.ang2pix(nside,theta,phi,lonlat=True)
+    cosbeta,cos2gamma,sin2gamma,spix=euler.fn_euler_trig2gamma(nside,cpix,theta_cutoff,inclusive=False,fact=4)
+    rker=np.zeros(npix,"double") ; rker[spix]= cos2gamma*gbeta
+    iker=np.zeros(npix,"double") ; iker[spix]= sin2gamma*gbeta
+    return[rker,iker]
+
+def return_qu2eb_kernel_radiate(nside,lon,lat,theta_cutoff,theta,rad_ker):
+    fn_rad_ker=interp1d(np.cos(theta)[::-1],rad_ker[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+    cpix=h.ang2pix(nside,theta,phi,lonlat=True)
+    cosbeta,cos2alpha,sin2alpha,spix=euler.fn_euler_trig2alpha(nside,cpix,theta_cutoff,inclusive=False,fact=4)
+
+    rker=np.zeros(npix,"double") ; rker[spix]=  cos2alpha*gbeta
+    iker=np.zeros(npix,"double") ; iker[spix]= -sin2alpha*gbeta
+    return[rker,iker]
+
+def return_I_kernel(nside,lon,lat,theta_cutoff,theta,rad_ker_i):
+    fn_rad_ker_i=interp1d(np.cos(theta)[::-1],rad_ker_i[::-1],assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+    
+    cpix=h.ang2pix(nside,theta,phi,lonlat=True)
[…]

### 2018-04-27 codes/modules_v2/convert_eb2qu.py

@@ -1,0 +1,54 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to generate E and B mode maps.
+def convert_eb2qu_convolve(e,b,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses E and B maps in reggions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes Q and U maps only inside the mask\n If you want it to compute only on masked E/B maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	q=np.zeros(npix,"double")
+	u=np.zeros(npix,"double")
+	for i in pix_list:
+		beta,alpha,gamma,spix=euler.return_euler_angles(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(beta)
+		c2afb=np.cos(2.*alpha)*gbeta ; s2afb=np.sin(2.*alpha)*gbeta
+		q[i] = (np.dot(-c2afb,e[spix]) + np.dot( s2afb,b[spix]))*domega
+		u[i] = (np.dot(-s2afb,e[spix]) + np.dot(-c2afb,b[spix]))*domega
+
+	return [np.zeros(npix),q,u]
+
+
+
+# Radiating method to generate Q and U mode maps.
+def convert_eb2qu_radiate(e,b,theta_cutoff,theta,rad_ker,mask=[]):
+	'''This function only uses E and B maps inside the mask provided. It computes Q and U maps in regions defined by the radial cutoff'''
+	fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(e) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
[…]

### 2018-04-27 codes/modules_v2/convert_qu2_equ_bqu.py

@@ -1,0 +1,77 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to separate Q U into Stokes parameters corresponding to E and B modes respectively
+def convert_qu2_equ_bqu_convolve(q,u,theta_cutoff,theta,rad_ker_d,cq=[],cu=[],mask=[]):
+	'''Pass alias corrected TQU map to this routine.'''
+	'''The delta function should act like an identity operator, but it does not on the Healpix pixelization'''
+	'''The delta term is thought to operate on the corrected TQU to return true TQU, but thats not the case as it returns TQU with error of order iter+1 order \n
+	where iter refers to the number of correction terms added to the tqu maps passed to this routine.'''
+	fn_rad_ker_d=interp1d(theta,rad_ker_d,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+
+	dqu=[np.zeros(npix,"double"),np.zeros(npix,"double")]
+	
+	if np.size(cq)!=0 and np.size(cu)!=0:
+		for i in pix_list:
+			beta,alpha,gamma,spix=euler.return_euler_angles(nside,i,theta_cutoff,inclusive=True,fact=4)
+			gbeta=fn_rad_ker_d(beta)
+			Dr=np.cos(2.*(alpha-gamma))*gbeta ; Di=np.sin(2.*(alpha-gamma))*gbeta
+
+			dqu[0][i]=(np.dot(Dr,cq[spix]) + np.dot( Di,cu[spix]))*domega
+			dqu[1][i]=(np.dot(Di,cq[spix]) + np.dot(-Dr,cu[spix]))*domega
+	else:
+		for i in pix_list:
+			beta,alpha,gamma,spix=euler.return_euler_angles(nside,i,theta_cutoff,inclusive=True,fact=4)
+			gbeta=fn_rad_ker_d(beta)
[…]

### 2018-04-27 codes/modules_v2/convert_qu2eb.py

@@ -1,0 +1,54 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+# Convolution method to generate E and B mode maps.
+def convert_qu2eb_convolve(q,u,theta_cutoff,theta,rad_ker,mask=[]):
+	'''
+	   This function uses Q and U maps in regions defined by the radial cutoff, irrespective of the mask.\n
+	   It computes E and B maps only inside the mask\n If you want it to compute only on masked Q/U maps then just pass masked maps.
+	'''
+	fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
+		pix_list=np.nonzero(mask)[0]
+
+	e=np.zeros(npix,"double")
+	b=np.zeros(npix,"double")
+	for i in pix_list:
+		beta,alpha,gamma,spix=euler.return_euler_angles(nside,i,theta_cutoff,inclusive=False,fact=4)
+		gbeta=fn_rad_ker(beta)
+		c2gfb=np.cos(2.*gamma)*gbeta ; s2gfb=np.sin(2.*gamma)*gbeta
+		e[i] = (np.dot(-c2gfb,q[spix]) + np.dot( s2gfb,u[spix]))*domega
+		b[i] = (np.dot(-s2gfb,q[spix]) + np.dot(-c2gfb,u[spix]))*domega
+	return [np.zeros(npix),e,b]
+
+
+
+# Radiating method to generate E and B mode maps.
+def convert_qu2eb_radiate(q,u,theta_cutoff,theta,rad_ker,mask=[]):
+	'''This function only uses Q and U maps inside the mask provided. It computes E and B maps in regions defined by the radial cutoff'''
+	fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+	nside=h.get_nside(q) ; npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+
+	if np.size(mask)==0:
+		pix_list=np.arange(npix)
+	else:
[…]

### 2018-04-27 codes/modules_v2/euler.py

@@ -1,0 +1,22 @@
+import numpy as np
+import healpy as h
+
+def return_euler_angles(nside,cpix,discsize=np.pi,inclusive=False,fact=4):
+	'''Returns the Euler angles for a pair of spherical coordinates'''
+	theta0,phi0=h.pix2ang(nside,cpix) ; v=h.pix2vec(nside,cpix)
+
+        spix=h.query_disc(nside,v,discsize,inclusive=inclusive,fact=fact)
+        theta1,phi1=h.pix2ang(nside,spix)
+
+	cosbeta=np.sin(theta0)*np.sin(theta1)*np.cos(phi1-phi0)+np.cos(theta0)*np.cos(theta1) 
+	beta=np.arccos(cosbeta)
+
+	na = np.sin(theta0)*np.sin(theta1)*np.sin(phi1-phi0)
+	da = np.cos(theta0)*cosbeta - np.cos(theta1)
+    	alpha=np.arctan2(na,da) ; alpha[abs(cosbeta)==1.]=0.
+
+	ng = na
+	dg = np.cos(theta1)*cosbeta - np.cos(theta0)
+    	gamma=np.arctan2(ng,dg) ; gamma[abs(cosbeta)==1.]=0.
+
+	return beta,alpha,gamma,spix

### 2018-04-27 codes/modules_v2/return_kernels.py

@@ -1,0 +1,56 @@
+import healpy as h
+import numpy as np
+import euler as euler
+from scipy.interpolate import interp1d
+
+def return_qu2eb_kernel_convolve(nside,lon,lat,theta_cutoff,theta,rad_ker):
+    fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+    cpix=h.ang2pix(nside,lon,lat,lonlat=True)
+
+    beta,alpha,gamma,spix=euler.return_euler_angles(nside,cpix,theta_cutoff,inclusive=False,fact=4)
+
+    gbeta=fn_rad_ker(beta)
+    rker=np.zeros(npix,"double") ; rker[spix]= np.cos(2.*gamma)*gbeta
+    iker=np.zeros(npix,"double") ; iker[spix]= np.sin(2.*gamma)*gbeta
+
+    return cpix,[rker,iker]
+
+def return_qu2eb_kernel_radiate(nside,lon,lat,theta_cutoff,theta,rad_ker):
+    fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+    cpix=h.ang2pix(nside,lon,lat,lonlat=True)
+
+    beta,alpha,gamma,spix=euler.return_euler_angles(nside,cpix,theta_cutoff,inclusive=False,fact=4)
+    
+    gbeta=fn_rad_ker(beta)
+    rker=np.zeros(npix,"double") ; rker[spix]=  np.cos(2.*alpha)*gbeta
+    iker=np.zeros(npix,"double") ; iker[spix]= -np.sin(2.*alpha)*gbeta
+    return cpix,[rker,iker]
+
+def return_I_kernel(nside,lon,lat,theta_cutoff,theta,rad_ker_i):
+    fn_rad_ker_i=interp1d(theta,rad_ker_i,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
+    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+    cpix=h.ang2pix(nside,lon,lat,lonlat=True)
+
[…]

### 2018-05-01 articles/formalism/sections/old_primer_and_heuristic_arg.tex
Pulled initial version of primer and heuristic argument into separate file.  Some additional editing.

--- 2018-04-11 articles/formalism/sections/real_space_formalism.tex
@@
 %--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
-
-Our derivation of real space operators is more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
-We introduce a matrix that encodes spin spherical harmonic basis vectors,
-%
-\beq
-{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,%,
-\eeq
-%
-%where $s$ denotes the spin of the basis functions.
-We will be working with cases $s \in [0,2]$.
-Each column maps to a specific harmonic basis function (i.e.
-indexed by $\ell m$) and each row maps to a pixel on the sphere.
-This matrix is not square in general: the number of rows is determined by the pixelization and the number of columns is set by the number of basis functions (e.g.
-determined by the band limit).
-
-We now define the different polarization data vectors and their representation in real  space as and harmonic as follows,\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}
-%
-\beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
-\eeqrys
-%
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript ${\ell m}$ for the spherical harmonic coefficients is suppressed for cleaner notation.
-
-We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$):
-%
-\beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
-\eeqrys
-%
-The sign conventions we have chosen match HEALPix.
-Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
-%
-\begin{subequations} \label{eq:pol_data_relns}
-  %Kevin's version
-  \beqry
-  \bar{X} &= \bar T  \bar{P}; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} ; \\
-  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
-  \eeqry
-  Meanwhile the spherical harmonic transforms are written as:
-  \beqry
-  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\dagger}  \bar X  ; \\
-  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} \bar S \,.
-  \eeqry
-% Aditya's version
-%\beqry
-%\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-%\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
-%\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-%\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
-%\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {{}_0\mathcal{Y}}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-%\eeqry
-\end{subequations}
-%
-Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace,
-%
-\begin{subequations} \label{eq:har_eb_op}
-\beqry
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E  \tilde S ,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B  \tilde S .
-\eeqry
-\end{subequations}
-%
-Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
-%
-%\begin{subequations} \label{eq:har_op_prop}
-%\beqry
-%\tilde O_E  \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B  \tilde O_B= \tilde O_B \,,\\
-% \tilde O_E  \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
-% \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-%\eeqry
-%\end{subequations}
-%
-The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
-
-\subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
-%To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
-We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
-%
-\beqrys
-\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,. \label{eq:qu2eb_op}
-\eeqrys
-%
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations,
-%
-\beqrys
-\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
-&=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{T*}_q  +  {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{T*}_q + {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
-\eeqrys
-%
-where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-Note that here we purposefully introduce the notation of the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
-%
-\beq
- \left [\sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{+2}Y^*_{\ell m}(\hat{n}_q)\right]^* = \sum_{\ell m} {}_{0}Y_{\ell m}(\hat{n}_e){}_{-2}Y^*_{\ell m}(\hat{n}_q) \,,
- \eeq
- %
-where the terms on either side of the equation are those that appear in \eq{eq:qu2eb_ker_1}.
-Note that the operator $\bar{O}$ is real as one expects, since each sub-matrix in \eq{eq:qu2eb_ker_1} is formed by summing a complex number and its conjugate.
-
-\noindent \eq{eq:qu2eb_ker_1} already presents a real space operator, but it is not in a form which can be practically implemented.
-To arrive at a real space operator which is practially usable, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles\cite{varshalovich},
-%
-\beq \label{eq:sum_spin_shf}
- \sum_{m}{{}_{s_1}Y}^*_{\ell m}(\hat{n}_i)\,{{}_{s_2}Y}_{\ell m}(\hat{n}_j) = \sqrt{\frac{2\ell+1}{4 \pi}} {{}_{s_2}}Y_{\ell \,-s_1}(\beta_{ij},\alpha_{ij}) e^{- i s_2 \gamma_{ij}} \,,
-\eeq
-%
-where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ so as to allign the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
-The different parts of the real space operator $\bar{O}$  are completely specified by the complex function,
-%
-\begin{subequations}\label{eq:qu2eb_gen_kernel}
-\beqry
-\mathcal{M}( \hat{n}_e, \hat{n}_q)  &=& \mathcal{M}_{r} + i \mathcal{M}_{i}  \,,\nonumber \\ 
-&=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_e) \, {{_{-2}}Y}^*_{\ell m}(\hat n_q) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{qe},\alpha_{qe})\,,\\
-&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{qe}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
-\eeqry
-\end{subequations}
-%
-where we have used the identity in \eq{eq:sum_spin_shf} to simplify the product of the spherical harmonic functions.
-Note that the function on the right depends only on two out of the three Euler angles.
-Employing \eq{eq:qu2eb_gen_kernel} to simplify the product of spherical harmonic functions in \eq{eq:qu2eb_ker_1}, the real space operator $\bar{O}$ can now be cast in this more useful form,
-%
-\beq\label{eq:op_qu2eb_rad}
-\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
-\eeq
-%
-where, we reiterate, $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
-
-\textit{Radiating kernel:} Using \eq{eq:op_qu2eb_rad} in \eq{eq:qu2eb_op} one can see that the $E$/$B$ contribution of the Stokes parameters at some location $\hat{n}_q$ is given by the following expression,
-%
-\beq  \label{eq:qu2eb_radiation_explicit}
-\bar{S}_q = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
-\eeq
-%
-The total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
-This operation can be cast in a concise form as follows,
-%
-\begin{subequations} \label{eq:qu2eb_radiation_concise}
-\beqry 
-\left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
-&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{G}[\hat{n}_q] \,,
-\eeqry
-\end{subequations}
-%
-where ``$\cdot$'' denotes a simple scalar multiplication.
-$\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it can be thought of as the Green's function of the operator, since $[E +iB] = \mathcal{M}_{G}$ is the spin-0 scalar field generated from the Stokes charge $[Q+iU] = [\delta(\hat{n}-\hat{n}_q) + i 0]$.
-
-We denote the kernel expressed in terms of the Euler angle $\alpha$ as the radiating kernel, since it allows us to evaluate the $E/B$ field contribution across the sphere due to a single Stoke (charge) parameter at a fixed location on the sphere.
-The total $E/B$ maps can then be thought of as just superposed radiation emerging from Stokes charges across the sphere.
-In this formulation, one is effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field across the sphere.
-%
-\begin{figure}[!t]
-\centering
-\includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{The local cartesian coordinate are only drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
-The value of the scalar field at location `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle (sphere).
-The convolutions are performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-Alternatively, one can compute the contribution from the Stokes parameter at location `q' to all the point on the blue circle(sphere) and this is a function of the Euler angle $\alpha_{eq}$.
-In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
-\label{fig:planar_euler_angles}
-\end{figure}
-%
-
-\textit{Convolution kernel:} We can also formulate the real space operator to be a function of Euler angles corresponding to the inverse rotation.
-The Euler angles for the inverse rotations (i.e.
-to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$) are related to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
-Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
-The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows,
-%
-\beq \label{eq:qu2eb_convolution_explicit}
-\bmat E_e \\ B_e  \emat =- \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega\,,
-\eeq
-%
-%where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
-\revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere.
-This operation can be expressed more concisely as follows,
-%
-\begin{subequations} \label{q:qu2eb_convolution_concise}
-\beqry 
-[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
-&=& \Bigg\lbrace \mathcal{M}_{B} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
-\eeqry
-\end{subequations}
-%
-where $\circ$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{Evaluating Stokes parameters $Q$ \& $U$ from scalar fields $E$ \& $B$}\label{sec:eb2qu}
-The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure.
-Expressed in the matrix-vector notation, inverse operator is given by,
-%
-\begin{subequations}
-\beqry
-\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} \,,  \\
-&=&  \bar O^{-1} *\bar{S}\,.
-\eeqry
-\end{subequations}
-%
-%The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
-%%
-%\beq
-%\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
-%\eeq
-%%
-The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation,
-%
-\beq
-{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
-\eeq
-%
-where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}.
-Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb_rad} by a change in sign on the off-diagonals of the block matrix.
-When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by,
-%
-\beqry
-{}_{+2}X(\hat{n}_q) &=& \Bigg\lbrace \mathcal{M}^*_{G} \circ [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} \textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}\\
-{}_{+2}X(\hat{n}_q) &=&  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e}) \cdot  \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} \textrm{\emph{Radiation kernel}}\,,
-\eeqry
-%
-where all the symbols have the same meaning as defined in \sec{sec:qu2eb}.
-Note that the conjugated forms of the Green's function and the effective beam for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{Decomposing Stokes parameters $Q$ \& $U$  into those corresponding to $E$ \& $B$ modes respectively}
-We can only measure the total Stokes vector which is a sum of the Stokes vectors corresponding to the respective scalar modes.
-The $E$ \& $B$ modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
-It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
-In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes.
-Though the algebra is a little more involved, the derivation is similar to that discussed in \sec{sec:qu2eb}, hence we refrain from presenting the detailed calculations here, but outline the key points.
-We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
-The Stokes parameters corresponding to each scalar mode are given by the following expressions,
-%
-\beqry
-\bar{P}_E &=&  [\bar T^{-1} * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {{}_2\mathcal{Y}^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {{}_2\mathcal{Y}}* \tilde T* \tilde O_B* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
-\eeqry
-%
-We contract over all the matrix operators to arrive at the the real space operators. On working through the algebra it can be shown that the real space operators have the following form,
-%
-\beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm 0.5 \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \,,\\
-\eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
-%
-\begin{subequations}
-\beqry
-\mathcal{I} (\hat{n}_e,\hat{n}_q) &=& \mathcal{I}_{r} + i \mathcal{I}_{i} = \sum_{\ell m} {_{-2}Y}_{\ell m}(\hat n_e) {_{-2}Y}^*_{\ell m}(\hat n_q) \,, \\
-\mathcal{D}(\hat{n}_e,\hat{n}_q)  &=& \mathcal{D}_{r} + i\mathcal{D}_{i} = \sum_{\ell m} {_2Y}_{\ell m}(\hat n_e) {_{-2}Y}^*_{\ell m}(\hat n_q) \,.
-\eeqry
-\end{subequations}
-%
-These functions can be further simplified using the identity of spin spherical harmonics given in \eq{eq:sum_spin_shf}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
-%
-\beqrys \label{eq:fn_i}
-\mathcal{I}(\hat{n}_e, \hat{n}_q) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_{-2}Y}_{\ell2}(\beta_{qe}, \alpha_{qe}) ~ \rm{e}^{i2 \gamma_{qe}} \label{eq:healpix-compatible-i} = \mathcal{I}_r + i \mathcal{I}_i \,, \\
-\mathcal{I}_r + i \mathcal{I}_i &=& \Big [ \cos(2 \alpha_{qe} +  2\gamma_{qe}) + i \sin(2 \alpha_{qe} +  2 \gamma_{qe}) \Big]   {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-%
-\beqrys \label{eq:fn_d}
-\mathcal{D}(\hat{n}_q, \hat{n}_e) &=& \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{_2Y}_{\ell 2}(\beta_{qe}, \alpha_{qe}) ~ \rm{e}^{- i2 \gamma_{qe}} \label{eq:healpix-compatible-m} =\mathcal{D}_r + i \mathcal{D}_i \,, \\
-\mathcal{D}_r + i \mathcal{D}_i &=&  \Big [ \cos(2 \alpha_{qe} - 2\gamma_{qe}) + i \sin(2 \alpha_{qe} -  2 \gamma_{qe}) \Big]   {{}_{\md}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,,
-\eeqrys
-%
-where the radial functions are given by,
-%
-\beq
-{{}_{\mdi}f}(\beta,\ell_{\rm min},\ell_{\rm max}) = \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2\ell+1}{ 4 \pi}} {{}_{ \mdi}f}_{\ell}(\beta) \label{eq:f2_rad_ker}\,,
-\eeq
-%
-where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
- %
- \beqry
- _{\mdi}f_{\ell}(\beta) &=& 2 \frac{(\ell-2)!}{(\ell+2)!}  \sqrt{\frac{2\ell +1 }{4 \pi}} \Bigg[ - P_{\ell}^{2} (\cos  \beta) \left( \frac{\ell-4}{\sin^2 \beta} + \frac{1}{2}\ell(\ell-1) \pm \frac{2 (\ell-1) \cos \beta}{\sin^2 \beta} \right) \nonumber \\
-&+& P_{\ell-1}^2 (\cos \beta) \left( (\ell+2) \frac{\cos \beta}{\sin^2 \beta} \pm \frac{2 (\ell+2)}{ \sin^2 \beta } \right) \Bigg] \,. \label{eq:rad_ker_quequbqu}
- \eeqry
- %
-Finally the Stokes parameters corresponding to the respective scalar fields can be computed by evaluating the following expressions, 
- %
-\beqry \label{eq:op_qu2equbqu}
-\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
-\eeqry
-%
-where all the symbols have their usual meaning. The above expression can be cast in the further simplified form,
-%
-\beqry
-{}_{+2}X_{E/B}(\hat{n}_e) &=&0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q) \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
-&=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
-\eeqry
-%
-where we have suppressed the explicit multipole dependence of functions ${}_{\mdi}f$ for brevity. \revisit{Comment on the radiating and convolution form of the operators.}
-
-\comment{Recheck the math described below}
-The operator $\mathcal{I}$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$) for spin-2 fields.
-When interpreted as a matrix it is a band limited version of the identity matrix.
-Though it has non-vanishing off diagonal elements ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
-Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
-It is useful to note that the operator $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{I}$ is an Hermitian operator.
-Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
-%
-\begin{subequations}
-\beqry
-\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
-\bar O_E*\bar O_B &=& 0 \,,\\
-\bar O_E + \bar O_B &=& \mathcal{I} \,,
-\eeqry
-\end{subequations}
-%
-which are the real space analogues of \eq{eq:har_op_prop}.
-While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly cancel each other.
-
-Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix. 
-%\comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} 
-This non-exactness is representative of the loss of information resulting from making this transformation on the measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators, which is exact.

### 2018-05-01 articles/formalism/sections/real_space_formalism.tex
Pulled initial version of primer and heuristic argument into separate file.  Some additional editing.

@@
 
-Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}$ is invariant under rotations and must by definition be spin-0:
+Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}$ is invariant under rotations and must be spin-0 by definition:
 \beq
@@
 \eeq
-Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
+The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
+At the same time, the imaginary part of the function is constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
 Therefore we can make the association that contributions to  $(E+iB)(\hat n_e)$ must be proportional to $ {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$.
@@
 The same rotation $\mathcal{R}_{\hat{z}_q}(\phi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
-Thus we can conclude that the form of the real-space operation must be like:
+Thus we can conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the form
 \beq
-(E+iB)(\hat n_e) = \int d\hat n_q \  {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}
+{}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}
 \eeq
+for some real function $f$.
 Note that when the two locations coincide ($\beta_{qe}=0$) then  $\alpha_{qe}=0,2\pi,4\pi,\dots$, implying $E + iB \propto Q+iU$.
-This cannot be because $Q+iU$ does not transform as a spin-0 field under local rotations.
-A similar fallacy arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$.
-Therefore we must have function $f(\beta_{qe} = 0 ) = f(\beta_{qe} = \pi ) = 0$.
+This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, and so we must have $f(\beta_{qe} = 0 ) = 0$.
+A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$, and so $f(\beta_{qe} = \pi ) = 0$.
 Hence the $E/B$ fields are necessarily non-local.
@@
 
-The kernel's azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so it's harmonic transform has no multipole $\ell$ dependence.
+This type of construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
+transforming spin-0 fields to spin-2).
+
+The kernel's azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so its harmonic transform has no multipole $\ell$ dependence.
 The azimuthal part is the crucial operation that translates between different spin representation of CMB polarization.
-Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation between locations and hence must completely incorporate the multipole $\ell$ dependence.
+Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation between locations and hence must completely incorporate all the multipole $\ell$ dependence.
 
-Note that this type of construction can be generalized to transform fields of arbitrary spin to a field of any other spin, and so we can use it in the opposite sense to transform $E/B$ maps back to the Stokes parameters (i.e.
-transforming spin-0 fields to spin-2.)
+%--------------------------------------------------------
+\subsection{Standard $E$/$B$ fields and Matrix notation} \label{sec:mat_pol_intro}
 
 The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
-The spin-raising operator ($\eth$), when operated on a field of spin-s $_{s}f$, results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$  \cite{goldberg67}.
-The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
+The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
 The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
@@
 %The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
+The $\cal E/B$ fields are defined locally at point $\hat n$ in terms of the derivative operators $\eth$ and $\bar \eth$.
 
@@
 %
-Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$.
+These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$), and are not local functions of Stokes $Q,U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
-
-%--------------------------------------------------------
-%--------------------------------------------------------
-%\section{The spin-0 description of CMB polarization} \label{sec:pol-intro}
-%--------------------------------------------------------
-\section{Polarization primer}\label{sec:pol-primer}
-The CMB polarization is measured in terms of Stokes $Q$ and $U$ parameters.
-Stokes $Q$ is defined as the linear polarization measured along local cartesian axes ($+$ along the $x$-axis and $-$ along the $y$-axis) while Stokes $U$ is defined as the linear polarization measured along the cartesian axes rotated by $45^{\circ}$ ($+$ along x-axis and $-$ along the y-axis in the counter-clockwise rotated system).
-The Stokes parameters depend on the choice of the coordinate system and two different coordinate systems rotated by an angle $\psi$ relate as
-%
-\beq \label{eq:qu-rot}
-\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,.
-\eeq
-%
-%which one can simply checked by verifying that $Q' \rightarrow U$ and $U' \rightarrow -Q$ when the coordinate systems are rotated by $45^\circ$ in the counter-clockwise sense.
-
-Following the notation of \cite{Zaldarriaga1997}, fields which transform as
-%
-%\beq
-${}_{s}f' = e^{-is\psi} {}_{s}f $
-%\eeq
-%
-under right handed rotations of the local coordinate system are termed spin-$s$ fields. The Stokes parameters can be combined to define the complex fields,
-%
-\beq \label{eq:spin-pol}
-_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n}) \,, %\nonumber \\ &=& \sum_{\ell m}  {_{\pm 2}} \tilde{X}_{\ell m}  \, {_{\pm 2}}Y_{\ell m} (\hat{n}) \,.
-\eeq
-%
-which under rotation of the local tangent plane coordinate system by an angle $\psi$ at any point on the sphere transform as: $_{\pm 2}X' = e^{\mp i2\psi} {_{\pm 2}X}$, which follows directly from \eq{eq:qu-rot}.
-Therefore the quantities $_{\pm2}X$ are spin ${\pm2}$ fields respectively.
-
-The coordinate dependence of Stokes parameters make them inconvenient to work with.
-With operations that raise (or lower) the spin of the field, we can produce a spin-0 scalar that is coordinate independent.
-The spin-raising operator ($\eth$), when operated on a field of spin-s $_{s}f$, results in a fields with spin-$(s+1)$: $(\eth _{s}f)' = e^{-i(s+1)\psi}(\eth _{s}f)$  \cite{goldberg67}.
-The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}f)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}f)$.
-The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
-%
-\begin{subequations}\label{eq:ebdef}
-\beqry
-\mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\\
-\mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,.
-\eeqry
-\end{subequations}
-%
-%which by the virtue of being scalars are independent of coordinate definitions.
-%The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
-
-The complex field $_{\pm 2}X$ defined on the sphere can be decomposed in spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
-On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67},
-%
-\begin{subequations}\label{eq:spinopylm} 
-\beqry
-\eth _s Y_{lm}(\hat{n}) &=& \sqrt{(\ell-s)(\ell+s+1)} _{s+1} Y_{lm}(\hat{n}) \,, \\
-\bar{\eth} _s Y_{lm}(\hat{n}) &=& -\sqrt{(\ell+s)(\ell-s+1)} _{s-1} Y_{lm}(\hat{n}) \,, 
-\eeqry
-\end{subequations}
-%
-where $_s Y_{lm}(\hat{n}) $ denote the spin-s spherical harmonics.
-
-Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
-%
-\beq \label{eq:pseudo}
-\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
-\eeq
-%
-where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
-%
-\beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
-\eeq
-%
-In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
-%
-\beq \label{eq:realeb}
-E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
-\eeq
-%
-Note that these $E/B$ fields are merely filtered versions of $\mathcal{E}/\mathcal{B}$ as their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$.
-%We make this choice since the CMB spectra are more closely related to the fields E \& B.
-%--------------------------------------------------------
-%--------------------------------------------------------
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Real space operators} \label{sec:real_space_operators}
-The vector-matrix notation introduced in  \sec{sec:mat_pol_intro} allows for concise book keeping of all the operations involved in the analysis of CMB polarization.
-In this section we use this notation to derive the real space operators which translate the Stokes vector \vp{}  to the vector of scalars \vs  and vice versa.
-This vector-matrix notation also allows us to simply derive real space operators for direct decomposition of the Stokes vector \vp{} in to a vector \vp{ E} that correspond to $E$-modes and another vector \vp{B} that corresponds to the $B$-modes of polarization, such that \vp{} = \vp{E} + \vp{B}, without ever evaluating the $E$ \& $B$ fields or their spherical harmonics.
-All the real space operators we derive are most conveniently expressed as functions of the Euler angles  $\alpha, ~\beta~\&~ \gamma$ on the sphere.
-Owing to this, we begin with a brief discussion on Euler angles and \revisit{present a visual method to think about them.}
-%
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=0.5\columnwidth]{euler.pdf}
-\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
-The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
-The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
-\label{fig:euler_angles}
-\end{figure}
-%
-
-\textit{Euler angles:}  We define the local cartesian coordinate system at any point on the sphere such that the z-axis points along the radial direction, the x-axis is along the vector tangent to the local longitude pointing south and the y-axis is a vector tangent to the local latitude pointing east as shown in \fig{fig:euler_angles}.
-The Euler angles $\alpha ,\beta ~\&~ \gamma$ define rotation operations that transforms the local cartesian coordinate system defined at the location $\hat{n}_q \equiv (\theta_q,\phi_q)$ such that it aligns with the local cartesian coordinate system at the location $\hat{n}_e \equiv (\theta_e,\phi_e)$ \cite{varshalovich}.
-
-For this work, it is convenient to think in the z-y1-z2 convention therefore all future references to Euler angles are in this convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y1-z2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y1-z2}$ \cite{varshalovich}.}.
-In the z-y1-z2 convention, $\alpha$ defines the rotation about the z-axis, $\beta$ defines the rotation about the new y-axis (y1-axis) after the previous rotation and $\gamma$ defines the rotation about the final z-axis (z2-axis) after carrying out the previous two rotations.
-These angles can be understood as follows: The rotation by $\alpha$ about the original z-axis is such that it aligns the x-axis of the cartesian system at location $\hat{n}_q$ along the great circle in the direction \revisit{of shortest arc length} towards $\hat{n}_e$.
-The rotation by $\beta$ about the y2-axis parallel transports the local cartesian coordinate system from location $\hat{n}_q$ to location $\hat{n}_e$, such that the z-axes of the two coordinate systems are parallel to each other.
-Finally the rotation by angle $\gamma$ about the z2-axis aligns the x \& y axes of the parallel transported system with those of the local cartesian system defined at $\hat{n}_e$.
-The different Euler angles and the corresponding rotations are schematically represented in \fig{fig:euler_angles}.
-
-The simplest scenario is when one of the coordinates coincides with the north pole $\hat{n}_q=(\theta_q,\phi_q)=(0,0)$ (the local cartesian system at this point being defined with an arbitrary convention set by choosing $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$), in which case it is easy to see that rotations by Euler angles: $(\alpha,\beta,\gamma) =(\phi_e,\theta_e,0)$ will align the cartesian system at $\hat{n}_q$ with that defined at position $\hat{n}_e$.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{A heuristic argument for constructing  $E/B$ modes from Stokes parameters $Q/U$ on the sphere} \label{sec:qu2eb_heuristic}
-The primary aim here is to make intuitive the construction of the spin-0 $E/B$ modes of polarization from the Stokes parameters.
-We present heuristic arguments which allows us to derive the important features of the real space kernels\footnote{These heuristic arguments were developed in hindsight but are very instructive.}.
-
-If one rotates the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes charge in the new coordinate system is related to the Stokes charge in the original coordinate system as: ${}_{+2}X'(\hat{n}_q) \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
-Similarly if the local planar axes are rotated by an angle $\phi$ then the Euler angle $\alpha_{qe}$ (recall that this Euler angle aligns the x-axis at $\hat{n}_q$ in the direction of the shortest path along the geodesic to the location $\hat{n}_e$) for the new coordinate system is given by: $\alpha'_{qe} \rightarrow \alpha_{qe} - \phi$ and therefore one can see that: $e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} e^{-i2\alpha_{qe}} e^{i2\phi}$.
-The Euler angles $|\beta_{qe}|$ which measure the angular distance between pixels remains unaltered under this local rotation operation.
-Given these transformation properties note that: ${}_{+2}X'(\hat{n}_q)e^{-i2\alpha'_{qe}} \xrightarrow{\mathcal{R}_{\hat{z}_q}(\phi)} {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$ is invariant under rotations  $\mathcal{R}_{\hat{z}_q}(\phi)$ and hence by definition must form a spin-0 field.
-Now note that the real part of the function are constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity while the imaginary part of the function are constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
-Therefore we can make the association: $E'+iB' \propto {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$
-
-Now note that when the two locations coincide $\hat{n}_q = \hat{n}_e$ then  $\alpha_{qe}=0,2\pi,4\pi,\cdots$ implying $E + iB \propto Q+iU$, which is a fallacy as we know that $Q+iU$ does not transform as a spin-0 field under local rotations.
-One runs into a similar fallacy when the two locations are diametrically opposite.
-Therefore to have a consistent definition of a spin-0 field constructed from a spin-2 field we require the kernel to have the form: $E'+iB' = {}_{+2}X(\hat{n}_q) f(\beta_{qe})  e^{-i2\alpha_{qe}}$, where the function $f(\beta_{qe})$ is such that it vanishes when the two locations are coincident$(\beta_{qe}=0)$ or diametrically opposite$(\beta_{qe}=\pi)$.
-Hence the $E/B$ fields are necessarily non-local.
-Note that this construction can be generalized to transform fields of arbitrary spin to a field of any other spin, one obvious case being constructing the Stokes field given the $E/B$ maps (i.e.
-deriving spin-2 fields from spin-0 fields.)
-
-The azimuthal part which depends only on the Euler angle $\alpha_{qe}$, has no multipole $\ell$ dependence and is the crucial operation which translates between the different spin representation of CMB polarization.
-Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation $|\beta_{qe}|$ between different locations on the sphere and hence must completely incorporate the multipole $\ell$ dependence of the kernel.
-These heuristic arguments cannot take us any further and we now shift to presenting a mathematically rigorous derivation of the real space operators in the following sections.
-%--------------------------------------------------------
-
-%--------------------------------------------------------
-\subsection{Matrix notation} \label{sec:mat_pol_intro}
 

### 2018-05-07 articles/formalism/sections/generalizedeb.tex
added new notebooks, revised sections and new figures

@@
 %--------------------------------------------------------
-\section{Generalized operators}
+\subsubsection{Generalized operators}
 In this section we present a systematic method to generalize the real space operators that translate been $Q/U$ and $E/B$ description of CMB polarization.
-The azimuthal part of the real space kernels is constrained to be of the form $e^{-i2 \alpha}$.
+The azimuthal part of the real space kernels is constrained to be of the form $\sim e^{\pm i2 \alpha}$.
 The shape of the radial part of the operator is determined by the basis functions and varies as a function of the multipoles included in the summation.
@@
 where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for $E$ and $B$ modes.
-To simplify the discussion and without loosing generality we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
-Once we have made a choice for this harmonic function, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
+To simplify discussions and without loosing generality we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
+Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
 %
@@
 where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
-If we require both the forward and inverse operators to be well defined, then we are constrained in choosing $\tilde{\mathcal{G}}$ such that it has a valid  inverse.
-As we will see this will be an important criteria to recover the standard CMB spectra.
+Requiring both the forward and inverse operators to be well defined, constrains the choice of $\tilde{\mathcal{G}}$ to be such that it has a valid  inverse.
+This is an important criteria to recover the standard CMB spectra.
 The radial parts of this generalized operator and its inverse are given by the following expressions,
 %
-\begin{subequations}
+\begin{subequations}\label{eq:generalized_radial_kernel}
 \beqry 
-G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \\
-G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,,\label{eq:mod_rad_inverse}
+G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \,, \\
+G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,.
+\label{eq:mod_rad_inverse}
 \eeqry
@@
 %
-where $g_{\ell}$ is the harmonic space function used in defining $\tilde{\mathcal{G}}$.
-Given this general definition for the radial function $G(\beta)$, note that the default radial function ${{}_{\mm}f}$ is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$).
-Note that for this choice of $\tilde{\mathcal{G}}$ the inverse is trivial $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)$.
+The default radial function is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$), in which case $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)={{}_{\mm}f}$.
 
-While defining these generalized operators, it seems more natural to choose the real space function $G(\beta)$ as compared to choosing the multipole function $g_{\ell}$.
-Using the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the following integral over the radial function $G(\beta)$,
+While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
+Employing the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the expression,
 %
@@
 %
-Here it is important to note that the radial function $G(\beta)$ has to be necessarily chosen such that it vanishes at $\beta=0$ and $\beta=\pi$ in order to ensure that the resultant field has the required spin properties.
-%One way to understand this is that the associated Legendre polynomials $P_{\ell}^2 \propto \sin^2{\beta}$ vanish at these values of the abscissa and hence cannot be used to describe functions which don't have this property.
-Another way to understand this requirements is that at these locations the coordinate dependence of the Stokes parameters cannot be integrated out, since the azimuthal angle is ill defined and hence the convolution kernel needs to have vanishing contribution from these locations.
-\revisit{The normalization of these functions is not critically important, since any choice defines a convention.
-It is important to ensure consistency with the convention once a choice has been made.} \comment{find a better location for this}
 
-An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B mode fields being convolved with some effective circularly symmetric instrument beam.
-The radial profile of this effective beam is given by,
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B fields being convolved with some effective circularly symmetric instrument beam whose radial profile is given by the expression,
 %
 \beq
-B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,.
+B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
 \eeq
 %
-Note that in contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has important differences, in harmonic space they play identical roles.
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
+In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has these differences, in harmonic space they play identical roles.
 %
@@
 
-\subsection{Relation to the spin raising$(\eth^2)$/lowering$(\bar{\eth}^2)$ operations}
-Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of the E/B mode maps as in \eq{eq:ebdef}.
-Now note that we can construct similarly filtered $E/B$ mode maps by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$.
-It can be shown that real space operator takes the following form,
-%
-\beq
-[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
-\eeq
-%
-Therefore the band limited version of the spin lowering operations is given by,
-%
-\beq
-\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}
-\eeq
-%
-The band limited version of the spin raising operations is given by merely by the conjugate $(\bar{\eth}^2)^*$.
+%--------------------------------------------------------
 \subsection{Recovering the default $E$ and $B$ mode spectra}
@@
 %
-which as we show are mere filtered version of he standard $E$ and $B$ modes maps.
-The harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam $B(\beta) = \sum_{\ell} \frac{2 \ell+1}{4 \pi} g_{\ell} P^0_{\ell}(\cos{\beta})$.
-The spectra of the scalar fields $E'$ and $B'$ derived using the real space operators constructed using an arbitrary radial function $G(\beta)$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
+which are merely filtered version of he standard $E$ and $B$ modes maps.
+Since the harmonic functions $g_{\ell}$ of the modified radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam, the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %
@@
  where $C_{\ell}$ denotes the angular power spectra and $T$ refers to the temperature anisotropy map.
-Therefore the standard $E$ and $B$ mode spectra can be recovered from the modified fields $E'$ and $B'$ and their accurate recovery only relies on the inverse of the harmonic functions $1/g_{\ell}$ being well behaved, which can be ensured by making a suitable choice for the radial function $G(\beta)$.
-Examples of various forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
+Therefore the standard CMB spectra can be always recovered as long as the $1/g_{\ell}$ is well behaved, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
+Some examples forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
 %One direct application of this freedom in choosing the radial kernel is that one can mitigate the issue of leakage of power from $E$ to $B$.
@@
 %--------------------------------------------------------
+
 %--------------------------------------------------------
+\subsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
+Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of the $E$ and $B$ mode maps as in \eq{eq:ebdef}.
+We can construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E$ and $B$ mode maps as follows,
+%
+\beq
+[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
+\label{eq:bl_ebdef_lower}
+\eeq
+%
+Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} allows us to map the following mapping,
+%
+\beq
+\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,.
+\eeq
+%
+Here it is important to the operator $\bar{\eth}^2$ is composed of derivatives and hence has an implicit bi-positional dependence for all practical purposes which is made explicit in the band limited version of the operator.
+The band limited version of the spin raising operator $\eth^2$ is derived by merely taking the conjugate of the above equation.
+%--------------------------------------------------------

### 2018-05-07 articles/formalism/sections/kernel_discussion.tex
added new notebooks, revised sections and new figures

@@
-\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
+\subsection{Visualizing the real space kernels} \label{sec:visualize_operator}
 %
@@
 \subfigure[$\textrm{Img} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
-\caption{This panel of figure depicts the various parts of the convolution kernel, discussed in \sec{sec:real_space_operators}.
-These kernels have been evaluated with the band limit: $\ell \in [2,192]$ but sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal.
+\caption{This panel of figure depicts the real and imaginary parts of the real space kernels $\mathcal{M}_{G}$, $\mathcal{M}_{B}$, $\mathcal{D}$ \& $\mathcal{I}$ respectively.
+These kernels have been evaluated with the band limit: $\ell \in [2,192]$ and sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal.
 The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations.
-The black circles denotes the position of the central pixel around which the convolution kernels have been evaluated while the black star marks the location of the north galactic pole.
+The black circles denotes the position of the center around which the kernels have been evaluated while the black star marks the location of the north galactic pole.
 The four rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.}
@@
 
-\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole $\hat{z}=(0,0)$ (this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$).
+%\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole $\hat{z}=(0,0)$ (this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$).
 In this case the Euler angles in the $z-y1-z2$ convention are simply given by: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$, where $(\theta_i,\phi_i)$ denote the coordinates of the location $\hat{n}_i$.} Since the Euler angle $\gamma=0$ when rotations are defined with respect to the pole, the respective kernels simplify to the following forms,
-%
-\begin{subequations}
-\beqry 
-\mathcal{M}(\hat{z},\hat{n}_i) &=&  \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\hat{n}_i) \,;\\
-\mathcal{I}(\hat{z},\hat{n}_i) &=& \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\hat{n}_i) ~~\,;~~
-\mathcal{D}(\hat{z},\hat{n}_i) =\sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\hat{n}_i) \,,
-\eeqry
-\end{subequations}
-%
-where ${}_{s}a_{\ell 2} = \sqrt{\frac{2 \ell+1}{ 4 \pi}} ~~\forall ~~ s \in [0,-2,+2]$.
-The convolution kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums: $\sum_{\ell m} {}_{s}a_{\ell m}\,{}_{s}Y_{\ell m}(\hat{n}_i)$ using the rotated harmonic coefficients given by: ${}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2}$, where $D^{\ell}_{2 m}$ are the Wigner-D functions.
-These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
-\comment{Make parallels with instrument beam analysis here ? Or is it trivial since its obvious that all convolution problems can be cast in this form.}
+%%
+%\begin{subequations}
+%\beqry 
+%\mathcal{M}(\hat{z},\hat{n}_i) &=&  \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\hat{n}_i) \,;\\
+%\mathcal{I}(\hat{z},\hat{n}_i) &=& \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\hat{n}_i) ~~\,;~~
+%\mathcal{D}(\hat{z},\hat{n}_i) =\sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\hat{n}_i) \,,
+%\eeqry
+%\end{subequations}
+%%
+%where ${}_{s}a_{\ell 2} = \sqrt{\frac{2 \ell+1}{ 4 \pi}} ~~\forall ~~ s \in [0,-2,+2]$.
+%The convolution kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums: $\sum_{\ell m} {}_{s}a_{\ell m}\,{}_{s}Y_{\ell m}(\hat{n}_i)$ using the rotated harmonic coefficients given by: ${}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2}$, where $D^{\ell}_{2 m}$ are the Wigner-D functions.
+%These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
+%\comment{Make parallels with instrument beam analysis here ? Or is it trivial since its obvious that all convolution problems can be cast in this form.}
 
-We compute the local convolution kernels using the procedure described above.
-To given an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the kernels at a few different locations.
+We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and the radiating kernels.
+To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
 For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
-All the plots have been rotated such that the central location $\hat{n}_j$ marked by the black circle are in the centre of the figure.
+All the plots have been rotated such that the central location marked by the black circle are in the centre of the figure.
 The horizontal and vertical lines that pass through the central black circle mark the local latitude and longitude respectively.
 
-The real and imaginary part of the kernel $\mathcal{M}$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
+The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
+This is consistent with the Green's function interpretation of these kernels.
 Note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
@@
 %
-\fig{fig:mixing_kernel} and the surrounding discussion provides a quantative understanding of the  azimuthal dependence of various kernels, however it is difficult to assess the radial nature of these kernels from these figures.
-The radial part determines the non-locality of the respective operators and encodes all the multipole dependence.
-We compute the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ by evaluating the respective multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.
+In the previous section we presented a quantitative understanding of the  azimuthal dependence of the real space kernels, providing little insight into their radial dependence.
+The radial part of these kernels determines the non-locality of the respective operators and encodes all their multipole dependencies.
+For illustration the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ are evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.
 %
@@
 \subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
-\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and different $\ell_{\rm max}$ as indicated by their legends.
-All the curves have been normalized such that the maximum of the curve is set to unity.
-The horizontal solid black line marks the location where the amplitude of the kernel falls below 1\% of its maximum.
-The slanted dashed black lines indicate a power law fit (by eye) to the envelope of the radial functions.
-While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
+\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
+All the curves are normalized such that their maxima is set to unity.
+The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum.
+The slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
+The black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0=min(180,180 \frac{24}{\ell_{\rm max}})$.}
+%While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
 \label{fig:rad_ker_decay}
@@
 %
-Recall that ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa.
-Note that ${_{\mm}f}$ has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$) as seen in \fig{fig:beta_kernel} and one can show that that ${_{\mm}f(\beta=\pi)}=0$.
-The coordinate dependence of the Stokes parameters cannot be integrated out in the vicinity of the locations $\beta=0,\pi$ due to the fact that the azimuthal angles become ill defined here therefore this nature of ${_{\mm}f}$ is necessary to ensure that the derived fields behave as scalars.
-Similarly while deriving the Stoke field from the scalars $E$ \& $B$ this nature of ${_{\mm}f}$ is necessary to ensure that the necessary coordinate dependencies are integrated in.
-${_{\md}f}$ shows a similar behaviour, it has a vanishing contribution in the vicinity of the central pixel and dominantly contributes in regions which are approximately at least 1 pixel distance away from the central pixel as seen in \fig{fig:beta_kernel}.
-${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly contributes the most at the location of the central pixel.
 
-\noindent \textit{The band limit dependence:} It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions.
+${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa and it has a vanishing contribution from the regions where ($\beta \rightarrow 0$) and from regions ($\beta \rightarrow \pi$) as seen in \fig{fig:beta_kernel}.
+This can be understood as arising from the fact that the coordinate dependence of the Stokes parameters cannot uniquely integrated out since the Euler angles $\alpha$ \& $\gamma$ are not uniquely defined at the locations $\beta=0,\pi$.
+This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
+
+\revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
+${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
+The main take away from these observations of the nature of the radial part of the kernel is that the real space operators which decompose the Stokes parameters into parts that correspond to E and B modes are necessarily non-local.}\\ \linebreak
+\noindent \textit{The band limit dependence:} 
+%It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. 
 We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis.
@@
 The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity.
-We note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distance from the central pixel.
 The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$.
-At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$, the details of this fit can be seen in \fig{fig:rad_ker_decay}.
-We observe that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow an interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+Note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
+At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
+In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
 %We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
@@
 
-It is useful to define a characteristic radius of the region from which the scalar fields evaluated at a point get most of their contribution from.
-Since the primarily interest is in the non-locality of the scalar modes $E$ \& $B$ we define the abscissa at which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
-For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima.
+It is useful to define a characteristic radius of the region from which the resultant fields evaluated at any location get most of their contribution.
+Our primary interest is in quantifying the non-locality of the scalar modes $E$ \& $B$, therefore we define the abscissa at which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
+%For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}.
 Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
+The simple empirical derived relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
+This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.

### 2018-05-07 articles/formalism/sections/real_space_formalism.tex
added new notebooks, revised sections and new figures

--- 2018-04-11 articles/formalism/sections/real_space_formalism.tex
@@
-\section{Real space polarization operators}
-\textit{Alternative for bringing the heuristic argument earlier.}
+%\section{Real space polarization operators}
+\section{Polarization primer}
+%\textit{Alternative for bringing the heuristic argument earlier.}
 
@@
 \eeq
-Because the combination $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$, the Stokes parameters are components of a spin-2 field \cite{Zaldarriaga1997}.
+Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
 
-The standard construction of $E/B$ fields arise from the desire to have a coordinate independent description of the polarization and follow from operations that raise (or lower) the spin of the $X$ field to construct scalar fields.
-But from the transform properties of the Stokes parameters, we can already make a heuristic argument for what these operations must look like in real space.
+The standard construction of $E$ and $B$ fields arise from the desire to have a coordinate independent description of the polarization.
+This follows from operations that raise (or lower) the spin of the $X$ field to construct scalar fields.
+But from the transform properties of the Stokes parameters, we can already construct a heuristic argument for what these operations must look like in real space.
 
 We consider the contribution from the polarization field (evaluated at $\hat n_q$) to a scalar field (evaluated at $\hat n_e$).
-Figure \ref{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$, and a rotation around $\hat n_q$ by $-\gamma$.
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$, and a rotation around $\hat n_q$ by $-\gamma$.
 This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}.
@@
 \beqry
-\mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\\
+\mathcal{E}(\hat{n}) + i \mathcal{B}(\hat{n}) &=& -\bar{\eth}^2 _{+ 2}\bar{X}(\hat{n}) \,,\label{eq:ebdef_lower}\\
 \mathcal{E}(\hat{n}) - i \mathcal{B}(\hat{n}) &=& -{\eth}^2 _{-2}\bar{X}(\hat{n}) \,.

### 2018-05-07 codes/modules_v2/rs_rad_ker.py

@@ -125,3 +125,5 @@ def get_beam_form_bl(theta,bl):
 	beam=lgdr.legval(np.cos(theta),((2.*ell+1.)/(4.*np.pi))*bl,tensor=False)
 	return beam
 
+def get_beta0(lmax):
+    return np.min(180.,180.*22./lmax)*np.pi/180.

### 2018-05-07 articles/formalism/sections/generalizedeb.tex
updated figures, table of contents

@@
 \subsubsection{Generalized operators}
-In this section we present a systematic method to generalize the real space operators that translate been $Q/U$ and $E/B$ description of CMB polarization.
+In this section we present a systematic method to generalize the real space operators that translate between $Q/U$ and $E/B$ description of CMB polarization.
 The azimuthal part of the real space kernels is constrained to be of the form $\sim e^{\pm i2 \alpha}$.
-The shape of the radial part of the operator is determined by the basis functions and varies as a function of the multipoles included in the summation.
+The shape of the radial part of the operator is determined by the basis functions and varies as a function of the band limit.
 It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
@@
 where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
-Requiring both the forward and inverse operators to be well defined, constrains the choice of $\tilde{\mathcal{G}}$ to be such that it has a valid  inverse.
+Requiring both the forward and inverse operators to be well defined constrains the choice of $\tilde{\mathcal{G}}$ to be such that it has a valid  inverse.
 This is an important criteria to recover the standard CMB spectra.
@@
 \subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
-\caption{\textit{Left:} The vertical dashed gray line depicts the approximate pixel size $\Delta_{\rm pix} = \sqrt{\frac{4 \pi}{N_{\rm pix}}}$ of a Nside=512 Healpix map.
-The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}.
-The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arcminutes respectively.
-The red curve depicts an example modified radial function: $G(\beta)=\mathcal{N} \beta^n \exp{\left[ -\left( \frac{\beta-\beta0}{\sqrt{2} \sigma} \right)^s \right]}$ with parameters set to the following values $[n=1;\, \beta_0=0 ;\, \sigma = 2\Delta_{\rm pix} ;\, s=1.5]$.
-The black dashed curve depicts the band limited reconstruction of the modified radial function $G(\beta)$.
-We intentionally have plotted $\beta G(\beta)$ to clearly depict the high $\beta$ behavior of these functions.
-\textit{Middle: } This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
+\caption{\textit{Top left:} The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}, multiplied by an apodized step function $\theta(3 \beta_0)$.
+The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arc-minutes respectively.
+The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( \frac{\beta-\beta_s}{\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
+The black dashed curve depicts the band limited reconstruction of the modified radial function.
+\textit{Top right:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
 The dashed curves of the corresponding color depict the inverse of the harmonic functions.
-\textit{Right:} This figure depicts the beam function $B(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an instrument beam.}
+\textit{Bottom:} This figure depicts the normalized beam function $B(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.}
 \label{fig:example_gbeta}
@@
  Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
-\fig{fig:glbl} depicts the harmonic functions $g_{\ell} (b_{\ell})$ for the respective radial kernel and beams.
+\fig{fig:glbl} depicts the harmonic functions $g_{\ell}$ for the respective radial kernel and beams.
 The modified radial kernel resulting from Gaussian beams with ${\rm fwhm} =15' \,\&\, 12'$ are depicted in \fig{fig:bl_gbeta} as blue and orange curves respectively.
@@
 The red curve depicts a modified radial kernel which by construction has a very small $\beta_0$.
-Similarly it is possible to interpret the harmonic representation $g_{\ell}$ of the radial function $G(\beta)$ as those corresponding to some instrument beam function.
-The beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of the delta function depicted by the green curve \fig{fig:gl_bbeta}, while the red curve depicts the same for the modified radial kernel.
+Note that the beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of the delta function beam.
+\fig{fig:gl_bbeta} depicts the radial profile of the  effective beams corresponding to the different radial kernels.
 
@@
 %--------------------------------------------------------
-\subsection{Recovering the default $E$ and $B$ mode spectra}
+\subsubsection{Recovering the default $E$ and $B$ mode spectra}
 The generalized convolution kernels defined in the previous section, when operated on the Stokes vector returns some scalar $E'$ and $B'$ mode maps,
@@
  where $C_{\ell}$ denotes the angular power spectra and $T$ refers to the temperature anisotropy map.
-Therefore the standard CMB spectra can be always recovered as long as the $1/g_{\ell}$ is well behaved, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
+Therefore the standard CMB spectra can be always recovered as long as the $1/g_{\ell}$ \& $1/g_{\ell}^2$ are well behaved functions, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
 Some examples forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
@@
 %--------------------------------------------------------
-\subsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
-Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of the $E$ and $B$ mode maps as in \eq{eq:ebdef}.
-We can construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E$ and $B$ mode maps as follows,
+\subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
+Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
+We can construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows,
 %
@@
 %
-Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} allows us to map the following mapping,
+Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping,
 %
@@
 %
-Here it is important to the operator $\bar{\eth}^2$ is composed of derivatives and hence has an implicit bi-positional dependence for all practical purposes which is made explicit in the band limited version of the operator.
+The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit bi-positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
 The band limited version of the spin raising operator $\eth^2$ is derived by merely taking the conjugate of the above equation.

### 2018-05-07 articles/formalism/sections/kernel_discussion.tex
updated figures, table of contents

@@
 To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
-For illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
+While the kernels are evaluated in the band limit $\ell \in [2,192]$, for illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
 All the plots have been rotated such that the central location marked by the black circle are in the centre of the figure.
@@
 Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is similar to $\mathcal{M}_r$ and $\mathcal{M}_i$ respectively.
-This also explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
-On moving to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
+This explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
+On transiting to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
 This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} =1 + i0$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
+%\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
+\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
 %
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
+\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
 \caption{The figure depicts the radial part of the convolution kernels.
@@
 \centering
-\subfigure{\includegraphics[width=0.96\columnwidth]{kernel/f_rad_ker_fn_of_ellmax.pdf}}
-\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fm2_rad_ker_fn_of_ellmax.pdf}}
-\subfigure{\includegraphics[width=0.48\columnwidth]{kernel/fp2_rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
+\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
 \caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
@@
 The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum.
-The slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
-The black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0=min(180,180 \frac{24}{\ell_{\rm max}})$.}
+The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
+The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0=min(180,180 \frac{22}{\ell_{\rm max}})$.}
 %While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
@@
 
-It is useful to define a characteristic radius of the region from which the resultant fields evaluated at any location get most of their contribution.
+It is useful to define a characteristic radius of the region from which the evaluated resultant fields get most of their contribution.
 Our primary interest is in quantifying the non-locality of the scalar modes $E$ \& $B$, therefore we define the abscissa at which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
@@
 Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
-The simple empirical derived relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$ provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
+The simple empirical derived relation: $\beta_o= {\rm min}(180,180 \frac{22}{\ell_{\rm max}})$ provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
 This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.

### 2018-05-07 articles/formalism/sections/real_space_formalism.tex
updated figures, table of contents

@@
-%\section{Real space polarization operators}
 \section{Polarization primer}
+\subsection{A heuristic argument for constructing $E/B$ fields on the sphere}
+\comment{Need a better title for the section that gives the heuristic argument}
 %\textit{Alternative for bringing the heuristic argument earlier.}
@@
 %--------------------------------------------------------
-\subsection{Standard $E$/$B$ fields and Matrix notation} \label{sec:mat_pol_intro}
+\subsection{Standard $E$/$B$ fields} \label{sec:mat_pol_intro}
 
@@
 
+\section{Real space polarization operators}
+\subsection{Matrix notation} \label{sec:mat_pol_intro}
 Our derivation of real space operators is more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}

### 2018-05-08 articles/formalism/sections/kernel_discussion.tex
updated kernel figures and the updated text to indicate the correct mapping between kernels and their Q/U and E/B interpretation

@@
 \subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Img} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Img} \left(\mathcal{M}_{B} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Im} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Im} \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
 \subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Img} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Im} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
 \subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Img} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
+\subfigure[$\textrm{Im} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
 \caption{This panel of figure depicts the real and imaginary parts of the real space kernels $\mathcal{M}_{G}$, $\mathcal{M}_{B}$, $\mathcal{D}$ \& $\mathcal{I}$ respectively.
@@
 
-We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and the radiating kernels.
+We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and radiation kernels.
 To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
@@
 \beqry
-\bmat E= -\mathcal{M}_r \\ B =+\mathcal{M}_i  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_j)\\ U=0 \emat ~~;~~ \bmat E= -\mathcal{M}_i \\ B = - \mathcal{M}_r  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_j) \emat \,,  \\
-\bmat Q= -\mathcal{M}_r \\ U = -\mathcal{M}_i  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_j)\\ B=0 \emat ~~;~~ \bmat Q= +\mathcal{M}_i \\ U = - \mathcal{M}_r  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_j) \emat \,.
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat ~;~ \bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat ~;~ \bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
 \eeqry

### 2018-05-08 articles/formalism/sections/real_space_formalism.tex
updated kernel figures and the updated text to indicate the correct mapping between kernels and their Q/U and E/B interpretation

@@
 %
+\begin{subequations}
 \beqry
 {}_{+2}X_{E/B}(\hat{n}_e) &=&0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q) \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
-&=& 0.5 \Bigg\lbrace \mathcal{I}^* \circ {}_{+2}X\pm \mathcal{D} \circ {}_{+2}X^* \Bigg\rbrace \,, \label{eq:qu2equbqu_convolution}
+&=& 0.5 \Bigg\lbrace  {}_{+2}X \cdot \mathcal{I}^*_G \pm {}_{+2}X^* \cdot \mathcal{D}_G \Bigg\rbrace \hspace{.5cm }\textrm{\emph{   Radiation kernel}} \,, \\
+&=& 0.5 \Bigg\lbrace \mathcal{I}_B \circ {}_{+2}X\pm \mathcal{D}_B \circ {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
 \eeqry
+\begin{subequations}
 %
-where we have suppressed the explicit multipole dependence of functions ${}_{\mdi}f$ for brevity. \revisit{Comment on the radiating and convolution form of the operators.}
+where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity.
+Note that when the operators $\mathcal{I}^*$ \& $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ \& $\mathcal{D}_G$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ \& $\mathcal{D}_B$.
+Note that unlike in the case of the operators $\mm_G$ \& $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ \& $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ \& $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 
-\comment{Recheck the math described below}
-The operator $\mathcal{I}$ is a band limited version of the delta function ($\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$) for spin-2 fields.
-When interpreted as a matrix it is a band limited version of the identity matrix.
-Though it has non-vanishing off diagonal elements ($\mathcal{I} \neq 0 $ when $\hat{n}_i \neq \hat{n}_j$) owing to the band limit, for all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
-Also $\mathcal{D}^*$ is the inverse of $\mathcal{D}$ in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
-It is useful to note that the operator $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{I}$ is an Hermitian operator.
+The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
+For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
+$\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
 Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
@@
 which are the real space analogues of \eq{eq:har_op_prop}.
-While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted, but they always occur in pairs with opposite signs, hence exactly cancel each other.
+\footnote{While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}
 
-Note that unlike in the harmonic case, the sum of the operators is not exactly an identity matrix. 
-%\comment{Isn't it possible to do some real space operations which doesn't care for the band limit but still returns the required decomposition into the respective scalar modes ?} 
+Note that unlike in the harmonic case, the sum of the operators is the band limited identity operator $\mathcal{I}$.
 This non-exactness is representative of the loss of information resulting from making this transformation on the measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators, which is exact.
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact and a more crucial property of the operators.

### 2018-05-08 codes/modules_v2/return_kernels.py

@@ -3,54 +3,89 @@ import numpy as np
 import euler as euler
 from scipy.interpolate import interp1d
 
-def return_qu2eb_kernel_convolve(nside,lon,lat,theta_cutoff,theta,rad_ker):
+
+def return_qu2eb_kernel_radiate(nside,lon,lat,theta_cutoff,theta,rad_ker,normalize=False):
     fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
-    cpix=h.ang2pix(nside,lon,lat,lonlat=True)
+    npix=h.nside2npix(nside) 
 
-    beta,alpha,gamma,spix=euler.return_euler_angles(nside,cpix,theta_cutoff,inclusive=False,fact=4)
-
-    gbeta=fn_rad_ker(beta)
-    rker=np.zeros(npix,"double") ; rker[spix]= np.cos(2.*gamma)*gbeta
-    iker=np.zeros(npix,"double") ; iker[spix]= np.sin(2.*gamma)*gbeta
-
-    return cpix,[rker,iker]
-
-def return_qu2eb_kernel_radiate(nside,lon,lat,theta_cutoff,theta,rad_ker):
-    fn_rad_ker=interp1d(theta,rad_ker,assume_sorted=True,kind="cubic",bounds_error=False,fill_value=0.0)
-    npix=h.nside2npix(nside) ; domega=4.*np.pi/float(npix)
+    domega=1.
+    if normalize:
+        domega=4.*np.pi/float(npix)
+    
     cpix=h.ang2pix(nside,lon,lat,lonlat=True)
 
     beta,alpha,gamma,spix=euler.return_euler_angles(nside,cpix,theta_cutoff,inclusive=False,fact=4)
     
     gbeta=fn_rad_ker(beta)
-    rker=np.zeros(npix,"double") ; rker[spix]=  np.cos(2.*alpha)*gbeta
-    iker=np.zeros(npix,"double") ; iker[spix]= -np.sin(2.*alpha)*gbeta
+    rker=np.zeros(npix,"double") ; rker[spix]= -np.cos(2.*alpha)*gbeta*domega
+    iker=np.zeros(npix,"double") ; iker[spix]=  np.sin(2.*alpha)*gbeta*domega
     return cpix,[rker,iker]
 
[…]

### 2018-05-11 articles/formalism/sections/kernel_paintbrush.tex
Added new figure on intuition for filaments.

\section{Intuition for the polarization structure of magnetized filaments}
\begin{figure}
  \includegraphics[width=0.5\columnwidth]{line.pdf}
  \includegraphics[width=0.5\columnwidth]{spiral.pdf}
  \caption{
    The polarization signals of toy filament structures.
    In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.  The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
    Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.  B-modes are only non-zero at the ends.  Right panels: in a curved filament, the E-mode is again positive along the filament.  Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.  The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
    In all images, the longitude increases to the left (sky convention).}
  \label{fig:polfilaments}
\end{figure}

Naturally describes the reason for a positive T/E correlation.  Figure~\ref{fig:polfilaments}.

### 2018-05-11 articles/formalism/sections/real_space_formalism.tex
adding non-corrupt pdf
Adding paintbrush figure into main text
New spiral figure and notation standardization

@@
-\section{Polarization primer}
-\subsection{A heuristic argument for constructing $E/B$ fields on the sphere}
-\comment{Need a better title for the section that gives the heuristic argument}
+\section{Polarization primer} \label{sec:pol-primer}
+\subsection{Constructing $E/B$ fields without harmonic space}
+%\comment{Need a better title for the section that gives the heuristic argument}
 %\textit{Alternative for bringing the heuristic argument earlier.}
 
- CMB polarization is measured in terms of Stokes parameters, averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.
-(Throughout we use the conventions of HEALPix \cite{healpix_primer}.) Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system and a rotation by an angle $\psi$ around the line of sight transforms them as
+ CMB polarization is measured in terms of Stokes parameters, time averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.\footnote{Throughout we use the conventions of HEALPix \cite{healpix_primer}, measuring the polarization angle East of South.} Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system, and a rotation by an angle $\psi$ around the line of sight transforms them as
 %
 \beq \label{eq:qu-rot}
-\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,.
+\fqu' = \begin{bmatrix} \cos{2 \phi} &  \sin{2 \phi} \\ -\sin{2\phi} & \cos{2 \phi} \end{bmatrix} \fqu \,.
 \eeq
-Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
+Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\phi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
 
@@
 
-We consider the contribution from the polarization field (evaluated at $\hat n_q$) to a scalar field (evaluated at $\hat n_e$).
+We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
 \fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$, and a rotation around $\hat n_q$ by $-\gamma$.
-This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}.
+This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}
 %
@@
 This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, and so we must have $f(\beta_{qe} = 0 ) = 0$.
+Hence the $E/B$ fields are necessarily non-local.
 A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$, and so $f(\beta_{qe} = \pi ) = 0$.
-Hence the $E/B$ fields are necessarily non-local.
-Any such function $f$ will give us $E/B$-like scalar fields.
+Any such function $f$ will let us construct $E/B$-like scalar fields.
 Below we derive the particular one that gives rise to our familiar $E/B$ modes.
@@
 
-The kernel's azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so its harmonic transform has no multipole $\ell$ dependence.
-The azimuthal part is the crucial operation that translates between different spin representation of CMB polarization.
-Only the radial part of the kernel $f(\beta_{qe})$ depends only on the angular separation between locations and hence must completely incorporate all the multipole $\ell$ dependence.
-
 %--------------------------------------------------------
-\subsection{Standard $E$/$B$ fields} \label{sec:mat_pol_intro}
+\subsection{Standard $E$/$B$ fields}
 
 The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
-The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
-The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
+The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\phi}(\eth _{s}g)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\phi}(\bar{\eth} _{s}g)$.
 The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
@@
 
-The complex field $_{\pm 2}X$ defined on the sphere can be decomposed in spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+We can decompose the complex field $_{\pm 2}X$ into spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
 On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67},
@@
 
-Using the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$ and the identities given in \eq{eq:spinopylm} it can be shown that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the following equations,
+From the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$, and the identities given in \eq{eq:spinopylm}, it follows that the scalar fields $\mathcal{E}/\mathcal{B}$ are,
 %
 \beq \label{eq:pseudo}
-\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) ~\,;~ \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
+\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n});\qquad
+\mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
 \eeq
 %
-where the harmonic coefficients $a^{E}_{\ell m}$  \& $a^{B}_{\ell m}$ are related to the harmonic coefficients of the spin-2 polarization field via the following equations,
+where the harmonic coefficients $a^{E}_{\ell m}$ and  $a^{B}_{\ell m}$ relate to the harmonic coefficients of the spin-2 polarization field via,
 %
 \beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big] ~\,;~a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big];\qquad a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
 \eeq
 %
-In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields as defined by the following equations, 
+In the remainder of this article, we will work with the scalar $E$ and pseudo scalar $B$ fields, defined by: 
 %
 \beq \label{eq:realeb}
-E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n}) ~\,;~ B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
+E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n});\qquad B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
 \eeq
 %
-These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$), and are not local functions of Stokes $Q,U$.
+These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$), and are not local functions of Stokes $Q/U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 
-\subsection{Evaluating scalar fields $E$ \& $B$ from Stokes parameters $Q$ \& $U$}\label{sec:qu2eb}
-In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields E \& B from the Stokes parameters Q \& U. 
+\subsection{Evaluating scalar $E/B$ from Stokes $Q/U$}\label{sec:qu2eb}
+In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields $E/B$ from the Stokes parameters $Q/U$. 
 %To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
@@
 \beqrys
-\bar{S} &=& {{}_0\mathcal{Y}} *\tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P} = \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T *\bar{P}   \,, \\
-&=&  \bar O *\bar{P} \,. \label{eq:qu2eb_op}
+\bar{S} &=& {{}_0\mathcal{Y}} \, \tilde T^{-1}  \, {{}_2\mathcal{Y}^{\dagger}} \, \bar T  \bar{P}
+= \frac{1}{2} {{}_0\mathcal{Y}} \, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \bar{P}    \\
+&=&  \bar O \bar{P}. \label{eq:qu2eb_op}
 \eeqrys
@@
 \beqrys
-\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}} *\tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T \,, \\
+\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}}\, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \,, \\
 &=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{T*}_q  +  {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{T*}_q - {}_{0}Y_e~ {}_{-2}Y^{T*}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{T*}_q + {}_{0}Y_e ~{}_{-2}Y^{T*}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
+&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{\dag}_q  +  {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{\dag}_q + {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
 \eeqrys
 %
-where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{T*}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
-Note that here we purposefully introduce the notation of the index ``e'' to denote the location where the scalar fields are being evaluated and the index ``q'' to denote the location from which  the Stokes parameters are being accessed.
+where the symbol ${}_{0}Y_e$ is used to denote the sub-matrix ${}_{0}Y_{\hat{n}_e \times \ell m} \equiv {}_{0}Y_{\ell m}(\hat{n}_e)$, the symbol ${}_{\pm 2}Y^{\dag}_q$ is used to denote the transposed conjugated matrix ${}_{\pm 2}Y^*_{\ell m \times \hat{n}_q} \equiv {}_{\pm 2}Y^*_{\ell m}(\hat{n}_q)$ and the summation is over the multipole indices $\ell,m$.
+As before, we use the notation that the index $e$ denotes the location where the scalar fields are being evaluated, and the index $q$ denotes the location from which  the Stokes parameters are being accessed.
 Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
@@
 \noindent \eq{eq:qu2eb_ker_1} already presents a real space operator, but it is not in a form which can be practically implemented.
-To arrive at a real space operator which is practially usable, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles\cite{varshalovich},
+To proceed, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles \cite{varshalovich},
 %
@@
 %
-where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ so as to allign the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
-The different parts of the real space operator $\bar{O}$  are completely specified by the complex function,
+where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ to align the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
+
+Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the complex function,
 %
@@
 &=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{qe}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
+&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] \quad {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
 \eeqry
@@
 where we have used the identity in \eq{eq:sum_spin_shf} to simplify the product of the spherical harmonic functions.
-Note that the function on the right depends only on two out of the three Euler angles.
+Note that the function depends only on two out of the three Euler angles.
+The azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so its harmonic transform has no multipole $\ell$ dependence.
+The azimuthal part is the crucial operation that translates between different spin representation of CMB polarization.
+Only the radial part $f(\beta_{qe})$ depends only on the angular separation between locations and hence  completely incorporates all the multipole $\ell$ dependence.
+
 Employing \eq{eq:qu2eb_gen_kernel} to simplify the product of spherical harmonic functions in \eq{eq:qu2eb_ker_1}, the real space operator $\bar{O}$ can now be cast in this more useful form,
@@
 %
-where, we reiterate, $\alpha_{qe}, ~\beta_{qe} ~\&~ \gamma_{qe}$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\hat{n}_q \xrightarrow{\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})} \hat{n}_e$.
+where $(\alpha_{qe}, ~\beta_{qe}, \gamma_{qe})$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})[\hat{n}_q] = \hat{n}_e$.
 
-\textit{Radiating kernel:} Using \eq{eq:op_qu2eb_rad} in \eq{eq:qu2eb_op} one can see that the $E$/$B$ contribution of the Stokes parameters at some location $\hat{n}_q$ is given by the following expression,
+\paragraph{Radiating kernel.} The expression we call the \textit{radiating kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
+The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere.
+In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluate its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
+
+The $E$/$B$ contribution from the Stokes parameters at some location $\hat{n}_q$ is given by the following expression (\eq{eq:op_qu2eb_rad} and \eq{eq:qu2eb_op}),
 %
 \beq  \label{eq:qu2eb_radiation_explicit}
-\bar{S}_q = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
+\bar{S}_q(\hat n_e) = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
 \eeq
 %
-The total map of E \& B modes can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$ : $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
-This operation can be cast in a concise form as follows,
+The total map can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$: $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
+This operation can be cast concisely as,
 %
@@
 \left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
-&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \cdot \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \cdot  \mathcal{M}_{G}[\hat{n}_q] \,,
+%&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
+&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat{n}_q) \,,
 \eeqry
@@
 %
-where ``$\cdot$'' denotes a simple scalar multiplication.
-$\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it can be thought of as the Green's function of the operator, since $[E +iB] = \mathcal{M}_{G}$ is the spin-0 scalar field generated from the Stokes charge $[Q+iU] = [\delta(\hat{n}-\hat{n}_q) + i 0]$.
+where the last line is a simple scalar multiplication between complex numbers.  The radiating kernel is then:
+\beq
+ \mathcal{M}_{G}(\hat{n}_e) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
+\eeq
+%. $\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it
+is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.
+That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
 
-We denote the kernel expressed in terms of the Euler angle $\alpha$ as the radiating kernel, since it allows us to evaluate the $E/B$ field contribution across the sphere due to a single Stoke (charge) parameter at a fixed location on the sphere.
-The total $E/B$ maps can then be thought of as just superposed radiation emerging from Stokes charges across the sphere.
-In this formulation, one is effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field across the sphere.
 %
@@
 
-\textit{Convolution kernel:} We can also formulate the real space operator to be a function of Euler angles corresponding to the inverse rotation.
-The Euler angles for the inverse rotations (i.e.
-to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$) are related to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
+\paragraph{Convolution kernel.} We can also formulate the real space operator as a convolution operation, where the scalar field at $\hat n_e$ gathers contributions from the Stokes fields.
+This is based around the inverse rotation (to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$).
+The inverse rotation Euler angles relates to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
 Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
@@
 \beqry 
-[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)} \,, \label{eq:qu2eb_physical}\\
-&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
-&=& \Bigg\lbrace \mathcal{M}_{B} \circ {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
+[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
+&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
+&=& \Bigg\lbrace \mathcal{M}_{B} \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
 \eeqry
@@
 %
-where $\circ$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
+where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
 %--------------------------------------------------------
@@
 \eeqry
-\begin{subequations}
+\end{subequations}
 %

### 2018-05-11 articles/formalism/sections/real_space_formalism.tex
Fixed up 3.4

@@
 \paragraph{Convolution kernel.} We can also formulate the real space operator as a convolution operation, where the scalar field at $\hat n_e$ gathers contributions from the Stokes fields.
-This is based around the inverse rotation (to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$).
+This is based around the inverse rotation from the previous section (to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$).
 The inverse rotation Euler angles relates to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
@@
 %--------------------------------------------------------
-\subsection{Evaluating Stokes parameters $Q$ \& $U$ from scalar fields $E$ \& $B$}\label{sec:eb2qu}
+\subsection{Evaluating Stokes $Q$/$U$ from scalar $E$/$B$}\label{sec:eb2qu}
 The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure.
@@
 \beqry
-\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} \,,  \\
-&=&  \bar O^{-1} *\bar{S}\,.
+\bar{P} &=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} {{}_2\mathcal{Y}} \,\tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S}\,,  \\
+&=&  \bar O^{-1} \bar{S}\,.
 \eeqry
@@
 \beqry
-{}_{+2}X(\hat{n}_q) &=& \Bigg\lbrace \mathcal{M}^*_{G} \circ [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} \textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}\\
-{}_{+2}X(\hat{n}_q) &=&  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e}) \cdot  \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} \textrm{\emph{Radiation kernel}}\,,
+    {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,\\
+    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
 \eeqry
@@
 %--------------------------------------------------------
-\subsection{Decomposing Stokes parameters $Q$ \& $U$  into those corresponding to $E$ \& $B$ modes respectively}
-We can only measure the total Stokes vector which is a sum of the Stokes vectors corresponding to the respective scalar modes.
-The $E$ \& $B$ modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
+\subsection{Purifying Stokes parameters $Q$/$U$ from $E$/$B$ modes}
+We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.
+The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
 It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
 In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes.
-Though the algebra is a little more involved, the derivation is similar to that discussed in \sec{sec:qu2eb}, hence we refrain from presenting the detailed calculations here, but outline the key points.
+The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here, and outline only the key points.
 We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
@@
 \beqry
-\bar{P}_E &=&  [\bar T^{-1} * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {{}_2\mathcal{Y}^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
-&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}* {{}_2\mathcal{Y}}* \tilde T* \tilde O_B* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}* \bar T]*\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
-&=&  \bar O_{B}*\bar{P} \,. \nonumber
+\bar{P}_E &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E  \tilde T^{\dagger}  {{}_2\mathcal{Y}^{\dagger}}\, \bar T ]\bar{P}  \,, \nonumber \\
+&=&  \bar O_{E} \bar{P} \,,\nonumber \\
+\bar{P}_B &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_B \tilde T^{-1} {{}_2\mathcal{Y}^{\dagger}} \bar T]\bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}}\, \tilde T  \tilde O_B \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}   \,, \nonumber\\
+&=&  \bar O_{B} \bar{P} \,. \nonumber
 \eeqry
@@
 %
-where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
+where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ \revisit{Is the prescript correct?} are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
  %
@@
 \beqry \label{eq:op_qu2equbqu}
-\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber
+\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace  \frac{\Delta\Omega}{2}  \,, \nonumber
 \eeqry
@@
 \beqry
-{}_{+2}X_{E/B}(\hat{n}_e) &=&0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q) \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
-&=& 0.5 \Bigg\lbrace  {}_{+2}X \cdot \mathcal{I}^*_G \pm {}_{+2}X^* \cdot \mathcal{D}_G \Bigg\rbrace \hspace{.5cm }\textrm{\emph{   Radiation kernel}} \,, \\
-&=& 0.5 \Bigg\lbrace \mathcal{I}_B \circ {}_{+2}X\pm \mathcal{D}_B \circ {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
+{}_{+2}X_{E/B}(\hat{n}_e) &=& 0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q)  \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
+&=& 0.5 \Bigg\lbrace  {}_{+2}X  \, \mathcal{I}^*_G \pm {}_{+2}X^* \, \mathcal{D}_G \Bigg\rbrace \hspace{.5cm } \textrm{\emph{   Radiation kernel}} \,, \\
+&=& 0.5 \Bigg\lbrace \mathcal{I}_B \star {}_{+2}X\pm \mathcal{D}_B \star {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
 \eeqry
@@
 where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity.
-Note that when the operators $\mathcal{I}^*$ \& $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ \& $\mathcal{D}_G$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ \& $\mathcal{D}_B$.
-Note that unlike in the case of the operators $\mm_G$ \& $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ \& $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ \& $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+Note that when the operators $\mathcal{I}^*$ and $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ and $\mathcal{D}_G$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ and $\mathcal{D}_B$.
+Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 
 The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
-For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$.
-$\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$.
+For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
+$\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^* \mathcal{D}=\mathcal{I}$.
 Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
@@
 \beqry
-\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
-\bar O_E*\bar O_B &=& 0 \,,\\
+\bar O_E  \bar O_E &=& \bar O_E;\qquad \bar O_B * \bar O_B = \bar O_B \,, \\
+\bar O_E \bar O_B &=& 0 \,,\\
 \bar O_E + \bar O_B &=& \mathcal{I} \,,
@@
 %
-which are the real space analogues of \eq{eq:har_op_prop}.
-\footnote{While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}
+which are the real space analogues of \eq{eq:har_op_prop}.\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}
 

### 2018-05-12 articles/formalism/sections/kernel_discussion.tex
Adding paintbrush figure into main text
Editing pass and notation cleanup.

@@
 \beqry
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat ~;~ \bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat ~;~ \bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat;\qquad
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat; \qquad
+\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
 \eeqry
@@
 %
-In the previous section we presented a quantitative understanding of the  azimuthal dependence of the real space kernels, providing little insight into their radial dependence.
-The radial part of these kernels determines the non-locality of the respective operators and encodes all their multipole dependencies.
-For illustration the radial kernels ${_{\mm}f}, {_{\md}f} ~\&~ {_{\mi}f} $ are evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ and the resultant functions are depicted in \fig{fig:beta_kernel}.
+In the previous section we presented a quantitative understanding of the  azimuthal dependence of the real space kernels.
+Here we probe the radial part that determines the non-locality of the operators and encodes all their multipole dependencies.
+For illustration the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$ are evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ \revisit{not match figure?} and the resultant functions are depicted in \fig{fig:beta_kernel}.
 %
@@
 
-${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$ \& $U$ to scalars $E$ \& $B$ and vice versa and it has a vanishing contribution from the regions where ($\beta \rightarrow 0$) and from regions ($\beta \rightarrow \pi$) as seen in \fig{fig:beta_kernel}.
-This can be understood as arising from the fact that the coordinate dependence of the Stokes parameters cannot uniquely integrated out since the Euler angles $\alpha$ \& $\gamma$ are not uniquely defined at the locations $\beta=0,\pi$.
+${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
+It has a vanishing contribution as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$.
+This can be understood as arising from the fact that the coordinate dependence of the Stokes parameters cannot be uniquely integrated out since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at the locations $\beta=0,\pi$.
 This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
@@
 ${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
-The main take away from these observations of the nature of the radial part of the kernel is that the real space operators which decompose the Stokes parameters into parts that correspond to E and B modes are necessarily non-local.}\\ \linebreak
-\noindent \textit{The band limit dependence:} 
+The main takeaway from these observations of the nature of the radial part of the kernel is that the real space operators which decompose the Stokes parameters into parts that correspond to E and B modes are necessarily non-local.}\\ \linebreak
+
+\paragraph{Band limit dependence.} 
 %It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. 

### 2018-05-14 articles/formalism/sections/generalizedeb.tex
Further edits through section 3.

@@
 %--------------------------------------------------------
-\subsubsection{Generalized operators}
-In this section we present a systematic method to generalize the real space operators that translate between $Q/U$ and $E/B$ description of CMB polarization.
-The azimuthal part of the real space kernels is constrained to be of the form $\sim e^{\pm i2 \alpha}$.
+\subsection{Generalized polarization operators}
+With our better understand of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
+The spin symmetry constrains the the azimuthal part of the real space kernels is constrained to be of the form $\sim e^{\pm i2 \alpha}$.
 The shape of the radial part of the operator is determined by the basis functions and varies as a function of the band limit.
@@
 
-We can systematically generalize the real space operator by introducing the following harmonic space operator,
+We can systematically generalize the real space operator by introducing the following harmonic space filter function,
 %
@@
 where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for $E$ and $B$ modes.
-To simplify discussions and without loosing generality we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
-Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q$ \& $U$ to scalars $E$ \& $B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
+To simplify discussions, we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
+Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q/U$ to scalars $E/B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
 %
@@
 \beqry
-{\bar O}' &=& {{}_0\mathcal{Y}} *\tilde T^{-1}*\tilde{\mathcal{G}}* {{}_2\mathcal{Y}^{\dagger}} *\bar T \,,\\
-{\bar O}'^{-1}&=& \bar{T}^{-1} *{{}_2\mathcal{Y}}* \tilde{\mathcal{G}}^{-1} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}
+{\bar O}' &=& {{}_0\mathcal{Y}} \, \tilde T^{-1} \tilde{\mathcal{G}} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \,,\\
+{\bar O}'^{-1}&=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde{\mathcal{G}}^{-1} \tilde T {{}_0\mathcal{Y}^{\dagger}}.
 \eeqry
@@
 %
-where we have used the primed notation  to distinguish these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
-Requiring both the forward and inverse operators to be well defined constrains the choice of $\tilde{\mathcal{G}}$ to be such that it has a valid  inverse.
-This is an important criteria to recover the standard CMB spectra.
+The primed notation distinguishes these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
+We require both the forward and inverse operators to be well defined.
+This constrains the choice of $\tilde{\mathcal{G}}$ to have a valid  inverse and is important to recover the standard CMB power spectra.
 The radial parts of this generalized operator and its inverse are given by the following expressions,
@@
 
-While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
+While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$ rather than the harmonic space $g_l$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
 Employing the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the expression,
@@
 
-An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard E and B fields being convolved with some effective circularly symmetric instrument beam whose radial profile is given by the expression,
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
 %
@@
 %
-where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.  \revisit{Need another symbol than $B$ for beam.}
 In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
@@
 
- Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
-\fig{fig:glbl} depicts the harmonic functions $g_{\ell}$ for the respective radial kernel and beams.
-The modified radial kernel resulting from Gaussian beams with ${\rm fwhm} =15' \,\&\, 12'$ are depicted in \fig{fig:bl_gbeta} as blue and orange curves respectively.
-Note that instruments  beams tend to increase the non-locality parameter $\beta_0$, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
-The red curve depicts a modified radial kernel which by construction has a very small $\beta_0$.
-Note that the beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of the delta function beam.
-\fig{fig:gl_bbeta} depicts the radial profile of the  effective beams corresponding to the different radial kernels.
+% Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
+In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
+ \fig{fig:gl_bbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.
+Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
+The exponential cutoff (red curve) by construction has a very small non-locality (parameterized by $\beta_0$).
 
+\fig{fig:glbl} depicts the harmonic description $g_{\ell}$ for these respective radial kernels and beams.
+ %The modified radial kernel resulting from Gaussian beams with ${\rm fwhm} =15' \,\&\, 12'$ are depicted in \fig{fig:bl_gbeta} as blue and orange curves respectively.
+Finally, the beam that the modified radial kernels appies to the $E/B$ fields we show in \fig{fig:gl_bbeta}.
+Note that the beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of a delta-function beam.
 %In \sec{sec:local_conv_eb} we constructed localized convolution kernels by multiplying $R(\beta)$ with an apodized version of the step function $\theta_{\rm apo}(r_{\rm cutoff})$.
@@
 %--------------------------------------------------------
-\subsubsection{Recovering the default $E$ and $B$ mode spectra}
+\subsubsection{Recovering the standard $E$ and $B$ mode spectra}
 The generalized convolution kernels defined in the previous section, when operated on the Stokes vector returns some scalar $E'$ and $B'$ mode maps,
@@
 \beq
-\bar{S}' = \bar{O}' * \bar{P}
+\bar{S}' = \bar{O}' \bar{P}
 \eeq
 %
-which are merely filtered version of he standard $E$ and $B$ modes maps.
-Since the harmonic functions $g_{\ell}$ of the modified radial function $G(\beta)$ can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam, the spectra of the scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
+which are merely filtered versions of the standard $E/B$ modes maps.
+Since the filter function is simply $g_{\ell}$, easily obtained from the modified radial function $G(\beta)$, and it can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam, the power spectra of the modified scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %
@@
  where $C_{\ell}$ denotes the angular power spectra and $T$ refers to the temperature anisotropy map.
-Therefore the standard CMB spectra can be always recovered as long as the $1/g_{\ell}$ \& $1/g_{\ell}^2$ are well behaved functions, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
-Some examples forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
+Therefore the standard CMB spectra can always be recovered as long as the $1/g_{\ell}$ and $1/g_{\ell}^2$ are well behaved functions, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
+%Some examples forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
 %One direct application of this freedom in choosing the radial kernel is that one can mitigate the issue of leakage of power from $E$ to $B$.

### 2018-05-14 articles/formalism/sections/kernel_discussion.tex
Further edits through section 3.

@@
 In the previous section we presented a quantitative understanding of the  azimuthal dependence of the real space kernels.
-Here we probe the radial part that determines the non-locality of the operators and encodes all their multipole dependencies.
-For illustration the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$ are evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ \revisit{not match figure?} and the resultant functions are depicted in \fig{fig:beta_kernel}.
+Here we probe the radial part, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
+For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ \revisit{not match figure caption?}.
 %
 \begin{figure}[t]
-\centering
-\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
-\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
-\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
+%\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
+%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
+%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
+\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}\hfill
+\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}\hfill
+\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
 \caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
@@
 
-${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-It has a vanishing contribution as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$.
-This can be understood as arising from the fact that the coordinate dependence of the Stokes parameters cannot be uniquely integrated out since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at the locations $\beta=0,\pi$.
-This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
+The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
+As a consequence of the spin-2 symmetry, tt vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at separations $\beta=0,\pi$.
+%This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
 
-\revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$ and expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
-${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
-The main takeaway from these observations of the nature of the radial part of the kernel is that the real space operators which decompose the Stokes parameters into parts that correspond to E and B modes are necessarily non-local.}\\ \linebreak
+The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to E and B modes  are also  necessarily non-local.
+The function \revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.
+It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
+${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.}
+\revisit{why?}
 
@@
 %It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. 
-We further quantify this non-locality by studying the radial extent of the kernels and its dependence on the maximum multipole accessible for analysis.
-To carry out this study we evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
+To quantify this non-locality, we study the radial extent of the kernels and its dependence on the maximum multipole accessible.
+We evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
 
@@
 In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+\revisit{Holds for small beta and moderately high ell?}
+
 %We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
@@
 
-It is useful to define a characteristic radius of the region from which the evaluated resultant fields get most of their contribution.
-Our primary interest is in quantifying the non-locality of the scalar modes $E$ \& $B$, therefore we define the abscissa at which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transits to being monotonously below 1\% of the maxima of the function as the non-locality parameter: $\beta_{o}$.
+To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.
+We define a non-locality parameter $\beta_{o}$ as the angle beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ consistently falls below 1\% of its maximum.
+\revisit{Why $\beta_o$ rather than $\beta_0$?}
 %For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}.
 Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
-The simple empirical derived relation: $\beta_o= {\rm min}(180,180 \frac{22}{\ell_{\rm max}})$ provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
+The empirical relation
+\beq
+\beta_o= {\rm min}\left(180,180 \frac{22}{\ell_{\rm max}} \right)
+\eeq
+provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
 This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.

### 2018-05-16 articles/formalism/sections/kernel_paintbrush.tex
New spiral figure and notation standardization
added text to discussion of kernel paintbrush

@@
-\section{Intuition for the polarization structure of magnetized filaments}
+\paragraph{Polarization signature of magnetized filaments}
+The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
+For example, a simple model for a magnetize filament has the magnetic field threaded along a linear gas overdensity.
+Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and to the filament overall).
+For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}.
+The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.
+
+The kernel can be thought of as the orientable nib of a calligraphy stylus, and traced along the filament.
+The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted in $E>0$.
+Since the overdensity will also have emission in total intensity, this naturally predicts a positive $T/E$ correlation for magnetized filaments.
+The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.
+
+The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.
+This results in a non-zero $B$ pattern for the filament, positive on the North-East and South-West, and negative in the North-West and South-East.
+\revisit{The non-zero $B$ result is somewhat surprising given that the polarization pattern is invariant under parity.}
+Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
+The description is also intuitive if we distort the shape of the filament.
+If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will council, and we are left with a pure $E$ pattern.
+The same general description holds for a spiral-shaped filament.
+The filament is highlighted by positive $E>0$.
+The $E$-pattern is more negative on the interior of a curve than on the exterior, and more so for a tighter radius of curvature.
+
 \begin{figure}
@@
 The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
-    In all images, the longitude increases to the left (sky convention).}
+    In all images, the longitude angle increases to the left (East in sky convention).}
   \label{fig:polfilaments}
@@
 
-Naturally describes the reason for a positive T/E correlation.  Figure~\ref{fig:polfilaments}.
+  Figure~\ref{fig:polfilaments}.

### 2018-05-17 articles/formalism/article.tex
Added new plot generation scripts: 1. euler angles plots and movie, 2. plot elucidating the radiation and convolution. | Tested the existing codes for conversion to qu2eb and eb2qu and qu2equ&bqu
Minor edits to Euler angles plot/movie. Added appendix in formalism paper deriving the important identity on product of spin spherical harmonics and the radiating and convolution interpretations of the kernel.
generated a proper sign version of the codes, generated the convolution kernel plots and added them to the pape. the kernel plots are updated to have the proper sign.
updated figures, table of c

@@
 \usepackage[normalem]{ulem}
+\usepackage{caption}
 \renewcommand{\thesubfigure}{(\roman{subfigure})}
@@
 \def\ymat#1{\begin{bmatrix} _{+2}Y_{#1} & 0  \\  0 & _{-2}Y_{#1}  \end{bmatrix}}
-\def\ymatc#1{\begin{bmatrix} _{+2}Y^{T*}_{#1} & 0  \\  0 & _{-2}Y^{T*}_{#1}  \end{bmatrix}}
+\def\ymatc#1{\begin{bmatrix} _{+2}Y^{\dag}_{#1} & 0  \\  0 & _{-2}Y^{\dag}_{#1}  \end{bmatrix}}
 \def\yzmat#1{\begin{bmatrix} _{0}Y_{#1} & 0  \\  0 & _{0}Y_{#1}  \end{bmatrix}}
@@
 
-\graphicspath{ {"../../figures/"//} }
+\graphicspath{ {"./figures/"//} }
 
@@
 The covolution kernels split naturally into angular and radial parts, and we show explicitly how the spatial extent of the convolution kernel depends on the targeted band-limit.
-We show that a arbitrary radial dependence can produce $E$/$B$-like maps and that these are simply filtered versions of the standard $E$/$B$ maps.
+We show that an arbitrary radial dependence can produce $E$/$B$-like maps and that these are simply filtered versions of the standard $E$/$B$ maps.
 This allows us to compute $E$/$B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
 We can compute power spectra using standard techniques, and recover the power spectrum of the sky with a simple window function.
+The spatial structure of the real space operator provides some intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds.
     %
@@
 \include{./sections/discussion}
+\include{./sections/acknowledgments}
+\include{./sections/appendix}
 \endgroup

### 2018-05-17 articles/formalism/sections/real_space_formalism.tex
Editing pass and notation cleanup.
Modified section pure E/B section
More details on filament discussion and other minor edits.

@@
 
-Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}$ is invariant under rotations and must be spin-0 by definition:
+Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations and must be spin-0 by definition:
 \beq
@@
 \eeq
-The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
+\revisit{I'm having some trouble understanding the next 2 sentences.} The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
 At the same time, the imaginary part of the function is constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
@@
 
-This type of construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
+This type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
 transforming spin-0 fields to spin-2).
@@
 %
-where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
+where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$.
+When expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
 %--------------------------------------------------------
@@
 %--------------------------------------------------------
-\subsection{Purifying Stokes parameters $Q$/$U$ from $E$/$B$ modes}
+\subsection{Purifying Stokes parameters $Q$/$U$ for $E$/$B$ modes}
 We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.
@@
 \beqry
-\bar O_E  \bar O_E &=& \bar O_E;\qquad \bar O_B * \bar O_B = \bar O_B \,, \\
-\bar O_E \bar O_B &=& 0 \,,\\
+\bar O_E \, \bar O_E &=& \bar O_E;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
+\bar O_E \, \bar O_B &=& 0 \,,\\
 \bar O_E + \bar O_B &=& \mathcal{I} \,,
@@
 %
-which are the real space analogues of \eq{eq:har_op_prop}.\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}
+which are the real space analogues of \eq{eq:har_op_prop}.\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}  Thus they are orthogonal and idempotent in a band-limited sense.
 

### 2018-05-18 articles/formalism/sections/kernel_paintbrush.tex
More details on filament discussion and other minor edits.
More minor edit

@@
 For example, a simple model for a magnetize filament has the magnetic field threaded along a linear gas overdensity.
-Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and to the filament overall).
-For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}.
+Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and perpendicular to the filament overall).
+For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}).
 The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.
 
-The kernel can be thought of as the orientable nib of a calligraphy stylus, and traced along the filament.
-The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted in $E>0$.
+The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.
+The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted as a segment with $E>0$.
 Since the overdensity will also have emission in total intensity, this naturally predicts a positive $T/E$ correlation for magnetized filaments.
@@
 The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.
-This results in a non-zero $B$ pattern for the filament, positive on the North-East and South-West, and negative in the North-West and South-East.
+This results in a non-zero $B$ pattern for the filament.
+For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.
 \revisit{The non-zero $B$ result is somewhat surprising given that the polarization pattern is invariant under parity.}
+
 Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
 The description is also intuitive if we distort the shape of the filament.
-If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will council, and we are left with a pure $E$ pattern.
-The same general description holds for a spiral-shaped filament.
+If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
+
+The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
 The filament is highlighted by positive $E>0$.
@@
 \end{figure}
-
-  Figure~\ref{fig:polfilaments}.

### 2018-05-18 articles/formalism/sections/real_space_formalism.tex
More minor edit

@@
 %&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat{n}_q) \,,
+&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_e,\hat{n}_q) \,,
 \eeqry
@@
 \beq
- \mathcal{M}_{G}(\hat{n}_e) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
+ \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
 \eeq
@@
 is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.
-That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
+That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
+We display the kernel later in \fig{fig:vis_kernel}.
 
@@
 When expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
+We display the kernel in \fig{fig:vis_kernel}.
 %--------------------------------------------------------

### 2018-05-22 articles/formalism/sections/real_space_formalism.tex
Added some reference and some detail to kernel paintbrush section.

@@
 
-\paragraph{Radiating kernel.} The expression we call the \textit{radiating kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
+\paragraph{Radiation kernel.} The expression we call the \textit{radiation kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
 The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere.
@@
 %
-where the last line is a simple scalar multiplication between complex numbers.  The radiating kernel is then:
+where the last line is a simple scalar multiplication between complex numbers.  The radiation kernel is then:
 \beq

### 2018-05-22 articles/formalism/sections/kernel_paintbrush.tex
Added some reference and some detail to kernel paintbrush section.
Cleaned up discussion of parity of filament and added discussion of Planck stacking.

@@
 The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted as a segment with $E>0$.
-Since the overdensity will also have emission in total intensity, this naturally predicts a positive $T/E$ correlation for magnetized filaments.
+Since the overdensity will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.
 The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.
@@
 For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.
-\revisit{The non-zero $B$ result is somewhat surprising given that the polarization pattern is invariant under parity.}
 
+The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.
+However, unlike a complete ring, this filament is not a configuration with a definite parity.
 Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
-The description is also intuitive if we distort the shape of the filament.
+A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.
+A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.
+We predict that it should be there in higher fidelity data.
+
+The intuition from the real-space kernels holds also when we distort the shape of the filament.
 If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
-
 The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
 The filament is highlighted by positive $E>0$.
-The $E$-pattern is more negative on the interior of a curve than on the exterior, and more so for a tighter radius of curvature.
+The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
+The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
 

### 2018-05-22 articles/formalism/sections/kernel_discussion.tex
Split kernel image and moved MG/MB to right after they are introduced.

@@
-\subsection{Visualizing the real space kernels} \label{sec:visualize_operator}
-%
-\begin{figure}[t] \label{fig:mixing_kernel}
-\centering
-\captionsetup[subfigure]{labelformat=empty}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf}}\hspace{-2mm}
+  %%%% NEW D/I
 
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf}}\hspace{-2mm}
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{m{8ex}m{\kernelfigwidth}m{\kernelfigwidth}|m{\kernelfigwidth}m{\kernelfigwidth}}
+$b=90^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf} \\
+$b=87^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf} \\
+$b=80^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf} \\
+$b=0^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf} \\
+&
+\centering $\textrm{Re} \left(\mathcal{D} \right)$ &
+\centering $\textrm{Im} \left(\mathcal{D} \right)$ &
+\centering $\textrm{Re} \left(\mathcal{I} \right)$ &
+\centering $\textrm{Im} \left(\mathcal{I} \right)$
+  \end{tabular}
+  \end{center}
+  \caption{Like Figure \ref{fig:vis_kernel}, but for the kernels that purify Stokes parameter into their $E/B$ parts.} \label{fig:vis_kernel_DI}
+\end{figure}
 
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf}}\hspace{-2mm}
-\subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Im} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Im} \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Im} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
-\subfigure[$\textrm{Im} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
-\caption{This panel of figure depicts the real and imaginary parts of the real space kernels $\mathcal{M}_{G}$, $\mathcal{M}_{B}$, $\mathcal{D}$ \& $\mathcal{I}$ respectively.
+%\begin{figure} \label{fig:mixing_kernel}
+  %%%%  OLD VERSION %%%%
+%  \centering
+%\captionsetup[subfigure]{labelformat=empty}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf}}\hspace{-2mm}
+
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf}}\hspace{-2mm}
+
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf}}\hspace{-2mm}
+%\subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Im} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Im} \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Im} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
+%\subfigure[$\textrm{Im} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
+%\caption{This panel of figure depicts the real and imaginary parts of the real space kernels $\mathcal{M}_{G}$, $\mathcal{M}_{B}$, $\mathcal{D}$ \& $\mathcal{I}$ respectively.
 These kernels have been evaluated with the band limit: $\ell \in [2,192]$ and sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal.
@@
 %from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-\label{fig:vis_kernel}
- \end{figure}
+%\label{fig:vis_kernel}
+% \end{figure}
 %
@@
 
-We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and radiation kernels.
-To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
-While the kernels are evaluated in the band limit $\ell \in [2,192]$, for illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
-All the plots have been rotated such that the central location marked by the black circle are in the centre of the figure.
-The horizontal and vertical lines that pass through the central black circle mark the local latitude and longitude respectively.
+%
 
-The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-This is consistent with the Green's function interpretation of these kernels.
-Note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
-Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
-From \eq{eq:qu2eb_convolution_explicit} and \eq{eq:eb2qu_convolution_explicit} it is clear that $\mathcal{M}_r$ and $\mathcal{M}_i$ can be interpreted in the following ways,
-%\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
-Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
-%
-\begin{subequations}
-\beqry
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat;\qquad
-\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat; \qquad
-\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
-\eeqry
-\end{subequations}
-%
-The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in the last four columns of \fig{fig:vis_kernel}.
+The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in the last four columns of \fig{fig:vis_kernel_DI}.
 These kernels show a two fold symmetry in the vicinity of the poles and this arises due to Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
-Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is similar to $\mathcal{M}_r$ and $\mathcal{M}_i$ respectively.
+Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is similar to $\mathcal{M}_G$ and $\mathcal{M}_B$ respectively.
 This explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
@@
 %
-In the previous section we presented a quantitative understanding of the  azimuthal dependence of the real space kernels.
-Here we probe the radial part, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
+We have explored in detail the  azimuthal dependence of the real space kernels.
+Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
 For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ \revisit{not match figure caption?}.

### 2018-05-22 articles/formalism/sections/real_space_formalism.tex
Split kernel image and moved MG/MB to right after they are introduced.

@@
 \beq \label{eq:qu-rot}
-\fqu' = \begin{bmatrix} \cos{2 \phi} &  \sin{2 \phi} \\ -\sin{2\phi} & \cos{2 \phi} \end{bmatrix} \fqu \,.
+\fqu' = \begin{bmatrix} \cos{2 \psi} &  \sin{2 \psi} \\ -\sin{2\psi} & \cos{2 \psi} \end{bmatrix} \fqu \,.
 \eeq
-Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\phi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
+Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
 
@@
 
-Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\phi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
-$\mathcal{R}_{\hat{z}_q}(\phi)[{}_{+2}X(\hat{n}_q)] =  {}_{+2}X(\hat{n}_q) e^{-i2\phi} $.
-This same rotation by $\phi$ alters the Euler angle $\alpha_{qe}$ (that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$): $\mathcal{R}_{\hat{z}_q}(\phi)[\alpha_{qe}] = \alpha_{qe} - \phi$.
-Therefore one can see that $\mathcal{R}_{\hat{z}_q}(\phi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\phi}$.
+Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
+$\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)] =  {}_{+2}X(\hat{n}_q) e^{-i2\psi} $.
+This same rotation by $\psi$ alters the Euler angle $\alpha_{qe}$ (that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$): $\mathcal{R}_{\hat{z}_q}(\psi)[\alpha_{qe}] = \alpha_{qe} - \psi$.
+Therefore one can see that $\mathcal{R}_{\hat{z}_q}(\psi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\psi}$.
 
@@
 \beq
-\mathcal{R}_{\hat{z}_q}(\phi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}
+\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}
 \eeq
@@
 
-The same rotation $\mathcal{R}_{\hat{z}_q}(\phi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
+The same rotation $\mathcal{R}_{\hat{z}_q}(\psi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
 Thus we can conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the form
@@
 The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
-The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\phi}(\eth _{s}g)$  \cite{goldberg67}.
-The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\phi}(\bar{\eth} _{s}g)$.
+The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
 The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
@@
 \beqrys
-\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1} ~~~~;~~ \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1} ~~;~~\bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
-\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1}  ~~; ~~ \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
+\bar{S} &=& \bmat E \\ B  \emat_{2 \rm N_{\rm pix} \times 1};\qquad \bar{X} = \bmat _{+2}X \\ _{-2}X \emat_{2 \rm N_{\rm pix} \times 1};\qquad \bar{P} =\fqu_{\tiny {2 \rm N_{\rm pix} \times 1}} \,, \\
+\tilde{S} &=& \bmat a^{E} \\ a^{B} \emat _{2 \rm N_{\rm alms} \times 1};\qquad \tilde{X} = \bmat _{+2} \tilde{X} \\ _{-2} \tilde{X} \emat_{2 \rm N_{\rm alms} \times 1} \,.
 \eeqrys
@@
 \beqrys
-\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ~~;~~ \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
-\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}} ~~;~~ \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
+\bar T &=& \qutox_{2 \rm N_{\rm pix} \times 2 \rm N_{\rm pix}} ;\qquad \bar T^{-1} = \frac{1}{2} \bar T^{\dagger} \,, \\
+\tilde T &=& -\qutox_{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms}};\qquad \tilde T^{-1} = \frac{1}{2} \tilde T^{\dagger} \,,
 \eeqrys
@@
 Alternatively, one can compute the contribution from the Stokes parameter at location `q' to all the point on the blue circle(sphere) and this is a function of the Euler angle $\alpha_{eq}$.
-In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiating and convolving kernels.}
+In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiation and convolution kernels.}
 \label{fig:planar_euler_angles}
@@
     {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,\\
-    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
+    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution_explicit}
 \eeqry
@@
 %--------------------------------------------------------
+
+\subsection{Visualizing the real space kernels} \label{sec:visualize_operator}
+%
+\newlength{\kernelfigwidth}
+\setlength{\kernelfigwidth}{0.2\columnwidth}
+\newlength{\kernelfigspace}
+\setlength{\kernelfigspace}{-1.8mm}
+
+\begin{figure}[t]
+
+  %%%% NEW MG/MB
+  \begin{center}
+    \begin{tabular}{m{8ex}m{\kernelfigwidth}m{\kernelfigwidth}|m{\kernelfigwidth}m{\kernelfigwidth}}
+%      & \multicolumn{2}{c}{$E+iB$} & \multicolumn{2}{c}{$Q+iU$} \\
+    $b=90^\circ$ &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf} \\
+$b=87^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf} \\
+$b=80^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf} \\
+$b=0^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf} \\
+&
+\centering $ \textrm{Re} \left(\mathcal{M}_{G} \right) $ &
+\centering $\textrm{Im} \left(\mathcal{M}_{G} \right) $ &
+\centering $\textrm{Re}  \left(\mathcal{M}_{B}^* \right) $ &
+\centering $\textrm{Im} \left(\mathcal{M}_{B}^* \right) $
+\end{tabular}
+\end{center}
+  \caption{Real and imaginary parts of real space kernels for $Q/U$ to $E/B$ translation (and vice versa).
+The function $\mathcal{M}_{G}$ is the Green's function (radiation kernel) that gives $E+iB$ for a delta function Stokes input $_{+2}X = Q+iU$ at the center.
+On the other hand, $\mathcal{M}^*_{B}$ is the Green's function (radiation kernel) that gives $_{+2}X$ for a delta function scalar input $E+iB$ at the center.
+The black circles denotes the position of the center around which the kernels have been evaluated while the black star marks the location of the North Pole.
+The four rows depict the kernels at different latitudes on the sphere.
+The kernels are unchanged for center points at constant latitude.
+$\mathcal{M}_G$ is invariant over the sphere because $E/B$ fields are coordinate independent.
+In the convolution kernels, $\mathcal{M}_G$ and $\mathcal{M}_B$ switch roles.
+The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter NSIDE=2048.
+Each panel is approximately $16^{\circ} \times 16^{\circ}$ in size with grid lines every 2 degrees.
+} \label{fig:vis_kernel}
+\end{figure}
+
+We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and radiation kernels.
+To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
+While the kernels are evaluated in the band limit $\ell \in [2,192]$, for illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
+All the plots have been rotated such that the central location marked by the black circle are in the centre of the figure.
+The horizontal and vertical lines that pass through the central black circle mark the local latitude and longitude respectively.
+
+The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
+This is consistent with the Green's function interpretation of these kernels.
+Note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
+Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
+From \eq{eq:qu2eb_convolution_explicit} and \eq{eq:eb2qu_convolution_explicit} it is clear that $\mathcal{M}_G$ and $\mathcal{M}_B$ can be interpreted in the following ways,
+%\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
+Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
+%
+\begin{subequations}
+\beqry
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat;\qquad
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat; \qquad
+\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
+\eeqry
+\end{subequations}
 

### 2018-05-25 articles/formalism/sections/generalizedeb.tex
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

@@
 \subsection{Generalized polarization operators}
-With our better understand of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
-The spin symmetry constrains the the azimuthal part of the real space kernels is constrained to be of the form $\sim e^{\pm i2 \alpha}$.
+With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
+The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.
 The shape of the radial part of the operator is determined by the basis functions and varies as a function of the band limit.
@@
 
-We can systematically generalize the real space operator by introducing the following harmonic space filter function,
+We can systematically generalize the real space operator by introducing the following harmonic space filter function:
 %
@@
 %
-where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.  \revisit{Need another symbol than $B$ for beam.}
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.  \comment{Need another symbol than $B$ for beam.}
 In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
@@
 Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
-We can construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows,
+Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:
 %
@@
 %
-Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping,
+Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping:
 %

### 2018-05-25 articles/formalism/sections/introduction.tex
Added new plot generation scripts: 1. euler angles plots and movie, 2. plot elucidating the radiation and convolution. | Tested the existing codes for conversion to qu2eb and eb2qu and qu2equ&bqu
Minor edits to Euler angles plot/movie. Added appendix in formalism paper deriving the important identity on product of spin spherical harmonics and the radiating and convolution interpretations of the kernel.
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

@@
 
-This paper is organized in the following manner: In \sec{sec:pol-intro} we present a primer on the description of CMB polarization on the sphere and introduce the matrix notation which provides a more concise description of the same.
-In \sec{sec:real_space_operators} we introduce the necessary tools  and discuss the derivations of the real space operators.
-In \sec{sec:visualize_operator} we evaluate the real space operators and present visualizations of these functions.
+This paper is organized in the following manner: In \sec{sec:pol-primer} we present a primer on the description of CMB polarization on the sphere.
+Here we begin with a heuristic argument that makes transparent the real space construction of E/B modes on the sphere.
+We then discuss the standard harmonic space procedures for this operation.
+Finally we introduce the matrix-vector notation which yields a more concise description of the harmonic space procedures.
+In \sec{sec:real_space_operators} we derive and discuss the real space operators that transform Q/U to E/B and vice versa.
+In \sec{sec:visualize_operator} we evaluate these real space operators and present visualizations of these functions.
+We also derive a real space operator that decomposes the Stokes Q/U  parameters into components that correspond to E and B modes respectively.
 Here we also discuss the locality of the real space E \& B operators.

### 2018-05-25 articles/formalism/sections/kernel_discussion.tex
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

@@
 
-The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in the last four columns of \fig{fig:vis_kernel_DI}.
+The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in \fig{fig:vis_kernel_DI}.
 These kernels show a two fold symmetry in the vicinity of the poles and this arises due to Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
-Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is similar to $\mathcal{M}_G$ and $\mathcal{M}_B$ respectively.
+Note that in this region, the azimuthal profile of the real and imaginary part of these kernels  is identical to $-\mathcal{M}_G$.
 This explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
@@
 This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} =1 + i0$.
-Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel} which depict the kernels evaluated at the equator $b=0^{\circ}$.
-The middle two row depict the kernels evaluated at a latitudes of $b=87^{\circ}~\&~ 80^{\circ}$ and serve to indicate the rate of this transition.
+Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$.
+The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}~\&~ 80^{\circ}$ and serve to indicate the rate of this transition.
 These kernels are invariant under changes in longitude of the central pixel, the latitude being held fixed, as one may have expected.
@@
 Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
-For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,192]$ \revisit{not match figure caption?}.
+For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$.
+\revisit{We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.}
 %
@@
 The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-As a consequence of the spin-2 symmetry, tt vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at separations $\beta=0,\pi$.
+As a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at separations $\beta=0,\pi$.
 %This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
@@
 ${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.}
-\revisit{why?}
 
@@
 
-The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}, where all the function have been normalized such that their global maxima is set to unity.
-The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$.
-Note that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
+The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}.
+While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, this feature of the kernels has been supressed as all the function have been normalized such that their global maxima is set to unity.
+This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
 At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
-In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property, $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
-\revisit{Holds for small beta and moderately high ell?}
+In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+\comment{Holds for small beta and moderately high ell?} \comment{I think its more general!
+See the notebook \href{https://github.com/adityarotti/Real-space-QU-to-EB-translation/blob/master/codes/notebooks_v2/}{Telescoping}}
 
-%We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property.
-Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.
-The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity.
-The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.
+\revisit{We can now understand the shifting left of the radial kernels on increasing the maximum multipole using this telescoping property.
+Lets say the function ${}_rf(\beta', \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta'_0$.
+The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller value angular distance $\beta$.
+The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}
 
 To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.
-We define a non-locality parameter $\beta_{o}$ as the angle beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ consistently falls below 1\% of its maximum.
-\revisit{Why $\beta_o$ rather than $\beta_0$?}
+We define a non-locality parameter $\beta_{0}$ as the angle beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ consistently falls below 1\% of its maximum.
 %For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}.
@@
 \beq
-\beta_o= {\rm min}\left(180,180 \frac{22}{\ell_{\rm max}} \right)
+\beta_0= {\rm min}\left(180,180 \frac{22}{\ell_{\rm max}} \right)
 \eeq
 provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
-This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.
+\revisit{This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.}

### 2018-05-25 articles/formalism/sections/kernel_paintbrush.tex
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

@@
 A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.
-A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.
-We predict that it should be there in higher fidelity data.
+
+%\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.
+We predict that it should be there in higher fidelity data.}
+\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal.
+We predict that a B-mode signal from filaments is present.
+A naive filament stacking analysis is only ideal for making E-mode detections.
+For detecting B-modes from filaments requires a more careful edge stacked filaments analysis.
+While its detectability from Planck requires more study, it should definitely be detectable in higher fidelity data.}
 
 The intuition from the real-space kernels holds also when we distort the shape of the filament.
-If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
+If the filament were bent around into a circle \comment{Not for an ellipse right?
+Maybe constant curvature argument is more general and more precise}, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
 The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.

### 2018-05-25 articles/formalism/sections/real_space_formalism.tex
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

@@
 \section{Polarization primer} \label{sec:pol-primer}
-\subsection{Constructing $E/B$ fields without harmonic space}
+%\subsection{Constructing $E/B$ fields without harmonic space}
+\subsection{A heuristic argument for real space construction of E/B fields on the sphere}
 %\comment{Need a better title for the section that gives the heuristic argument}
@@
 We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
-\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$, and a rotation around $\hat n_q$ by $-\gamma$.
-This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
+This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}}\\
 %
@@
 %
-
 Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
@@
 %The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
-The $\cal E/B$ fields are defined locally at point $\hat n$ in terms of the derivative operators $\eth$ and $\bar \eth$.
+The $\cal E/B$ fields are defined locally at point $\hat n$ in terms of the operators $\eth$ and $\bar \eth$.
 
-We can decompose the complex field $_{\pm 2}X$ into spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
-On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67},
+It is possible to decompose the complex field $_{\pm 2}X$ into spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67}:
 %
@@
 
-From the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$, and the identities given in \eq{eq:spinopylm}, it follows that the scalar fields $\mathcal{E}/\mathcal{B}$ are,
+From the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$, and the identities given in \eq{eq:spinopylm}, it follows that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the equations:
 %
 \beq \label{eq:pseudo}
-\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n});\qquad
+\mathcal{E}(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n})\qquad;\qquad
 \mathcal{B}(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} \sqrt{\frac{(\ell+2)!}{(\ell-2)!}} Y_{\ell m} (\hat{n}) \,,
@@
 %
-where the harmonic coefficients $a^{E}_{\ell m}$ and  $a^{B}_{\ell m}$ relate to the harmonic coefficients of the spin-2 polarization field via,
+where the harmonic coefficients $a^{E}_{\ell m}$ and  $a^{B}_{\ell m}$ relate to the harmonic coefficients of the spin-2 polarization field via the following equations:
 %
 \beq\label{eq:x2eb}
-a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big];\qquad a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
+a^{E}_{\ell m} = -\frac{1}{2} \Big[ {}_{+2}\tilde{X}_{\ell m} + {}_{-2}\tilde{X}_{\ell m} \Big]\qquad;\qquad a^{B}_{\ell m} = -\frac{1}{2i} \Big[ {}_{+2}\tilde{X}_{\ell m} - {}_{-2}\tilde{X}_{\ell m} \Big] \,.
 \eeq
@@
 \beq \label{eq:realeb}
-E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n});\qquad B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
+E(\hat{n}) = \sum_{\ell m} a^{E}_{\ell m} Y_{\ell m} (\hat{n})\qquad;\qquad B(\hat{n})  =\sum_{\ell m} a^{B}_{\ell m} Y_{\ell m} (\hat{n}) \,.
 \eeq
 %
-These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$), and are not local functions of Stokes $Q/U$.
+These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$) and are not local functions of Stokes $Q/U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
 
-\section{Real space polarization operators}
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
 Our derivation of real space operators is more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
-We introduce a matrix that encodes spin spherical harmonic basis vectors,
+We introduce a matrix that encodes spin spherical harmonic basis vectors:
 %
 \beq
-{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,%,
+{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,.
 \eeq
@@
 
-We now define the different polarization data vectors and their representation in real  space as and harmonic as follows,\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}
+We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}:
 %
@@
 
-We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$):
+We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$ and back):
 %
@@
 The sign conventions we have chosen match HEALPix.
-Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors as follows,
+Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors via the following equations:
 %
@@
   \beqry
-  \bar{X} &= \bar T  \bar{P}; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} ; \\
-  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
+  \bar{X} &= \bar T  \bar{P} \qquad; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} \,, \\
+  \tilde{X} &= \tilde T \tilde{S} \qquad; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
   \eeqry
@@
 %
-Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace,
+Finally we introduce the operators that project harmonic space data vector to the $E$ or $B$ subspace:
 %
@@
 %
-Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
+Note that these harmonic space matrices are idempotent: ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal: ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix: ($\tilde O_E + \tilde O_B = \mathbb{1}$).
 %
@@
 %
-The above relations for these harmonic space operators are exactly valid.  In the following sections we aim to derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
+The above relations for these harmonic space operators are exactly valid.  In the following sections we derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
 
+\section{Real space polarization operators} \label{sec:real_space_operators}
 \subsection{Evaluating scalar $E/B$ from Stokes $Q/U$}\label{sec:qu2eb}
@@
 In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
-We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{},
+We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{}:
 %
@@
 \bar{S} &=& {{}_0\mathcal{Y}} \, \tilde T^{-1}  \, {{}_2\mathcal{Y}^{\dagger}} \, \bar T  \bar{P}
-= \frac{1}{2} {{}_0\mathcal{Y}} \, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \bar{P}    \\
+= \frac{1}{2} {{}_0\mathcal{Y}} \, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \bar{P} \,,   \\
 &=&  \bar O \bar{P}. \label{eq:qu2eb_op}
@@
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations,
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations:
 %
@@
 As before, we use the notation that the index $e$ denotes the location where the scalar fields are being evaluated, and the index $q$ denotes the location from which  the Stokes parameters are being accessed.
-Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true,
+Using the conjugation properties of the spin spherical harmonic functions it can be shown that the following identity holds true:
 %
@@
 
-\noindent \eq{eq:qu2eb_ker_1} already presents a real space operator, but it is not in a form which can be practically implemented.
-To proceed, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles \cite{varshalovich},
+\eq{eq:qu2eb_ker_1} already presents a real space operator, but it is not in a form which can be practically implemented.
+To proceed, we use the fact that the $m$ sum over the product of two spin spherical harmonic functions can be expressed as a function of the Euler angles \cite{varshalovich}:
 %
@@
 where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ to align the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
-
-Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the complex function,
+Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the following complex function:
 %
@@
 Only the radial part $f(\beta_{qe})$ depends only on the angular separation between locations and hence  completely incorporates all the multipole $\ell$ dependence.
+\comment{Maybe we should  reference back to the heuristic argument here?}
 
-Employing \eq{eq:qu2eb_gen_kernel} to simplify the product of spherical harmonic functions in \eq{eq:qu2eb_ker_1}, the real space operator $\bar{O}$ can now be cast in this more useful form,
+Employing \eq{eq:qu2eb_gen_kernel} to simplify the product of spherical harmonic functions in \eq{eq:qu2eb_ker_1}, the real space operator $\bar{O}$ can now be cast in this more useful form:
 %
@@
 where $(\alpha_{qe}, ~\beta_{qe}, \gamma_{qe})$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})[\hat{n}_q] = \hat{n}_e$.
+\comment{This notation is unclear.}
 
@@
 
-The $E$/$B$ contribution from the Stokes parameters at some location $\hat{n}_q$ is given by the following expression (\eq{eq:op_qu2eb_rad} and \eq{eq:qu2eb_op}),
+The $E$/$B$ contribution from the Stokes parameters at some location $\hat{n}_q$ is given by the following expression (\eq{eq:op_qu2eb_rad} and \eq{eq:qu2eb_op}):
 %
@@
 The total map can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$: $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$.
-This operation can be cast concisely as,
+This operation can be cast concisely as:
 %
@@
 \beq
- \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
+ \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}} \,,
 \eeq
 %. $\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it
-is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.
+which is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.
 That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
@@
 Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
-The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows,
+The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows:
 %
@@
 \revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere.
-This operation can be expressed more concisely as follows,
+This operation can be expressed more concisely as follows:
 %
@@
 The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure.
-Expressed in the matrix-vector notation, inverse operator is given by,
+Expressed in the matrix-vector notation, inverse operator is given by the following equation:
 %
@@
 %%
-The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation,
+The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation:
 %
@@
 Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb_rad} by a change in sign on the off-diagonals of the block matrix.
-When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by,
+When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by the following equations:
 %
@@
 
+\comment{Add discussion here on the inverse greens function and why it changes as a function of position.}
+
 %--------------------------------------------------------
@@
 We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.
-The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}.
+The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as discussed in \sec{sec:mat_pol_intro}.
 It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
@@
 We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
-The Stokes parameters corresponding to each scalar mode are given by the following expressions,
+The Stokes parameters corresponding to each scalar mode are given by the following expressions:
 %
@@
 %
-We contract over all the matrix operators to arrive at the the real space operators. On working through the algebra it can be shown that the real space operators have the following form,
+We contract over all the matrix operators to arrive at the the real space operators. On working through the algebra it can be shown that the real space operators have the following form:
 %
@@
 \eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions,
+where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions:
 %
@@
 These functions can be further simplified using the identity of spin spherical harmonics given in \eq{eq:sum_spin_shf}.
-Specifically it can be shown that these functions reduce to the following mathematical forms,
+Specifically it can be shown that these functions reduce to the following mathematical forms:
 %
@@
 %
-where the radial functions are given by,
+where the radial functions are given by:
 %
@@
 %
-where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ \revisit{Is the prescript correct?} are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,
+where the functions ${{}_{\mdi}f}_{\ell}(\beta)$ are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms:
  %
@@
  %
-Finally the Stokes parameters corresponding to the respective scalar fields can be computed by evaluating the following expressions, 
+Finally the Stokes parameters corresponding to the respective scalar fields can be computed by evaluating the following expressions:
  %
@@
 where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity.
-Note that when the operators $\mathcal{I}^*$ and $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ and $\mathcal{D}_G$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ and $\mathcal{D}_B$.
-Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+\revisit{Note that when the operators $\mathcal{I}^*$ and $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ and $\mathcal{D}_G$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them as $\mathcal{I}_B$ and $\mathcal{D}_B$.} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 
 The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
-For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
+For all practical purposes $\mathcal{I}$ acts like an identity operator as ascertained by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
 $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^* \mathcal{D}=\mathcal{I}$.
-Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
+Using these properties\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.} of the operators $\mathcal{I}$ and $\mathcal{D}$ , one can verify that the real space operators satisfy the following identities:
 %
@@
 \beqry
-\bar O_E \, \bar O_E &=& \bar O_E;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
+\bar O_E \, \bar O_E &=& \bar O_E \qquad ;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
 \bar O_E \, \bar O_B &=& 0 \,,\\
@@
 %
-which are the real space analogues of \eq{eq:har_op_prop}.\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}  Thus they are orthogonal and idempotent in a band-limited sense.
-
+which are the real space analogues of their harmonic space counterparts discussed in \sec{sec:mat_pol_intro}.
+Thus they are exactly orthogonal and idempotent.
 Note that unlike in the harmonic case, the sum of the operators is the band limited identity operator $\mathcal{I}$.

### 2018-05-25 articles/formalism/sections/real_space_formalism.tex
updated the greens function interpretation around figure 3

@@
 \eeq
-\revisit{I'm having some trouble understanding the next 2 sentences.} The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
+\comment{I'm having some trouble understanding the next 2 sentences.} The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
 At the same time, the imaginary part of the function is constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
@@
 \beqry
-    {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,\\
-    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution_explicit}
+    {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
+    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
 \eeqry
@@
 The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-This is consistent with the Green's function interpretation of these kernels.
-Note that these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
-Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$.
-From \eq{eq:qu2eb_convolution_explicit} and \eq{eq:eb2qu_convolution_explicit} it is clear that $\mathcal{M}_G$ and $\mathcal{M}_B$ can be interpreted in the following ways,
-%\revisit{Recall that the angle $\gamma$ defines the rotation about the final z-axis which co-alligns the planar axes.
-Since the function $\mathcal{M}$ does not depend of this final orientation, it implies a rotational invariance of the fields constructed by convolving with this kernel.}
+These functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
+These observations are consistent with the Green's function interpretation of the kernel $\mathcal{M}_{G}$ which yield coordinate independent scalars E/B.
+From \eq{eq:qu2eb_radiation_concise} it is clear that $\mathcal{M}_G$ can be interpreted in the following ways:
 %
-\begin{subequations}
-\beqry
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat;\qquad
-\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat \,,\\
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat; \qquad
-\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat \,.
-\eeqry
-\end{subequations}
-
-\comment{Add discussion here on the inverse greens function and why it changes as a function of position.}
+\beq
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat \hspace{5 mm};\hspace{5 mm}
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat\,,
+\eeq
+%
+$\mathcal{M}^*_B$ is the Greens function of the operator that transforms E/B to Stokes parameters Q/U.
+The real and imaginary parts of $\mathcal{M}^*_B$ are identical irrespective of the galactic longitude, however they vary as a function of galactic latitude.
+This latitude dependent shape is necessary as the coordinate dependence of the Stokes parameters derived from the scalar E/B is built in via this Greens function.
+From \eq{eq:eb2qu_radiation} it is clear that $\mathcal{M}^*_B$ can be interpreted in the following manner:
+%
+\beq
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat \hspace{5 mm};\hspace{5 mm}
+\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat\,.
+\eeq
+%
+%Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$. 
+%\comment{Add discussion here on the inverse greens function and why it changes as a function of position.}
 

### 2018-05-29 articles/formalism/sections/introduction.tex
Working some on introduction

@@
 \section{Introduction}
-The Cosmic Mircowave Background is 10 percent polarized, but the polarization contains independent cosmological information.
+During reionization, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
+The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature \citep{1997NewA....2..323H}.
+The standard analysis technique converts the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, which are easier to compare to theory.
+The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations.
+Thus any $B$-modes that appear must be from:
+% Need citations for all...
+(1) primordial tensor perturbations (gravitational waves), which reveal the energy scale of inflation
+\citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
+(2) lensing of $E$-modes, which helps to reveal the distribution of matter in the universe;
+(3) foregrounds (especially Galactic synchrotron and dust emission)
+\citep{2016A&A...586A.133P};
+(4) unknown systematic problems in the data;
+(5) unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
+\citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.
 
-Standard technique is to convert Stokes parameters into scalar and pseudo-scalar modes, which are easier to compare to theory.
+The formalism for converting the Stokes parameters to scalar quantities is well established \citep{1997PhRvD..55.7368K,1997PhRvD..55.1830Z}.
+The reason we take a detailed look at it here is that with renewed focus on foreground contamination to the $B$-mode signal, we wanted to gain an intuition for what $E/B$ mode patterns arise from physical polarized structures in the galaxy.
+We also wanted to gain insight into the problem of masking and the non-locality of the $E/B$ fields compared to the Stokes parameters.
 
-The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations
-
-primordial tensor perturbations
-
-lensing of $E$-modes
-
-systematics checks
-
-exotic phenemena like cosmic birefringence
-
-The spin-0 $E$/$B$ modes relate to the spin-2 Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.
 However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.
@@
 
-Zaldarriaga explored the spatial real-space kernels in the flat-sky approximation \citep{}.
-
-In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.
+Zaldarriaga explored the spatial real-space kernels in the flat-sky approximation \citep{Zaldarriaga2001a}.
 

### 2018-05-29 articles/formalism/sections/real_space_formalism.tex
Working some on introduction

@@
 The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
+%
 The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
@@
 
-We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}:
+We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables, as in \citep{Zaldarriaga2001a}.
+}:
 %

### 2018-05-29 articles/formalism/sections/introduction.tex
Fixed reionizations -> recombination

@@
 \section{Introduction}
-During reionization, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
+During recombination, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
 The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature \citep{1997NewA....2..323H}.

### 2018-06-07 articles/formalism/sections/generalizedeb.tex
added definition y_dagger and introduced normalization in all necessary places. Revised some discussion with added clarity. Changes marked in red text left some comments to be addressed

@@
 \beq
-B(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
+b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
 \eeq
 %
-where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.  \comment{Need another symbol than $B$ for beam.}
-In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $B(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-Though the real space behavior of these two function $G(\beta)$ and $B(\beta)$ has these differences, in harmonic space they play identical roles.
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
+In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+Though the real space behavior of these two function $G(\beta)$ and $b(\beta)$ has these differences, in harmonic space they play identical roles.
 %
@@
 The dashed curves of the corresponding color depict the inverse of the harmonic functions.
-\textit{Bottom:} This figure depicts the normalized beam function $B(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.}
+\textit{Bottom:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.}
 \label{fig:example_gbeta}
@@
 \fig{fig:glbl} depicts the harmonic description $g_{\ell}$ for these respective radial kernels and beams.
- %The modified radial kernel resulting from Gaussian beams with ${\rm fwhm} =15' \,\&\, 12'$ are depicted in \fig{fig:bl_gbeta} as blue and orange curves respectively.
 Finally, the beam that the modified radial kernels appies to the $E/B$ fields we show in \fig{fig:gl_bbeta}.
@@
 \subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
-Recall that's on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
+Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
 Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:

### 2018-06-07 articles/formalism/sections/kernel_discussion.tex
added definition y_dagger and introduced normalization in all necessary places. Revised some discussion with added clarity. Changes marked in red text left some comments to be addressed

@@
 On transiting to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
-This transition can be most easily understood in the flat sky limit where $\gamma = -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} =e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} =1 + i0$.
+This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$.
 Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$.
@@
 \includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
-\caption{The top panel depicts the radial function  ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ while the bottom left and right panels show the radial functions ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max}) ~\&~ {}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, for fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
+\caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
+The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
 All the curves are normalized such that their maxima is set to unity.
@@
 In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
-\comment{Holds for small beta and moderately high ell?} \comment{I think its more general!
-See the notebook \href{https://github.com/adityarotti/Real-space-QU-to-EB-translation/blob/master/codes/notebooks_v2/}{Telescoping}}
 
@@
 Lets say the function ${}_rf(\beta', \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta'_0$.
-The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller value angular distance $\beta$.
+The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller angular distance $\beta$.
 The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}

### 2018-06-07 articles/formalism/sections/real_space_formalism.tex
added definition y_dagger and introduced normalization in all necessary places. Revised some discussion with added clarity. Changes marked in red text left some comments to be addressed

@@
 %\subsection{Constructing $E/B$ fields without harmonic space}
-\subsection{A heuristic argument for real space construction of E/B fields on the sphere}
+\subsection{A heuristic argument for real space construction of E/B fields on the sphere} \label{sec:qu2eb_heuristic}
 %\comment{Need a better title for the section that gives the heuristic argument}
@@
 
- CMB polarization is measured in terms of Stokes parameters, time averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.\footnote{Throughout we use the conventions of HEALPix \cite{healpix_primer}, measuring the polarization angle East of South.} Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system, and a rotation by an angle $\psi$ around the line of sight transforms them as
+ CMB polarization is measured in terms of Stokes parameters, time averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.\footnote{Throughout we use the conventions of HEALPix \cite{healpix_primer}, measuring the polarization angle East of South.} Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system and a rotation by an angle $\psi$ around the line of sight transforms them as:
 %
@@
 We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
-\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
-This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}}\\
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ (unit outward pointing radial vector at $(\theta_q,\phi_q)$) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
+This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}}
 %
@@
 \caption{This figure depicts the Euler angles in the z-y1-z2 convention.
-The cartesian coordinates shown in dark green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The cartesian coordinates shown in \revisit{dark solid green} are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in \revisit{dark solid red} are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
 The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
@@
 %
+
 Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
@@
 \beq
-\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}
+\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}} \,. \label{eq:invariant}
 \eeq
-\comment{I'm having some trouble understanding the next 2 sentences.} The real part of the function is constructed by product of functions $(Q\cos{2\alpha}, U\sin{2 \alpha})$ having the same parity and hence the real part must have even parity.
-At the same time, the imaginary part of the function is constructed by multiplying functions $(Q\sin{2 \alpha}, U\cos{2\alpha})$ of opposite parity and hence must have an odd parity.
+Further note that $Q~ \& \cos2 \alpha$ have even parity since they do not change sign when $\hat{x} \rightarrow -\hat{x}$ (or $\hat{y} \rightarrow -\hat{y}$  ) while $U~ \& \sin 2 \alpha$ change sign under this transformation and hence have odd parity.
+The real part of the function  ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is composed of $Q\cos{2\alpha} ~ \& ~ U\sin{2 \alpha}$ which are product of functions having the same parity and hence the real part must have even parity.
+Similarly the imaginary part of the function is composed of $Q\sin{2 \alpha}~\&~ U\cos{2\alpha}$ which are product of functions having opposite parity and hence the imaginary part must have an odd parity.
 Therefore we can make the association that contributions to  $(E+iB)(\hat n_e)$ must be proportional to $ {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$.
@@
 The same rotation $\mathcal{R}_{\hat{z}_q}(\psi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
-Thus we can conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the form
+Thus we can conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the form:
 \beq
@@
 %
-The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a fields with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
-The complementary spin-lowering operator $(\bar{\eth})$  similarly results with $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
+The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a field with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
+The complementary spin-lowering operator $(\bar{\eth})$  similarly results in a field with spin-$(s-1)$: $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
 The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
@@
 
-It is possible to decompose the complex field $_{\pm 2}X$ into spin spherical harmonic functions: ${}_{\pm 2}X(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
-On applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67}:
+It is possible to decompose the complex field $_{\pm 2}\bar{X}$ into spin spherical harmonic functions: ${}_{\pm 2}\bar{X}(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+Applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67}:
 %
@@
 
-From the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}X$, and the identities given in \eq{eq:spinopylm}, it follows that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the equations:
+From the definition of $\mathcal{E/B}$, the spin spherical harmonic decomposition of ${}_{\pm2}\bar{X}$, and the identities given in \eq{eq:spinopylm}, it follows that the scalar fields $\mathcal{E}/\mathcal{B}$ are given by the equations:
 %
@@
 %
-These $E/B$ fields are merely red-filtered versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$) and are not local functions of Stokes $Q/U$.
+These $E/B$ fields are merely \revisit{red-filtered} \comment{Is this unabbiguously understood as down weighing the high multipoles ?
+} versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$) and are not local functions of Stokes $Q/U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 \beq
-{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} \,.
+{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} ;\qquad  {}_{|s|}\mathcal{Y}^{\dagger}= \Delta \Omega \bmat _{+s}Y^{\dagger} & 0 \\ 0 & _{-s}Y^{\dagger} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm pix}} \,,
 \eeq
 %
-%where $s$ denotes the spin of the basis functions.
+\revisit{where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\dagger}$ differs from the conventional dagger operation by the factor $\Delta \Omega$ which is introduced to ensures the ortho-\textit{normality} of the basis functions: ${}_{|s|}\mathcal{Y}^{\dagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere.}
+
 We will be working with cases $s \in [0,2]$.
-Each column maps to a specific harmonic basis function (i.e.
+Each column of ${}_{|s|}\mathcal{Y}$ maps to a specific harmonic basis function (i.e.
 indexed by $\ell m$) and each row maps to a pixel on the sphere.
@@
 
-We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2} X$ and back):
+We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2}\bar{X}$ and back):
 %
@@
 \bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}}\, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \,, \\
-&=& -0.5 \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
-&=& -0.5 \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{\dag}_q  +  {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{\dag}_q + {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
+&=& -0.5 \Delta \Omega \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
+&=& -0.5 \Delta \Omega \begin{bmatrix} \sum ({}_{0}Y_e ~{}_{2}Y^{\dag}_q  +  {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & {\rm i}  \sum ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \\  - {\rm i} \sum  ({}_{0}Y_e ~ {}_{2}Y^{\dag}_q - {}_{0}Y_e~ {}_{-2}Y^{\dag}_q) & \sum ({}_{0}Y_e~ {}_{2}Y^{\dag}_q + {}_{0}Y_e ~{}_{-2}Y^{\dag}_q)  \end{bmatrix} \,, \label{eq:qu2eb_ker_1}
 \eeqrys
@@
 %
-where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ to align the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation become more obvious when this equation is written in terms of the Wigner-D functions.}.
+where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ to align the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation becomes more obvious when this equation is written in terms of the Wigner-D functions.}.
 Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the following complex function:
@@
  &=&\sum_{\ell m} {{_0}Y}_{\ell m}(\hat n_e) \, {{_{-2}}Y}^*_{\ell m}(\hat n_q) = \sum_{\ell} \sqrt{\frac{2\ell+1}{ 4 \pi}}{{_0Y}_{\ell 2}}(\beta_{qe},\alpha_{qe})\,,\\
-&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell 2} (\cos\beta_{qe}) \,, \label{eq:rad_ker_queb} \\
-&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] \quad {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
+&=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big]   \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} {\frac{2\ell+1}{ 4 \pi}} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}}P_{\ell}^2 (\cos\beta_{qe}) \,, \label{eq:rad_ker_queb} \\
+\mathcal{M}(\beta_{qe}, \alpha_{qe})  &=&  \Big [ \cos(2 \alpha_{qe}) + i \sin(2 \alpha_{qe} ) \Big] \quad {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \,, 
 \eeqry
@@
 Only the radial part $f(\beta_{qe})$ depends only on the angular separation between locations and hence  completely incorporates all the multipole $\ell$ dependence.
-\comment{Maybe we should  reference back to the heuristic argument here?}
+\revisit{Recall that we had guessed the general form of the kernel using simple heuristic arguments in \sec{sec:qu2eb_heuristic}.
+Here we have rigorously derived the exact form of the function $f(\beta)$.
+Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, as was argued to be a necessary property to yield a field of requisite spin.}
 
@@
 \beq\label{eq:op_qu2eb_rad}
-\bar O =-\bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} = -{{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
+\bar O =- \Delta \Omega \bmat  \mathcal{M}_{r} & \mathcal{M}_{i} \\  -\mathcal{M}_{i}  & \mathcal{M}_{r} \emat = - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & \sin(2\alpha_{qe})\\  -\sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
 \eeq
 %
-where $(\alpha_{qe}, ~\beta_{qe}, \gamma_{qe})$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated): $\mathcal{R}(\alpha_{qe},\beta_{qe},\gamma_{qe})[\hat{n}_q] = \hat{n}_e$.
-\comment{This notation is unclear.}
+where $(\alpha_{qe}, ~\beta_{qe}, \gamma_{qe})$ denote the Euler angles which rotate the local cartesian system at $\hat{n}_q$ (location where Stokes parameters are accessed) to the cartesian system at  $\hat{n}_e$ (location where the scalar fields are evaluated).
 
@@
 In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluate its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
+\revisit{This one to many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.}
 
@@
 %
-where the last line is a simple scalar multiplication between complex numbers.  The radiation kernel is then:
-\beq
- \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}} \,,
-\eeq
-%. $\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it
-which is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.
-That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
+where $\Delta \Omega$ denotes the pixel area and the last line is a simple scalar multiplication between complex numbers.
+The radiation kernel is then: $ \mathcal{M}_{G} =-  \Delta \Omega \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
 We display the kernel later in \fig{fig:vis_kernel}.
@@
 \includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{The local cartesian coordinate are only drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
-The value of the scalar field at location `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle (sphere).
-The convolutions are performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-Alternatively, one can compute the contribution from the Stokes parameter at location `q' to all the point on the blue circle(sphere) and this is a function of the Euler angle $\alpha_{eq}$.
-In the flat sky limit, since $\gamma=-\alpha$ there is no difference between the radiation and convolution kernels.}
+\caption{\revisit{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle(sphere), representative of the coordinate dependence of the Stokes parameters.
+The two sets of dotted lines drawn at representative points denote great circles, one which passes through the central point labelled `e' and the other chosen such that the two have locally orthogonal tangent vectors $(\hat{r},\hat{\phi})$.
+The angle $\alpha_{qe}$ defines a rotation operator that aligns the local $\hat{x}$ with $\hat{r}$.
+\textit{Convolution kernel:} The resultant scalar field at `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle.
+This convolution is performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
+\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `q' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
+On the flat sky $\gamma_{eq}=-\alpha_{qe}$ and consequently there is no difference between the radiation and convolution kernels.}}
 \label{fig:planar_euler_angles}
@@
 \beq \label{eq:qu2eb_convolution_explicit}
-\bmat E_e \\ B_e  \emat =- \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega\,,
+\bmat E_e \\ B_e  \emat =- \Delta \Omega\sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \,,
 \eeq
 %
-%where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
-\revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere.
+This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere.
 This operation can be expressed more concisely as follows:
@@
 \beqry 
-[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
-&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
+[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max}) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
+%&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
 &=& \Bigg\lbrace \mathcal{M}_{B} \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
@@
 %
-where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$.
-When expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
-We display the kernel in \fig{fig:vis_kernel}.
+where $\star$ denotes a convolution and $\mathcal{M}_{B} = - \Delta \Omega\mm(\beta_{eq},\gamma_{eq})$.
+When $\mm$ is expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
+\revisit{This many to one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.} We display the kernel in \fig{fig:vis_kernel}.
 %--------------------------------------------------------
@@
 \beq
-{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
+{\bar O}^{-1}=- \Delta \Omega\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat=- \Delta \Omega{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
 \eeq
@@
 \beqry
-    {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
-    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
+    {}_{+2}X(\hat{n}_q) &&=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm}\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
+    {}_{+2}X(\hat{n}_q) &&= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm}\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
 \eeqry
@@
 \begin{figure}[t] 
-
   %%%% NEW MG/MB
@@
 \end{figure}
-
+%
 We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and radiation kernels.
@@
 The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-These functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first three rows of \fig{fig:vis_kernel}.
+These functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}.
 These observations are consistent with the Green's function interpretation of the kernel $\mathcal{M}_{G}$ which yield coordinate independent scalars E/B.
@@
 \beq
-\bar O_{E/B} = 0.5 \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm 0.5 \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \,,\\
+\bar O_{E/B} = 0.5 \Delta \Omega \Bigg\lbrace \bmat \mathcal{I}_{r} & \mathcal{I}_{i} \\  -\mathcal{I}_{i}  & \mathcal{I}_{r} \emat \pm \bmat \mathcal{D}_{r} & \mathcal{D}_{i} \\  \mathcal{D}_{i}  & - \mathcal{D}_{r} \emat \Bigg\rbrace \,,\\
 \eeq
@@
 {}_{+2}X_{E/B}(\hat{n}_e) &=& 0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q)  \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
-&=& 0.5 \Bigg\lbrace  {}_{+2}X  \, \mathcal{I}^*_G \pm {}_{+2}X^* \, \mathcal{D}_G \Bigg\rbrace \hspace{.5cm } \textrm{\emph{   Radiation kernel}} \,, \\
+&=& 0.5 \Bigg\lbrace  {}_{+2}X  \, \mathcal{I}_G \pm {}_{+2}X^* \, \mathcal{D}_G \Bigg\rbrace \hspace{.5cm } \textrm{\emph{   Radiation kernel}} \,, \\
 &=& 0.5 \Bigg\lbrace \mathcal{I}_B \star {}_{+2}X\pm \mathcal{D}_B \star {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
@@
 where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity.
-\revisit{Note that when the operators $\mathcal{I}^*$ and $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ and $\mathcal{D}_G$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them as $\mathcal{I}_B$ and $\mathcal{D}_B$.} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+\revisit{Note that when the operators are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them by $\mathcal{I}_G=\Delta \Omega \mathcal{I}^*$ and $\mathcal{D}_G=\Delta \Omega \mathcal{D}$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 
-The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
+The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity: $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
 For all practical purposes $\mathcal{I}$ acts like an identity operator as ascertained by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
 $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^* \mathcal{D}=\mathcal{I}$.
-Using these properties\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.} of the operators $\mathcal{I}$ and $\mathcal{D}$ , one can verify that the real space operators satisfy the following identities:
+Using these properties\footnote{While testing the real space operator identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.} of the operators $\mathcal{I}$ and $\mathcal{D}$ , one can verify that the real space operators satisfy the following identities:
 %
@@
 Note that unlike in the harmonic case, the sum of the operators is the band limited identity operator $\mathcal{I}$.
-This non-exactness is representative of the loss of information resulting from making this transformation on the measured data with some imposed band limit.
+This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
 Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact and a more crucial property of the operators.

### 2018-06-08 articles/formalism/sections/kernel_paintbrush.tex
added definition y_dagger and introduced normalization in all necessary places. Revised some discussion with added clarity. Changes marked in red text left some comments to be addressed
some updates in the  introduction and discussion sections

@@
 \paragraph{Polarization signature of magnetized filaments}
+% 
+\begin{figure}[t]
+\includegraphics[width=0.5\columnwidth]{line.pdf}
+\includegraphics[width=0.5\columnwidth]{spiral.pdf}
+\caption{ The polarization signals of toy filament structures.
+In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.
+The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
+Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.
+B-modes are only non-zero at the ends.
+Right panels: in a curved filament, the E-mode is again positive along the filament.
+Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.
+The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
+In all images, the longitude angle increases to the left (East in sky convention).\comment{Colorbar on plots to give a sense of B amplitude as compared to E.}}
+\label{fig:polfilaments}
+\end{figure}
+%
+
 The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
@@
 The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
-
-\begin{figure}
-  \includegraphics[width=0.5\columnwidth]{line.pdf}
-  \includegraphics[width=0.5\columnwidth]{spiral.pdf}
-  \caption{
-    The polarization signals of toy filament structures.
-    In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.
-The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
-    Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.
-B-modes are only non-zero at the ends.
-Right panels: in a curved filament, the E-mode is again positive along the filament.
-Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.
-The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
-    In all images, the longitude angle increases to the left (East in sky convention).}
-  \label{fig:polfilaments}
-\end{figure}

### 2018-06-11 articles/formalism/sections/discussion.tex
added explanation for the alpha and gamma as being the radiating and the convolution kernels, still sharpening the explanation
Editing pass and notation cleanup.
Added some reference and some detail to kernel paintbrush section.

@@
 
-In this article we have cast the standard CMB polarization analysis operations in a vector matrix notation.
-Using this concise notation we derive the real space operators that translate the Stokes vector \vp{} to  the vector of scalars \vs and vice versa.
+\begin{itemize}
+\item Summarize what has been achieved in this peice of work.
+\item Whats new as compared to work done by Zaldariaga?
+\item Not having to compute spin spherical harmonics.
+\item Potentially allows for TOD to E/B map generation.
+\item Compact kernels and understanding of why mask apodization works.
+\item Can you deconvolve anisotropic compact kernels?
+Meaning different radial cut-off in different portions of the sky.
+This will be useful to dealing with foregrounds.
+Its not obvious if this can be achieved in harmonic space.
+\item The relation to galaxy shear E/B estimates.
+\item Understanding E/B signatures of magentized filaments.
+\end{itemize}
+
+\revisit{A similar equation for real space $E$ \& $B$ operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
+
+In this work we present real space operators on the sphere that transform maps of Stoke Q/U parameters to scalars E/B.
+We  also present real space operators that decompose maps of Stokes Q/U parameters into the parts that only contribute to E/B modes.
+We introduced a vector-matrix notation which allows for concise book keeping of all the operations involved and simplifies the derivation of the real space operators.
+
+These real space operators provide a spatially intuitive way of understanding construction of the scalar modes.
+We explicitly  demonstrated that all the operators can be separated into a band limit independent azimuthal operation and band limit dependent radial weights.
+The azimuthal part of the operator is primarily responsible for the requisite spinorial decomposition, while the radial weights determine the non-local dependence of the construction of the resultant fields.
+We define the $\beta_0$ parameter using an empirical relation to characterize the non-locality and demonstrate that it scales $\propto \ell_{\rm max}^{-1}$.
+
+Our careful study of the real space operators reveals the dual interpretation of the operators as either the Greens function or a convolving beam depending on whether the kernels are expressed in terms of the forward rotation Euler angles or the inverse rotation Euler angles.
+While the convolution interpretation is familiar to all, the Green's function interpretation is a new one arising from this work.
+In particular the Green's function interpretation allows us to think of ${}_{+2}X$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
+The resultant E/B maps can be then understood as arising from superposition of the radiating field from all the spin charges on the sphere.
+
  We explicitly demonstrated that this real space operation can be simply interpreted as a convolution over the complex field $[Q - i U]$ (or $[E + iB]$) with an effective complex beam which is fully expressed in terms of the $Y_{\ell 2}$ spherical harmonic functions.
 We also use this vector matrix notation to derive real space operators which allow the direct decomposition of the full Stokes vector \vp{} into the vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
-
-Given the effective beam interpretation of these real space operators we derive the harmonic coefficients of these effective beams at the north galactic pole.
-Using these harmonic coefficients we provide a prescription for computing the convolution kernels at any position on the sphere using the standard Healpix built in functions.
-The procedure is equivalent to parallel transporting the beam at the north pole to any desired location on the sphere.
-We implement the prescription to compute the  kernel at different location on the sphere and provide simple explanations in terms of Euler angles for the observed variations.
-
-These real space convolution kernels provide a spatially intuitive way of understanding the construction of the scalar modes.
-We explicitly show that the kernels separates into an band limit independent azimuthal operation around any given direction which is primarily responsible for requisite decomposition, while the band limit dependent radial weights can be interpreted as some isotropic smoothing operation.
-These radial weights primarily determine the non-local dependence of the construction of the respective fields at any location on the Stoke field.
-We define the parameter $\beta_0$ as a means to characterize the non-locality and show that $\beta_0$ scales $\propto \ell_{\rm max}^{-1}$.
-We show that this non-locality parameter also characterized the non-locality of the $\bar{O}_{E/B}$ operators.
 
@@
 On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}
+
+\input{sections/kernel_paintbrush.tex}

### 2018-06-11 articles/formalism/sections/generalizedeb.tex

@@
 %--------------------------------------------------------
-\subsection{Generalized polarization operators}
+\subsection{Generalized polarization operators}\label{sec:generalized_operators}
 With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.

### 2018-06-11 articles/formalism/sections/introduction.tex

@@
 Here we begin with a heuristic argument that makes transparent the real space construction of E/B modes on the sphere.
-We then discuss the standard harmonic space procedures for this operation.
+We discuss the standard harmonic space procedures for this operation.
 Finally we introduce the matrix-vector notation which yields a more concise description of the harmonic space procedures.
-In \sec{sec:real_space_operators} we derive and discuss the real space operators that transform Q/U to E/B and vice versa.
+In \sec{sec:qu2eb} and \sec{sec:eb2qu} we derive and discuss the real space operators that transform Q/U to E/B and vice versa.
 In \sec{sec:visualize_operator} we evaluate these real space operators and present visualizations of these functions.
-We also derive a real space operator that decomposes the Stokes Q/U  parameters into components that correspond to E and B modes respectively.
-Here we also discuss the locality of the real space E \& B operators.
-In \sec{sec:numerical_implementation} we implement these operators to evaluate E \& B  maps from the Stokes parameters Q \& U and compare these maps and their spectra from those derived using Healpix.
-We conclude with a discussion and the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.
+In \sec{sec:purify_stokes_qu} we derive a real space operator that decomposes the Stokes Q/U  parameters into components that correspond to E and B modes respectively and present its visualizations.
+In \sec{sec:radial_locality} we study the locality of the real space operators and explore its band limit dependence.
+In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by varying the non-locality parameter and discuss the connection to the spin raising and lower operators.
+We conclude with a summary and discuss the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.

### 2018-06-11 articles/formalism/sections/kernel_discussion.tex

@@
 Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
-The empirical relation
+\revisit{The empirical relation:
 \beq
-\beta_0= {\rm min}\left(180,180 \frac{22}{\ell_{\rm max}} \right)
+\beta_0= {\rm min}\left(180,180 \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
 \eeq
-provides a reasonable estimate of this transition point for  ${}_{\mm}f$.
-\revisit{This empirical function also provides a reasonable estimate for the transition point for the function ${}_{\md}f$ particularly for high $\ell_{\rm max}$ and it systematically over-predicts the transition point for the function ${}_{\mi}f$ as seen in \fig{fig:rad_ker_decay}.}
+with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}.
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ provides the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.}

### 2018-06-11 articles/formalism/article.tex
Added some reference and some detail to kernel paintbrush section.
Split kernel image and moved MG/MB to right after they are introduced.
Working some on introduction
significant updates to discussions and polarized filaments sections

@@
 \usepackage{caption}
+\usepackage{array}
+\usepackage{aas_macros}
+
 \renewcommand{\thesubfigure}{(\roman{subfigure})}
@@
 
+\newcommand{\na}{New Astronomy}
+%\newcommand{\aap}{Astronomy and Astrophysics}
 \newcommand{\beq}{\begin{equation}}
@@
   \noindent 
-  \revisit{  We derive full-sky, real-space operators that convert between polarization Stokes $Q$/$U$ parameters to the coordinate-independent, scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background and cosmic shear analysis.
-The covolution kernels split naturally into angular and radial parts, and we show explicitly how the spatial extent of the convolution kernel depends on the targeted band-limit.
-We show that an arbitrary radial dependence can produce $E$/$B$-like maps and that these are simply filtered versions of the standard $E$/$B$ maps.
-This allows us to compute $E$/$B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
-We can compute power spectra using standard techniques, and recover the power spectrum of the sky with a simple window function.
-The spatial structure of the real space operator provides some intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds.
+  \revisit{We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters to the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background(CMB) and cosmic shear analysis.
+The covolution kernels split naturally into angular and radial parts and we show explicitly how the radial extent of the convolution kernel depends on the targeted band-limit.
+We show that an arbitrary radial dependence can produce $E/B$-like maps and that these are simply filtered versions of the standard $E/B$ maps.
+This allows us to compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
+We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function.
+The spatial structure of the real space operator provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds and we predict non-zero B-mode signature that is expected from finite filaments in the sky.
     %
@@
 \include{./sections/generalizedeb}
+\input{./sections/kernel_paintbrush.tex}
 \include{./sections/discussion}
@@
 \bibliographystyle{JHEP}
-\bibliography{ref}
+\bibliography{ref,refkmh}
 

### 2018-06-11 articles/formalism/sections/discussion.tex
significant updates to discussions and polarized filaments sections

--- 2017-11-01 articles/formalism/sections/discussion.tex
@@
 
-In this article we have cast the standard CMB polarization analysis operations in a vector matrix notation.
-Using this concise notation we derive the real space operators that translate the Stokes vector \vp{} to  the vector of scalars \vs and vice versa.
-We explicitly demonstrated that this real space operation can be simply interpreted as a convolution over the complex field $[Q - i U]$ (or $[E + iB]$) with an effective complex beam which is fully expressed in terms of the $Y_{\ell 2}$ spherical harmonic functions.
-We also use this vector matrix notation to derive real space operators which allow the direct decomposition of the full Stokes vector \vp{} into the vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
+We introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of CMB polarization maps.
+This notation simplifies the derivation of the real space operators.
+We presented a first derivation of the real space operators on the sphere that transforms the Stokes vector \vp{} to into a vector of scalars \vs{} and vice versa.
+We also presented real space operators that directly decompose the full Stokes vector \vp{} into vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
 
-Given the effective beam interpretation of these real space operators we derive the harmonic coefficients of these effective beams at the north galactic pole.
-Using these harmonic coefficients we provide a prescription for computing the convolution kernels at any position on the sphere using the standard Healpix built in functions.
-The procedure is equivalent to parallel transporting the beam at the north pole to any desired location on the sphere.
-We implement the prescription to compute the  kernel at different location on the sphere and provide simple explanations in terms of Euler angles for the observed variations.
+These real space operators provide a spatially intuitive way of understanding the different decompositions of the Stokes vector.
+We explicitly  demonstrated that all the real space operators have the common characteristic  of being separable into a azimuthal part that is band limit independent and radial part that incorporates all the band limit dependence.
+The azimuthal part of the operator is primarily responsible for the requisite spinorial decomposition, while the radial weights determine the non-local dependence of the construction of the resultant fields on the original fields.
+Using the self similarity property of the radial functions we define a non-locality parameter and argued that it is proportional to $\ell_{\rm max}^{-1}$.
+The scalar decomposition of the Stokes parameters being of primary interest,  we empirically derived the non-locality parameter $\beta_0$ for this operation and showed that the proportionality constant $\ell_{0}=22$ provided a good prediction for the angular distance at which the ${}_{\mm}f$ falls below 1\% of its maxima as seen in \fig{fig:rad_ker_decay}.
 
-These real space convolution kernels provide a spatially intuitive way of understanding the construction of the scalar modes.
-We explicitly show that the kernels separates into an band limit independent azimuthal operation around any given direction which is primarily responsible for requisite decomposition, while the band limit dependent radial weights can be interpreted as some isotropic smoothing operation.
-These radial weights primarily determine the non-local dependence of the construction of the respective fields at any location on the Stoke field.
-We define the parameter $\beta_0$ as a means to characterize the non-locality and show that $\beta_0$ scales $\propto \ell_{\rm max}^{-1}$.
-We show that this non-locality parameter also characterized the non-locality of the $\bar{O}_{E/B}$ operators.
+Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a convolving beam depending on whether the kernels are expressed in terms of the forward rotation Euler angles or the inverse rotation Euler angles.
+While the convolution interpretation is a familiar one, the Green's function interpretation is a new way of looking at this operation.
+This new interpretation allows us to think of ${}_{+2}X$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
+The resultant complex scalar maps can be then understood as arising from superposition of the radiating field emanating from all the spin charges on the sphere.
+The $E/B$ mode maps are merely the real and imaginary parts of this resultant complex scalar field.
 
-Finally we present the generalized real space operators $\bar{O}'$, which are derived by allowing the radial function to vary from its default form.
-We derive constraints on the modifications to these radial function by demanding the inverse operator to be well defined.
-We argue that these modifications to the radial kernel can be be interpreted as a some smoothing smoothing operation on the scalar fields with a circularly symmetric instrument beam.
-We also show that as long as these radial function are invertible, the standard spectra can always be recovered from these modified $E'$ \& $B'$ maps.
-The main advantage of modifying these radial function is the ability to generate more locally defined $E$ and $B$ mode maps.
-This could potentially be useful in reducing foreground contamination on large angular scales in a full sky $E/B$ analysis.
-Also defining more locally constructed scalar fields $E$ \& $B$ can be used to circumvent the power leakage nuisance.
-We explore and demonstrate the working of these ideas in the next paper in this series.
+\revisit{A similar equation for real space $E$ \& $B$ operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
+
+Understanding the non-locality of the real space operators, allowed us to generalize the real space operators $\bar{O}'$ and its inverse ${\bar O}'^{-1}$, which transform between the spin-2 and spin-0 representations of the CMB polarization.
+We presented a method of systematically generalizing these operators by introducing the harmonic space operator $\tilde{\mathcal{G}}$ which in effect causes the radial function to vary from its default form.
+We show that these modifications to the radial kernel can be interpreted as a smoothing operation on the scalar fields with a circularly symmetric instrument beam.
+We argue that one can choose any arbitrary form for $\tilde{\mathcal{G}}$ as long as one adheres to the constraint that $\tilde{\mathcal{G}}^{-1}$ and $\tilde{\mathcal{G}}^{-2}$ are well defined operators.
+These constraints are necessary to ensure that all the standard CMB spectra are recoverable from the modified $E'$/$B'$ maps emerging from the modified operators on the Stokes parameter maps.
+Noting that that the standard spin raising $\eth^2$ and spin lowering $\bar{\eth}^2$ operators are special cases of these generalized operators, we presented a band limited representation of these operators.
+
+\revisit{Discussion on results from polarized filaments filaments, compare and contrast with those in \cite{Zaldarriaga2001a}.}
+
+There are several advantages and alternative analysis routes that emerge from employing these real space operators for analysis of CMB polarization maps.
+To begin with, one does not need to evaluate the spin harmonic functions as the real space operators only rely on computing the Euler angles which can be done on the fly and the $P_{\ell}^{2}$ functions need to be tabulated only once for analysis at some predetermined resolution.
+Note that this real space analysis method trivially generalizes to analyzing maps of arbitrary spin.
+Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable, since the $E/B$ contribution from the Stokes charge in each pixel can be evaluated independently.
+Also note that the evaluation of contribution from charges in the masked portion of the sky can be easily omitted, unlike in the harmonic analysis.
+Given the Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.
+Since the real space operators offer the ability of tuning the locality of $E/B$ maps, this can be potentially exploited to reduce foreground contamination from distant parts of the sky.
+For instance the real space operators can be defined such that the locality of their radial kernels is varied on different portions of the sky, dictated by say the foreground morphology, resulting in some scalar $E'/B'$ maps.
+While this idea seems promising, the usefulness of this implementation will depend on whether the standard $E/B$ mode spectra are recoverable from scalar maps derived in this fashion.
+Note that it would be fairly non-trivial to think of such implementations using conventional harmonic space methods.
+
+Results demonstrating the equivalence of these real space methods to the conventional harmonic space methods and from explorations of some of the ideas discussed above will be presented in the second part of this series of papers.
+
 %\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.

### 2018-06-11 articles/formalism/sections/generalizedeb.tex
significant updates to discussions and polarized filaments sections

@@
 \subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
-Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{-2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
+Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
 Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:
@@
 \beq 
+\label{eq:bl_ebdef_lower}
 [\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
-\label{eq:bl_ebdef_lower}
 \eeq

### 2018-06-11 articles/formalism/sections/kernel_discussion.tex
significant updates to discussions and polarized filaments sections

@@
 with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}.
-Setting $\ell_{0}=10$ and $\ell_{0}=32$ provides the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.}
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.} \comment{How sensitive is this transition point to $\ell{\rm min}$?}
+
+\comment{Compare the fitted slope to the one in the Zaldariaga paper.}

### 2018-06-11 articles/formalism/sections/kernel_paintbrush.tex
Added colorbar
significant updates to discussions and polarized filaments sections

@@
-\paragraph{Polarization signature of magnetized filaments}
+\section{Understanding polarization signatures of magnetized filaments}
 % 
@@
 \includegraphics[width=0.5\columnwidth]{spiral.pdf}
+\includegraphics[width=1.0\columnwidth]{colorbar.pdf}
 \caption{ The polarization signals of toy filament structures.
@@
 The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
-In all images, the longitude angle increases to the left (East in sky convention).\comment{Colorbar on plots to give a sense of B amplitude as compared to E.}}
+In all images, the longitude angle increases to the left (East in sky convention).
+All plot are on a common, arbitrary color scale.}
 \label{fig:polfilaments}
@@
 The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.
-However, unlike a complete ring, this filament is not a configuration with a definite parity.
+However, unlike a circular ring, this filament is not a configuration with a definite parity.
 Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
@@
 \revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal.
-We predict that a B-mode signal from filaments is present.
-A naive filament stacking analysis is only ideal for making E-mode detections.
-For detecting B-modes from filaments requires a more careful edge stacked filaments analysis.
-While its detectability from Planck requires more study, it should definitely be detectable in higher fidelity data.}
+We predict that a B-mode signal from filaments should be present.
+A naive filament stacking analysis is only suited for making E-mode detections.
+Detecting B-modes from filaments requires a more careful edge stacked filaments analysis.
+While the detectability of B-mode signature from filaments from Planck data calls for a more careful assessment, it should definitely be detectable in higher fidelity data.}
 
 The intuition from the real-space kernels holds also when we distort the shape of the filament.
-If the filament were bent around into a circle \comment{Not for an ellipse right?
-Maybe constant curvature argument is more general and more precise}, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
+If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern (note that this cancellation would not happen for an ellipse or any loop of non-contant radius of curvature).
 The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
@@
 The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
+\comment{Add that the spiral has a constant radius of curvature and thats the reason you dont see B-mode signal in intermediate regions of the spiral!}
+
+\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the tangent to the filament at any given point and this results in dominantly generating an E-mode signal while the B-mode signal is present only near the edges.
+By similar arguments it can be seen that that polarization pattern will be dominated by B-modes if the polarization vector is always at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
+Therefore a careful study of the $E/B$ mode power in a filament can provide insights into the orientation of the magnetic field with respect to the length of the filament, assuming the polarization vectors (headless) are always perpendicular to the magnetic field vector.}

### 2018-06-12 articles/formalism/sections/real_space_formalism.tex
some updates in the  introduction and discussion sections
Minor edits in pol primer

@@
 %\subsection{Constructing $E/B$ fields without harmonic space}
-\subsection{A heuristic argument for real space construction of E/B fields on the sphere} \label{sec:qu2eb_heuristic}
+\subsection{Heuristic, real-space construction of E/B fields on the sphere} \label{sec:qu2eb_heuristic}
 %\comment{Need a better title for the section that gives the heuristic argument}
@@
 
- CMB polarization is measured in terms of Stokes parameters, time averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.\footnote{Throughout we use the conventions of HEALPix \cite{healpix_primer}, measuring the polarization angle East of South.} Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system and a rotation by an angle $\psi$ around the line of sight transforms them as:
+ CMB polarization is measured in terms of Stokes parameters, time averages of the linear polarization of the electric field along cartesian axes perpendicular to the line of sight.\footnote{Throughout we use the conventions of HEALPix \cite{healpix_primer}, measuring the polarization angle East of South.} Thus Stokes $Q$ and $U$ depend on the choice of the local coordinate system, and a rotation by an angle $\psi$ around the line of sight transforms them as:
 %
@@
 \eeq
-Equivalently the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin-2 field \cite{Zaldarriaga1997}.
+Equivalently, the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin $\pm$2 field \cite{Zaldarriaga1997}.
 
@@
 We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
-\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ (unit outward pointing radial vector at $(\theta_q,\phi_q)$) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
 This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}}
@@
 The cartesian coordinates shown in \revisit{dark solid green} are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in \revisit{dark solid red} are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
-The blue coordinates at different locations are representative of the parallel transport along the geodesic connection the two locations $\hat{n}_q$ \& $\hat{n}_e$ on the sphere.}
+The blue coordinates at different locations are representative of the parallel transport along the geodesic connection between the two locations $\hat{n}_q$ and $\hat{n}_e$ on the sphere.}
 \label{fig:euler_angles}
@@
 
+We consider the impact of local rotations on these Euler angles.
 Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
 $\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)] =  {}_{+2}X(\hat{n}_q) e^{-i2\psi} $.
-This same rotation by $\psi$ alters the Euler angle $\alpha_{qe}$ (that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$): $\mathcal{R}_{\hat{z}_q}(\psi)[\alpha_{qe}] = \alpha_{qe} - \psi$.
+This same rotation by $\psi$ alters the Euler angle $\alpha_{qe}$, the angle that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$, so that $\mathcal{R}_{\hat{z}_q}(\psi)[\alpha_{qe}] = \alpha_{qe} - \psi$.
 Therefore one can see that $\mathcal{R}_{\hat{z}_q}(\psi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\psi}$.
@@
 \eeq
-Further note that $Q~ \& \cos2 \alpha$ have even parity since they do not change sign when $\hat{x} \rightarrow -\hat{x}$ (or $\hat{y} \rightarrow -\hat{y}$  ) while $U~ \& \sin 2 \alpha$ change sign under this transformation and hence have odd parity.
-The real part of the function  ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is composed of $Q\cos{2\alpha} ~ \& ~ U\sin{2 \alpha}$ which are product of functions having the same parity and hence the real part must have even parity.
-Similarly the imaginary part of the function is composed of $Q\sin{2 \alpha}~\&~ U\cos{2\alpha}$ which are product of functions having opposite parity and hence the imaginary part must have an odd parity.
+Thus we can build a scalar polarization quantity out of such combinations.
+Further note that both $Q$ and $\cos2 \alpha$ have even parity since they do not change sign when $\hat{x} \rightarrow -\hat{x}$ (or $\hat{y} \rightarrow -\hat{y}$).
+Meanwhile $U$ and $\sin 2 \alpha$ change sign under this transformation and hence have odd parity.
+The real part of the function  ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ must have even parity, because it is composed of terms containing $Q\cos{2\alpha}$ and  $U\sin{2 \alpha}$ which are product of functions with the same parity.
+Similarly, the imaginary part of the function must have odd parity, because it is composed of $Q\sin{2 \alpha}$ and $U\cos{2\alpha}$ which are product of functions with opposite parity.
 Therefore we can make the association that contributions to  $(E+iB)(\hat n_e)$ must be proportional to $ {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}}$.
@@
 %--------------------------------------------------------
-\subsection{Purifying Stokes parameters $Q$/$U$ for $E$/$B$ modes}
+\subsection{Purifying Stokes parameters $Q$/$U$ for $E$/$B$ modes} \label{sec:purify_stokes_qu}
 We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.

### 2018-06-12 articles/formalism/sections/real_space_formalism.tex
Hit upon ddagger solution to the problem with cal Y.

@@
 
-It is possible to decompose the complex field $_{\pm 2}\bar{X}$ into spin spherical harmonic functions: ${}_{\pm 2}\bar{X}(\hat{n}) = \sum_{\ell m} {}_{\pm 2} X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
+It is possible to decompose the complex field $_{\pm 2}\bar{X}$ into spin spherical harmonic functions: ${}_{\pm 2}\bar{X}(\hat{n}) = \sum_{\ell m} {}_{\pm 2} \tilde X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
 Applying the spin raising and lowering operators on the spin spherical harmonic functions leads to the following identities \cite{goldberg67}:
@@
 %
-These $E/B$ fields are merely \revisit{red-filtered} \comment{Is this unabbiguously understood as down weighing the high multipoles ?
-} versions of $\mathcal{E}/\mathcal{B}$ (their spherical harmonic coefficients of expansion are related by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$) and are not local functions of Stokes $Q/U$.
+These $E/B$ fields are merely versions of $\mathcal{E}/\mathcal{B}$ that downweight higher-$\ell$ modes  (their spherical harmonic coefficients of expansion are reduced by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$).
+They are not local functions of Stokes $Q/U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 \beq
-{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} ;\qquad  {}_{|s|}\mathcal{Y}^{\dagger}= \Delta \Omega \bmat _{+s}Y^{\dagger} & 0 \\ 0 & _{-s}Y^{\dagger} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm pix}} \,,
+{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} ;\qquad  {}_{|s|}\mathcal{Y}^{\ddagger}= \Delta \Omega \bmat _{+s}Y^{\dagger} & 0 \\ 0 & _{-s}Y^{\dagger} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm pix}} \,,
 \eeq
 %
-\revisit{where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\dagger}$ differs from the conventional dagger operation by the factor $\Delta \Omega$ which is introduced to ensures the ortho-\textit{normality} of the basis functions: ${}_{|s|}\mathcal{Y}^{\dagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere.}
+where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
+We introduce this to ensures the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.
 
@@
   \beqry
-  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\dagger}  \bar X  ; \\
-  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} \bar S \,.
+  \bar X &=  {{}_2\mathcal{Y}}  \tilde X; &\qquad \tilde X ={{}_2\mathcal{Y}}^{\ddagger}  \bar X  ; \\
+  \bar S &=  {{}_0\mathcal{Y}} \tilde S; &\qquad  \tilde S =  {{}_0\mathcal{Y}}^{\ddagger} \bar S \,.
   \eeqry
@@
 \beqrys
-\bar{S} &=& {{}_0\mathcal{Y}} \, \tilde T^{-1}  \, {{}_2\mathcal{Y}^{\dagger}} \, \bar T  \bar{P}
-= \frac{1}{2} {{}_0\mathcal{Y}} \, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \bar{P} \,,   \\
+\bar{S} &=& {{}_0\mathcal{Y}} \, \tilde T^{-1}  \, {{}_2\mathcal{Y}^{\ddagger}} \, \bar T  \bar{P}
+= \frac{1}{2} {{}_0\mathcal{Y}} \, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\ddagger}} \, \bar T \bar{P} \,,   \\
 &=&  \bar O \bar{P}. \label{eq:qu2eb_op}
@@
 \beqrys
-\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}}\, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \,, \\
+\bar{O} &=& \frac{1}{2} {{}_0\mathcal{Y}}\, \tilde T^{\dagger} {{}_2\mathcal{Y}^{\ddagger}} \, \bar T \,, \\
 &=& -0.5 \Delta \Omega \yzmat{e} \qutoxd \ymatc{q} \qutox   \,, \\
@@
 \beqry
-\bar{P} &=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} {{}_2\mathcal{Y}} \,\tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S}\,,  \\
+\bar{P} &=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde T {{}_0\mathcal{Y}^{\ddagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} {{}_2\mathcal{Y}} \,\tilde T {{}_0\mathcal{Y}^{\ddagger}}\bar{S}\,,  \\
 &=&  \bar O^{-1} \bar{S}\,.
@@
 \beqry
-\bar{P}_E &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E  \tilde T^{\dagger}  {{}_2\mathcal{Y}^{\dagger}}\, \bar T ]\bar{P}  \,, \nonumber \\
+\bar{P}_E &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E \tilde T^{-1} {{}_2\mathcal{Y}^{\ddagger}}\, \bar T] \bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E  \tilde T^{\dagger}  {{}_2\mathcal{Y}^{\ddagger}}\, \bar T ]\bar{P}  \,, \nonumber \\
 &=&  \bar O_{E} \bar{P} \,,\nonumber \\
-\bar{P}_B &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_B \tilde T^{-1} {{}_2\mathcal{Y}^{\dagger}} \bar T]\bar{P}  \,, \\
-&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}}\, \tilde T  \tilde O_B \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}   \,, \nonumber\\
+\bar{P}_B &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_B \tilde T^{-1} {{}_2\mathcal{Y}^{\ddagger}} \bar T]\bar{P}  \,, \\
+&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}}\, \tilde T  \tilde O_B \tilde T^{\dagger} {{}_2\mathcal{Y}^{\ddagger}}\, \bar T] \bar{P}   \,, \nonumber\\
 &=&  \bar O_{B} \bar{P} \,. \nonumber

### 2018-06-12 articles/formalism/sections/real_space_formalism.tex
More minor edits.

@@
 %
-where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
-We introduce this to ensures the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.
+where $s$ denotes the spin of the basis functions and our \revisit{definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
+We introduce this to ensure the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.
+[Orthonormal only in infimetesimal pixel limit?]}
 
@@
 %
-The different symbols have the same meaning as that discussed in \sec{sec:pol-primer}, except that the subscript ${\ell m}$ for the spherical harmonic coefficients is suppressed for cleaner notation.
+The symbols have the same meaning as in \sec{sec:pol-primer}, except that the subscript ${\ell m}$ for the spherical harmonic coefficients is suppressed for cleaner notation.
 
@@
 \beqry
-\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }   ~~;~~ \tilde S_E = \tilde O_E  \tilde S ,\\
-\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} } ~~; ~~ \tilde S_B = \tilde O_B  \tilde S .
+\tilde O_E &=& \bmat \mathbb{1} & \mathbb{0} \\ \mathbb{0} & \mathbb{0} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }; \qquad \tilde S_E = \tilde O_E  \tilde S ,\\
+\tilde O_B &=& \bmat \mathbb{0} & \mathbb{0} \\ \mathbb{0} & \mathbb{1} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm alms} }; \qquad \tilde S_B = \tilde O_B  \tilde S .
 \eeqry
@@
 %
-Note that these harmonic space matrices are idempotent: ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal: ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix: ($\tilde O_E + \tilde O_B = \mathbb{1}$).
+Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
 %
@@
 %To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-In this section we derive the real space convolution kernels on the sphere which can be used to directly evaluate the scalar fields $E$ \& $B$ on the sphere.
+In this section we derive the real space kernels which we can use to directly evaluate the scalar fields $E$ and $B$ on the sphere.
 We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{}:
@@
 %
-where $\alpha_{ij}, ~\beta_{ij} ~\&~ \gamma_{ij}$ denote the Euler angles that specifically transform $(i \rightarrow j)$: the coordinate system at $\hat{n}_i$ to align the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation becomes more obvious when this equation is written in terms of the Wigner-D functions.}.
+where $(\alpha_{ij}, ~\beta_{ij}, \gamma_{ij})$ denote the Euler angles that specifically transform $(i \rightarrow j)$ so that the coordinate system at $\hat{n}_i$ aligns with the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation becomes more obvious when this equation is written in terms of the Wigner-D functions.}.
 Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the following complex function:
@@
 Here we have rigorously derived the exact form of the function $f(\beta)$.
-Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, as was argued to be a necessary property to yield a field of requisite spin.}
+Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we argued to be a necessary property to yield a field of correct spin.}
 
@@
 
-\paragraph{Radiation kernel.} The expression we call the \textit{radiation kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
+\paragraph{Radiation kernel.} The expression that we call the \textit{radiation kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
 The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere.
-In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluate its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
-\revisit{This one to many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.}
+In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
+\revisit{This one-to-many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.}
 
@@
 The inverse rotation Euler angles relates to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$.
-Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
+Since the kernel depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign.
 The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows:
@@
 When $\mm$ is expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
-\revisit{This many to one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.} We display the kernel in \fig{fig:vis_kernel}.
+\revisit{This many-to-one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.} We display the kernel in \fig{fig:vis_kernel}.
 %--------------------------------------------------------

### 2018-06-12 articles/formalism/sections/real_space_formalism.tex
Editing through visualizing kernels

@@
 The angle $\alpha_{qe}$ defines a rotation operator that aligns the local $\hat{x}$ with $\hat{r}$.
-\textit{Convolution kernel:} The resultant scalar field at `e' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle.
+\textit{Convolution kernel:} The resultant scalar field at `$e$' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle.
 This convolution is performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `q' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
+\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `$q$' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
 On the flat sky $\gamma_{eq}=-\alpha_{qe}$ and consequently there is no difference between the radiation and convolution kernels.}}
@@
 \subsection{Evaluating Stokes $Q$/$U$ from scalar $E$/$B$}\label{sec:eb2qu}
-The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure.
+The real space operator which translates $E$/$B$ fields to Stokes parameters $Q$/$U$ can be derived using a similar procedure.
 Expressed in the matrix-vector notation, inverse operator is given by the following equation:
@@
 where all the symbols have the same meaning as defined in \sec{sec:qu2eb}.
-Note that the conjugated forms of the Green's function and the effective beam for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
+Note that the conjugated forms of the radiation kernel (Green's function) and the convolution kernel (effective beam) for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
 %--------------------------------------------------------
@@
 
-The real and imaginary part of the kernel $\mathcal{M}_G$ are identical irrespective of changes in the galactic latitude and longitude of the central pixel.
-These functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}.
-These observations are consistent with the Green's function interpretation of the kernel $\mathcal{M}_{G}$ which yield coordinate independent scalars E/B.
-From \eq{eq:qu2eb_radiation_concise} it is clear that $\mathcal{M}_G$ can be interpreted in the following ways:
+The kernel $\mathcal{M}_G$ is the Green's function of the operator that transforms Stoke parameters to coordinate independent $E/B$.
+The coordinate independence implies that the real and imaginary parts of the kernel do not vary with changes in the galactic latitude and longitude of the central pixel.
+In particular these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}.
+From \eq{eq:qu2eb_radiation_concise}, we can see the $E/B$ patterns that $\delta$-functions in the Stokes parameters produce:
 %
 \beq
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat \hspace{5 mm};\hspace{5 mm}
-\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat\,,
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat ;\qquad
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat.
 \eeq
 %
-$\mathcal{M}^*_B$ is the Greens function of the operator that transforms E/B to Stokes parameters Q/U.
-The real and imaginary parts of $\mathcal{M}^*_B$ are identical irrespective of the galactic longitude, however they vary as a function of galactic latitude.
-This latitude dependent shape is necessary as the coordinate dependence of the Stokes parameters derived from the scalar E/B is built in via this Greens function.
-From \eq{eq:eb2qu_radiation} it is clear that $\mathcal{M}^*_B$ can be interpreted in the following manner:
+On the other hand, $\mathcal{M}^*_B$ is the Green's function of the operator that transforms E/B to coordinate-dependent Stokes parameters Q/U.
+The kernel $\mathcal{M}^*_B$ does not change with the central longitude, but varies as a function of galactic latitude.
+This latitude-dependent shape carries the  coordinate dependence of the Stokes parameters.
+From \eq{eq:eb2qu_radiation}, we $\mathcal{M}^*_B$ arises from $\delta$-functions in $E/B$:
 %
 \beq
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat \hspace{5 mm};\hspace{5 mm}
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat;\qquad
 \bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat\,.

### 2018-06-12 articles/formalism/sections/real_space_formalism.tex
Edits and queries in purifying section

@@
 \subsection{Purifying Stokes parameters $Q$/$U$ for $E$/$B$ modes} \label{sec:purify_stokes_qu}
-We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.
+We can only measure the total Stokes vector, a sum of the part that corresponds to scalar $E$ and the part that corresponds to $B$.
 The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as discussed in \sec{sec:mat_pol_intro}.
@@
 \eeq
-where $\mathcal{I}_{r} ~\&~ \mathcal{D}_{r}$ and $\mathcal{I}_{i} ~\&~ \mathcal{D}_{i}$ are the real and complex parts of the following complex functions:
+where $\mathcal{I}_{r}, \mathcal{D}_{r}$ and $\mathcal{I}_{i}, \mathcal{D}_{i}$ are the real and imaginary parts of the following complex functions:
 %
@@
 \revisit{Note that when the operators are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them by $\mathcal{I}_G=\Delta \Omega \mathcal{I}^*$ and $\mathcal{D}_G=\Delta \Omega \mathcal{D}$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.
+[K: question about $\Delta \Omega$ here.]} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 
-The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity: $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
+The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity: $\lim_{\ell_{\rm max} \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
 For all practical purposes $\mathcal{I}$ acts like an identity operator as ascertained by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
@@
 \beqry
-\bar O_E \, \bar O_E &=& \bar O_E \qquad ;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
+\bar O_E \, \bar O_E &=& \bar O_E;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
 \bar O_E \, \bar O_B &=& 0 \,,\\
@@
 This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact and a more crucial property of the operators.
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which \revisit{is exact and a more crucial property of the operators.[K: what does this mean?]}

### 2018-06-15 articles/formalism/article.tex
updated abstract and section 4- polarized filaments

@@
 \revisit{We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters to the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background(CMB) and cosmic shear analysis.
-The covolution kernels split naturally into angular and radial parts and we show explicitly how the radial extent of the convolution kernel depends on the targeted band-limit.
-We show that an arbitrary radial dependence can produce $E/B$-like maps and that these are simply filtered versions of the standard $E/B$ maps.
+We also derive real space operators that decompose the measured Stokes parameters into those corresponding to E-modes and B-modes respectively, without ever evaluating the scalar fields themselves.
+We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidate these derivations.
+For all these real space operators we show that the kernels split naturally into angular and radial parts and we show explicitly how the radial extent of these kernels depends on the targeted band-limit.
+We show that the kernels can be interpreted either as a complex convolving beam or the Green's function when they are expressed as functions of the forward or inverse rotation Euler angles respectively.
+We show that an arbitrary radial dependence, satisfying the constraint that it vanishes at angular separations of $0$ and $\pi$, can produce $E/B$-like maps and that these are simply filtered versions of the standard $E/B$ maps.
 This allows us to compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
+We show that the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators are a special case of these generalized operators and present their band limited versions.
 We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function.
+We present a scheme to derive this window function for any radial dependence.
 The spatial structure of the real space operator provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds and we predict non-zero B-mode signature that is expected from finite filaments in the sky.
-    %
-     We cast the standard CMB polarization analysis operators in a matrix-vector notation which facilitates the derivations and shows that the kernels relate directly to spin-0 $Y_{\ell 2}$ spherical harmonic functions.
-This new notation also allows us to derive real space operators which decompose the measured Stokes parameters into their even and odd-parity parts, without ever evaluating the scalar $E$/$B$ fields themselves.
 This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.

### 2018-06-15 articles/formalism/sections/discussion.tex
updated abstract and section 4- polarized filaments

@@
 
-These real space operators provide a spatially intuitive way of understanding the different decompositions of the Stokes vector.
+These real space operators provide a spatially intuitive way of understanding the different decompositions of the Stokes vector on the sphere.
 We explicitly  demonstrated that all the real space operators have the common characteristic  of being separable into a azimuthal part that is band limit independent and radial part that incorporates all the band limit dependence.
@@
 
-Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a convolving beam depending on whether the kernels are expressed in terms of the forward rotation Euler angles or the inverse rotation Euler angles.
+Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a complex convolving beam depending on whether the kernels are expressed in terms of the forward rotation Euler angles or the inverse rotation Euler angles.
 While the convolution interpretation is a familiar one, the Green's function interpretation is a new way of looking at this operation.

### 2018-06-15 articles/formalism/sections/kernel_paintbrush.tex
updated abstract and section 4- polarized filaments

@@
 Detecting B-modes from filaments requires a more careful edge stacked filaments analysis.
-While the detectability of B-mode signature from filaments from Planck data calls for a more careful assessment, it should definitely be detectable in higher fidelity data.}
+While the detectability of B-mode signature from filaments from Planck data calls for a more careful assessment, it should be detectable in higher fidelity data.}
 
@@
 The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
-\comment{Add that the spiral has a constant radius of curvature and thats the reason you dont see B-mode signal in intermediate regions of the spiral!}
+\revisit{The spiral filament showcased in \fig{fig:polfilaments} has a constant radius of curvature and thats the reason for not seeing a B-mode signal in intermediate regions of the spiral.
+For filaments that don't have a constant radius of curvature one expects to generate more B-mode power.} \comment{This is an important point right?
+So even if the magnetic field is perfectly aligned with the filament, one can generate B-mode signal in intermediate regions of the filament just by having the filament with changing radius of curvature.
+There is no reason for filaments to have a constant radius of curvature.}
 
-\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the tangent to the filament at any given point and this results in dominantly generating an E-mode signal while the B-mode signal is present only near the edges.
-By similar arguments it can be seen that that polarization pattern will be dominated by B-modes if the polarization vector is always at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
-Therefore a careful study of the $E/B$ mode power in a filament can provide insights into the orientation of the magnetic field with respect to the length of the filament, assuming the polarization vectors (headless) are always perpendicular to the magnetic field vector.}
+\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point and this results in generating dominantly an E-mode signal while the B-mode signal is present only near the edges.
+By similar arguments it can be shown that that polarization pattern will be dominated by B-modes if the polarization vector is aligned at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
+Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.}

### 2018-06-15 articles/formalism/sections/real_space_formalism.tex
updated abstract and section 4- polarized filaments

@@
 where $s$ denotes the spin of the basis functions and our \revisit{definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
-We introduce this to ensure the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.
-[Orthonormal only in infimetesimal pixel limit?]}
+We introduce this to ensure the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.} \comment{[Orthonormal only in infimetesimal pixel limit?, I think it doesnt have to be infitesimal but sufficiently small.]}
 
@@
 This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which \revisit{is exact and a more crucial property of the operators.[K: what does this mean?]}
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which \revisit{is exact and a more crucial property of the operators.} \comment{[K: what does this mean?, A: Just mean that power conservation is not as important as the orthogonality of the E/B mode functions.]}

### 2018-06-15 articles/formalism/sections/generalizedeb.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

@@
 \beq 
-\label{eq:bl_ebdef_lower}
-[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
+[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.\label{eq:bl_ebdef_lower}
 \eeq

### 2018-06-15 articles/formalism/sections/kernel_discussion.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

@@
 \comment{Compare the fitted slope to the one in the Zaldariaga paper.}
+\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to the $E/B$ Fourier modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}.
+In this work we formally derive the function form of ${}_\mm f(\beta)$, which is seen to have an oscillatory nature and find that that the envelope of the function scales as $\beta^{-1.55}$.}
+\comment{So whats the point and is this discussion better suited for the conclusions? Could the fit by eye be highly misleading? }

### 2018-06-15 articles/formalism/sections/kernel_paintbrush.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

@@
 So even if the magnetic field is perfectly aligned with the filament, one can generate B-mode signal in intermediate regions of the filament just by having the filament with changing radius of curvature.
-There is no reason for filaments to have a constant radius of curvature.}
+There is no reason for filaments to have a constant radius of curvature.
+Maybe its important to make this demonstration?}
 
@@
 Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.}
+
+\revisit{Our conclusions differ subtly from those presented in \cite{Zaldarriaga2001a}, where in it is argued that that filaments cannot produce B-mode signals for configurations in which the polarization vector is parallel or perpendicular to the length of the filament.
+While this conclusion is true for filaments of infinite length, in reality we expect filaments that are observed on the sky to have a finite length and in this case one expects a definite B-mode pattern from the edges of the filament.
+One also does not expect that filaments have a constant radius of curvature and this will result in an additional generation of B-mode power.} \comment{Move to conclusions?}

### 2018-06-15 articles/formalism/sections/discussion.tex
reordered text and made some changes to section on polarized filaments

@@
 The azimuthal part of the operator is primarily responsible for the requisite spinorial decomposition, while the radial weights determine the non-local dependence of the construction of the resultant fields on the original fields.
-Using the self similarity property of the radial functions we define a non-locality parameter and argued that it is proportional to $\ell_{\rm max}^{-1}$.
+Using the self similarity property of the radial functions we define a non-locality parameter and show that it is proportional to $\ell_{\rm max}^{-1}$.
 The scalar decomposition of the Stokes parameters being of primary interest,  we empirically derived the non-locality parameter $\beta_0$ for this operation and showed that the proportionality constant $\ell_{0}=22$ provided a good prediction for the angular distance at which the ${}_{\mm}f$ falls below 1\% of its maxima as seen in \fig{fig:rad_ker_decay}.
 
-Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a complex convolving beam depending on whether the kernels are expressed in terms of the forward rotation Euler angles or the inverse rotation Euler angles.
+Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a complex convolving beam depending on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
 While the convolution interpretation is a familiar one, the Green's function interpretation is a new way of looking at this operation.

### 2018-06-15 articles/formalism/sections/kernel_paintbrush.tex
reordered text and made some changes to section on polarized filaments

--- 2018-06-15 articles/formalism/sections/kernel_paintbrush.tex
@@
 However, unlike a circular ring, this filament is not a configuration with a definite parity.
-Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
+Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
 A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.
+
+The intuition from the real-space kernels holds also when we distort the shape of the filament.
+If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
+Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-contant radius of curvature.
+The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
+The filament is highlighted by positive $E>0$.
+The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
+While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions due to the varying radius of curvature of the spiral \footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
+\comment{If this is correct, then one expects to see a higher B-mode signal in intermediate regions of the spiral, as compared to the B-mode signal in the intermediate regions of the linear filament.
+This  then should be more visible in a logarithmically scaled version of Fig.
+8.}
+
+\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point.
+This results in generating dominantly an E-mode signal while the B-mode signal is present only near the edges.
+By similar arguments it can be shown that that polarization pattern will be dominated by B-modes if the polarization vectors were aligned at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
+One way to get this configuration is to change the orientation of the magnetic field vector with respect to the tangent to the filament.
+Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.}
 
@@
 \revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal.
-We predict that a B-mode signal from filaments should be present.
+We predict that a B-mode signal from filaments should be present, since they have a finite length and a varying radius of curvature.
 A naive filament stacking analysis is only suited for making E-mode detections.
-Detecting B-modes from filaments requires a more careful edge stacked filaments analysis.
+Detecting B-modes from filament edges will require a more careful edge stacked filament analysis.
 While the detectability of B-mode signature from filaments from Planck data calls for a more careful assessment, it should be detectable in higher fidelity data.}
 
-The intuition from the real-space kernels holds also when we distort the shape of the filament.
-If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern (note that this cancellation would not happen for an ellipse or any loop of non-contant radius of curvature).
-The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
-The filament is highlighted by positive $E>0$.
-The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
-The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
-\revisit{The spiral filament showcased in \fig{fig:polfilaments} has a constant radius of curvature and thats the reason for not seeing a B-mode signal in intermediate regions of the spiral.
-For filaments that don't have a constant radius of curvature one expects to generate more B-mode power.} \comment{This is an important point right?
-So even if the magnetic field is perfectly aligned with the filament, one can generate B-mode signal in intermediate regions of the filament just by having the filament with changing radius of curvature.
-There is no reason for filaments to have a constant radius of curvature.}
-
-\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point and this results in generating dominantly an E-mode signal while the B-mode signal is present only near the edges.
-By similar arguments it can be shown that that polarization pattern will be dominated by B-modes if the polarization vector is aligned at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
-Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.}
+\revisit{In \cite{Zaldarriaga2001a} it is argued that linear filaments of infinite length in which the configuration of the polarization vector is parallel or perpendicular to the length of the filament cannot produce B-mode power.
+While this conclusion is true for filaments of infinite length, in reality we expect filaments that are observed on the sky to have a finite length and in this case one expects a definite B-mode pattern from the edges of the filament.
+One also does not expect that filaments have a constant radius of curvature and this will result in an additional generation of B-mode power.
+Therefore our study indicates results which subtly differ from those presented in \cite{Zaldarriaga2001a} and these differences can be attributed to the more realistic assumptions about the geometry of the filaments made in our analysis.} \comment{Move to conclusions?}

### 2018-06-18 articles/formalism/sections/kernel_discussion.tex
Minor edits for clarity.

@@
 
-The kernels $\mathcal{D}$ \& $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel as seen in \fig{fig:vis_kernel_DI}.
-These kernels show a two fold symmetry in the vicinity of the poles and this arises due to Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
+The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}.
+These kernels show a two fold symmetry in the vicinity of the poles.
+Here the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
 Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}_G$.
-This explains why the imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
-On transiting to lower latitudes, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
+The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
+On transiting to lower latitudes, however, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
 This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$.
 Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$.
-The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}~\&~ 80^{\circ}$ and serve to indicate the rate of this transition.
-These kernels are invariant under changes in longitude of the central pixel, the latitude being held fixed, as one may have expected.
+The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}$ and $b=80^{\circ}$ and serve to indicate the rate of this transition.
+As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.
 

### 2018-06-19 articles/formalism/sections/generalizedeb.tex
Editing text and commenting through generalized E/B

@@
 %--------------------------------------------------------
-\subsection{Generalized polarization operators}\label{sec:generalized_operators}
+\subsection{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
 With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
 The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.
-The shape of the radial part of the operator is determined by the basis functions and varies as a function of the band limit.
+The radial parts of the stardard operators are determined by the sum over spherical harmonics and varies as a function of the band limit.
 It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
@@
 To simplify discussions, we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
-Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q/U$ to scalars $E/B$ and the inverse operator $\bar{O}'^{-1}$ in the following manner,
+Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q/U$ to $E/B$-like scalars (and the inverse operator $\bar{O}'^{-1}$) in the following manner,
 %
@@
 In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-Though the real space behavior of these two function $G(\beta)$ and $b(\beta)$ has these differences, in harmonic space they play identical roles.
+Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
 %
@@
 %
+
+\comment{It is weird the order that the subplots are referenced.}
 
@@
 %--------------------------------------------------------
-\subsubsection{Recovering the standard $E$ and $B$ mode spectra}
+%\subsubsection{Recovering the standard $E$ and $B$ mode spectra}
+
 The generalized convolution kernels defined in the previous section, when operated on the Stokes vector returns some scalar $E'$ and $B'$ mode maps,
@@
 %--------------------------------------------------------
-\subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
+\paragraph{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators.}
 Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
-Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:
+Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = ({(\ell+2)!/(\ell-2)!})^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
 %
@@
 %
-The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit bi-positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
-The band limited version of the spin raising operator $\eth^2$ is derived by merely taking the conjugate of the above equation.
+The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
+The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.
 %--------------------------------------------------------

### 2018-06-19 articles/formalism/sections/kernel_discussion.tex
Editing text and commenting through generalized E/B

@@
 %
-We have explored in detail the  azimuthal dependence of the real space kernels.
+Above, we have explored in detail the  azimuthal dependence of the real space kernels.
 Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
@@
 The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
-The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0=min(180,180 \frac{22}{\ell_{\rm max}})$.}
+The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.}
 %While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
@@
 The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-As a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at separations $\beta=0,\pi$.
+It oscillates and, as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
 %This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
 
-The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to E and B modes  are also  necessarily non-local.
+The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to $E$ and $B$ modes  are also  necessarily non-local.
 The function \revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.
@@
 The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}.
-While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, this feature of the kernels has been supressed as all the function have been normalized such that their global maxima is set to unity.
+While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.
 This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
 At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
-In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are self similar and follow this interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
+In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
 
@@
 The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller angular distance $\beta$.
-The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}
+The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}  \revisit{[K: there is not a lot of content to this paragraph...
+It just says higher lmax falls below a fixed threshold faster, but this is already in the plot and surrounding paragraphs.]}
 
@@
 \beq
-\beta_0= {\rm min}\left(180,180 \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
+\beta_0= {\rm min}\left(180^\circ,180^\circ \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
 \eeq
 with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}.
-Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.} \comment{How sensitive is this transition point to $\ell{\rm min}$?}
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.} \comment{How sensitive is this transition point to $\ell{\rm min}$?} \comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}
 

### 2018-06-19 articles/formalism/sections/kernel_paintbrush.tex
Editing text and commenting through generalized E/B

@@
 The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
-In all images, the longitude angle increases to the left (East in sky convention).
+In all images, the longitude angle increases to the left (which is East in sky convention).
 All plot are on a common, arbitrary color scale.}
@@
 The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
-For example, a simple model for a magnetize filament has the magnetic field threaded along a linear gas overdensity.
+For example, a simple model for a magnetized filament has the magnetic field threaded along a linear gas overdensity.
 Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and perpendicular to the filament overall).
@@
 Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
-A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.
+A filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
 
@@
 The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
-While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions due to the varying radius of curvature of the spiral \footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
+While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions due to the varying radius of curvature of the spiral.
+%\footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
+
 \comment{If this is correct, then one expects to see a higher B-mode signal in intermediate regions of the spiral, as compared to the B-mode signal in the intermediate regions of the linear filament.

### 2018-06-19 articles/formalism/sections/real_space_formalism.tex
Editing text and commenting through generalized E/B

@@
 %
-where $s$ denotes the spin of the basis functions and our \revisit{definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
-We introduce this to ensure the ortho-\textit{normality} of these operations, so that ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$ on the discretized sphere, and maintain the standard definition of spherical harmonics.} \comment{[Orthonormal only in infimetesimal pixel limit?, I think it doesnt have to be infitesimal but sufficiently small.]}
+where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
+We introduce this to ensure the orthonormality of these operations on the discretized sphere when the pixel size is sufficiently small, ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$, and also maintain the standard definition of spherical harmonics.
 
@@
 \revisit{Note that when the operators are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them by $\mathcal{I}_G=\Delta \Omega \mathcal{I}^*$ and $\mathcal{D}_G=\Delta \Omega \mathcal{D}$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.
-[K: question about $\Delta \Omega$ here.]} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.} \comment{[K: question about $\Delta \Omega$ and sums over pixels here and in the rest of the kernels.]} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 

### 2018-06-20 articles/formalism/sections/kernel_paintbrush.tex
Updated kernel paintbrush discussion.

@@
 For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.
+The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
 
@@
 A filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
+
+Changing the polarization direction within the filament changes the $E/B$ patterns.
+A $90^\circ$ rotation of the polarization with respect to the filament changes the sign of both $E$ and $B$.
+In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
+The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments (infinite and without ends) can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
+Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.
 
@@
 The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
-While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions due to the varying radius of curvature of the spiral.
+While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions along the filament due to the varying radius of curvature of the spiral.
 %\footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
 
-\comment{If this is correct, then one expects to see a higher B-mode signal in intermediate regions of the spiral, as compared to the B-mode signal in the intermediate regions of the linear filament.
+%\comment{If this is correct, then one expects to see a higher B-mode signal in intermediate regions of the spiral, as compared to the B-mode signal in the intermediate regions of the linear filament.
 This  then should be more visible in a logarithmically scaled version of Fig.
-8.}
+8.}  % K: addressed with new plot
 
-\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point.
+%\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point.
 This results in generating dominantly an E-mode signal while the B-mode signal is present only near the edges.
@@
 One way to get this configuration is to change the orientation of the magnetic field vector with respect to the tangent to the filament.
-Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.}
+Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.} % K: addressed
 
@@
 We predict that it should be there in higher fidelity data.}
-\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal.
-We predict that a B-mode signal from filaments should be present, since they have a finite length and a varying radius of curvature.
-A naive filament stacking analysis is only suited for making E-mode detections.
-Detecting B-modes from filament edges will require a more careful edge stacked filament analysis.
-While the detectability of B-mode signature from filaments from Planck data calls for a more careful assessment, it should be detectable in higher fidelity data.}
+A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal above the noise.
+We predict that a B-mode signal from filaments should be present, since they have a finite length of a few degrees.
+Detecting B-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
+The detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
 
-\revisit{In \cite{Zaldarriaga2001a} it is argued that linear filaments of infinite length in which the configuration of the polarization vector is parallel or perpendicular to the length of the filament cannot produce B-mode power.
+%\revisit{In \cite{Zaldarriaga2001a} it is argued that linear filaments of infinite length in which the configuration of the polarization vector is parallel or perpendicular to the length of the filament cannot produce B-mode power.
 While this conclusion is true for filaments of infinite length, in reality we expect filaments that are observed on the sky to have a finite length and in this case one expects a definite B-mode pattern from the edges of the filament.

### 2018-06-21 articles/formalism/article.tex
Edit on title and discussion section.

@@
 %\title{Real space operators for Stokes $Q$ \& $U$ to scalars $E$ \& $B$ translation}
-\title{Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels}
+%\title{Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels}
+\title{Real-space computation of $E$/$B$-mode maps I: \revisit{Formalism, Compact Kernels, and Polarized Filaments}}
+
 \author[]{Aditya Rotti and}
@@
 We present a scheme to derive this window function for any radial dependence.
-The spatial structure of the real space operator provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds and we predict non-zero B-mode signature that is expected from finite filaments in the sky.
+The spatial structure of the real space operator provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds and we predict a non-zero $B$-mode signature that is expected from finite filaments in the sky.
 This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.

### 2018-06-21 articles/formalism/sections/discussion.tex
Edit on title and discussion section.

@@
 \section{Discussion}\label{sec:discussion}
-
-We introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of CMB polarization maps.
-This notation simplifies the derivation of the real space operators.
-We presented a first derivation of the real space operators on the sphere that transforms the Stokes vector \vp{} to into a vector of scalars \vs{} and vice versa.
+In this work, we presented a \revisit{first} derivation of the real space operators on the sphere that transforms the Stokes vector to into a vector of scalars and vice versa.
 We also presented real space operators that directly decompose the full Stokes vector \vp{} into vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
+A vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of CMB polarization maps.
+This real-space analysis method trivially generalizes to maps of arbitrary spin.
 
 These real space operators provide a spatially intuitive way of understanding the different decompositions of the Stokes vector on the sphere.
-We explicitly  demonstrated that all the real space operators have the common characteristic  of being separable into a azimuthal part that is band limit independent and radial part that incorporates all the band limit dependence.
-The azimuthal part of the operator is primarily responsible for the requisite spinorial decomposition, while the radial weights determine the non-local dependence of the construction of the resultant fields on the original fields.
-Using the self similarity property of the radial functions we define a non-locality parameter and show that it is proportional to $\ell_{\rm max}^{-1}$.
-The scalar decomposition of the Stokes parameters being of primary interest,  we empirically derived the non-locality parameter $\beta_0$ for this operation and showed that the proportionality constant $\ell_{0}=22$ provided a good prediction for the angular distance at which the ${}_{\mm}f$ falls below 1\% of its maxima as seen in \fig{fig:rad_ker_decay}.
+We explicitly  demonstrated that all the real space operators are separable into azimuthal and radial parts.
+Only the radial part depends on the band limit.
+The azimuthal part of the operator is primarily responsible for handling the spin decomposition, while the radial weights determine the non-local dependence of the resulting fields on the original fields.
+The radial part of the operator kernel is roughly self-similar.
+For the kernel to fall to a fixed fraction of its maximum, the radial distance scales as $\ell_{\rm max}^{-1}$.
+The angle where the kernel falls to one percent is approximately $\beta_0 = \ell_{0}/\ell_{\rm max}$ with $\ell_{0}=22$ (\fig{fig:rad_ker_decay}).
 
-Our careful study of the real space operators reveals the dual interpretation of the operators as either the Green's function or a complex convolving beam depending on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
-While the convolution interpretation is a familiar one, the Green's function interpretation is a new way of looking at this operation.
-This new interpretation allows us to think of ${}_{+2}X$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
-The resultant complex scalar maps can be then understood as arising from superposition of the radiating field emanating from all the spin charges on the sphere.
-The $E/B$ mode maps are merely the real and imaginary parts of this resultant complex scalar field.
+Our close study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
+The interpretation  depends on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
+These functions are complex-valued and in many cases latitude-dependent.
 
-\revisit{A similar equation for real space $E$ \& $B$ operators was derived in \cite{Zaldarriaga2001a}, however those results were derived for the flat sky case and did not explicitly derive the radial kernel.} \comment{A discussion on this should be in the conclusions.}
+The Green's function interpretation provides some useful insights into these operations.
+This interpretation allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
+The resulting complex scalar maps can be then understood as arising from superposition of the radiating fields emanating from all the spin charges on the sphere.
+The $E/B$ mode maps are merely the real and imaginary parts of this field.
+\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, but treated the flat sky case and did not explicitly derive the radial kernel.}
 
-Understanding the non-locality of the real space operators, allowed us to generalize the real space operators $\bar{O}'$ and its inverse ${\bar O}'^{-1}$, which transform between the spin-2 and spin-0 representations of the CMB polarization.
-We presented a method of systematically generalizing these operators by introducing the harmonic space operator $\tilde{\mathcal{G}}$ which in effect causes the radial function to vary from its default form.
-We show that these modifications to the radial kernel can be interpreted as a smoothing operation on the scalar fields with a circularly symmetric instrument beam.
+Understanding the non-locality of the real space operators allowed us to generalize the real space operators % $\bar{O}'$ and its inverse ${\bar O}'^{-1}$, which
+that transform between the spin-2 and spin-0 representations of the CMB polarization.
+We showed how to modify and gereralize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
+These modifications to the radial kernel have the same effect as a smoothing operation on the scalar fields by a circularly symmetric beam.
+Thus they are trivial to recover the standard $E/B$ power spectra in maps from the modified kernels.
+%We presented a method of systematically generalizing these operators by introducing the harmonic space operator $\tilde{\mathcal{G}}$ which in effect causes the radial function to vary from its default form.
 We argue that one can choose any arbitrary form for $\tilde{\mathcal{G}}$ as long as one adheres to the constraint that $\tilde{\mathcal{G}}^{-1}$ and $\tilde{\mathcal{G}}^{-2}$ are well defined operators.
 These constraints are necessary to ensure that all the standard CMB spectra are recoverable from the modified $E'$/$B'$ maps emerging from the modified operators on the Stokes parameter maps.
-Noting that that the standard spin raising $\eth^2$ and spin lowering $\bar{\eth}^2$ operators are special cases of these generalized operators, we presented a band limited representation of these operators.
+Noting that that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators, we presented a band limited representation of these operators.
 
-\revisit{Discussion on results from polarized filaments filaments, compare and contrast with those in \cite{Zaldarriaga2001a}.}
+The toolbox of real-space operators gives us more intuition about the $E$- and $B$-mode structure of polarized filaments in the Milky Way gas and dust, potentially important sources of foregrounds for inflationary science.
+We predict a characteristic $B$-mode pattern from filament sources.
 
-There are several advantages and alternative analysis routes that emerge from employing these real space operators for analysis of CMB polarization maps.
-To begin with, one does not need to evaluate the spin harmonic functions as the real space operators only rely on computing the Euler angles which can be done on the fly and the $P_{\ell}^{2}$ functions need to be tabulated only once for analysis at some predetermined resolution.
-Note that this real space analysis method trivially generalizes to analyzing maps of arbitrary spin.
-Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable, since the $E/B$ contribution from the Stokes charge in each pixel can be evaluated independently.
-Also note that the evaluation of contribution from charges in the masked portion of the sky can be easily omitted, unlike in the harmonic analysis.
-Given the Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.
-Since the real space operators offer the ability of tuning the locality of $E/B$ maps, this can be potentially exploited to reduce foreground contamination from distant parts of the sky.
-For instance the real space operators can be defined such that the locality of their radial kernels is varied on different portions of the sky, dictated by say the foreground morphology, resulting in some scalar $E'/B'$ maps.
-While this idea seems promising, the usefulness of this implementation will depend on whether the standard $E/B$ mode spectra are recoverable from scalar maps derived in this fashion.
-Note that it would be fairly non-trivial to think of such implementations using conventional harmonic space methods.
+%\revisit{Discussion on results from polarized filaments, compare and contrast with those in \cite{Zaldarriaga2001a}.}
 
-Results demonstrating the equivalence of these real space methods to the conventional harmonic space methods and from explorations of some of the ideas discussed above will be presented in the second part of this series of papers.
+Several alternative analysis routes emerge from considering  these real space operators.
+No spin-harmonic transforms are necessary as the real space operators only rely on computing the Euler angles which can be done on the fly.
+The radial functions (depending on $P_{\ell}^{2}$) need be tabulated only once at some determined resolution.
+Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
+Although the scaling for the real space method (${\cal O}(N_{\rm pix}^2)$) is steeper than for the spherical harmonic transforms (${\cal O}(N_{\rm pix}^{3/2})$), the simple parallelization and the small prefactor for compact kernels at high-resolution / high-band-limit could make it faster in some contexts.
+It can have a small memory footprint.
+\comment{Does parallel S2hat have memory constraints at high l?}  The evaluation of contribution from charges in the masked portion of the sky can simply be omitted.
+\comment{hybrid low-l / high-l schemes}
+
+\revisit{The Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.}  \comment{K: question whether this actually works.
+What does E/B tod really mean?}
+
+Since the real space operators let us tune the locality of $E/B$ maps, this can be potentially exploited to eliminate foreground contamination from distant parts of the sky.
+Such applications can be difficult to implement using conventional harmonic space methods.
+For instance, the real space operators can be defined such that the locality of their radial kernels is varied on different portions of the sky, dictated by say the foreground morphology, resulting in some modified scalar $E'/B'$ maps.
+While this idea seems interesting, the usefulness of this implementation will depend on whether the standard $E/B$ mode spectra are easily recoverable in this fashion.
+
+Results that demonstrate the equivalence of these real space methods to the conventional harmonic space methods will be presented in the next paper in this series, along with explorations of some of the ideas discussed above.
 

### 2018-06-21 articles/formalism/sections/discussion.tex
more discussion edits

@@
 The $E/B$ mode maps are merely the real and imaginary parts of this field.
-\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, but treated the flat sky case and did not explicitly derive the radial kernel.}
+\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, treating the flat sky case and not explicitly deriving the radial kernel.}
 

### 2018-06-29 articles/formalism/sections/generalizedeb.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

@@
 \centering
-\subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
+\subfigure[\label{fig:gl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
 \subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
@@
 The black dashed curve depicts the band limited reconstruction of the modified radial function.
-\textit{Top right:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
-The dashed curves of the corresponding color depict the inverse of the harmonic functions.
-\textit{Bottom:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.}
+\textit{Top right:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.
+\textit{Bottom:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
+The dashed curves of the corresponding color depict the inverse of the harmonic functions.}
 \label{fig:example_gbeta}
@@
 
-\comment{It is weird the order that the subplots are referenced.}
-
 % Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
 In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
- \fig{fig:gl_bbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.
+ \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.
 Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.

### 2018-06-29 articles/formalism/sections/kernel_discussion.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

@@
 For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$.
-\revisit{We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.}
+We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.
 %
@@
 The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-It oscillates and, as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
+It oscillates and as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
 %This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
@@
 The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to $E$ and $B$ modes  are also  necessarily non-local.
-The function \revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.
+The function ${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.
 It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
-${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.}
+${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
 
@@
 At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
-In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.
-
-\revisit{We can now understand the shifting left of the radial kernels on increasing the maximum multipole using this telescoping property.
-Lets say the function ${}_rf(\beta', \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta'_0$.
-The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller angular distance $\beta$.
-The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}  \revisit{[K: there is not a lot of content to this paragraph...
-It just says higher lmax falls below a fixed threshold faster, but this is already in the plot and surrounding paragraphs.]}
+In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
+\revisit{We can now understand the amplitude scaling and the shifting left of the radial kernels on increasing the maximum multipole by studying this telescoping property.
+Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.}
 
 To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.
-We define a non-locality parameter $\beta_{0}$ as the angle beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ consistently falls below 1\% of its maximum.
+We define a non-locality parameter $\beta_{0}$ as the angular distance beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transitions to being consistently below 1\% of its maximum.
 %For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}.
 Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
-\revisit{The empirical relation:
+The empirical relation:
 \beq
@@
 with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}.
-Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.} \comment{How sensitive is this transition point to $\ell{\rm min}$?} \comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.%\comment{How sensitive is this transition point to $\ell{\rm min}$?}
 
-\comment{Compare the fitted slope to the one in the Zaldariaga paper.}
-\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to the $E/B$ Fourier modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}.
-In this work we formally derive the function form of ${}_\mm f(\beta)$, which is seen to have an oscillatory nature and find that that the envelope of the function scales as $\beta^{-1.55}$.}
-\comment{So whats the point and is this discussion better suited for the conclusions? Could the fit by eye be highly misleading? }
+In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}.
+Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature whose amplitude decays on increasing angular distance.
+We find that the the positive envelope of the function scales as $\beta^{-1.55}$.
+\comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}

### 2018-06-29 articles/formalism/sections/kernel_paintbrush.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

@@
 Detecting B-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
-The detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
+While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
 

### 2018-06-29 articles/formalism/sections/real_space_formalism.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

@@
 We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
-\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a \revisit{counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
-This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}}
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
+This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}
 %
@@
 \caption{This figure depicts the Euler angles in the z-y1-z2 convention.
-The cartesian coordinates shown in \revisit{dark solid green} are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in \revisit{dark solid red} are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The cartesian coordinates shown in dark solid green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark solid red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
 The blue coordinates at different locations are representative of the parallel transport along the geodesic connection between the two locations $\hat{n}_q$ and $\hat{n}_e$ on the sphere.}
@@
 Only the radial part $f(\beta_{qe})$ depends only on the angular separation between locations and hence  completely incorporates all the multipole $\ell$ dependence.
-\revisit{Recall that we had guessed the general form of the kernel using simple heuristic arguments in \sec{sec:qu2eb_heuristic}.
+Recall that we had guessed the general form of the kernel using simple heuristic arguments in \sec{sec:qu2eb_heuristic}.
 Here we have rigorously derived the exact form of the function $f(\beta)$.
-Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we argued to be a necessary property to yield a field of correct spin.}
+Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we argued to be a necessary property to yield a field of correct spin.
 
@@
 In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
-\revisit{This one-to-many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.}
+This one-to-many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.
 
@@
 %&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
-&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_e,\hat{n}_q) \,,
+&=& \Delta \Omega \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_q) \,,
 \eeqry
@@
 where $\Delta \Omega$ denotes the pixel area and the last line is a simple scalar multiplication between complex numbers.
-The radiation kernel is then: $ \mathcal{M}_{G} =-  \Delta \Omega \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$.
+The radiation kernel is then: $ \mathcal{M}_{G} =- \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB]= \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU] = [\delta(\hat{n}-\hat{n}_q)/{\Delta \Omega} + i0]$.
 We display the kernel later in \fig{fig:vis_kernel}.
@@
 \includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{\revisit{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle(sphere), representative of the coordinate dependence of the Stokes parameters.
+\caption{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle(sphere), representative of the coordinate dependence of the Stokes parameters.
 The two sets of dotted lines drawn at representative points denote great circles, one which passes through the central point labelled `e' and the other chosen such that the two have locally orthogonal tangent vectors $(\hat{r},\hat{\phi})$.
@@
 \textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `$q$' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
-On the flat sky $\gamma_{eq}=-\alpha_{qe}$ and consequently there is no difference between the radiation and convolution kernels.}}
+On the flat sky $\gamma_{eq}=-\alpha_{qe}$ and consequently there is no difference between the radiation and convolution kernels.}
 \label{fig:planar_euler_angles}
@@
 %
-where $\star$ denotes a convolution and $\mathcal{M}_{B} = - \Delta \Omega\mm(\beta_{eq},\gamma_{eq})$.
+where $\star$ denotes a convolution and $\mathcal{M}_{B} = -\mm(\beta_{eq},\gamma_{eq})$.
 When $\mm$ is expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$.
-\revisit{This many-to-one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.} We display the kernel in \fig{fig:vis_kernel}.
+This many-to-one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.
+We display the kernel in \fig{fig:vis_kernel}.
 %--------------------------------------------------------
@@
 \beqry
-    {}_{+2}X(\hat{n}_q) &&=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm}\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
-    {}_{+2}X(\hat{n}_q) &&= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm}\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
+    {}_{+2}X(\hat{n}_q) &&=  \Delta \Omega \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}(\hat{n}_e) \hspace{0.8cm}\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
+    {}_{+2}X(\hat{n}_q) &&= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{1.4cm}\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
 \eeqry
@@
 \beq
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\delta(\hat{n} - \hat{n}_q)\\ U=0 \emat ;\qquad
-\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\delta(\hat{n} - \hat{n}_q) \emat.
+\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega}\\ U=0 \emat ;\qquad
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega} \emat.
 \eeq
@@
 \beq
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\delta(\hat{n} - \hat{n}_e)\\ B=0 \emat;\qquad
-\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = \textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\delta(\hat{n} - \hat{n}_e) \emat\,.
+\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega}\\ B=0 \emat;\qquad
+\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = +\textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega} \emat\,.
 \eeq
@@
 {}_{+2}X_{E/B}(\hat{n}_e) &=& 0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q)  \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
-&=& 0.5 \Bigg\lbrace  {}_{+2}X  \, \mathcal{I}_G \pm {}_{+2}X^* \, \mathcal{D}_G \Bigg\rbrace \hspace{.5cm } \textrm{\emph{   Radiation kernel}} \,, \\
-&=& 0.5 \Bigg\lbrace \mathcal{I}_B \star {}_{+2}X\pm \mathcal{D}_B \star {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
+&=& 0.5 \Bigg\lbrace \Delta \Omega \sum_{q=1}^{N_{\rm pix}}  {}_{+2}X(\hat{n}_q)  \, \mathcal{I}_G(\hat{n}_q) \pm {}_{+2}X(\hat{n}_q)^* \, \mathcal{D}_G(\hat{n}_q) \Bigg\rbrace \hspace{.5cm } \textrm{\emph{  Radiation kernel}} \nonumber \,, \\ \vspace{-1cm} \\
+&=& 0.5 \Bigg\lbrace \mathcal{I}_B \star {}_{+2}X\pm \mathcal{D}_B \star {}_{+2}X^* \Bigg\rbrace(\hat{n}_e)   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}
 \eeqry
@@
 where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity.
-\revisit{Note that when the operators are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them by $\mathcal{I}_G=\Delta \Omega \mathcal{I}^*$ and $\mathcal{D}_G=\Delta \Omega \mathcal{D}$.
-When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\Delta \Omega \mathcal{I}$ and $\mathcal{D}_B=\Delta \Omega \mathcal{D}$.} \comment{[K: question about $\Delta \Omega$ and sums over pixels here and in the rest of the kernels.]} Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
+Note that when the operators are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them by $\mathcal{I}_G=\mathcal{I}^*$ and $\mathcal{D}_G=\mathcal{D}$.
+When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as some convolving beam and we denote them by $\mathcal{I}_B=\mathcal{I}$ and $\mathcal{D}_B=\mathcal{D}$.
+Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.
 

### 2018-06-29 articles/formalism/sections/introduction.tex
showed the radial function equivalence to zaldariagga radial function.

@@
 
-The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second \revisit{\st{derivatives}} evaulated locally.
 However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.

### 2018-06-29 articles/formalism/sections/kernel_discussion.tex
showed the radial function equivalence to zaldariagga radial function.

@@
 \begin{figure}[t]
-%\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
-%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
-%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
-\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}\hfill
-\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}\hfill
-\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
+\subfigure[]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}}\hfill
+\subfigure[]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}\hfill
+\subfigure[]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}\hfill
+\centering
+\subfigure[]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
+\subfigure[]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax_zaldariagga_scaling.pdf}}
+
 \caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
-The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
+The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
 All the curves are normalized such that their maxima is set to unity.
@@
 Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature whose amplitude decays on increasing angular distance.
-We find that the the positive envelope of the function scales as $\beta^{-1.55}$.
+\revisit{While we find that the the positive envelope of the function scales as $\beta^{-1.55}$, the radial function resulting from taking a moving average of the radial function does show a scaling of $\beta^{-2}$ at intermediate angular separations.
+Hence we conclude that the form of the radial function argued in \cite{Zaldarriaga2001a} corresponds to the sliding averaged full sky radial function.}
 \comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}

### 2018-06-29 articles/formalism/article.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour
small edits to introduction and filament section.

@@
 %\title{Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels}
-\title{Real-space computation of $E$/$B$-mode maps I: \revisit{Formalism, Compact Kernels, and Polarized Filaments}}
+\title{Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments}
 
@@
 \author[]{Kevin Huffenberger}
-\affiliation[]{Department of Physics, Florida State University, Keen Physics Building, 77 Chieftan Way, Tallahassee, Florida, U.S.A.}
+\affiliation[]{Department of Physics, Florida State University, Keen Physics Building, Tallahassee, Florida 32306}
 \emailAdd{adityarotti@gmail.com}
@@
 \noindent 
-\revisit{We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters to the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background(CMB) and cosmic shear analysis.
-We also derive real space operators that decompose the measured Stokes parameters into those corresponding to E-modes and B-modes respectively, without ever evaluating the scalar fields themselves.
-We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidate these derivations.
+    {We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters and the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background (CMB) and cosmic shear analysis.
+We also derive real space operators that decompose the measured Stokes parameters into those corresponding to $E$-modes and $B$-modes respectively, without ever evaluating the scalar fields themselves.
+We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidates these derivations.
 For all these real space operators we show that the kernels split naturally into angular and radial parts and we show explicitly how the radial extent of these kernels depends on the targeted band-limit.
-We show that the kernels can be interpreted either as a complex convolving beam or the Green's function when they are expressed as functions of the forward or inverse rotation Euler angles respectively.
-We show that an arbitrary radial dependence, satisfying the constraint that it vanishes at angular separations of $0$ and $\pi$, can produce $E/B$-like maps and that these are simply filtered versions of the standard $E/B$ maps.
-This allows us to compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and can be employed in a massively parallel scheme at high-resolution.
-We show that the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators are a special case of these generalized operators and present their band limited versions.
+We show that the kernels can be interpreted either as a complex convolving beam or a Green's function when they are expressed as functions of the forward or inverse rotation Euler angles respectively.
+We show that an arbitrary radial function can produce $E/B$-like maps, provides it vanishes at the origin and the  antipodal point.
+These maps are simply filtered versions of the standard $E/B$ maps.
+We present a scheme to derive this window function for any radial dependence.
+For this reason we can compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and could be employed in a massively-parallel scheme at high-resolution.
+We show that the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators are another special case of these generalized radial functions, and present their band limited versions.
 We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function.
-We present a scheme to derive this window function for any radial dependence.
-The spatial structure of the real space operator provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds and we predict a non-zero $B$-mode signature that is expected from finite filaments in the sky.
+The spatial structure of the real space operators provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds.
+We predict a non-zero $B$-mode signature that is expected from finite filaments in the sky.
 This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.

### 2018-06-29 articles/formalism/sections/kernel_paintbrush.tex
small edits to introduction and filament section.

@@
 The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
+In contrast to the kernel radial fuctions, which are more compact at higher bandlimit, the filament $B$-mode  pattern does not depend much on the bandlimit, provided it is sufficient to resolve the filament structure.
+A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
 
@@
 Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
-A filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
+For example, a filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
 
@@
 The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments (infinite and without ends) can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
-Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.
+Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament.
 
@@
 If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
-Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-contant radius of curvature.
+Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-constant radius of curvature.
 The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
@@
 While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions along the filament due to the varying radius of curvature of the spiral.
+A spiral turning with the other handedness will have a $B$-pattern with the opposite sign.
 %\footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
@@
 We predict that it should be there in higher fidelity data.}
-A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal above the noise.
+A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claims no $B$-mode signal above the noise.
 We predict that a B-mode signal from filaments should be present, since they have a finite length of a few degrees.

### 2018-06-29 articles/formalism/sections/generalizedeb.tex
Promoted generalized operators to it's own section.

@@
 %--------------------------------------------------------
-\subsection{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
+\section{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
 With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.

### 2018-07-10 articles/formalism/sections/introduction.tex
updates to the section on non-location of radial kernels. Added discussion on the zaldariagga kernel

--- 2018-06-11 articles/formalism/sections/introduction.tex
@@
 
-The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally.
 However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.

### 2018-07-10 articles/formalism/sections/kernel_discussion.tex
updates to the section on non-location of radial kernels. Added discussion on the zaldariagga kernel

--- 2018-06-29 articles/formalism/sections/kernel_discussion.tex
@@
 \begin{figure}[t]
-%\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
-%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
-%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
-\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}\hfill
-\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}\hfill
-\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
+\subfigure[\label{fig:fbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}}\hfill
+\subfigure[\label{fig:dfbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}\hfill
+\subfigure[\label{fig:ifbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}\hfill
+\centering
+\subfigure[\label{fig:fbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
+\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax_zaldariagga_scaling.pdf}}
+
 \caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
-The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
+\fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, \fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
 All the curves are normalized such that their maxima is set to unity.
@@
 The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
-The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.}
+The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.
+\fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg} depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ and has width $1.4\beta_0$.
+These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}
 %While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
@@
 In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
-\revisit{We can now understand the amplitude scaling and the shifting left of the radial kernels on increasing the maximum multipole by studying this telescoping property.
-Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.}
+We can now understand the amplitude scaling and the shifting left of the radial kernels on increasing the maximum multipole by studying this telescoping property.
+Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.
 
@@
 
-In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}.
-Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature whose amplitude decays on increasing angular distance.
-We find that the the positive envelope of the function scales as $\beta^{-1.55}$.
-\comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}
+\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}.
+Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude decaying on increasing angular distance.
+While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$, the function resulting from performing a sliding average on it is seen to scale as $\beta^{-2}$ at intermediate angular separations as seen in \fig{fig:fbeta_avg}, in agreement with the hypothesis made in \cite{Zaldarriaga2001a}.
+We find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}
+
+\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning to some lower band limit (determined by the width of the sliding window) radial function from a higher band limit radial function.
+On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, one seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of infinite band limit one can see that the behaviour will approach $\beta^{-2}$ across the domain $\beta\in[0,\pi]$.}
+
+\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function gets modified and is partly responsible for the scaling deviating from the power law.
+More importantly note that ${}_{\mm}f$ and ${}_{\md}f$ vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behaviour of the form $\beta^{-2}$.}

### 2018-07-10 articles/formalism/sections/real_space_formalism.tex
updates to the section on non-location of radial kernels. Added discussion on the zaldariagga kernel

@@
 This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which \revisit{is exact and a more crucial property of the operators.} \comment{[K: what does this mean?, A: Just mean that power conservation is not as important as the orthogonality of the E/B mode functions.]}
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact and a more crucial property of the operators.

### 2018-07-11 articles/formalism/sections/kernel_discussion.tex
refined section on kernel discussion

@@
 
-\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}.
-Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude decaying on increasing angular distance.
-While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$, the function resulting from performing a sliding average on it is seen to scale as $\beta^{-2}$ at intermediate angular separations as seen in \fig{fig:fbeta_avg}, in agreement with the hypothesis made in \cite{Zaldarriaga2001a}.
-We find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}
+\revisit{Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude of the envelope decaying on increasing angular distance at intermediate $\beta$ and increasing as $\beta \rightarrow \pi$.
+While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$ at intermediate $\beta$, the function resulting from performing a sliding average, is seen to scale as $\beta^{-2}$ in this regime as seen in \fig{fig:fbeta_avg}.
+This is in agreement with the hypothesis made for the flat sky case, where it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}.
+In addition through this exercise we also find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}
 
-\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning to some lower band limit (determined by the width of the sliding window) radial function from a higher band limit radial function.
-On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, one seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$.
-Extrapolating this trend to the case of infinite band limit one can see that the behaviour will approach $\beta^{-2}$ across the domain $\beta\in[0,\pi]$.}
+\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning from a higher band limit radial function to a radial function with an effectively lower band limit, set by the width of the sliding window.
+On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, it's seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of infinite band it is expected that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi]$ for $\epsilon << 1$.}
 
 \revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function gets modified and is partly responsible for the scaling deviating from the power law.
-More importantly note that ${}_{\mm}f$ and ${}_{\md}f$ vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behaviour of the form $\beta^{-2}$.}
+It is important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behavior of the form $\beta^{-2}$.}

### 2018-07-13 articles/formalism/sections/generalizedeb.tex
Edited moving average, dealt with problematic equation reference

@@
 \beq 
-[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.\label{eq:bl_ebdef_lower}
+[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
+\label{eq:bl_ebdef_lower}
 \eeq
 %
-Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping:
+Comparing to \eq{eq:ebdef_lower} %to \eq{eq:bl_ebdef_lower}
+makes apparent the following mapping:
 %

### 2018-07-13 articles/formalism/sections/kernel_discussion.tex
Edited moving average, dealt with problematic equation reference

--- 2018-07-10 articles/formalism/sections/kernel_discussion.tex
@@
 For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$.
-We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.
+We choose such a low band limit to highlight some key features of their radial profile.
 %
@@
 This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
-At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
-In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
-We can now understand the amplitude scaling and the shifting left of the radial kernels on increasing the maximum multipole by studying this telescoping property.
+At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$.
+As the band limit changes, the small angle portion of the radial functions have a similar shape.
+
+These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar and related by this telescoping and scaling property:
+$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad \mbox{(small angles)},$$
+where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
+This telescoping property encapsulates both the amplitude scaling and leftward shift of the radial kernels on increasing the maximum multipole.
 Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.
@@
 
-\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}.
-Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude decaying on increasing angular distance.
-While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$, the function resulting from performing a sliding average on it is seen to scale as $\beta^{-2}$ at intermediate angular separations as seen in \fig{fig:fbeta_avg}, in agreement with the hypothesis made in \cite{Zaldarriaga2001a}.
-We find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}
+\revisit{The radial function ${}_\mm f(\beta)$ is oscillatory, regardless of the maximum $l_{\rm max}$.
+The envelope of the oscillation decays with angular separation at intermediate $\beta$ but increases as $\beta \rightarrow \pi$.
+We find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$ at intermediate $\beta$.
+However, when we average over several oscillations with a moving window, we find that the average behavior as intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
+(We have narrowed the window as the band limit increases so that the number of oscillations averaged remains the same.)  This agrees with the hypothesis for the flat sky case, for which e.g.
+Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).
+In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as in \fig{fig:dfbeta_avg}.}
 
-\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning to some lower band limit (determined by the width of the sliding window) radial function from a higher band limit radial function.
-On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, one seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$.
-Extrapolating this trend to the case of infinite band limit one can see that the behaviour will approach $\beta^{-2}$ across the domain $\beta\in[0,\pi]$.}
+\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning from a higher band limit radial function to a radial function with an effectively lower band limit, set by the width of the sliding window.}
+\comment{K: I don't follow this sentence.} 
+\revisit{Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of a very high band limit we may expect that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.}
 
-\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function gets modified and is partly responsible for the scaling deviating from the power law.
-More importantly note that ${}_{\mm}f$ and ${}_{\md}f$ vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behaviour of the form $\beta^{-2}$.}
+\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function partly falls outside the domain and this is in part responsible for the scaling deviating from the power law, but it is also important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.}

### 2018-07-13 articles/formalism/sections/discussion.tex
updates to discussions

@@
 \section{Discussion}\label{sec:discussion}
-In this work, we presented a \revisit{first} derivation of the real space operators on the sphere that transforms the Stokes vector to into a vector of scalars and vice versa.
+In this work, we presented a first derivation of the real space operators on the sphere that transforms the Stokes vector to into a vector of scalars and vice versa.
 We also presented real space operators that directly decompose the full Stokes vector \vp{} into vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
-A vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of CMB polarization maps.
+To facilitate these derivations we introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of (spin-2 fields) polarization maps on the sphere.
 This real-space analysis method trivially generalizes to maps of arbitrary spin.
 
-These real space operators provide a spatially intuitive way of understanding the different decompositions of the Stokes vector on the sphere.
+These real space operators offer a spatially intuitive way of understanding the different decompositions of the Stokes vector on the sphere.
 We explicitly  demonstrated that all the real space operators are separable into azimuthal and radial parts.
-Only the radial part depends on the band limit.
-The azimuthal part of the operator is primarily responsible for handling the spin decomposition, while the radial weights determine the non-local dependence of the resulting fields on the original fields.
-The radial part of the operator kernel is roughly self-similar.
-For the kernel to fall to a fixed fraction of its maximum, the radial distance scales as $\ell_{\rm max}^{-1}$.
-The angle where the kernel falls to one percent is approximately $\beta_0 = \ell_{0}/\ell_{\rm max}$ with $\ell_{0}=22$ (\fig{fig:rad_ker_decay}).
+While the azimuthal part of the operators is primarily responsible for handling the spin decomposition, the radial weights determine the non-local dependence of the resulting fields on the original fields.
+Only the radial part of the kernel depends on the band limit.
+The radial part of the operator kernel are roughly self-similar in the sense that the radial kernels evaluated with some band limit is related to another radial kernel evaluated with a different band limit by a simple rescaling of the function.
+We use this property to define a non-locality parameter $\beta_0$ which is simply the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
+We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180, 180 \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
+\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, treating the flat sky case and not explicitly deriving the radial kernel.} \comment{Need to build in the relating to the Zaldariagga power law radial function here.}
 
-Our close study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
-The interpretation  depends on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
-These functions are complex-valued and in many cases latitude-dependent.
+Our careful study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
+While the convolving beam interpretation is well known and leads to the popular spokes and pinwheel descriptions of the $E/B$ modes, the Green's function interpretation of the operators is a new one and discussed for the first time in this work.
+These two different interpretations of the operators emerge depending on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
 
 The Green's function interpretation provides some useful insights into these operations.
-This interpretation allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
-The resulting complex scalar maps can be then understood as arising from superposition of the radiating fields emanating from all the spin charges on the sphere.
+In particular it allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
+The resulting complex scalar maps can be then understood as arising from superposition of the radiated spin-0 scalar fields emanating from all the spin charges on the sphere.
 The $E/B$ mode maps are merely the real and imaginary parts of this field.
-\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, treating the flat sky case and not explicitly deriving the radial kernel.}
 
-Understanding the non-locality of the real space operators allowed us to generalize the real space operators % $\bar{O}'$ and its inverse ${\bar O}'^{-1}$, which
-that transform between the spin-2 and spin-0 representations of the CMB polarization.
+A deeper understanding of the non-locality of the real space operators allowed us to generalize the real space operators that transform between the spin-2 and spin-0 representations of the CMB polarization.
 We showed how to modify and gereralize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
-These modifications to the radial kernel have the same effect as a smoothing operation on the scalar fields by a circularly symmetric beam.
-Thus they are trivial to recover the standard $E/B$ power spectra in maps from the modified kernels.
-%We presented a method of systematically generalizing these operators by introducing the harmonic space operator $\tilde{\mathcal{G}}$ which in effect causes the radial function to vary from its default form.
-We argue that one can choose any arbitrary form for $\tilde{\mathcal{G}}$ as long as one adheres to the constraint that $\tilde{\mathcal{G}}^{-1}$ and $\tilde{\mathcal{G}}^{-2}$ are well defined operators.
-These constraints are necessary to ensure that all the standard CMB spectra are recoverable from the modified $E'$/$B'$ maps emerging from the modified operators on the Stokes parameter maps.
+We argue that these modifications to the radial kernel have the same effect as a smoothing operation on the scalar fields by a circularly symmetric beam.
+Therefore it is trivial to recover the standard CMB angular power spectra from the modified scalar polarization maps estimated using the modified kernels.
 Noting that that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators, we presented a band limited representation of these operators.
@@
 The toolbox of real-space operators gives us more intuition about the $E$- and $B$-mode structure of polarized filaments in the Milky Way gas and dust, potentially important sources of foregrounds for inflationary science.
-We predict a characteristic $B$-mode pattern from filament sources.
+We demonstrate that filaments with finite length and/or changing radius of curvature results in a definite $B$-mode pattern in addition to the conventional $E$-mode pattern expected from filaments.
+We therefore predict a characteristic $B$-mode pattern from filament sources.
 
@@
 Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
-Although the scaling for the real space method (${\cal O}(N_{\rm pix}^2)$) is steeper than for the spherical harmonic transforms (${\cal O}(N_{\rm pix}^{3/2})$), the simple parallelization and the small prefactor for compact kernels at high-resolution / high-band-limit could make it faster in some contexts.
+
+%Although the scaling for the real space method (${\cal O}(N_{\rm pix}^2)$) is steeper than for the spherical harmonic transforms (${\cal O}(N_{\rm pix}^{3/2})$), the simple parallelization and the small prefactor for compact kernels at high-resolution / high-band-limit could make it faster in some contexts.
 It can have a small memory footprint.
@@
 
-\revisit{The Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.}  \comment{K: question whether this actually works.
+\revisit{Further the Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.}  \comment{K: question whether this actually works.
 What does E/B tod really mean?}

### 2018-07-13 articles/formalism/sections/discussion.tex
Clean up mapmaking discusion

@@
 We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180, 180 \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
-\revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, treating the flat sky case and not explicitly deriving the radial kernel.} \comment{Need to build in the relating to the Zaldariagga power law radial function here.}
+\revisit{An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.
+It did not explicitly derive the radial part of the kernel, but argued on geometric grounds that it should fall with angular separation as $\beta^{-2}$.
+We find that this agrees with the average behavior of radial functions after averaging oscillations, and some such averaging takes place due to pixelization of the signal.
+However, for precision reconstruction of $E/B$ on the sphere, the oscillations must be taken into account.}
 
 Our careful study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
-While the convolving beam interpretation is well known and leads to the popular spokes and pinwheel descriptions of the $E/B$ modes, the Green's function interpretation of the operators is a new one and discussed for the first time in this work.
-These two different interpretations of the operators emerge depending on whether the kernels are expressed in terms of the forward or inverse rotation Euler angles.
+\revisit{The convolution interpretation is not a totally new concept.
+It guides the discussion in \cite{Zaldarriaga2001a} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
+However, the Green's function interpretation of the operators is a new one and is discussed here for the first time.} These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
 
@@
 
-A deeper understanding of the non-locality of the real space operators allowed us to generalize the real space operators that transform between the spin-2 and spin-0 representations of the CMB polarization.
+Results that demonstrate the equivalence of these real space methods to the conventional harmonic space methods will be presented in the next paper in this series.
+
+Deeper understanding of the non-locality of the real space operators has allowed us to generalize the real space operators that transform between the spin-2 and spin-0 representations of the CMB polarization.
 We showed how to modify and gereralize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
-We argue that these modifications to the radial kernel have the same effect as a smoothing operation on the scalar fields by a circularly symmetric beam.
-Therefore it is trivial to recover the standard CMB angular power spectra from the modified scalar polarization maps estimated using the modified kernels.
+We argue that these modifications to the radial kernel have the same effect as a smoothing operation on the $E/B$ fields by a circularly symmetric beam.
+Therefore it is trivial to recover the standard CMB angular power spectra from the modified scalar polarization maps resulting from the modified kernels.
 Noting that that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators, we presented a band limited representation of these operators.
-
-The toolbox of real-space operators gives us more intuition about the $E$- and $B$-mode structure of polarized filaments in the Milky Way gas and dust, potentially important sources of foregrounds for inflationary science.
-We demonstrate that filaments with finite length and/or changing radius of curvature results in a definite $B$-mode pattern in addition to the conventional $E$-mode pattern expected from filaments.
-We therefore predict a characteristic $B$-mode pattern from filament sources.
 
@@
 
-Several alternative analysis routes emerge from considering  these real space operators.
+Modified real-space operators with compact kernels could open several alternative analysis routes in the future.
 No spin-harmonic transforms are necessary as the real space operators only rely on computing the Euler angles which can be done on the fly.
 The radial functions (depending on $P_{\ell}^{2}$) need be tabulated only once at some determined resolution.
-Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
+Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable over a compact domain, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
 
@@
 
-\revisit{Further the Green's function interpretation of the  real space operators and their locality, suggests the possibility of converting the Stokes parameter time ordered data to scalar $E/B$ time ordered data given the pointing model for the observations, which can then be subsequently converted to maps of $E/B$ modes using standard map making techniques.}  \comment{K: question whether this actually works.
-What does E/B tod really mean?}
+\revisit{The real space kernels could in principle be incorporated into the pointing matrices for map making, allowing maps of $E/B$ to be made directly from instrument data, without the need for Stokes parameter maps as intermediate products.
+  The pointing matrix---projecting the maps into the time-ordered data at a point---requires the convolution version of the kernel, while the transpose pointing matrix---projecting the time-ordered data to the map---requires the Green's function kernel.
+  The method would be similar to pixel-based strategies to deconvolve an instrument beam during map making \citep[e.g.][]{2010ApJS..187..212C}.
+However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.}
 
@@
 While this idea seems interesting, the usefulness of this implementation will depend on whether the standard $E/B$ mode spectra are easily recoverable in this fashion.
+We will explore some of these possible analysis directions in the future papers of this series.
 
-Results that demonstrate the equivalence of these real space methods to the conventional harmonic space methods will be presented in the next paper in this series, along with explorations of some of the ideas discussed above.
+Finally, the toolbox of real-space operators gives us more intuition about the $E$- and $B$-mode structure of polarized gas and dust filaments in the Milky Way, an important foreground for inflationary science.
+We demonstrate that filaments with finite length or changing radius of curvature result in $B$-mode patterns in addition to the $E$-mode pattern already expected.
+We therefore predict a characteristic $B$-mode pattern from filament sources that should be accesible in data.
 

### 2018-07-13 articles/formalism/sections/real_space_formalism.tex
Clean up mapmaking discusion

@@
 In the convolution kernels, $\mathcal{M}_G$ and $\mathcal{M}_B$ switch roles.
-The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter NSIDE=2048.
+The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
 Each panel is approximately $16^{\circ} \times 16^{\circ}$ in size with grid lines every 2 degrees.
@@
 %
-We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two Healpix pixels and use these to evaluate the convolution and radiation kernels.
+We compute the Euler angles $(\alpha, \beta, \gamma)$ given the angular coordinates of any two HEALPix pixels and use these to evaluate the convolution and radiation kernels.
 To provide an intuition for how these kernels vary as a function of position of the central pixel we depict in \fig{fig:vis_kernel} the respective kernels at a few different locations on the sphere.
-While the kernels are evaluated in the band limit $\ell \in [2,192]$, for illustration these functions are sampled at a very high Healpix resolution parameter of NSIDE=2048.
+While the kernels are evaluated in the band limit $\ell \in [2,192]$, for illustration these functions are sampled at a very high Healpix resolution parameter of $N_{\rm side}=2048$.
 All the plots have been rotated such that the central location marked by the black circle are in the centre of the figure.
-The horizontal and vertical lines that pass through the central black circle mark the local latitude and longitude respectively.
+The grid spacing is 2 degrees.
 
@@
 In particular these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}.
-From \eq{eq:qu2eb_radiation_concise}, we can see the $E/B$ patterns that $\delta$-functions in the Stokes parameters produce:
+From \eq{eq:qu2eb_radiation_concise}, we can see the $E/B$ patterns that Kronecker $\delta$-functions in the Stokes parameter pixels produce:
 %

### 2018-07-16 articles/formalism/article.tex
updates to introduction and revision to figures (removed NSIDE and corrected lmax numbers)

@@
 
-\author[]{Aditya Rotti and}
-\author[]{Kevin Huffenberger}
-\affiliation[]{Department of Physics, Florida State University, Keen Physics Building, Tallahassee, Florida 32306}
+\author[a,b]{Aditya Rotti}
+\author[a]{and Kevin Huffenberger}
+\affiliation[a]{Department of Physics, Florida State University, Keen Physics Building, Tallahassee, Florida 32306, USA}
+\affiliation[b]{Jodrell Bank Center for Astrophysics, University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 \emailAdd{adityarotti@gmail.com}

### 2018-07-16 articles/formalism/sections/introduction.tex
updates to introduction and revision to figures (removed NSIDE and corrected lmax numbers)

@@
 During recombination, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
-The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature \citep{1997NewA....2..323H}.
-The standard analysis technique converts the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, which are easier to compare to theory.
-The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations.
-Thus any $B$-modes that appear must be from:
+The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature anisotropies \citep{1997NewA....2..323H}.
+The standard analysis technique involves translating the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, since the statistics of these coordinate independent scalar fields are predicted by theory.
+
+The dominant contribution to the $E$-modes of polarization are sourced by primordial scalar perturbations, however these do not generate B-modes of polarization at first order.
+The $B$-modes of CMB polarization can be generated by various sources:
 % Need citations for all...
-(1) primordial tensor perturbations (gravitational waves), which reveal the energy scale of inflation
+(1) primordial tensor perturbations (gravitational waves)%, which reveal the energy scale of inflation
 \citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
-(2) lensing of $E$-modes, which helps to reveal the distribution of matter in the universe;
+(2) weak gravitational lensing of $E$-modes resulting as a consequence of photon deflections induced by intervening large scale structures;
 (3) foregrounds (especially Galactic synchrotron and dust emission)
@@
 \citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.
+ The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
+Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations which will finally lead to important constraints on models of inflation \cite{?}.
+The measurement of $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \cite{?}.
+
+The primary aim of the current CMB experiments is to make precise measurements of the CMB polarizations.
+While the E-modes of polarization have been measured reasonably well by a number of experiments \cite{?
+}, the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy and angular resolution.
+The detectors are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$).
+However B-mode generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.
+Precise modelling and subtraction of this large foreground contribution poses a major challenge for a robust unravelling of the minuscule $B$-mode signal.
 
 The formalism for converting the Stokes parameters to scalar quantities is well established \citep{1997PhRvD..55.7368K,1997PhRvD..55.1830Z}.
-The reason we take a detailed look at it here is that with renewed focus on foreground contamination to the $B$-mode signal, we wanted to gain an intuition for what $E/B$ mode patterns arise from physical polarized structures in the galaxy.
-We also wanted to gain insight into the problem of masking and the non-locality of the $E/B$ fields compared to the Stokes parameters.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally.
+However, in practice the $E$/$B$ modes are computed to some specified band limit and this makes them non-local functions of the polarization field.
+In other words, band limited $E$/$B$ modes evaluated at a point receive contributions from all over the sky.
+In this work we aim to gain real space insights into the non-locality of the $E/B$ fields compared to the Stokes parameters.
+With renewed focus on foreground contamination to the $B$-mode signal we aim to gain an intuition for $E/B$ mode patterns resulting from physical polarized structures in the galaxy.
+These real space insights may potentially yield new ideas for minimizing foreground contamination which may not be possible using conventional approaches.
 
-The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally.
-However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.
-In other words, the $E$/$B$ modes at a point can get contributions from all over the sky.
-
-(stuff about foregrounds, masking, ambiguous modes with references)
-
-Zaldarriaga explored the spatial real-space kernels in the flat-sky approximation \citep{Zaldarriaga2001a}.
+Some of the ideas presented in this work bear resemblance with those in \citep{Zaldarriaga2001a}, however the approach adopted here is more rigorous and consequently there are updates to interpretation of the results and substantial differences in details.
 
@@
 In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by varying the non-locality parameter and discuss the connection to the spin raising and lower operators.
+In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of realistic filaments.
 We conclude with a summary and discuss the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.

### 2018-07-16 articles/formalism/sections/discussion.tex
minor update to references, revision to discussion surround the radial kernel relation to zaldariagga kernel

@@
 We use this property to define a non-locality parameter $\beta_0$ which is simply the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
-We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180, 180 \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
+We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
 \revisit{An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.

### 2018-07-16 articles/formalism/sections/kernel_discussion.tex
minor update to references, revision to discussion surround the radial kernel relation to zaldariagga kernel

@@
 The envelope of the oscillation decays with angular separation at intermediate $\beta$ but increases as $\beta \rightarrow \pi$.
-We find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$ at intermediate $\beta$.
-However, when we average over several oscillations with a moving window, we find that the average behavior as intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
-(We have narrowed the window as the band limit increases so that the number of oscillations averaged remains the same.)  This agrees with the hypothesis for the flat sky case, for which e.g.
+We find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.6}$ at intermediate $\beta$.
+However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}  (Note: We have narrowed the window as the band limit increases so that the number of oscillations averaged remains roughly the same.).
+This agrees with the hypothesis for the flat sky case, for which e.g.
 Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).
-In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as in \fig{fig:dfbeta_avg}.}
-
-\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning from a higher band limit radial function to a radial function with an effectively lower band limit, set by the width of the sliding window.}
-\comment{K: I don't follow this sentence.} 
-\revisit{Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
-Extrapolating this trend to the case of a very high band limit we may expect that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.}
+In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.} \revisit{Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of a very high band limit we may expect that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.} \revisit{In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.}
 

### 2018-07-16 articles/formalism/sections/real_space_formalism.tex
minor update to references, revision to discussion surround the radial kernel relation to zaldariagga kernel

@@
 
-We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables, as in \citep{Zaldarriaga2001a}.
-}:
+We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.
+}:%as in \citep{Zaldarriaga2001a}
 %
@@
 \section{Real space polarization operators} \label{sec:real_space_operators}
-\subsection{Evaluating scalar $E/B$ from Stokes $Q/U$}\label{sec:qu2eb}
+\subsection{Evaluating scalars $E/B$ from Stokes $Q/U$}\label{sec:qu2eb}
 In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields $E/B$ from the Stokes parameters $Q/U$. 

### 2018-07-16 articles/formalism/sections/discussion.tex
minor edits to discussion

@@
 The radial part of the operator kernel are roughly self-similar in the sense that the radial kernels evaluated with some band limit is related to another radial kernel evaluated with a different band limit by a simple rescaling of the function.
-We use this property to define a non-locality parameter $\beta_0$ which is simply the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
+We use this property to define a non-locality parameter $\beta_0$ as the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
 We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
@@
 The $E/B$ mode maps are merely the real and imaginary parts of this field.
-
 Results that demonstrate the equivalence of these real space methods to the conventional harmonic space methods will be presented in the next paper in this series.
@@
 Deeper understanding of the non-locality of the real space operators has allowed us to generalize the real space operators that transform between the spin-2 and spin-0 representations of the CMB polarization.
-We showed how to modify and gereralize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
+We presented a systematic procedure to modify and generalize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
 We argue that these modifications to the radial kernel have the same effect as a smoothing operation on the $E/B$ fields by a circularly symmetric beam.
 Therefore it is trivial to recover the standard CMB angular power spectra from the modified scalar polarization maps resulting from the modified kernels.
-Noting that that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators, we presented a band limited representation of these operators.
+We noted that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators which allowed us to present a band limited representation of these operators.
 
@@
 We demonstrate that filaments with finite length or changing radius of curvature result in $B$-mode patterns in addition to the $E$-mode pattern already expected.
-We therefore predict a characteristic $B$-mode pattern from filament sources that should be accesible in data.
+We therefore predict a characteristic $B$-mode pattern from filament sources that should be measurable in future polarization measurements.
 

### 2018-07-17 articles/formalism/sections/introduction.tex
Minor tweaks and refs

@@
 % Need citations for all...
-(1) primordial tensor perturbations (gravitational waves)%, which reveal the energy scale of inflation
+primordial tensor perturbations (gravitational waves)%, which reveal the energy scale of inflation
 \citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
-(2) weak gravitational lensing of $E$-modes resulting as a consequence of photon deflections induced by intervening large scale structures;
-(3) foregrounds (especially Galactic synchrotron and dust emission)
+weak gravitational lensing of $E$-modes resulting from photon deflections induced by the potential of intervening large scale structure;
+foregrounds (especially Galactic synchrotron and dust emission)
 \citep{2016A&A...586A.133P};
-(4) unknown systematic problems in the data;
-(5) unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
+uncorrected systematic problems in the data \citep{2003PhRvD..67d3004H,2008PhRvD..77h3003S};
+and unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
 \citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.
+
 The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
@@
 The primary aim of the current CMB experiments is to make precise measurements of the CMB polarizations.
-While the E-modes of polarization have been measured reasonably well by a number of experiments \cite{?
-}, the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy and angular resolution.
-The detectors are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$).
-However B-mode generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.
+While the E-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy and angular resolution.
+The detectors are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$) \cite{s4 science book, pico mission study}.
+However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.
 Precise modelling and subtraction of this large foreground contribution poses a major challenge for a robust unravelling of the minuscule $B$-mode signal.
@@
 With renewed focus on foreground contamination to the $B$-mode signal we aim to gain an intuition for $E/B$ mode patterns resulting from physical polarized structures in the galaxy.
-These real space insights may potentially yield new ideas for minimizing foreground contamination which may not be possible using conventional approaches.
+These real space insights may yield new ideas for minimizing foreground contamination which may not be possible using conventional approaches.
 
-Some of the ideas presented in this work bear resemblance with those in \citep{Zaldarriaga2001a}, however the approach adopted here is more rigorous and consequently there are updates to interpretation of the results and substantial differences in details.
+Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}, however the approach adopted here is more rigorous and consequently there are updates to interpretation of the results and substantial differences in details.
+\comment{``more rigorous'' is a little harsh}
 
-This paper is organized in the following manner: In \sec{sec:pol-primer} we present a primer on the description of CMB polarization on the sphere.
-Here we begin with a heuristic argument that makes transparent the real space construction of E/B modes on the sphere.
-We discuss the standard harmonic space procedures for this operation.
-Finally we introduce the matrix-vector notation which yields a more concise description of the harmonic space procedures.
-In \sec{sec:qu2eb} and \sec{sec:eb2qu} we derive and discuss the real space operators that transform Q/U to E/B and vice versa.
+This paper is organized in the following manner: In \sec{sec:pol-primer} we present a primer on the description of CMB polarization on the sphere, beginning with a heuristic argument that makes transparent the real space construction of $E$/$B$ modes.
+We discuss the standard harmonic-space procedures for this operation.
+Finally, we introduce the matrix-vector notation which yields a more concise description of the harmonic space procedures.
+In \sec{sec:qu2eb} and \sec{sec:eb2qu} we derive and discuss the real space operators that transform $Q$/$U$ to $E$/$B$ and vice versa.
 In \sec{sec:visualize_operator} we evaluate these real space operators and present visualizations of these functions.
-In \sec{sec:purify_stokes_qu} we derive a real space operator that decomposes the Stokes Q/U  parameters into components that correspond to E and B modes respectively and present its visualizations.
+In \sec{sec:purify_stokes_qu} we derive a real space operator that decomposes the Stokes $Q$/$U$  parameters into components that correspond to $E$ and $B$ modes respectively and present its visualizations.
 In \sec{sec:radial_locality} we study the locality of the real space operators and explore its band limit dependence.
-In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by varying the non-locality parameter and discuss the connection to the spin raising and lower operators.
-In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of realistic filaments.
-We conclude with a summary and discuss the scope of this new method of analyzing CMB polarization in \sec{sec:discussion}.
+In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by controling the non-locality while recovering the standard power spectra, and we discuss the connection to the spin raising and lower operators.
+In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of foreground filaments.
+In \sec{sec:discussion}, we conclude with a summary and discuss the prospects this new method of analyzing CMB polarization.

### 2018-07-17 articles/formalism/sections/real_space_formalism.tex

@@
 %
-These $E/B$ fields are merely versions of $\mathcal{E}/\mathcal{B}$ that downweight higher-$\ell$ modes  (their spherical harmonic coefficients of expansion are reduced by the factor $[{(\ell+2)!}/{(\ell-2)!}]^{1/2}$).
-They are not local functions of Stokes $Q/U$.
+These $E/B$ fields are merely versions of $\mathcal{E}/\mathcal{B}$ that downweight higher-$\ell$ modes  (their spherical harmonic coefficients of expansion are reduced by the factor $[{(\ell-2)!}/{(\ell+2)!}]^{1/2}$).
+%They are not local functions of Stokes $Q/U$.
 %We make this choice since the CMB spectra are more closely related to the fields E \& B.
@@
 %
-The sign conventions we have chosen match HEALPix.
+The sign conventions we have chosen matches that of HEALPix.
 Using the data vectors and the matrix operators defined above we can now express, in compact notation, the forward and inverse relations between different representations of the polarization data vectors via the following equations:
@@
 Note that the function depends only on two out of the three Euler angles.
-The azimuthal part depends only on the Euler angle $\alpha_{qe}$, and so its harmonic transform has no multipole $\ell$ dependence.
+The azimuthal part depends only on the Euler angle $\alpha_{qe}$ and its harmonic transform has no multipole $\ell$ dependence.
 The azimuthal part is the crucial operation that translates between different spin representation of CMB polarization.
-Only the radial part $f(\beta_{qe})$ depends only on the angular separation between locations and hence  completely incorporates all the multipole $\ell$ dependence.
+The radial part $f(\beta_{qe})$ depends only on the angular separation between locations and completely incorporates all the multipole $\ell$ dependence.
 Recall that we had guessed the general form of the kernel using simple heuristic arguments in \sec{sec:qu2eb_heuristic}.
 Here we have rigorously derived the exact form of the function $f(\beta)$.
-Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we argued to be a necessary property to yield a field of correct spin.
+Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we had argued is a necessary property to yield a field of correct spin.
 

### 2018-07-18 articles/formalism/sections/introduction.tex
made minor revisions and finalized upto section 2.3

@@
 The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
-Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations which will finally lead to important constraints on models of inflation \cite{?}.
-The measurement of $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \cite{?}.
+Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations which will finally lead to important constraints on models of inflation and the measurement of $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \citep{Abazajian2015, Kamionkowski2016,Abazajian2016,Hu2002c,Wehus2016}.
 
@@
 
-Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}, however the approach adopted here is more rigorous and consequently there are updates to interpretation of the results and substantial differences in details.
-\comment{``more rigorous'' is a little harsh}
+\revisit{Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}, however the approach adopted here is more mathematically rigorous and consequently leads to updates in interpretation of the results and substantial differences in detail.
+This has enabled us to develop a real space polarization analysis tool, the details of which are beyond the scope of this article but will be discussed in a subsequent publication.}
 
@@
 In \sec{sec:radial_locality} we study the locality of the real space operators and explore its band limit dependence.
-In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by controling the non-locality while recovering the standard power spectra, and we discuss the connection to the spin raising and lower operators.
+In \sec{sec:generalized_operators} we present a systematic method of generalizing the real space operators by controlling the non-locality while recovering the standard power spectra and we discuss the connection to the standard spin raising and lower operators.
 In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of foreground filaments.
-In \sec{sec:discussion}, we conclude with a summary and discuss the prospects this new method of analyzing CMB polarization.
+In \sec{sec:discussion}, we conclude with a summary and discuss the prospects of this new method of analyzing CMB polarization maps.

### 2018-07-18 articles/formalism/sections/real_space_formalism.tex
made minor revisions and finalized upto section 2.3

@@
 The standard construction of $E$ and $B$ fields arise from the desire to have a coordinate independent description of the polarization.
-This follows from operations that raise (or lower) the spin of the $X$ field to construct scalar fields.
-But from the transform properties of the Stokes parameters, we can already construct a heuristic argument for what these operations must look like in real space.
+This follows from operations that raise (or lower) the spin of the field ${}_{\pm2}X$ to construct scalar fields.
+By understanding the transform properties of the Stokes parameters and those of the Euler angles on the sphere, we can already construct a heuristic argument for what these operations must look like in real space.
+We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
 
-We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
 \fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
@@
 \includegraphics[width=0.5\columnwidth]{euler.pdf}
-\caption{This figure depicts the Euler angles in the z-y1-z2 convention.
+\caption{This figure depicts the Euler angles in the $z-y1-z2$ convention.
 The cartesian coordinates shown in dark solid green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark solid red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
@@
 
-We consider the impact of local rotations on these Euler angles.
+We consider the impact of local rotations  the Stokes parameters and on these Euler angles.
 Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
 $\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)] =  {}_{+2}X(\hat{n}_q) e^{-i2\psi} $.
-This same rotation by $\psi$ alters the Euler angle $\alpha_{qe}$, the angle that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$, so that $\mathcal{R}_{\hat{z}_q}(\psi)[\alpha_{qe}] = \alpha_{qe} - \psi$.
-Therefore one can see that $\mathcal{R}_{\hat{z}_q}(\psi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\psi}$.
+This same rotation by $\psi$ alters the Euler angle $\alpha_{qe}$, the angle that aligns the $x$-axis at $\hat{n}_q$ along the geodesic to the location $\hat{n}_e$, so that: $\mathcal{R}_{\hat{z}_q}(\psi)[\alpha_{qe}] = \alpha_{qe} - \psi$.
+Therefore one can see that: $\mathcal{R}_{\hat{z}_q}(\psi)[e^{-i2\alpha_{qe}}] =  e^{-i2\alpha_{qe}} e^{i2\psi}$.
 
-Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations and must be spin-0 by definition:
+Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations and hence must be spin-0 or scalar quantity by definition:
 \beq
@@
 The same rotation $\mathcal{R}_{\hat{z}_q}(\psi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
-Thus we can conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the form:
+Thus we further conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the generic form:
 \beq
@@
 Note that when the two locations coincide ($\beta_{qe}=0$) then  $\alpha_{qe}=0,2\pi,4\pi,\dots$, implying $E + iB \propto Q+iU$.
-This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, and so we must have $f(\beta_{qe} = 0 ) = 0$.
-Hence the $E/B$ fields are necessarily non-local.
-A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$, and so $f(\beta_{qe} = \pi ) = 0$.
+This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, hence we must have $f(\beta_{qe} = 0 ) = 0$.
+This immediately implies that the $E/B$ fields are necessarily defined non-locally.
+A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$ and therefore we also require that $f(\beta_{qe} = \pi ) = 0$.
 Any such function $f$ will let us construct $E/B$-like scalar fields.
@@
 
-This type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
+Note that this type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
 transforming spin-0 fields to spin-2).
@@
 
-The standard construction of $E/B$ fields depend on the spin-raising and -lowering operators, and is usually carried out in harmonic space.
-%
-The spin-raising operator ($\eth$), applied to a field of spin-s $_{s}g$, results in a field with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
+The standard construction of $E/B$ fields is expressed in terms of the spin-raising and spin-lowering operators and this operation is usually carried out in harmonic space.
+The spin-raising operator ($\eth$) applied to a field of spin-s $_{s}g$, results in a field with spin-$(s+1)$: $(\eth _{s}g)' = e^{-i(s+1)\psi}(\eth _{s}g)$  \cite{goldberg67}.
 The complementary spin-lowering operator $(\bar{\eth})$  similarly results in a field with spin-$(s-1)$: $(\bar{\eth} _{s}g)' = e^{-i(s-1)\psi}(\bar{\eth} _{s}g)$.
-The complex spin-0 scalar now arise from  the spin-2 fields ${_{\pm 2}X}$ as follows,
+The complex spin-0 scalar now arise from these spin lowering/raising operations of the spin-2 fields ${_{\pm 2}X}$ as follows:
 %
@@
 The $\cal E/B$ fields are defined locally at point $\hat n$ in terms of the operators $\eth$ and $\bar \eth$.
-
 It is possible to decompose the complex field $_{\pm 2}\bar{X}$ into spin spherical harmonic functions: ${}_{\pm 2}\bar{X}(\hat{n}) = \sum_{\ell m} {}_{\pm 2} \tilde X_{\ell m} {}_{\pm 2}Y_{\ell m}(\hat{n})$.
@@
 %
-These $E/B$ fields are merely versions of $\mathcal{E}/\mathcal{B}$ that downweight higher-$\ell$ modes  (their spherical harmonic coefficients of expansion are reduced by the factor $[{(\ell-2)!}/{(\ell+2)!}]^{1/2}$).
-%They are not local functions of Stokes $Q/U$.
-%We make this choice since the CMB spectra are more closely related to the fields E \& B.
+These $E/B$ fields are merely versions of $\mathcal{E}/\mathcal{B}$ that downweight higher-$\ell$ modes  (i.e.
+their spherical harmonic coefficients of expansion are reduced by the factor $[{(\ell-2)!}/{(\ell+2)!}]^{1/2}$).
 
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
-Our derivation of real space operators is more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
+Our derivations of the real space operators are more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
 We introduce a matrix that encodes spin spherical harmonic basis vectors:
@@
 
-We define transformations between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2}\bar{X}$ and back):
+We define an operator that transforms between different representations of the polarization field (i.e. from $Q,U$ to $_{\pm2}\bar{X}$ and back):
 %
@@
 %
-Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$), and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
+Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$) and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
 %

### 2018-07-19 articles/formalism/sections/real_space_formalism.tex
revisions to near finalize section 3-3.3

@@
 %To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
-In this section we derive the real space kernels which we can use to directly evaluate the scalar fields $E$ and $B$ on the sphere.
+In this section we derive the real space operators which can be used to directly evaluate the scalar fields $E$/$B$ on the sphere.
 We use the vector-matrix notation introduced in \sec{sec:mat_pol_intro} to write down an operator equation relating the real space vector of scalars \vs to the Stokes polarization vector \vp{}:
@@
 Here we have rigorously derived the exact form of the function $f(\beta)$.
-Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it is easy to show that $f(\beta)$ vanishes at $\beta=0,\pi$, which we had argued is a necessary property to yield a field of correct spin.
+Studying the $P_{\ell}^2$ functions in the limits $\beta \rightarrow 0,\pi$ it can be shown that $f(\beta)$ vanishes at $\beta=0,\pi$, which we had argued is a crucial property to yield a field of correct spin.
 
@@
 In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluating its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.
-This one-to-many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented in \fig{fig:planar_euler_angles}.
+This one-to-many mapping from a point in the spin-2 Stokes field to the complex spin-0 (scalar) field across the sphere is graphically represented by the blue circle in \fig{fig:planar_euler_angles}.
 
@@
 This convolution is performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `$q$' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
-On the flat sky $\gamma_{eq}=-\alpha_{qe}$ and consequently there is no difference between the radiation and convolution kernels.}
+\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `$q$' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.}
 \label{fig:planar_euler_angles}
@@
 %
-%Both these facts can be associated with the fact that this function does not depend on the Euler angle $\gamma$. 
-%\comment{Add discussion here on the inverse greens function and why it changes as a function of position.}
+\revisit{It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+This result can also be understood as the flat sky case where the radiation and convolution kernels are expected to be identical.}
 

### 2018-07-19 articles/formalism/sections/real_space_formalism.tex
revisions to near finalize section 3.3-3.4

@@
 %
-\revisit{It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+\revisit{It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
 This result can also be understood as the flat sky case where the radiation and convolution kernels are expected to be identical.}
@@
 It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
-In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes.
-The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here, and outline only the key points.
+In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar $E/B$ modes.
+The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here and outline only the key points.
 We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators.
@@
 \bar O_E \, \bar O_E &=& \bar O_E;\qquad \bar O_B \, \bar O_B = \bar O_B \,, \\
-\bar O_E \, \bar O_B &=& 0 \,,\\
+\bar O_E \, \bar O_B &=& 0 \,,\label{eq:real_ortho}\\
 \bar O_E + \bar O_B &=& \mathcal{I} \,,
@@
 This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact and a more crucial property of the operators.
+Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.

### 2018-07-19 articles/formalism/sections/kernel_discussion.tex
final remarks of sec 3.5. Revised figures to reflect details given in text.

@@
 The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-It oscillates and as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
-%This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.
+It has an oscillatory nature at intermediate angular separations and vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$ (this is critical to ensure that the derived fields have the necessary spin properties), since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
 
@@
 %It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. 
-To quantify this non-locality, we study the radial extent of the kernels and its dependence on the maximum multipole accessible.
+To quantify the non-locality of the real space operators, we study the radial extent of the respective radial kernels and their dependence on the maximum multipole accessible.
 We evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
@@
 The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}.
-While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.
+The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.
 This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
@@
 These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar and related by this telescoping and scaling property:
-$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad \mbox{(small angles)},$$
+$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad \revisit{\mbox{(small angles)}},$$
 where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
 This telescoping property encapsulates both the amplitude scaling and leftward shift of the radial kernels on increasing the maximum multipole.
-Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.
+\revisit{Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified(supressed) by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed(expanded) by a factor $(\ell'_{\rm max}/\ell_{\rm max})$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$ when $\ell_{\rm max} > \ell'_{\rm max}$($\ell_{\rm max} < \ell'_{\rm max}$).}
 
@@
 
-\revisit{The radial function ${}_\mm f(\beta)$ is oscillatory, regardless of the maximum $l_{\rm max}$.
+The radial function ${}_\mm f(\beta)$ is oscillatory, regardless of the maximum $\ell_{\rm max}$.
 The envelope of the oscillation decays with angular separation at intermediate $\beta$ but increases as $\beta \rightarrow \pi$.
 We find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.6}$ at intermediate $\beta$.
-However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}  (Note: We have narrowed the window as the band limit increases so that the number of oscillations averaged remains roughly the same.).
-This agrees with the hypothesis for the flat sky case, for which e.g.
+However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
+We set the width of the smoothing window to $0.3\beta_0$, this results in the narrowing of the smoothing width as the band limit increases so as to keep the number of oscillations averaged over, remain roughly the same.
+This agrees with the hypothesis for the \revisit{flat sky case} \comment{is this flat sky or continuum case?}, for which e.g.
 Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).
-In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.} \revisit{Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
-Extrapolating this trend to the case of a very high band limit we may expect that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.} \revisit{In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.}
+In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.
+Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
+In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.
 
-\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function partly falls outside the domain and this is in part responsible for the scaling deviating from the power law, but it is also important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.}
+Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function partly falls outside the domain and this is in part responsible for the scaling deviating from the power law, but it is also important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.

### 2018-07-19 articles/formalism/sections/generalizedeb.tex
final revision to sec4 and sec5. cleaned up the latex files by removing all the commented lines.

@@
 The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.
-The radial parts of the stardard operators are determined by the sum over spherical harmonics and varies as a function of the band limit.
+The radial parts of the standard operators are determined by the sum over spherical harmonics and varies as a function of the band limit.
 It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
@@
 This constrains the choice of $\tilde{\mathcal{G}}$ to have a valid  inverse and is important to recover the standard CMB power spectra.
-The radial parts of this generalized operator and its inverse are given by the following expressions,
+The radial parts of this generalized operator and it's inverse are given by the following expressions,
 %
@@
 The default radial function is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$), in which case $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)={{}_{\mm}f}$.
-
-While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$ rather than the harmonic space $g_l$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
-Employing the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the expression,
-%
-\beq
-g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,. \label{eq:gb2bl}
-\eeq
-%
-
-An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
-%
-\beq
-b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
-\eeq
-%
-where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
-In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
-Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
 %
@@
 
+While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$ rather than the harmonic space $g_l$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
+Employing the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the expression,
+%
+\beq
+g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,. \label{eq:gb2bl}
+\eeq
+%
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
+%
+\beq
+b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
+\eeq
+%
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
+In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
+
 % Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
 In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
- \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.
+ \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, a radial function without oscillations and an exponential cutoff.
 Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
@@
 \fig{fig:glbl} depicts the harmonic description $g_{\ell}$ for these respective radial kernels and beams.
-Finally, the beam that the modified radial kernels appies to the $E/B$ fields we show in \fig{fig:gl_bbeta}.
+Finally, the beam that the modified radial kernels effectively apply to the $E/B$ fields are shown in \fig{fig:gl_bbeta}.
 Note that the beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of a delta-function beam.
-%In \sec{sec:local_conv_eb} we constructed localized convolution kernels by multiplying $R(\beta)$ with an apodized version of the step function $\theta_{\rm apo}(r_{\rm cutoff})$.
-The oscillation seen in the spectra in \fig{fig:eb-spectra_rad_cutoff} can be explained to be due to this effective beam characterized by $g_{\ell}^2$ operating on the power spectra.
-The effective beam can be evaluated by computing the multipole function $g_{\ell}$ as follows,
-%%
-%\beq
-%g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{r_{\rm cutoff}} R(\beta) \theta_{\rm apo}(r_{\rm cutoff})  P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,, \label{eq:gb2bl} \,,
-%\eeq
-%%
-%where the upper limit of the integration is set to $r_{\rm cutoff}$ since the function $\theta_{\rm apo}(r_{\rm cutoff})$ vanishes for $\beta>r_{\rm cutoff}$.
-The function $b^2_{\ell}-1$ matches the oscillation seen in \fig{fig:eb-spectra_rad_cutoff} as  seen in \fig{fig:match_cl_oscillations} where the two results have been over plotted.
-%%
-%\begin{figure}[!t] 
-%\centering
-%\subfigure[]{\includegraphics[width=0.98\columnwidth]{analytical_cl_oscillations_vs_data.pdf}}
-%\caption{The thin lines depicts the same spectral differences as those seen in \fig{fig:eb-spectra_rad_cutoff}, while the thick lines of the corresponding color depict the function $g_{\ell}^2 -1$ as derived from evaluating \eq{eq:gb2bl} for different $r_{\rm cutoff}$}.
-%\label{fig:match_cl_oscillations}
-%\end{figure}
-%%
-%The apodized step function in this case transition from 1 at $\beta < r_{\rm cutoff} -w$ to 0 at $r_{\rm cutoff}$ over a width $w= 3^{\circ}$ with a cosine squared profile .
-
-%--------------------------------------------------------
-%\subsubsection{Recovering the standard $E$ and $B$ mode spectra}
 
@@
 which are merely filtered versions of the standard $E/B$ modes maps.
-Since the filter function is simply $g_{\ell}$, easily obtained from the modified radial function $G(\beta)$, and it can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam, the power spectra of the modified scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
+The filter function is simply $g_{\ell}$, easily obtained from the modified radial function $G(\beta)$ and it can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam.
+The power spectra of the modified scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %
@@
 Therefore the standard CMB spectra can always be recovered as long as the $1/g_{\ell}$ and $1/g_{\ell}^2$ are well behaved functions, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
-%Some examples forms of $G(\beta)$, its harmonic representation $g_{\ell}$ (and its inverse $1/g_{\ell}$ ) and the corresponding beam $B(\beta)$ are depicted in \fig{fig:example_gbeta}.
-%One direct application of this freedom in choosing the radial kernel is that one can mitigate the issue of leakage of power from $E$ to $B$.
-By constructing a radial function which tapers to zero at sufficiently small radii one can clearly discard pixels which are affected by masking.
 %--------------------------------------------------------
@@
 %
-Comparing to \eq{eq:ebdef_lower} %to \eq{eq:bl_ebdef_lower}
-makes apparent the following mapping:
+Comparing to \eq{eq:ebdef_lower} makes apparent the following mapping:
 %

### 2018-07-19 articles/formalism/sections/kernel_paintbrush.tex
updates to introduction and revision to figures (removed NSIDE and corrected lmax numbers)
final revision to sec4 and sec5. cleaned up the latex files by removing all the commented lines.

@@
 \section{Understanding polarization signatures of magnetized filaments}
+\label{sec:pol_filaments}
+
+The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
+For example, a simple model for a magnetized filament has the magnetic field threaded along a linear gas over-density.
+Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and perpendicular to the filament overall).
+For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}).
+The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.
+
+The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.
+The positive components for the $E$ part of the Green's function align and reinforce along the filament, consequently the filament is highlighted as a segment with $E>0$.
+Since the over-density will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.
+The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.
+
+The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.
+This results in a non-zero $B$ pattern for the filament.
+For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East as seen in \fig{fig:polfilaments}.
+The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
+In contrast to the kernel radial fuctions, which are more compact at higher band limit, the filament $B$-mode  pattern does not depend much on the band limit, provided it is sufficient to resolve the filament structure.
+A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
+
+The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.
+However, unlike a circular ring, this filament is not a configuration with a definite parity.
+Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
+For example, a filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
+
+Changing the polarization direction within the filament changes the $E/B$ patterns.
+A $90^\circ$ rotation of the polarization with respect to the filament changes the sign of both $E$ and $B$.
+In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
+The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments (infinite and without ends) can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
+Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament, this information could potentially shed light on the internal dynamics of filaments.
 % 
@@
 %
-
-The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
-For example, a simple model for a magnetized filament has the magnetic field threaded along a linear gas overdensity.
-Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and perpendicular to the filament overall).
-For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}).
-The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.
-
-The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.
-The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted as a segment with $E>0$.
-Since the overdensity will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.
-The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.
-
-The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.
-This results in a non-zero $B$ pattern for the filament.
-For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.
-The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
-In contrast to the kernel radial fuctions, which are more compact at higher bandlimit, the filament $B$-mode  pattern does not depend much on the bandlimit, provided it is sufficient to resolve the filament structure.
-A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
-
-The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.
-However, unlike a circular ring, this filament is not a configuration with a definite parity.
-Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
-For example, a filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
-
-Changing the polarization direction within the filament changes the $E/B$ patterns.
-A $90^\circ$ rotation of the polarization with respect to the filament changes the sign of both $E$ and $B$.
-In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
-The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments (infinite and without ends) can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
-Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament.
-
-The intuition from the real-space kernels holds also when we distort the shape of the filament.
+\indent The intuition from the real-space kernels holds also when we distort the shape of the filament.
 If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
@@
 A spiral turning with the other handedness will have a $B$-pattern with the opposite sign.
-%\footnote{ \revisit{Why do we use this specific spiral - Its easy to compute the tangent to the spiral at any point.}}.
 
-%\comment{If this is correct, then one expects to see a higher B-mode signal in intermediate regions of the spiral, as compared to the B-mode signal in the intermediate regions of the linear filament.
-This  then should be more visible in a logarithmically scaled version of Fig.
-8.}  % K: addressed with new plot
-
-%\revisit{Note that we have made the simplifying assumption that the polarization headless vectors are perpendicular to the magnetic field which is always assumed parallel to the tangent to the filament at any given point.
-This results in generating dominantly an E-mode signal while the B-mode signal is present only near the edges.
-By similar arguments it can be shown that that polarization pattern will be dominated by B-modes if the polarization vectors were aligned at $+45$ (or $-45$) degrees to the tangent to the filament while the E-mode signal would only be present at the edges.
-One way to get this configuration is to change the orientation of the magnetic field vector with respect to the tangent to the filament.
-Therefore a careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the length of the filament.} % K: addressed
-
-%\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.
-We predict that it should be there in higher fidelity data.}
 A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claims no $B$-mode signal above the noise.
@@
 While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
-
-%\revisit{In \cite{Zaldarriaga2001a} it is argued that linear filaments of infinite length in which the configuration of the polarization vector is parallel or perpendicular to the length of the filament cannot produce B-mode power.
-While this conclusion is true for filaments of infinite length, in reality we expect filaments that are observed on the sky to have a finite length and in this case one expects a definite B-mode pattern from the edges of the filament.
-One also does not expect that filaments have a constant radius of curvature and this will result in an additional generation of B-mode power.
-Therefore our study indicates results which subtly differ from those presented in \cite{Zaldarriaga2001a} and these differences can be attributed to the more realistic assumptions about the geometry of the filaments made in our analysis.} \comment{Move to conclusions?}

### 2018-07-19 articles/formalism/sections/kernel_discussion.tex
cleaned up latex files of text not appearing in the final draft

@@
-  %%%% NEW D/I
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{m{8ex}m{\kernelfigwidth}m{\kernelfigwidth}|m{\kernelfigwidth}m{\kernelfigwidth}}
-$b=90^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf} \\
-$b=87^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf} \\
-$b=80^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf} \\
-$b=0^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf} \\
-&
-\centering $\textrm{Re} \left(\mathcal{D} \right)$ &
-\centering $\textrm{Im} \left(\mathcal{D} \right)$ &
-\centering $\textrm{Re} \left(\mathcal{I} \right)$ &
-\centering $\textrm{Im} \left(\mathcal{I} \right)$
-  \end{tabular}
-  \end{center}
-  \caption{Like Figure \ref{fig:vis_kernel}, but for the kernels that purify Stokes parameter into their $E/B$ parts.} \label{fig:vis_kernel_DI}
-\end{figure}
-
-%\begin{figure} \label{fig:mixing_kernel}
-  %%%%  OLD VERSION %%%%
-%  \centering
-%\captionsetup[subfigure]{labelformat=empty}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf}}\hspace{-2mm}
-
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf}}\hspace{-2mm}
-
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf}}\hspace{-2mm}
-%\subfigure[$ \textrm{Re} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Im} \left(\mathcal{M}_{G} \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Re}  \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Im} \left(\mathcal{M}_{B}^* \right) $]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Re} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Im} \left(\mathcal{D} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Re} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf}}\hspace{-2mm}
-%\subfigure[$\textrm{Im} \left(\mathcal{I} \right)$]{\includegraphics[width=0.125\columnwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf}}\hspace{-2mm}
-%\caption{This panel of figure depicts the real and imaginary parts of the real space kernels $\mathcal{M}_{G}$, $\mathcal{M}_{B}$, $\mathcal{D}$ \& $\mathcal{I}$ respectively.
-These kernels have been evaluated with the band limit: $\ell \in [2,192]$ and sampled at the Healpix resolution parameter NSIDE=2048 for visual appeal.
-The size of each panel is approximately $16^{\circ} \times 16^{\circ}$ and the grid lines are marked at 2 degree separations.
-The black circles denotes the position of the center around which the kernels have been evaluated while the black star marks the location of the north galactic pole.
-The four rows depict the kernels at different location on the sphere and the galactic coordinates of the central pixel are specified in each panel.}
-%from top to bottom rows are as follows $[b,\ell] = [0^{\circ},0^{\circ}], [87^{\circ},0^{\circ}], [87^{\circ},30^{\circ}], [80^{\circ},30^{\circ}], [0^{\circ},90^{\circ}]$.}
-%\label{fig:vis_kernel}
-% \end{figure}
-%
-
-%\textit{Evaluating the local kernels: }\revisit{Let us consider the case when one of the coordinates coincides with the north pole $\hat{z}=(0,0)$ (this refers to the point $\theta_0 \rightarrow 0$ while moving along the longitude $\phi_0=0$).
-In this case the Euler angles in the $z-y1-z2$ convention are simply given by: $(\alpha,\beta,\gamma) =(\phi_i,\theta_i,0)$, where $(\theta_i,\phi_i)$ denote the coordinates of the location $\hat{n}_i$.} Since the Euler angle $\gamma=0$ when rotations are defined with respect to the pole, the respective kernels simplify to the following forms,
-%%
-%\begin{subequations}
-%\beqry 
-%\mathcal{M}(\hat{z},\hat{n}_i) &=&  \sum_{\ell} {{}_{0}}a_{\ell 2} \, {{}_{0}}Y_{\ell 2}(\hat{n}_i) \,;\\
-%\mathcal{I}(\hat{z},\hat{n}_i) &=& \sum_{\ell} {{}_{-2}}a_{\ell 2}\, {{}_{-2}}Y_{\ell 2}(\hat{n}_i) ~~\,;~~
-%\mathcal{D}(\hat{z},\hat{n}_i) =\sum_{\ell} {{}_{2}}a_{\ell 2} \, {{}_{2}}Y_{\ell 2}(\hat{n}_i) \,,
-%\eeqry
-%\end{subequations}
-%%
-%where ${}_{s}a_{\ell 2} = \sqrt{\frac{2 \ell+1}{ 4 \pi}} ~~\forall ~~ s \in [0,-2,+2]$.
-%The convolution kernels centered around any other location $\hat{n}_j = (\theta_j,\phi_j)$ are simply given by evaluating the respective spherical harmonic sums: $\sum_{\ell m} {}_{s}a_{\ell m}\,{}_{s}Y_{\ell m}(\hat{n}_i)$ using the rotated harmonic coefficients given by: ${}_s a_{\ell m} = D^{\ell}_{m 2}(\phi_j , \theta_j, 0) {{}_s}a_{\ell 2}$, where $D^{\ell}_{2 m}$ are the Wigner-D functions.
-%These rotation operations can be carried out using inbuilt Healpix routine \textit{rotate\_alm}, while the convolution kernels can be synthesized by evaluating the respective spherical harmonic sums using the \textit{alm2map} routine.
-%\comment{Make parallels with instrument beam analysis here ? Or is it trivial since its obvious that all convolution problems can be cast in this form.}
-
-%
-
-The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}.
-These kernels show a two fold symmetry in the vicinity of the poles.
-Here the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
-Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}_G$.
-The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
-On transiting to lower latitudes, however, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
-This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$.
-Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$.
-The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}$ and $b=80^{\circ}$ and serve to indicate the rate of this transition.
-As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
 \subsection{The non-locality of the real space operators} \label{sec:radial_locality}
@@
 These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}
-%While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
 \label{fig:rad_ker_decay}
@@
 \paragraph{Band limit dependence.} 
-%It is clear from previous discussions that the scalar field $E$ \& $B$ constructed at a location depends on the Stokes field in the surrounding regions. 
 To quantify the non-locality of the real space operators, we study the radial extent of the respective radial kernels and their dependence on the maximum multipole accessible.
@@
 We define a non-locality parameter $\beta_{0}$ as the angular distance beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transitions to being consistently below 1\% of its maximum.
-%For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}.
-Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
 The empirical relation:
@@
 with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}.
-Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.%\comment{How sensitive is this transition point to $\ell{\rm min}$?}
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.
 

### 2018-07-19 articles/formalism/sections/real_space_formalism.tex
cleaned up latex files of text not appearing in the final draft

@@
 \section{Polarization primer} \label{sec:pol-primer}
-%\subsection{Constructing $E/B$ fields without harmonic space}
 \subsection{Heuristic, real-space construction of E/B fields on the sphere} \label{sec:qu2eb_heuristic}
-%\comment{Need a better title for the section that gives the heuristic argument}
-%\textit{Alternative for bringing the heuristic argument earlier.}
 
@@
 %
-%which by the virtue of being scalars are independent of coordinate definitions.
-%The real part of this complex spin-0 scalar field corresponds to the E-mode while the imaginary part to the B-modes \cite{Kamionkowski1997}.
 The $\cal E/B$ fields are defined locally at point $\hat n$ in terms of the operators $\eth$ and $\bar \eth$.
@@
 
-We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.
-}:%as in \citep{Zaldarriaga2001a}
+We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}
 %
@@
 \begin{subequations} \label{eq:pol_data_relns}
-  %Kevin's version
   \beqry
@@
   \eeqry
-% Aditya's version
-%\beqry
-%\bar{X} &=& \bar T * \bar{P} ~~;~~\bar{P} = \frac{1}{2} \bar T^{\dagger} * \bar{X} \,, \\
-%\bar X &=&  {{}_2\mathcal{Y}} * \tilde X  ~~;~~ \tilde X ={{}_2\mathcal{Y}}^{\dagger} * \bar X  \,, \\
-%\tilde{X} &=& \tilde T * \tilde{S} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\ 
-%\bar S &=&  {{}_0\mathcal{Y}} * \tilde S ~~;~~  \tilde S =  {{}_0\mathcal{Y}}^{\dagger} * \bar S \,.
-%\tilde X &=&  {{}_2\mathcal{Y}}^{\dagger} * \bar X ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{S} &=& {{}_0\mathcal{Y}}*\tilde S ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,.\\
-%\bar{X} &=& \bar T * \bar{P} ~~;~~ \tilde{X} = \tilde T * \tilde{S} \,, \\
-%\bar{P} &=& \frac{1}{2} \bar T^{\dagger} * \bar{X} ~~;~~ \tilde{S} = \frac{1}{2}\tilde T^{\dagger} * \tilde{X} \,. \\
-%\eeqry
 \end{subequations}
@@
 Note that these harmonic space matrices are idempotent ($\tilde O_E  \tilde O_E = \tilde O_E;  \tilde O_B  \tilde O_B= \tilde O_B$), orthogonal ($\tilde O_E  \tilde O_B = \mathbb{0}$) and sum to the identity matrix ($\tilde O_E + \tilde O_B = \mathbb{1}$).
-%
-%\begin{subequations} \label{eq:har_op_prop}
-%\beqry
-%\tilde O_E  \tilde O_E&=& \tilde O_E ~~;~~  \tilde O_B  \tilde O_B= \tilde O_B \,,\\
-% \tilde O_E  \tilde O_B&=& \mathbb{0} \,, \label{eq:op_eb_ortho}\\ 
-% \tilde O_E + \tilde O_B&=& \mathbb{1} \,.
-%\eeqry
-%\end{subequations}
-%
+
 The above relations for these harmonic space operators are exactly valid.  In the following sections we derive the real space analogues ($O_E,O_B$) of these harmonic space operators.
@@
 In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields $E/B$ from the Stokes parameters $Q/U$.
-%To reiterate, this process involved taking the spin harmonic transform of the complex spin-2 fields ${}_{\pm2} \bar X$, forming specific linear combinations of the resultant coefficients of expansion ${}_{\pm 2} \tilde X_{\ell m}$ and evaluating the forward spin-0 transform to derive the scalar E \& B fields.
+
 In this section we derive the real space operators which can be used to directly evaluate the scalar fields $E$/$B$ on the sphere.
@@
 \left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
-%&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
 &=& \Delta \Omega \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_q) \,,
@@
 [E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max}) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
-%&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
 &=& \Bigg\lbrace \mathcal{M}_{B} \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
@@
 %
-%The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
-%%
-%\beq
-%\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
-%\eeq
-%%
+
 The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation:
@@
 \begin{tabular}{m{8ex}m{\kernelfigwidth}m{\kernelfigwidth}|m{\kernelfigwidth}m{\kernelfigwidth}}
-%      & \multicolumn{2}{c}{$E+iB$} & \multicolumn{2}{c}{$Q+iU$} \\
 $b=90^\circ$ &
@@
 Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.
+%
+\begin{figure}[!t]
+  \begin{center}
+  \begin{tabular}{m{8ex}m{\kernelfigwidth}m{\kernelfigwidth}|m{\kernelfigwidth}m{\kernelfigwidth}}
+$b=90^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf} \\
+$b=87^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf} \\
+$b=80^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf} \\
+$b=0^\circ$&
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf} \\
+&
+\centering $\textrm{Re} \left(\mathcal{D} \right)$ &
+\centering $\textrm{Im} \left(\mathcal{D} \right)$ &
+\centering $\textrm{Re} \left(\mathcal{I} \right)$ &
+\centering $\textrm{Im} \left(\mathcal{I} \right)$
+  \end{tabular}
+  \end{center}
+  \caption{Like Figure \ref{fig:vis_kernel}, but for the kernels that purify Stokes parameter into their $E/B$ parts.} \label{fig:vis_kernel_DI}
+\end{figure}
+%
+
+The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}.
+These kernels show a two fold symmetry in the vicinity of the poles.
+Here the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
+Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}_G$.
+The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.
+On transiting to lower latitudes, however, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function.
+This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$.
+Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$.
+The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}$ and $b=80^{\circ}$ and serve to indicate the rate of this transition.
+As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.

### 2018-07-20 articles/formalism/sections/discussion.tex
added references for r>0.001 and minor edits to text

@@
 We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
-\revisit{An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.
+An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.
 It did not explicitly derive the radial part of the kernel, but argued on geometric grounds that it should fall with angular separation as $\beta^{-2}$.
-We find that this agrees with the average behavior of radial functions after averaging oscillations, and some such averaging takes place due to pixelization of the signal.
-However, for precision reconstruction of $E/B$ on the sphere, the oscillations must be taken into account.}
+We find that this agrees with the average behavior of radial functions after averaging oscillations and some such averaging takes place due to pixelization of the signal.
+However, for precision reconstruction of $E/B$ on the sphere, the oscillations must be taken into account.
 
 Our careful study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
-\revisit{The convolution interpretation is not a totally new concept.
+The convolution interpretation is not a totally new concept.
 It guides the discussion in \cite{Zaldarriaga2001a} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
-However, the Green's function interpretation of the operators is a new one and is discussed here for the first time.} These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
+However, the Green's function interpretation of the operators is a new one and is discussed here for the first time.
+These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
 
@@
 
-%\revisit{Discussion on results from polarized filaments, compare and contrast with those in \cite{Zaldarriaga2001a}.}
-
 Modified real-space operators with compact kernels could open several alternative analysis routes in the future.
@@
 
-%Although the scaling for the real space method (${\cal O}(N_{\rm pix}^2)$) is steeper than for the spherical harmonic transforms (${\cal O}(N_{\rm pix}^{3/2})$), the simple parallelization and the small prefactor for compact kernels at high-resolution / high-band-limit could make it faster in some contexts.
-It can have a small memory footprint.
-\comment{Does parallel S2hat have memory constraints at high l?}  The evaluation of contribution from charges in the masked portion of the sky can simply be omitted.
-\comment{hybrid low-l / high-l schemes}
-
-\revisit{The real space kernels could in principle be incorporated into the pointing matrices for map making, allowing maps of $E/B$ to be made directly from instrument data, without the need for Stokes parameter maps as intermediate products.
+The real space kernels could in principle be incorporated into the pointing matrices for map making, allowing maps of $E/B$ to be made directly from instrument data, without the need for Stokes parameter maps as intermediate products.
   The pointing matrix---projecting the maps into the time-ordered data at a point---requires the convolution version of the kernel, while the transpose pointing matrix---projecting the time-ordered data to the map---requires the Green's function kernel.
   The method would be similar to pixel-based strategies to deconvolve an instrument beam during map making \citep[e.g.][]{2010ApJS..187..212C}.
-However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.}
+However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.
 
@@
 We therefore predict a characteristic $B$-mode pattern from filament sources that should be measurable in future polarization measurements.
-
-%\revisit{The discussion till now gives the impression that using the localized convolution kernels is no different from from using the default kernel and altering the spherical harmonic coefficients of expansion of the relavant fields by appropriately operating on them with the  effective beam functions $g_{\ell}$.
-To appreciate the difference between these two, it is important to realize that in general one can make a choice of a radial function which may not have a band limited description.
-In such a case these two method of evaluating the relevant fields is not identical.
-An example of this claim is depicted in \fig{fig:example_gbeta}.\\
-%Another important thing to realize is that the harmonic coefficients derived from default full sky operations get some contributions from different portions of sky.
-For instance evaluating the E and B fields in the vicinity of the poles is are prone to receiving significant contributions from strong foregrounds near the equator.
-Correcting the harmonic coefficients of expansion with the effective beam function does not cancel these non-local contribution.
-On the contrary by performing the convolution with the localized real space kernels, the regions which contribute to the local field evaluations are predetermined by the choice of the radial function.}

### 2018-07-20 articles/formalism/sections/introduction.tex
added references for r>0.001 and minor edits to text

@@
 While the E-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy and angular resolution.
-The detectors are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$) \cite{s4 science book, pico mission study}.
+The instruments are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$) \cite{Spider, CLASS,Litebird, BICEP22015}.
 However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.

### 2018-07-20 articles/formalism/sections/kernel_discussion.tex
added references for r>0.001 and minor edits to text

@@
 These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar and related by this telescoping and scaling property:
-$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad \revisit{\mbox{(small angles)}},$$
+$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad ,$$
 where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
 This telescoping property encapsulates both the amplitude scaling and leftward shift of the radial kernels on increasing the maximum multipole.
-\revisit{Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified(supressed) by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed(expanded) by a factor $(\ell'_{\rm max}/\ell_{\rm max})$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$ when $\ell_{\rm max} > \ell'_{\rm max}$($\ell_{\rm max} < \ell'_{\rm max}$).}
+\revisit{Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed by a factor $(\ell'_{\rm max}/\ell_{\rm max})$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$ when $\ell_{\rm max} > \ell'_{\rm max}$.
+The details of the accuracy of this approximation vary with the angular separation $\beta$ and the difference in the maximum multipoles ($\ell_{\rm max}$ \& $\ell'_{\rm max}$)  used in evaluating the two functions.}
 
@@
 We set the width of the smoothing window to $0.3\beta_0$, this results in the narrowing of the smoothing width as the band limit increases so as to keep the number of oscillations averaged over, remain roughly the same.
-This agrees with the hypothesis for the \revisit{flat sky case} \comment{is this flat sky or continuum case?}, for which e.g.
+This agrees with the hypothesis for the \revisit{flat sky and continuum case}, for which e.g.
 Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).

### 2018-07-20 articles/formalism/article.tex
made minor revisions and finalized upto section 2.3
cleaned up latex files of text not appearing in the final draft
corrected reference file
Minor edits and cleanup through the introduction

@@
 \renewcommand{\thesubfigure}{(\roman{subfigure})}
-%\renewcommand{\thesubfigure}{}
 
@@
 \begin{document}
-%\title{Quantifying the locality of operators that translate Stokes $Q$ \& $U$ to scalars $E$ \& $B$}
-%\title{Real space operators for Stokes $Q$ \& $U$ to scalars $E$ \& $B$ translation}
-%\title{Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels}
 \title{Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments}
@@
 \abstract{
-\noindent 
-    {We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters and the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background (CMB) and cosmic shear analysis.
+  \noindent {We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters and the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background (CMB) and cosmic shear analysis.
 We also derive real space operators that decompose the measured Stokes parameters into those corresponding to $E$-modes and $B$-modes respectively, without ever evaluating the scalar fields themselves.
@@
 For all these real space operators we show that the kernels split naturally into angular and radial parts and we show explicitly how the radial extent of these kernels depends on the targeted band-limit.
-We show that the kernels can be interpreted either as a complex convolving beam or a Green's function when they are expressed as functions of the forward or inverse rotation Euler angles respectively.
+We show that each kernel can be interpreted either as a complex convolving beam or as a Green's function when they are expressed in terms of the Euler angles  respectively for a forward or inverse rotation.
 We show that an arbitrary radial function can produce $E/B$-like maps, provides it vanishes at the origin and the  antipodal point.
 These maps are simply filtered versions of the standard $E/B$ maps.
-We present a scheme to derive this window function for any radial dependence.
+We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function, which we show how to derive for any radial dependence.
 For this reason we can compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and could be employed in a massively-parallel scheme at high-resolution.
-We show that the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators are another special case of these generalized radial functions, and present their band limited versions.
-We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function.
+We show that the spin raising  and lowering  operators $\eth^2$/$\bar{\eth}^2$ are special cases of these generalized radial functions, and present their band limited versions.
     The spatial structure of the real space operators provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds.
-We predict a non-zero $B$-mode signature that is expected from finite filaments in the sky.
-This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.
+We predict a non-zero $B$-mode signature that is expected from polarized filaments in the sky.
+This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.}
 }
-  \\
-  \\
-%  We derive fully sky real space operators to translate Stokes Q \& U parameters to scalars $E$ \& $B$ and vice versa.
-We explicitly show that these local real space operator are fully characterized by the spin-0 $Y_{\ell 2}$ spherical harmonic functions.
-These real space operators make transparent the association of radial and tangential patterns of polarization with the E modes and that of  the clockwise and anti-clockwise pinwheel patterns of polarization with B-modes.
-We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidate these derivations.
-Using this new notation also allows us to derive real space operators which decompose the measured Stokes parameters into those corresponding to E-modes and B-modes respectively, without ever evaluating the scalar fields themselves.
-We use these analytical derivations us to quantify the non-local nature of the relation between the two representations of the polarization field.
-We present a prescription for generalizing these operators, which allow the non-local behavior of these operators to be a tunable parameter.
-We derive constraints on these generalized operators to ensure reliable recovery of the standard $E$ and $B$ fields and the corresponding power spectra.
-\revisit{This is part 1 of a series of papers where we have derived the real space operators.
-In the following papers we will explore some of their applications.} \comment{Needs better blending.}
-}
-
 \maketitle

### 2018-07-20 articles/formalism/sections/introduction.tex
Minor edits and cleanup through the introduction

--- 2018-07-17 articles/formalism/sections/introduction.tex
@@
 \section{Introduction}
-During recombination, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
+During recombination, the Cosmic Mircowave Background (CMB) undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
 The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature anisotropies \citep{1997NewA....2..323H}.
-The standard analysis technique involves translating the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, since the statistics of these coordinate independent scalar fields are predicted by theory.
+Standard CMB analysis techniques involve translating the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, since the statistics of these coordinate independent scalar fields are predicted by theory.
 
-The dominant contribution to the $E$-modes of polarization are sourced by primordial scalar perturbations, however these do not generate B-modes of polarization at first order.
-The $B$-modes of CMB polarization can be generated by various sources:
+The dominant contribution to the $E$-modes of polarization is sourced by primordial scalar perturbations, but these do not generate B-modes of polarization at first order.
+Various phenomena may generate $B$-modes in polarization measurements of the microwave sky:
 % Need citations for all...
@@
 \citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
-weak gravitational lensing of $E$-modes resulting from photon deflections induced by the potential of intervening large scale structure;
-foregrounds (especially Galactic synchrotron and dust emission)
+weak gravitational lensing of $E$-modes induced by the potential of intervening large scale structure;
+Milky Way foregrounds (especially Galactic synchrotron and dust emission)
 \citep{2016A&A...586A.133P};
@@
 The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
-Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations which will finally lead to important constraints on models of inflation \cite{?}.
-The measurement of $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \cite{?}.
+Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations and lead to important constraints on models of inflation.
+The measurement of lensing $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \citep{Abazajian2015, Kamionkowski2016,Abazajian2016,Hu2002c,Wehus2016}.
 
 The primary aim of the current CMB experiments is to make precise measurements of the CMB polarizations.
-While the E-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy and angular resolution.
-The detectors are swiftly approaching the desired sensitivities enabling us to in principle measure tiny $B$-mode signals ($r\gtrsim 0.001$) \cite{s4 science book, pico mission study}.
+While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy.
+The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A}.
 However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.
@@
 The formalism for converting the Stokes parameters to scalar quantities is well established \citep{1997PhRvD..55.7368K,1997PhRvD..55.1830Z}.
-The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally.
-However, in practice the $E$/$B$ modes are computed to some specified band limit and this makes them non-local functions of the polarization field.
-In other words, band limited $E$/$B$ modes evaluated at a point receive contributions from all over the sky.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally and filtered.
+In practice the $E$/$B$ modes are computed to some specified band limit, and the filtering and band limit make them non-local functions of the polarization field.
+In other words, $E$/$B$ modes evaluated at a point receive contributions from all over the sky.
 In this work we aim to gain real space insights into the non-locality of the $E/B$ fields compared to the Stokes parameters.
 With renewed focus on foreground contamination to the $B$-mode signal we aim to gain an intuition for $E/B$ mode patterns resulting from physical polarized structures in the galaxy.
-These real space insights may yield new ideas for minimizing foreground contamination which may not be possible using conventional approaches.
+These real space insights may yield new ideas for minimizing foreground contamination which may not be obvious using conventional approaches.
 
-Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}, however the approach adopted here is more rigorous and consequently there are updates to interpretation of the results and substantial differences in details.
-\comment{``more rigorous'' is a little harsh}
+{Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}.
+Here we dig deeper into the mathematical formulation of the real space operations on the curved sky.
+This has consequently led us to updates in interpretation and some substantial differences in detail.
+We describe our approach in this article and will discuss applications of the codes and analysis tools we have developed in a subsequent publication.}
 
@@
 We discuss the standard harmonic-space procedures for this operation.
-Finally, we introduce the matrix-vector notation which yields a more concise description of the harmonic space procedures.
+Finally, we introduce a matrix-vector notation which yields a more concise description of the harmonic space procedures.
 In \sec{sec:qu2eb} and \sec{sec:eb2qu} we derive and discuss the real space operators that transform $Q$/$U$ to $E$/$B$ and vice versa.
@@
 In \sec{sec:radial_locality} we study the locality of the real space operators and explore its band limit dependence.
-In \sec{sec:generalized_operators} we present a systematic way to generalize the real space operators by controling the non-locality while recovering the standard power spectra, and we discuss the connection to the spin raising and lower operators.
+In \sec{sec:generalized_operators} we present a systematic method of generalizing the real space operators by controlling the non-locality while recovering the standard power spectra.
+We discuss the connection to the standard spin raising and lower operators.
 In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of foreground filaments.
-In \sec{sec:discussion}, we conclude with a summary and discuss the prospects this new method of analyzing CMB polarization.
+In \sec{sec:discussion}, we conclude with a summary and discuss the prospects of this new method for analyzing CMB polarization maps.

### 2018-07-20 articles/formalism/sections/real_space_formalism.tex
Edits through sec 3.2/

@@
 \eeq
-Equivalently, the object $_{\pm 2}\bar{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin $\pm$2 field \cite{Zaldarriaga1997}.
+Equivalently, the object $_{\pm 2}{X}(\hat{n}) = Q(\hat{n}) \pm i U (\hat{n})$ transforms as ${}_{\pm 2}f' = e^{\mp 2i\psi} {}_{s}f$ and hence forms a spin $\pm$2 field \cite{Zaldarriaga1997}.
 
 The standard construction of $E$ and $B$ fields arise from the desire to have a coordinate independent description of the polarization.
-This follows from operations that raise (or lower) the spin of the field ${}_{\pm2}X$ to construct scalar fields.
-By understanding the transform properties of the Stokes parameters and those of the Euler angles on the sphere, we can already construct a heuristic argument for what these operations must look like in real space.
+This follows from operations that raise (or lower) the spin of the field ${}_{\pm2}{X}$ to construct scalar fields.
+By understanding the transformation properties of the Stokes parameters and those of the Euler angles on the sphere, we can already construct a heuristic argument for what these operations must look like in real space.
 We consider the contribution to a scalar field at $\hat n_e$ from the polarization field at $\hat n_q$.
@@
   \beqry
-  \bar{X} &= \bar T  \bar{P} \qquad; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} \,, \\
-  \tilde{X} &= \tilde T \tilde{S} \qquad; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
+  \bar{X} &= \bar T  \bar{P} ; &\qquad \bar{P} = \frac{1}{2} \bar T^{\dagger}  \bar{X} \,, \\
+  \tilde{X} &= \tilde T \tilde{S}; &\qquad \tilde{S} = \frac{1}{2}\tilde T^{\dagger} \tilde{X} \,.
   \eeqry
@@
 In \sec{sec:pol-primer} we described the conventional procedure of computing the scalar fields $E/B$ from the Stokes parameters $Q/U$. 
-
 In this section we derive the real space operators which can be used to directly evaluate the scalar fields $E$/$B$ on the sphere.
@@
 %
-where $(\alpha_{ij}, ~\beta_{ij}, \gamma_{ij})$ denote the Euler angles that specifically transform $(i \rightarrow j)$ so that the coordinate system at $\hat{n}_i$ aligns with the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation becomes more obvious when this equation is written in terms of the Wigner-D functions.}.
+where $(\alpha_{ij}, ~\beta_{ij}, \gamma_{ij})$ denote the Euler angles that specifically transform $(i \rightarrow j)$ so that the coordinate system at $\hat{n}_i$ aligns with the coordinate system at $\hat{n}_j$\footnote{The sense of the rotation becomes more obvious when this equation is written in terms of the Wigner-$D$ functions.}.
 Using this identity, the different parts of the real space operator $\bar{O}$  (from eq.~\ref{eq:qu2eb_ker_1}) are completely specified by the following complex function:
@@
 The real space operator which translates $E$/$B$ fields to Stokes parameters $Q$/$U$ can be derived using a similar procedure.
-Expressed in the matrix-vector notation, inverse operator is given by the following equation:
+Expressed in the matrix-vector notation, the inverse operator is given by the following equation:
 %
@@
 \beqry
-    {}_{+2}X(\hat{n}_q) &&=  \Delta \Omega \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}(\hat{n}_e) \hspace{0.8cm}\textrm{\emph{Radiation kernel}}\,,\label{eq:eb2qu_radiation} \\
-    {}_{+2}X(\hat{n}_q) &&= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{1.4cm}\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
+    {}_{+2}X(\hat{n}_q) &&=  \Delta \Omega \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}(\hat{n}_e) \hspace{0.8cm}\textrm{\emph{Radiation kernel}},\label{eq:eb2qu_radiation} \\
+    {}_{+2}X(\hat{n}_q) &&= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{1.4cm}\textrm{\emph {Convolution kernel}}, \label{eq:eb2qu_convolution}
 \eeqry

### 2018-07-20 articles/formalism/sections/real_space_formalism.tex
Minor edits through 3.4

@@
 This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit.
-Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.
+If we were to force the sum of the operators to be exactly an identity matrix, we would compromise the orthogonality property of $\bar{O}_E$ and $\bar{O}_B$, which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.
 %

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
Added some explanatory introduction paragraph to the notion of radiation and convolution kernels.

@@
 
-\paragraph{Radiation kernel.} The expression that we call the \textit{radiation kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
+\revisit{It turns out that the real space operations can \emph{also} be expressed in terms of the inverse rotation.
+These two expressions lead to two sets of kernels that are conceptually different, although they both ultimately yield the same mathematical result.
+The first set act like Green's functions, where, for example, a pixel of the Stokes parameters broadcasts or radiates an $E$/$B$ field.
+The second set act like a convolving beams, gathering Stokes contributions to the $E/B$ fields at a point.
+On the equator, or in the flat sky approximation, these kernels are identical and this distinction is immaterial.
+On the curved sky it matters, and the kernels are especially different near the poles.}
+
+\paragraph{Radiation kernel.} The expression above, based on the $\hat n_q \rightarrow \hat n_e$ rotation,  we call the \textit{radiation kernel}.
+It allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location.
 The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere.
@@
 $\mathcal{M}_G$ is invariant over the sphere because $E/B$ fields are coordinate independent.
-In the convolution kernels, $\mathcal{M}_G$ and $\mathcal{M}_B$ switch roles.
+In the convolution kernels, $\mathcal{M}_G$ and $\mathcal{M}_B$ are conjugated and switch roles.
 The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
@@
 %
-On the other hand, $\mathcal{M}^*_B$ is the Green's function of the operator that transforms E/B to coordinate-dependent Stokes parameters Q/U.
+On the other hand, $\mathcal{M}^*_B$ is the Green's function of the operator that transforms $E/B$ to coordinate-dependent Stokes parameters $Q/U$.
 The kernel $\mathcal{M}^*_B$ does not change with the central longitude, but varies as a function of galactic latitude.
@@
 %
-\revisit{It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
-This result can also be understood as the flat sky case where the radiation and convolution kernels are expected to be identical.}
+\revisit{Recall that the complex conjugates of these functions switch roles to form the convolution kernels.
+(For example, $\mathcal{M}_B$ is the convolution kernel for $Q/U \rightarrow E/B$.)}  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
 

### 2018-07-23 articles/formalism/sections/kernel_discussion.tex
Minor edits through 3.5

--- 2018-07-19 articles/formalism/sections/kernel_discussion.tex
@@
 The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}.
-The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.
+The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$.
+For clarity in the plot, their global maxima are normalized to unity.
 This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
@@
 
-These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar and related by this telescoping and scaling property:
-$${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \qquad \revisit{\mbox{(small angles)}},$$
+These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar over many oscillations, and are related by this telescoping and scaling property:
+\begin{equation}{}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}),\end{equation}
 where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
 This telescoping property encapsulates both the amplitude scaling and leftward shift of the radial kernels on increasing the maximum multipole.
-\revisit{Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified(supressed) by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed(expanded) by a factor $(\ell'_{\rm max}/\ell_{\rm max})$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$ when $\ell_{\rm max} > \ell'_{\rm max}$($\ell_{\rm max} < \ell'_{\rm max}$).}
+{Specifically, when $\ell_{\rm max} > \ell'_{\rm max}$, the global maxima of the kernel with maximum multipole $\ell_{\rm max}$ is amplified by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$, while the period of the oscillation is compressed by a factor $(\ell'_{\rm max}/\ell_{\rm max})$.
+The detailed accuracy of this approximation varies with the angular separation $\beta$ and the difference in the maximum multipoles ($\ell_{\rm max}$, $\ell'_{\rm max}$)  used in evaluating the two functions.}
 
@@
 However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
-We set the width of the smoothing window to $0.3\beta_0$, this results in the narrowing of the smoothing width as the band limit increases so as to keep the number of oscillations averaged over, remain roughly the same.
-This agrees with the hypothesis for the \revisit{flat sky case} \comment{is this flat sky or continuum case?}, for which e.g.
+We set the width of the smoothing window to $0.3\beta_0$, and this results in the narrowing of the smoothing width as the band limit increases, so as to keep the number of oscillations averaged over roughly the same.
+This agrees with the hypothesis for the {flat sky and continuum case}, for which e.g.
 Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).

### 2018-07-23 articles/formalism/sections/generalizedeb.tex
Minor edits, section 4.

@@
 \beqry
-{\bar O}' &=& {{}_0\mathcal{Y}} \, \tilde T^{-1} \tilde{\mathcal{G}} {{}_2\mathcal{Y}^{\dagger}} \, \bar T \,,\\
-{\bar O}'^{-1}&=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde{\mathcal{G}}^{-1} \tilde T {{}_0\mathcal{Y}^{\dagger}}.
+{\bar O}' &=& {{}_0\mathcal{Y}} \, \tilde T^{-1} \tilde{\mathcal{G}} {{}_2\mathcal{Y}^{\ddag}} \, \bar T \,,\\
+{\bar O}'^{-1}&=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde{\mathcal{G}}^{-1} \tilde T {{}_0\mathcal{Y}^{\ddag}}.
 \eeqry
@@
 We require both the forward and inverse operators to be well defined.
-This constrains the choice of $\tilde{\mathcal{G}}$ to have a valid  inverse and is important to recover the standard CMB power spectra.
+This constrains the choice of $\tilde{\mathcal{G}}$ to have a valid  inverse, which is important when recovering the standard CMB power spectra.
 The radial parts of this generalized operator and it's inverse are given by the following expressions,
@@
 where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
-In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+In contrast to the radial function $G(\beta)$, a beam function when appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
 Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
@@
 In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
- \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, a radial function without oscillations and an exponential cutoff.
+ \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel modified by a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, and a radial function without oscillations and an exponential cutoff.
 Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
@@
 which are merely filtered versions of the standard $E/B$ modes maps.
-The filter function is simply $g_{\ell}$, easily obtained from the modified radial function $G(\beta)$ and it can be simply interpreted as the harmonic coefficients of some azimuthally symmetric beam.
-The power spectra of the modified scalar fields $E'$ and $B'$ are related to the spectra of the standard $E$ and $B$ fields via the following relation,
+The filter function is simply $g_{\ell}$, which is easily obtained from the modified radial function $G(\beta)$.
+It can be simply interpreted as the set of harmonic coefficients for some azimuthally symmetric beam.
+The power spectra of the modified scalar fields $E'$ and $B'$ are thus related to the spectra of the standard $E$ and $B$ fields via the following relation,
  %

### 2018-07-23 articles/formalism/sections/kernel_paintbrush.tex
Minor edits in sec 5

@@
 Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-constant radius of curvature.
-The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.
+The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament (right panel of  \fig{fig:polfilaments}).
 The filament is highlighted by positive $E>0$.
@@
 A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claims no $B$-mode signal above the noise.
-We predict that a B-mode signal from filaments should be present, since they have a finite length of a few degrees.
-Detecting B-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
+We predict that a $B$-mode signal from filaments should be present, since they have a finite length of a few degrees.
+Detecting $B$-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
 While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.

### 2018-07-23 articles/formalism/sections/discussion.tex
Edits to discussion.  Added reference to febecop.  Moved note about real-space implemented in that foreground paper to a footnote in the formalism section.

@@
 \section{Discussion}\label{sec:discussion}
-In this work, we presented a first derivation of the real space operators on the sphere that transforms the Stokes vector to into a vector of scalars and vice versa.
-We also presented real space operators that directly decompose the full Stokes vector \vp{} into vector \vp{E} and \vp{B} that correspond to the respective scalar modes.
-To facilitate these derivations we introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of (spin-2 fields) polarization maps on the sphere.
+In this work, we presented a first derivation of the real space operators on the sphere that transform the Stokes polarization vector to into a vector of scalars and vice versa.
+We also presented real space operators that directly decompose the full Stokes vector \vp{} into vectors \vp{E} and \vp{B} that correspond to the respective scalar modes.
+To facilitate these derivations we introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of  polarization maps (or any spin-2 fields) on the sphere.
 This real-space analysis method trivially generalizes to maps of arbitrary spin.
@@
 Only the radial part of the kernel depends on the band limit.
-The radial part of the operator kernel are roughly self-similar in the sense that the radial kernels evaluated with some band limit is related to another radial kernel evaluated with a different band limit by a simple rescaling of the function.
+The radial parts of the operator kernels are roughly self-similar in the sense that the radial kernels evaluated with some band limit are related to other radial kernels (evaluated with a different band limit) by an approximate rescaling of the function.
 We use this property to define a non-locality parameter $\beta_0$ as the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
@@
 It did not explicitly derive the radial part of the kernel, but argued on geometric grounds that it should fall with angular separation as $\beta^{-2}$.
-We find that this agrees with the average behavior of radial functions after averaging oscillations and some such averaging takes place due to pixelization of the signal.
+We find that this agrees with the average behavior of radial functions after averaging oscillations and note that some such averaging always takes place in practice due to pixelization of the signal.
 However, for precision reconstruction of $E/B$ on the sphere, the oscillations must be taken into account.
 
-Our careful study of the real space operators show that they can be expressed either as a Green's function or as a convolving beam function.
+Our careful study of the real space operators show that they can be expressed either as Green's functions or as convolving beam functions.
 The convolution interpretation is not a totally new concept.
 It guides the discussion in \cite{Zaldarriaga2001a} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
-However, the Green's function interpretation of the operators is a new one and is discussed here for the first time.
+However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time in detail on the sphere.
 These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
+The mathematical forms of the Green's function and convolution kernels swap roles (and are conjugated) when transforming back to $Q/U$ from $E/B$.
 
@@
 Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable over a compact domain, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
+\revisit{Alternatively, the spatially-varying convolution kernel could be applied a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.}
 
@@
 We demonstrate that filaments with finite length or changing radius of curvature result in $B$-mode patterns in addition to the $E$-mode pattern already expected.
-We therefore predict a characteristic $B$-mode pattern from filament sources that should be measurable in future polarization measurements.
+We therefore predict a characteristic $B$-mode pattern from filament sources that should be observable in future polarization measurements.

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
Edits to discussion.  Added reference to febecop.  Moved note about real-space implemented in that foreground paper to a footnote in the formalism section.

@@
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations:
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.\footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that implements the similar idea of real-space transformation of Stokes $Q/U$ parameters to their $E/B$ counterparts, but we treat it here in much more detail.}
+This procedure is explicitly worked out in the following set of equations:
 %

### 2018-07-23 articles/formalism/sections/generalizedeb.tex
Edits to figure captions.

@@
 The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arc-minutes respectively.
-The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( \frac{\beta-\beta_s}{\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
+The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( {(\beta-\beta_s)}{/\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
 The black dashed curve depicts the band limited reconstruction of the modified radial function.
-\textit{Top right:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.
-\textit{Bottom:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend.
-The dashed curves of the corresponding color depict the inverse of the harmonic functions.}
+\textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
+The dashed curves of the corresponding color depict the inverse of the harmonic functions.
+\textit{Bottom:}  The normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective beam applied to $E/B$.
+}
 \label{fig:example_gbeta}

### 2018-07-23 articles/formalism/sections/kernel_discussion.tex
Edits to figure captions.

@@
 These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$.
-The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
+The vertical dashed line marks the approximate Healpix pixel size of a $N_{\rm side}=8$, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
 \label{fig:beta_kernel}
@@
 
-\caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends.
-\fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, \fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively.
+\caption{This figures depicts the radial functions for the different kernels and varying band limit, set by fixed $\ell_{\rm min}=2$ and varied $\ell_{\rm max}$ as indicated.
+\fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ the kernel for $Q/U$ to $E/B$ and vice versa.
+\fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, the Stokes purification kernels.
 All the curves are normalized such that their maxima is set to unity.
@@
 The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.
-\fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg} depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ and has width $1.4\beta_0$.
+We show moving averages over oscillations in \fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg}.
+They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $1.4\beta_0$.
 These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}

### 2018-07-23 articles/formalism/sections/kernel_paintbrush.tex
Edits to figure captions.

@@
 The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
-Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.
-B-modes are only non-zero at the ends.
-Right panels: in a curved filament, the E-mode is again positive along the filament.
+Left panels: in a straight filament, the $E$-mode is positive along the filament and at the ends, but negative along the sides.
+The $B$-modes are only non-zero at the ends.
+Right panels: in a curved filament, the $E$-mode is again positive along the filament.
 Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.
-The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
+The $B$-modes are again non-zero at the ends, akin to the straight filament case, but also somewhat along the filament due to the changing radius of curvature.
 In all images, the longitude angle increases to the left (which is East in sky convention).

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
Edits to figure captions.

--- 2018-07-23 articles/formalism/sections/real_space_formalism.tex
@@
 \includegraphics[width=0.5\columnwidth]{euler.pdf}
-\caption{This figure depicts the Euler angles in the $z-y1-z2$ convention.
-The cartesian coordinates shown in dark solid green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark solid red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
-The blue coordinates at different locations are representative of the parallel transport along the geodesic connection between the two locations $\hat{n}_q$ and $\hat{n}_e$ on the sphere.}
+\caption{This figure depicts the Euler angles in the $z-y_1-z_2$ convention.
+The cartesian coordinate axes shown in dark solid green are those that lie in the tangent plane at location $\hat{n}_q = (\theta_q, \phi_q)$ while those shown in dark solid red are the ones that lie in the tangent plane at location $\hat{n}_e = (\theta_e, \phi_e)$.
+The blue axes represent the parallel transport along the geodesic connection between the two locations $\hat{n}_q$ and $\hat{n}_e$ on the sphere.}
 \label{fig:euler_angles}
@@
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations:
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.\footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that implements the similar idea of real-space transformation of Stokes $Q/U$ parameters to their $E/B$ counterparts in real space, but we treat it here in much more detail.}
+This procedure is explicitly worked out in the following set of equations:
 %
@@
 \caption{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle(sphere), representative of the coordinate dependence of the Stokes parameters.
-The two sets of dotted lines drawn at representative points denote great circles, one which passes through the central point labelled `e' and the other chosen such that the two have locally orthogonal tangent vectors $(\hat{r},\hat{\phi})$.
+The two sets of dotted lines drawn at representative points denote great circles, one which passes through the central point labelled `$e$' and the other chosen such that the two have locally orthogonal tangent vectors $(\hat{r},\hat{\phi})$.
 The angle $\alpha_{qe}$ defines a rotation operator that aligns the local $\hat{x}$ with $\hat{r}$.
-\textit{Convolution kernel:} The resultant scalar field at `$e$' can be evaluated by summing over the contribution from all the Stokes parameters on the red circle.
-This convolution is performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.
-\textit{Radiation kernel:} It is also possible to compute the contribution from the Stokes parameter at `$q$' to all the point on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.}
+\textit{Radiation kernel:} We can compute the contribution from the Stokes parameter at `$q$' to all the points on the blue circle and this is a function of the Euler angle $\alpha_{qe}$.
+\textit{Convolution kernel:} The resultant scalar field at `$e$' can also be evaluated by summing over the contribution from all the Stokes parameters on the red circle.
+This convolution is performed with kernels which are defined in term of the Euler angle $\gamma_{eq}$.}
 \label{fig:planar_euler_angles}

### 2018-07-23 articles/formalism/sections/discussion.tex
clean up and minor edits

@@
 Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable over a compact domain, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
-\revisit{Alternatively, the spatially-varying convolution kernel could be applied a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.}
+Alternatively, the spatially-varying convolution kernel could be applied a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.
 
@@
   The method would be similar to pixel-based strategies to deconvolve an instrument beam during map making \citep[e.g.][]{2010ApJS..187..212C}.
-However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.
+Such a strategy for map making would result in the pointing matrix in being much less sparse, hence making a practical implementation significantly challenging.
+Using the compact radial kernels might help with restoring some of the sparseness of the pointing matrix and this requires a more careful feasibility study.
+  %However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.
 

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
clean up and minor edits

@@
 
-\revisit{It turns out that the real space operations can \emph{also} be expressed in terms of the inverse rotation.
+It turns out that the real space operations can \emph{also} be expressed in terms of the inverse rotation.
 These two expressions lead to two sets of kernels that are conceptually different, although they both ultimately yield the same mathematical result.
@@
 On the equator, or in the flat sky approximation, these kernels are identical and this distinction is immaterial.
-On the curved sky it matters, and the kernels are especially different near the poles.}
+On the curved sky it matters, and the kernels are especially different near the poles.
 
@@
 %
-\revisit{Recall that the complex conjugates of these functions switch roles to form the convolution kernels.
-(For example, $\mathcal{M}_B$ is the convolution kernel for $Q/U \rightarrow E/B$.)}  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+Recall that the complex conjugates of these functions switch roles to form the convolution kernels (For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.).
+It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
 The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.

### 2018-07-23 articles/formalism/sections/discussion.tex
minor edit to discussion on map making

@@
 Such a strategy for map making would result in the pointing matrix in being much less sparse, hence making a practical implementation significantly challenging.
-Using the compact radial kernels might help with restoring some of the sparseness of the pointing matrix and this requires a more careful feasibility study.
+Using the compact radial kernels might help with restoring some of the sparseness of the pointing matrix, however a real world implementation of this method requires a more careful feasibility study.
   %However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
Fix small typo in 3.3.

@@
 %
-Recall that the complex conjugates of these functions switch roles to form the convolution kernels (For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.).
-It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+Recall that the complex conjugates of these functions switch roles to form the convolution kernels.
+(For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
 The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.

### 2018-07-26 articles/formalism/sections/generalizedeb.tex
corrected type, added text to heuristic argument, changed to discrete Kronecker delta and revised discussion on band limited spin raising lowering operators

@@
 \beq
-\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,.
+\bar{\eth}^2_{\textrm BL} \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,,
 \eeq
 %
-The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
+\revisit{where $\bar{\eth}^2_{\textrm BL}$ denotes the band limited spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
+In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.}
+%The operator $\bar{\eth}^2_{\textrm BL}$ is composed of derivative operations and hence has an implicit positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
 The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.

### 2018-07-26 articles/formalism/sections/real_space_formalism.tex
corrected type, added text to heuristic argument, changed to discrete Kronecker delta and revised discussion on band limited spin raising lowering operators

@@
 
-\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_q$ by $-\gamma$.
+\fig{fig:euler_angles} shows that the transformation of the local coordinate system between the two positions can be described by a counter-clockwise rotation around the local $\hat n_q$ (unit radial vector at $(\theta_q,\phi_q)$ pointing outward) by angle $\alpha$, parallel transport by angle $\beta$ along the shorter geodesic and a counter-clockwise rotation around $\hat n_e$ by $-\gamma$.
 This corresponds to a rotation by Euler angles $(\alpha,\beta,-\gamma)$ in the $z-y_1-z_2$ convention.\footnote{The Euler angles in the more standard $z-y-z$ convention are related to those in the $z-y_1-z_2$ convection by the following rule: $(\alpha,\beta,\gamma)_{z-y-z} =(\gamma,\beta,\alpha)_{z-y_1-z_2}$ \cite{varshalovich}.}
@@
 Any such function $f$ will let us construct $E/B$-like scalar fields.
-Below we derive the particular one that gives rise to our familiar $E/B$ modes.
+\revisit{Finally the total $(E+iB)$ field results from summing over the contributions from all the Stokes charges ${}_{+2}X(\hat{n}_q)$ across the sphere.}  Below we derive the particular one that gives rise to our familiar $E/B$ modes.
 
@@
 \beq
-\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega}\\ U=0 \emat ;\qquad
-\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega} \emat.
+\bmat E= +\textrm{Re}(\mathcal{M}_G) \\ B =+\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\frac{\delta_{\hat{n},\hat{n}_q}}{\Delta \Omega}\\ U=0 \emat ;\qquad
+\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\frac{\delta_{\hat{n},\hat{n}_q}}{\Delta \Omega} \emat.
 \eeq
@@
 \beq
-\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega}\\ B=0 \emat;\qquad
-\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = +\textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega} \emat\,.
+\bmat Q= +\textrm{Re}(\mathcal{M}^*_B) \\ U = +\textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\frac{\delta_{\hat{n},\hat{n}_e}}{\Delta \Omega}\\ B=0 \emat;\qquad
+\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = +\textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\frac{\delta_{\hat{n},\hat{n}_e}}{\Delta \Omega} \emat\,.
 \eeq

### 2018-07-26 articles/formalism/sections/discussion.tex
added reference to The Annulus-Filtered E and B Modes in CMBR Polarization

@@
 The convolution interpretation is not a totally new concept.
-It guides the discussion in \cite{Zaldarriaga2001a} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
-However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time in detail on the sphere.
+\revisit{It guides the discussion in \cite{Zaldarriaga2001a,Chiueh2002} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.}  However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time in detail on the sphere.
 These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.

### 2018-07-26 articles/formalism/sections/generalizedeb.tex
added reference to The Annulus-Filtered E and B Modes in CMBR Polarization

@@
 %
-\revisit{where $\bar{\eth}^2_{\textrm BL}$ denotes the band limited spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
+\revisit{where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
 In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.}

### 2018-07-30 articles/formalism/sections/real_space_formalism.tex
Minor reordering for flow

@@
 \eeq
-for some real function $f$.
-Note that when the two locations coincide ($\beta_{qe}=0$) then  $\alpha_{qe}=0,2\pi,4\pi,\dots$, implying $E + iB \propto Q+iU$.
+for some real function $f$. \revisit{The total $(E+iB)$ field results from summing over all  contributions  from Stokes parameters ${}_{+2}X(\hat{n}_q)$ across the sphere.}
+
+Geometry places immediate constraints on function $f$.
+When the two locations coincide ($\beta_{qe}=0$) then  $\alpha_{qe}=0,2\pi,4\pi,\dots$, implying $E + iB \propto Q+iU$.
 This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, hence we must have $f(\beta_{qe} = 0 ) = 0$.
 This immediately implies that the $E/B$ fields are necessarily defined non-locally.
-A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$ and therefore we also require that $f(\beta_{qe} = \pi ) = 0$.
-Any such function $f$ will let us construct $E/B$-like scalar fields.
-\revisit{Finally the total $(E+iB)$ field results from summing over the contributions from all the Stokes charges ${}_{+2}X(\hat{n}_q)$ across the sphere.}  Below we derive the particular one that gives rise to our familiar $E/B$ modes.
+A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$, and therefore we also require that $f(\beta_{qe} = \pi ) = 0$.
+Any such function with these constraints will let us construct $E/B$-like scalar fields.
+Below we derive the particular $f$ that gives rise to our familiar $E/B$ modes.
 
-Note that this type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
+This type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
 transforming spin-0 fields to spin-2).

### 2018-07-30 articles/formalism/sections/generalizedeb.tex
removed text change highlights and added acknowledgements

--- 2018-07-26 articles/formalism/sections/generalizedeb.tex
@@
 %
-\revisit{where $\bar{\eth}^2_{\textrm BL}$ denotes the band limited spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
-In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.}
-%The operator $\bar{\eth}^2_{\textrm BL}$ is composed of derivative operations and hence has an implicit positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.
+where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
+In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.
 The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.

### 2018-07-31 articles/formalism/sections/discussion.tex
removed text change highlights and added acknowledgements
Added some clarifications based on Mathieu comments.

--- 2018-07-23 articles/formalism/sections/discussion.tex
@@
 While the azimuthal part of the operators is primarily responsible for handling the spin decomposition, the radial weights determine the non-local dependence of the resulting fields on the original fields.
-Only the radial part of the kernel depends on the band limit.
+Only the radial part of each kernel depends on the band limit.
 The radial parts of the operator kernels are roughly self-similar in the sense that the radial kernels evaluated with some band limit are related to other radial kernels (evaluated with a different band limit) by an approximate rescaling of the function.
 We use this property to define a non-locality parameter $\beta_0$ as the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
-We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes Q/U to scalars E/B and vice versa (see \fig{fig:rad_ker_decay}).
+We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes $Q/U$ to scalars $E/B$ and vice versa (see \fig{fig:rad_ker_decay}).
 An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.
@@
 The convolution interpretation is not a totally new concept.
-It guides the discussion in \cite{Zaldarriaga2001a} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
+It guides the discussion in \cite{Zaldarriaga2001a,Chiueh2002} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
 However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time in detail on the sphere.
@@
 For instance, the real space operators can be defined such that the locality of their radial kernels is varied on different portions of the sky, dictated by say the foreground morphology, resulting in some modified scalar $E'/B'$ maps.
-While this idea seems interesting, the usefulness of this implementation will depend on whether the standard $E/B$ mode spectra are easily recoverable in this fashion.
+While this idea seems interesting, the usefulness of this idea will depend on whether the standard $E/B$ mode spectra are easily recoverable in this fashion.
 We will explore some of these possible analysis directions in the future papers of this series.

### 2018-07-31 articles/formalism/sections/generalizedeb.tex
Added some clarifications based on Mathieu comments.

@@
 %
-where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere.
+where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, that is relevant in the case of a discretely sampled spin-2 field on the sphere.
 In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.

### 2018-07-31 articles/formalism/sections/kernel_paintbrush.tex
Added some clarifications based on Mathieu comments.

@@
 Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-constant radius of curvature.
-The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament (right panel of  \fig{fig:polfilaments}).
+The same general description holds for a spiral-shaped filament, which can can be viewed as the distortion of the straight filament (right panel of  \fig{fig:polfilaments}).
 The filament is highlighted by positive $E>0$.
@@
 A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claims no $B$-mode signal above the noise.
-We predict that a $B$-mode signal from filaments should be present, since they have a finite length of a few degrees.
+We predict that a $B$-mode signal from the filaments should be present, since they have a finite length of a few degrees.
 Detecting $B$-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
removed text change highlights and added acknowledgements
Added some clarifications based on Mathieu comments.

@@
 \eeq
-for some real function $f$. \revisit{The total $(E+iB)$ field results from summing over all  contributions  from Stokes parameters ${}_{+2}X(\hat{n}_q)$ across the sphere.}
+for some real function $f$. The total $(E+iB)$ field results from summing over all  contributions  from Stokes parameters ${}_{+2}X(\hat{n}_q)$ across the sphere.
 
@@
 where $\Delta \Omega$ denotes the pixel area and the last line is a simple scalar multiplication between complex numbers.
-The radiation kernel is then: $ \mathcal{M}_{G} =- \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB]= \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU] = [\delta(\hat{n}-\hat{n}_q)/{\Delta \Omega} + i0]$.
+The radiation kernel is then: $ \mathcal{M}_{G} =- \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB]= \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU] = [\delta(\hat{n},\hat{n}_q)/{\Delta \Omega} + i0]$.
 We display the kernel later in \fig{fig:vis_kernel}.
@@
 This many-to-one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.
-We display the kernel in \fig{fig:vis_kernel}.
+\revisit{We display the complex conjugate of this kernel in \fig{fig:vis_kernel}.
+(Later we see that the complex conjugate of this kernel is the radiation kernel for the inverse transform.)}
 %--------------------------------------------------------
@@
 where all the symbols have the same meaning as defined in \sec{sec:qu2eb}.
-Note that the conjugated forms of the radiation kernel (Green's function) and the convolution kernel (effective beam) for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
+\revisit{Note that $M_B$ (the convolution kernel before for $Q/U \rightarrow E/B$) is here the radiation kernel (as $M_B^*$) for $E/B \rightarrow Q/U$.
+Similarly $M_G$ (the radiation kernel before for $Q/U \rightarrow E/B$) is here the convolution kernel (as $M_G^*$) for $E/B \rightarrow Q/U$.}
+Thus the conjugated forms of the radiation kernel (Green's function) and the convolution kernel (effective beam) for the operator $\bar{O}$ reverse roles for the inverse operator $\bar{O}^{-1}$.
 %--------------------------------------------------------
@@
 $\mathcal{M}_G$ is invariant over the sphere because $E/B$ fields are coordinate independent.
-In the convolution kernels, $\mathcal{M}_G$ and $\mathcal{M}_B$ are conjugated and switch roles.
-The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
+\revisit{The \textit{convolution kernels} for these translations are respectively $\mathcal{M}_B$ and $\mathcal{M}_G^*$: the functions are conjugated and switch roles between forward and inverse translation.}  The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
 Each panel is approximately $16^{\circ} \times 16^{\circ}$ in size with grid lines every 2 degrees.
@@
 Recall that the complex conjugates of these functions switch roles to form the convolution kernels.
-(For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
-The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
+(For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+\revisit{This is visible in \fig{fig:vis_kernel} (although it displays $M_B^*$ not $M_B$).}  The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
 

### 2018-07-31 articles/formalism/sections/introduction.tex
cleaned up red text, minor text edits, added remazeilles2018 reference

@@
 While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy.
-The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A}.
+The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Remazeilles2018}.
 However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
cleaned up red text, minor text edits, added remazeilles2018 reference

@@
 This many-to-one mapping from the spin-2 Stokes field on the sphere to the complex spin-0 (scalar) field at a point on the sphere is graphically represented in \fig{fig:planar_euler_angles}.
-\revisit{We display the complex conjugate of this kernel in \fig{fig:vis_kernel}.
-(Later we see that the complex conjugate of this kernel is the radiation kernel for the inverse transform.)}
+We display the complex conjugate of this kernel in \fig{fig:vis_kernel}.
+(Later we see that the complex conjugate of this kernel is the radiation kernel for the inverse transform.)
 %--------------------------------------------------------
@@
 where all the symbols have the same meaning as defined in \sec{sec:qu2eb}.
-\revisit{Note that $M_B$ (the convolution kernel before for $Q/U \rightarrow E/B$) is here the radiation kernel (as $M_B^*$) for $E/B \rightarrow Q/U$.
-Similarly $M_G$ (the radiation kernel before for $Q/U \rightarrow E/B$) is here the convolution kernel (as $M_G^*$) for $E/B \rightarrow Q/U$.}
+Note that $M_B$ (the convolution kernel before for $Q/U \rightarrow E/B$) is here the radiation kernel (as $M_B^*$) for $E/B \rightarrow Q/U$.
+Similarly $M_G$ (the radiation kernel before for $Q/U \rightarrow E/B$) is here the convolution kernel (as $M_G^*$) for $E/B \rightarrow Q/U$.
 Thus the conjugated forms of the radiation kernel (Green's function) and the convolution kernel (effective beam) for the operator $\bar{O}$ reverse roles for the inverse operator $\bar{O}^{-1}$.
@@
 $\mathcal{M}_G$ is invariant over the sphere because $E/B$ fields are coordinate independent.
-\revisit{The \textit{convolution kernels} for these translations are respectively $\mathcal{M}_B$ and $\mathcal{M}_G^*$: the functions are conjugated and switch roles between forward and inverse translation.}  The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
+The \textit{convolution kernels} for the corresponding translations are $\mathcal{M}_B$ and $\mathcal{M}_G^*$ respectively: the functions are conjugated and switch roles between forward and inverse translation.
+The kernels have been evaluated with the band limit $\ell \in [2,192]$ and sampled at the HEALPix resolution parameter $N_{\rm side}=2048$.
 Each panel is approximately $16^{\circ} \times 16^{\circ}$ in size with grid lines every 2 degrees.
@@
 (For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
-\revisit{This is visible in \fig{fig:vis_kernel} (although it displays $M_B^*$ not $M_B$).}  The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
+This is visible in \fig{fig:vis_kernel} (although it displays $M_B^*$ not $M_B$).
+The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
 

### 2018-07-31 articles/formalism/article.tex
minor edits and typo corrections

@@
 For all these real space operators we show that the kernels split naturally into angular and radial parts and we show explicitly how the radial extent of these kernels depends on the targeted band-limit.
-We show that each kernel can be interpreted either as a complex convolving beam or as a Green's function when they are expressed in terms of the Euler angles  respectively for a forward or inverse rotation.
-We show that an arbitrary radial function can produce $E/B$-like maps, provides it vanishes at the origin and the  antipodal point.
+We show that the kernels can be interpreted either as a complex convolving beam or as a Green's function when they are expressed in terms of the forward or inverse rotation Euler angles.
+We show that an arbitrary radial function can produce $E/B$-like maps, provided it vanishes at the origin and the  antipodal point.
 These maps are simply filtered versions of the standard $E/B$ maps.
 We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function, which we show how to derive for any radial dependence.
-For this reason we can compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and could be employed in a massively-parallel scheme at high-resolution.
+For these reasons we can compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and could be employed in a massively-parallel scheme at high-resolution.
 We show that the spin raising  and lowering  operators $\eth^2$/$\bar{\eth}^2$ are special cases of these generalized radial functions, and present their band limited versions.

### 2018-07-31 articles/formalism/sections/discussion.tex
minor edits and typo corrections

@@
 It guides the discussion in \cite{Zaldarriaga2001a,Chiueh2002} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
-However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time in detail on the sphere.
+However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time.
 These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
@@
 Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable over a compact domain, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
-Alternatively, the spatially-varying convolution kernel could be applied a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.
+Alternatively, the spatially-varying convolution kernel could be applied as a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.
 
@@
 Using the compact radial kernels might help with restoring some of the sparseness of the pointing matrix, however a real world implementation of this method requires a more careful feasibility study.
-  %However, such a strategy for map making would force the pointing matrix to be much less sparse and it may not be practical.
 

### 2018-07-31 articles/formalism/sections/generalizedeb.tex
minor edits and typo corrections

@@
 Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
-Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = ({(\ell+2)!/(\ell-2)!})^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
+Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = [{(\ell+2)!/(\ell-2)!}]^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
 %

### 2018-07-31 articles/formalism/sections/introduction.tex
minor edits and typo corrections

@@
 \citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
-weak gravitational lensing of $E$-modes induced by the potential of intervening large scale structure;
+weak gravitational lensing of $E$-modes induced by the potentials of intervening large scale structures;
 Milky Way foregrounds (especially Galactic synchrotron and dust emission)
@@
 The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
-Hence a measurement of the large angular scale B-modes will yield information about the statistical properties of tensor perturbations and lead to important constraints on models of inflation.
+Hence a measurement of these large angular scale B-modes will yield information about the statistical properties of tensor perturbations that will eventually lead to important constraints on models of inflation.
 The measurement of lensing $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \citep{Abazajian2015, Kamionkowski2016,Abazajian2016,Hu2002c,Wehus2016}.
@@
 Here we dig deeper into the mathematical formulation of the real space operations on the curved sky.
-This has consequently led us to updates in interpretation and some substantial differences in detail.
+This has consequently led to updates in interpretation and some substantial differences in detail.
 We describe our approach in this article and will discuss applications of the codes and analysis tools we have developed in a subsequent publication.}

### 2018-07-31 articles/formalism/sections/kernel_paintbrush.tex
minor edits and typo corrections

@@
 For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}).
-The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.
+The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\mm_G$ in \fig{fig:vis_kernel}.
 
@@
 
-The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.
-This results in a non-zero $B$ pattern for the filament.
+The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament.  
  For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East as seen in \fig{fig:polfilaments}.
@@
 Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.
-The $B$-modes are again non-zero at the ends, akin to the straight filament case, but also somewhat along the filament due to the changing radius of curvature.
+The $B$-modes are again non-zero at the ends, akin to the straight filament case, but also along the filament due to the changing radius of curvature.
 In all images, the longitude angle increases to the left (which is East in sky convention).

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
minor edits and typo corrections

@@
 
-We consider the impact of local rotations  the Stokes parameters and on these Euler angles.
+We consider the impact of local rotations on the Stokes parameters and on these Euler angles.
 Rotating the cartesian coordinates in the tangent plane at location $\hat{n}_q$ by an angle $\psi$ about the local $\hat{z}_q$ axis, the Stokes parameters in the new coordinate system relate to those in the original coordinate system as:
@@
 \beq
-\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha'_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}} \,. \label{eq:invariant}
+\mathcal{R}_{\hat{z}_q}(\psi)[{}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}] = {}_{+2}X(\hat{n}_q) e^{-i2\alpha_{qe}} \,. \label{eq:invariant}
 \eeq
@@
 The same rotation $\mathcal{R}_{\hat{z}_q}(\psi)$ leaves the Euler angle $|\beta_{qe}|$ unaltered (it measures the angular distance between the points).
-Thus we further conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $n_q$ must have the generic form:
+Thus we further conclude that the contribution to $(E+iB)(\hat n_e)$ from the position $\hat{n}_q$ must have the generic form:
 \beq
@@
 This is a contradiction because $Q+iU$ does not transform as a spin-0 field under local rotations, hence we must have $f(\beta_{qe} = 0 ) = 0$.
-This immediately implies that the $E/B$ fields are necessarily defined non-locally.
+This implies that the $E/B$ fields are necessarily defined non-locally.
 A similar contradiction arises when the two locations are diametrically opposite, $\beta_{qe} = \pi$, and therefore we also require that $f(\beta_{qe} = \pi ) = 0$.
-Any such function with these constraints will let us construct $E/B$-like scalar fields.
+Any function that satisfies these constraints will let us construct $E/B$-like scalar fields.
 Below we derive the particular $f$ that gives rise to our familiar $E/B$ modes.
 
-This type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
+Note that this type of real-space construction can be generalized to transform a field of any spin to a field of any other spin, not just two and zero, and so we can use a similar construction (in the opposite direction) to transform $E/B$ maps back to the Stokes parameters (i.e.
 transforming spin-0 fields to spin-2).
@@
 \subsection{Matrix notation} \label{sec:mat_pol_intro}
-Our derivations of the real space operators are more transparent in a matrix-vector notation.\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}
+Our derivations of the real space operators are more transparent in a matrix-vector notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}.
 We introduce a matrix that encodes spin spherical harmonic basis vectors:
@@
 
-We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}
+We now define the different polarization data vectors and their representation in real and harmonic space as follows\footnote{We adopt a convention in which real space quantities are denoted by bar-ed variable while those in harmonic space are denoted by tilde-ed variables.}:
 %
@@
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators.\footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that implements the similar idea of real-space transformation of Stokes $Q/U$ parameters to their $E/B$ counterparts in real space, but we treat it here in much more detail.}
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators \footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that implements the similar idea of real-space transformation of Stokes $Q/U$ parameters to their $E/B$ counterparts in real space, but we treat it here in much more detail.}.
 This procedure is explicitly worked out in the following set of equations:
@@
 The first set act like Green's functions, where, for example, a pixel of the Stokes parameters broadcasts or radiates an $E$/$B$ field.
-The second set act like a convolving beams, gathering Stokes contributions to the $E/B$ fields at a point.
+The second set act like convolving beams, gathering Stokes contributions to the $E/B$ fields at a point.
 On the equator, or in the flat sky approximation, these kernels are identical and this distinction is immaterial.
-On the curved sky it matters, and the kernels are especially different near the poles.
+On the curved sky this distinction is important, and the kernels are especially different near the poles.
 
@@
 where $\Delta \Omega$ denotes the pixel area and the last line is a simple scalar multiplication between complex numbers.
-The radiation kernel is then: $ \mathcal{M}_{G} =- \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB]= \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU] = [\delta(\hat{n},\hat{n}_q)/{\Delta \Omega} + i0]$.
+The radiation kernel is then: $ \mathcal{M}_{G} =- \mm(\beta_{qe},\alpha_{qe})^*$ which can be thought of as the Green's function of the operator, since $[E +iB]= \mathcal{M}_{G}$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU] = [\delta_{\hat{n},\hat{n}_q}/{\Delta \Omega} + i0]$.
 We display the kernel later in \fig{fig:vis_kernel}.
@@
 This latitude-dependent shape carries the  coordinate dependence of the Stokes parameters.
-From \eq{eq:eb2qu_radiation}, we $\mathcal{M}^*_B$ arises from $\delta$-functions in $E/B$:
+From \eq{eq:eb2qu_radiation}, we can see the Q/U patterns that arise from $\delta$-functions in $E/B$:
 %
@@
 %
-Recall that the complex conjugates of these functions switch roles to form the convolution kernels.
-(For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
-This is visible in \fig{fig:vis_kernel} (although it displays $M_B^*$ not $M_B$).
+Recall that the complex conjugates of these functions switch roles to form the convolution kernels (e.g., $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator.
+This is visible in \fig{fig:vis_kernel} (although it displays $\mm_B^*$ and not $\mm_B$).
 The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
@@
 These functions can be further simplified using the identity of spin spherical harmonics given in \eq{eq:sum_spin_shf}.
-Specifically it can be shown that these functions reduce to the following mathematical forms:
+Specifically, it can be shown that these functions reduce to the following mathematical forms:
 %
@@
 
-The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity: $\lim_{\ell_{\rm max} \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$.
+The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity: $\lim_{\ell_{\rm max} \rightarrow \infty} \mathcal{I} = \delta_{\hat{n}_i, \hat{n}_j}$.
 For all practical purposes $\mathcal{I}$ acts like an identity operator as ascertained by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$.
@@
 The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}.
-These kernels show a two fold symmetry in the vicinity of the poles.
-Here the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
-Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}_G$.
+These kernels show a two fold symmetry in the vicinity of the poles, which can be understood as a consequence of the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$.
+Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}^*_G$.
 The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions.

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
relocated footnote

@@
 %
-The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators \footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that implements the similar idea of real-space transformation of Stokes $Q/U$ parameters to their $E/B$ counterparts in real space, but we treat it here in much more detail.}.
-This procedure is explicitly worked out in the following set of equations:
+The explicit form of the real space operator $\bar O$ can be derived by contracting over all the matrix operators. This procedure is explicitly worked out in the following set of equations:
 %

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
relocated footnote

@@
 It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization.
-In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar $E/B$ modes.
+In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar $E/B$ modes \footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that discussed a similar idea of real-space purification of Stokes $Q/U$ parameters to their $E/B$ counterparts, but we treat it here in much more detail.}.
 The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here and outline only the key points.

### 2018-07-31 articles/formalism/sections/kernel_paintbrush.tex
Added clarifying sentence on direction in plots.

@@
 The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament.  
- For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East as seen in \fig{fig:polfilaments}.
-The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
+ For a North--South filament, the $B$-mode pattern is positive on the northeast and southwest, and negative in the northwest and southeast.
+(\fig{fig:polfilaments} shows East to the left in sky map convention.)  The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
 In contrast to the kernel radial fuctions, which are more compact at higher band limit, the filament $B$-mode  pattern does not depend much on the band limit, provided it is sufficient to resolve the filament structure.
 A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
+The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments that are infinite and without ends can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
 
@@
 In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
-The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments (infinite and without ends) can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
 Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament, this information could potentially shed light on the internal dynamics of filaments.
@@
 \end{figure}
-%
-\indent The intuition from the real-space kernels holds also when we distort the shape of the filament.
+
+The intuition from the real-space kernels holds also when we distort the shape of the filament.
 If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.

### 2018-07-31 articles/formalism/sections/introduction.tex
Minor cleanups in introduction.

@@
 
-The dominant contribution to the $E$-modes of polarization is sourced by primordial scalar perturbations, but these do not generate B-modes of polarization at first order.
+The dominant contribution to the $E$-modes of polarization is sourced by primordial scalar perturbations, but these do not generate $B$-modes of polarization at first order.
 Various phenomena may generate $B$-modes in polarization measurements of the microwave sky:
@@
 
-The primary aim of the current CMB experiments is to make precise measurements of the CMB polarizations.
-While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review), the ongoing and future CMB experiments aim to measure the B-modes of CMB polarization with unprecedented accuracy.
+The primary aim of the current CMB experiments is to make precise measurements of CMB polarization.
+While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review),  ongoing and future CMB experiments aim to measure the $B$-modes of CMB polarization with unprecedented accuracy.
 The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Remazeilles2018}.
@@
 With renewed focus on foreground contamination to the $B$-mode signal we aim to gain an intuition for $E/B$ mode patterns resulting from physical polarized structures in the galaxy.
-These real space insights may yield new ideas for minimizing foreground contamination which may not be obvious using conventional approaches.
+These real space insights may yield new ideas for minimizing foreground contamination that are not obvious using conventional approaches.
 

### 2018-07-31 articles/formalism/sections/introduction.tex
updated reference for CORE

@@
 While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review),  ongoing and future CMB experiments aim to measure the $B$-modes of CMB polarization with unprecedented accuracy.
-The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Remazeilles2018}.
+The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Delabrouille2017}.
 However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.

### 2018-10-05 articles/formalism_jcap_submission/Original jcap submission/article/article.tex
added the latest files, with referee response and edited draft

--- 2018-07-31 articles/formalism/sections/real_space_formalism.tex
@@
+\documentclass[a4paper,11pt]{article}
+\pdfoutput=1
+\usepackage{jcappub}
+
+\usepackage[latin1]{inputenc}
+\usepackage{amsmath, amsfonts, amssymb, hyperref, graphicx, multirow, subfigure, bbold}
+\hypersetup{colorlinks=True,citecolor=blue}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\usepackage[normalem]{ulem}
+\usepackage{caption}
+\usepackage{array}
+\usepackage{aas_macros}
+
+\renewcommand{\thesubfigure}{(\roman{subfigure})}
+
+\newcommand{\na}{New Astronomy}
+%\newcommand{\aap}{Astronomy and Astrophysics}
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\eeq}{\end{equation}}
+\newcommand{\beqry}{\begin{eqnarray}}
+\newcommand{\eeqry}{\end{eqnarray}}
+\newcommand{\beqrys}{\begin{subequations}\begin{eqnarray}}
+\newcommand{\eeqrys}{\end{eqnarray}\end{subequations}}
+\newcommand{\fqu}{\begin{bmatrix} Q \\ U \end{bmatrix}}
+\newcommand{\xpm}{\begin{bmatrix} _{+2}X \\ _{-2}X \end{bmatrix}}
+\newcommand{\equ}{\begin{bmatrix} Q \\ U \end{bmatrix}_{E}}
+\newcommand{\bqu}{\begin{bmatrix} Q \\ U \end{bmatrix}_{B}}
+\newcommand{\eblm}{\begin{bmatrix} a^E \\ a^{B} \end{bmatrix}}
+\newcommand{\qutox}{\begin{bmatrix} \mathbb{1} & i\mathbb{1}  \\  \mathbb{1} & -i\mathbb{1}   \end{bmatrix}}
+\newcommand{\qutoxd}{\begin{bmatrix} \mathbb{1} & \mathbb{1}  \\  -i\mathbb{1} & i\mathbb{1}   \end{bmatrix}}
+\newcommand{\ymat}{\begin{bmatrix} _{+2}Y & 0  \\  0 & _{-2}Y  \end{bmatrix}}
+\newcommand{\ymatc}{\begin{bmatrix} _{+2}Y^* & 0  \\  0 & _{-2}Y^*  \end{bmatrix}}
+\newcommand{\yzmat}{\begin{bmatrix} _{0}Y & 0  \\  0 & _{0}Y  \end{bmatrix}}
+\newcommand{\yzmatc}{\begin{bmatrix} _{0}Y^* & 0  \\  0 & _{0}Y^*  \end{bmatrix}}
+\newcommand{\ope}{\hat{O}_{E}}
+\newcommand{\opb}{\hat{O}_{B}}
+\newcommand{\bmat}{\begin{bmatrix}}
+\newcommand{\emat}{\end{bmatrix}}
+\newcommand{\mdi}{\mathcal{D}/\mathcal{I}}
+\newcommand{\mm}{\mathcal{M}}
+\newcommand{\md}{\mathcal{D}}
+\newcommand{\mi}{\mathcal{I}}
+\def\vp#1{$\bar{P}_{#1}$ }
+\def\vs{$\bar{S}~$}
+\def\eq#1{{Eq.~(\ref{#1})}}
+\def\sec#1{{Sec.~\ref{#1}}}
+\def\fig#1{{Fig.~\ref{#1}}}
+\def\app#1{{Appendix~\ref{#1}}}
+\def\ymat#1{\begin{bmatrix} _{+2}Y_{#1} & 0  \\  0 & _{-2}Y_{#1}  \end{bmatrix}}
+\def\ymatc#1{\begin{bmatrix} _{+2}Y^{\dag}_{#1} & 0  \\  0 & _{-2}Y^{\dag}_{#1}  \end{bmatrix}}
+\def\yzmat#1{\begin{bmatrix} _{0}Y_{#1} & 0  \\  0 & _{0}Y_{#1}  \end{bmatrix}}
+\def\yzmatc#1{\begin{bmatrix} _{0}Y^*_{#1} & 0  \\  0 & _{0}Y^*_{#1}  \end{bmatrix}}
+
+% Text comments and highlights
+\newcommand{\st}{\sout}
+\newcommand{\revisit}{\textcolor{red}}
+\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
+\newcommand{\rfedit}{\textcolor{magenta}  }
+\newcommand{\soothe}{\textcolor{BlueViolet}  }
+
+%\graphicspath{ {"./"//} }
+
+\begin{document}
+\title{Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments}
+
+\author[a,b]{Aditya Rotti}
+\author[a]{and Kevin Huffenberger}
+\affiliation[a]{Department of Physics, Florida State University, Keen Physics Building, Tallahassee, Florida 32306, USA}
+\affiliation[b]{Jodrell Bank Center for Astrophysics, University of Manchester, Oxford Road, Manchester M13 9PL, UK}
+\emailAdd{adityarotti@gmail.com}
+\emailAdd{khuffenberger@fsu.edu}
+
+\abstract{
+  \noindent {We derive full-sky, real-space operators that convert between polarization Stokes $Q/U$ parameters and the coordinate-independent scalar $E$/$B$ modes that are widely used in Cosmic Microwave Background (CMB) and cosmic shear analysis.
+We also derive real space operators that decompose the measured Stokes parameters into those corresponding to $E$-modes and $B$-modes respectively, without ever evaluating the scalar fields themselves.
+We cast the standard CMB polarization analysis operators in a matrix-vector notation which elucidates these derivations.
+For all these real space operators we show that the kernels split naturally into angular and radial parts and we show explicitly how the radial extent of these kernels depends on the targeted band-limit.
+We show that the kernels can be interpreted either as a complex convolving beam or as a Green's function when they are expressed in terms of the forward or inverse rotation Euler angles.
+We show that an arbitrary radial function can produce $E/B$-like maps, provided it vanishes at the origin and the  antipodal point.
+These maps are simply filtered versions of the standard $E/B$ maps.
+We can recover the standard power spectrum of the polarized CMB sky by correcting the power spectra of these maps with a simple window function, which we show how to derive for any radial dependence.
+For these reasons we can compute $E/B$ maps in real space with a compactly-supported kernel, an approach that can guarantee the avoidance of known foreground regions and could be employed in a massively-parallel scheme at high-resolution.
+We show that the spin raising  and lowering  operators $\eth^2$/$\bar{\eth}^2$ are special cases of these generalized radial functions, and present their band limited versions.
+The spatial structure of the real space operators provides great intuition for the $E/B$ structure of polarized, filamentary galactic foregrounds.
+We predict a non-zero $B$-mode signature that is expected from polarized filaments in the sky.
+This paper is the first part in a series of papers that explore real-space computation of polarization modes and their applications.}
+}
+\maketitle
+\begingroup
+\let\clearpage\relax
+%---------------------------------------------------------------------------------------------------------
+\section{Introduction}
+During recombination, the Cosmic Mircowave Background (CMB) undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.
+The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature anisotropies \citep{1997NewA....2..323H}.
+Standard CMB analysis techniques involve translating the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, since the statistics of these coordinate independent scalar fields are predicted by theory.
+
+The dominant contribution to the $E$-modes of polarization is sourced by primordial scalar perturbations, but these do not generate $B$-modes of polarization at first order.
+Various phenomena may generate $B$-modes in polarization measurements of the microwave sky: primordial tensor perturbations (gravitational waves) \citep{1997PhRvD..56..596H,1997PhRvL..78.2054S}; weak gravitational lensing of $E$-modes induced by the potentials of intervening large scale structures;
+Milky Way foregrounds (especially Galactic synchrotron and dust emission)
+\citep{2016A&A...586A.133P}; uncorrected systematic problems in the data \citep{2003PhRvD..67d3004H,2008PhRvD..77h3003S}; and unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
+\citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.
+
+The pseudo-scalar $B$-modes particularly on large angular scales ($\sim 2$ degrees) are expected to have a significant contribution from primordial tensor perturbations generated during inflation.
+Hence a measurement of these large angular scale B-modes will yield information about the statistical properties of tensor perturbations that will eventually lead to important constraints on models of inflation.
+The measurement of lensing $B$-modes on small angular scales ($\sim$ few arcminute) will yield information on the clustering of matter across cosmic ages \citep{Abazajian2015, Kamionkowski2016,Abazajian2016,Hu2002c,Wehus2016}.
+
+The primary aim of the current CMB experiments is to make precise measurements of CMB polarization.
+While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review),  ongoing and future CMB experiments aim to measure the $B$-modes of CMB polarization with unprecedented accuracy.
+The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Delabrouille2017}.
+However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.
+Precise modelling and subtraction of this large foreground contribution poses a major challenge for a robust unravelling of the minuscule $B$-mode signal.
+
+The formalism for converting the Stokes parameters to scalar quantities is well established \citep{1997PhRvD..55.7368K,1997PhRvD..55.1830Z}.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally and filtered.
+In practice the $E$/$B$ modes are computed to some specified band limit, and the filtering and band limit make them non-local functions of the polarization field.
+In other words, $E$/$B$ modes evaluated at a point receive contributions from all over the sky.
+In this work we aim to gain real space insights into the non-locality of the $E/B$ fields compared to the Stokes parameters.
+With renewed focus on foreground contamination to the $B$-mode signal we aim to gain an intuition for $E/B$ mode patterns resulting from physical polarized structures in the galaxy.
+These real space insights may yield new ideas for minimizing foreground contamination that are not obvious using conventional approaches.
+
+{Some of the ideas presented in this work bear resemblance to those in Zaldarriaga (2001) \citep{Zaldarriaga2001a}.
+Here we dig deeper into the mathematical formulation of the real space operations on the curved sky.
+This has consequently led to updates in interpretation and some substantial differences in detail.
+We describe our approach in this article and will discuss applications of the codes and analysis tools we have developed in a subsequent publication.}
+
+This paper is organized in the following manner: In \sec{sec:pol-primer} we present a primer on the description of CMB polarization on the sphere, beginning with a heuristic argument that makes transparent the real space construction of $E$/$B$ modes.
+We discuss the standard harmonic-space procedures for this operation.
+Finally, we introduce a matrix-vector notation which yields a more concise description of the harmonic space procedures.
+In \sec{sec:qu2eb} and \sec{sec:eb2qu} we derive and discuss the real space operators that transform $Q$/$U$ to $E$/$B$ and vice versa.
+In \sec{sec:visualize_operator} we evaluate these real space operators and present visualizations of these functions.
+In \sec{sec:purify_stokes_qu} we derive a real space operator that decomposes the Stokes $Q$/$U$  parameters into components that correspond to $E$ and $B$ modes respectively and present its visualizations.
+In \sec{sec:radial_locality} we study the locality of the real space operators and explore its band limit dependence.
+In \sec{sec:generalized_operators} we present a systematic method of generalizing the real space operators by controlling the non-locality while recovering the standard power spectra.
+We discuss the connection to the standard spin raising and lower operators.
+In \sec{sec:pol_filaments} we discuss $E/B$ mode signatures of foreground filaments.
+In \sec{sec:discussion}, we conclude with a summary and discuss the prospects of this new method for analyzing CMB polarization maps.
+%---------------------------------------------------------------------------------------------------------
 \section{Polarization primer} \label{sec:pol-primer}
@@
 $b=90^\circ$ &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat90_lon45.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_rad_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_rad_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_con_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_con_lat90_lon45.pdf} \\
 $b=87^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat87_lon45.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_rad_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_rad_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_con_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_con_lat87_lon45.pdf} \\
 $b=80^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat80_lon30.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_rad_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_rad_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_con_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_con_lat80_lon30.pdf} \\
 $b=0^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_rad_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_rad_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_rker_con_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2eb_iker_con_lat0_lon90.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_rad_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_rad_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_rker_con_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2eb_iker_con_lat0_lon90.pdf} \\
 &
@@
 On the other hand, $\mathcal{M}^*_{B}$ is the Green's function (radiation kernel) that gives $_{+2}X$ for a delta function scalar input $E+iB$ at the center.
-The black circles denotes the position of the center around which the kernels have been evaluated while the black star marks the location of the North Pole.
+The black circles denotes the position of the center around which the kernels have been evaluated while the black cross marks the location of the North Pole.
 The four rows depict the kernels at different latitudes on the sphere.
@@
 Each panel is approximately $16^{\circ} \times 16^{\circ}$ in size with grid lines every 2 degrees.
-} \label{fig:vis_kernel}
+East is to the left, as in sky map convention.} \label{fig:vis_kernel}
 \end{figure}
@@
 $b=90^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat90_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat90_lon45.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_D_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_I_lat90_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_I_lat90_lon45.pdf} \\
 $b=87^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat87_lon45.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat87_lon45.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_D_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_I_lat87_lon45.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_I_lat87_lon45.pdf} \\
 $b=80^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat80_lon30.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat80_lon30.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_D_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_I_lat80_lon30.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_I_lat80_lon30.pdf} \\
 $b=0^\circ$&
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_D_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_D_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_rker_I_lat0_lon90.pdf} &
-\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{new_kernel/qu2ebqu_iker_I_lat0_lon90.pdf} \\
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_D_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_rker_I_lat0_lon90.pdf} &
+\hspace{\kernelfigspace}\includegraphics[width=\kernelfigwidth]{qu2ebqu_iker_I_lat0_lon90.pdf} \\
 &
@@
 As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.
+%---------------------------------------------------------------------------------------------------------
+%\include{kernel_discussion}
+\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
+%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
+\caption{The figure depicts the radial part of the convolution kernels.
+These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$.
+The vertical dashed line marks the approximate Healpix pixel size of a $N_{\rm side}=8$, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
+\label{fig:beta_kernel}
+\end{figure}
+%
+Above, we have explored in detail the  azimuthal dependence of the real space kernels.
+Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies.
+For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$.
+We choose such a low band limit to highlight some key features of their radial profile.
+%
+\begin{figure}[t]
+\subfigure[\label{fig:fbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}}\hfill
+\subfigure[\label{fig:dfbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}\hfill
+\subfigure[\label{fig:ifbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}\hfill
+\centering
+\subfigure[\label{fig:fbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
+\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax_zaldariagga_scaling.pdf}}
+
+\caption{This figures depicts the radial functions for the different kernels and varying band limit, set by fixed $\ell_{\rm min}=2$ and varied $\ell_{\rm max}$ as indicated.
+\fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ the kernel for $Q/U$ to $E/B$ and vice versa.
+\fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, the Stokes purification kernels.
+All the curves are normalized such that their maxima is set to unity.
+The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum.
+The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions.
+The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.
+We show moving averages over oscillations in \fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg}.
+They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $1.4\beta_0$.
+These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}
+\label{fig:rad_ker_decay}
+\end{figure}
+%
+
+The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
+It has an oscillatory nature at intermediate angular separations and vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$ (this is critical to ensure that the derived fields have the necessary spin properties), since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
+
+The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to $E$ and $B$ modes  are also  necessarily non-local.
+The function ${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.
+It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
+${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
+
+\paragraph{Band limit dependence.} 
+To quantify the non-locality of the real space operators, we study the radial extent of the respective radial kernels and their dependence on the maximum multipole accessible.
+We evaluate the radial functions for different values of $\ell_{\rm max}$, while keeping the lowest multipole fixed at $\ell_{\rm min}=2$.
+
+The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}.
+The amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$.
+For clarity in the plot, their global maxima are normalized to unity.
+This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.
+At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$.
+As the band limit changes, the small angle portion of the radial functions have a similar shape.
+
+These finding are neatly summarized in the observation that the radial functions with different maximum multipoles are approximately self-similar over many oscillations, and are related by this telescoping and scaling property:
+\begin{equation}{}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}),\end{equation}
+where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions.
+This telescoping property encapsulates both the amplitude scaling and leftward shift of the radial kernels on increasing the maximum multipole.
+{Specifically, when $\ell_{\rm max} > \ell'_{\rm max}$, the global maxima of the kernel with maximum multipole $\ell_{\rm max}$ is amplified by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$, while the period of the oscillation is compressed by a factor $(\ell'_{\rm max}/\ell_{\rm max})$.
+The detailed accuracy of this approximation varies with the angular separation $\beta$ and the difference in the maximum multipoles ($\ell_{\rm max}$, $\ell'_{\rm max}$)  used in evaluating the two functions.}
+
+To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.
+We define a non-locality parameter $\beta_{0}$ as the angular distance beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transitions to being consistently below 1\% of its maximum.
+The empirical relation:
+\beq
+\beta_0= {\rm min}\left(180^\circ,180^\circ \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
+\eeq
+with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as depicted by the short dashed vertical black lines in \fig{fig:fbeta}.
+Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.
+
+The radial function ${}_\mm f(\beta)$ is oscillatory, regardless of the maximum $\ell_{\rm max}$.
+The envelope of the oscillation decays with angular separation at intermediate $\beta$ but increases as $\beta \rightarrow \pi$.
+We find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.6}$ at intermediate $\beta$.
+However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
+We set the width of the smoothing window to $0.3\beta_0$, and this results in the narrowing of the smoothing width as the band limit increases, so as to keep the number of oscillations averaged over roughly the same.
+This agrees with the hypothesis for the {flat sky and continuum case}, for which e.g.
+Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).
+In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.
+Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
+Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
+In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.
+
+Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function partly falls outside the domain and this is in part responsible for the scaling deviating from the power law, but it is also important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.
+%---------------------------------------------------------------------------------------------------------
+%\include{generalizedeb}
+\section{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
+With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
+The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.
+The radial parts of the standard operators are determined by the sum over spherical harmonics and varies as a function of the band limit.
+It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
+
+We can systematically generalize the real space operator by introducing the following harmonic space filter function:
+%
+\beq
+\tilde{\mathcal{G}} = {\begin{bmatrix} g_{\ell}^E & 0  \\  0 & g_{\ell}^B \end{bmatrix}} \,,
+\eeq
+%
+where the functions $g_{\ell}^E$ and $g_{\ell}^B$ represent the harmonic representation of the modified radial functions and can in the most general case be chosen to be different for $E$ and $B$ modes.
+To simplify discussions, we proceed by setting $g_{\ell}^E = g_{\ell}^B= g_{\ell}$.
+Given this harmonic function $g_{\ell}$, we can define the real space operator $\bar{O}'$ which translates Stokes $Q/U$ to $E/B$-like scalars (and the inverse operator $\bar{O}'^{-1}$) in the following manner,
+% 
+\begin{subequations} \label{eq:gen_qu2eb}
+\beqry
+{\bar O}' &=& {{}_0\mathcal{Y}} \, \tilde T^{-1} \tilde{\mathcal{G}} {{}_2\mathcal{Y}^{\ddag}} \, \bar T \,,\\
+{\bar O}'^{-1}&=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde{\mathcal{G}}^{-1} \tilde T {{}_0\mathcal{Y}^{\ddag}}.
+\eeqry
+\end{subequations}
+%
+The primed notation distinguishes these generalized operators from the default operators defined in \sec{sec:qu2eb} and \sec{sec:eb2qu}.
+We require both the forward and inverse operators to be well defined.
+This constrains the choice of $\tilde{\mathcal{G}}$ to have a valid  inverse, which is important when recovering the standard CMB power spectra.
+The radial parts of this generalized operator and it's inverse are given by the following expressions,
+%
+\begin{subequations}\label{eq:generalized_radial_kernel}
+\beqry 
+G_{QU \rightarrow EB}(\beta) &=& G(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \, \label{eq:mod_rad_forward} \,, \\
+G_{EB \rightarrow QU}(\beta) &=& G^{-1}(\beta) = \sum _{\ell=2} ^{\ell_{\rm max}} g_{\ell}^{-1}\frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell + 2)!}} P_{\ell}^2(\cos{\beta}) \,.
+\label{eq:mod_rad_inverse}
+\eeqry
+\end{subequations}
+%
+The default radial function is just a special case resulting from the choice $\tilde{\mathcal{G}}=\mathbb{1}$ ($g_{\ell}=1$), in which case $\tilde{\mathcal{G}}^{-1}=\tilde{\mathcal{G}}$ and therefore $G^{-1}(\beta) = G(\beta)={{}_{\mm}f}$.
+%
+\begin{figure}[!t] 
+\centering
+\subfigure[\label{fig:gl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
+\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
+\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
+\caption{\textit{Top left:} The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}, multiplied by an apodized step function $\theta(3 \beta_0)$.
+The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arc-minutes respectively.
+The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( {(\beta-\beta_s)}{/\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
+The black dashed curve depicts the band limited reconstruction of the modified radial function.
+\textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
+The dashed curves of the corresponding color depict the inverse of the harmonic functions.
+\textit{Bottom:}  The normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective beam applied to $E/B$.
+}
+\label{fig:example_gbeta}
+\end{figure}
+%
+
+While defining these generalized operators, it is more natural to choose the real space function $G(\beta)$ rather than the harmonic space $g_l$, bearing in mind the constraint that $G(\beta=0)=G(\beta=\pi)=0$.
+Employing the orthogonality property of associated Legendre polynomials it can be shown that the harmonic function $g_{\ell}$ is given by the expression,
+%
+\beq
+g_{\ell} = 2 \pi \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} \int _{0}^{\pi} G(\beta) P_{\ell}^{2}(\cos{\beta}) d\cos{\beta} \,. \label{eq:gb2bl}
+\eeq
+%
+An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
+%
+\beq
+b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
+\eeq
+%
+where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
+In contrast to the radial function $G(\beta)$, a beam function when appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$.
+Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
+
+% Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
+In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
+ \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel modified by a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, and a radial function without oscillations and an exponential cutoff.
+Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
+The exponential cutoff (red curve) by construction has a very small non-locality (parameterized by $\beta_0$).
+
+\fig{fig:glbl} depicts the harmonic description $g_{\ell}$ for these respective radial kernels and beams.
+Finally, the beam that the modified radial kernels effectively apply to the $E/B$ fields are shown in \fig{fig:gl_bbeta}.
+Note that the beam function corresponding to the default radial kernel ($g_{\ell}=1$) is merely a band limited representation of a delta-function beam.
+
+The generalized convolution kernels defined in the previous section, when operated on the Stokes vector returns some scalar $E'$ and $B'$ mode maps,
+%
+\beq
+\bar{S}' = \bar{O}' \bar{P}
+\eeq
+%
+which are merely filtered versions of the standard $E/B$ modes maps.
+The filter function is simply $g_{\ell}$, which is easily obtained from the modified radial function $G(\beta)$.
+It can be simply interpreted as the set of harmonic coefficients for some azimuthally symmetric beam.
+The power spectra of the modified scalar fields $E'$ and $B'$ are thus related to the spectra of the standard $E$ and $B$ fields via the following relation,
+ %
+ \begin{subequations}
+ \beqry
+C_{\ell}^{EE,BB,EB} &= &C_{\ell}^{E'E',B'B',E'B'} /   g_{\ell}^2\,,\\
+C_{\ell}^{TE,TB}  &=&  C_{\ell}^{TE',TB'} / g_{\ell}\,,
+ \eeqry
+ \end{subequations}
+ %
+ where $C_{\ell}$ denotes the angular power spectra and $T$ refers to the temperature anisotropy map.
+Therefore the standard CMB spectra can always be recovered as long as the $1/g_{\ell}$ and $1/g_{\ell}^2$ are well behaved functions, which can be ensured by making a suitable choice for the modified radial function $G(\beta)$.
+%--------------------------------------------------------
+
+%--------------------------------------------------------
+\paragraph{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators.}
+Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}.
+Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = [{(\ell+2)!/(\ell-2)!}]^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
+%
+\beq 
+[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.
+\label{eq:bl_ebdef_lower}
+\eeq
+%
+Comparing to \eq{eq:ebdef_lower} makes apparent the following mapping:
+%
+\beq
+\bar{\eth}^2_{\textrm BL} \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,,
+\eeq
+%
+where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, that is relevant in the case of a discretely sampled spin-2 field on the sphere.
+In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.
+The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.
+%---------------------------------------------------------------------------------------------------------
+%\input{kernel_paintbrush.tex}
+\section{Understanding polarization signatures of magnetized filaments}
+\label{sec:pol_filaments}
+
+The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.
+For example, a simple model for a magnetized filament has the magnetic field threaded along a linear gas over-density.
+Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and perpendicular to the filament overall).
+For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}).
+The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\mm_G$ in \fig{fig:vis_kernel}.
+
+The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.
+The positive components for the $E$ part of the Green's function align and reinforce along the filament, consequently the filament is highlighted as a segment with $E>0$.
+Since the over-density will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.
+The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.
+
+The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament.  
+ For a North--South filament, the $B$-mode pattern is positive on the northeast and southwest, and negative in the northwest and southeast.
+(\fig{fig:polfilaments} shows East to the left in sky map convention.)  The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
+In contrast to the kernel radial fuctions, which are more compact at higher band limit, the filament $B$-mode  pattern does not depend much on the band limit, provided it is sufficient to resolve the filament structure.
+A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
+The work in \cite{Zaldarriaga2001a} correctly argued that linear filaments that are infinite and without ends can only produce $E$-power, but we find that for realistic filaments, the ends produce $B$-mode power with a clear signature.
+
+The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.
+However, unlike a circular ring, this filament is not a configuration with a definite parity.
+Since the scalar description of polarization is coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
+For example, a filament inclined at $45^\circ$ will have a similarly inclined $E/B$ pattern, but different reflection symmetries.
+
+ Changing the polarization direction within the filament changes the $E/B$ patterns.
+A $90^\circ$ rotation of the polarization with respect to the filament changes the sign of both $E$ and $B$.
+In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
+Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament, this information could potentially shed light on the internal dynamics of filaments.
+% 
+\begin{figure}[t]
+\includegraphics[width=0.5\columnwidth]{line.pdf}
+\includegraphics[width=0.5\columnwidth]{spiral.pdf}
+\includegraphics[width=1.0\columnwidth]{colorbar.pdf}
+\caption{ The polarization signals of toy filament structures.
+In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.
+The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
+Left panels: in a straight filament, the $E$-mode is positive along the filament and at the ends, but negative along the sides.
+The $B$-modes are only non-zero at the ends.
+Right panels: in a curved filament, the $E$-mode is again positive along the filament.
+Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.
+The $B$-modes are again non-zero at the ends, akin to the straight filament case, but also along the filament due to the changing radius of curvature.
+In all images, the longitude angle increases to the left (which is East in sky convention).
+All plot are on a common, arbitrary color scale.}
+\label{fig:polfilaments}
+\end{figure}
+
+The intuition from the real-space kernels holds also when we distort the shape of the filament.
+If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.
+Here it is important to note that this cancellation will not happen for an ellipse or any loop of non-constant radius of curvature.
+The same general description holds for a spiral-shaped filament, which can can be viewed as the distortion of the straight filament (right panel of  \fig{fig:polfilaments}).
+The filament is highlighted by positive $E>0$.
+The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.
+While the $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations, note that it is non-vanishing in the intermediate regions along the filament due to the varying radius of curvature of the spiral.
+A spiral turning with the other handedness will have a $B$-pattern with the opposite sign.
+
+A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claims no $B$-mode signal above the noise.
+We predict that a $B$-mode signal from the filaments should be present, since they have a finite length of a few degrees.
+Detecting $B$-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
+While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
+%---------------------------------------------------------------------------------------------------------
+%\include{discussion}
+\section{Discussion}\label{sec:discussion}
+In this work, we presented a first derivation of the real space operators on the sphere that transform the Stokes polarization vector to into a vector of scalars and vice versa.
+We also presented real space operators that directly decompose the full Stokes vector \vp{} into vectors \vp{E} and \vp{B} that correspond to the respective scalar modes.
+To facilitate these derivations we introduced a vector-matrix notation which allows for concise book keeping of all the standard operations involved in the analysis of  polarization maps (or any spin-2 fields) on the sphere.
+This real-space analysis method trivially generalizes to maps of arbitrary spin.
+
+These real space operators offer a spatially intuitive way of understanding the different decompositions of the Stokes vector on the sphere.
+We explicitly  demonstrated that all the real space operators are separable into azimuthal and radial parts.
+While the azimuthal part of the operators is primarily responsible for handling the spin decomposition, the radial weights determine the non-local dependence of the resulting fields on the original fields.
+Only the radial part of each kernel depends on the band limit.
+The radial parts of the operator kernels are roughly self-similar in the sense that the radial kernels evaluated with some band limit are related to other radial kernels (evaluated with a different band limit) by an approximate rescaling of the function.
+We use this property to define a non-locality parameter $\beta_0$ as the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
+We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes $Q/U$ to scalars $E/B$ and vice versa (see \fig{fig:rad_ker_decay}).
+An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.
+It did not explicitly derive the radial part of the kernel, but argued on geometric grounds that it should fall with angular separation as $\beta^{-2}$.
+We find that this agrees with the average behavior of radial functions after averaging oscillations and note that some such averaging always takes place in practice due to pixelization of the signal.
+However, for precision reconstruction of $E/B$ on the sphere, the oscillations must be taken into account.
+
+Our careful study of the real space operators show that they can be expressed either as Green's functions or as convolving beam functions.
+The convolution interpretation is not a totally new concept.
+It guides the discussion in \cite{Zaldarriaga2001a,Chiueh2002} and closely relates to the popular spokes and pinwheel descriptions of the $E/B$ modes.
+However, the radiation/Green's function interpretation of the operators is a new one and is discussed here for the first time.
+These two different interpretations of the operators emerge from the expression of the kernels in terms of the forward or inverse rotation Euler angles.
+The mathematical forms of the Green's function and convolution kernels swap roles (and are conjugated) when transforming back to $Q/U$ from $E/B$.
+
+The Green's function interpretation provides some useful insights into these operations.
+In particular it allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$.
+The resulting complex scalar maps can be then understood as arising from superposition of the radiated spin-0 scalar fields emanating from all the spin charges on the sphere.
+The $E/B$ mode maps are merely the real and imaginary parts of this field.
+Results that demonstrate the equivalence of these real space methods to the conventional harmonic space methods will be presented in the next paper in this series.
+
+Deeper understanding of the non-locality of the real space operators has allowed us to generalize the real space operators that transform between the spin-2 and spin-0 representations of the CMB polarization.
+We presented a systematic procedure to modify and generalize the construction of the scalar polarization fields and to control the radial kernels, specifying them with few restrictions.
+We argue that these modifications to the radial kernel have the same effect as a smoothing operation on the $E/B$ fields by a circularly symmetric beam.
+Therefore it is trivial to recover the standard CMB angular power spectra from the modified scalar polarization maps resulting from the modified kernels.
+We noted that the standard spin-raising ($\eth^2$) and spin-lowering ($\bar{\eth}^2$) operators are special cases of these generalized operators which allowed us to present a band limited representation of these operators.
+
+Modified real-space operators with compact kernels could open several alternative analysis routes in the future.
+No spin-harmonic transforms are necessary as the real space operators only rely on computing the Euler angles which can be done on the fly.
+The radial functions (depending on $P_{\ell}^{2}$) need be tabulated only once at some determined resolution.
+Especially given the Green's function interpretation of these operators, their implementation is trivially parallelizable over a compact domain, since the $E/B$ contribution from the Stokes charges in each pixel can be evaluated independently.
+Alternatively, the spatially-varying convolution kernel could be applied as a polarized effective beam, as implemented in \cite{2011ApJS..193....5M} in a parallel scheme.
+
+The real space kernels could in principle be incorporated into the pointing matrices for map making, allowing maps of $E/B$ to be made directly from instrument data, without the need for Stokes parameter maps as intermediate products.
+The pointing matrix---projecting the maps into the time-ordered data at a point---requires the convolution version of the kernel, while the transpose pointing matrix---projecting the time-ordered data to the map---requires the Green's function kernel.
+The method would be similar to pixel-based strategies to deconvolve an instrument beam during map making \citep[e.g.][]{2010ApJS..187..212C}.
+Such a strategy for map making would result in the pointing matrix in being much less sparse, hence making a practical implementation significantly challenging.
+Using the compact radial kernels might help with restoring some of the sparseness of the pointing matrix, however a real world implementation of this method requires a more careful feasibility study.
+
+Since the real space operators let us tune the locality of $E/B$ maps, this can be potentially exploited to eliminate foreground contamination from distant parts of the sky.
+Such applications can be difficult to implement using conventional harmonic space methods.
+For instance, the real space operators can be defined such that the locality of their radial kernels is varied on different portions of the sky, dictated by say the foreground morphology, resulting in some modified scalar $E'/B'$ maps.
+While this idea seems interesting, the usefulness of this idea will depend on whether the standard $E/B$ mode spectra are easily recoverable in this fashion.
+We will explore some of these possible analysis directions in the future papers of this series.
+
+Finally, the toolbox of real-space operators gives us more intuition about the $E$- and $B$-mode structure of polarized gas and dust filaments in the Milky Way, an important foreground for inflationary science.
+We demonstrate that filaments with finite length or changing radius of curvature result in $B$-mode patterns in addition to the $E$-mode pattern already expected.
+We therefore predict a characteristic $B$-mode pattern from filament sources that should be observable in future polarization measurements.
+%---------------------------------------------------------------------------------------------------------
+%\include{acknowledgments}
+\section*{Acknowledgments}
+
+This work was supported by NASA Astrophysics Theory Program under grant NNX17AF87G.
+We thank David~C.~Collins for useful discussions.
+We also thank Anthony Challinor and Mathieu Remazeilles for closely reading a draft of this text and providing useful comments.
+%---------------------------------------------------------------------------------------------------------
+\endgroup
+
+\bibliographystyle{JHEP}
+\bibliography{ref}
+
+\end{document}

### 2018-10-05 articles/jcap_referee_response/Response to referee/response to referee.tex
renamed folder to a more appropriate name

\documentclass[12pt]{article}

\usepackage[latin1]{inputenc}
\usepackage{amsmath, amsfonts, amssymb, hyperref, graphicx, multirow, subfigure, bbold}
\hypersetup{colorlinks=True,citecolor=blue}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{array}

\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{magenta}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{blue}  }
\newcommand{\rfedit}{\textcolor{magenta}}
\newcommand{\addtext}{\textcolor{BlueViolet}  }

\begin{document}

\title{Response to referee}
\author{Aditya Rotti and Kevin Huffenberger}
\date{}
\maketitle

We would like to thank the referee for a careful reviewing of our paper.  Below we systematically respond to each of the points raised by the referee, within the scope of the work presented in this article. Where necessary, we have made appropriate edits to the draft which are highlighted in \textcolor{magenta}{magenta} colored text.

\begin{itemize}

\item[{Referee comment: }] The real space formalism looks very helpful, but it is unclear what a mask can do to the E/B mixing. The E/B leakage due to masking is inevitable as Ref. [31] argued, but it is not discussed. Also, some brief comparison with the conventional approaches in the literature, such as the pure estimator (astro- ph/0511629), could be added to explain why such a real space approach is necessarily required and why it is more advantageous.
\item[{Authors response: }] We agree that masking induced $E/B$ mixing is an important issue pertinent to this translation from the spinorial to scalar description of the polarization field, however this is beyond the scope of this paper. As noted in the paper, this is a first in a series of papers and the next paper(in preparation) will discuss and detail the implementation of these real space operators, their comparison to conventional methods and issues related to masking. We do not argue that real space method is necessarily advantageous, instead we present the formalism as an alternate methodology for carrying out analysis of spin fields on the sphere. %This complementary analysis route, alternative analysis strategies which may not be possible using conventional approaches. 
\comment{Add a line to the draft.}

\item[{Referee comment: }]  At the end of paragraph 5 in the introduction, it says ?... for minimizing foreground contamination...?. Similar to the question above, it looks like the main motivation is the foreground isolation but it is not discussed.
Maybe this is still related to the first question. 
\item[{Referee comment: }] We do allude to the speculative idea of alternative methods of dealing with mitigation problems of foreground mitigation using tunable real space kernels as one of the motivations, however we are at this moment unable to discuss this in further detais.\\

\item[{Referee comment: }] The authors derived the radiation and convolution kernels that are shown in Figs. 3 and 4. It is still unclear to me what the E/B power spectra look like from this real-space computation. For example, the authors can make a quick simulation on a small patch or the full-sky to easily validate that the E/B power spectra are correctly recovered from this real space computation.

\item[{Referee comment: }]  Our main aim in this paper was to layout the formalism for real space evaluations of $E/B$ fields from the measured Stokes $Q/U$ parameters and highlight and discuss in detail the two different interpretations, namely the ``radiation" and ``convolution" forms of the real space kernels. Please see the supplementary section at the end of this response, where we present some results from real space evaluation of E/B maps and the corresponding power spectra.\\

\item[{Referee comment:}] What is the time complexity of the real space transformation? Eq. (3.26) seems to indicate it is actually $O(N_{\rm pix}^2 )$ which is not as efficient as the conventional approaches. If possible, the authors could briefly discuss it.

\item[{Authors response:}] Yes, naively the real space implementation which is perfectly equivalent to conventional methods would scale as $O(N_{\rm pix}^2 )$. However we have noted that this scaling could be significantly improved by reconstructing some filtered versions $E/B$ fields, which will have a better scaling. We are in process of quantifying this relative efficiency and plan to report our finding in a subsequent publication. \comment{Comment on computation time and clarify on computation time.}

\item[{Referee comment: }]It looks like the real part (E) and imaginary part (B) can be easily calculated from Eq. (3.8). It is unclear why the purifying procedure ? Eq. (3.25) is needed. The authors should explain it at the beginning of section 3.4. Also, the maps $\bar P_E$ and $\bar P_B$ in Eqs. (3.17) and (3.18) should be explicitly written down using E and B modes like Eq. (2.8).

\item[{Authors respone: }] As stated in the text at the beginning of Sec.~(3.4), the main point is that we present an operator which directly decomposes the total Stokes vector into a component that purely contributes to E-modes and another which contributes  to B-modes, \emph{without first having to evaluate the $E/B$ modes themselves.} One can ofcourse carry out this operation by first evaluating the $E$ \& $B$ mode maps and then translating these individually to the corresponding Stokes vector. This procedure can be evaluated by following the procedure outlined in Sec. (3.1) and Sec.(3.2). %Note that this alternate procedure would be twice as expensive, as compared to the procedure outlined in Sec.(3.4). 
\comment{It is interesting to look at the kernels.}

\item[{Referee comment: }] In the first row of Fig. 3, why is the color/pattern of the third plot so different from the rest? Is there any numerical issue with the pole? Why is necessary to show the location of the North Pole in Fig. 3?

\item[{Authors response: }] The plot has been revised to match the color scale in other plots in Fig. 3.

Note that the third plot in first row of Fig. 3, depicts the $Q$ pattern correspond to $E$ field which is non-vanishing only at the north pole (or $U$ pattern due to $B$ field which is non-zero only at the north pole). For this special setting the $Q$(or $U$) are expected to have angular symmetry while their amplitude is modulated in the radial direction by ${}_{\mathcal{M}}f$. Kindly note Eq. 3.15 and 3.16 which encode these details.

\item[{Referee comment: }] Section 3.5 fails to explain what the non-locality is, why it matters, especially how that is connected to the E/B separation problem. Also, what is the implication of the band limit dependence for E/B separation problem? Is there any first-principle calculation of the value $\ell_0$ that is purely phenomenological in the text?

\item[{Authors response: }] \addtext{We have made appropriate revisions in text to highlight the relevance of this section.} A high band limit causes the radial function to be more sharply peaked in the vicinity of the location of where the $E/B$ fields are being evaluated, as depicted in Fig.6. It is this property of the radial kernels that  clarifies why techniques of mask apodization help mitigate the $E/B$ mixing problem.%, as it explains why the leakage field is large in the vicinity of where the mask transitions from 1 to 0. $\ell_0$ is derived purely empirically as it only suggests an indicative non-locality parameter $\beta_0$.

\item[{Referee comment: }] Given the oscillatory feature in Fig. 6, is there any technical difficulty for getting a good convergence for the real space transformation when the radiation/convolution kernels are sampled at discrete pixels? Is there any convergence criterion?
\item[{Authors response: }]  The oscillatory nature of the radial kernels shown in Fig. 3 emanates purely from sums over associated Legendre polynomials, where the limits of summation are set by the band limit. There is no convergence issue related to evaluating these kernels. The discretized pixels only result in sampling these radial kernels at specific arguments.

\item[{Referee comment: }] For any subplot shown in Fig.~6, is the pixel size $\Delta \Omega$ a fixed value or varying at different lmax? Can the authors clarify this? It seems to indicate that the resulting E/B power spectra will depend on the lmax even for the same Q/U maps. Or simply, how would the lmax be chosen for a given experiment if the transformation kernel is dependent of lmax?
\item[{Authors response: }] Generation of Fig.~6 does not depend on pixel size $\Delta \Omega$. The figures (\rm i,\rm {ii},\rm {iii}) in the top panel of Fig. 6 are generated by evaluating the respective summations over associated Legendre polynomials on an arbitrarily finely spaced grid of angular separation $\beta$. These specific figures depict the radial kernels that would go into evaluating the real space kernels on the sphere.\\
$~~~~$The plot in the bottom of Fig.~6 (\rm iv, \rm v) result from evaluating a moving average with window of size $0.3 \beta_0$ on the respective radial kernels and these are presented to demonstrate that the average behaviour of the oscillatory radial kernels matches the scaling behaviour argued in Zaldariagga (2001).

\item[{Referee comment: }] With a high value of $\ell_{\rm max}$, it looks like only the neighboring pixels are important for the kernels. What is the ratio of $\beta_0/\sqrt{\Delta \Omega}$ at different $\ell_{max}$? As Fig.~7 indicates, is the portion $\theta > 3\beta_0$ just neglected to speed up the computation? If true, how big is the error?
\item[{Authors response: }] In this work we do not compute the $E/B$ maps to evaluate and asses the quality of the corresponding spectra. The purpose of Fig.~7 is to present some example radial kernels, their respective harmonic space representations and the resultant harmonic space filters which would be needed to evaluate the default $E/B$ mode spectra. Implementation details of the real space operators and assessing the quality of the reconstructed $E/B$ maps and the corresponding spectra is the subject of follow up work on this topic. For a simple demonstration see the supplementary section.

%\revisit{The ratio $\beta_0/\sqrt{\Delta \Omega} = \frac{\pi \ell_0/\ell_{\rm max}} \frac{\sqrt{4 \pi}}{\sqrt{12 N_{\rm side}^2-1}}$

\item[{Referee comment: }] In Fig. 7, the authors need to discuss a few aspects for the chosen example of the modified radial function, including what motivates this form, how this is done for the real-space maps and how it is reconstructed. A fractional error is seen from the input (red) and reconstructed (dashed black) so there might be a leakage from the E modes into B modes. Ideally the reconstruction at any $\ell_{\rm max}$ should work, for example $\ell_{\rm max} = 768$, not just limited to 1536. Can the authors verify this?
\item[{Authors response: }] The red curve is motivated by demanding that the radial kernel have a compact support, unlike the default radial kernel ${}_\mathcal{M} f$ which spans the complete domain $\theta \in [0,\pi]$. In Fig.~7, the black curve represents the band limited ($\ell_{\rm max}=1536$) reconstruction of the red curve and the error represents the inability to reconstruct the red curve given the band limit. This is likely to limit the reconstruction of large scale $E/B$ modes, however it will not result in $E/B$ mixing. The details of how this would be implemented on real data and assessing the quality of $E/B$ reconstruction are beyond the scope of this work. However, for a simple demonstration see the supplementary section.

\item[{Referee comment: }] It is unclear what motivates the discussion of section 4 on page 19. The authors should add some introductory text at the beginning of section 4 to connect it to the previous sections.
\item[{Authors response: }] \addtext{We have appropriate text at the beginning of Sec. 4.}

\item[{Referee comment: }] A few definitions are missing: $\bar P_E$ and $\bar P_B$ in Eqs.~(3.17) and (3.18), ${}_{+2} X_{E/B}$ in Eq. (3.26), ${}_\mathcal{M} f$ in Eq. (3.5c), $N_{\rm pix}$ and $N_{\rm alm}$ in Eq. (2.9).
\item[{Authors response: }] Eqs.~(3.17),  Eq.~(3.18) and Eq. (3.26) serve as definitions of the variables $\bar P_E$, $\bar P_B$ and ${}_{+2} X_{E/B}$ respectively. Going from Eq.~(3.5b) to Eq.~(3.5c) defines ${}_\mathcal{M} f$ by association. The text has now been appropriately modified to explicitly define $N_{\rm pix}$ and $N_{\rm alm}$.

\item[{Referee comment: }] Fig. 5 seems to be redundant because Fig. 6 shows the same content although in log scale. The authors should mention the difference between the two.
\item[{Authors response: }] Yes Fig.~(5) and Fig.~(6) decpict the same radial kernels, however Fig.~(5) serves to clearly show some of the features of the radial kernel which are not visible in the log-scale version of the plot. For instance the negatives of the radial kernel, the vanishing of ${}_\mathcal{M}f$ etc...

\item[{Referee comment: }] Figs 6 and 7 are not legible.
\item[{Authors response: }] \addtext{The label sizes have been revised to make the figures more legible.}

\end{itemize}

\section*{Supplementary}
We note that, many of the questions raised by the referee, are relevant, but beyond the scope of the work presented in this article. Most of these questions form the topic of our follow up work, where we discuss the implementation details of the real space operator, their comparison to conventional approaches, E/B mixing on masked skies using these real space kernels, etc.

Since the referee has asked many question pertaining to issues relating to actual implementations, here we present some results from our follow up work.

\end{document}

### 2018-10-05 articles/jcap_referee_response/modified article jcap/article.tex
renamed folder to a more appropriate name

--- 2018-10-05 articles/formalism_jcap_submission/Original jcap submission/article/article.tex
@@
 \newcommand{\rfedit}{\textcolor{magenta}  }
+\newcommand{\addtext}{\textcolor{magenta}  }
 \newcommand{\soothe}{\textcolor{BlueViolet}  }
@@
 %
-where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
+where $s$ denotes the spin of the basis functions, \addtext{$N_{pix}$ denotes the number of pixels on the sphere and $N_{alms}$ denotes the number of spherical harmonic coefficients of expansion.} %and
+Note that our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.
 We introduce this to ensure the orthonormality of these operations on the discretized sphere when the pixel size is sufficiently small, ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$, and also maintain the standard definition of spherical harmonics.
@@
 \subfigure[\label{fig:fbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
-\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax_zaldariagga_scaling.pdf}}
+\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax_zaldariagga_scaling.pdf}}
 
@@
 We show moving averages over oscillations in \fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg}.
-They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $1.4\beta_0$.
+They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $\beta_0$.
 These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}

### 2018-11-30 articles/jcap_referee_response/Response to referee/response to referee.tex
added near final referee report and updated draft

@@
 \item[{Authors response: }] We agree that masking induced $E/B$ mixing is an important issue pertinent to this translation from the spinorial to scalar description of the polarization field, however this is beyond the scope of this paper.
-As noted in the paper, this is a first in a series of papers and the next paper(in preparation) will discuss and detail the implementation of these real space operators, their comparison to conventional methods and issues related to masking.
-We do not argue that real space method is necessarily advantageous, instead we present the formalism as an alternate methodology for carrying out analysis of spin fields on the sphere.
-%This complementary analysis route, alternative analysis strategies which may not be possible using conventional approaches.
-\comment{Add a line to the draft.}
+We do not argue that real space method is necessarily advantageous, instead we present the real space formalism as an alternate methodology for carrying out analysis of spin fields on the sphere.
 
-\item[{Referee comment: }]  At the end of paragraph 5 in the introduction, it says ?...
-for minimizing foreground contamination...?.
+As noted in the paper, this is a first in a series of papers and the following paper (in preparation) will discuss and detail the implementation of these real space operators, their comparison to conventional methods and issues related to masking.
+
+\item[{Referee comment: }]  At the end of paragraph 5 in the introduction, it says ``...
+for minimizing foreground contamination...".
 Similar to the question above, it looks like the main motivation is the foreground isolation but it is not discussed.
 Maybe this is still related to the first question. 
-\item[{Referee comment: }] We do allude to the speculative idea of alternative methods of dealing with mitigation problems of foreground mitigation using tunable real space kernels as one of the motivations, however we are at this moment unable to discuss this in further detais.\\
+\item[{Referee comment: }] We do allude to the speculative idea of alternative methods of dealing with mitigation problems of foreground mitigation using tunable real space kernels as one of the motivations, however we are at this moment unable to discuss this in further detail.\\
 
@@
 \item[{Referee comment: }]  Our main aim in this paper was to layout the formalism for real space evaluations of $E/B$ fields from the measured Stokes $Q/U$ parameters and highlight and discuss in detail the two different interpretations, namely the ``radiation" and ``convolution" forms of the real space kernels.
-Please see the supplementary section at the end of this response, where we present some results from real space evaluation of E/B maps and the corresponding power spectra.\\
+Please see the supplementary section at the end of this response, where we present preliminary results from real space evaluation of E/B maps and the corresponding power spectra.\\
 
@@
 We are in process of quantifying this relative efficiency and plan to report our finding in a subsequent publication.
-\comment{Comment on computation time and clarify on computation time.}
 
@@
 
-\item[{Authors respone: }] As stated in the text at the beginning of Sec.~(3.4), the main point is that we present an operator which directly decomposes the total Stokes vector into a component that purely contributes to E-modes and another which contributes  to B-modes, \emph{without first having to evaluate the $E/B$ modes themselves.} One can ofcourse carry out this operation by first evaluating the $E$ \& $B$ mode maps and then translating these individually to the corresponding Stokes vector.
-This procedure can be evaluated by following the procedure outlined in Sec.
-(3.1) and Sec.(3.2).
-%Note that this alternate procedure would be twice as expensive, as compared to the procedure outlined in Sec.(3.4).
-\comment{It is interesting to look at the kernels.}
+\item[{Authors respone: }] We would like to clarify that Eq.~3.25 decomposes the total Stokes parameters into two spin-2 components that correspond to the $E$-modes and $B$-modes respectively.
+The Stokes parameters corresponding to the $E$ and $B$ scalar fields are not the same as the scalar fields themselves  Infact the main point of Sec.~3.4 is that we present a real space operator which directly decomposes the total Stokes vector into these components, \emph{without first having to evaluate the scalar $E/B$ modes themselves.}
+
+One can of course carry out this operation by first evaluating the scalar $E/B$ mode maps (as in Eq.~3.8) and then translating these individually to the corresponding Stokes vector (using Eq.~3.13).
+This would require making two different operations unlike the single step operation presented in Sec.
+3.4 of the paper.
 
@@
 
-Note that the third plot in first row of Fig.
+The third plot in first row of Fig.
 3, depicts the $Q$ pattern correspond to $E$ field which is non-vanishing only at the north pole (or $U$ pattern due to $B$ field which is non-zero only at the north pole).
@@
 
-\item[{Authors response: }] \addtext{We have made appropriate revisions in text to highlight the relevance of this section.} A high band limit causes the radial function to be more sharply peaked in the vicinity of the location of where the $E/B$ fields are being evaluated, as depicted in Fig.6.
-It is this property of the radial kernels that  clarifies why techniques of mask apodization help mitigate the $E/B$ mixing problem.%, as it explains why the leakage field is large in the vicinity of where the mask transitions from 1 to 0.
-$\ell_0$ is derived purely empirically as it only suggests an indicative non-locality parameter $\beta_0$.
+\item[{Authors response: }] Non-locality is not a sharp concept.
+It is introduced to give an idea of how much contribution the E/B fields at the central pixels receive from other sky locations which are at varying angular distances from it.
+This is determined by the variations in the amplitude of the radial kernel which is the topic of discussion in Sec.
+3.5.
+
+A high band limit causes the radial function to be more sharply peaked in the vicinity of the location of where the $E/B$ fields are being evaluated, as depicted in Fig.6.
+It is this property of the radial kernels that  clarifies why techniques of mask apodization help mitigate the $E/B$ mixing problem.
+ \hspace{0.02cm} $\ell_0$ is derived empirically by studying the radial kernel which is used to define a characteristic non-locality parameter $\beta_0$.
+There is no first principle calculation of $\ell_0$.
+
+ Even though the kernels become sharply peaked for higher band limit, the E/B field evaluations cannot be made local particularly if one is interested in measuring the power on large angular scales.
+So in this sense non-locality is multipole dependent.
 
@@
 These specific figures depict the radial kernels that would go into evaluating the real space kernels on the sphere.\\
-$~~~~$The plot in the bottom of Fig.~6 (\rm iv, \rm v) result from evaluating a moving average with window of size $0.3 \beta_0$ on the respective radial kernels and these are presented to demonstrate that the average behaviour of the oscillatory radial kernels matches the scaling behaviour argued in Zaldariagga (2001).
+$~~~~$The plot in the bottom of Fig.~6 (\rm iv, \rm v) result from evaluating a moving average with window of size $\beta_0$ on the respective radial kernels and these are presented to demonstrate that the average behaviour of the oscillatory radial kernels matches the scaling behaviour argued in Zaldariagga (2001).\\
+$~~~~$The $\ell^{\rm Data}_{\rm max}$ for any analysis is set by the instrument characteristics such as the rms noise and the  beam width, like in any other conventional band limited analysis.\\
+$~~~~$ Lets say we choose $\ell_{\rm max}^{\rm Analysis}$ to compute the radial kernel, then (i) if  $\ell_{\rm max}^{\rm Analysis}< \ell^{\rm Data}_{\rm max}$ then this will result in $E/B$ maps which are filtered to exclude modes $\ell > \ell_{\rm max}^{\rm Analysis}$, (ii) if  $\ell_{\rm max}^{\rm Analysis}> \ell^{Data}_{\rm max}$ then this makes no difference to the resultant $E/B$ modes as long as the radial kernels are evaluated over the complete domain $[0,\pi]$.
 
@@
 Implementation details of the real space operators and assessing the quality of the reconstructed $E/B$ maps and the corresponding spectra is the subject of follow up work on this topic.
-For a simple demonstration see the supplementary section.
-
 %\revisit{The ratio $\beta_0/\sqrt{\Delta \Omega} = \frac{\pi \ell_0/\ell_{\rm max}} \frac{\sqrt{4 \pi}}{\sqrt{12 N_{\rm side}^2-1}}$
@@
 In Fig.~7, the black curve represents the band limited ($\ell_{\rm max}=1536$) reconstruction of the red curve and the error represents the inability to reconstruct the red curve given the band limit.
-This is likely to limit the reconstruction of large scale $E/B$ modes, however it will not result in $E/B$ mixing.
+This is likely to limit the reconstruction of large scale $E/B$ modes, however it will not result in $E/B$ mixing (see supplementary section at the end).
+Since this black curve will never be relevant in actual analysis, we have removed the black dashed curve from the plot.
+
 The details of how this would be implemented on real data and assessing the quality of $E/B$ reconstruction are beyond the scope of this work.
-However, for a simple demonstration see the supplementary section.
+However an example demonstration can be found in the supplementary section at the end of this response.
 
@@
 The authors should add some introductory text at the beginning of section 4 to connect it to the previous sections.
-\item[{Authors response: }] \addtext{We have appropriate text at the beginning of Sec. 4.}
+\item[{Authors response: }] The translations between Q/U and E/B representations of the polarization map, the azimuthal dependence of the kernel cannot be altered, because they are tied to the spin properties of the fields.
+The only freedom is to alter the radial kernel and this is the motivation for Section 4.
+This is already explicitly discussed in the first paragraph of Section 4.
 
@@
 Going from Eq.~(3.5b) to Eq.~(3.5c) defines ${}_\mathcal{M} f$ by association.
-The text has now been appropriately modified to explicitly define $N_{\rm pix}$ and $N_{\rm alm}$.
+The text following Eq.~2.9 has been modified to explicitly define $N_{\rm pix}$ and $N_{\rm alm}$.
 
 \item[{Referee comment: }] Fig. 5 seems to be redundant because Fig. 6 shows the same content although in log scale. The authors should mention the difference between the two.
-\item[{Authors response: }] Yes Fig.~(5) and Fig.~(6) decpict the same radial kernels, however Fig.~(5) serves to clearly show some of the features of the radial kernel which are not visible in the log-scale version of the plot.
-For instance the negatives of the radial kernel, the vanishing of ${}_\mathcal{M}f$ etc...
+\item[{Authors response: }] Yes, Fig.~(5) and Fig.~(6) decpict the same radial kernels, however Fig.~(5) serves to clearly show some of the features of the radial kernel which are not visible in the log-scale version of the plot.
+For instance the negatives of the radial kernel, the vanishing of ${}_\mathcal{M}f$ at the two poles etc...
 
 \item[{Referee comment: }] Figs 6 and 7 are not legible.
-\item[{Authors response: }] \addtext{The label sizes have been revised to make the figures more legible.}
+\item[{Authors response: }] The label sizes have been revised to make them more legible.
 
@@
 
+\newpage
 \section*{Supplementary}
-We note that, many of the questions raised by the referee, are relevant, but beyond the scope of the work presented in this article.
-Most of these questions form the topic of our follow up work, where we discuss the implementation details of the real space operator, their comparison to conventional approaches, E/B mixing on masked skies using these real space kernels, etc.
+We note that, many of the questions raised by the referee, are relevant, but beyond the scope of the work presented in the article.
+Many of these questions form the topic of our follow up work, where we discuss the implementation details of the real space operator, their comparison to conventional approaches, E/B mixing on masked skies using these real space kernels, etc.
 
-Since the referee has asked many question pertaining to issues relating to actual implementations, here we present some results from our follow up work.
+However, here we present preliminary results of the exercise of evaluating the $E/B$ maps using the real space kernels and their corresponding power spectra. 
+%
+\begin{figure}[h]
+\centering
+\subfigure[\label{fig:fbeta}]{\includegraphics[width=0.45\columnwidth]{modified_radial_kernel.pdf}}
+\subfigure[\label{fig:gl}]{\includegraphics[width=0.45\columnwidth]{effective_beam.pdf}}
+\caption{}
+%\label{fig:rad_ker_decay}
+\end{figure}
+%
+We work at a Healpix resolution of ${\textrm Nside}=256$.
+We simulate CMB polarization map using power spectra computed with CAMB with fiducial cosmological parameters and B-modes corresponding to $r=0.001$.
+We evaluate the $E/B$ maps using real space kernels on a patch of $10 ^{\circ} \times 25^{\circ}$, centered at a latitude of zero and the long axis of the patch aligned with the equator.
+%
+\begin{figure}[h]
+\centering
+\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_B.pdf}}
+\subfigure{\includegraphics[width=0.45\columnwidth]{true_B.pdf}}
+\caption{}
+\label{fig:compare_B}
+\end{figure}
+%
+We evaluate the E/B maps using the real space operator, in which we modify the radial kernel by imposing a radial cut-off of $\sim 22^{\circ}$.
+The radial kernel used for constructing the real space operator is shown in Fig.
+\ref{fig:fbeta} while the effective beam corresponding to it is depicted in Fig.~\ref{fig:gl}.
+The resultant $B$ mode maps evaluated using the real space method and true B-mode map is shown in Fig~\ref{fig:compare_B}. 
+%
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_ee_spectra.pdf}}
+\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_bb_spectra.pdf}}
+\caption{}
+\label{fig:compare_spectra}
+\end{figure}
+%
+Finally the power spectra estimated from $E/B$ maps evaluated using these real space operators and their comparison to the true power spectrum is depicted in Fig.~\ref{fig:compare_spectra}.
+
+Note that in the results presented here, while we compute the $E/B$ maps on the square patch, we use Stokes parameters outside the mask boundary.
+We do not claim to address any issue relating to masking related E/B mixing via these results.
 

### 2018-11-30 articles/jcap_referee_response/modified article jcap/article.tex
added near final referee report and updated draft

@@
 The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( {(\beta-\beta_s)}{/\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
-The black dashed curve depicts the band limited reconstruction of the modified radial function.
-\textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
+\addtext{\st{The black dashed curve depicts the band limited reconstruction of the modified radial function.}} \textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
 The dashed curves of the corresponding color depict the inverse of the harmonic functions.

### 2018-12-06 articles/jcap_referee_response/Response to referee/response to referee.tex
refinements to referee report and revised draft

@@
 
-\item[{Authors response:}] Yes, naively the real space implementation which is perfectly equivalent to conventional methods would scale as $O(N_{\rm pix}^2 )$.
-However we have noted that this scaling could be significantly improved by reconstructing some filtered versions $E/B$ fields, which will have a better scaling.
+\item[{Authors response:}] Yes the real space implementation which is perfectly equivalent to conventional methods would scale as $O(N_{\rm pix}^2 )$.
+However we have noted that the computation time can be significantly improved by reconstructing a filtered versions $E/B$ fields which would scale as $O(\epsilon N_{\rm pix}^2 )$, where $\epsilon$ is a very small number and is determined by the radial cutoff.
 We are in process of quantifying this relative efficiency and plan to report our finding in a subsequent publication.
@@
 
-However, here we present preliminary results of the exercise of evaluating the $E/B$ maps using the real space kernels and their corresponding power spectra. 
+\textit{In this supplementary section we present some preliminary results which basically demonstrates that the real space E/B separation works.}
+
+We evaluate the $E/B$ maps from simulated Stokes Q/U maps using the real space kernels and finally evaluate the corresponding power spectra. 
 %
@@
 %
-We work at a Healpix resolution of ${\textrm Nside}=256$.
+For this exercise, we work at a Healpix resolution of ${\textrm Nside}=256$.
 We simulate CMB polarization map using power spectra computed with CAMB with fiducial cosmological parameters and B-modes corresponding to $r=0.001$.
-We evaluate the $E/B$ maps using real space kernels on a patch of $10 ^{\circ} \times 25^{\circ}$, centered at a latitude of zero and the long axis of the patch aligned with the equator.
+We evaluate the $E/B$ maps using real space kernels on a patch of $10 ^{\circ} \times 25^{\circ}$, centered at zero galactic latitude and the long axis of the patch aligned with the equator.
 %
@@
 \centering
-\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_B.pdf}}
-\subfigure{\includegraphics[width=0.45\columnwidth]{true_B.pdf}}
-\caption{}
+\subfigure[Real space B]{\includegraphics[width=0.45\columnwidth]{real_space_B.pdf}}
+\subfigure[True B]{\includegraphics[width=0.45\columnwidth]{true_B.pdf}}
+\caption{The figure on the left depicts the B-mode maps evaluated using the modified real space kernel while that on the right depicts the true B-mode map.}
 \label{fig:compare_B}
@@
 The radial kernel used for constructing the real space operator is shown in Fig.
-\ref{fig:fbeta} while the effective beam corresponding to it is depicted in Fig.~\ref{fig:gl}.
-The resultant $B$ mode maps evaluated using the real space method and true B-mode map is shown in Fig~\ref{fig:compare_B}. 
+\ref{fig:fbeta} while the effective harmonic space filter corresponding to this radial filter is depicted in Fig.~\ref{fig:gl}.
+
+The resultant $B$ mode maps evaluated using the real space method and true B-mode map evaluated using the conventional method is shown in Fig~\ref{fig:compare_B}. 
 %
@@
 \centering
-\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_ee_spectra.pdf}}
-\subfigure{\includegraphics[width=0.45\columnwidth]{real_space_bb_spectra.pdf}}
-\caption{}
+\subfigure[E-mode power spectra]{\includegraphics[width=0.45\columnwidth]{real_space_ee_spectra.pdf}}
+\subfigure[B-mode power spectra]{\includegraphics[width=0.45\columnwidth]{real_space_bb_spectra.pdf}}
+\caption{In these plots, the black line depicts the theory power spectrum, the blue line depict the power spectrum evaluated from the true E/B maps while the red dashed lines depict the power spectrum evaluted from real space evaluated E/B maps.}
 \label{fig:compare_spectra}
@@
 
-Note that in the results presented here, while we compute the $E/B$ maps on the square patch, we use Stokes parameters outside the mask boundary.
-We do not claim to address any issue relating to masking related E/B mixing via these results.
+Note that in the results presented here, we compute the $E/B$ maps on the square patch for which we have used Stokes parameters outside the mask boundary.
+Hence via the results presented here, we do not claim to address any issues relating to masking induced E/B mixing.
 

### 2018-12-06 articles/jcap_referee_response/modified article jcap/article.tex
refinements to referee report and revised draft

@@
 \section{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
-With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
+\addtext{In this section we relate our new found knowledge about the radial part of the kernel to the standard CMB polarization angular power spectra.} With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
 The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.

### 2018-12-10 articles/jcap_referee_response/modified article jcap/article.tex
Minor typo fixes and minor rewording.

@@
 The formalism for converting the Stokes parameters to scalar quantities is well established \citep{1997PhRvD..55.7368K,1997PhRvD..55.1830Z}.
-The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), which are derivatives evaluated locally and filtered.
+The spin-0 scalar $E$/$B$ modes relate to the spin-2 complex Stokes parameters via the spin-raising and -lowering operators ($\eth^2,\bar \eth^2$), derivatives evaluated locally,  which are then filtered.
 In practice the $E$/$B$ modes are computed to some specified band limit, and the filtering and band limit make them non-local functions of the polarization field.
@@
 
-Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations and hence must be spin-0 or scalar quantity by definition:
+Given these transformation properties, the combination ${}_{+2}X(\hat{n}_q)e^{-i2\alpha_{qe}}$ is invariant under rotations and hence must be a spin-0 or scalar quantity by definition:
 \beq
@@
 \includegraphics[width=0.5\columnwidth]{radiation_convolution.pdf}
-\caption{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle(sphere), representative of the coordinate dependence of the Stokes parameters.
+\caption{The local cartesian coordinates $(\hat{x},\hat{y})$ are drawn on the red circle, representative of the coordinate dependence of the Stokes parameters.
 The two sets of dotted lines drawn at representative points denote great circles, one which passes through the central point labelled `$e$' and the other chosen such that the two have locally orthogonal tangent vectors $(\hat{r},\hat{\phi})$.
@@
 For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$.
-We choose such a low band limit to highlight some key features of their radial profile.
+We choose such a low band limit to highlight some key features of the radial profiles.
 %
@@
 The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.
-It has an oscillatory nature at intermediate angular separations and vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$ (this is critical to ensure that the derived fields have the necessary spin properties), since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
+It has an oscillatory nature at intermediate angular separations and vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
+(This is critical to ensure that the derived fields have the necessary spin properties.)
 
@@
 It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.
-${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
+The function ${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$.
+However, it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.
 
@@
 At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$.
-As the band limit changes, the small angle portion of the radial functions have a similar shape.
+Even as the band limit changes, the small-angle portions of the radial functions have similar shapes.
 
@@
 {Specifically, when $\ell_{\rm max} > \ell'_{\rm max}$, the global maxima of the kernel with maximum multipole $\ell_{\rm max}$ is amplified by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$, while the period of the oscillation is compressed by a factor $(\ell'_{\rm max}/\ell_{\rm max})$.
-The detailed accuracy of this approximation varies with the angular separation $\beta$ and the difference in the maximum multipoles ($\ell_{\rm max}$, $\ell'_{\rm max}$)  used in evaluating the two functions.}
+The detailed accuracy of this approximation varies with the angular separation $\beta$ and the difference in the maximum multipoles ($\ell_{\rm max}$, $\ell'_{\rm max}$)  used in evaluating the two functions.}  \rfedit{The scaling does not hold as angle $\beta$ approaches the antipodal point.}
 
@@
 However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
-We set the width of the smoothing window to $0.3\beta_0$, and this results in the narrowing of the smoothing width as the band limit increases, so as to keep the number of oscillations averaged over roughly the same.
-This agrees with the hypothesis for the {flat sky and continuum case}, for which e.g.
+\revisit{To take the average, we set the width of the moving window to $0.3\beta_0$, so that it narrows as the band limit increases, keeping the number of oscillations in the window roughly the same.
+The finding of $\beta^{-2}$} agrees with the hypothesis for the {flat sky and continuum case}, for which e.g.
 Zaldarriaga (2001) \cite{Zaldarriaga2001a} argued that form of the radial function has to be ${}_\mm f(\beta>0)\simeq\beta^{-2}$ to ensure that the Fourier modes of Stokes $Q/U$ relate to those of $E/B$ merely by rotations (with no scale dependence).
 In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.
-Applying a moving average on radial functions with increasing band limit, we see that a larger fraction of angular domain matches the scaling of $\beta^{-2}$.
-Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
+\revisit{When the moving average is applied radial functions with progressively higher band limits, we see that a larger and larger fraction of angular domain matches the scaling of $\beta^{-2}$.}   Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
 In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.
 
-Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function partly falls outside the domain and this is in part responsible for the scaling deviating from the power law, but it is also important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.
+\revisit{In \fig{fig:fbeta_avg}, near the edges ($\beta \rightarrow 0,\pi$), the window function partly falls outside the domain, and this in part causes the the scaling to deviate from the power law $\beta^{-2}$.}  Note also that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.
 %---------------------------------------------------------------------------------------------------------
@@
 \section{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
-\addtext{In this section we relate our new found knowledge about the radial part of the kernel to the standard CMB polarization angular power spectra.} With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
+\addtext{In this section we relate our new-found knowledge about the radial part of the kernel to the computation of the standard CMB polarization power spectra.} With this better understanding, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
 The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.
@@
  \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel modified by a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, and a radial function without oscillations and an exponential cutoff.
-Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
+Note that the smoothing tends to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.
 The exponential cutoff (red curve) by construction has a very small non-locality (parameterized by $\beta_0$).
@@
 where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, that is relevant in the case of a discretely sampled spin-2 field on the sphere.
-In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.
+In the limit of $\ell_{\rm max} \rightarrow \infty$, we have $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.
 The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.
@@
 The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.
-The positive components for the $E$ part of the Green's function align and reinforce along the filament, consequently the filament is highlighted as a segment with $E>0$.
+The positive components for the $E$ part of the Green's function align and reinforce along the filament, and consequently the filament is highlighted as a segment with $E>0$.
 Since the over-density will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.
@@
  For a North--South filament, the $B$-mode pattern is positive on the northeast and southwest, and negative in the northwest and southeast.
-(\fig{fig:polfilaments} shows East to the left in sky map convention.)  The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
-In contrast to the kernel radial fuctions, which are more compact at higher band limit, the filament $B$-mode  pattern does not depend much on the band limit, provided it is sufficient to resolve the filament structure.
+(\fig{fig:polfilaments} shows East to the left in sky map convention, and uses HEALPix conventions for polarization angle definitions.)  The size of this $B$-mode pattern is set by the dimensions of the filament, chiefly the width.
+In contrast to the kernel radial fuctions, which are more compact at higher band limit, the filament $B$-mode  pattern does not depend much on the band limit, provided that it is sufficient to resolve the filament structure.
 A filament with a more gradual edge has a $B$-pattern that is more spread out, but follows the same general structure.
@@
 In a polarization pattern aligned at $45^\circ$ to the filament, the $E$ pattern will swap with the $B$ pattern.
-Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament, this information could potentially shed light on the internal dynamics of filaments.
+Careful study of the $E/B$ mode power in filaments can provide insights into the orientation of the magnetic field with respect to the axis of the filament.
+This information could potentially shed light on the internal dynamics of filaments.
 % 
@@
 Detecting $B$-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.
-While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
+While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in future, higher-fidelity data.
 %---------------------------------------------------------------------------------------------------------
@@
 We use this property to define a non-locality parameter $\beta_0$ as the angular distance at which the amplitude of the radial kernel falls below one percent of its maxima and it  is a function of the maximum multipole $\ell_{\rm max}$ available for the analysis.
-We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operator that converts Stokes $Q/U$ to scalars $E/B$ and vice versa (see \fig{fig:rad_ker_decay}).
+We empirically show that the non-locality parameter is approximately given by: $\beta_0 = \mathrm{min}(180^{\circ}, 180^{\circ} \frac{\ell_{0}}{\ell_{\rm max}})$ with $\ell_{0}=22$ for the operators that converts Stokes $Q/U$ to scalars $E/B$ and vice versa (see \fig{fig:rad_ker_decay}).
 An analysis in  \cite{Zaldarriaga2001a} treated real space $E/B$ operators in the flat sky.

### 2018-12-10 articles/jcap_referee_response/modified article jcap/article.tex
added final resubmitted version of the draft

@@
 However, when we average over several oscillations with a moving window, we find that the average behavior at intermediate $\beta$ scales as $\beta^{-2}$, visible in \fig{fig:fbeta_avg}.
-\revisit{To take the average, we set the width of the moving window to $0.3\beta_0$, so that it narrows as the band limit increases, keeping the number of oscillations in the window roughly the same.
+\addtext{To take the average, we set the width of the moving window to $0.3\beta_0$, so that it narrows as the band limit increases, keeping the number of oscillations in the window roughly the same.
 The finding of $\beta^{-2}$} agrees with the hypothesis for the {flat sky and continuum case}, for which e.g.
@@
 In addition, we find that ${}_{\md}f$ under a moving average shows a similar scaling of $\beta^{-2}$, as seen in \fig{fig:dfbeta_avg}.
-\revisit{When the moving average is applied radial functions with progressively higher band limits, we see that a larger and larger fraction of angular domain matches the scaling of $\beta^{-2}$.}   Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
+\addtext{When the moving average is applied radial functions with progressively higher band limits, we see that a larger and larger fraction of angular domain matches the scaling of $\beta^{-2}$.}   Extrapolating this trend to the case of a very high band limit one expects this behavior to approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi-\epsilon]$ for $\epsilon \ll 1$.
 In essence the moving average can be understood as the averaging resulting from discrete sampling of a continuum field (one with an infinite band limit) where the width of the averaging window corresponds to the size of the pixel.
 
-\revisit{In \fig{fig:fbeta_avg}, near the edges ($\beta \rightarrow 0,\pi$), the window function partly falls outside the domain, and this in part causes the the scaling to deviate from the power law $\beta^{-2}$.}  Note also that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.
+\addtext{In \fig{fig:fbeta_avg}, near the edges ($\beta \rightarrow 0,\pi$), the window function partly falls outside the domain, and this in part causes the the scaling to deviate from the power law $\beta^{-2}$.}  Note also that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of these points cannot have the same power law behavior.
 %---------------------------------------------------------------------------------------------------------
@@
 The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( {(\beta-\beta_s)}{/\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$.
-\addtext{\st{The black dashed curve depicts the band limited reconstruction of the modified radial function.}} \textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
+\textit{Top right:} The harmonic representation of the respective radial functions as indicated by the legend.
 The dashed curves of the corresponding color depict the inverse of the harmonic functions.
